### 2021-03-22 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Introduction of manuscript is drafted, with additional literature to frame the paper

---
title: What about children's wellbeing? Framing active school travel in Ontario, Canada
author:
  # see ?rjournal_article for more information
  - name: Elise Desjardins
    affiliation: School of Earth, Environment & Society, McMaster University
    address:
    - 1280 Main Street West, Hamilton, ON L8S 4L8
    email: desjae@mcmaster.ca
  - name: Jason Lam
    email: lamj54@mcmaster.ca
    affiliation: Affiliation 1
    address:
    - line 1 affiliation 1
  - name: Owen Waygood
    affiliation: University Polytechnique de Montreal
    email: owen.waygood@polymtl.ca
    address:
    - Montreal, QC
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: Affiliation 1
    address:
    - line 1 affiliation
abstract: >
  An abstract of less than 200 words.
preamble: |
  % Any extra LaTeX you need in the preamble

journal: "Journal of School Health"
date: "`r Sys.Date()`"
bibliography: References.bib
#linenumbers: true
#numbersections: true
output: rticles::rjournal_article
---

# Background

Walking and cycling to school, commonly known as active school travel or active school transportation (AST) has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020]. This trend has prompted an abundance of worlwide research over the past two decades to examine why fewer children are walking and cycling to school, what influences AST, and the associated implications for children's health. Many studies have been specific to Canada [*inter alia*, see: @buliungActiveSchoolTransportation2009; @faulknerSchoolTravelChildren2013; @mammenUnderstandingDriveEscort2012; @mammenSchoolTravelPlanning2014; @rothmanActiveSchoolTransportation2021; @wilsonUnderstandingChildParent2018] which aligns with and informs a growing interest in increasing active school travel levels. Indeed, a diversity of stakeholders responsible for transportation, public health, and education are collaborating and spearheading efforts to get more children walking and cycling. Promoting AST is seen as an affordable, convenient, and environmentally friendly way to enhance the mental, physical, and psychological health of children [@mammenSchoolTravelPlanning2014]. These goals should be clearly articulated and reflected in transportation plans and policies to guide initiatives, but there is research lacking that specifically explores how Canadian municipalities and schools frame and discuss AST with the public.

## Literature Review

Several recent reviews offer a comprehensive synopsis of the state of active school travel [@ikedaAssociationsChildrenActive2018; @rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenIndependent2013], while others assess the efficacy of interventions and strategies that have been implemented to encourage and support AST [@buttazzoniActiveSchoolTravel2018; @chillonSystematicReviewInterventions2011; @jonesInterventionsPromotingActive2019; @laroucheEffectivenessActiveSchool2018; @marziInterventionsAimingPromote2020; @schonbachStrategiesEffectsSchoolbased2020]. Many patterns emerge from studies within and between countries with respect to the factors that are positively associated with AST. These factors broadly fall into distinct categories: individual, household, social environment, and physical environment. Among the most influential are age, gender, distance to school, parental perceptions of the environment [@demeesterParentalPerceivedNeighborhood2014] and children's skills [@ghekiereInsightsChildrenIndependent2017], quality of the built environment, and urban infrastructure. The consensus is that these factors are interrelated and that interventions ought to target multiple factors in order to increase walking and cycling levels to school. More recently, researchers have been exploring the link between transportation and children's wellbeing [@waygoodTransportChildrenWellbeing2020], which has relevant applications to the study of school travel and satisfaction [see @vandenbergFactorsAffectingParental2020] among others.

Furthermore, AST is one of the most common opportunities for children to travel without adult supervision on a regular basis. CIM was first described by Hillman et al. [-@hillmanOneFalseMove1990] as the freedom of children to travel and play within their neighborhood and city without the presence of adults. Similar to AST, children's independent mobility (CIM) is much less common than it was for previous generations [@bhosaleIntergenerationalChangeChildren2017], and is influenced by related personal and environmental factors [@marziChildrenIndependentMobility2018]. CIM is particularly important for different domains of children's health and wellbeing [@riaziChildrenIndependentMobility2018]. There is also sufficient evidence in the literature linking the association between AST and CIM [@laroucheRelationshipsChildrenIndependent2020; @mitraIndependentMobilityMode2013], particularly in boys [@schoeppeAssociationsChildrenIndependent2014]. The gender disparity has also been noted in other papers regarding CIM [@marziSocialPhysicalEnvironmental2018; @marziInterventionsAimingPromote2020] with recommendations being made for interventions to specifically target girls to boost their mobility within their neighborhood [@schoeppeSociodemographicFactorsNeighbourhood2015]. CIM offers other benefits to adolescents such as increasing traffic and safety skills, boosting spatial awareness when navigating public spaces, and providing more opportunity for social interaction with peers [@schoeppeAssociationsChildrenIndependent2014]. What is less clear is how CIM plays into the consideration of policymakers when they act on the objective of improving AST.

In the case of Canada... _review a few prominent Canadian studies on AST and CIM in more detail: Riazi et al., 2019; Mammen et al., 2012 & 2014; Rothman et al., 2021_

The correlates and effective interventions of AST and CIM are important knowledge for policymakers because they identify points of intervention, as well as potential benefits, that ought to be communicated to the public to build support for new planning paradigms. Framing analysis is one method to analyze how particular issues are framed to groups of people, for instance parents or educators who might be inclined to support AST. It attempts to understand how information presented from a "communicator" leads the "receiver" to a desired response [@reynardGrowthResilienceHow2021]. In Reynard et al., [-@reynardGrowthResilienceHow2021] framing analysis was applied to review municipal policies addressing climate change in four western Canadian cities. The authors determined that most issues are framed favoring merely a tinkering of the status quo as opposed to pushing for real change. The way these policy issues are framed is important to understand because it plays a role in either altering or preserving the existing social perceptions. In the case of AST and CIM in Canada, Riazi et al. [-@riaziCorrelatesChildrenIndependent2019] state: "it will be vital for interventions to target modifiable factors, including children's and parents' perceptions of their social environment." Parents play the important role of "gatekeeper" by either granting or restricting CIM licenses, meaning whether children can travel alone [@sharminAssociationBuiltEnvironment2017]. Framing is also important because both walking and cycling are often targeted together, whereas evidence shows that distinct interventions should target each separately [see @helbichChildrenSchoolCommuting2017], which has implications for how municipalities and schools aim to address this issue. For these reasons, the framing of active school travel should be explored and considered given its potential to influence and incentivize behaviour change.

The aim of this paper is to consider how AST, STP, and CIM are framed in the province of Ontario in Canada by varying stakeholders involved in these initiatives. Specifically, municipal governments, public health units, transportation consortium, and school boards who work together to promote active school travel. _Describe in further detail once procedure for analysis is conceptualized_

## Case Study: Ontario, Canada

In Ontario, active school travel initiatives spread across the province by the 2000s [@ontarioactiveschooltravel] and were attempted by individual schools independent of a coordinated movement. Such one-off efforts, particularly those targeting education or promotional initiatives, may only prove to provide AST in the short term [@chillonSystematicReviewInterventions2011]. At about the same time, a concept called School Travel Planning (STP) was developed in the United Kingdom [@greencommunities2007]. STP offered an opportunity for key local stakeholders such as schools, school boards, and municipalities to make tangible changes to both the social and physical environment to encourage AST among their students that can be sustained in the long term. However, it was not until 2007-2009 that Green Communities Canada (GCC), a non-profit organization, began adapting and delivering a universal STP framework. This initiative followed their publication on the _Review of International School Travel Planning Best Practices_ in 2007, which included the initial pilot in the United Kingdom, and others in New Zealand, Australia, and United States. Under GCC’s framework, a Canadian pilot intervention was trialed at twelve schools across four provinces [@buliungSchoolTravelPlanning2011a]. The results of the pilot convinced the government of the Province of Ontario to issue a grant which culminated in the development of the program _Ontario Active School Travel_ (OAST), formerly known as Active & Safe Routes to School, headed by GCC.

As of 2021, OAST continues its work by providing resources for interested stakeholders and funding projects across Ontario led by collaborative groups involving school boards, municipalities/regions, and regional transportation consortiums. The latter is a unique group of entities sanctioned by the Ontario Ministry of Education in 2006. These entities are a collaboration between regions and school boards whose objective is to deliver more efficient and effective transportation services to its area [@ministryeducation2006].

# Methods

## Procedure

## Data Analysis

# Results

# Discussion

## Limitations

## Conclusion

# Implications for School Health

Schools are an influential contributor to AST and STP efforts in Canada.

### 2021-03-25 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
First Version of PDF to Corpus

@@
 
+### Approach to collecting data
+
+There are three folders containing pdf documents from corresponding sources, consortiums, municipalities/regions, and school boards.
+Docurments are sourced from direct affiliate websites from those three groups and are printed to pdf via the web browser if deemed eligible.
+Unique criteria was used for each source type to determine eligibility of documents.
+For all sources, however, it was important that webpages were fairly easy to find as the analysis pretains to how such issues are framed to the public.'Fairly easy' means webpages that are required several steps of search or navigation to find.
+
+To start a list of all school boards in Ontario and their associated consortium and municipalitiy/region is created. This list is used as a guide and dictate the the search.
+
+School boards generally will have a single page for transportation so documents were sourced from those pages regardless in mentioned STP or AST.
+In cases were both AST and STP are mentioned both those pages are included.
+Municipalities/regions would have often time pages about transportation that involved the service it provided which is not relevent to our analysis.
+Only pages specifically dicussing active travel, AST, or STP are included.
+Page were also sourced from associated local health units which were considered part of municpalities/regions
+
+Consortiums are deicated transportation pages that primarly focus of providing the school bussing service to families.
+For this group it was determined that only relevent pages specifically relating to AST or STP would be included.
+
+**NOTE: Current version of the code converts 1 file containing pdf doccuments at a time**
+
+### Import packages
+
+```{r}
+library(tm)
+library(readr)
+library(tools)
+```
+
+### Searchable pdf files to txt conversion
+
+```{r}
+# Files must be pdf for this code to properlly detect and convert
+
+# IMPORTANT: Change the code below based on where the documents are store locally on your computer
+pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Consortium" 
+txtLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Consortium txt"
+
+# Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above 
+fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
+filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
+n <- 1
+
+for (address in filePath)
+{
+doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
+test <- doc$content
+# "file_path_sans_ext(basename())" from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
+# use of 'sep = ""' argument is important to prevent the addition of spaces, which is the default for the paste function 
+newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
+write(test, file = newFile)
+print( paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
+assign(paste("text", n, sep = ""), readChar(newFile, file.info(newFile)$size))
+n <- n+1
+}
+```
+
+### Creating data frame of texts
+
+```{r}
+# This loop creates a vector of the texts
+
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+text[i] <- eval(parse(text = paste("text", i, sep = "")))
+}
+
+# Turns vector into data frame 
+# doc_id and text are required fields for creation of a corpus, additional fields may be included in data frame ,it will however be treated as metadata by the corpus
+
+textDF <- data.frame(doc_id, text)
+```
+
+### Conversion of data frame to corpus
+
+```{r}
+df_source <- DataframeSource(textDF)
+corpus <- VCorpus(df_source)
+# Example 
+content(corpus[[1]])
+```
+
+### Corpus cleaning
+
+```{r}
+corpus <- tm_map(corpus, stripWhitespace)
+corpus <- tm_map(corpus, content_transformer(tolower))
+corpus <- tm_map(corpus, removePunctuation)
+corpus <- tm_map(corpus, removeWords, stopwords("english"))
+#corpus <- tm_map(corpus, removeNumbers)
+
+# Example
+content(corpus[[1]])
+```
+
+### Term Document Matrix & Document Term Matrix
+
+```{r}
+TDM <- TermDocumentMatrix(corpus)
+DTM <- DocumentTermMatrix(corpus)
+matrix1 <- as.matrix(TDM)
+matrix2 <- as.matrix(DTM)
+```
+
 ## Data Analysis

### 2021-04-09 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Cleaning code update and intro paragraph
Slightly updated the corpus cleaning code and added a new paragraph in the intro about CIM study in Canada

@@
 
-In the case of Canada... _review a few prominent Canadian studies on AST and CIM in more detail: Riazi et al., 2019; Mammen et al., 2012 & 2014; Rothman et al., 2021_
+In the case of Canada, Riazi found that location, specifically concentration of population, was the stronger correlate to CIM even after accounting for the influence of gender.
+However whereas European countries have a positive correlation between population density and impendence level (Masoumi, 2020), Canadian cities saw the inverse effect with more dense cities such as Ottawa and Vancouver rating much lower in CIM than Trois-Rivieres, a small city between Quebec City and Montreal.
+Riazi's team is quick to note that such differences in the Canadian context could be a results of the multicultural diversity in large Canadian cities and thus are sites of very differing social and cultural norms influence the CIM findings.
+(Missing Reference.bib citations)
+_review a few prominent Canadian studies on AST and CIM in more detail: Riazi et al., 2019; Mammen et al., 2012 & 2014; Rothman et al., 2021_
 
@@
 corpus <- tm_map(corpus, content_transformer(tolower))
+
+# Words can also be removed manually by creating a vector of strings 
+#NAwords <- c("school", "transportation", "can", "use", "active")
+#corpus <- tm_map(corpus, removeWords, NAwords)
+#corpus <- tm_map(corpus, removeNumbers)
+
 corpus <- tm_map(corpus, removePunctuation)
 corpus <- tm_map(corpus, removeWords, stopwords("english"))
-#corpus <- tm_map(corpus, removeNumbers)
 

### 2021-04-12 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Create markdown for Elsevier article

--- 2021-03-25 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
@@
 author:
-  # see ?rjournal_article for more information
-  - name: Elise Desjardins
-    affiliation: School of Earth, Environment & Society, McMaster University
+  - name: Author 1
+    email: author1@example.com
+    affiliation: Some Department
+    footnote: 1
+  - name: Author 2
+    email: author2@example.com
+    affiliation: Some Department
+  - name: Author 3
+    email: author3@example.com
+    affiliation: Another University
+    footnote: 2
+  - name: Author 4
+    email: author4@example.com
+    affiliation: Some Institute
+    footnote: 2
+  - name: Author 5
+    email: author5@example.com
+    affiliation: Some University
+  - name: Author 6
+    email: author6@example.com
+    affiliation: Some Department
 address:
-    - 1280 Main Street West, Hamilton, ON L8S 4L8
-    email: desjae@mcmaster.ca
-  - name: Jason Lam
-    email: lamj54@mcmaster.ca
-    affiliation: Affiliation 1
-    address:
-    - line 1 affiliation 1
-  - name: Owen Waygood
-    affiliation: University Polytechnique de Montreal
-    email: owen.waygood@polymtl.ca
-    address:
-    - Montreal, QC
-  - name: Antonio Paez
-    email: paezha@mcmaster.ca
-    affiliation: Affiliation 1
-    address:
-    - line 1 affiliation
-abstract: >
-  An abstract of less than 200 words.
-preamble: |
-  % Any extra LaTeX you need in the preamble
+  - code: Some Department
+    address: Department, Street, City, Province, Postal Code
+  - code: Another University
+    address: Department, Street, City, Province, Postal Code
+  - code: Some Institute
+    address: Street, City, Province, Postal Code
+  - code: Some University
+    address: Department, Street, City, Province, Postal Code
+footnote:
+  - code: 1
+    text: "Corresponding Author"
+  - code: 2
+    text: "Equal contribution"
+abstract: |
+  This is the abstract.
 
-journal: "Journal of School Health"
+  It consists of two paragraphs.
+
+journal: "Journal of Transport & Health"
 date: "`r Sys.Date()`"
-bibliography: References.bib
+bibliography: mybibfile.bib
 #linenumbers: true
 #numbersections: true
-output: rticles::rjournal_article
+csl: elsevier-harvard.csl
+output: rticles::elsevier_article
 ---
 
-# Background
+```{r, include=FALSE}
+library(tm)
+library(readr)
+library(tools)
+```
+
+1. Background
+===============
 
@@
 This trend has prompted an abundance of worlwide research over the past two decades to examine why fewer children are walking and cycling to school, what influences AST, and the associated implications for children's health.
-Many studies have been specific to Canada [*inter alia*, see: @buliungActiveSchoolTransportation2009; @faulknerSchoolTravelChildren2013; @mammenUnderstandingDriveEscort2012; @mammenSchoolTravelPlanning2014; @rothmanActiveSchoolTransportation2021; @wilsonUnderstandingChildParent2018] which aligns with and informs a growing interest in increasing active school travel levels.
+Many studies have been specific to Canada [e.g., see: @buliungActiveSchoolTransportation2009; @faulknerSchoolTravelChildren2013; @mammenUnderstandingDriveEscort2012; @mammenSchoolTravelPlanning2014; @rothmanActiveSchoolTransportation2021; @wilsonUnderstandingChildParent2018] which aligns with and informs a growing interest in increasing active school travel levels.
 Indeed, a diversity of stakeholders responsible for transportation, public health, and education are collaborating and spearheading efforts to get more children walking and cycling.
@@
 
-## Literature Review
+## 1.1. Literature Review
 
@@
 
-## Case Study: Ontario, Canada
+## 1.2. Case Study: Ontario, Canada
 
@@
 
-# Methods
+2. Methods
+===============
 
-## Procedure
-
-### Approach to collecting data
+## 2.1. Procedure
 
 There are three folders containing pdf documents from corresponding sources, consortiums, municipalities/regions, and school boards.
-Docurments are sourced from direct affiliate websites from those three groups and are printed to pdf via the web browser if deemed eligible.
+Documents are sourced from direct affiliate websites from those three groups and are printed to pdf via the web browser if deemed eligible.
 Unique criteria was used for each source type to determine eligibility of documents.
-For all sources, however, it was important that webpages were fairly easy to find as the analysis pretains to how such issues are framed to the public.'Fairly easy' means webpages that are required several steps of search or navigation to find.
+For all sources, however, it was important that web pages were fairly easy to find as the analysis pertains to how such issues are framed to the public.'Fairly easy' means web pages that are required several steps of search or navigation to find.
 
-To start a list of all school boards in Ontario and their associated consortium and municipalitiy/region is created. This list is used as a guide and dictate the the search.
+To start a list of all school boards in Ontario and their associated consortium and municipality/region is created. This list is used as a guide and dictate the the search.
 
@@
 In cases were both AST and STP are mentioned both those pages are included.
-Municipalities/regions would have often time pages about transportation that involved the service it provided which is not relevent to our analysis.
+Municipalities/regions would have often time pages about transportation that involved the service it provided which is not relevant to our analysis.
 Only pages specifically dicussing active travel, AST, or STP are included.
-Page were also sourced from associated local health units which were considered part of municpalities/regions
+Page were also sourced from associated local health units which were considered part of municipalities/regions
 
-Consortiums are deicated transportation pages that primarly focus of providing the school bussing service to families.
-For this group it was determined that only relevent pages specifically relating to AST or STP would be included.
+Consortiums are dedicated transportation pages that primarily focus of providing the school busing service to families.
+For this group it was determined that only relevant pages specifically relating to AST or STP would be included.
 
 **NOTE: Current version of the code converts 1 file containing pdf doccuments at a time**
-
-### Import packages
-
-```{r}
-library(tm)
-library(readr)
-library(tools)
-```
 
@@
 
-## Data Analysis
+## 2.2. Data Analysis
 
-# Results
+3. Results
+===============
 
-# Discussion
+4. Discussion
+===============
 
-## Limitations
+# 4.1. Implications for School Travel Planning
 
-## Conclusion
+School boards and educators are an influential contributor to AST and STP efforts in Canada.
 
-# Implications for School Health
+## 4.2. Limitations
 
-Schools are an influential contributor to AST and STP efforts in Canada.
+5. Conclusion
+===============
+
+References
+===============

### 2021-04-12 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Introduction edited and reorganized

@@
 ---
-title: What about children's wellbeing? Framing active school travel in Ontario, Canada
+title: Framing active school travel in Ontario, Canada
 author:
@@
 
-Walking and cycling to school, commonly known as active school travel or active school transportation (AST) has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020].
-This trend has prompted an abundance of worlwide research over the past two decades to examine why fewer children are walking and cycling to school, what influences AST, and the associated implications for children's health.
-Many studies have been specific to Canada [e.g., see: @buliungActiveSchoolTransportation2009; @faulknerSchoolTravelChildren2013; @mammenUnderstandingDriveEscort2012; @mammenSchoolTravelPlanning2014; @rothmanActiveSchoolTransportation2021; @wilsonUnderstandingChildParent2018] which aligns with and informs a growing interest in increasing active school travel levels.
+Walking and cycling to school, commonly known as active school travel or active school transportation (AST), has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020].
+This trend has prompted an abundance of research over the past two decades to examine why fewer children are walking and cycling to school, what influences AST, and the associated implications for children's health.
+Many studies have been specific to Canada [e.g., see: @buliungActiveSchoolTransportation2009; @faulknerSchoolTravelChildren2013; @mammenUnderstandingDriveEscort2012; @mammenSchoolTravelPlanning2014; @rothmanActiveSchoolTransportation2021; @wilsonUnderstandingChildParent2018] which aligns with and informs a growing interest in school travel planning (STP) across the country.
 Indeed, a diversity of stakeholders responsible for transportation, public health, and education are collaborating and spearheading efforts to get more children walking and cycling.
 Promoting AST is seen as an affordable, convenient, and environmentally friendly way to enhance the mental, physical, and psychological health of children [@mammenSchoolTravelPlanning2014].
-These goals should be clearly articulated and reflected in transportation plans and policies to guide initiatives, but there is research lacking that specifically explores how Canadian municipalities and schools frame and discuss AST with the public.
+Therefore, these goals ought to be clearly articulated and reflected in transportation plans and policies to guide initiatives.
+Presently, however, there is research lacking that specifically explores how Canadian municipalities and schools frame and discuss AST with the public.
 
@@
 Many patterns emerge from studies within and between countries with respect to the factors that are positively associated with AST.
-These factors broadly fall into distinct categories: individual, household, social environment, and physical environment.
+These factors broadly fall into distinct levels: individual, household, social environment, and physical environment.
 Among the most influential are age, gender, distance to school, parental perceptions of the environment [@demeesterParentalPerceivedNeighborhood2014] and children's skills [@ghekiereInsightsChildrenIndependent2017], quality of the built environment, and urban infrastructure.
@@
 Furthermore, AST is one of the most common opportunities for children to travel without adult supervision on a regular basis.
-CIM was first described by Hillman et al.
+Children's independent mobility (CIM) was first described by Hillman et al.
 [-@hillmanOneFalseMove1990] as the freedom of children to travel and play within their neighborhood and city without the presence of adults.
-Similar to AST, children's independent mobility (CIM) is much less common than it was for previous generations [@bhosaleIntergenerationalChangeChildren2017], and is influenced by related personal and environmental factors [@marziChildrenIndependentMobility2018].
+Similar to AST, children's independent mobility is much less common now than it was for previous generations [@bhosaleIntergenerationalChangeChildren2017], and is influenced by similar personal and environmental factors [@marziChildrenIndependentMobility2018].
 CIM is particularly important for different domains of children's health and wellbeing [@riaziChildrenIndependentMobility2018].
 There is also sufficient evidence in the literature linking the association between AST and CIM [@laroucheRelationshipsChildrenIndependent2020; @mitraIndependentMobilityMode2013], particularly in boys [@schoeppeAssociationsChildrenIndependent2014].
-The gender disparity has also been noted in other papers regarding CIM [@marziSocialPhysicalEnvironmental2018; @marziInterventionsAimingPromote2020] with recommendations being made for interventions to specifically target girls to boost their mobility within their neighborhood [@schoeppeSociodemographicFactorsNeighbourhood2015].
-CIM offers other benefits to adolescents such as increasing traffic and safety skills, boosting spatial awareness when navigating public spaces, and providing more opportunity for social interaction with peers [@schoeppeAssociationsChildrenIndependent2014].
+The gender disparity has been noted in other papers regarding CIM [@marziSocialPhysicalEnvironmental2018; @marziInterventionsAimingPromote2020] with recommendations being made for interventions to specifically target girls to boost their mobility within their neighborhood [@schoeppeSociodemographicFactorsNeighbourhood2015].
+CIM offers other benefits such as increasing traffic and safety skills, boosting spatial awareness when navigating public spaces, and providing more opportunity for social interaction with peers [@schoeppeAssociationsChildrenIndependent2014].
 What is less clear is how CIM plays into the consideration of policymakers when they act on the objective of improving AST.
@@
 In the case of Canada, Riazi found that location, specifically concentration of population, was the stronger correlate to CIM even after accounting for the influence of gender.
-However whereas European countries have a positive correlation between population density and impendence level (Masoumi, 2020), Canadian cities saw the inverse effect with more dense cities such as Ottawa and Vancouver rating much lower in CIM than Trois-Rivieres, a small city between Quebec City and Montreal.
-Riazi's team is quick to note that such differences in the Canadian context could be a results of the multicultural diversity in large Canadian cities and thus are sites of very differing social and cultural norms influence the CIM findings.
-(Missing Reference.bib citations)
+Whereas European countries have a positive correlation between population density and impendence level (Masoumi, 2020), Canadian cities saw the inverse effect with more dense cities such as Ottawa and Vancouver rating much lower in CIM than Trois-Rivieres, a small city in Quebec.
+Riazi et al.
+[-@riaziChildrenIndependentMobility2018] note, however, that such differences in the Canadian context could be a result of the multicultural diversity in large Canadian cities which leads to very differing social and cultural norms that may influence the findings.
 _review a few prominent Canadian studies on AST and CIM in more detail: Riazi et al., 2019; Mammen et al., 2012 & 2014; Rothman et al., 2021_
 
-The correlates and effective interventions of AST and CIM are important knowledge for policymakers because they identify points of intervention, as well as potential benefits, that ought to be communicated to the public to build support for new planning paradigms.
+The correlates of AST and CIM are important knowledge for policymakers because they identify points of intervention and potential benefits that ought to be communicated to the public to build support for new planning paradigms.
 Framing analysis is one method to analyze how particular issues are framed to groups of people, for instance parents or educators who might be inclined to support AST.
 It attempts to understand how information presented from a "communicator" leads the "receiver" to a desired response [@reynardGrowthResilienceHow2021].
-In Reynard et al., [-@reynardGrowthResilienceHow2021] framing analysis was applied to review municipal policies addressing climate change in four western Canadian cities.
-The authors determined that most issues are framed favoring merely a tinkering of the status quo as opposed to pushing for real change.
+In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review municipal policies addressing climate change in four western Canadian cities.
+The authors determined that most issues are framed favouring merely a tinkering of the status quo as opposed to pushing for real change.
 The way these policy issues are framed is important to understand because it plays a role in either altering or preserving the existing social perceptions.
@@
 Framing is also important because both walking and cycling are often targeted together, whereas evidence shows that distinct interventions should target each separately [see @helbichChildrenSchoolCommuting2017], which has implications for how municipalities and schools aim to address this issue.
-For these reasons, the framing of active school travel should be explored and considered given its potential to influence and incentivize behaviour change.
+For these reasons, the framing of active school travel should be explored and considered in the school travel literature given its potential to influence and incentivize behaviour change.
 
-The aim of this paper is to consider how AST, STP, and CIM are framed in the province of Ontario in Canada by varying stakeholders involved in these initiatives.
-Specifically, municipal governments, public health units, transportation consortium, and school boards who work together to promote active school travel.
+The aim of this paper is to consider how AST, STP, and CIM are framed in the province of Ontario, Canada.
+Using a framing analysis approach, we explore how varying stakeholders involved in these initiatives (for example, municipal governments, public health units, transportation consortium, and school boards) present the benefits, challenges, and solutions for improving active school travel.
 _Describe in further detail once procedure for analysis is conceptualized_
@@
 
-In Ontario, active school travel initiatives spread across the province by the 2000s [@ontarioactiveschooltravel] and were attempted by individual schools independent of a coordinated movement.
+In Ontario, active school travel initiatives spread across the province by the 2000s and were initially attempted by individual schools without a coordinated movement [@ontarioactiveschooltravel].
 Such one-off efforts, particularly those targeting education or promotional initiatives, may only prove to provide AST in the short term [@chillonSystematicReviewInterventions2011].
-At about the same time, a concept called School Travel Planning (STP) was developed in the United Kingdom [@greencommunities2007].
+At about the same time, a concept called school travel planning (STP) was developed in the United Kingdom [@greencommunities2007].
 STP offered an opportunity for key local stakeholders such as schools, school boards, and municipalities to make tangible changes to both the social and physical environment to encourage AST among their students that can be sustained in the long term.
-However, it was not until 2007-2009 that Green Communities Canada (GCC), a non-profit organization, began adapting and delivering a universal STP framework.
+However, it was not until 2007 that Green Communities Canada (GCC), a non-profit organization, began adapting and delivering a universal STP framework in Canada.
 This initiative followed their publication on the _Review of International School Travel Planning Best Practices_ in 2007, which included the initial pilot in the United Kingdom, and others in New Zealand, Australia, and United States.
 Under GCC’s framework, a Canadian pilot intervention was trialed at twelve schools across four provinces [@buliungSchoolTravelPlanning2011a].
-The results of the pilot convinced the government of the Province of Ontario to issue a grant which culminated in the development of the program _Ontario Active School Travel_ (OAST), formerly known as Active & Safe Routes to School, headed by GCC.
-
-As of 2021, OAST continues its work by providing resources for interested stakeholders and funding projects across Ontario led by collaborative groups involving school boards, municipalities/regions, and regional transportation consortiums.
+The results of the pilot convinced the government of the Province of Ontario to issue a grant which culminated in the development of the program _Ontario Active School Travel_ (OAST), led by GCC, to fund initiatives that promote active school travel.
+As of 2021, OAST has funded _X_ projects in Ontario.
+GCC continues its work by providing resources for interested stakeholders and funding projects across Ontario led by collaborative groups involving school boards, municipalities/regions, and regional transportation consortiums.
 The latter is a unique group of entities sanctioned by the Ontario Ministry of Education in 2006.
@@
 
-To start a list of all school boards in Ontario and their associated consortium and municipality/region is created. This list is used as a guide and dictate the the search.
+To start a list of all school boards in Ontario and their associated consortium and municipality/region is created. This list is used as a guide and dictate the search.
 
@@
 Municipalities/regions would have often time pages about transportation that involved the service it provided which is not relevant to our analysis.
-Only pages specifically dicussing active travel, AST, or STP are included.
+Only pages specifically discussing active travel, AST, or STP are included.
 Page were also sourced from associated local health units which were considered part of municipalities/regions
 
-Consortiums are dedicated transportation pages that primarily focus of providing the school busing service to families.
+Consortia are dedicated transportation pages that primarily focus of providing the school busing service to families.
 For this group it was determined that only relevant pages specifically relating to AST or STP would be included.
 
-**NOTE: Current version of the code converts 1 file containing pdf doccuments at a time**
+**NOTE: Current version of the code converts 1 file containing pdf documents at a time**
 
@@
 
+## 2.3. Reproducibility
+
+This paper is an example of open and reproducible research that uses only open software.
+All data were obtained from publicly available sources and organized in the form of a data package.
+Following best practices in spatial data science [@brunsdon2020opening], the code and data needed to reproduce or conduct a similar analysis for other regions in North America or elsewhere are available for download.
+
 3. Results

### 2021-04-14 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Updated Methodology

@@
 
-There are three folders containing pdf documents from corresponding sources, consortiums, municipalities/regions, and school boards.
-Documents are sourced from direct affiliate websites from those three groups and are printed to pdf via the web browser if deemed eligible.
-Unique criteria was used for each source type to determine eligibility of documents.
-For all sources, however, it was important that web pages were fairly easy to find as the analysis pertains to how such issues are framed to the public.'Fairly easy' means web pages that are required several steps of search or navigation to find.
+This section provides methodology for converting searchable portable document formats (PDFs) into a text corpus that can then be used in further natural language processing (NPL) analysis.
+The text corpus is a collection of structured texts which enables anaylsis for packages such as 'topicmodels' This notebook serves as an introduction on how to convert files and conduct an surface level analysis.
 
-To start a list of all school boards in Ontario and their associated consortium and municipality/region is created. This list is used as a guide and dictate the search.
+Below are the folders used and how they have been obtained.
+
+__'Academic Papers'__
+
+[Insert Methodology for obtaining Academic Papers]
+
+For these three following folders, docurments are sourced from direct affiliate websites from those three groups and are printed to pdf via the web browser if deemed eligible.
+The criteria below indicates how eligibility was determined for each grouping.
+It was important that webpages were easy to find as the analysis pretains to how such issues are framed to the public.
+Our interpretation of 'easy to find' are webpages that required no more than 2-4 seperate links from the initial browser search.
+The search was guilded based off a list of all Ontario school boards.
+Consortiums and Municipalities/Regions were organized based on the school boards.
+
+__'Consortium'__
+
+Consortiums are dedicated transportation bodies that primarly focus of providing the school bussing service to families in their associated region.
+Pages are determined to be relevent if they specifically relate to AST or STP.
+9 - Total documents
+
+__'Municipalities or Regions'__
+
+Municipalities/regions had pages about transportation that involved the service it provided which is not relevent to our analysis.
+Only pages specifically dicussing active travel, AST, or STP are included.
+Page were also sourced from associated local health units which were considered part of municpalities/regions.
+29 - Total doucments
+
+__'School Boards'__
 
@@
 In cases were both AST and STP are mentioned both those pages are included.
-Municipalities/regions would have often time pages about transportation that involved the service it provided which is not relevant to our analysis.
-Only pages specifically discussing active travel, AST, or STP are included.
-Page were also sourced from associated local health units which were considered part of municipalities/regions
-
-Consortia are dedicated transportation pages that primarily focus of providing the school busing service to families.
-For this group it was determined that only relevant pages specifically relating to AST or STP would be included.
+27 - Total doucments
 
@@
 
+The conversion process in this notebook can only be conducted on one file at a time.
+Select one of the files provided to use.
+If you want to run multiple files to create seperate corpora use 'Multiple PDF Files to Corpora.Rmd'.
+
+Searchable PDF files to .txt conversion
+
+PDFs can be brought into the corpus directly however each page of the PDF is read as an invividual document.
+For our purposes a conversion from PDF to .txt will allow us to keep all pages in a document together when loading it into the corpus.
+Make sure you have the directory pat to where your PDFs are stored.
+In addition you will need to manually create a seperate file where you wish to store your .txt files.
+Re-assign the 'pdfLocation' and 'txtLocation' to those corresponding locations.
+
 ```{r}
-# Files must be pdf for this code to properlly detect and convert
-
-# IMPORTANT: Change the code below based on where the documents are store locally on your computer
-pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Consortium" 
-txtLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Consortium txt"
+pdfLocation <- "E:/Dr. Paez Articles/with References"
+txtLocation <-  "E:/Dr. Paez Articles/txt"
 
 # Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
+
 fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
@@
 print( paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
+# Creates uniquely id text store in 'Environment'
 assign(paste("text", n, sep = ""), readChar(newFile, file.info(newFile)$size))
@@
 
+Creation of a data frame of texts is required prior to conversion to corpus.
+The data fram must contain 'doc_id' and 'text'.
+Additional fields may be included in data frame ,it will however be treated as metadata by the corpus.
+
 ```{r}
 # This loop creates a vector of the texts
-
 text <- vector()
@@
 # Turns vector into data frame 
-# doc_id and text are required fields for creation of a corpus, additional fields may be included in data frame ,it will however be treated as metadata by the corpus
-
 textDF <- data.frame(doc_id, text)
@@
 ### Corpus cleaning 
-
 ```{r}
@@
 ### Term Document Matrix & Document Term Matrix
-
 ```{r}

### 2021-04-15 AST-Framing-Ontario/Data Pre-Processesing.rmd
Create Data Pre-Processesing.rmd

---
title: "PDF to Corpus"
author: "Jason Lam"
date: "11/03/2021"
output:
  pdf_document: default
  word_document: default
---

# Introduction

This notebook provides a methodology for converting portable document formats (PDFs) into a text corpus that can be used in natural language processing (NPL) analysis. The text corpus is a collection of structured texts which enables anaylsis using packages such as `topicmodels`. This notebook serves as an introduction on how to convert files and conduct a surface level analysis.

Instructions are provided below for processing either one folder of PDF documents at a time and multiple folders simultaneously. (*Jason, you can add the content from 'Multiple PDF Files to Corpus.Rmd' to the sections below*)

# Preliminaries

Clear the environment: 
```{r}
rm(list = ls())
```

Load the following packages:
```{r}
library(tm)
library(readr)
library(tools)
library(dplyr)
library(tidytext)
library(topicmodels)
library(ggplot2)
library(wordcloud)
```

# Accessing Data: Grey Literature

Activel school travel (AST) and school travel planning (STP) initiatives typically bring together a group of stakeholders from the planning, transportation, public health, and education sectors. These stakeholders may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents.

First, we do a preliminary scan of current AST and/or STP projects funded by the Ontario Active School Travel fund to determine which stakeholders are involved in such initiatives. We find that AST projects in are often led by a school board in collaboration with transportation planners, public health professionals, and regional transportation consortia. Non-profit organizations, police services, and advocacy groups are other common stakeholders who play a role in support AST and STP.

Next, we create one folder for each of the stakeholder groups involved in AST and/or STP efforts. The folders below were used in the framing analysis; they are provided in this notebook as an example to recreate, modify, or extend our analysis.

For these three following folders, webpages were sourced directly from stakeholder websites from three main groups: transportation consortias, municipalities or regions, and school boards. These webpages were saved as PDF documents via the web browser. Inclusion of webpages was determined based on the following considerations:

1) It was important that webpages were easy to find as the analysis pretains to how such issues are framed to the public. Our interpretation of 'easy to find' are webpages that required no more than 2-4 seperate links from the initial browser search. 
2) The analysis focuses on the province of Ontario, not a single municipality or region. For this reason, the search was based off a list of all school boards across this province. The websites of each school board were searched to determine whether they discussed AST and/or STP, which . 
3) Consortia and municipalities/regions were organized based on the school boards.

__Transportation Consortia__

Transporation consortia are dedicated transportation bodies that primarly focus on providing the school busing service to families in their associated region. Pages are determined to be relevent if they specifically relate to AST or STP.

In total, 9 webpages *Jason: did they mention AST? mention STP?*
*What proportion of consortia across the province meet the criteria? E.g., 9 out of how many?*

__Municipalities or Regions__

Municipalities or regions have general webpages about transportation plans, programs, and services provided, some of which are not relevent to our analysis. Only webpages specifically dicussing active travel, AST, or STP were included. Webpages were also sourced from associated public health units which are overseen by governing bodies at the municipal or regional level.

In total, 29 webpages *Jason: did they mention AST? mention STP?*
*What proportion of municipalities/regions across the province meet the criteria? E.g., 29 out of how many?*

__School Boards__

School boards generally have a single page to discuss transportation options and services for students. Documents were sourced from those webpages regardless if they mentioned STP and/or AST.

In total, 27 webpages *Jason: did they mention AST? mention STP?*
*What proportion of municipalities/regions across the province meet the criteria? E.g., 27 out of how many?*

# Accessing Data: Research Literature

__Academic Papers__

[Insert Methodology for obtaining Academic Papers]

# Conversion Process

The conversion process in this notebook can only be conducted on one file at a time. We select one of the files provided to use in this package as an example of the process. Alternatively, you can use a file relevant to your municipality/region. To run multiple files to create seperate corpora, refer to the section below.

## Searchable PDF files to .txt conversion

PDF documents are brought into the corpus directly, however each page of the document is read as an invividual document. For our purposes, a conversion from PDF to .txt will allow us to keep all pages in a document together when loading it into the corpus. Make sure you have the directory path to where your documents are stored. Next, we manually created a seperate file to store the .txt files. Re-assign the 'pdfLocation' and 'txtLocation' to those corresponding locations.

```{r}
pdfLocation <- "E:/Dr. Paez Articles/with References"
txtLocation <-  "E:/Dr. Paez Articles/txt"

# Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above

fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
n <- 1

for (address in filePath)
{
doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
test <- doc$content
# "file_path_sans_ext(basename())" from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt 
# use of 'sep = ""' argument is important to prevent the addition of spaces, which is the default for the paste function 
newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
write(test, file = newFile)
print( paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
# Creates uniquely id text store in 'Environment'
assign(paste("text", n, sep = ""), readChar(newFile, file.info(newFile)$size))
n <- n+1
}
```

## Creating data frame of texts

Creation of a data frame of texts is required prior to conversion to corpus. The data frame must contain 'doc_id' and 'text'. Additional fields may be included in the data frame, however it will be treated as metadata by the corpus.

```{r}
# This loop creates a vector of the texts
text <- vector()
doc_id <- c(2:n-1)

for (i in seq(1, n-1, 1))
{
text[i] <- eval(parse(text = paste("text", i, sep = "")))
}

# Turns vector into data frame 
textDF <- data.frame(doc_id, text)
```

## Conversion of data frame to corpus

Next, convert the data frame to a corpus:
```{r}
df_source <- DataframeSource(textDF)
corpus <- VCorpus(df_source)
# Example 
content(corpus[[1]])
```

## Corpus cleaning

Many words should be removed while cleaning the corpus to ensure that the analysis does not pick up on common nouns, adjectives, or indefinite articles. Words can be removed manually by creating a vector of strings. Add strings to 'NAwords': 
```{r}
corpus <- tm_map(corpus, stripWhitespace)
corpus <- tm_map(corpus, content_transformer(tolower))

NAwords <- c("school", "transportation", "can", "use", "active", "et al", "travel", "j", "behav" , "nutr", "phys", "int", "n", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "s")
corpus <- tm_map(corpus, removeWords, NAwords)
corpus <- tm_map(corpus, removeNumbers)

corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeWords, stopwords("english"))

# Example
content(corpus[[1]])
```

## Term Document Matrix & Document Term Matrix

[Insert brief description of this step]

```{r}
TDM <- TermDocumentMatrix(corpus)
DTM <- DocumentTermMatrix(corpus)
matrix1 <- as.matrix(TDM)
matrix2 <- as.matrix(DTM)

```

## NLP Analysis

[Insert brief description of this step]

Latent Dirichlet Allocation (LDA) (*Jason: can you explain what this means*?)
This algorithm 
```{r}
# k represents the number of topics to be generated by the algorithm 
lda <- LDA(DTM, k = 4, control = list(seed = 1234))

topics <- tidy(lda, matrix = "beta")

# The value below determines the number of top terms
top_terms <- topics %>% 
  group_by(topic) %>% 
  top_n(15, beta) %>% 
  ungroup() %>% 
  arrange(topic, -beta)
top_terms

# Beta represents the probability of 'term' being generated in topic 'n' 
# Topics are generated by the LDA algorithm, its is up to the user to interpret the context of the topics

top_terms %>% 
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~topic, scales = "free") + 
  scale_y_reordered() +
  scale_x_continuous(limits = c(0,0.06))

```

## Tokenization by n-gram

[Insert brief description of this step]

```{r}
# Converting corpus to tidytext data type 
td_corpus <- tidy(corpus)

# n can be changed 
test_bigrams <- td_corpus %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

test_trigrams <- td_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)
# Bigrams & Trigrams that are most common

top_bigrams <- test_bigrams %>%
  count(bigram, sort = TRUE)

top_trigrams <- test_trigrams %>% 
  count(trigram, sort = TRUE)

top_bigrams
top_trigrams
```

## Using TDM to make a word cloud

[Insert brief description of this step]

```{r}
v <- sort(rowSums(matrix1), decreasing= TRUE)
d <- data.frame(word = names(v), freq=v)
set.seed(4321)
wordcloud(d$word, d$freq, min.freq = 10, max.words = 50, random.order = FALSE, rot.per = 0.5, random.color = TRUE)
```

### 2021-04-15 AST-Framing-Ontario/Data Pre-Processesing.rmd
Adding multi-file conversion functionality

@@
 
-Instructions are provided below for processing either one folder of PDF documents at a time and multiple folders simultaneously.
+Instructions are provided below for processing a single folder of PDF documents, as a walkthough of the processing techniques used.
+Another set of instructions is provided at the end of this notebook that allows for the processing multiple folders simultaneously.
 (*Jason, you can add the content from 'Multiple PDF Files to Corpus.Rmd' to the sections below*)
@@
 ```
+
+# Multi-Files
+
+Clear Environment 
+```{r}
+rm(list = ls())
+```
+
+'masterFolder' will be the location of your subfolders, containing your PDFs.
+Unlike in 'PDF to Corpus.Rmd' you do not need to create .txt folder corresponding to each PDF folder, this is done automatically by the code.
+
+IMPORTANT: The names of the folders cannot contain the consecutive characters 'txt', the code filters out those folders. 
+NOTE: The order of files below will also be the order the corpus are created, the index will match the corpus number 
+```{r}
+masterFolder <- "C:/Users/Jason/Desktop/Master PDF"
+
+subFolders <- list.files(masterFolder, full.names=TRUE)
+# if txt folder already exists from previous execution of code this ensures it is not added to subfolders 
+# The limitation is that your file name, at any point cannot contain the sequence of characters "txt" as it will be flagged as a non-pdf subfolder 
+subFolders <- subFolders[grep(x =list.files(masterFolder, full.names=TRUE), pattern =  "txt", invert = TRUE)]
+subFolders
+```
+
+This code is a is a version of the code in the 'AST-Framing-Ontario.Rmd'.
+It is compressed into a single block to allow the iterative conversion each subfolder.
+Corpus' will be cleaned for white spaces, punctuations, English stopwords, and converted to lowercases.
+Any additional stopwords will need to be removed manually as the user sees fit.
+```{r}
+# Iterating through each subfolders 
+m <- 1
+for (subFolder in subFolders){
+
+  pdfLocation <- subFolder
+  if (file.exists(paste(pdfLocation, "txt"))){
+    txtLocation <- paste(pdfLocation, "txt")
+  }else{
+    dir.create(paste(pdfLocation, "txt"))
+    txtLocation <- paste(pdfLocation, "txt")
+  }
+  fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
+  filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
+  n <- 1
+
+  for (address in filePath)
+{
+doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
+test <- doc$content
+# "file_path_sans_ext(basename())" from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
+# use of 'sep = ""' argument is important to prevent the addition of spaces, which is the default for the paste function 
+newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
+write(test, file = newFile)
+print( paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
+# Creates uniquely id text store in 'Environment'
+assign(paste("text", n, sep = ""), readChar(newFile, file.info(newFile)$size))
+n <- n+1
+  }
+
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+text[i] <- eval(parse(text = paste("text", i, sep = "")))
+}
+
+textDF <- data.frame(doc_id, text)
+
+temp_df_source <- DataframeSource(textDF)
+tempCorpus <- VCorpus(temp_df_source)
+tempCorpus <- tm_map(tempCorpus, stripWhitespace)
+tempCorpus <- tm_map(tempCorpus, content_transformer(tolower))
+tempCorpus <- tm_map(tempCorpus, removePunctuation)
+tempCorpus <- tm_map(tempCorpus, removeWords, stopwords("english"))
+
+assign(paste("corpus", m, sep= ""), tempCorpus)
+
+# removed tempory texts for next iteration
+m <- m + 1 
+rm(list=ls(pattern = "^text"))
+
+}
+rm(temp_df_source, tempCorpus, matrix1, matrix2, address, doc_id, fileBaseNames, filePath, i, m, n, newFile, pdfLocation, subFolder, test, txtLocation)
+```
+
+Uncomment and use the code below to further clean you corpuses. Insert stopwords as list of strings in 'NAwords'.  
+```{r}
+#NAwords <- c()
+#corpus <- tm_map(corpus, removeWords, NAwords)
+#corpus <- tm_map(corpus, removeNumbers)
+```
+
+Creating Term-Document Matrix and Document-Term Matrix with the fully cleaned  corpuses 
+```{r}
+# n - number of corpuses
+n <- 3
+for (i in seq(1, n, 1))
+{
+tempCorpus <-  eval(parse(text = paste("corpus", toString(i), sep = "")))
+TDM <- TermDocumentMatrix(tempCorpus)
+DTM <- DocumentTermMatrix(tempCorpus)
+matrix1 <- as.matrix(TDM)
+matrix2 <- as.matrix(DTM)
+
+assign(paste("corpus", i, "TDM", sep= ""), matrix1)
+assign(paste("corpus", i, "DTM", sep= ""), matrix2)
+
+}
+```

### 2021-04-16 AST-Framing-Ontario/Data Pre-Processesing.rmd
April 16 Update
Added Missing Documents
Added multiple seed LDA test
Add STP school master list

@@
 ---
-title: "PDF to Corpus"
+title: "Data Pre-Processing"
 author: "Jason Lam"
@@
 Transporation consortia are dedicated transportation bodies that primarly focus on providing the school busing service to families in their associated region.
-Pages are determined to be relevent if they specifically relate to AST or STP.
 
-In total, 9 webpages *Jason: did they mention AST? mention STP?*
-*What proportion of consortia across the province meet the criteria? E.g., 9 out of how many?*
+In total, 9 webpages were pulled from 7 of the 39 consortia examined in Ontario. Webpages are determined to be relevent and specifically pretain/mention AST or STP.
 
@@
 Only webpages specifically dicussing active travel, AST, or STP were included.
-Webpages were also sourced from associated public health units which are overseen by governing bodies at the municipal or regional level.
+Webpages were also sourced from associated public health units becasues their direct relation to governing bodies at the municipal or regional level.
 
-In total, 29 webpages *Jason: did they mention AST? mention STP?*
-*What proportion of municipalities/regions across the province meet the criteria? E.g., 29 out of how many?*
+In total, 29 webpages were pulled.
 
@@
 
-School boards generally have a single page to discuss transportation options and services for students. Documents were sourced from those webpages regardless if they mentioned STP and/or AST.
+These bodies use funding provided to them by the province to run a collection of schools.
+They prepare the annual budget, hire teachers and staff, supervise the education program, and other tasks ensure schools are following all regulations set by the *Education Act* [Ministry of Education].
+Only the Englished based public and Catholic school boards were considered.
 
-In total, 27 webpages *Jason: did they mention AST? mention STP?*
-*What proportion of municipalities/regions across the province meet the criteria? E.g., 27 out of how many?*
+Pages mentioning STP and/or AST were prioritized.
+However, if they did not exist, pages discussing transportation were downloaded instead.
+In total, 32 webpages were pulled from 31 of the 61 school boards examined in Ontario.
+Of the remaining the were not included, 22 linked their respective corsortia, 7 did not have pages that meet the criteria, 1 met criteria but could not be downloaded in a processable format.
 
@@
 For our purposes, a conversion from PDF to .txt will allow us to keep all pages in a document together when loading it into the corpus.
-Make sure you have the directory path to where your documents are stored.
-Next, we manually created a seperate file to store the .txt files.
-Re-assign the 'pdfLocation' and 'txtLocation' to those corresponding locations.
+Make sure you have the directory path to where your documents are stored and Re-assign the 'pdfLocation' to that corresponding location.
+R uses '/' as the directory seporator.
 
 ```{r}
-pdfLocation <- "E:/Dr. Paez Articles/with References"
-txtLocation <-  "E:/Dr. Paez Articles/txt"
+pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Consortium"
+
+# Creates folder for .txt files
+if (file.exists(paste(pdfLocation, "txt"))){
+    txtLocation <- paste(pdfLocation, "txt")
+  }else{
+    dir.create(paste(pdfLocation, "txt"))
+    txtLocation <- paste(pdfLocation, "txt")
+  }
 
 # Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
-
 fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
@@
 # k represents the number of topics to be generated by the algorithm 
-lda <- LDA(DTM, k = 4, control = list(seed = 1234))
+k <- 4
+lda <- LDA(DTM, k, control = list(seed = 1234))
 
@@
   ggplot(aes(beta, term, fill = factor(topic))) + 
+  geom_col(show.legend = FALSE) + 
+  facet_wrap(~topic, scales = "free") + 
+  scale_y_reordered() +
+  scale_x_continuous(limits = c(0,0.06))
+
+```
+
+LDA using multiple seeds
+
+This is a more robust approach since LDA has some random compenent on how it begins developing its clusters. By taking the average of multiple iterations with random seeds we
+
+```{r}
+
+# Generate a random seed to use 
+numIteration <- 10
+r <- 1 
+col <- 4 
+betaList <- c("beta.0")
+seeds <- sample.int(10000, numIteration-1)
+avgtopics <- topics
+
+for (seed1 in seeds){
+  templda <- LDA(DTM, k, control = list(seed = seed1))
+  temptopics <- tidy(templda, matrix = "beta")
+  avgtopics <- left_join(avgtopics, temptopics , by = c("topic", "term"))
+  colnames(avgtopics)[col] <- paste("beta.", r, sep = "")
+  betaList <- append(betaList, paste("beta.", r, sep = ""))
+  r <- r + 1
+  col <- col + 1 
+}
+colnames(avgtopics)[3] <- "beta.0"
+
+avgtopics$beta.mean <- rowMeans(avgtopics[betaList])
+
+# The value below determines the number of top terms
+avg_top_terms <- avgtopics %>% 
+  group_by(topic) %>% 
+  top_n(15, beta.mean) %>% 
+  ungroup() %>% 
+  arrange(topic, -beta.mean)
+avg_top_terms
+
+# Beta represents the probability of 'term' being generated in topic 'n' 
+# Topics are generated by the LDA algorithm, its is up to the user to interpret the context of the topics
+
+avg_top_terms %>% 
+  mutate(term = reorder_within(term, beta.mean, topic)) %>%
+  ggplot(aes(beta.mean, term, fill = factor(topic))) + 
   geom_col(show.legend = FALSE) + 

### 2021-04-21 AST-Framing-Ontario/Data Pre-Processesing.rmd
April 21 Updates

@@
 Another set of instructions is provided at the end of this notebook that allows for the processing multiple folders simultaneously.
-(*Jason, you can add the content from 'Multiple PDF Files to Corpus.Rmd' to the sections below*)
 
@@
 ```{r}
-pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Consortium"
+pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Municipalities or Regions"
 
@@
 
-NAwords <- c("school", "transportation", "can", "use", "active", "et al", "travel", "j", "behav" , "nutr", "phys", "int", "n", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "s")
+NAwords <- c("school", "transportation", "can", "use", "active", "et al", "travel", "j", "behav" , "nutr", "phys", "int", "n", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "s", "the")
 corpus <- tm_map(corpus, removeWords, NAwords)
@@
 
-## NLP Analysis
+## Natural Languange Processing (NLP) Analysis
 
-[Insert brief description of this step]
+NLP is a way to correlate words across a collection of texts or corpus.
 
-Latent Dirichlet Allocation (LDA) (*Jason: can you explain what this means*?)
-This algorithm 
+Topic Modelling with Latent Dirichlet Allocation (LDA)
+
+The goal of topic modelling is to identify the re-occurring themes in our corpus quantitatively with code.
+The code below utilizes LDA, an algorithm that when provided a number of desrete topics, 'k', will calculate the likelyhood of any given term being generated in a given topic.
+This algorithm runs under the 'bag of words' assumptions with means grammatic structre (adjective, noun, verb) is not considered.
+Words are rather considered
 ```{r}
 # k represents the number of topics to be generated by the algorithm 
-k <- 4
+k <- 5
 lda <- LDA(DTM, k, control = list(seed = 1234))
@@
 # Topics are generated by the LDA algorithm, its is up to the user to interpret the context of the topics 
-
+terms(lda,15)
 top_terms %>% 
@@
 ```
-
 LDA using multiple seeds
@@
 
-[Insert brief description of this step]
+Here we examine texts based on the structural relationship of a sequence of words.
+We can tokenize n-grams, where 'n' represents the number of consecutive words, to chart what group of words most frequently occur in our corpus.
 
@@
 
-[Insert brief description of this step]
+Word cloud is a nice visual way to view the most common words in your text document matrix
 
@@
 This code is a is a version of the code in the 'AST-Framing-Ontario.Rmd'.
-It is compressed into a single block to allow the iterative conversion each subfolder.
-Corpus' will be cleaned for white spaces, punctuations, English stopwords, and converted to lowercases.
+It is condensed into a single block to allow the iterative conversion each subfolder.
+Corpora will be cleaned for white spaces, punctuations, English stopwords, and converted to lowercases.
 Any additional stopwords will need to be removed manually as the user sees fit.
@@
 ```{r}
-# n - number of corpuses
+# n - number of corpora
 n <- 3

### 2021-04-27 AST-Framing-Ontario/Data Pre-Processesing.rmd
April 26th Changes

@@
 library(wordcloud)
+library(word2vec)
 ```
@@
 
-Municipalities or regions have general webpages about transportation plans, programs, and services provided, some of which are not relevent to our analysis.
+Municipalities or regions have webpages about transportation plans, programs, and services provided, some of which are not relevent to our analysis.
 Only webpages specifically dicussing active travel, AST, or STP were included.
@@
 
+Location:
+
+"E:/Github/AST-Framing-Analysis-Ontario/Texts/Academic Papers"
+"E:/Github/AST-Framing-Analysis-Ontario/Texts/Consortia"
+"E:/Github/AST-Framing-Analysis-Ontario/Texts/Municipalities or Regions"
+"E:/Github/AST-Framing-Analysis-Ontario/Texts/School Boards"
+
 ```{r}
-pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Municipalities or Regions"
+pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Texts/School Boards"
 
@@
 
-NAwords <- c("school", "transportation", "can", "use", "active", "et al", "travel", "j", "behav" , "nutr", "phys", "int", "n", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "s", "the")
+NAwords <- c("contact", "cancellations", "catholic", "waterloo", "board", "east", "transportation", "students", "student", "website", "tri", "can", "district", "will", "please", "may", "school", "https")
 corpus <- tm_map(corpus, removeWords, NAwords)
@@
 # Example
-content(corpus[[1]])
+content(corpus[[5]])
 ```
@@
 # k represents the number of topics to be generated by the algorithm 
-k <- 5
+k <- 4
 lda <- LDA(DTM, k, control = list(seed = 1234))
@@
 ```
+# Word to Vector Test
+https://m-clark.github.io/text-analysis-with-R/word-embeddings.html 
+```{r}
+library(text2vec)
+
+# Need to create new data frame with the cleaned corpus 
+cleanTextDF <- data.frame(text = sapply(corpus, as.character), stringsAsFactors = FALSE)
+
+it_train = itoken(cleanTextDF$text, progressbar = FALSE)
+vocab = create_vocabulary(it_train)
+
+# Cuts out terms that have a minimum count of 5 
+vocab <- prune_vocabulary(vocab, term_count_min = 5)
+vocab
+
+vectorizer <- vocab_vectorizer(vocab)
+tcm <- create_tcm(it_train, vectorizer, skip_grams_window = 10)
+
+glove = GlobalVectors$new(rank = 50, x_max = 10)
+main = glove$fit_transform(tcm, n_iter = 10, convergence_tol = 0.001)
+context = glove$components
+
+word_vectors = main + t(context)
+
+safe = word_vectors["mental", , drop = FALSE]
+
+cos_sim = sim2(x = word_vectors, y = safe, method = "cosine")
+
+head(sort(cos_sim[,1], decreasing = TRUE), 10)
+
+```
 
@@
 
-This code is a is a version of the code in the 'AST-Framing-Ontario.Rmd'.
-It is condensed into a single block to allow the iterative conversion each subfolder.
-Corpora will be cleaned for white spaces, punctuations, English stopwords, and converted to lowercases.
-Any additional stopwords will need to be removed manually as the user sees fit.
+Corpora will be cleaned for white spaces, punctuations, English stopwords, and converted to lowercases. Any additional stopwords will need to be removed manually as the user sees fit. 
 ```{r}
@@
 
-Creating Term-Document Matrix and Document-Term Matrix with the fully cleaned  corpuses 
+Creating Term-Document Matrix and Document-Term Matrix with the fully cleaned corpora.
 ```{r}
@@
 ```
+
+# Vector Sort
+
+```{r}
+sort(NAwords)
+```

### 2021-04-28 AST-Framing-Ontario/Data Pre-Processesing.rmd
Updated pre-processing instructions

@@
 This notebook provides a methodology for converting portable document formats (PDFs) into a text corpus that can be used in natural language processing (NPL) analysis.
-The text corpus is a collection of structured texts which enables anaylsis using packages such as `topicmodels`.
+The text corpus is a collection of structured texts which enables analysis using packages such as `topicmodels`.
 This notebook serves as an introduction on how to convert files and conduct a surface level analysis.
 
-Instructions are provided below for processing a single folder of PDF documents, as a walkthough of the processing techniques used.
-Another set of instructions is provided at the end of this notebook that allows for the processing multiple folders simultaneously.
+Instructions are provided below for processing a single folder of PDF documents, as a step-by-step guide of the processing techniques used.
+Another set of instructions is provided at the end of this notebook for the processing multiple folders simultaneously.
 
@@
 library(word2vec)
+library(pdftools)
+library(reshape2)
 ```
+
+*Parametrize the document to run different corpus*
 
@@
 
-Activel school travel (AST) and school travel planning (STP) initiatives typically bring together a group of stakeholders from the planning, transportation, public health, and education sectors.
+Active school travel (AST) and school travel planning (STP) initiatives typically bring together a group of stakeholders from the planning, transportation, public health, and education sectors.
 These stakeholders may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents.
@@
 First, we do a preliminary scan of current AST and/or STP projects funded by the Ontario Active School Travel fund to determine which stakeholders are involved in such initiatives.
-We find that AST projects in are often led by a school board in collaboration with transportation planners, public health professionals, and regional transportation consortia.
+We find that AST projects are often led by a school board in collaboration with transportation planners, public health professionals, and regional transportation consortia.
 Non-profit organizations, police services, and advocacy groups are other common stakeholders who play a role in support AST and STP.
 
-Next, we create one folder for each of the stakeholder groups involved in AST and/or STP efforts.
+Next, we create one folder for each stakeholder group involved in AST and/or STP efforts.
 The folders below were used in the framing analysis; they are provided in this notebook as an example to recreate, modify, or extend our analysis.
 
-For these three following folders, webpages were sourced directly from stakeholder websites from three main groups: transportation consortias, municipalities or regions, and school boards.
+For these three following folders, webpages were sourced directly from stakeholder websites from three main groups: transportation consortia, municipalities or regions, and school boards.
 These webpages were saved as PDF documents via the web browser.
+
 Inclusion of webpages was determined based on the following considerations:
-
-1) It was important that webpages were easy to find as the analysis pretains to how such issues are framed to the public.
-Our interpretation of 'easy to find' are webpages that required no more than 2-4 seperate links from the initial browser search.
+1) It was important that webpages were easy to find as the analysis pertains to how such issues are framed to the public.
+Our interpretation of 'easy to find' are webpages that required no more than 2-4 separate links from the initial browser search.
 2) The analysis focuses on the province of Ontario, not a single municipality or region.
-For this reason, the search was based off a list of all school boards across this province.
-The websites of each school board were searched to determine whether they discussed AST and/or STP, which .
-3) Consortia and municipalities/regions were organized based on the school boards.
+For this reason, the search was guided by a list of all school boards across the province.
+The websites of each school board were manually searched to determine whether they discussed AST and/or STP.
+3) Consortia and municipalities/regions were organized based on geographic area (i.e., proximity to the school boards).
 
@@
 
-Transporation consortia are dedicated transportation bodies that primarly focus on providing the school busing service to families in their associated region.
+Transportation consortia are dedicated transportation bodies that primarily focus on providing the school busing service to families in their associated region.
 
-In total, 9 webpages were pulled from 7 of the 39 consortia examined in Ontario. Webpages are determined to be relevent and specifically pretain/mention AST or STP.
+In total, 9 webpages were pulled from 7 of the 39 consortia examined in Ontario. Webpages are determined to be relevant if they specifically pertain and/or mention AST or STP.
 
@@
 
-Municipalities or regions have webpages about transportation plans, programs, and services provided, some of which are not relevent to our analysis.
-Only webpages specifically dicussing active travel, AST, or STP were included.
-Webpages were also sourced from associated public health units becasues their direct relation to governing bodies at the municipal or regional level.
+Municipalities or regions have webpages about transportation plans, programs, and services provided, some of which are not relevant to our analysis.
+Only webpages specifically discussing active travel, AST, or STP were included.
+Webpages were also sourced from associated public health units because they have a direct relation to governing bodies at the municipal or regional level.
 
@@
 These bodies use funding provided to them by the province to run a collection of schools.
-They prepare the annual budget, hire teachers and staff, supervise the education program, and other tasks ensure schools are following all regulations set by the *Education Act* [Ministry of Education].
-Only the Englished based public and Catholic school boards were considered.
+They prepare the annual budget, hire teachers and staff, supervise the education program, and other tasks to ensure schools are following all regulations set by the Province of Ontario's *Education Act*.
+Only English speaking public and Catholic school boards were considered.
 
@@
 In total, 32 webpages were pulled from 31 of the 61 school boards examined in Ontario.
-Of the remaining the were not included, 22 linked their respective corsortia, 7 did not have pages that meet the criteria, 1 met criteria but could not be downloaded in a processable format.
+Of the remaining the were not included, 22 linked their respective transportation consortia, 7 did not have pages that meet the criteria, 1 met the criteria but could not be downloaded in a PDF format.
 
@@
 
-[Insert Methodology for obtaining Academic Papers]
+A literature search was conducted in _Web of Science_ using "active", "travel", "school" as keywords, and then further narrowed down by discipline "geography", "transportation, "planning".
+
+In total, _X_ articles were accessed.
 
@@
 
-The conversion process in this notebook can only be conducted on one file at a time.
+The conversion process for this section can only be conducted on one file at a time.
 We select one of the files provided to use in this package as an example of the process.
 Alternatively, you can use a file relevant to your municipality/region.
-To run multiple files to create seperate corpora, refer to the section below.
+To run multiple files or to create separate corpora, refer to the section below.
 
@@
 
-PDF documents are brought into the corpus directly, however each page of the document is read as an invividual document.
+PDF documents are brought into the corpus directly, however each page of the document is read as an individual document.
 For our purposes, a conversion from PDF to .txt will allow us to keep all pages in a document together when loading it into the corpus.
-Make sure you have the directory path to where your documents are stored and Re-assign the 'pdfLocation' to that corresponding location.
-R uses '/' as the directory seporator.
-
-Location:
-
-"E:/Github/AST-Framing-Analysis-Ontario/Texts/Academic Papers"
-"E:/Github/AST-Framing-Analysis-Ontario/Texts/Consortia"
-"E:/Github/AST-Framing-Analysis-Ontario/Texts/Municipalities or Regions"
-"E:/Github/AST-Framing-Analysis-Ontario/Texts/School Boards"
+Make sure you have the directory path to where your documents are stored and re-assign the `pdfLocation` to that corresponding location.
+R uses '/' as the directory separator.
 
 ```{r}
-pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Texts/School Boards"
+pdfLocation <- "Texts/School Boards"
 
@@
 test <- doc$content
-# "file_path_sans_ext(basename())" from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
-# use of 'sep = ""' argument is important to prevent the addition of spaces, which is the default for the paste function 
+
+# `file_path_sans_ext(basename())` from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
+
+# use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
 newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
@@
 print( paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
+
 # Creates uniquely id text store in 'Environment'
@@
 
-NAwords <- c("contact", "cancellations", "catholic", "waterloo", "board", "east", "transportation", "students", "student", "website", "tri", "can", "district", "will", "please", "may", "school", "https")
+NAwords <- c("contact", "cancellations", "catholic", "waterloo", "board", "east", "transportation", "students", "student", "website", "tri", "can", "district", "will", "please", "may", "school", "https", "school", "schools", "walking", "cycling", "gta", "login", "and", "or", "the", "active", "asst", "stp")
 corpus <- tm_map(corpus, removeWords, NAwords)
@@
 # Example
-content(corpus[[5]])
+content(corpus[[1]])
 ```
@@
 
-Topic Modelling with Latent Dirichlet Allocation (LDA)
+### Topic Modelling with Latent Dirichlet Allocation (LDA)
 
 The goal of topic modelling is to identify the re-occurring themes in our corpus quantitatively with code.
-The code below utilizes LDA, an algorithm that when provided a number of desrete topics, 'k', will calculate the likelyhood of any given term being generated in a given topic.
-This algorithm runs under the 'bag of words' assumptions with means grammatic structre (adjective, noun, verb) is not considered.
-Words are rather considered
+The code below utilizes LDA, an algorithm that when provided a number of discrete topics, `k`, will calculate the likelihood of any given term being generated in a given topic.
+This algorithm runs under the 'bag of words' assumptions with means grammatical structure is not considered.
+Only words are rather considered.
+
 ```{r}
@@
 ```
-LDA using multiple seeds
 
-This is a more robust approach since LDA has some random compenent on how it begins developing its clusters. By taking the average of multiple iterations with random seeds we
+### LDA using multiple seeds
+
+This is a more robust approach since LDA has some random components on how it begins developing its clusters.
+By taking the average of multiple iterations with random seeds, we ....
+[_finish sentence_]
 
@@
 # Beta represents the probability of 'term' being generated in topic 'n' 
-# Topics are generated by the LDA algorithm, its is up to the user to interpret the context of the topics
+# Topics are generated by the LDA algorithm, it's up to the user to interpret the context of the topics
 
@@
 Here we examine texts based on the structural relationship of a sequence of words.
-We can tokenize n-grams, where 'n' represents the number of consecutive words, to chart what group of words most frequently occur in our corpus.
+We can "tokenize" n-grams, where `n` represents the number of consecutive words, to chart what group of words most frequently occur in our corpus.
 
@@
 ```
+
 # Word to Vector Test
+
 https://m-clark.github.io/text-analysis-with-R/word-embeddings.html
+
 ```{r}
@@
 
-# Need to create new data frame with the cleaned corpus 
+# Create new data frame with the cleaned corpus 
 cleanTextDF <- data.frame(text = sapply(corpus, as.character), stringsAsFactors = FALSE)
@@
 
-# Cuts out terms that have a minimum count of 5 
+# Cut out terms that have a minimum count of 5 
 vocab <- prune_vocabulary(vocab, term_count_min = 5)
@@
 
-safe = word_vectors["mental", , drop = FALSE]
+safe = word_vectors["wellbeing", , drop = FALSE] - word_vectors["physical", , drop = FALSE] + word_vectors["mental", , drop = FALSE]
 
@@
 head(sort(cos_sim[,1], decreasing = TRUE), 10)
-
 ```
@@
 
-'masterFolder' will be the location of your subfolders, containing your PDFs.
+`masterFolder` will be the location of your sub-folders, containing your PDFs.
 Unlike in 'PDF to Corpus.Rmd' you do not need to create .txt folder corresponding to each PDF folder, this is done automatically by the code.
 
-IMPORTANT: The names of the folders cannot contain the consecutive characters 'txt', the code filters out those folders. 
+IMPORTANT: The names of the folders cannot contain the consecutive characters `txt`, the code filters out those folders. 
 NOTE: The order of files below will also be the order the corpus are created, the index will match the corpus number 
 ```{r}
-masterFolder <- "C:/Users/Jason/Desktop/Master PDF"
+masterFolder <- "Texts"
 
@@
 # The limitation is that your file name, at any point cannot contain the sequence of characters "txt" as it will be flagged as a non-pdf subfolder
+
 subFolders <- subFolders[grep(x =list.files(masterFolder, full.names=TRUE), pattern =  "txt", invert = TRUE)]
@@
 
-Corpora will be cleaned for white spaces, punctuations, English stopwords, and converted to lowercases. Any additional stopwords will need to be removed manually as the user sees fit. 
+Corpora will be cleaned for white spaces, punctuation, English stop words, and converted to lowercase. Any additional stop words will need to be removed manually as the user sees fit. 
 ```{r}

### 2021-05-04 AST-Framing-Ontario/Data Pre-Processesing.rmd
May 4th update

@@
 library(wordcloud)
-library(word2vec)
+#library(word2vec)
 library(pdftools)
 library(reshape2)
+library(text2vec)
 ```
@@
 *Parametrize the document to run different corpus* 
+[We could parametrize specific stop words base on the specific files]
 
@@
 
-In total, _X_ articles were accessed.
+In total, 233 articles were included from a list of 253. Reasons of exclusions for remaining 20 include unavailablity online, access only on print, and published in non-english.
 
@@
 ```{r}
-pdfLocation <- "Texts/School Boards"
+pdfLocation <- "Texts/Academic Papers NoRef"
 
@@
 
-NAwords <- c("contact", "cancellations", "catholic", "waterloo", "board", "east", "transportation", "students", "student", "website", "tri", "can", "district", "will", "please", "may", "school", "https", "school", "schools", "walking", "cycling", "gta", "login", "and", "or", "the", "active", "asst", "stp")
+NAwords <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "use", "n", "s", "schools", "also", "p", "b", "used", "number")
 corpus <- tm_map(corpus, removeWords, NAwords)
@@
 
+NOTE: RUNNING THE BLOCK BELOW WITH 'Academic Articles'AS INPUT WILL RESULT IN VERY LONG PROCESSING TIME
+
 ```{r}
-
-# Generate a random seed to use 
-numIteration <- 10
-r <- 1 
-col <- 4 
-betaList <- c("beta.0")
-seeds <- sample.int(10000, numIteration-1)
-avgtopics <- topics
-
-for (seed1 in seeds){
-  templda <- LDA(DTM, k, control = list(seed = seed1))
-  temptopics <- tidy(templda, matrix = "beta")
-  avgtopics <- left_join(avgtopics, temptopics , by = c("topic", "term"))
-  colnames(avgtopics)[col] <- paste("beta.", r, sep = "")
-  betaList <- append(betaList, paste("beta.", r, sep = ""))
-  r <- r + 1
-  col <- col + 1 
-}
-colnames(avgtopics)[3] <- "beta.0"
-
-avgtopics$beta.mean <- rowMeans(avgtopics[betaList])
-
-# The value below determines the number of top terms
-avg_top_terms <- avgtopics %>% 
-  group_by(topic) %>% 
-  top_n(15, beta.mean) %>% 
-  ungroup() %>% 
-  arrange(topic, -beta.mean)
-avg_top_terms
-
-# Beta represents the probability of 'term' being generated in topic 'n' 
-# Topics are generated by the LDA algorithm, it's up to the user to interpret the context of the topics
-
-avg_top_terms %>% 
-  mutate(term = reorder_within(term, beta.mean, topic)) %>%
-  ggplot(aes(beta.mean, term, fill = factor(topic))) + 
-  geom_col(show.legend = FALSE) + 
-  facet_wrap(~topic, scales = "free") + 
-  scale_y_reordered() +
-  scale_x_continuous(limits = c(0,0.06))
+# 
+# # Generate a random seed to use 
+# numIteration <- 10
+# r <- 1 
+# col <- 4 
+# betaList <- c("beta.0")
+# seeds <- sample.int(10000, numIteration-1)
+# avgtopics <- topics
+# 
+# for (seed1 in seeds){
+#   templda <- LDA(DTM, k, control = list(seed = seed1))
+#   temptopics <- tidy(templda, matrix = "beta")
+#   avgtopics <- left_join(avgtopics, temptopics , by = c("topic", "term"))
+#   colnames(avgtopics)[col] <- paste("beta.", r, sep = "")
+#   betaList <- append(betaList, paste("beta.", r, sep = ""))
+#   r <- r + 1
+#   col <- col + 1 
+# }
+# colnames(avgtopics)[3] <- "beta.0"
+# 
+# avgtopics$beta.mean <- rowMeans(avgtopics[betaList])
+# 
+# # The value below determines the number of top terms
+# avg_top_terms <- avgtopics %>% 
+#   group_by(topic) %>% 
+#   top_n(15, beta.mean) %>% 
+#   ungroup() %>% 
+#   arrange(topic, -beta.mean)
+# avg_top_terms
+# 
+# # Beta represents the probability of 'term' being generated in topic 'n' 
+# # Topics are generated by the LDA algorithm, it's up to the user to interpret the context of the topics 
+# 
+# avg_top_terms %>% 
+#   mutate(term = reorder_within(term, beta.mean, topic)) %>%
+#   ggplot(aes(beta.mean, term, fill = factor(topic))) + 
+#   geom_col(show.legend = FALSE) + 
+#   facet_wrap(~topic, scales = "free") + 
+#   scale_y_reordered() +
+#   scale_x_continuous(limits = c(0,0.06))
 
@@
 
-# Word to Vector Test
+# GloVe Word Embeddings
 
@@
 ```{r}
-library(text2vec)
-
 # Create new data frame with the cleaned corpus 
@@
 
-Corpora will be cleaned for white spaces, punctuation, English stop words, and converted to lowercase. Any additional stop words will need to be removed manually as the user sees fit. 
+Corpora will be cleaned for white spaces, punctuation, English stop words, and converted to lowercase.
+Any additional stop words will need to be removed manually as the user sees fit.
+'corpusKey' is a data frame that indicates which file a corpus was derived from.
 ```{r}
+# Stop words for each of the corpora, or based on how your directory organizes files 
+# Add stop words if you have more than 4 corpora 
+NAwords2 <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "tip", "london", "provides", "elgin", "find", "make", "active", "travel", "lord", "holy", "toronto", "-")
+NAwords3 <- c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get")
+NAwords4 <- c("active", "and", "asst", "board", "can", "cancellations", "catholic", "contact", "cycling", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "walking", "waterloo", "website", "will")
+NAwords1 <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "use", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "intrument", "may")
+
+corpusNum <- c()
+
 # Iterating through each subfolders 
@@
 test <- doc$content
+
 # "file_path_sans_ext(basename())" from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
@@
 write(test, file = newFile)
-print( paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
+
+####print(paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
+
 # Creates uniquely id text store in 'Environment'
@@
 tempCorpus <- VCorpus(temp_df_source)
+
+# corpus cleaning 
 tempCorpus <- tm_map(tempCorpus, stripWhitespace)
@@
 tempCorpus <- tm_map(tempCorpus, removeWords, stopwords("english"))
+tempCorpus <- tm_map(tempCorpus, removeWords, eval(parse(text = paste("NAwords", m, sep = ""))))
+tempCorpus <- tm_map(tempCorpus, removeNumbers)
+
+assign(paste("cleanTextDF", m, sep = ""), data.frame(text = sapply(tempCorpus, as.character), stringsAsFactors = FALSE))
 
 assign(paste("corpus", m, sep= ""), tempCorpus)
+
+corpusNum <- c(corpusNum, paste(m))
 
@@
 }
-rm(temp_df_source, tempCorpus, matrix1, matrix2, address, doc_id, fileBaseNames, filePath, i, m, n, newFile, pdfLocation, subFolder, test, txtLocation)
-```
 
-Uncomment and use the code below to further clean you corpuses. Insert stopwords as list of strings in 'NAwords'.  
-```{r}
-#NAwords <- c()
-#corpus <- tm_map(corpus, removeWords, NAwords)
-#corpus <- tm_map(corpus, removeNumbers)
+corpusKey <- data.frame(corpusNum, subFolders)
+
+rm(temp_df_source, tempCorpus, address, doc_id, fileBaseNames, filePath, i, m, n, newFile, pdfLocation, subFolder, test, txtLocation)
 ```
@@
 # n - number of corpora
-n <- 3
+n <- 4
 for (i in seq(1, n, 1))
 {
-tempCorpus <-  eval(parse(text = paste("corpus", toString(i), sep = "")))
+tempCorpus <-  eval(parse(text = paste("corpus", i, sep = "")))
 TDM <- TermDocumentMatrix(tempCorpus)
@@
 }
+rm(matrix1, matrix2)
+```
+
+# Vocabulary
+
+```{r}
+# n - number of corpora
+n <- 4
+
+for (i in seq(1, n, 1))
+{
+  tempDF <- eval(parse(text = paste("cleanTextDF", i, sep = "")))
+  it_train = itoken(tempDF$text, progressbar = FALSE)
+  assign(paste("vocab", i, sep= ""), create_vocabulary(it_train))
+  tempVocab <- create_vocabulary(it_train)
+  assign(paste("vocab", i, sep= ""), prune_vocabulary(tempVocab, term_count_min = 5))
+}
+
+rm(tempVocab)
 ```
@@
 ```{r}
-sort(NAwords)
+#eval(parse(text = paste("NAwords", 1, sep = "")))
+NAwords1
+
 ```

### 2021-05-04 AST-Framing-Ontario/Data Pre-Processesing.rmd
Stop Words Update
Updated stops words text file

@@
 library(wordcloud)
-#library(word2vec)
+library(word2vec)
 library(pdftools)
@@
 # Add stop words if you have more than 4 corpora
-NAwords2 <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "tip", "london", "provides", "elgin", "find", "make", "active", "travel", "lord", "holy", "toronto", "-")
-NAwords3 <- c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get")
-NAwords4 <- c("active", "and", "asst", "board", "can", "cancellations", "catholic", "contact", "cycling", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "walking", "waterloo", "website", "will")
-NAwords1 <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "use", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "intrument", "may")
+
+NAwords1 <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
+
+NAwords2 <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
+
+NAwords3 <- c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
+
+NAwords4 <- c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")
 
@@
 ```{r}
-#eval(parse(text = paste("NAwords", 1, sep = "")))
-NAwords1
+
+paste(sort(NAwords4), collapse = " ")
 

### 2021-05-05 AST-Framing-Ontario/Data Pre-Processesing.rmd
CorpusKey before stopwords

@@
 
+'n' represents the number of subfolders and subsequently corpora that you intent the produce. 'corpusKey' will indicate the numbering convention of the corpora and analysis in subsequent code. 
+```{r}
+# n - number of corpora
+n <- 4
+corpusNum <- seq(1, n, 1)
+corpusKey <- data.frame(corpusNum, subFolders)
+```
+
 Corpora will be cleaned for white spaces, punctuation, English stop words, and converted to lowercase.
@@
 
-corpusNum <- c(corpusNum, paste(m))
-
 # removed tempory texts for next iteration
@@
 ```{r}
-# n - number of corpora
-n <- 4
 for (i in seq(1, n, 1))
@@
 ```{r}
-# n - number of corpora
-n <- 4
-
 for (i in seq(1, n, 1))

### 2021-05-14 AST-Framing-Ontario/Data Pre-Processesing.rmd
Changes From Past Week
- Parameters at the top
- Function for ligature replacement
- Double column function
- Other code clean up and bug fixes

@@
 output:
+  html_document:
+    df_print: paged
   pdf_document: default
   word_document: default
+params:
+  Academic_Papers: "Texts/Academic Papers NoRef"
+  Academic_Papers_DoubCol: "Texts/Academic Papers NoRef DoubleCol"
+  Consortia: "Texts/Consortia"
+  Municipalities_Regions: "Texts/Municipalities or Regions"
+  School Boards: "Texts/School Boards"
+  AP_stopW: c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
+  AP_DoubCol_stopW: c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
+  Con_stopW: c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
+  Mun_Reg_stopW: c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
+  SB_stopW: c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")
+
 ---
@@
 ```{r}
+library(dplyr)
+library(ggraph)
+library(ggplot2)
+library(igraph)
+library(pdftools)
+library(readr)
+library(reshape2)
+library(stringr)
+library(text2vec)
+library(tidyr)
+library(tidytext)
 library(tm) 
-library(readr)
 library(tools)
-library(dplyr)
-library(tidytext)
 library(topicmodels)
-library(ggplot2)
+library(word2vec)
 library(wordcloud)
-library(word2vec)
-library(pdftools)
-library(reshape2)
-library(text2vec)
 ```
@@
 
+## Function to clean text of Ligatures
+
+The function below allows you to find and replace certain strings.
+The main use in this context is to replace encoding errors where specific sequences of character such as "fi" or "fl" are encoded as ligatures in the pdf.
+During the conversion process those character can be lost and their subsequent words are misintrupted.
+
+https://stackoverflow.com/questions/17517319/r-replacing-foreign-characters-in-a-string 
+```{r}
+to.plain <- function(s) {
+
+   # 1 character substitutions
+   old1 <- "šžþàáâãäåçèéêëìíîïðñòóôõöùúûüý"
+   new1 <- "szyaaaaaaceeeeiiiidnooooouuuuy"
+   s1 <- chartr(old1, new1, s)
+
+   # 2 character substitutions
+   old2 <- c("<U+FB03>", "<U+FB01>", "<U+FB00>", "<U+FB02>")
+   new2 <- c("ffi", "fi", "ff", "fl")
+   s2 <- s1
+   for(i in seq_along(old2)) s2 <- gsub(old2[i], new2[i], s2, fixed = TRUE)
+
+   s2
+}
+```
+
 ## Searchable PDF files to .txt conversion
@@
 ```{r}
-pdfLocation <- "Texts/Academic Papers NoRef"
+pdfLocation <- params$Academic_Papers
 
@@
 newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
+print( paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
+
 write(test, file = newFile)
-print( paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
 
@@
 assign(paste("text", n, sep = ""), readChar(newFile, file.info(newFile)$size))
+
 n <- n+1
@@
 {
-text[i] <- eval(parse(text = paste("text", i, sep = "")))
+  #
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
 }
@@
 textDF <- data.frame(doc_id, text)
+
 ```
@@
 # Example 
-content(corpus[[1]])
+content(corpus[[2]])
 ```
@@
 
-NAwords <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "use", "n", "s", "schools", "also", "p", "b", "used", "number")
+NAwords <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
 corpus <- tm_map(corpus, removeWords, NAwords)
@@
 # Example
-content(corpus[[1]])
+content(corpus[[2]])
 ```
@@
 
+Bi-gram visualizations 
+```{r}
+bigrams_separated <- test_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+bigram_counts <- bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurence
+# Error will occur if n is outide the range of occurences 
+bigram_graph <- bigram_counts %>%
+  filter(n > 5) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+ggraph(bigram_graph, layout = "fr") +
+  geom_edge_link() +
+  geom_node_point() +
+  geom_node_text(aes(label = name), vjust = 1, hjust = 1)
+
+```
+
 ## Using TDM to make a word cloud
@@
 
-safe = word_vectors["wellbeing", , drop = FALSE] - word_vectors["physical", , drop = FALSE] + word_vectors["mental", , drop = FALSE]
+#safe = word_vectors["wellbeing", , drop = FALSE] - word_vectors["physical", , drop = FALSE] + word_vectors["mental", , drop = FALSE]
 
-cos_sim = sim2(x = word_vectors, y = safe, method = "cosine")
+#cos_sim = sim2(x = word_vectors, y = safe, method = "cosine")
 
-head(sort(cos_sim[,1], decreasing = TRUE), 10)
+#head(sort(cos_sim[,1], decreasing = TRUE), 10)
 ```
@@
 
+## Function to clean text of Ligatures
+```{r}
+to.plain <- function(s) {
+
+   # 1 character substitutions
+   old1 <- "šžþàáâãäåçèéêëìíîïðñòóôõöùúûüý"
+   new1 <- "szyaaaaaaceeeeiiiidnooooouuuuy"
+   s1 <- chartr(old1, new1, s)
+
+   # 2 character substitutions
+   old2 <- c("<U+FB03>", "<U+FB01>", "<U+FB00>", "<U+FB02>")
+   new2 <- c("ffi", "fi", "ff", "fl")
+   s2 <- s1
+   for(i in seq_along(old2)) s2 <- gsub(old2[i], new2[i], s2, fixed = TRUE)
+
+   s2
+}
+```
+
 'n' represents the number of subfolders and subsequently corpora that you intent the produce. 'corpusKey' will indicate the numbering convention of the corpora and analysis in subsequent code. 
@@
 # n - number of corpora
-n <- 4
+n <- 5
 corpusNum <- seq(1, n, 1)
@@
 
-corpusNum <- c()
+NAwords5 <- c()
 
@@
 {
-text[i] <- eval(parse(text = paste("text", i, sep = "")))
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
 }
@@
 
-corpusKey <- data.frame(corpusNum, subFolders)
-
-rm(temp_df_source, tempCorpus, address, doc_id, fileBaseNames, filePath, i, m, n, newFile, pdfLocation, subFolder, test, txtLocation)
+rm(temp_df_source, tempCorpus, address, doc_id, fileBaseNames, filePath, i, m, newFile, pdfLocation, subFolder, test, txtLocation)
 ```
@@
 ```{r}
+n <- 5 
 for (i in seq(1, n, 1))
@@
 
-paste(sort(NAwords4), collapse = " ")
+paste(sort(c("tm", "readr", "tools", "dplyr", "tidytext", "topicmodels", "ggplot2", "wordcloud", "word2vec", "pdftools", "reshape2", "text2vec", "stringr", "tidyr", "igraph")), collapse = " ")
 
 ```
+
+# Coverts double coloumn documents to single column
+
+The first chuck sets up the function used in the second section.
+
+https://stackoverflow.com/questions/42541849/extract-text-from-two-column-pdf-with-r 
+```{r}
+
+trim <- function (x) gsub("^\\s+|\\s+$", "", x)
+
+QTD_COLUMNS <- 2
+read_text <- function(text) {
+  result <- ''
+  #Get all index of " " from page.
+  lstops <- gregexpr(pattern =" ",text)
+  #Puts the index of the most frequents ' ' in a vector.
+  stops <- as.integer(names(sort(table(unlist(lstops)),decreasing=TRUE)[1:2]))
+  #Slice based in the specified number of colums (this can be improved)
+  for(i in seq(1, QTD_COLUMNS, by=1))
+  {
+    temp_result <- sapply(text, function(x){
+      start <- 1
+      stop <-stops[i] 
+      if(i > 1)            
+        start <- stops[i-1] + 1
+      if(i == QTD_COLUMNS)#last column, read until end.
+        stop <- nchar(x)+1
+      substr(x, start=start, stop=stop)
+    }, USE.NAMES=FALSE)
+    temp_result <- trim(temp_result)
+    result <- append(result, temp_result)
+  }
+  result
+}
+
+# Create a loop of the code below to run through list of documents
+
+pdfLocation <- "Texts/Academic Papers NoRef DoubleCol"
+
+ if (file.exists(paste(pdfLocation, "txt"))){
+    txtLocation <- paste(pdfLocation, "txt")
+  }else{
+    dir.create(paste(pdfLocation, "txt"))
+    txtLocation <- paste(pdfLocation, "txt")
+  }
+  fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
+  filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
+
+for (pdf in filePath)
+  {
+txt <- pdf_text(pdf)
+result <- ''
+for (i in 1:length(txt)) { 
+  page <- txt[i]
+  t1 <- unlist(strsplit(page, "\n"))      
+  maxSize <- max(nchar(t1))
+  t1 <- paste0(t1,strrep(" ", maxSize-nchar(t1)))
+  result = append(result,read_text(t1))
+}
+newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(pdf)), ".txt", sep = "")
+write(result, newFile)
+}
+
+```
+
+```{r}
+rm(list=ls(pattern = "^text"))
+```

### 2021-05-18 AST-Framing-Ontario/Data Pre-Processesing.rmd
May 18
- Added Re-trimmed academic papers
- Added excel documenting changes
- Added Original pdf folder

@@
 params:
-  Academic_Papers: "Texts/Academic Papers NoRef"
-  Academic_Papers_DoubCol: "Texts/Academic Papers NoRef DoubleCol"
+  Academic_Papers_SinglCol: "Texts/Academic Papers Trimmed Single Col"
+  Academic_Papers_DoubCol: "Texts/Academic Papers Trimmed Double Col"
   Consortia: "Texts/Consortia"
@@
 ```{r}
-pdfLocation <- params$Academic_Papers
+pdfLocation <- params$Academic_Papers_SinglCol
 
@@
 
-pdfLocation <- "Texts/Academic Papers NoRef DoubleCol"
+pdfLocation <- "Texts/Academic Papers Trimmed Double Col"
 

### 2021-06-03 AST-Framing-Ontario/AST-Framing-Ontario.Rmd

@@
 ---
-title: Framing active school travel in Ontario, Canada
+title: How do school travel planning stakeholders frame active school travel in Ontario, Canada?
 author:
@@
 library(tools)
+library(DiagrammeR)
+library(kableExtra)
 ```
@@
 Walking and cycling to school, commonly known as active school travel or active school transportation (AST), has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020].
-This trend has prompted an abundance of research over the past two decades to examine why fewer children are walking and cycling to school, what influences AST, and the associated implications for children's health.
-Many studies have been specific to Canada [e.g., see: @buliungActiveSchoolTransportation2009; @faulknerSchoolTravelChildren2013; @mammenUnderstandingDriveEscort2012; @mammenSchoolTravelPlanning2014; @rothmanActiveSchoolTransportation2021; @wilsonUnderstandingChildParent2018] which aligns with and informs a growing interest in school travel planning (STP) across the country.
-Indeed, a diversity of stakeholders responsible for transportation, public health, and education are collaborating and spearheading efforts to get more children walking and cycling.
-Promoting AST is seen as an affordable, convenient, and environmentally friendly way to enhance the mental, physical, and psychological health of children [@mammenSchoolTravelPlanning2014].
+This trend has prompted an abundance of research over the past two decades to examine why fewer children are walking and cycling to school, what influences AST, and what the associated implications are for children's health.
+Many studies on this topic have been specific to Canada [e.g., see: @buliungActiveSchoolTransportation2009; @faulknerSchoolTravelChildren2013; @mammenUnderstandingDriveEscort2012; @mammenSchoolTravelPlanning2014; @rothmanActiveSchoolTransportation2021; @wilsonUnderstandingChildParent2018] which aligns with and informs a growing interest in school travel planning across the country.
+
+School travel planning (STP) is a "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, public health, and safety [@mammenSchoolTravelPlanning2014].
+Parents and parent councils also typically have a role in supporting or implementing STP.
+The intervention encourages "community-wide involvement" and collaboration between participating stakeholders, who contribute their expertise to remove "school-specific" barriers to AST and to identify strategies for promoting and encouraging AST.
+STP may also involve other stakeholders including local advocacy groups or environmental organizations who are familiar with the state of active travel at the community-level.
+Buliung et al.
+[-@buliungSchoolTravelPlanning2011] piloted an STP intervention at 12 schools in 4 Canadian provinces and reported that it increased AST rates and led to a "mobilization of diverse community resources".
+Since this seminal study, STP interventions have become increasingly popular and common at schools across Canada and have even attracted funding from provincial governments.
+In 2017, the provincial government of Ontario issued funding to launch the _Ontario Active School Travel_ (OAST) program, which supports stakeholders in municipalities across the province implement STP.
+
+The ways in which interventions are framed to their target audience can ultimately influence how they are received and whether they result in behaviour change. Framing analysis is a method
+
 Therefore, these goals ought to be clearly articulated and reflected in transportation plans and policies to guide initiatives.
@@
 In the case of Canada, Riazi found that location, specifically concentration of population, was the stronger correlate to CIM even after accounting for the influence of gender.
-Whereas European countries have a positive correlation between population density and impendence level (Masoumi, 2020), Canadian cities saw the inverse effect with more dense cities such as Ottawa and Vancouver rating much lower in CIM than Trois-Rivieres, a small city in Quebec.
+Whereas European countries have a positive correlation between population density and impedence level (Masoumi, 2020), Canadian cities saw the inverse effect with more dense cities such as Ottawa and Vancouver rating much lower in CIM than Trois-Rivieres, a small city in Quebec.
 Riazi et al.
@@
 The way these policy issues are framed is important to understand because it plays a role in either altering or preserving the existing social perceptions.
+
 In the case of AST and CIM in Canada, Riazi et al.
@@
 
-The aim of this paper is to consider how AST, STP, and CIM are framed in the province of Ontario, Canada.
-Using a framing analysis approach, we explore how varying stakeholders involved in these initiatives (for example, municipal governments, public health units, transportation consortium, and school boards) present the benefits, challenges, and solutions for improving active school travel.
+The aim of this paper is to analyze how AST and STP are framed in Ontario, Canada.
+Using a framing analysis approach, we examine how varying stakeholders involved in these initiatives present the benefits, challenges, and solutions for improving active school travel.
 _Describe in further detail once procedure for analysis is conceptualized_
@@
 
-In Ontario, active school travel initiatives spread across the province by the 2000s and were initially attempted by individual schools without a coordinated movement [@ontarioactiveschooltravel].
+In Ontario, AST initiatives spread across the province by the early 2000s and were initially attempted by individual schools without a coordinated movement [@ontarioactiveschooltravel].
 Such one-off efforts, particularly those targeting education or promotional initiatives, may only prove to provide AST in the short term [@chillonSystematicReviewInterventions2011].
-At about the same time, a concept called school travel planning (STP) was developed in the United Kingdom [@greencommunities2007].
+Around the same time, school travel planning was developed in the United Kingdom [@greencommunities2007].
 STP offered an opportunity for key local stakeholders such as schools, school boards, and municipalities to make tangible changes to both the social and physical environment to encourage AST among their students that can be sustained in the long term.
+
 However, it was not until 2007 that Green Communities Canada (GCC), a non-profit organization, began adapting and delivering a universal STP framework in Canada.
-This initiative followed their publication on the _Review of International School Travel Planning Best Practices_ in 2007, which included the initial pilot in the United Kingdom, and others in New Zealand, Australia, and United States.
+This initiative followed their publication on the _Review of International School Travel Planning Best Practices_ in 2007, which included the initial pilot in the United Kingdom and others in New Zealand, Australia, and United States.
 Under GCC’s framework, a Canadian pilot intervention was trialed at twelve schools across four provinces [@buliungSchoolTravelPlanning2011a].
-The results of the pilot convinced the government of the Province of Ontario to issue a grant which culminated in the development of the program _Ontario Active School Travel_ (OAST), led by GCC, to fund initiatives that promote active school travel.
+
+In 2017, the provincial government of Ontario issued funding to Green Communities Canada to launch the _Ontario Active School Travel_ (OAST) program.
+The program provides funding for school and community-based initiatives that promote active school travel in municipalities and regions across Ontario.
 As of 2021, OAST has funded _X_ projects in Ontario.
-GCC continues its work by providing resources for interested stakeholders and funding projects across Ontario led by collaborative groups involving school boards, municipalities/regions, and regional transportation consortiums.
-The latter is a unique group of entities sanctioned by the Ontario Ministry of Education in 2006.
-These entities are a collaboration between regions and school boards whose objective is to deliver more efficient and effective transportation services to its area [@ministryeducation2006].
+GCC continues its work by providing resources for interested stakeholders and funding projects across Ontario led by collaborative groups involving school boards, municipal or regional governments, and regional transportation consortia.
+The latter are dedicated transportation bodies that deliver efficient and effective transportation services, which generally focuses on providing the school busing service to families in their associated region.
 
@@
 
-## 2.1. Procedure
+## 2.1. Framing Analysis
 
-This section provides methodology for converting searchable portable document formats (PDFs) into a text corpus that can then be used in further natural language processing (NPL) analysis.
-The text corpus is a collection of structured texts which enables anaylsis for packages such as 'topicmodels' This notebook serves as an introduction on how to convert files and conduct an surface level analysis.
+## 2.2. Procedure
 
-Below are the folders used and how they have been obtained.
+To determine which stakeholder groups are typically involved in AST and/or STP initiatives in Ontario, we first conducted a preliminary scan of current and past projects funded by the _Ontario Active School Travel_.
+We found that projects are often led in collaboration by a school board, the respective municipality or region (i.e., transportation planners, public health professionals, engineers, etc.), and the regional transportation consortia.
+Non-profit organizations, police services, and advocacy groups are other stakeholders who may play a role in supporting AST and/or STP.
 
-__'Academic Papers'__
+We then assembled a collection of publicly available documents that were sourced online from the main stakeholder groups: i) English school boards; ii) municipal government; and iii) transportation consortia.
+The search was guided first by a list of all English school boards across Ontario.
+The websites of each school board were searched for pages related to transportation or school travel.
+These pages were manually downloaded.
+Next, we collected documents by searching municipal government and transportation consortia websites.
+The latter were identified based on geographic area (i.e., the municipalities and/or transportation consortia who are in the same geographic area of each school board).
+Pages related to active transportation or school travel were manually downloaded.
+Webpages were included in the corpus if they were easy to find.
+This criteria was important since our analysis pertains to how such issues are framed to the public.
+Thus, these pages ought to be easy to find, which we defined as requiring no more than 2-4 separate links from the initial Google search.
 
-[Insert Methodology for obtaining Academic Papers]
+The initial corpus included 64 relevant documents (i.e., one webpage or more) from all main stakeholder groups.
+It is important to note that school boards, municipal governments, and transportation consortia may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents.
+Search results are summarized in Table \ref{tab:search-results}.
 
-For these three following folders, docurments are sourced from direct affiliate websites from those three groups and are printed to pdf via the web browser if deemed eligible.
-The criteria below indicates how eligibility was determined for each grouping.
-It was important that webpages were easy to find as the analysis pretains to how such issues are framed to the public.
-Our interpretation of 'easy to find' are webpages that required no more than 2-4 seperate links from the initial browser search.
-The search was guilded based off a list of all Ontario school boards.
-Consortiums and Municipalities/Regions were organized based on the school boards.
+```{r search-results, echo=FALSE}
+data_tbl <- data.frame(
+  Stakeholder = c("English school boards", "Municipal or regional governments", "Transportation Consortia"),
+  Total = c("62", "62", "39"),
+  Included = c("31", "25", "8")
+)
 
-__'Consortium'__
+kable(data_tbl,
+      "latex",
+      booktabs = TRUE,
+      caption = "\\label{tab:search-results}Search results from the main stakeholder groups.") %>%
+  kable_paper(full_width = F) %>%
+  column_spec(1, bold = T, border_right = T) %>%
+  column_spec(2, width = "30em") %>%
+  column_spec(3, border_left = T) %>%
+  kable_styling(latex_options = c("striped", "scale_down"))
+```
 
-Consortiums are dedicated transportation bodies that primarly focus of providing the school bussing service to families in their associated region.
-Pages are determined to be relevent if they specifically relate to AST or STP.
-9 - Total documents
-
-__'Municipalities or Regions'__
-
-Municipalities/regions had pages about transportation that involved the service it provided which is not relevent to our analysis.
-Only pages specifically dicussing active travel, AST, or STP are included.
-Page were also sourced from associated local health units which were considered part of municpalities/regions.
-29 - Total doucments
-
-__'School Boards'__
-
-School boards generally will have a single page for transportation so documents were sourced from those pages regardless in mentioned STP or AST.
-In cases were both AST and STP are mentioned both those pages are included.
-27 - Total doucments
-
-**NOTE: Current version of the code converts 1 file containing pdf documents at a time**
-
-### Searchable pdf files to txt conversion
-
-The conversion process in this notebook can only be conducted on one file at a time.
-Select one of the files provided to use.
-If you want to run multiple files to create seperate corpora use 'Multiple PDF Files to Corpora.Rmd'.
-
-Searchable PDF files to .txt conversion
-
-PDFs can be brought into the corpus directly however each page of the PDF is read as an invividual document.
-For our purposes a conversion from PDF to .txt will allow us to keep all pages in a document together when loading it into the corpus.
-Make sure you have the directory pat to where your PDFs are stored.
-In addition you will need to manually create a seperate file where you wish to store your .txt files.
-Re-assign the 'pdfLocation' and 'txtLocation' to those corresponding locations.
-
-```{r}
+```{r, include=FALSE}
 pdfLocation <- "E:/Dr. Paez Articles/with References"
@@
 
-### Creating data frame of texts
-
-Creation of a data frame of texts is required prior to conversion to corpus.
-The data fram must contain 'doc_id' and 'text'.
-Additional fields may be included in data frame ,it will however be treated as metadata by the corpus.
-
-```{r}
+```{r, include=FALSE}
 # This loop creates a vector of the texts
@@
 
-### Conversion of data frame to corpus
-
-```{r}
+```{r, include=FALSE}
 df_source <- DataframeSource(textDF)
@@
 
-### Corpus cleaning 
-```{r}
+```{r, include=FALSE}
 corpus <- tm_map(corpus, stripWhitespace)
@@
 
-### Term Document Matrix & Document Term Matrix
-```{r}
+```{r, include=FALSE}
 TDM <- TermDocumentMatrix(corpus)

### 2021-06-08 AST-Framing-Ontario/Data Pre-Processesing.rmd
Split Procedure
Creation of corpus now pulls from clean texts as opposed trimmed ones

@@
 ```{r}
-pdfLocation <- params$Academic_Papers_SinglCol
+pdfLocation <- params$Academic_Papers_DoubCol
 
@@
 
+n <- n+1
+}
+```
+
+## Creating importing texts to environment
+
+imports texts that were manually cleaned
+
+```{r}
+# location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/Academic Papers"
+
+cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
+n <- 1 
+for (txt in cleantxtlist) {
+
 # Creates uniquely id text store in 'Environment'
-assign(paste("text", n, sep = ""), readChar(newFile, file.info(newFile)$size))
-
-n <- n+1
+assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
+n <- n + 1 
 }
@@
 # Example 
-content(corpus[[2]])
+content(corpus[[6]])
 ```
@@
 # Example
-content(corpus[[2]])
+content(corpus[[6]])
 ```

### 2021-06-10 AST-Framing-Ontario/Data Pre-Processesing.rmd
May 9 - 10 Changes
- Reviewed Single Column clean docs
- Fix stop words Parameters
- Updated excel documenting Academic documents

@@
   School Boards: "Texts/School Boards"
-  AP_stopW: c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
-  AP_DoubCol_stopW: c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
-  Con_stopW: c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
-  Mun_Reg_stopW: c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
-  SB_stopW: c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")
+  AP_stopW: !r c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
+  Con_stopW: !r c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
+  Mun_Reg_stopW: !r c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
+  SB_stopW: !r c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")
 
@@
 # Example 
-content(corpus[[6]])
+content(corpus[[7]])
 ```
@@
 
-NAwords <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
+NAwords <- params$AP_stopW
 corpus <- tm_map(corpus, removeWords, NAwords)
@@
 # Example
-content(corpus[[6]])
+content(corpus[[7]])
 ```

### 2021-06-15 AST-Framing-Ontario/Data Pre-Processesing.rmd
June 15th
- Combined clean academic papers
- Sentiment analysis testing
- Bi-gram visualization update

@@
   Con_stopW: !r c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
-  Mun_Reg_stopW: !r c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
+  Mun_Reg_stopW: !r c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", m  "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
   SB_stopW: !r c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")
@@
 library(text2vec)
+library(textdata)
 library(tidyr)
@@
 
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
 # Adjust the parameter below to filter out based on number of occurence
 # Error will occur if n is outide the range of occurences
+
 bigram_graph <- bigram_counts %>%
-  filter(n > 5) %>%
+  filter(n > 100) %>%
   graph_from_data_frame()
@@
   geom_edge_link() +
-  geom_node_point() +
-  geom_node_text(aes(label = name), vjust = 1, hjust = 1)
+  geom_node_point(color = "lightgreen", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
 
@@
 ```
+
+```{r}
+bing <- get_sentiments(lexicon = "nrc")
+colnames(vocab)[1] <- "word"
+senti <- inner_join(bing, vocab, by= "word")
+
+```

### 2021-06-18 AST-Framing-Ontario/Data Pre-Processesing.rmd
June 18, 2021
- Initial Sentiment

@@
 library(topicmodels)
+library(widyr)
 library(word2vec)
@@
 # location of manually cleaned .txt documents
-cleantxtLocation <- "Cleaned .txt/Academic Papers"
+cleantxtLocation <- "Cleaned .txt/Policy"
 
@@
 
-a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
-
 # Adjust the parameter below to filter out based on number of occurence
@@
 bigram_graph <- bigram_counts %>%
-  filter(n > 100) %>%
+  filter(n > 10) %>%
   graph_from_data_frame()
@@
 
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
 ggraph(bigram_graph, layout = "fr") +
-  geom_edge_link() +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
   geom_node_point(color = "lightgreen", size = 4) +
@@
 set.seed(4321)
-wordcloud(d$word, d$freq, min.freq = 10, max.words = 50, random.order = FALSE, rot.per = 0.5, random.color = TRUE)
+wordcloud(d$word, d$freq, min.freq = 25, max.words = 50, random.order = FALSE, rot.per = 0.5, random.color = TRUE)
 ```
@@
 ```
+
+```{r}
+library(widyr)
+
+words <- td_corpus %>%
+  unnest_tokens(word, text, token = "ngrams", n = 1)
+
+# word_count <- words %>%
+#   count(word, sort = TRUE)
+
+word_pairs <- words %>%
+  pairwise_count(word, id, sort = TRUE)
+
+word_pairs %>%
+  filter(item1 == "traffic")
+
+```
+```{r}
+word_pairs %>%
+  filter(item1 %in% c("traffic", "safety", "urban", "street")) %>%
+  group_by(item1) %>%
+  slice_max(n, n = 10) %>%
+  ungroup() %>%
+  mutate(item2 = reorder(item2, n)) %>%
+  ggplot(aes(item2, n)) +
+  geom_bar(stat = "identity") +
+  facet_wrap(~ item1, scales = "free") +
+  coord_flip()
+```
+
+```{r}
+word_cors <- words %>% 
+  group_by(word) %>% 
+  filter(n() >= 10) %>%
+  pairwise_cor(word, id, sort = TRUE)
+
+```
+
+```{r}
+
+word_cors %>%
+  filter(item1 == "traffic")
+
+word_cors %>%
+  filter(item1 == "safety")
+
+word_cors %>%
+  filter(item1 == "urban")
+
+word_cors %>%
+  filter(item1 == "car")
+
+word_cors %>%
+  filter(item1 == "transit")
+
+word_cors %>%
+  filter(item1 == "independent")
+
+word_cors %>%
+  filter(item1 == "transit")
+
+word_cors %>%
+  filter(item1 == "street")
+
+word_cors %>%
+  filter(item1 == "age")
+
+word_cors %>%
+  filter(item1 == "parental")
+
+```
+```{r}
+word_cors %>%
+  filter(item1 %in% c("traffic", "independent", "safety", "urban", "density", "street")) %>%
+  group_by(item1) %>%
+  slice_max(correlation, n = 7) %>%
+  ungroup() %>%
+  mutate(item2 = reorder(item2, correlation)) %>%
+  ggplot(aes(item2, correlation)) +
+  geom_bar(stat = "identity") +
+  facet_wrap(~ item1, scales = "free") +
+  coord_flip()
+```

### 2021-06-18 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Acknowledgements added

@@
 
+Acknowledgments
+===================
+
+This research was completed using open software, and the authors wish to acknowledge the developers of the following `R` packages: `biscale` [@R-biscale], `cowplot` [@R-cowplot], `data.table` [@R-data.table], `disk.frame` [@R-disk.frame], `gdistance` [@R-gdistance], `gridExtra` [@R-gridExtra], `kableExtra` [@R-kableExtra], `knitr` [@R-knitr], `pycno` [@R-pycno], `r5r` [@R-r5r], `raster` [@R-raster], `rgdal` [@R-rgdal], `rticles` [@R-rticles], `sf` [@R-sf], `tidyverse` [@R-tidyverse], `tinytex` [@R-tinytex],
+`units` [@R-units].
+
 References

### 2021-06-24 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Manuscript is reorganized with added content to introduction and methods

--- 2021-06-03 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
@@
 
-1. Background
+1. Introduction
 ===============
 
-Walking and cycling to school, commonly known as active school travel or active school transportation (AST), has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020].
-This trend has prompted an abundance of research over the past two decades to examine why fewer children are walking and cycling to school, what influences AST, and what the associated implications are for children's health.
-Many studies on this topic have been specific to Canada [e.g., see: @buliungActiveSchoolTransportation2009; @faulknerSchoolTravelChildren2013; @mammenUnderstandingDriveEscort2012; @mammenSchoolTravelPlanning2014; @rothmanActiveSchoolTransportation2021; @wilsonUnderstandingChildParent2018] which aligns with and informs a growing interest in school travel planning across the country.
+## 1.1. School travel planning in Canada
 
-School travel planning (STP) is a "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, public health, and safety [@mammenSchoolTravelPlanning2014].
+Walking and bicycling to school, commonly known as active school travel or active school transportation (AST), has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020].
+This trend has prompted a multi-sector response to identify strategies to increase AST, the most popular of which is a growing interest in school travel planning across Canada.
+
+School travel planning (STP) is a "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health [@mammenSchoolTravelPlanning2014].
 Parents and parent councils also typically have a role in supporting or implementing STP.
-The intervention encourages "community-wide involvement" and collaboration between participating stakeholders, who contribute their expertise to remove "school-specific" barriers to AST and to identify strategies for promoting and encouraging AST.
-STP may also involve other stakeholders including local advocacy groups or environmental organizations who are familiar with the state of active travel at the community-level.
+The intervention encourages participation from the broader community and collaboration between involved stakeholders, who contribute their expertise to remove "school-specific" barriers to AST and to identify strategies for promoting and encouraging AST.
+STP may also involve other stakeholders including local advocacy groups or environmental organizations who are familiar with the state of AST at the community-level.
 Buliung et al.
@@
 Since this seminal study, STP interventions have become increasingly popular and common at schools across Canada and have even attracted funding from provincial governments.
-In 2017, the provincial government of Ontario issued funding to launch the _Ontario Active School Travel_ (OAST) program, which supports stakeholders in municipalities across the province implement STP.
 
-The ways in which interventions are framed to their target audience can ultimately influence how they are received and whether they result in behaviour change. Framing analysis is a method
+## 1.2. Correlates of active school travel
 
-Therefore, these goals ought to be clearly articulated and reflected in transportation plans and policies to guide initiatives.
-Presently, however, there is research lacking that specifically explores how Canadian municipalities and schools frame and discuss AST with the public.
+Factors that influence AST are typically conceptualized according to the socioecological model whereby children's travel behaviour is understood within the context of their household, social, and built environments [see @mitraIndependentMobilityMode2013].
+At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018].
+There is some evidence that gender is a determinant of AST [@larsenInfluencePhysicalEnvironment2009], although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
+Distance between home and school is associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
+Car ownership is an important household-level influence on AST [@pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], as is household income [@pontEnvironmentalCorrelatesChildren2009].
+Parental perceptions of the environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and children's skills [@ghekiereInsightsChildrenIndependent2017] also influence whether they allow their children to walk or cycle to school.
+Finally, many studies have found that the quality of the built environment [@ikedaAssociationsChildrenActive2018; @kimBuiltNaturalEnvironmental2020] and active travel infrastructure [@pontEnvironmentalCorrelatesChildren2009] facilitate AST.
+Concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012].
+The consensus is that all of these factors are interrelated and that interventions ought to target multiple factors in order to increase walking and bicycling levels to school.
 
-## 1.1. Literature Review
+## 1.3. Correlates of children's independent mobility
 
-Several recent reviews offer a comprehensive synopsis of the state of active school travel [@ikedaAssociationsChildrenActive2018; @rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenIndependent2013], while others assess the efficacy of interventions and strategies that have been implemented to encourage and support AST [@buttazzoniActiveSchoolTravel2018; @chillonSystematicReviewInterventions2011; @jonesInterventionsPromotingActive2019; @laroucheEffectivenessActiveSchool2018; @marziInterventionsAimingPromote2020; @schonbachStrategiesEffectsSchoolbased2020].
-Many patterns emerge from studies within and between countries with respect to the factors that are positively associated with AST.
-These factors broadly fall into distinct levels: individual, household, social environment, and physical environment.
-Among the most influential are age, gender, distance to school, parental perceptions of the environment [@demeesterParentalPerceivedNeighborhood2014] and children's skills [@ghekiereInsightsChildrenIndependent2017], quality of the built environment, and urban infrastructure.
-The consensus is that these factors are interrelated and that interventions ought to target multiple factors in order to increase walking and cycling levels to school.
-More recently, researchers have been exploring the link between transportation and children's wellbeing [@waygoodTransportChildrenWellbeing2020], which has relevant applications to the study of school travel and satisfaction [see @vandenbergFactorsAffectingParental2020] among others.
-
-Furthermore, AST is one of the most common opportunities for children to travel without adult supervision on a regular basis.
+AST is one of the most common opportunities for children to travel without adult supervision on a regular basis.
 Children's independent mobility (CIM) was first described by Hillman et al.
 [-@hillmanOneFalseMove1990] as the freedom of children to travel and play within their neighborhood and city without the presence of adults.
-Similar to AST, children's independent mobility is much less common now than it was for previous generations [@bhosaleIntergenerationalChangeChildren2017], and is influenced by similar personal and environmental factors [@marziChildrenIndependentMobility2018].
-CIM is particularly important for different domains of children's health and wellbeing [@riaziChildrenIndependentMobility2018].
-There is also sufficient evidence in the literature linking the association between AST and CIM [@laroucheRelationshipsChildrenIndependent2020; @mitraIndependentMobilityMode2013], particularly in boys [@schoeppeAssociationsChildrenIndependent2014].
-The gender disparity has been noted in other papers regarding CIM [@marziSocialPhysicalEnvironmental2018; @marziInterventionsAimingPromote2020] with recommendations being made for interventions to specifically target girls to boost their mobility within their neighborhood [@schoeppeSociodemographicFactorsNeighbourhood2015].
-CIM offers other benefits such as increasing traffic and safety skills, boosting spatial awareness when navigating public spaces, and providing more opportunity for social interaction with peers [@schoeppeAssociationsChildrenIndependent2014].
-What is less clear is how CIM plays into the consideration of policymakers when they act on the objective of improving AST.
+The ability of children to reach destinations such as school or local parks by walking or bicycling on their own as a growing area of research that is related to the body of literature on AST.
+Similar to AST, CIM is much less common now than it was for previous generations [@bhosaleIntergenerationalChangeChildren2017], and is influenced by many similar personal and environmental factors as AST [@marziChildrenIndependentMobility2018; @mitraIndependentMobilityMode2013].
+In a study conducted in multiple Canadian cities, Riazi et al.
+[-@riaziCorrelatesChildrenIndependent2019] found that a range of factors such as child grade, car ownership, and parental perceptions of safety and environment were associated with CIM.
 
-In the case of Canada, Riazi found that location, specifically concentration of population, was the stronger correlate to CIM even after accounting for the influence of gender.
-Whereas European countries have a positive correlation between population density and impedence level (Masoumi, 2020), Canadian cities saw the inverse effect with more dense cities such as Ottawa and Vancouver rating much lower in CIM than Trois-Rivieres, a small city in Quebec.
-Riazi et al.
-[-@riaziChildrenIndependentMobility2018] note, however, that such differences in the Canadian context could be a result of the multicultural diversity in large Canadian cities which leads to very differing social and cultural norms that may influence the findings.
-_review a few prominent Canadian studies on AST and CIM in more detail: Riazi et al., 2019; Mammen et al., 2012 & 2014; Rothman et al., 2021_
+## 1.4. Benefits of AST and CIM
 
-The correlates of AST and CIM are important knowledge for policymakers because they identify points of intervention and potential benefits that ought to be communicated to the public to build support for new planning paradigms.
-Framing analysis is one method to analyze how particular issues are framed to groups of people, for instance parents or educators who might be inclined to support AST.
+The desire to increase AST is warranted - there is strong evidence that children who walk and bicycle to school accrue physical and mental health benefits.
+Many studies and reviews have focused on the association between AST or CIM and physical activity [e.g., @faulknerActiveSchoolTransport2009; @mitraChildrenActivitytransportationLifestyles2017; @schoeppeAssociationsChildrenActive2015], with findings consistently demonstrating that children who travel by walking or bicycling to school are more active than their peers who do not use active travel.
+More recently, researchers have been exploring the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020], which has relevant applications to the study of school travel and satisfaction [see @vandenbergFactorsAffectingParental2020].
+CIM is also important for different domains of children's health and wellbeing [@riaziChildrenIndependentMobility2018].
+It offers benefits such as increasing traffic and safety skills, boosting spatial awareness when navigating public spaces, and providing more opportunity for social interaction with peers [@schoeppeAssociationsChildrenIndependent2014].
+
+## 1.5. Encouraging adoption of active school travel
+
+In the case of AST and CIM in Canada, Riazi et al.
+[-@riaziCorrelatesChildrenIndependent2019] state: "it will be vital for interventions to target modifiable factors, including children's and parents' perceptions of their social environment." Parents play the important role of "gatekeeper" by either granting or restricting CIM licenses, meaning whether children can travel alone [@sharminAssociationBuiltEnvironment2017].
+For this reason, stakeholders involved in STP produce information targeted for both children and parents, and aim to involve the broader community in their efforts.
+
+However, the ways in which interventions like STP are framed to their target audience can ultimately influence how they are received and whether they result in behaviour change.
+The correlates of AST are important knowledge for policymakers because they identify points of intervention and potential benefits that ought to be communicated to the public encourage adoption of AST and to build support for new planning paradigms.
+What is less clear is how CIM plays into the consideration of policymakers when they act on the objective of increasing AST.
+
+Any goals for AST, and also CIM, ought to be clearly articulated and reflected in transportation plans and policies to guide initiatives.
+Presently, however, there has been no study to date that explores how Canadian municipalities and schools frame and discuss AST with the public.
+Framing or content analysis is one method to analyze how particular issues are framed to groups of people, for instance parents or educators who might be inclined to support AST.
 It attempts to understand how information presented from a "communicator" leads the "receiver" to a desired response [@reynardGrowthResilienceHow2021].
@@
 The authors determined that most issues are framed favouring merely a tinkering of the status quo as opposed to pushing for real change.
-The way these policy issues are framed is important to understand because it plays a role in either altering or preserving the existing social perceptions.
+Natural language processing (NLP) was used for a similar purpose to examine content in general plans from Californian cities [@brinkleyWhatPlanUsing2021].
+The way policy issues are framed is important to understand because it plays a role in either altering or preserving the existing social perceptions.
 
-In the case of AST and CIM in Canada, Riazi et al.
-[-@riaziCorrelatesChildrenIndependent2019] state: "it will be vital for interventions to target modifiable factors, including children's and parents' perceptions of their social environment." Parents play the important role of "gatekeeper" by either granting or restricting CIM licenses, meaning whether children can travel alone [@sharminAssociationBuiltEnvironment2017].
-Framing is also important because both walking and cycling are often targeted together, whereas evidence shows that distinct interventions should target each separately [see @helbichChildrenSchoolCommuting2017], which has implications for how municipalities and schools aim to address this issue.
-For these reasons, the framing of active school travel should be explored and considered in the school travel literature given its potential to influence and incentivize behaviour change.
+## 1.6. Study aim
 
-The aim of this paper is to analyze how AST and STP are framed in Ontario, Canada.
-Using a framing analysis approach, we examine how varying stakeholders involved in these initiatives present the benefits, challenges, and solutions for improving active school travel.
-_Describe in further detail once procedure for analysis is conceptualized_
+The aim of this paper is to analyze how AST is framed by STP stakeholders in Ontario, Canada.
+We used topic modelling and content analysis to examine how the benefits and barriers of AST are presented and which solutions for improving AST are identified in local policy documents from Ontario municipalities and school boards.
+We compared these documents to a selection of studies on AST and CIM to explore the extent to which research findings have trickled down to inform policy and planning for AST interventions.
 
-## 1.2. Case Study: Ontario, Canada
+2. Methods
+===============
 
-In Ontario, AST initiatives spread across the province by the early 2000s and were initially attempted by individual schools without a coordinated movement [@ontarioactiveschooltravel].
-Such one-off efforts, particularly those targeting education or promotional initiatives, may only prove to provide AST in the short term [@chillonSystematicReviewInterventions2011].
-Around the same time, school travel planning was developed in the United Kingdom [@greencommunities2007].
-STP offered an opportunity for key local stakeholders such as schools, school boards, and municipalities to make tangible changes to both the social and physical environment to encourage AST among their students that can be sustained in the long term.
+## 2.1. Case study: Ontario, Canada
 
-However, it was not until 2007 that Green Communities Canada (GCC), a non-profit organization, began adapting and delivering a universal STP framework in Canada.
-This initiative followed their publication on the _Review of International School Travel Planning Best Practices_ in 2007, which included the initial pilot in the United Kingdom and others in New Zealand, Australia, and United States.
-Under GCC’s framework, a Canadian pilot intervention was trialed at twelve schools across four provinces [@buliungSchoolTravelPlanning2011a].
-
-In 2017, the provincial government of Ontario issued funding to Green Communities Canada to launch the _Ontario Active School Travel_ (OAST) program.
-The program provides funding for school and community-based initiatives that promote active school travel in municipalities and regions across Ontario.
+In 2017, the provincial government of Ontario issued funding to Green Communities Canada (GCC), a non-profit organization, to launch the _Ontario Active School Travel_ (OAST) program.
+The program provides funding for school and community-based initiatives and supports stakeholders in municipalities across the province to implement STP and other interventions aimed at increasing AST.
 As of 2021, OAST has funded _X_ projects in Ontario.
@@
 
-2. Methods
-===============
+## 2.2. Data retrieval
 
-## 2.1. Framing Analysis
-
-## 2.2. Procedure
+### 2.2.1. Policy documents
 
@@
 Webpages were included in the corpus if they were easy to find.
-This criteria was important since our analysis pertains to how such issues are framed to the public.
+This primary criteria was important since our analysis pertains to how such issues are framed to the public.
 Thus, these pages ought to be easy to find, which we defined as requiring no more than 2-4 separate links from the initial Google search.
 
-The initial corpus included 64 relevant documents (i.e., one webpage or more) from all main stakeholder groups.
-It is important to note that school boards, municipal governments, and transportation consortia may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents.
+The initial policy corpus included 64 relevant policy documents (i.e., one webpage or more) from all main stakeholder groups.
+It is important to note that school boards, municipalities, and transportation consortia may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents.
 Search results are summarized in Table \ref{tab:search-results}.
@@
 ```
+
+### 2.2.1. Academic papers
+
+## 2.2. Data cleaning
+
+A multi-step process was conducted to ensure that the analysis captured as much  content as possible from both the policy documents (n = 64) and academic papers (n = 233).
+We manually removed any extraneous material in the documents that did not pertain to AST specifically.
+This included footnotes, references, acknowledgments, and conflict of interest statements in the academic papers.
+We removed all phone numbers, inserted links to other webpages, personal names, and content not to specific to AST from the policy documents that were retrieved from the websites of school boards, municipalities, and transportation consortia.
+
+To begin, the webpages, which were manually downloaded in portable document format (PDF), were trimmed so that pages that only consisted of tables, figures, or references were removed.
+Many academic papers were in a two-column format, which is not ideal for conversion to `txt`.
+We adapted a procedure (https://stackoverflow.com/questions/42541849/extract-text-from-two-column-pdf-with-r) to read the two-column PDF documents so that they would be converted correctly.
+Four academic papers did not join sufficiently and were taken out of the corpus due to the substantial time required to manually correct their inconsistencies.
+
+We then converted the trimmed PDF documents into `txt` files so that they could be imported in `R` for topic modelling.
+We proceeded to a manual cleaning phase where we removed any remaining tables, figures, references, headers/footings, and captions that could not be trimmed.
+Manual corrections were also required for certain pages in academic papers that remained in two-column format after the conversion process.
+This typically occured on pages that had a table or figure which disrupted the text.
+Finally, we reviewed all of the documents to remove hyphenation by line breaks and to keep hyphenated words together on the same line.
+Any ligatures (e.g., combinations of characters or letters that were not properly detected during the conversion process) were fixed by inserting the unicode sequence of character to replace the missing sequence of characters.
+
+At this point, the documents were imported into the corpus in `R` and added to a data frame for analysis.
+In the final step before analysis, we removed all blank spaces, punctuation, capitalization, and numbers.
+English stop words, as identified in a predetermined list by Lewis et al.
+[@R-tm], were removed.
+
+## 2.3. Topic modelling
+
+## 2.4. Summative content Analysis
+
+## 2.5. Reproducibility
+
+This paper is an example of open and reproducible research that uses only open software.
+All data were obtained from publicly available sources and organized in the form of a data package.
+Following best practices in spatial data science [@brunsdon2020opening], the code and data needed to reproduce or conduct a similar analysis for other regions in North America or elsewhere are available for download.
+
+3. Results
+===============
+
+## 3.1. Word Frequency
+
+## 3.2. Bigrams and Correlations
+
+## 3.3. Policy content
 
@@
 
-## 2.2. Data Analysis
-
-## 2.3. Reproducibility
-
-This paper is an example of open and reproducible research that uses only open software.
-All data were obtained from publicly available sources and organized in the form of a data package.
-Following best practices in spatial data science [@brunsdon2020opening], the code and data needed to reproduce or conduct a similar analysis for other regions in North America or elsewhere are available for download.
-
-3. Results
-===============
-
 4. Discussion
@@
 
-# 4.1. Implications for School Travel Planning
+## 4.1. Framing of AST in policy documents
+
+## 4.2. Framing of AST in academic papers
+
+## 4.3. Implications for School Travel Planning
 
@@
 
-## 4.2. Limitations
+## 4.4. Limitations
 
@@
 
+## 5.1. Future research
+
+Acknowledgments
+===================
+
+This research was completed using open software, and the authors wish to acknowledge the developers of the following `R` packages: `dplyr` [@R-dplyr], `ggraph` [@R-ggraph], `ggplot2` [@R-ggplot2], `igraph` [@R-igraph], `pdftools` [@R-pdftools], `readr` [@R-readr], `reshape2` [@R-reshape2], `stringr` [@R-stringr], `text2vec` [@R-text2vec], `textdata` [@R-textdata], `tidyr` [@R-tidyr], `tidytext` [@R-tidytext], `tm` [@R-tm], `tools` [@R-tools], `topicmodels` [@R-topicmodels], `widyr` [@R-widyr],
+`word2vec` [@R-word2vec], `wordcloud` [@R-wordcloud].
+
 References

### 2021-06-24 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
June 24th Changes

@@
 
+Loading in clean corpus. These are the products of 'Data Pre-Processing.Rmd'
+```{r}
+load(file= "Corpus .rda/academic_corpus.rda")
+load(file= "Corpus .rda/municipal_corpus.rda")
+load(file= "Corpus .rda/consortium_corpus.rda")
+load(file= "Corpus .rda/school_corpus.rda")
+load(file= "Corpus .rda/policy_corpus.rda")
+```
+
+Municipal Bi/Trigrams
+```{r}
+# Converting corpus to tidytext data type 
+td_municipal_corpus <- tidy(municipal_corpus)
+
+# n can be changed 
+municipal_bigrams <- td_municipal_corpus %>%
+  unnest_tokens(bigram, text, token = "ngrams", n = 2)
+
+municipal_trigrams <- td_municipal_corpus %>%
+  unnest_tokens(trigram, text, token = "ngrams", n = 3)
+# Bigrams & Trigrams that are most common
+
+top_municipal_bigrams <- municipal_bigrams %>%
+  count(bigram, sort = TRUE)
+
+top_municipal_trigrams <- municipal_trigrams %>% 
+  count(trigram, sort = TRUE)
+
+top_municipal_bigrams
+top_municipal_trigrams
+```
+
+Consortium Bi/Trigrams
+```{r}
+# Converting corpus to tidytext data type 
+td_consortium_corpus <- tidy(consortium_corpus)
+
+# n can be changed 
+consortium_bigrams <- td_consortium_corpus %>%
+  unnest_tokens(bigram, text, token = "ngrams", n = 2)
+
+consortium_trigrams <- td_consortium_corpus %>%
+  unnest_tokens(trigram, text, token = "ngrams", n = 3)
+# Bigrams & Trigrams that are most common
+
+top_consortium_bigrams <- consortium_bigrams %>%
+  count(bigram, sort = TRUE)
+
+top_consortium_trigrams <- consortium_trigrams %>% 
+  count(trigram, sort = TRUE)
+
+top_consortium_bigrams
+top_consortium_trigrams
+```
+
+School board Bi/Trigrams
+```{r}
+# Converting corpus to tidytext data type 
+td_school_corpus <- tidy(school_corpus)
+
+# n can be changed 
+school_bigrams <- td_school_corpus %>%
+  unnest_tokens(bigram, text, token = "ngrams", n = 2)
+
+school_trigrams <- td_school_corpus %>%
+  unnest_tokens(trigram, text, token = "ngrams", n = 3)
+# Bigrams & Trigrams that are most common
+
+top_school_bigrams <- school_bigrams %>%
+  count(bigram, sort = TRUE)
+
+top_school_trigrams <- school_trigrams %>% 
+  count(trigram, sort = TRUE)
+
+top_school_bigrams
+top_school_trigrams
+```
+
+Policy Bi/Trigrams
+```{r}
+# Converting corpus to tidytext data type 
+td_policy_corpus <- tidy(policy_corpus)
+
+# n can be changed 
+policy_bigrams <- td_policy_corpus %>%
+  unnest_tokens(bigram, text, token = "ngrams", n = 2)
+
+policy_trigrams <- td_policy_corpus %>%
+  unnest_tokens(trigram, text, token = "ngrams", n = 3)
+# Bigrams & Trigrams that are most common
+
+top_policy_bigrams <- policy_bigrams %>%
+  count(bigram, sort = TRUE)
+
+top_policy_trigrams <- policy_trigrams %>% 
+  count(trigram, sort = TRUE)
+
+top_policy_bigrams
+top_policy_trigrams
+```
+
+Academic Bi/Trigrams
+```{r}
+# Converting corpus to tidytext data type 
+td_academic_corpus <- tidy(academic_corpus)
+
+# n can be changed 
+academic_bigrams <- td_academic_corpus %>%
+  unnest_tokens(bigram, text, token = "ngrams", n = 2)
+
+academic_trigrams <- td_academic_corpus %>%
+  unnest_tokens(trigram, text, token = "ngrams", n = 3)
+# Bigrams & Trigrams that are most common
+
+top_academic_bigrams <- academic_bigrams %>%
+  count(bigram, sort = TRUE)
+
+top_academic_trigrams <- academic_trigrams %>% 
+  count(trigram, sort = TRUE)
+
+top_academic_bigrams
+top_academic_trigrams
+```
+
+Municipal Bi-gram visualizations 
+```{r}
+municipal_bigrams_separated <- municipal_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+municipal_bigram_counts <- municipal_bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurence
+# Error will occur if n is outide the range of occurences
+
+municipal_bigram_graph <- municipal_bigram_counts %>%
+  filter(n > 8) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
+ggraph(municipal_bigram_graph, layout = "fr") +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
+  geom_node_point(color = "lightblue", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
+```
+
+Consortium Bi-gram visualizations 
+```{r}
+consortium_bigrams_separated <- consortium_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+consortium_bigram_counts <- consortium_bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurence
+# Error will occur if n is outide the range of occurences
+
+consortium_bigram_graph <- consortium_bigram_counts %>%
+  filter(n > 5) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
+ggraph(consortium_bigram_graph, layout = "fr") +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
+  geom_node_point(color = "red", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
+```
+
+School Board Bi-gram visualizations 
+```{r}
+school_bigrams_separated <- school_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+school_bigram_counts <- school_bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurence
+# Error will occur if n is outide the range of occurences
+
+school_bigram_graph <- school_bigram_counts %>%
+  filter(n > 8) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
+ggraph(school_bigram_graph, layout = "fr") +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
+  geom_node_point(color = "orange", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
+```
+
+Policy Bi-gram visualizations 
+```{r}
+policy_bigrams_separated <- policy_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+policy_bigram_counts <- policy_bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurence
+# Error will occur if n is outide the range of occurences
+
+policy_bigram_graph <- policy_bigram_counts %>%
+  filter(n > 10) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
+ggraph(policy_bigram_graph, layout = "fr") +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
+  geom_node_point(color = "purple", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
+```
+
+Academic Bi-gram visualizations 
+```{r}
+academic_bigrams_separated <- academic_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+academic_bigram_counts <- academic_bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurence
+# Error will occur if n is outide the range of occurences
+
+academic_bigram_graph <- academic_bigram_counts %>%
+  filter(n > 150) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
+ggraph(academic_bigram_graph, layout = "fr") +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
+  geom_node_point(color = "lightgreen", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
+
+```
+
 ### 2.2.1. Academic papers
@@
 
-```{r, include=FALSE}
-pdfLocation <- "E:/Dr. Paez Articles/with References"
-txtLocation <-  "E:/Dr. Paez Articles/txt"
-
-# Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
-
-fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
-filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
-n <- 1
-
-for (address in filePath)
-{
-doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
-test <- doc$content
-# "file_path_sans_ext(basename())" from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
-# use of 'sep = ""' argument is important to prevent the addition of spaces, which is the default for the paste function 
-newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
-write(test, file = newFile)
-print( paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
-# Creates uniquely id text store in 'Environment'
-assign(paste("text", n, sep = ""), readChar(newFile, file.info(newFile)$size))
-n <- n+1
-}
-```
-
-```{r, include=FALSE}
-# This loop creates a vector of the texts
-text <- vector()
-doc_id <- c(2:n-1)
-
-for (i in seq(1, n-1, 1))
-{
-text[i] <- eval(parse(text = paste("text", i, sep = "")))
-}
-
-# Turns vector into data frame 
-textDF <- data.frame(doc_id, text)
-```
-
-```{r, include=FALSE}
-df_source <- DataframeSource(textDF)
-corpus <- VCorpus(df_source)
-# Example 
-content(corpus[[1]])
-```
-
-```{r, include=FALSE}
-corpus <- tm_map(corpus, stripWhitespace)
-corpus <- tm_map(corpus, content_transformer(tolower))
-
-# Words can also be removed manually by creating a vector of strings 
-#NAwords <- c("school", "transportation", "can", "use", "active")
-#corpus <- tm_map(corpus, removeWords, NAwords)
-#corpus <- tm_map(corpus, removeNumbers)
-
-corpus <- tm_map(corpus, removePunctuation)
-corpus <- tm_map(corpus, removeWords, stopwords("english"))
-
-# Example
-content(corpus[[1]])
-```
-
-```{r, include=FALSE}
-TDM <- TermDocumentMatrix(corpus)
-DTM <- DocumentTermMatrix(corpus)
-matrix1 <- as.matrix(TDM)
-matrix2 <- as.matrix(DTM)
-```
-
 4. Discussion

### 2021-06-24 AST-Framing-Ontario/Data Pre-Processesing Roughwork.rmd
June 24th Changes

--- 2021-06-18 AST-Framing-Ontario/Data Pre-Processesing.rmd
@@
 # location of manually cleaned .txt documents
-cleantxtLocation <- "Cleaned .txt/Policy"
+cleantxtLocation <- "Cleaned .txt/Academic Papers"
 
@@
 bigram_graph <- bigram_counts %>%
-  filter(n > 10) %>%
+  filter(n > 150) %>%
   graph_from_data_frame()
@@
 ```{r}
-bing <- get_sentiments(lexicon = "nrc")
+bing <- get_sentiments(lexicon = "afinn")
 colnames(vocab)[1] <- "word"

### 2021-06-24 AST-Framing-Ontario/Data Pre-Processesing.rmd
June 24th Changes

--- 2021-06-10 AST-Framing-Ontario/Data Pre-Processesing.rmd
@@
 author: "Jason Lam"
-date: "11/03/2021"
-output:
-  html_document:
-    df_print: paged
-  pdf_document: default
-  word_document: default
-params:
-  Academic_Papers_SinglCol: "Texts/Academic Papers Trimmed Single Col"
-  Academic_Papers_DoubCol: "Texts/Academic Papers Trimmed Double Col"
-  Consortia: "Texts/Consortia"
-  Municipalities_Regions: "Texts/Municipalities or Regions"
-  School Boards: "Texts/School Boards"
-  AP_stopW: !r c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
-  Con_stopW: !r c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
-  Mun_Reg_stopW: !r c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
-  SB_stopW: !r c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")
-
+date: "22/06/2021"
+output: pdf_document
 ---
-
-# Introduction
-
-This notebook provides a methodology for converting portable document formats (PDFs) into a text corpus that can be used in natural language processing (NPL) analysis.
-The text corpus is a collection of structured texts which enables analysis using packages such as `topicmodels`.
-This notebook serves as an introduction on how to convert files and conduct a surface level analysis.
-
-Instructions are provided below for processing a single folder of PDF documents, as a step-by-step guide of the processing techniques used.
-Another set of instructions is provided at the end of this notebook for the processing multiple folders simultaneously.
-
 # Preliminaries
@@
 ```
-
-*Parametrize the document to run different corpus* 
-[We could parametrize specific stop words base on the specific files]
-
-# Accessing Data: Grey Literature
-
-Active school travel (AST) and school travel planning (STP) initiatives typically bring together a group of stakeholders from the planning, transportation, public health, and education sectors.
-These stakeholders may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents.
-
-First, we do a preliminary scan of current AST and/or STP projects funded by the Ontario Active School Travel fund to determine which stakeholders are involved in such initiatives.
-We find that AST projects are often led by a school board in collaboration with transportation planners, public health professionals, and regional transportation consortia.
-Non-profit organizations, police services, and advocacy groups are other common stakeholders who play a role in support AST and STP.
-
-Next, we create one folder for each stakeholder group involved in AST and/or STP efforts.
-The folders below were used in the framing analysis; they are provided in this notebook as an example to recreate, modify, or extend our analysis.
-
-For these three following folders, webpages were sourced directly from stakeholder websites from three main groups: transportation consortia, municipalities or regions, and school boards.
-These webpages were saved as PDF documents via the web browser.
-
-Inclusion of webpages was determined based on the following considerations:
-1) It was important that webpages were easy to find as the analysis pertains to how such issues are framed to the public.
-Our interpretation of 'easy to find' are webpages that required no more than 2-4 separate links from the initial browser search.
-2) The analysis focuses on the province of Ontario, not a single municipality or region.
-For this reason, the search was guided by a list of all school boards across the province.
-The websites of each school board were manually searched to determine whether they discussed AST and/or STP.
-3) Consortia and municipalities/regions were organized based on geographic area (i.e., proximity to the school boards).
-
-__Transportation Consortia__
-
-Transportation consortia are dedicated transportation bodies that primarily focus on providing the school busing service to families in their associated region.
-
-In total, 9 webpages were pulled from 7 of the 39 consortia examined in Ontario. Webpages are determined to be relevant if they specifically pertain and/or mention AST or STP.
-
-__Municipalities or Regions__
-
-Municipalities or regions have webpages about transportation plans, programs, and services provided, some of which are not relevant to our analysis.
-Only webpages specifically discussing active travel, AST, or STP were included.
-Webpages were also sourced from associated public health units because they have a direct relation to governing bodies at the municipal or regional level.
-
-In total, 29 webpages were pulled.
-
-__School Boards__
-
-These bodies use funding provided to them by the province to run a collection of schools.
-They prepare the annual budget, hire teachers and staff, supervise the education program, and other tasks to ensure schools are following all regulations set by the Province of Ontario's *Education Act*.
-Only English speaking public and Catholic school boards were considered.
-
-Pages mentioning STP and/or AST were prioritized.
-However, if they did not exist, pages discussing transportation were downloaded instead.
-In total, 32 webpages were pulled from 31 of the 61 school boards examined in Ontario.
-Of the remaining the were not included, 22 linked their respective transportation consortia, 7 did not have pages that meet the criteria, 1 met the criteria but could not be downloaded in a PDF format.
-
-# Accessing Data: Research Literature
-
-__Academic Papers__
-
-A literature search was conducted in _Web of Science_ using "active", "travel", "school" as keywords, and then further narrowed down by discipline "geography", "transportation, "planning".
-
-In total, 233 articles were included from a list of 253. Reasons of exclusions for remaining 20 include unavailablity online, access only on print, and published in non-english.
-
-# Conversion Process
-
-The conversion process for this section can only be conducted on one file at a time.
-We select one of the files provided to use in this package as an example of the process.
-Alternatively, you can use a file relevant to your municipality/region.
-To run multiple files or to create separate corpora, refer to the section below.
-
-## Function to clean text of Ligatures
 
@@
 
-https://stackoverflow.com/questions/17517319/r-replacing-foreign-characters-in-a-string 
 ```{r}
@@
 
-## Searchable PDF files to .txt conversion
+Stop words
+
+```{r}
+AP_stopW <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
+
+Con_stopW <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
+
+ Mun_Reg_stopW <- c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
+
+SB_stopW <- c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")
+
+Policy_StopW <- union(AP_stopW, Mun_Reg_stopW)
+Policy_StopW <- union(Policy_StopW, SB_stopW)
+
+```
+
+# Creating Academic Corpus
 
@@
 
+## Single Column Conversion
+
 ```{r}
-pdfLocation <- params$Academic_Papers_DoubCol
+pdfLocation <- "Texts/Academic Papers Trimmed Single Col"
 
@@
 newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
-print( paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
 
@@
 
-## Creating importing texts to environment
+## Double Column Conversion
 
-imports texts that were manually cleaned
-
-```{r}
-# location of manually cleaned .txt documents
-cleantxtLocation <- "Cleaned .txt/Academic Papers"
-
-cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
-n <- 1 
-for (txt in cleantxtlist) {
-
-# Creates uniquely id text store in 'Environment'
-assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
-n <- n + 1 
-}
-```
-
-## Creating data frame of texts
-
-Creation of a data frame of texts is required prior to conversion to corpus.
-The data frame must contain 'doc_id' and 'text'.
-Additional fields may be included in the data frame, however it will be treated as metadata by the corpus.
-
-```{r}
-# This loop creates a vector of the texts
-text <- vector()
-doc_id <- c(2:n-1)
-
-for (i in seq(1, n-1, 1))
-{
-  #
-text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
-}
-
-# Turns vector into data frame 
-textDF <- data.frame(doc_id, text)
-
-```
-
-## Conversion of data frame to corpus
-
-Next, convert the data frame to a corpus:
-```{r}
-df_source <- DataframeSource(textDF)
-corpus <- VCorpus(df_source)
-# Example 
-content(corpus[[7]])
-```
-
-## Corpus cleaning
-
-Many words should be removed while cleaning the corpus to ensure that the analysis does not pick up on common nouns, adjectives, or indefinite articles.
-Words can be removed manually by creating a vector of strings.
-Add strings to 'NAwords':
-```{r}
-corpus <- tm_map(corpus, stripWhitespace)
-corpus <- tm_map(corpus, content_transformer(tolower))
-
-NAwords <- params$AP_stopW
-corpus <- tm_map(corpus, removeWords, NAwords)
-corpus <- tm_map(corpus, removeNumbers)
-
-corpus <- tm_map(corpus, removePunctuation)
-corpus <- tm_map(corpus, removeWords, stopwords("english"))
-
-# Example
-content(corpus[[7]])
-```
-
-## Term Document Matrix & Document Term Matrix
-
-[Insert brief description of this step]
-
-```{r}
-TDM <- TermDocumentMatrix(corpus)
-DTM <- DocumentTermMatrix(corpus)
-matrix1 <- as.matrix(TDM)
-matrix2 <- as.matrix(DTM)
-
-```
-
-## Natural Languange Processing (NLP) Analysis
-
-NLP is a way to correlate words across a collection of texts or corpus.
-
-### Topic Modelling with Latent Dirichlet Allocation (LDA)
-
-The goal of topic modelling is to identify the re-occurring themes in our corpus quantitatively with code.
-The code below utilizes LDA, an algorithm that when provided a number of discrete topics, `k`, will calculate the likelihood of any given term being generated in a given topic.
-This algorithm runs under the 'bag of words' assumptions with means grammatical structure is not considered.
-Only words are rather considered.
-
-```{r}
-# k represents the number of topics to be generated by the algorithm 
-k <- 4
-lda <- LDA(DTM, k, control = list(seed = 1234))
-
-topics <- tidy(lda, matrix = "beta")
-
-# The value below determines the number of top terms
-top_terms <- topics %>% 
-  group_by(topic) %>% 
-  top_n(15, beta) %>% 
-  ungroup() %>% 
-  arrange(topic, -beta)
-top_terms
-
-# Beta represents the probability of 'term' being generated in topic 'n' 
-# Topics are generated by the LDA algorithm, its is up to the user to interpret the context of the topics 
-terms(lda,15)
-top_terms %>% 
-  mutate(term = reorder_within(term, beta, topic)) %>%
-  ggplot(aes(beta, term, fill = factor(topic))) + 
-  geom_col(show.legend = FALSE) + 
-  facet_wrap(~topic, scales = "free") + 
-  scale_y_reordered() +
-  scale_x_continuous(limits = c(0,0.06))
-
-```
-
-### LDA using multiple seeds
-
-This is a more robust approach since LDA has some random components on how it begins developing its clusters.
-By taking the average of multiple iterations with random seeds, we ....
-[_finish sentence_]
-
-NOTE: RUNNING THE BLOCK BELOW WITH 'Academic Articles'AS INPUT WILL RESULT IN VERY LONG PROCESSING TIME
-
-```{r}
-# 
-# # Generate a random seed to use 
-# numIteration <- 10
-# r <- 1 
-# col <- 4 
-# betaList <- c("beta.0")
-# seeds <- sample.int(10000, numIteration-1)
-# avgtopics <- topics
-# 
-# for (seed1 in seeds){
-#   templda <- LDA(DTM, k, control = list(seed = seed1))
-#   temptopics <- tidy(templda, matrix = "beta")
-#   avgtopics <- left_join(avgtopics, temptopics , by = c("topic", "term"))
-#   colnames(avgtopics)[col] <- paste("beta.", r, sep = "")
-#   betaList <- append(betaList, paste("beta.", r, sep = ""))
-#   r <- r + 1
-#   col <- col + 1 
-# }
-# colnames(avgtopics)[3] <- "beta.0"
-# 
-# avgtopics$beta.mean <- rowMeans(avgtopics[betaList])
-# 
-# # The value below determines the number of top terms
-# avg_top_terms <- avgtopics %>% 
-#   group_by(topic) %>% 
-#   top_n(15, beta.mean) %>% 
-#   ungroup() %>% 
-#   arrange(topic, -beta.mean)
-# avg_top_terms
-# 
-# # Beta represents the probability of 'term' being generated in topic 'n' 
-# # Topics are generated by the LDA algorithm, it's up to the user to interpret the context of the topics 
-# 
-# avg_top_terms %>% 
-#   mutate(term = reorder_within(term, beta.mean, topic)) %>%
-#   ggplot(aes(beta.mean, term, fill = factor(topic))) + 
-#   geom_col(show.legend = FALSE) + 
-#   facet_wrap(~topic, scales = "free") + 
-#   scale_y_reordered() +
-#   scale_x_continuous(limits = c(0,0.06))
-
-```
-
-## Tokenization by n-gram
-
-Here we examine texts based on the structural relationship of a sequence of words.
-We can "tokenize" n-grams, where `n` represents the number of consecutive words, to chart what group of words most frequently occur in our corpus.
-
-```{r}
-# Converting corpus to tidytext data type 
-td_corpus <- tidy(corpus)
-
-# n can be changed 
-test_bigrams <- td_corpus %>%
-  unnest_tokens(bigram, text, token = "ngrams", n = 2)
-
-test_trigrams <- td_corpus %>%
-  unnest_tokens(trigram, text, token = "ngrams", n = 3)
-# Bigrams & Trigrams that are most common
-
-top_bigrams <- test_bigrams %>%
-  count(bigram, sort = TRUE)
-
-top_trigrams <- test_trigrams %>% 
-  count(trigram, sort = TRUE)
-
-top_bigrams
-top_trigrams
-```
-
-Bi-gram visualizations 
-```{r}
-bigrams_separated <- test_bigrams %>%
-  separate(bigram, c("word1", "word2"), sep = " ")
-
-bigram_counts <- bigrams_separated %>% 
-  count(word1, word2, sort = TRUE)
-
-# Adjust the parameter below to filter out based on number of occurence
-# Error will occur if n is outide the range of occurences 
-bigram_graph <- bigram_counts %>%
-  filter(n > 5) %>%
-  graph_from_data_frame()
-
-set.seed(2021)
-
-ggraph(bigram_graph, layout = "fr") +
-  geom_edge_link() +
-  geom_node_point() +
-  geom_node_text(aes(label = name), vjust = 1, hjust = 1)
-
-```
-
-## Using TDM to make a word cloud
-
-Word cloud is a nice visual way to view the most common words in your text document matrix
-
-```{r}
-v <- sort(rowSums(matrix1), decreasing= TRUE)
-d <- data.frame(word = names(v), freq=v)
-set.seed(4321)
-wordcloud(d$word, d$freq, min.freq = 10, max.words = 50, random.order = FALSE, rot.per = 0.5, random.color = TRUE)
-```
-
-# GloVe Word Embeddings
-
-https://m-clark.github.io/text-analysis-with-R/word-embeddings.html
-
-```{r}
-# Create new data frame with the cleaned corpus 
-cleanTextDF <- data.frame(text = sapply(corpus, as.character), stringsAsFactors = FALSE)
-
-it_train = itoken(cleanTextDF$text, progressbar = FALSE)
-vocab = create_vocabulary(it_train)
-
-# Cut out terms that have a minimum count of 5 
-vocab <- prune_vocabulary(vocab, term_count_min = 5)
-vocab
-
-vectorizer <- vocab_vectorizer(vocab)
-tcm <- create_tcm(it_train, vectorizer, skip_grams_window = 10)
-
-glove = GlobalVectors$new(rank = 50, x_max = 10)
-main = glove$fit_transform(tcm, n_iter = 10, convergence_tol = 0.001)
-context = glove$components
-
-word_vectors = main + t(context)
-
-#safe = word_vectors["wellbeing", , drop = FALSE] - word_vectors["physical", , drop = FALSE] + word_vectors["mental", , drop = FALSE]
-
-#cos_sim = sim2(x = word_vectors, y = safe, method = "cosine")
-
-#head(sort(cos_sim[,1], decreasing = TRUE), 10)
-```
-
-# Multi-Files
-
-Clear Environment 
-```{r}
-rm(list = ls())
-```
-
-`masterFolder` will be the location of your sub-folders, containing your PDFs.
-Unlike in 'PDF to Corpus.Rmd' you do not need to create .txt folder corresponding to each PDF folder, this is done automatically by the code.
-
-IMPORTANT: The names of the folders cannot contain the consecutive characters `txt`, the code filters out those folders. 
-NOTE: The order of files below will also be the order the corpus are created, the index will match the corpus number 
-```{r}
-masterFolder <- "Texts"
-
-subFolders <- list.files(masterFolder, full.names=TRUE)
-# if txt folder already exists from previous execution of code this ensures it is not added to subfolders 
-# The limitation is that your file name, at any point cannot contain the sequence of characters "txt" as it will be flagged as a non-pdf subfolder
-
-subFolders <- subFolders[grep(x =list.files(masterFolder, full.names=TRUE), pattern =  "txt", invert = TRUE)]
-subFolders
-```
-
-## Function to clean text of Ligatures
-```{r}
-to.plain <- function(s) {
-
-   # 1 character substitutions
-   old1 <- "šžþàáâãäåçèéêëìíîïðñòóôõöùúûüý"
-   new1 <- "szyaaaaaaceeeeiiiidnooooouuuuy"
-   s1 <- chartr(old1, new1, s)
-
-   # 2 character substitutions
-   old2 <- c("<U+FB03>", "<U+FB01>", "<U+FB00>", "<U+FB02>")
-   new2 <- c("ffi", "fi", "ff", "fl")
-   s2 <- s1
-   for(i in seq_along(old2)) s2 <- gsub(old2[i], new2[i], s2, fixed = TRUE)
-
-   s2
-}
-```
-
-'n' represents the number of subfolders and subsequently corpora that you intent the produce. 'corpusKey' will indicate the numbering convention of the corpora and analysis in subsequent code. 
-```{r}
-# n - number of corpora
-n <- 5
-corpusNum <- seq(1, n, 1)
-corpusKey <- data.frame(corpusNum, subFolders)
-```
-
-Corpora will be cleaned for white spaces, punctuation, English stop words, and converted to lowercase.
-Any additional stop words will need to be removed manually as the user sees fit.
-'corpusKey' is a data frame that indicates which file a corpus was derived from.
-```{r}
-# Stop words for each of the corpora, or based on how your directory organizes files 
-# Add stop words if you have more than 4 corpora
-
-NAwords1 <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
-
-NAwords2 <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
-
-NAwords3 <- c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
-
-NAwords4 <- c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")
-
-NAwords5 <- c()
-
-# Iterating through each subfolders 
-m <- 1
-for (subFolder in subFolders){
-
-  pdfLocation <- subFolder
-  if (file.exists(paste(pdfLocation, "txt"))){
-    txtLocation <- paste(pdfLocation, "txt")
-  }else{
-    dir.create(paste(pdfLocation, "txt"))
-    txtLocation <- paste(pdfLocation, "txt")
-  }
-  fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
-  filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
-  n <- 1
-
-  for (address in filePath)
-{
-doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
-test <- doc$content
-
-# "file_path_sans_ext(basename())" from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
-# use of 'sep = ""' argument is important to prevent the addition of spaces, which is the default for the paste function 
-newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
-write(test, file = newFile)
-
-####print(paste(file_path_sans_ext(basename(address)), ".txt Has been created", sep = ""))
-
-# Creates uniquely id text store in 'Environment'
-assign(paste("text", n, sep = ""), readChar(newFile, file.info(newFile)$size))
-n <- n+1
-  }
-
-text <- vector()
-doc_id <- c(2:n-1)
-
-for (i in seq(1, n-1, 1))
-{
-text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
-}
-
-textDF <- data.frame(doc_id, text)
-
-temp_df_source <- DataframeSource(textDF)
-tempCorpus <- VCorpus(temp_df_source)
-
-# corpus cleaning 
-tempCorpus <- tm_map(tempCorpus, stripWhitespace)
-tempCorpus <- tm_map(tempCorpus, content_transformer(tolower))
-tempCorpus <- tm_map(tempCorpus, removePunctuation)
-tempCorpus <- tm_map(tempCorpus, removeWords, stopwords("english"))
-tempCorpus <- tm_map(tempCorpus, removeWords, eval(parse(text = paste("NAwords", m, sep = ""))))
-tempCorpus <- tm_map(tempCorpus, removeNumbers)
-
-assign(paste("cleanTextDF", m, sep = ""), data.frame(text = sapply(tempCorpus, as.character), stringsAsFactors = FALSE))
-
-assign(paste("corpus", m, sep= ""), tempCorpus)
-
-# removed tempory texts for next iteration
-m <- m + 1 
-rm(list=ls(pattern = "^text"))
-
-}
-
-rm(temp_df_source, tempCorpus, address, doc_id, fileBaseNames, filePath, i, m, newFile, pdfLocation, subFolder, test, txtLocation)
-```
-
-Creating Term-Document Matrix and Document-Term Matrix with the fully cleaned corpora.
-```{r}
-for (i in seq(1, n, 1))
-{
-tempCorpus <-  eval(parse(text = paste("corpus", i, sep = "")))
-TDM <- TermDocumentMatrix(tempCorpus)
-DTM <- DocumentTermMatrix(tempCorpus)
-matrix1 <- as.matrix(TDM)
-matrix2 <- as.matrix(DTM)
-
-assign(paste("corpus", i, "TDM", sep= ""), matrix1)
-assign(paste("corpus", i, "DTM", sep= ""), matrix2)
-
-}
-rm(matrix1, matrix2)
-```
-
-# Vocabulary
-
-```{r}
-n <- 5 
-for (i in seq(1, n, 1))
-{
-  tempDF <- eval(parse(text = paste("cleanTextDF", i, sep = "")))
-  it_train = itoken(tempDF$text, progressbar = FALSE)
-  assign(paste("vocab", i, sep= ""), create_vocabulary(it_train))
-  tempVocab <- create_vocabulary(it_train)
-  assign(paste("vocab", i, sep= ""), prune_vocabulary(tempVocab, term_count_min = 5))
-}
-
-rm(tempVocab)
-```
-
-# Vector Sort
-
-```{r}
-
-paste(sort(c("tm", "readr", "tools", "dplyr", "tidytext", "topicmodels", "ggplot2", "wordcloud", "word2vec", "pdftools", "reshape2", "text2vec", "stringr", "tidyr", "igraph")), collapse = " ")
-
-```
-
-# Coverts double coloumn documents to single column
-
-The first chuck sets up the function used in the second section.
-
-https://stackoverflow.com/questions/42541849/extract-text-from-two-column-pdf-with-r 
 ```{r}
@@
 
+## Imports texts that were manually cleaned
+
+```{r}
+# location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/Academic Papers"
+
+cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
+n <- 1 
+for (txt in cleantxtlist) {
+
+# Creates uniquely id text store in 'Environment'
+assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
+n <- n + 1 
+}
+```
+
+## Creating data frame of texts
+
+Creation of a data frame of texts is required prior to conversion to corpus.
+The data frame must contain 'doc_id' and 'text'.
+Additional fields may be included in the data frame, however it will be treated as metadata by the corpus.
+
+```{r}
+# This loop creates a vector of the texts
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+  #
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
+}
+
+# Turns vector into data frame 
+textDF <- data.frame(doc_id, text)
+
+```
+
+## Conversion of data frame to corpus
+
+Next, convert the data frame to a corpus:
+```{r}
+df_source <- DataframeSource(textDF)
+academic_corpus <- VCorpus(df_source)
+```
+
+## Corpus cleaning
+
+Many words should be removed while cleaning the corpus to ensure that the analysis does not pick up on common nouns, adjectives, or indefinite articles.
+Words can be removed manually by creating a vector of strings.
+The Argument 'AP_stopW' on line 224 accomplishes that.
+Refer to line 63 for stop words.
+
+```{r}
+academic_corpus <- tm_map(academic_corpus, stripWhitespace)
+academic_corpus <- tm_map(academic_corpus, content_transformer(tolower))
+
+academic_corpus <- tm_map(academic_corpus, removeWords, AP_stopW)
+academic_corpus <- tm_map(academic_corpus, removeNumbers)
+
+academic_corpus <- tm_map(academic_corpus, removePunctuation)
+academic_corpus <- tm_map(academic_corpus, removeWords, stopwords("english"))
+
+```
+
+## Cleaning up Environment
+
 ```{r}
 rm(list=ls(pattern = "^text"))
+rm(df_source)
 ```
+
+# Creating Municipal Corpus
+
+# Single Column Conversion
+
+```{r}
+pdfLocation <- "Texts/Municipalities or Regions"
+
+# Creates folder for .txt files
+if (file.exists(paste(pdfLocation, "txt"))){
+    txtLocation <- paste(pdfLocation, "txt")
+  }else{
+    dir.create(paste(pdfLocation, "txt"))
+    txtLocation <- paste(pdfLocation, "txt")
+  }
+
+# Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
+fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
+filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
+n <- 1
+
+for (address in filePath)
+{
+doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
+test <- doc$content
+
+# `file_path_sans_ext(basename())` from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
+
+# use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
+newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
+
+write(test, file = newFile)
+
+n <- n+1
+}
+```
+
+## Imports texts that were manually cleaned
+
+```{r}
+# location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/Municipalities or Regions"
+
+cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
+n <- 1 
+for (txt in cleantxtlist) {
+
+# Creates uniquely id text store in 'Environment'
+assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
+n <- n + 1 
+}
+```
+
+## Creating data frame of texts
+
+```{r}
+# This loop creates a vector of the texts
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+  #
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
+}
+
+# Turns vector into data frame 
+textDF <- data.frame(doc_id, text)
+
+```
+
+## Conversion of data frame to corpus
+
+Next, convert the data frame to a corpus:
+```{r}
+df_source <- DataframeSource(textDF)
+municipal_corpus <- VCorpus(df_source)
+```
+
+## Corpus cleaning
+
+```{r}
+municipal_corpus <- tm_map(municipal_corpus, stripWhitespace)
+municipal_corpus <- tm_map(municipal_corpus, content_transformer(tolower))
+
+municipal_corpus <- tm_map(municipal_corpus, removeWords, Mun_Reg_stopW)
+municipal_corpus <- tm_map(municipal_corpus, removeNumbers)
+
+municipal_corpus <- tm_map(municipal_corpus, removePunctuation)
+municipal_corpus <- tm_map(municipal_corpus, removeWords, stopwords("english"))
+
+```
+
+## Cleaning up Environment
+
+```{r}
+rm(list=ls(pattern = "^text"))
+rm(df_source)
+```
+
+# Creating Consortia Corpus
+
+## Single Column Conversion
+
+```{r}
+pdfLocation <- "Texts/Consortia"
+
+# Creates folder for .txt files
+if (file.exists(paste(pdfLocation, "txt"))){
+    txtLocation <- paste(pdfLocation, "txt")
+  }else{
+    dir.create(paste(pdfLocation, "txt"))
+    txtLocation <- paste(pdfLocation, "txt")
+  }
+
+# Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
+fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
+filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
+n <- 1
+
+for (address in filePath)
+{
+doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
+test <- doc$content
+
+# `file_path_sans_ext(basename())` from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
+
+# use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
+newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
+
+write(test, file = newFile)
+
+n <- n+1
+}
+```
+
+## Imports texts that were manually cleaned
+
+```{r}
+# location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/Consortia"
+
+cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
+n <- 1 
+for (txt in cleantxtlist) {
+
+# Creates uniquely id text store in 'Environment'
+assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
+n <- n + 1 
+}
+```
+
+## Creating data frame of texts
+
+```{r}
+# This loop creates a vector of the texts
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+  #
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
+}
+
+# Turns vector into data frame 
+textDF <- data.frame(doc_id, text)
+
+```
+
+## Conversion of data frame to corpus
+
+Next, convert the data frame to a corpus:
+```{r}
+df_source <- DataframeSource(textDF)
+consortium_corpus <- VCorpus(df_source)
+```
+
+## Corpus cleaning
+
+```{r}
+consortium_corpus <- tm_map(consortium_corpus, stripWhitespace)
+consortium_corpus <- tm_map(consortium_corpus, content_transformer(tolower))
+
+consortium_corpus <- tm_map(consortium_corpus, removeWords, Con_stopW)
+consortium_corpus <- tm_map(consortium_corpus, removeNumbers)
+
+consortium_corpus <- tm_map(consortium_corpus, removePunctuation)
+consortium_corpus <- tm_map(consortium_corpus, removeWords, stopwords("english"))
+
+```
+
+## Cleaning up Environment
+
+```{r}
+rm(list=ls(pattern = "^text"))
+rm(df_source)
+```
+
+# Creating School Board Corpus
+
+## Single Column Conversion
+
+```{r}
+pdfLocation <- "Texts/School Boards"
+
+# Creates folder for .txt files
+if (file.exists(paste(pdfLocation, "txt"))){
+    txtLocation <- paste(pdfLocation, "txt")
+  }else{
+    dir.create(paste(pdfLocation, "txt"))
+    txtLocation <- paste(pdfLocation, "txt")
+  }
+
+# Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
+fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
+filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
+n <- 1
+
+for (address in filePath)
+{
+doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
+test <- doc$content
+
+# `file_path_sans_ext(basename())` from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
+
+# use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
+newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
+
+write(test, file = newFile)
+
+n <- n+1
+}
+```
+
+## Imports texts that were manually cleaned
+
+```{r}
+# location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/School Boards"
+
+cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
+n <- 1 
+for (txt in cleantxtlist) {
+
+# Creates uniquely id text store in 'Environment'
+assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
+n <- n + 1 
+}
+```
+
+## Creating data frame of texts
+
+```{r}
+# This loop creates a vector of the texts
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+  #
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
+}
+
+# Turns vector into data frame 
+textDF <- data.frame(doc_id, text)
+
+```
+
+## Conversion of data frame to corpus
+
+Next, convert the data frame to a corpus:
+```{r}
+df_source <- DataframeSource(textDF)
+school_corpus <- VCorpus(df_source)
+```
+
+## Corpus cleaning
+
+```{r}
+school_corpus <- tm_map(school_corpus, stripWhitespace)
+school_corpus <- tm_map(school_corpus, content_transformer(tolower))
+
+school_corpus <- tm_map(school_corpus, removeWords, Con_stopW)
+school_corpus <- tm_map(school_corpus, removeNumbers)
+
+school_corpus <- tm_map(school_corpus, removePunctuation)
+school_corpus <- tm_map(school_corpus, removeWords, stopwords("english"))
+
+```
+
+## Cleaning up Environment
+
+```{r}
+rm(list=ls(pattern = "^text"))
+rm(df_source)
+```
+
+# Creating Policy Corpus
+
+## Imports texts that were manually cleaned
+
+```{r}
+# location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/Policy"
+
+cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
+n <- 1 
+for (txt in cleantxtlist) {
+
+# Creates uniquely id text store in 'Environment'
+assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
+n <- n + 1 
+}
+```
+
+## Creating data frame of texts
+
+```{r}
+# This loop creates a vector of the texts
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+  #
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
+}
+
+# Turns vector into data frame 
+textDF <- data.frame(doc_id, text)
+
+```
+
+## Conversion of data frame to corpus
+
+Next, convert the data frame to a corpus:
+```{r}
+df_source <- DataframeSource(textDF)
+policy_corpus <- VCorpus(df_source)
+```
+
+## Corpus cleaning
+
+```{r}
+policy_corpus <- tm_map(policy_corpus, stripWhitespace)
+policy_corpus <- tm_map(policy_corpus, content_transformer(tolower))
+
+policy_corpus <- tm_map(policy_corpus, removeWords,Policy_StopW)
+policy_corpus <- tm_map(policy_corpus, removeNumbers)
+
+policy_corpus <- tm_map(policy_corpus, removePunctuation)
+policy_corpus <- tm_map(policy_corpus, removeWords, stopwords("english"))
+
+```
+
+# Exporting the Corpora
+
+```{r}
+save(academic_corpus, file= "Corpus .rda/academic_corpus.rda")
+save(consortium_corpus, file= "Corpus .rda/consortium_corpus.rda")
+save(municipal_corpus, file= "Corpus .rda/municipal_corpus.rda")
+save(school_corpus, file= "Corpus .rda/school_corpus.rda")
+save(policy_corpus, file= "Corpus .rda/policy_corpus.rda")
+```

### 2021-06-24 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Last Update before June 14 Meeting

@@
 ```{r, include=FALSE}
+library(DiagrammeR)
+library(dplyr)
+library(ggraph)
+library(ggplot2)
+library(igraph)
+library(kableExtra)
+library(pdftools)
+library(readr)
+library(reshape2)
+library(stringr)
+library(text2vec)
+library(textdata)
+library(tidyr)
+library(tidytext)
 library(tm) 
-library(readr)
 library(tools)
-library(DiagrammeR)
-library(kableExtra)
+library(topicmodels)
+library(widyr)
+library(word2vec)
+library(wordcloud)
 ```
@@
 
+Academic corpus vocabulary 
+```{r}
+# Create new data frame with the cleaned corpus 
+AcademicTextDF <- data.frame(text = sapply(academic_corpus, as.character), stringsAsFactors = FALSE)
+
+it_train = itoken(AcademicTextDF$text, progressbar = FALSE)
+academic_vocab = create_vocabulary(it_train)
+
+# Cut out terms that have a minimum count of 5 
+academic_vocab <- prune_vocabulary(academic_vocab, term_count_min = 5)
+academic_vocab
+```
+
 ### 2.2.1. Academic papers

### 2021-06-24 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Moved analysis code to Results section

--- 2021-06-24 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
@@
 bibliography: mybibfile.bib
-#linenumbers: true
+linenumbers: false
 #numbersections: true
@@
 
-```{r, include=FALSE}
+```{r load-packages, include=FALSE}
+library(DiagrammeR)
+library(dplyr)
+library(ggraph)
+library(ggplot2)
+library(igraph)
+library(kableExtra)
+library(pdftools)
+library(readr)
+library(reshape2)
+library(stringr)
+library(text2vec)
+library(textdata)
+library(tidyr)
+library(tidytext)
 library(tm) 
-library(readr)
 library(tools)
-library(DiagrammeR)
-library(kableExtra)
+library(topicmodels)
+library(widyr)
+library(word2vec)
+library(wordcloud)
 ```
+
+```{r load-data, include=FALSE}
+load(file= "Corpus .rda/academic_corpus.rda")
+load(file= "Corpus .rda/municipal_corpus.rda")
+load(file= "Corpus .rda/consortium_corpus.rda")
+load(file= "Corpus .rda/school_corpus.rda")
+load(file= "Corpus .rda/policy_corpus.rda")
+```
+
+```{r package-bib, include=FALSE}
+# This function is used to write a bibliography for the `R` packages used in the paper
+knitr::write_bib(file = 'packages.bib')
+```
+
+  ***Background***:  
+  ***Methods***:  
+  ***Results***: 
+  ***Conclusions***:
+
+\newpage
 
@@
 
-2. Methods
+2. Data
 ===============
 
-## 2.1. Case study: Ontario, Canada
+## 2.1. Data retrieval
 
-In 2017, the provincial government of Ontario issued funding to Green Communities Canada (GCC), a non-profit organization, to launch the _Ontario Active School Travel_ (OAST) program.
-The program provides funding for school and community-based initiatives and supports stakeholders in municipalities across the province to implement STP and other interventions aimed at increasing AST.
-As of 2021, OAST has funded _X_ projects in Ontario.
-GCC continues its work by providing resources for interested stakeholders and funding projects across Ontario led by collaborative groups involving school boards, municipal or regional governments, and regional transportation consortia.
-The latter are dedicated transportation bodies that deliver efficient and effective transportation services, which generally focuses on providing the school busing service to families in their associated region.
-
-## 2.2. Data retrieval
-
-### 2.2.1. Policy documents
+### 2.1.1. Policy documents
 
@@
 
-```{r search-results, echo=FALSE}
+```{r policy-documents, echo=FALSE}
 data_tbl <- data.frame(
-  Stakeholder = c("English school boards", "Municipal or regional governments", "Transportation Consortia"),
+  Stakeholder = c("English school boards", "Municipalities or regions", "Transportation consortia"),
   Total = c("62", "62", "39"),
@@
       booktabs = TRUE,
-      caption = "\\label{tab:search-results}Search results from the main stakeholder groups.") %>%
+      caption = "\\label{tab:search-results}Search results from the main STP stakeholder groups.") %>%
   kable_paper(full_width = F) %>%
@@
   kable_styling(latex_options = c("striped", "scale_down"))
-```
-
-Loading in clean corpus. These are the products of 'Data Pre-Processing.Rmd'
-```{r}
-load(file= "Corpus .rda/academic_corpus.rda")
-load(file= "Corpus .rda/municipal_corpus.rda")
-load(file= "Corpus .rda/consortium_corpus.rda")
-load(file= "Corpus .rda/school_corpus.rda")
-load(file= "Corpus .rda/policy_corpus.rda")
-```
-
-Municipal Bi/Trigrams
-```{r}
-# Converting corpus to tidytext data type 
-td_municipal_corpus <- tidy(municipal_corpus)
-
-# n can be changed 
-municipal_bigrams <- td_municipal_corpus %>%
-  unnest_tokens(bigram, text, token = "ngrams", n = 2)
-
-municipal_trigrams <- td_municipal_corpus %>%
-  unnest_tokens(trigram, text, token = "ngrams", n = 3)
-# Bigrams & Trigrams that are most common
-
-top_municipal_bigrams <- municipal_bigrams %>%
-  count(bigram, sort = TRUE)
-
-top_municipal_trigrams <- municipal_trigrams %>% 
-  count(trigram, sort = TRUE)
-
-top_municipal_bigrams
-top_municipal_trigrams
-```
-
-Consortium Bi/Trigrams
-```{r}
-# Converting corpus to tidytext data type 
-td_consortium_corpus <- tidy(consortium_corpus)
-
-# n can be changed 
-consortium_bigrams <- td_consortium_corpus %>%
-  unnest_tokens(bigram, text, token = "ngrams", n = 2)
-
-consortium_trigrams <- td_consortium_corpus %>%
-  unnest_tokens(trigram, text, token = "ngrams", n = 3)
-# Bigrams & Trigrams that are most common
-
-top_consortium_bigrams <- consortium_bigrams %>%
-  count(bigram, sort = TRUE)
-
-top_consortium_trigrams <- consortium_trigrams %>% 
-  count(trigram, sort = TRUE)
-
-top_consortium_bigrams
-top_consortium_trigrams
-```
-
-School board Bi/Trigrams
-```{r}
-# Converting corpus to tidytext data type 
-td_school_corpus <- tidy(school_corpus)
-
-# n can be changed 
-school_bigrams <- td_school_corpus %>%
-  unnest_tokens(bigram, text, token = "ngrams", n = 2)
-
-school_trigrams <- td_school_corpus %>%
-  unnest_tokens(trigram, text, token = "ngrams", n = 3)
-# Bigrams & Trigrams that are most common
-
-top_school_bigrams <- school_bigrams %>%
-  count(bigram, sort = TRUE)
-
-top_school_trigrams <- school_trigrams %>% 
-  count(trigram, sort = TRUE)
-
-top_school_bigrams
-top_school_trigrams
-```
-
-Policy Bi/Trigrams
-```{r}
-# Converting corpus to tidytext data type 
-td_policy_corpus <- tidy(policy_corpus)
-
-# n can be changed 
-policy_bigrams <- td_policy_corpus %>%
-  unnest_tokens(bigram, text, token = "ngrams", n = 2)
-
-policy_trigrams <- td_policy_corpus %>%
-  unnest_tokens(trigram, text, token = "ngrams", n = 3)
-# Bigrams & Trigrams that are most common
-
-top_policy_bigrams <- policy_bigrams %>%
-  count(bigram, sort = TRUE)
-
-top_policy_trigrams <- policy_trigrams %>% 
-  count(trigram, sort = TRUE)
-
-top_policy_bigrams
-top_policy_trigrams
-```
-
-Academic Bi/Trigrams
-```{r}
-# Converting corpus to tidytext data type 
-td_academic_corpus <- tidy(academic_corpus)
-
-# n can be changed 
-academic_bigrams <- td_academic_corpus %>%
-  unnest_tokens(bigram, text, token = "ngrams", n = 2)
-
-academic_trigrams <- td_academic_corpus %>%
-  unnest_tokens(trigram, text, token = "ngrams", n = 3)
-# Bigrams & Trigrams that are most common
-
-top_academic_bigrams <- academic_bigrams %>%
-  count(bigram, sort = TRUE)
-
-top_academic_trigrams <- academic_trigrams %>% 
-  count(trigram, sort = TRUE)
-
-top_academic_bigrams
-top_academic_trigrams
-```
-
-Municipal Bi-gram visualizations 
-```{r}
-municipal_bigrams_separated <- municipal_bigrams %>%
-  separate(bigram, c("word1", "word2"), sep = " ")
-
-municipal_bigram_counts <- municipal_bigrams_separated %>% 
-  count(word1, word2, sort = TRUE)
-
-# Adjust the parameter below to filter out based on number of occurence
-# Error will occur if n is outide the range of occurences
-
-municipal_bigram_graph <- municipal_bigram_counts %>%
-  filter(n > 8) %>%
-  graph_from_data_frame()
-
-set.seed(2021)
-
-a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
-
-ggraph(municipal_bigram_graph, layout = "fr") +
-  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
-                 arrow = a, end_cap = circle(.07, 'inches')) +
-  geom_node_point(color = "lightblue", size = 4) +
-  geom_node_text(aes(label = name), repel = TRUE) + 
-  theme_void()
-```
-
-Consortium Bi-gram visualizations 
-```{r}
-consortium_bigrams_separated <- consortium_bigrams %>%
-  separate(bigram, c("word1", "word2"), sep = " ")
-
-consortium_bigram_counts <- consortium_bigrams_separated %>% 
-  count(word1, word2, sort = TRUE)
-
-# Adjust the parameter below to filter out based on number of occurence
-# Error will occur if n is outide the range of occurences
-
-consortium_bigram_graph <- consortium_bigram_counts %>%
-  filter(n > 5) %>%
-  graph_from_data_frame()
-
-set.seed(2021)
-
-a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
-
-ggraph(consortium_bigram_graph, layout = "fr") +
-  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
-                 arrow = a, end_cap = circle(.07, 'inches')) +
-  geom_node_point(color = "red", size = 4) +
-  geom_node_text(aes(label = name), repel = TRUE) + 
-  theme_void()
-```
-
-School Board Bi-gram visualizations 
-```{r}
-school_bigrams_separated <- school_bigrams %>%
-  separate(bigram, c("word1", "word2"), sep = " ")
-
-school_bigram_counts <- school_bigrams_separated %>% 
-  count(word1, word2, sort = TRUE)
-
-# Adjust the parameter below to filter out based on number of occurence
-# Error will occur if n is outide the range of occurences
-
-school_bigram_graph <- school_bigram_counts %>%
-  filter(n > 8) %>%
-  graph_from_data_frame()
-
-set.seed(2021)
-
-a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
-
-ggraph(school_bigram_graph, layout = "fr") +
-  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
-                 arrow = a, end_cap = circle(.07, 'inches')) +
-  geom_node_point(color = "orange", size = 4) +
-  geom_node_text(aes(label = name), repel = TRUE) + 
-  theme_void()
-```
-
-Policy Bi-gram visualizations 
-```{r}
-policy_bigrams_separated <- policy_bigrams %>%
-  separate(bigram, c("word1", "word2"), sep = " ")
-
-policy_bigram_counts <- policy_bigrams_separated %>% 
-  count(word1, word2, sort = TRUE)
-
-# Adjust the parameter below to filter out based on number of occurence
-# Error will occur if n is outide the range of occurences
-
-policy_bigram_graph <- policy_bigram_counts %>%
-  filter(n > 10) %>%
-  graph_from_data_frame()
-
-set.seed(2021)
-
-a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
-
-ggraph(policy_bigram_graph, layout = "fr") +
-  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
-                 arrow = a, end_cap = circle(.07, 'inches')) +
-  geom_node_point(color = "purple", size = 4) +
-  geom_node_text(aes(label = name), repel = TRUE) + 
-  theme_void()
-```
-
-Academic Bi-gram visualizations 
-```{r}
-academic_bigrams_separated <- academic_bigrams %>%
-  separate(bigram, c("word1", "word2"), sep = " ")
-
-academic_bigram_counts <- academic_bigrams_separated %>% 
-  count(word1, word2, sort = TRUE)
-
-# Adjust the parameter below to filter out based on number of occurence
-# Error will occur if n is outide the range of occurences
-
-academic_bigram_graph <- academic_bigram_counts %>%
-  filter(n > 150) %>%
-  graph_from_data_frame()
-
-set.seed(2021)
-
-a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
-
-ggraph(academic_bigram_graph, layout = "fr") +
-  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
-                 arrow = a, end_cap = circle(.07, 'inches')) +
-  geom_node_point(color = "lightgreen", size = 4) +
-  geom_node_text(aes(label = name), repel = TRUE) + 
-  theme_void()
-
 ```
@@
 In the final step before analysis, we removed all blank spaces, punctuation, capitalization, and numbers.
-English stop words, as identified in a predetermined list by Lewis et al.
-[@R-tm], were removed.
+English stop words, which are common words such as _and_ or _the_ as identified in a predetermined list by Lewis et al.
+[@R-tm] and other frequent terms in the documents like places were removed from the corpus.
 
-## 2.3. Topic modelling
+3. Methods
+===============
 
-## 2.4. Summative content Analysis
+## 3.1. Case study: Ontario, Canada
 
-## 2.5. Reproducibility
+In 2017, the provincial government of Ontario issued funding to Green Communities Canada (GCC), a non-profit organization, to launch the _Ontario Active School Travel_ (OAST) program.
+The program provides funding for school and community-based initiatives and supports stakeholders in municipalities across the province to implement STP and other interventions aimed at increasing AST.
+As of 2021, OAST has funded _X_ projects in Ontario.
+GCC continues its work by providing resources for interested stakeholders and funding projects across Ontario led by collaborative groups involving school boards, municipal or regional governments, and regional transportation consortia.
+The latter are dedicated transportation bodies that deliver efficient and effective transportation services, which generally focuses on providing the school busing service to families in their associated region.
+
+## 3.2. Topic modelling
+
+## 3.3. Summative content analysis
+
+## 3.4. Reproducibility
 
@@
 
-3. Results
+4. Results
 ===============
 
-## 3.1. Word Frequency
+```{r city-bigrams, echo=FALSE}
+# Converting corpus to tidytext data type 
+td_municipal_corpus <- tidy(municipal_corpus)
 
-## 3.2. Bigrams and Correlations
+# n can be changed 
+municipal_bigrams <- td_municipal_corpus %>%
+  unnest_tokens(bigram, text, token = "ngrams", n = 2)
 
-## 3.3. Policy content
+municipal_trigrams <- td_municipal_corpus %>%
+  unnest_tokens(trigram, text, token = "ngrams", n = 3)
 
-4. Discussion
+# Bigrams and trigrams that are most common 
+top_municipal_bigrams <- municipal_bigrams %>%
+  count(bigram, sort = TRUE)
+
+top_municipal_trigrams <- municipal_trigrams %>% 
+  count(trigram, sort = TRUE)
+
+top_municipal_bigrams
+top_municipal_trigrams
+```
+
+```{r consortia-bigrams, echo=FALSE}
+
+# Converting corpus to tidytext data type 
+td_consortium_corpus <- tidy(consortium_corpus)
+
+# n can be changed 
+consortium_bigrams <- td_consortium_corpus %>%
+  unnest_tokens(bigram, text, token = "ngrams", n = 2)
+
+consortium_trigrams <- td_consortium_corpus %>%
+  unnest_tokens(trigram, text, token = "ngrams", n = 3)
+
+# Bigrams and trigrams that are most common 
+top_consortium_bigrams <- consortium_bigrams %>%
+  count(bigram, sort = TRUE)
+
+top_consortium_trigrams <- consortium_trigrams %>% 
+  count(trigram, sort = TRUE)
+
+top_consortium_bigrams
+top_consortium_trigrams
+```
+
+```{r school-bigrams, echo=FALSE}
+
+# Converting corpus to tidytext data type 
+td_school_corpus <- tidy(school_corpus)
+
+# n can be changed 
+school_bigrams <- td_school_corpus %>%
+  unnest_tokens(bigram, text, token = "ngrams", n = 2)
+
+school_trigrams <- td_school_corpus %>%
+  unnest_tokens(trigram, text, token = "ngrams", n = 3)
+
+# Bigrams and trigrams that are most common 
+top_school_bigrams <- school_bigrams %>%
+  count(bigram, sort = TRUE)
+
+top_school_trigrams <- school_trigrams %>% 
+  count(trigram, sort = TRUE)
+
+top_school_bigrams
+top_school_trigrams
+```
+
+```{r policy-bigrams, echo=FALSE}
+
+# Converting corpus to tidytext data type 
+td_policy_corpus <- tidy(policy_corpus)
+
+# n can be changed 
+policy_bigrams <- td_policy_corpus %>%
+  unnest_tokens(bigram, text, token = "ngrams", n = 2)
+
+policy_trigrams <- td_policy_corpus %>%
+  unnest_tokens(trigram, text, token = "ngrams", n = 3)
+
+# Bigrams and trigrams that are most common 
+top_policy_bigrams <- policy_bigrams %>%
+  count(bigram, sort = TRUE)
+
+top_policy_trigrams <- policy_trigrams %>% 
+  count(trigram, sort = TRUE)
+
+top_policy_bigrams
+top_policy_trigrams
+```
+
+```{r academic-bigrams, echo=FALSE}
+
+# Converting corpus to tidytext data type 
+td_academic_corpus <- tidy(academic_corpus)
+
+# n can be changed 
+academic_bigrams <- td_academic_corpus %>%
+  unnest_tokens(bigram, text, token = "ngrams", n = 2)
+
+academic_trigrams <- td_academic_corpus %>%
+  unnest_tokens(trigram, text, token = "ngrams", n = 3)
+
+# Bigrams and trigrams that are most common 
+top_academic_bigrams <- academic_bigrams %>%
+  count(bigram, sort = TRUE)
+
+top_academic_trigrams <- academic_trigrams %>% 
+  count(trigram, sort = TRUE)
+
+top_academic_bigrams
+top_academic_trigrams
+```
+
+```{r city-visual, echo=FALSE}
+municipal_bigrams_separated <- municipal_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+municipal_bigram_counts <- municipal_bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurrence
+
+# Error will occur if n is outide the range of occurrences
+
+municipal_bigram_graph <- municipal_bigram_counts %>%
+  filter(n > 8) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
+ggraph(municipal_bigram_graph, layout = "fr") +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
+  geom_node_point(color = "lightblue", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
+```
+
+```{r consortia-visual, echo=FALSE}
+consortium_bigrams_separated <- consortium_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+consortium_bigram_counts <- consortium_bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurrence
+
+# Error will occur if n is outide the range of occurrences
+
+consortium_bigram_graph <- consortium_bigram_counts %>%
+  filter(n > 5) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
+ggraph(consortium_bigram_graph, layout = "fr") +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
+  geom_node_point(color = "red", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
+```
+
+```{r school-visual, echo=FALSE}
+school_bigrams_separated <- school_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+school_bigram_counts <- school_bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurrence
+
+# Error will occur if n is outide the range of occurrences
+
+school_bigram_graph <- school_bigram_counts %>%
+  filter(n > 8) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
+ggraph(school_bigram_graph, layout = "fr") +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
+  geom_node_point(color = "orange", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
+```
+
+```{r policy-visual, echo=FALSE}
+policy_bigrams_separated <- policy_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+policy_bigram_counts <- policy_bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurrence
+
+# Error will occur if n is outide the range of occurrences
+
+policy_bigram_graph <- policy_bigram_counts %>%
+  filter(n > 10) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
+ggraph(policy_bigram_graph, layout = "fr") +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
+  geom_node_point(color = "purple", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
+```
+
+```{r academic-visual, echo=FALSE}
+academic_bigrams_separated <- academic_bigrams %>%
+  separate(bigram, c("word1", "word2"), sep = " ")
+
+academic_bigram_counts <- academic_bigrams_separated %>% 
+  count(word1, word2, sort = TRUE)
+
+# Adjust the parameter below to filter out based on number of occurrence
+
+# Error will occur if n is outside the range of occurrences
+
+academic_bigram_graph <- academic_bigram_counts %>%
+  filter(n > 150) %>%
+  graph_from_data_frame()
+
+set.seed(2021)
+
+a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+
+ggraph(academic_bigram_graph, layout = "fr") +
+  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
+                 arrow = a, end_cap = circle(.07, 'inches')) +
+  geom_node_point(color = "lightgreen", size = 4) +
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void()
+
+```
+
+```{r academic-term-frequency, echo=FALSE}
+# Create new data frame with the cleaned corpus 
+AcademicTextDF <- data.frame(text = sapply(academic_corpus, as.character), stringsAsFactors = FALSE)
+
+it_train = itoken(AcademicTextDF$text, progressbar = FALSE)
+academic_vocab = create_vocabulary(it_train)
+
+# Cut out terms that have a minimum count of 5 
+academic_vocab <- prune_vocabulary(academic_vocab, term_count_min = 5)
+academic_vocab
+```
+
+## 4.1. Word Frequency
+
+## 4.2. Bigrams and Correlations
+
+## 4.3. Policy content
+
+5. Discussion
 ===============
 
-## 4.1. Framing of AST in policy documents
+## 5.1. Framing of AST in policy documents
 
-## 4.2. Framing of AST in academic papers
+## 5.2. Framing of AST in academic papers
 
-## 4.3. Implications for School Travel Planning
+## 5.3. Implications for School Travel Planning
 
@@
 
-## 4.4. Limitations
+## 5.4. Limitations
 
-5. Conclusion
+6.1. Conclusion
 ===============
 
-## 5.1. Future research
+## 6.1. Future research
 

### 2021-06-24 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Revised Introduction section

@@
 At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018].
-There is some evidence that gender is a determinant of AST [@larsenInfluencePhysicalEnvironment2009], although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
+There is some evidence that gender is a determinant of AST [@babbChildrenActiveTravel2017; @larsenInfluencePhysicalEnvironment2009], although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
 Distance between home and school is associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
@@
 [-@riaziCorrelatesChildrenIndependent2019] found that a range of factors such as child grade, car ownership, and parental perceptions of safety and environment were associated with CIM.
+In addition to independent trips to school, children also travel by walking or bicycling on their own to other non-school destinations such as outdoor spaces (i.e., parks, playgrounds), the homes of family members or friends, shopping places, and libraries, to name a few [@badlandAssessingNeighbourhoodDestination2015; @villanuevaWhereChildrenTravel2013a].
 
@@
 Many studies and reviews have focused on the association between AST or CIM and physical activity [e.g., @faulknerActiveSchoolTransport2009; @mitraChildrenActivitytransportationLifestyles2017; @schoeppeAssociationsChildrenActive2015], with findings consistently demonstrating that children who travel by walking or bicycling to school are more active than their peers who do not use active travel.
-More recently, researchers have been exploring the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020], which has relevant applications to the study of school travel and satisfaction [see @vandenbergFactorsAffectingParental2020].
+More recently, researchers have been exploring the link between transport and children's wellbeing [@babbChildrenActiveTravel2017; @waygoodTransportChildrenWellbeing2020], which has relevant applications to the study of school travel and satisfaction [see @vandenbergFactorsAffectingParental2020].
 CIM is also important for different domains of children's health and wellbeing [@riaziChildrenIndependentMobility2018].
@@
 [-@riaziCorrelatesChildrenIndependent2019] state: "it will be vital for interventions to target modifiable factors, including children's and parents' perceptions of their social environment." Parents play the important role of "gatekeeper" by either granting or restricting CIM licenses, meaning whether children can travel alone [@sharminAssociationBuiltEnvironment2017].
-For this reason, stakeholders involved in STP produce information targeted for both children and parents, and aim to involve the broader community in their efforts.
+For this reason, stakeholders involved in STP produce information targeted for both children and parents, and aim to involve the broader community in their efforts to increase the number of children walking and bicycling to school..
 
@@
 Presently, however, there has been no study to date that explores how Canadian municipalities and schools frame and discuss AST with the public.
-Framing or content analysis is one method to analyze how particular issues are framed to groups of people, for instance parents or educators who might be inclined to support AST.
+Content analysis is one method to analyze how particular issues are framed to groups of people, for instance parents or educators who might be inclined to support AST.
 It attempts to understand how information presented from a "communicator" leads the "receiver" to a desired response [@reynardGrowthResilienceHow2021].
 In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review municipal policies addressing climate change in four western Canadian cities.
-The authors determined that most issues are framed favouring merely a tinkering of the status quo as opposed to pushing for real change.
 Natural language processing (NLP) was used for a similar purpose to examine content in general plans from Californian cities [@brinkleyWhatPlanUsing2021].

### 2021-06-25 AST-Framing-Ontario/Data Pre-Processesing.rmd
Revise and reorganize data pre-processing procedure

@@
 ---
-# Preliminaries
+
+# 0. Preliminaries
 
@@
 
-The function below allows you to find and replace certain strings.
-The main use in this context is to replace encoding errors where specific sequences of character such as "fi" or "fl" are encoded as ligatures in the pdf.
-During the conversion process those character can be lost and their subsequent words are misintrupted.
+This notebook outlines the procedure for data pre-processing and cleaning for the manuscript titled _How do school travel planning stakeholders frame active school travel in Ontario, Canada?_.
+The paper uses data retrieved from policy documents and academic papers on the subject of active school travel to conduct topic modelling and content analysis.
 
+The following steps can be replicated for other case studies, or to verify the method and results of the paper.
+
+# 1. Document Retrieval
+
+First, assemble a collection of publicly available documents sourced online from the primary school travel planning stakeholder groups: i) English school boards; ii) municipal government; and iii) transportation consortia.
+Manually download all relevant webpages in PDF.
+
+Next, conduct a search in the Web of Science database to retrieve academic papers on the topic of active school travel. Manually download all relevant studies in PDF.
+
+# 2. Creating a Corpus
+
+PDF documents are brought into the corpus directly, however each page of the document is read as an individual document.
+For our purposes, a conversion from .PDF to .txt will allow us to keep all pages in a document together when loading it into the corpus.
+Make sure you have the directory path to where your documents are stored and re-assign the `pdfLocation` to that corresponding location.
+R uses '/' as the directory separator.
+
+Create an individual corpus for each of the categories of documents: academic papers, municipal webpages, transportation consortia webpages, and school board webpages.
+
+During the conversion process, some documents will have encoding errors where specific sequences of characters, such as "fi" or "fl", are encoded as ligatures in the PDF.
+Those characters can be lost and their subsequent words are contain spaces or are not read properly by the code.
+
+This function allows you to find and replace strings:
 ```{r}
@@
 
-Stop words
+## 2.1 Academic Papers
 
-```{r}
-AP_stopW <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
+### 2.1.1 Convert single column files
 
-Con_stopW <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
-
- Mun_Reg_stopW <- c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
-
-SB_stopW <- c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")
-
-Policy_StopW <- union(AP_stopW, Mun_Reg_stopW)
-Policy_StopW <- union(Policy_StopW, SB_stopW)
-
-```
-
-# Creating Academic Corpus
-
-PDF documents are brought into the corpus directly, however each page of the document is read as an individual document.
-For our purposes, a conversion from PDF to .txt will allow us to keep all pages in a document together when loading it into the corpus.
-Make sure you have the directory path to where your documents are stored and re-assign the `pdfLocation` to that corresponding location.
-R uses '/' as the directory separator.
-
-## Single Column Conversion
-
+Trim and convert all single column formatted papers from PDF to .txt:
 ```{r}
@@
 
-# Creates folder for .txt files
+# Create a folder for .txt files
 if (file.exists(paste(pdfLocation, "txt"))){
@@
 
-# Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
+# Create a complete list of full directory paths and file names (with extension .pdf) from the PDF location as specified above
 fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
@@
 
-# use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
+# Use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
 newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
@@
 
-## Double Column Conversion
+### 2.1.2 Convert double column files
 
+Trim and convert all double column formatted papers from PDF to .txt:
 ```{r}
@@
 
-## Imports texts that were manually cleaned
+### 2.1.3 Manually clean files
+
+Proceed to manually cleaning the trimmed and converted .txt files by removing any remaining tables, figures, references, headers/footings, and captions that could not be trimmed.
+Manual corrections may be required for certain pages in academic papers that remained in two-column format after the conversion process.
+This typically occurs on pages that have a table or figure which disrupted the text.
+Finally, review all of the documents to remove hyphenation by line breaks and to keep hyphenated words together on the same line.
+Any ligatures (e.g., combinations of characters or letters that were not properly detected during the conversion process) can be fixed by inserting the unicode sequence of character to replace the missing sequence of characters.
+
+### 2.1.4 Import texts that were manually cleaned
+
+Next, import texts that were manually cleaned:
+```{r}
+# Location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/Academic Papers"
+
+cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
+n <- 1 
+for (txt in cleantxtlist) {
+
+# Create a uniquely id text store in 'Environment'
+assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
+n <- n + 1 
+}
+```
+
+### 2.1.5 Create a data frame of texts
+
+Creation of a data frame of texts is required prior to conversion to corpus.
+The data frame must contain 'doc_id' and 'text'.
+Additional fields may be included in the data frame, however it will be treated as metadata by the corpus.
+
+Create data frame:
+```{r}
+# This loop creates a vector of the texts
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+  #
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
+}
+
+# Turn vector into data frame 
+textDF <- data.frame(doc_id, text)
+
+```
+
+### 2.1.6 Convert data frame to corpus
+
+Next, convert the data frame to a corpus:
+```{r}
+df_source <- DataframeSource(textDF)
+academic_corpus <- VCorpus(df_source)
+```
+
+### 2.1.7 Clean corpus
+
+Many words should be removed while cleaning the corpus to ensure that the analysis does not pick up common nouns, adjectives, or indefinite articles.
+Words can be removed manually by creating a vector of strings.
+
+Identify relevant stop words to exclude from texts:
+```{r}
+academic_stopwords <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
+```
+
+Remove stop words and punctuation:
+```{r}
+academic_corpus <- tm_map(academic_corpus, stripWhitespace)
+academic_corpus <- tm_map(academic_corpus, content_transformer(tolower))
+
+academic_corpus <- tm_map(academic_corpus, removeWords, academic_stopwords)
+academic_corpus <- tm_map(academic_corpus, removeNumbers)
+
+academic_corpus <- tm_map(academic_corpus, removePunctuation)
+academic_corpus <- tm_map(academic_corpus, removeWords, stopwords("english"))
+
+```
+
+### 2.1.8 Clean environment
 
 ```{r}
-# location of manually cleaned .txt documents
-cleantxtLocation <- "Cleaned .txt/Academic Papers"
+rm(list=ls(pattern = "^text"))
+rm(df_source)
+```
+
+## 2.2 Municipalities
+
+### 2.2.1 Convert single column files
+
+Convert all single column webpages from PDF to .txt:
+```{r}
+pdfLocation <- "Texts/Municipalities or Regions"
+
+# Create a folder for .txt files
+if (file.exists(paste(pdfLocation, "txt"))){
+    txtLocation <- paste(pdfLocation, "txt")
+  }else{
+    dir.create(paste(pdfLocation, "txt"))
+    txtLocation <- paste(pdfLocation, "txt")
+  }
+
+# Create a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
+fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
+filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
+n <- 1
+
+for (address in filePath)
+{
+doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
+test <- doc$content
+
+# `file_path_sans_ext(basename())` from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
+
+# Use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
+newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
+
+write(test, file = newFile)
+
+n <- n+1
+}
+```
+
+### 2.2.2 Manually clean files
+
+Proceed to manually cleaning the trimmed and converted .txt files by removing telephone numbers, website links, hyperlinks, and any other extraneous content that does not relate specifically to active school travel or school travel planning.
+Finally, review all of the documents to remove hyphenation by line breaks and to keep hyphenated words together on the same line.
+Any ligatures (e.g., combinations of characters or letters that were not properly detected during the conversion process) can be fixed by inserting the unicode sequence of character to replace the missing sequence of characters.
+
+### 2.2.3 Import texts that were manually cleaned
+
+Next, import texts that were manually cleaned:
+```{r}
+# Location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/Municipalities or Regions"
+
+cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
+n <- 1 
+for (txt in cleantxtlist) {
+
+# Create a uniquely id text store in 'Environment'
+assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
+n <- n + 1 
+}
+```
+
+### 2.2.4 Create a data frame of texts
+
+Creation of a data frame of texts is required prior to conversion to corpus.
+The data frame must contain 'doc_id' and 'text'.
+Additional fields may be included in the data frame, however it will be treated as metadata by the corpus.
+
+Create data frame:
+```{r}
+# This loop creates a vector of the texts
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+  #
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
+}
+
+# Turn vector into data frame 
+textDF <- data.frame(doc_id, text)
+
+```
+
+### 2.2.5 Convert data frame to corpus
+
+Next, convert the data frame to a corpus:
+```{r}
+df_source <- DataframeSource(textDF)
+municipal_corpus <- VCorpus(df_source)
+```
+
+### 2.2.6 Clean corpus
+
+Identify relevant stop words to exclude from texts:
+```{r}
+municipal_stopwords <- c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
+```
+
+Remove stop words and punctuation:
+```{r}
+municipal_corpus <- tm_map(municipal_corpus, stripWhitespace)
+municipal_corpus <- tm_map(municipal_corpus, content_transformer(tolower))
+
+municipal_corpus <- tm_map(municipal_corpus, removeWords, municipal_stopwords)
+municipal_corpus <- tm_map(municipal_corpus, removeNumbers)
+
+municipal_corpus <- tm_map(municipal_corpus, removePunctuation)
+municipal_corpus <- tm_map(municipal_corpus, removeWords, stopwords("english"))
+
+```
+
+### 2.2.7 Clean environment
+
+```{r}
+rm(list=ls(pattern = "^text"))
+rm(df_source)
+```
+
+## 2.3 Consortia
+
+### 2.3.1 Convert single column files
+
+Trim and convert all single column files from PDF to .txt:
+```{r}
+pdfLocation <- "Texts/Consortia"
+
+# Create a folder for .txt files
+if (file.exists(paste(pdfLocation, "txt"))){
+    txtLocation <- paste(pdfLocation, "txt")
+  }else{
+    dir.create(paste(pdfLocation, "txt"))
+    txtLocation <- paste(pdfLocation, "txt")
+  }
+
+# Create a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
+fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
+filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
+n <- 1
+
+for (address in filePath)
+{
+doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
+test <- doc$content
+
+# `file_path_sans_ext(basename())` from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
+
+# Use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
+newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
+
+write(test, file = newFile)
+
+n <- n+1
+}
+```
+
+### 2.3.2 Manually clean files
+
+Proceed to manually cleaning the trimmed and converted .txt files by removing telephone numbers, website links, hyperlinks, and any other extraneous content that does not relate specifically to active school travel or school transportation.
+Finally, review all of the documents to remove hyphenation by line breaks and to keep hyphenated words together on the same line.
+Any ligatures (e.g., combinations of characters or letters that were not properly detected during the conversion process) can be fixed by inserting the unicode sequence of character to replace the missing sequence of characters.
+
+### 2.3.3 Import texts that were manually cleaned
+
+Next, import texts that were manually cleaned:
+```{r}
+# Location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/Consortia"
+
+cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
+n <- 1 
+for (txt in cleantxtlist) {
+
+# Create a uniquely id text store in 'Environment'
+assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
+n <- n + 1 
+}
+```
+
+### 2.3.4 Create a data frame of texts
+
+Creation of a data frame of texts is required prior to conversion to corpus.
+The data frame must contain 'doc_id' and 'text'.
+Additional fields may be included in the data frame, however it will be treated as metadata by the corpus.
+
+Create data frame:
+```{r}
+# This loop creates a vector of the texts
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+  #
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
+}
+
+# Turn vector into data frame 
+textDF <- data.frame(doc_id, text)
+
+```
+
+### 2.3.5 Conversion of data frame to corpus
+
+Next, convert the data frame to a corpus:
+```{r}
+df_source <- DataframeSource(textDF)
+consortium_corpus <- VCorpus(df_source)
+```
+
+### 2.3.6 Clean corpus
+
+Identify relevant stop words to exclude from texts:
+```{r}
+consortium_stopwords <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
+```
+
+Remove stop words and punctuation:
+```{r}
+consortium_corpus <- tm_map(consortium_corpus, stripWhitespace)
+consortium_corpus <- tm_map(consortium_corpus, content_transformer(tolower))
+
+consortium_corpus <- tm_map(consortium_corpus, removeWords, consortium_stopwords)
+consortium_corpus <- tm_map(consortium_corpus, removeNumbers)
+
+consortium_corpus <- tm_map(consortium_corpus, removePunctuation)
+consortium_corpus <- tm_map(consortium_corpus, removeWords, stopwords("english"))
+
+```
+
+### 2.3.7 Clean environment
+
+```{r}
+rm(list=ls(pattern = "^text"))
+rm(df_source)
+```
+
+## 2.4 School Boards
+
+### 2.4.1 Convert single column files
+
+Trim and convert all single column files from PDF to .txt:
+```{r}
+pdfLocation <- "Texts/School Boards"
+
+# Create a folder for .txt files
+if (file.exists(paste(pdfLocation, "txt"))){
+    txtLocation <- paste(pdfLocation, "txt")
+  }else{
+    dir.create(paste(pdfLocation, "txt"))
+    txtLocation <- paste(pdfLocation, "txt")
+  }
+
+# Create a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
+fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
+filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
+n <- 1
+
+for (address in filePath)
+{
+doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
+test <- doc$content
+
+# `file_path_sans_ext(basename())` from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
+
+# Use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
+newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
+
+write(test, file = newFile)
+
+n <- n+1
+}
+```
+
+### 2.4.2 Manually clean files
+
+Proceed to manually cleaning the trimmed and converted .txt files by removing telephone numbers, website links, hyperlinks, and any other extraneous content that does not relate specifically to active school travel or school transportation.
+Finally, review all of the documents to remove hyphenation by line breaks and to keep hyphenated words together on the same line.
+Any ligatures (e.g., combinations of characters or letters that were not properly detected during the conversion process) can be fixed by inserting the unicode sequence of character to replace the missing sequence of characters.
+
+### 2.4.3 Import texts that were manually cleaned
+
+Next, import texts that were manually cleaned:
+```{r}
+# Location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/School Boards"
 
@@
 
-## Creating data frame of texts
+### 2.4.4 Create a data frame of texts
 
-Creation of a data frame of texts is required prior to conversion to corpus.
-The data frame must contain 'doc_id' and 'text'.
-Additional fields may be included in the data frame, however it will be treated as metadata by the corpus.
+Create data frame:
+```{r}
+# This loop creates a vector of the texts
+text <- vector()
+doc_id <- c(2:n-1)
+
+for (i in seq(1, n-1, 1))
+{
+  #
+text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
+}
+
+# Turn vector into data frame 
+textDF <- data.frame(doc_id, text)
+
+```
+
+### 2.4.5 Convert  data frame to corpus
+
+Next, convert the data frame to a corpus:
+```{r}
+df_source <- DataframeSource(textDF)
+school_corpus <- VCorpus(df_source)
+```
+
+### 2.4.6 Clean corpus
+
+Identify relevant stop words to exclude from texts:
+```{r}
+school_stopwords <- c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")
+```
+
+Remove stop words and punctuation:
+```{r}
+school_corpus <- tm_map(school_corpus, stripWhitespace)
+school_corpus <- tm_map(school_corpus, content_transformer(tolower))
+
+school_corpus <- tm_map(school_corpus, removeWords, Con_stopW)
+school_corpus <- tm_map(school_corpus, removeNumbers)
+
+school_corpus <- tm_map(school_corpus, removePunctuation)
+school_corpus <- tm_map(school_corpus, removeWords, stopwords("english"))
+
+```
+
+### 2.4.7 Clean environment
+
+```{r}
+rm(list=ls(pattern = "^text"))
+rm(df_source)
+```
+
+# 3. Combine Policy Corpora
+
+To compare the body of policy documents to the academic paper corpus, combine all of the municipal, consortia, and school board documents in one corpus.
+
+## 3.1 Imports texts that were manually cleaned
+
+```{r}
+# Location of manually cleaned .txt documents
+cleantxtLocation <- "Cleaned .txt/Policy"
+
+cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
+n <- 1 
+for (txt in cleantxtlist) {
+
+# Create a uniquely id text store in 'Environment'
+assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
+n <- n + 1 
+}
+```
+
+## 3.2 Create a data frame of texts
 
@@
 
-# Turns vector into data frame 
+# Turn vector into data frame 
 textDF <- data.frame(doc_id, text)
@@
 
-## Conversion of data frame to corpus
-
-Next, convert the data frame to a corpus:
-```{r}
-df_source <- DataframeSource(textDF)
-academic_corpus <- VCorpus(df_source)
-```
-
-## Corpus cleaning
-
-Many words should be removed while cleaning the corpus to ensure that the analysis does not pick up on common nouns, adjectives, or indefinite articles.
-Words can be removed manually by creating a vector of strings.
-The Argument 'AP_stopW' on line 224 accomplishes that.
-Refer to line 63 for stop words.
-
-```{r}
-academic_corpus <- tm_map(academic_corpus, stripWhitespace)
-academic_corpus <- tm_map(academic_corpus, content_transformer(tolower))
-
-academic_corpus <- tm_map(academic_corpus, removeWords, AP_stopW)
-academic_corpus <- tm_map(academic_corpus, removeNumbers)
-
-academic_corpus <- tm_map(academic_corpus, removePunctuation)
-academic_corpus <- tm_map(academic_corpus, removeWords, stopwords("english"))
-
-```
-
-## Cleaning up Environment
-
-```{r}
-rm(list=ls(pattern = "^text"))
-rm(df_source)
-```
-
-# Creating Municipal Corpus
-
-# Single Column Conversion
-
-```{r}
-pdfLocation <- "Texts/Municipalities or Regions"
-
-# Creates folder for .txt files
-if (file.exists(paste(pdfLocation, "txt"))){
-    txtLocation <- paste(pdfLocation, "txt")
-  }else{
-    dir.create(paste(pdfLocation, "txt"))
-    txtLocation <- paste(pdfLocation, "txt")
-  }
-
-# Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
-fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
-filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
-n <- 1
-
-for (address in filePath)
-{
-doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
-test <- doc$content
-
-# `file_path_sans_ext(basename())` from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
-
-# use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
-newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
-
-write(test, file = newFile)
-
-n <- n+1
-}
-```
-
-## Imports texts that were manually cleaned
-
-```{r}
-# location of manually cleaned .txt documents
-cleantxtLocation <- "Cleaned .txt/Municipalities or Regions"
-
-cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
-n <- 1 
-for (txt in cleantxtlist) {
-
-# Creates uniquely id text store in 'Environment'
-assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
-n <- n + 1 
-}
-```
-
-## Creating data frame of texts
-
-```{r}
-# This loop creates a vector of the texts
-text <- vector()
-doc_id <- c(2:n-1)
-
-for (i in seq(1, n-1, 1))
-{
-  #
-text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
-}
-
-# Turns vector into data frame 
-textDF <- data.frame(doc_id, text)
-
-```
-
-## Conversion of data frame to corpus
-
-Next, convert the data frame to a corpus:
-```{r}
-df_source <- DataframeSource(textDF)
-municipal_corpus <- VCorpus(df_source)
-```
-
-## Corpus cleaning
-
-```{r}
-municipal_corpus <- tm_map(municipal_corpus, stripWhitespace)
-municipal_corpus <- tm_map(municipal_corpus, content_transformer(tolower))
-
-municipal_corpus <- tm_map(municipal_corpus, removeWords, Mun_Reg_stopW)
-municipal_corpus <- tm_map(municipal_corpus, removeNumbers)
-
-municipal_corpus <- tm_map(municipal_corpus, removePunctuation)
-municipal_corpus <- tm_map(municipal_corpus, removeWords, stopwords("english"))
-
-```
-
-## Cleaning up Environment
-
-```{r}
-rm(list=ls(pattern = "^text"))
-rm(df_source)
-```
-
-# Creating Consortia Corpus
-
-## Single Column Conversion
-
-```{r}
-pdfLocation <- "Texts/Consortia"
-
-# Creates folder for .txt files
-if (file.exists(paste(pdfLocation, "txt"))){
-    txtLocation <- paste(pdfLocation, "txt")
-  }else{
-    dir.create(paste(pdfLocation, "txt"))
-    txtLocation <- paste(pdfLocation, "txt")
-  }
-
-# Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
-fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
-filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
-n <- 1
-
-for (address in filePath)
-{
-doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
-test <- doc$content
-
-# `file_path_sans_ext(basename())` from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
-
-# use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
-newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
-
-write(test, file = newFile)
-
-n <- n+1
-}
-```
-
-## Imports texts that were manually cleaned
-
-```{r}
-# location of manually cleaned .txt documents
-cleantxtLocation <- "Cleaned .txt/Consortia"
-
-cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
-n <- 1 
-for (txt in cleantxtlist) {
-
-# Creates uniquely id text store in 'Environment'
-assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
-n <- n + 1 
-}
-```
-
-## Creating data frame of texts
-
-```{r}
-# This loop creates a vector of the texts
-text <- vector()
-doc_id <- c(2:n-1)
-
-for (i in seq(1, n-1, 1))
-{
-  #
-text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
-}
-
-# Turns vector into data frame 
-textDF <- data.frame(doc_id, text)
-
-```
-
-## Conversion of data frame to corpus
-
-Next, convert the data frame to a corpus:
-```{r}
-df_source <- DataframeSource(textDF)
-consortium_corpus <- VCorpus(df_source)
-```
-
-## Corpus cleaning
-
-```{r}
-consortium_corpus <- tm_map(consortium_corpus, stripWhitespace)
-consortium_corpus <- tm_map(consortium_corpus, content_transformer(tolower))
-
-consortium_corpus <- tm_map(consortium_corpus, removeWords, Con_stopW)
-consortium_corpus <- tm_map(consortium_corpus, removeNumbers)
-
-consortium_corpus <- tm_map(consortium_corpus, removePunctuation)
-consortium_corpus <- tm_map(consortium_corpus, removeWords, stopwords("english"))
-
-```
-
-## Cleaning up Environment
-
-```{r}
-rm(list=ls(pattern = "^text"))
-rm(df_source)
-```
-
-# Creating School Board Corpus
-
-## Single Column Conversion
-
-```{r}
-pdfLocation <- "Texts/School Boards"
-
-# Creates folder for .txt files
-if (file.exists(paste(pdfLocation, "txt"))){
-    txtLocation <- paste(pdfLocation, "txt")
-  }else{
-    dir.create(paste(pdfLocation, "txt"))
-    txtLocation <- paste(pdfLocation, "txt")
-  }
-
-# Creates a complete list of full directory paths and file names (with extension .pdf) from the pdf location as specified above
-fileBaseNames <- list.files(pdfLocation, pattern = "*.pdf", full.names=FALSE)
-filePath <- list.files(pdfLocation, pattern = "*.pdf", full.names=TRUE)
-n <- 1
-
-for (address in filePath)
-{
-doc <- readPDF(control = list(text = "-layout"))(elem = list(uri = address), language = "en")
-test <- doc$content
-
-# `file_path_sans_ext(basename())` from the tools package strips the base name for the file of interest and removed the extension at the end which as seen below allow for the replacement of .pdf for .txt
-
-# use of `sep = ""` argument is important to prevent the addition of spaces, which is the default for the paste function 
-newFile <- paste(txtLocation, "/", file_path_sans_ext(basename(address)), ".txt", sep = "")
-
-write(test, file = newFile)
-
-n <- n+1
-}
-```
-
-## Imports texts that were manually cleaned
-
-```{r}
-# location of manually cleaned .txt documents
-cleantxtLocation <- "Cleaned .txt/School Boards"
-
-cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
-n <- 1 
-for (txt in cleantxtlist) {
-
-# Creates uniquely id text store in 'Environment'
-assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
-n <- n + 1 
-}
-```
-
-## Creating data frame of texts
-
-```{r}
-# This loop creates a vector of the texts
-text <- vector()
-doc_id <- c(2:n-1)
-
-for (i in seq(1, n-1, 1))
-{
-  #
-text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
-}
-
-# Turns vector into data frame 
-textDF <- data.frame(doc_id, text)
-
-```
-
-## Conversion of data frame to corpus
-
-Next, convert the data frame to a corpus:
-```{r}
-df_source <- DataframeSource(textDF)
-school_corpus <- VCorpus(df_source)
-```
-
-## Corpus cleaning
-
-```{r}
-school_corpus <- tm_map(school_corpus, stripWhitespace)
-school_corpus <- tm_map(school_corpus, content_transformer(tolower))
-
-school_corpus <- tm_map(school_corpus, removeWords, Con_stopW)
-school_corpus <- tm_map(school_corpus, removeNumbers)
-
-school_corpus <- tm_map(school_corpus, removePunctuation)
-school_corpus <- tm_map(school_corpus, removeWords, stopwords("english"))
-
-```
-
-## Cleaning up Environment
-
-```{r}
-rm(list=ls(pattern = "^text"))
-rm(df_source)
-```
-
-# Creating Policy Corpus
-
-## Imports texts that were manually cleaned
-
-```{r}
-# location of manually cleaned .txt documents
-cleantxtLocation <- "Cleaned .txt/Policy"
-
-cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
-n <- 1 
-for (txt in cleantxtlist) {
-
-# Creates uniquely id text store in 'Environment'
-assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
-n <- n + 1 
-}
-```
-
-## Creating data frame of texts
-
-```{r}
-# This loop creates a vector of the texts
-text <- vector()
-doc_id <- c(2:n-1)
-
-for (i in seq(1, n-1, 1))
-{
-  #
-text[i] <- to.plain(eval(parse(text = paste("text", i, sep = ""))))
-}
-
-# Turns vector into data frame 
-textDF <- data.frame(doc_id, text)
-
-```
-
-## Conversion of data frame to corpus
+## 3.3 Convert data frame to corpus
 
@@
 
-## Corpus cleaning
+## 3.4. Clean corpus
 
+Identify relevant stop words to exclude from texts, in this all of the stop words previously identified for the other corpora:
+```{r}
+policy_stopwords <- union(consortium_stopwords, municipal_stopwords)
+policy_stopwords <- union(policy_stopwords, school_stopwords)
+```
+
+Remove stop words and punctuation:
 ```{r}
@@
 
-policy_corpus <- tm_map(policy_corpus, removeWords,Policy_StopW)
+policy_corpus <- tm_map(policy_corpus, removeWords,policy_stopwords)
 policy_corpus <- tm_map(policy_corpus, removeNumbers)
@@
 
-# Exporting the Corpora
+# 4. Save and export the corpora
 

### 2021-06-25 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
June 25 Changes

@@
 
+```{r}
+MunicipalTextDF <- data.frame(text = sapply(municipal_corpus, as.character), stringsAsFactors = FALSE)
+
+M_it_train = itoken(MunicipalTextDF$text, progressbar = FALSE)
+municipal_vocab = create_vocabulary(M_it_train)
+
+municipal_vocab <- prune_vocabulary(municipal_vocab, term_count_min = 5)
+municipal_vocab
+```
+
+```{r}
+ConsortiumTextDF <- data.frame(text = sapply(consortium_corpus, as.character), stringsAsFactors = FALSE)
+
+C_it_train = itoken(ConsortiumTextDF$text, progressbar = FALSE)
+consortium_vocab = create_vocabulary(C_it_train)
+
+consortium_vocab <- prune_vocabulary(consortium_vocab, term_count_min = 5)
+consortium_vocab
+```
+
+```{r}
+SchoolTextDF <- data.frame(text = sapply(school_corpus, as.character), stringsAsFactors = FALSE)
+
+S_it_train = itoken(SchoolTextDF$text, progressbar = FALSE)
+school_vocab = create_vocabulary(S_it_train)
+
+school_vocab <- prune_vocabulary(school_vocab, term_count_min = 5)
+school_vocab
+```
+
+```{r}
+PolicyTextDF <- data.frame(text = sapply(policy_corpus, as.character), stringsAsFactors = FALSE)
+
+P_it_train = itoken(PolicyTextDF$text, progressbar = FALSE)
+policy_vocab = create_vocabulary(P_it_train)
+
+policy_vocab <- prune_vocabulary(policy_vocab, term_count_min = 5)
+policy_vocab
+```
+
 ## 4.1. Word Frequency

### 2021-06-25 AST-Framing-Ontario/Data Pre-Processesing.rmd
June 25 Changes

@@
 ```{r}
-academic_stopwords <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
+academic_stopwords <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-", "hong", "kong", "united", "states", "new", "zealand")
 ```
@@
 
-school_corpus <- tm_map(school_corpus, removeWords, Con_stopW)
+school_corpus <- tm_map(school_corpus, removeWords, school_stopwords)
 school_corpus <- tm_map(school_corpus, removeNumbers)

### 2021-07-09 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Analysis of concordance and topic modelling are added

--- 2021-06-24 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
@@
 
+```{r echo=FALSE}
+rm(list = ls())
+```
+
 ```{r load-packages, include=FALSE}
@@
 library(wordcloud)
+library(ldatuning)
+library(quanteda)
 ```
@@
 
-## 1.3. Correlates of children's independent mobility
-
-AST is one of the most common opportunities for children to travel without adult supervision on a regular basis.
-Children's independent mobility (CIM) was first described by Hillman et al.
-[-@hillmanOneFalseMove1990] as the freedom of children to travel and play within their neighborhood and city without the presence of adults.
-The ability of children to reach destinations such as school or local parks by walking or bicycling on their own as a growing area of research that is related to the body of literature on AST.
-Similar to AST, CIM is much less common now than it was for previous generations [@bhosaleIntergenerationalChangeChildren2017], and is influenced by many similar personal and environmental factors as AST [@marziChildrenIndependentMobility2018; @mitraIndependentMobilityMode2013].
-In a study conducted in multiple Canadian cities, Riazi et al.
-[-@riaziCorrelatesChildrenIndependent2019] found that a range of factors such as child grade, car ownership, and parental perceptions of safety and environment were associated with CIM.
-In addition to independent trips to school, children also travel by walking or bicycling on their own to other non-school destinations such as outdoor spaces (i.e., parks, playgrounds), the homes of family members or friends, shopping places, and libraries, to name a few [@badlandAssessingNeighbourhoodDestination2015; @villanuevaWhereChildrenTravel2013a].
-
-## 1.4. Benefits of AST and CIM
+## 1.3. Benefits of AST
 
@@
 
-## 1.5. Encouraging adoption of active school travel
+## 1.4. Encouraging adoption of active school travel
 
-In the case of AST and CIM in Canada, Riazi et al.
+To increase rates of walking and bicycling independently to school, Riazi et al.
 [-@riaziCorrelatesChildrenIndependent2019] state: "it will be vital for interventions to target modifiable factors, including children's and parents' perceptions of their social environment." Parents play the important role of "gatekeeper" by either granting or restricting CIM licenses, meaning whether children can travel alone [@sharminAssociationBuiltEnvironment2017].
-For this reason, stakeholders involved in STP produce information targeted for both children and parents, and aim to involve the broader community in their efforts to increase the number of children walking and bicycling to school..
+For this reason, stakeholders involved in STP produce information targeted for both children and parents, and aim to involve the broader community in their efforts to increase the number of children walking and bicycling to school.
 
@@
 In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review municipal policies addressing climate change in four western Canadian cities.
-Natural language processing (NLP) was used for a similar purpose to examine content in general plans from Californian cities [@brinkleyWhatPlanUsing2021].
-The way policy issues are framed is important to understand because it plays a role in either altering or preserving the existing social perceptions.
+Natural language processing (NLP) has also been used for a similar purpose to examine content in general plans from Californian cities [@brinkleyWhatPlanUsing2021].
+The way policy issues are framed is ultimately important to understand because it plays a role in either altering or preserving the existing social perceptions.
 
-## 1.6. Study aim
+## 1.5. Study aim
+
+In 2017, the provincial government of Ontario in Canada issued funding to Green Communities Canada (GCC), a non-profit organization, to launch the _Ontario Active School Travel_ (OAST) program.
+The program provides funding for school and community-based initiatives and supports stakeholders in municipalities across the province to implement STP and other interventions aimed at increasing AST.
+As of 2021, OAST has funded _X_ projects in Ontario.
+GCC continues has funded projects across Ontario led by collaborative groups involving school boards, municipal or regional governments, and regional transportation consortia.
+The latter are dedicated transportation bodies that deliver efficient and effective transportation services, which generally focus on providing the school busing service to families in their associated region.
 
 The aim of this paper is to analyze how AST is framed by STP stakeholders in Ontario, Canada.
-We used topic modelling and content analysis to examine how the benefits and barriers of AST are presented and which solutions for improving AST are identified in local policy documents from Ontario municipalities and school boards.
-We compared these documents to a selection of studies on AST and CIM to explore the extent to which research findings have trickled down to inform policy and planning for AST interventions.
+We used text mining and topic modelling to examine how local policy documents from Ontario municipalities and school boards present and communicate the benefits and barriers of AST and the solutions for improving AST.
+We compared the findings from these documents to a selection of studies on AST and explored the extent to which research findings have trickled down to inform policy and planning for increasing AST.
 
@@
 
-To determine which stakeholder groups are typically involved in AST and/or STP initiatives in Ontario, we first conducted a preliminary scan of current and past projects funded by the _Ontario Active School Travel_.
-We found that projects are often led in collaboration by a school board, the respective municipality or region (i.e., transportation planners, public health professionals, engineers, etc.), and the regional transportation consortia.
-Non-profit organizations, police services, and advocacy groups are other stakeholders who may play a role in supporting AST and/or STP.
+We assembled a collection of publicly available documents that were sourced online from the main stakeholder groups involved in STP initiatives in Ontario: i) school boards (public and English-speaking only); ii) municipal governments; and iii) transportation consortia.
+Non-profit organizations, police services, and advocacy groups are other stakeholders who may play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in initiatives.
 
-We then assembled a collection of publicly available documents that were sourced online from the main stakeholder groups: i) English school boards; ii) municipal government; and iii) transportation consortia.
-The search was guided first by a list of all English school boards across Ontario.
-The websites of each school board were searched for pages related to transportation or school travel.
-These pages were manually downloaded.
+The search was guided first by a list of all English public school boards across Ontario.
+The websites of each school board were manually searched for pages related to school transportation or travel.
+Any pages relevant to these topics were manually downloaded.
 Next, we collected documents by searching municipal government and transportation consortia websites.
 The latter were identified based on geographic area (i.e., the municipalities and/or transportation consortia who are in the same geographic area of each school board).
-Pages related to active transportation or school travel were manually downloaded.
-Webpages were included in the corpus if they were easy to find.
+Pages related to active or school travel were manually downloaded.
+Webpages from STP stakeholder websites were included in our analysis if they were easy to find.
 This primary criteria was important since our analysis pertains to how such issues are framed to the public.
-Thus, these pages ought to be easy to find, which we defined as requiring no more than 2-4 separate links from the initial Google search.
+Thus, we included only webpages that were easy to find, which we defined as requiring no more than 2-4 separate links from the initial Google search.
 
-The initial policy corpus included 64 relevant policy documents (i.e., one webpage or more) from all main stakeholder groups.
-It is important to note that school boards, municipalities, and transportation consortia may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents.
-Search results are summarized in Table \ref{tab:search-results}.
+The initial corpus of policy documents included 64 relevant webpages (i.e., one page or more) from all STP stakeholder groups.
+It is important to note that school boards, municipalities, and transportation consortia may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents, which means that some of these groups for particular regions in Ontario are not included in our analysis.
+Search results are summarized in Table \ref{tab:policy-documents}.
 
@@
 data_tbl <- data.frame(
-  Stakeholder = c("English school boards", "Municipalities or regions", "Transportation consortia"),
+  Stakeholder = c("School boards", "Municipalities", "Transportation consortia"),
   Total = c("62", "62", "39"),
@@
   column_spec(1, bold = T, border_right = T) %>%
-  column_spec(2, width = "30em") %>%
   column_spec(3, border_left = T) %>%
@@
 A multi-step process was conducted to ensure that the analysis captured as much content as possible from both the policy documents (n = 64) and academic papers (n = 233).
-We manually removed any extraneous material in the documents that did not pertain to AST specifically.
-This included footnotes, references, acknowledgments, and conflict of interest statements in the academic papers.
-We removed all phone numbers, inserted links to other webpages, personal names, and content not to specific to AST from the policy documents that were retrieved from the websites of school boards, municipalities, and transportation consortia.
-
 To begin, the webpages, which were manually downloaded in portable document format (PDF), were trimmed so that pages that only consisted of tables, figures, or references were removed.
@@
 
-We then converted the trimmed PDF documents into `txt` files so that they could be imported in `R` for topic modelling.
-We proceeded to a manual cleaning phase where we removed any remaining tables, figures, references, headers/footings, and captions that could not be trimmed.
+Next, we converted the trimmed PDF documents into `txt` files so that they could be imported in R for analysis.
+We then proceeded to a manual cleaning phase where we removed any remaining tables, figures, references, headers/footings, and captions that could not be trimmed.
 Manual corrections were also required for certain pages in academic papers that remained in two-column format after the conversion process.
-This typically occured on pages that had a table or figure which disrupted the text.
+This typically occurred on pages that had a table or figure which disrupted the text.
 Finally, we reviewed all of the documents to remove hyphenation by line breaks and to keep hyphenated words together on the same line.
@@
 
-At this point, the documents were imported into the corpus in `R` and added to a data frame for analysis.
-In the final step before analysis, we removed all blank spaces, punctuation, capitalization, and numbers.
+We also manually removed any extraneous material in the academic papers that did not pertain to AST specifically.
+This included footnotes, references, acknowledgments, and conflict of interest statements in the academic papers.
+We removed all phone numbers, inserted links to other webpages, personal names, and content not to specific to AST from the policy documents that were retrieved from the websites of school boards, municipalities, and transportation consortia.
+
+In the final step, we removed all blank spaces, punctuation, capitalization, and numbers.
 English stop words, which are common words such as _and_ or _the_ as identified in a predetermined list by Lewis et al.
-[@R-tm] and other frequent terms in the documents like places were removed from the corpus.
+[@R-tm] and other frequent terms in the documents like "school" and specific location names, were removed from the corpora.
 
@@
 
-## 3.1. Case study: Ontario, Canada
+## 3.1. Natural language processing
 
-In 2017, the provincial government of Ontario issued funding to Green Communities Canada (GCC), a non-profit organization, to launch the _Ontario Active School Travel_ (OAST) program.
-The program provides funding for school and community-based initiatives and supports stakeholders in municipalities across the province to implement STP and other interventions aimed at increasing AST.
-As of 2021, OAST has funded _X_ projects in Ontario.
-GCC continues its work by providing resources for interested stakeholders and funding projects across Ontario led by collaborative groups involving school boards, municipal or regional governments, and regional transportation consortia.
-The latter are dedicated transportation bodies that deliver efficient and effective transportation services, which generally focuses on providing the school busing service to families in their associated region.
+Natural language processing [see @silgetextmining2021]
 
-## 3.2. Topic modelling
+Topic modelling
 
-## 3.3. Summative content analysis
-
-## 3.4. Reproducibility
+## 3.2. Reproducibility
 
@@
 
-```{r city-bigrams, echo=FALSE}
+## 4.1. Word and document frequency
+
+We analyzed word and document frequency for each corpora.
+Table \ref{tab:word-table} shows the most frequent terms found in the municipal, transportation consortia, school board, and academic documents.
+As expected, STP documents and academic papers reference _active travel_, _walking_, _biking_ or _cycling_, and _students_ more than other terms.
+Each corpora also has _safety_ and _traffic_ as common words which suggests congruence on these key factors between the research literature and how AST is framed to the public.
+The word _physical_ is present in each corpus which could refer to either _physical activity_, _physical health_, or the _physical environment_.
+Furthermore, documents from STP stakeholders discuss _resources_, _information_, and _services_ about school travel.
+In the section below, the context in which these terms appear is explored further through their concordance.
+Unlike the academic papers, STP stakeholder documents include the words _route_ or _routes_.
+This could reflect their role in identifying safe routes to school to share with parents or families, as well as the STP emphasis on making the physical environment safer for AST.
+The academic corpora differs from the policy documents in that _parents_ and _distance_ are the second and third most common terms.
+In addition, _time_, _factors_, _environment_, and _age_ are also identified in academic papers.
+These words are absent from the list of common words in policy documents.
+Table \ref{tab:word-table} indicates that the research corpora discusses a broader range of determinants of AST than the policy documents.
+The number of references for each term in the academic papers is also significantly higher due to the inclusion of more documents.
+
+```{r municipal-term-frequency, echo=FALSE}
+# Create new data frame with the cleaned corpus 
+MunicipalTextDF <- data.frame(text = sapply(municipal_corpus, as.character), stringsAsFactors = FALSE)
+
+municipal_it_train = itoken(MunicipalTextDF$text, progressbar = FALSE)
+municipal_vocab = create_vocabulary(municipal_it_train)
+
+# Cut out terms that have a minimum count of 1 
+municipal_vocab <- prune_vocabulary(municipal_vocab, term_count_min = 1)
+```
+
+```{r consortia-term-frequency, echo=FALSE}
+# Create new data frame with the cleaned corpus 
+ConsortiumTextDF <- data.frame(text = sapply(consortium_corpus, as.character), stringsAsFactors = FALSE)
+
+consortium_it_train = itoken(ConsortiumTextDF$text, progressbar = FALSE)
+consortium_vocab = create_vocabulary(consortium_it_train)
+
+# Cut out terms that have a minimum count of 1
+consortium_vocab <- prune_vocabulary(consortium_vocab, term_count_min = 1)
+```
+
+```{r school-term-frequency, echo=FALSE}
+# Create new data frame with the cleaned corpus 
+SchoolTextDF <- data.frame(text = sapply(school_corpus, as.character), stringsAsFactors = FALSE)
+
+school_it_train = itoken(SchoolTextDF$text, progressbar = FALSE)
+school_vocab = create_vocabulary(school_it_train)
+
+# Cut out terms that have a minimum count of 1 
+school_vocab <- prune_vocabulary(school_vocab, term_count_min = 1)
+```
+
+```{r academic-term-frequency, echo=FALSE}
+# Create new data frame with the cleaned corpus 
+AcademicTextDF <- data.frame(text = sapply(academic_corpus, as.character), stringsAsFactors = FALSE)
+
+it_train = itoken(AcademicTextDF$text, progressbar = FALSE)
+academic_vocab = create_vocabulary(it_train)
+
+# Cut out terms that have a minimum count of 100 
+academic_vocab <- prune_vocabulary(academic_vocab, term_count_min = 100)
+```
+
+```{r top-word-frequencies, echo=FALSE}
+municipal_words <- municipal_vocab %>% slice(1939:1915)
+school_words <- school_vocab %>% slice(1861:1837)
+consortia_words <- consortium_vocab[-c(971),] %>% slice(993:968)
+academic_words <- academic_vocab[-c(1309, 1304),] %>% slice(1311:1285)
+```
+
+```{r word-table, echo=FALSE}
+top_words <- cbind(
+  municipal_words,
+  school_words,
+  consortia_words,
+  academic_words)
+
+colnames(top_words) <- c("Term", "Count (n)", "Documents (n)", "Term", "Count (n)", "Documents (n)", "Term", "Count (n)", "Documents (n)", "Term", "Count (n)", "Documents (n)")
+
+# add frequency term count / words
+
+kable(top_words,
+      "latex",
+      booktabs = TRUE,
+      col.names = c("Term",
+                    "Count (n)",
+                    "Documents (n)",
+                    "Term",
+                    "Count (n)",
+                    "Documents (n)",
+                    "Term",
+                    "Count (n)", 
+                    "Documents (n)",
+                    "Term",
+                    "Count (n)",
+                    "Documents (n)"),
+      align = c("l", "c", "c", "l", "c", "c", "l", "c", "c", "l", "c", "c"), 
+      caption = "\\label{tab:word-table}Top 25 terms identified in each corpora. Document frequencies are also indicated.") %>%
+  kable_styling(latex_options = c("striped", "scale_down")) %>%
+  add_header_above(c("Municipalities" = 3, "School Boards" = 3, "Transportation Consortia" = 3, "Academic Papers" = 3)) %>%
+  footnote(general = " ",
+           alphabet = c("Count (n) refers to the total number of times the term is found in the corpora", "Documents (n) refers to the total number of documents that feature the term"))
+```
+
+## 4.2. Bigrams and concordances
+
+Bigrams for each policy corpora that occur more than 5 times are shown in Figures \ref{fig:city-visual},  \ref{fig:consortia-visual}, and \ref{fig:school-visual}.
+These figures help to make further sense of the word frequencies reported above, and highlight the main ideas that are presented to the public in each of the policy corpora.
+Municipalities primarily discuss _physical activity_ (n = 53) and _public health_ (n = 19) in the context of active travel.
+In addition, _travel planning_ (n = 19), _bike lanes_ (n = 16), and _safe routes_ (n = 14) are also identified, conceivably as interventions and built environment factors that support AST.
+Key issues related to transport such as _traffic safety_ (n = 10), _air quality_ (n = 9), and _greenhouse gases_ (n = 9) are conveyed to the public through AST documents.
+It is not surprising to find this focus in AST documents given that municipalities in Ontario are concerned about climate change and have increasingly looked to active modes of travel to offset transport-related emissions in urban areas.
+
+Similar word bigrams are found in school board documents: _travel planning_ (n = 33), _safe routes_ (n = 15), _physical activity_ (n = 10), and _public health_ (n = 10) are among the most common bigrams.
+Both municipalities and school boards in Ontario seem to emphasize what can be or has been done to improve AST (i.e., policy or planning changes), while outlining some of the benefits of AST at the individual- or community-level to potentially encourage behaviour change (i.e., physical activity for children or improved air quality).
+Unlike other STP stakeholders, school boards also consider _inclement weather_ (n = 24) and _bus cancellations_ (n = 13).
+This is likely because many students in Ontario travel to school by bus and this information is presented alongside AST options.
+Finally, transportation consortia documents highlight topics such as _physical activity_ (n = 10), _pedestrian safety_ (n = 8), _crossing guards_ (n = 6), _travel planning_ (n = 6), and _walk zones_ (n = 6).
+Biking or cycling is notably absent from transportation consortia documents.
+
+```{r city-bigrams, include=FALSE, echo=FALSE}
 # Converting corpus to tidytext data type 
@@
   count(trigram, sort = TRUE)
-
-top_municipal_bigrams
-top_municipal_trigrams
 ```
 
-```{r consortia-bigrams, echo=FALSE}
-
+```{r consortia-bigrams, include=FALSE, echo=FALSE}
 # Converting corpus to tidytext data type 
@@
   count(trigram, sort = TRUE)
-
-top_consortium_bigrams
-top_consortium_trigrams
 ```
 
-```{r school-bigrams, echo=FALSE}
-
+```{r school-bigrams, include=FALSE, echo=FALSE}
 # Converting corpus to tidytext data type 
@@
   count(trigram, sort = TRUE)
-
-top_school_bigrams
-top_school_trigrams
 ```
 
-```{r policy-bigrams, echo=FALSE}
-
+```{r policy-bigrams, include=FALSE, echo=FALSE}
 # Converting corpus to tidytext data type 
@@
   count(trigram, sort = TRUE)
-
-top_policy_bigrams
-top_policy_trigrams
 ```
 
-```{r academic-bigrams, echo=FALSE}
-
+```{r academic-bigrams, include=FALSE, echo=FALSE}
 # Converting corpus to tidytext data type 
@@
   count(trigram, sort = TRUE)
-
-top_academic_bigrams
-top_academic_trigrams
 ```
 
-```{r city-visual, echo=FALSE}
+```{r, include=FALSE}
 municipal_bigrams_separated <- municipal_bigrams %>%
@@
 a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+```
 
+```{r city-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the municipal or regional government documents."}
 ggraph(municipal_bigram_graph, layout = "fr") +
@@
 
-```{r consortia-visual, echo=FALSE}
+```{r, include=FALSE}
 consortium_bigrams_separated <- consortium_bigrams %>%
@@
 a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+```
 
+```{r consortia-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the transportation consortia documents."}
 ggraph(consortium_bigram_graph, layout = "fr") +
@@
 
-```{r school-visual, echo=FALSE}
+```{r, include=FALSE}
 school_bigrams_separated <- school_bigrams %>%
@@
 a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+```
 
+```{r school-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the school board documents."}
 ggraph(school_bigram_graph, layout = "fr") +
@@
 
-```{r policy-visual, echo=FALSE}
+```{r, include=FALSE}
 policy_bigrams_separated <- policy_bigrams %>%
@@
 a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+```
 
+```{r policy-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in all of the policy documents (i.e., school board, municipality, and transportation consortia combined."}
 ggraph(policy_bigram_graph, layout = "fr") +
@@
 
-```{r academic-visual, echo=FALSE}
+We combined all of the municipality, school board, and transportation consortia documents into one "policy" corpora.
+This enabled us to examine and visualize the most common bigrams found across all of the STP material in Ontario.
+Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the corpora.
+In addition to the common bigrams already identified above, we also found _mental health_, _walk day_, and _green communities_ as common pairs of consecutive words.
+Overall, policy documents from STP stakeholders focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or considerations; and iv) supports for AST.
+
+We analyzed bigrams in the academic corpora separately to make comparisons with the policy corpora.
+Figure \ref{fig:academic-visual} indicates that the academic corpora includes several common bigrams that were also found in the policy documents including _physical activity_ (n = 1566), which is the top bigram, _traffic safety_ (n = 308), and _safe routes_ (n = 268).
+However, many other factors relating to AST are identified in the research literature that are not presented to the public through policy documents.
+After _physical activity_, _built environment_ (n = 1175), _independent mobility_ (n = 774), and _urban form_ (n = 352) are the most frequent pairs of consecutive words.
+Academic papers also often discuss _distance home_ (n = 258), _car ownership_ (n = 254), _household income_ (n = 254), and _population density_ (n = 205), which are factors that have been found to influence AST.
+It is evident that many papers investigate gender differences in AST given that _boys girls_ (n = 211) is another common bigram.
+Finally, the presence of _statistically significant_ among the top bigrams underscores that researchers aim to identify determinants that are not due to chance but that likely influence AST.
+The academic corpora focuses on a greater range of topics than found in the STP material.
+
+```{r academic-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the academic papers."}
 academic_bigrams_separated <- academic_bigrams %>%
@@
 academic_bigram_graph <- academic_bigram_counts %>%
-  filter(n > 150) %>%
+  filter(n > 200) %>%
   graph_from_data_frame()
@@
 a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
+```
 
+```{r}
 ggraph(academic_bigram_graph, layout = "fr") +
@@
   theme_void()
-
 ```
 
-```{r academic-term-frequency, echo=FALSE}
-# Create new data frame with the cleaned corpus 
-AcademicTextDF <- data.frame(text = sapply(academic_corpus, as.character), stringsAsFactors = FALSE)
+We interpreted the most common bigrams from the policy corpora (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholders are focusing on and communicating to the public about AST.
+We used the `kwic` function from the R _quanteda_ package to identify and better understand identify the context of these key themes.
 
-it_train = itoken(AcademicTextDF$text, progressbar = FALSE)
-academic_vocab = create_vocabulary(it_train)
+```{r policy-concordance, echo=FALSE}
+# Import VCorpus created by tm package
 
-# Cut out terms that have a minimum count of 5 
-academic_vocab <- prune_vocabulary(academic_vocab, term_count_min = 5)
-academic_vocab
+policy_quanteda <- tm::VCorpus(tm::VectorSource(policy_corpus))
+policy_quanteda <- corpus(policy_quanteda)
+
+# Extraction of various search terms and the surrounding sentence context
+
+kwic_pol_physical <- kwic(tokens(policy_quanteda), pattern = "physical")
+kwic_pol_mental <- kwic(tokens(policy_quanteda), pattern = "mental")
+kwic_pol_air <- kwic(tokens(policy_quanteda), pattern = "air")
+kwic_pol_traffic <- kwic(tokens(policy_quanteda), pattern = "traffic")
+kwic_pol_safety <- kwic(tokens(policy_quanteda), pattern = "safety")
+kwic_pol_health <- kwic(tokens(policy_quanteda), pattern = "health")
+kwic_pol_emissions <- kwic(tokens(policy_quanteda), pattern = "emissions")
+kwic_pol_routes <- kwic(tokens(policy_quanteda), pattern = "routes")
+kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes")
+kwic_pol_zone <- kwic(tokens(policy_quanteda), pattern = "zone")
+kwic_pol_bus <- kwic(tokens(policy_quanteda), pattern = "bus")
+kwic_pol_comm <- kwic(tokens(policy_quanteda), pattern = "community")
+kwic_pol_ben <- kwic(tokens(policy_quanteda), pattern = "benefit")
+kwic_pol_wea <- kwic(tokens(policy_quanteda), pattern = "weather")
+kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes")
 ```
 
-## 4.1. Word Frequency
+```{r content-table, echo=FALSE}
+text_tbl <- data.frame(
+  Terms = c("Physical health", "Emissions"),
+  Stakeholder = c("School Board", "Municipality"),
+  Context = c(
+    "ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.",
+    "Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.")
+)
 
-## 4.2. Bigrams and Correlations
+kbl(text_tbl) %>%
+  kable_paper(full_width = F) %>%
+  column_spec(1, bold = T) %>%
+  column_spec(3, width = "30em")
+```
 
-## 4.3. Policy content
+## 4.3. Topic modelling
+
+```{r corpus-dtm, echo=FALSE}
+# Create DTM from corpus
+
+municipal_dtm <- DocumentTermMatrix(municipal_corpus)
+school_dtm <- DocumentTermMatrix(school_corpus)
+consortia_dtm <- DocumentTermMatrix(consortium_corpus)
+policy_dtm <- DocumentTermMatrix(policy_corpus)
+academic_dtm <- DocumentTermMatrix(academic_corpus)
+```
+
+```{r topics-number, echo=FALSE}
+# Select number of topics for each LDA model using `ldatuning`
+
+municipal_lda_num <- FindTopicsNumber(
+  municipal_dtm, # Check with other DTM
+  topics = seq(from = 5, to = 20, by = 2),
+  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  method = "Gibbs",
+  #control = list(seed = 77),
+  #mc.cores = 2L,
+  #verbose = TRUE
+)
+
+school_lda_num <- FindTopicsNumber(
+  school_dtm, # Check with other DTM
+  topics = seq(from = 5, to = 20, by = 2),
+  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  method = "Gibbs",
+  #control = list(seed = 77),
+  #mc.cores = 2L,
+  #verbose = TRUE
+)
+
+consortia_lda_num <- FindTopicsNumber(
+  consortia_dtm, # Check with other DTM
+  topics = seq(from = 5, to = 20, by = 2),
+  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  method = "Gibbs",
+  #control = list(seed = 77),
+  #mc.cores = 2L,
+  #verbose = TRUE
+)
+
+policy_lda_num <- FindTopicsNumber(
+  policy_dtm, # Check with other DTM
+  topics = seq(from = 5, to = 20, by = 2),
+  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  method = "Gibbs",
+  #control = list(seed = 77),
+  #mc.cores = 2L,
+  #verbose = TRUE
+)
+
+#academic_lda_num <- FindTopicsNumber(
+  #academic_dtm, # Check with other DTM
+  #topics = seq(from = 2, to = 50, by = 5),
+  #metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  #method = "Gibbs",
+  #control = list(seed = 77),
+  #mc.cores = 2L,
+  #verbose = TRUE)
+```
+
+```{r evaluate-lda, echo=FALSE}
+
+#FindTopicsNumber_plot(municipal_lda_num)
+FindTopicsNumber_plot(school_lda_num)
+#FindTopicsNumber_plot(consortia_lda_num)
+#FindTopicsNumber_plot(policy_lda_num)
+#FindTopicsNumber_plot(academic_lda_num)
+
+# The output suggests that there are 9 topics in the municipal corpus
+# The output suggests that there are 9 topics in the school corpus
+# The output suggests that there are 7 topics in the municipal corpus
+# The output suggests that there are 9 topics in the municipal corpus
+# The output suggests that there are ? topics in the municipal corpus
+```
+
+```{r corpus-lda-model, echo=FALSE}
+municipal_lda <- LDA(municipal_dtm, k = 9)
+school_lda <- LDA(school_dtm, k = 9)
+consortia_lda <- LDA(consortia_dtm, k = 7)
+policy_lda <- LDA(policy_dtm, k = 9)
+#academic_lda <- LDA(academic_dtm, k = ?)
+```
+
+```{r municipal-topics, echo=FALSE}
+municipal_topics <- tidy(municipal_lda, matrix = "beta")
+school_topics <- tidy(school_lda, matrix = "beta")
+consortia_topics <- tidy(consortia_lda, matrix = "beta")
+policy_topics <- tidy(policy_lda, matrix = "beta")
+#academic_topics <- tidy(academic_lda, matrix = "beta")
+```
+
+```{r municipal-terms, echo=FALSE}
+municipal_top_terms <- municipal_topics %>%
+  group_by(topic) %>%
+  slice_max(beta, n = 10) %>% 
+  ungroup() %>%
+  arrange(topic, -beta)
+
+municipal_top_terms %>%
+  mutate(term = reorder_within(term, beta, topic)) %>%
+  ggplot(aes(beta, term, fill = factor(topic))) +
+  geom_col(show.legend = FALSE) +
+  facet_wrap(~ topic, scales = "free") +
+  scale_y_reordered()
+```
+
+```{r school-terms, echo=FALSE}
+school_top_terms <- school_topics %>%
+  group_by(topic) %>%
+  slice_max(beta, n = 10) %>% 
+  ungroup() %>%
+  arrange(topic, -beta)
+
+school_top_terms %>%
+  mutate(term = reorder_within(term, beta, topic)) %>%
+  ggplot(aes(beta, term, fill = factor(topic))) +
+  geom_col(show.legend = FALSE) +
+  facet_wrap(~ topic, scales = "free") +
+  scale_y_reordered()
+```
+
+```{r consortia-terms, echo=FALSE}
+consortia_top_terms <- consortia_topics %>%
+  group_by(topic) %>%
+  slice_max(beta, n = 10) %>% 
+  ungroup() %>%
+  arrange(topic, -beta)
+
+consortia_top_terms %>%
+  mutate(term = reorder_within(term, beta, topic)) %>%
+  ggplot(aes(beta, term, fill = factor(topic))) +
+  geom_col(show.legend = FALSE) +
+  facet_wrap(~ topic, scales = "free") +
+  scale_y_reordered()
+```
+
+```{r policy-terms, echo=FALSE}
+policy_top_terms <- policy_topics %>%
+  group_by(topic) %>%
+  slice_max(beta, n = 10) %>% 
+  ungroup() %>%
+  arrange(topic, -beta)
+
+policy_top_terms %>%
+  mutate(term = reorder_within(term, beta, topic)) %>%
+  ggplot(aes(beta, term, fill = factor(topic))) +
+  geom_col(show.legend = FALSE) +
+  facet_wrap(~ topic, scales = "free") +
+  scale_y_reordered()
+```
+
+```{r academic-terms, echo=FALSE}
+# Do not run; number of topics is not yet determined
+
+academic_top_terms <- academic_topics %>%
+  group_by(topic) %>%
+  slice_max(beta, n = 10) %>% 
+  ungroup() %>%
+  arrange(topic, -beta)
+
+academic_top_terms %>%
+  mutate(term = reorder_within(term, beta, topic)) %>%
+  ggplot(aes(beta, term, fill = factor(topic))) +
+  geom_col(show.legend = FALSE) +
+  facet_wrap(~ topic, scales = "free") +
+  scale_y_reordered()
+```
+
+```{r}
+#municipal_beta <- municipal_topics %>%
+  #mutate(topic = paste0("topic", topic)) %>%
+  #pivot_wider(names_from = topic, values_from = beta) %>% 
+  #filter(topic1 > .001 | topic2 > .001) %>%
+  #mutate(log_ratio = log2(topic2 / topic1))
+#municipal_beta
+```
+
+```{r document-matrix}
+# Identify topics by document across each corpora
+
+municipal_documents <- tidy(municipal_lda, matrix = "gamma")
+school_documents <- tidy(school_lda, matrix = "gamma")
+consortia_documents <- tidy(consortia_lda, matrix = "gamma")
+policy_documents <- tidy(policy_lda, matrix = "gamma")
+academic_documents <- tidy(academic_lda, matrix = "gamma")
+```
 
@@
 
+The presence of _travel planning_ among the top pairs of consecutive words for municipalities, school boards, and transportation consortia reflects the priority given to this intervention in Ontario.
+
 ## 5.2. Framing of AST in academic papers
+
+Notably absent from the policy corpora is _children's independent mobility_ (CIM).
+AST is one of the most common opportunities for children to travel without adult supervision on a regular basis, yet STP stakeholders do not discuss this topic.
+CIM was first described by Hillman et al.
+[-@hillmanOneFalseMove1990] as the freedom of children to travel and play within their neighborhood and city without the presence of adults.
+The ability of children to reach destinations such as school or local parks by walking or bicycling on their own is a growing area of research that is related to and often overlaps with the body of literature on AST.
+
+In a study conducted in multiple Canadian cities, Riazi et al.
+[-@riaziCorrelatesChildrenIndependent2019] found that a range of factors such as child grade, car ownership, and parental perceptions of safety and environment were associated with CIM.
+Parental perceptions of children's autonomy also influences CIM [@alparoneChildrenIndependentMobility2012].
+In addition to independent trips to school, children also travel by walking or bicycling on their own to other non-school destinations such as outdoor spaces (i.e., parks, playgrounds), the homes of family members or friends, shopping places, and libraries, to name a few [@badlandAssessingNeighbourhoodDestination2015; @villanuevaWhereChildrenTravel2013a].
 
@@
 
-This research was completed using open software, and the authors wish to acknowledge the developers of the following `R` packages: `dplyr` [@R-dplyr], `ggraph` [@R-ggraph], `ggplot2` [@R-ggplot2], `igraph` [@R-igraph], `pdftools` [@R-pdftools], `readr` [@R-readr], `reshape2` [@R-reshape2], `stringr` [@R-stringr], `text2vec` [@R-text2vec], `textdata` [@R-textdata], `tidyr` [@R-tidyr], `tidytext` [@R-tidytext], `tm` [@R-tm], `tools` [@R-tools], `topicmodels` [@R-topicmodels], `widyr` [@R-widyr],
-`word2vec` [@R-word2vec], `wordcloud` [@R-wordcloud].
+This research was completed using open software, and the authors wish to acknowledge the developers of the following `R` packages: `dplyr` [@R-dplyr], `ggraph` [@R-ggraph], `ggplot2` [@R-ggplot2], `igraph` [@R-igraph], `pdftools` [@R-pdftools], `readr` [@R-readr], `reshape2` [@R-reshape2], `stringr` [@R-stringr], `text2vec` [@R-text2vec], `textdata` [@R-textdata], `tidyr` [@R-tidyr], `tidytext` [@R-tidytext], `tm` [@R-tm], `tools` [@R-tools], `topicmodels` [@R-topicmodels], `widyr` [@R-widyr], `word2vec` [@R-word2vec], `wordcloud` [@R-wordcloud], `DiagrammeR` [@R-diagrammeR], and `kableextra` [@R-kableextra].
 

### 2021-07-09 AST-Framing-Ontario/AST-Framing-Ontario.tex
PDF of article rendered to visualize figures and tables

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

  \journal{Journal of Transport \& Health} % Sets Journal name

\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={How do school travel planning stakeholders frame active school travel in Ontario, Canada?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}

% Pandoc citation processing

% Pandoc header
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}
\begin{frontmatter}

  \title{How do school travel planning stakeholders frame active school travel in
Ontario, Canada?}
    \author[Some Department]{Author 1\corref{1}}
   \ead{author1@example.com} 
    \author[Some Department]{Author 2}
   \ead{author2@example.com} 
    \author[Another University]{Author 3\corref{2}}
   \ead{author3@example.com} 
    \author[Some Institute]{Author 4\corref{2}}
   \ead{author4@example.com} 
    \author[Some University]{Author 5}
   \ead{author5@example.com} 
    \author[Some Department]{Author 6}
   \ead{author6@example.com} 
      \address[Some Department]{Department, Street, City, Province, Postal Code}
    \address[Another University]{Department, Street, City, Province, Postal Code}
    \address[Some Institute]{Street, City, Province, Postal Code}
    \address[Some University]{Department, Street, City, Province, Postal Code}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

  \begin{abstract}
  This is the abstract.

  It consists of two paragraphs.
  \end{abstract}

 \end{frontmatter}

\textbf{\emph{Background}}:\\
\textbf{\emph{Methods}}:\\
\textbf{\emph{Results}}: \textbf{\emph{Conclusions}}:

\newpage

\hypertarget{introduction}{%
\section{1. Introduction}\label{introduction}}

\hypertarget{school-travel-planning-in-canada}{%
\subsection{1.1. School travel planning in
Canada}\label{school-travel-planning-in-canada}}

Walking and bicycling to school, commonly known as active school travel
or active school transportation (AST), has been declining in Canada and
North America for decades ({\textbf{???}}), with levels much lower than
other developed countries like The Netherlands ({\textbf{???}}) and
Japan ({\textbf{???}}). This trend has prompted a multi-sector response
to identify strategies to increase AST, the most popular of which is a
growing interest in school travel planning across Canada.

School travel planning (STP) is a ``school-specific'' intervention led
by a facilitator that brings together a committee of stakeholders from
diverse sectors including education, planning, transportation, and
public health ({\textbf{???}}). Parents and parent councils also
typically have a role in supporting or implementing STP. The
intervention encourages participation from the broader community and
collaboration between involved stakeholders, who contribute their
expertise to remove ``school-specific'' barriers to AST and to identify
strategies for promoting and encouraging AST. STP may also involve other
stakeholders including local advocacy groups or environmental
organizations who are familiar with the state of AST at the
community-level. Buliung et al.~({\textbf{???}}) piloted an STP
intervention at 12 schools in 4 Canadian provinces and reported that it
increased AST rates and led to a ``mobilization of diverse community
resources''. Since this seminal study, STP interventions have become
increasingly popular and common at schools across Canada and have even
attracted funding from provincial governments.

\hypertarget{correlates-of-active-school-travel}{%
\subsection{1.2. Correlates of active school
travel}\label{correlates-of-active-school-travel}}

Factors that influence AST are typically conceptualized according to the
socioecological model whereby children's travel behaviour is understood
within the context of their household, social, and built environments
(see {\textbf{???}}). At the individual level, older child age is often
associated with AST ({\textbf{???}}; {\textbf{???}}; {\textbf{???}}).
There is some evidence that gender is a determinant of AST
({\textbf{???}}; {\textbf{???}}), although this is not a strong or
consistent finding ({\textbf{???}}; {\textbf{???}}). Distance between
home and school is associated with AST ({\textbf{???}}; {\textbf{???}};
{\textbf{???}}; {\textbf{???}}) with less AST reported among children
who have to travel farther to school. Car ownership is an important
household-level influence on AST ({\textbf{???}}; {\textbf{???}};
{\textbf{???}}), as is household income ({\textbf{???}}). Parental
perceptions of the environment ({\textbf{???}}; {\textbf{???}}) and
children's skills ({\textbf{???}}) also influence whether they allow
their children to walk or cycle to school. Finally, many studies have
found that the quality of the built environment ({\textbf{???}};
{\textbf{???}}) and active travel infrastructure ({\textbf{???}})
facilitate AST. Concerns about traffic and strangers have been reported
by parents who drive their children to school ({\textbf{???}}). The
consensus is that all of these factors are interrelated and that
interventions ought to target multiple factors in order to increase
walking and bicycling levels to school.

\hypertarget{benefits-of-ast}{%
\subsection{1.3. Benefits of AST}\label{benefits-of-ast}}

The desire to increase AST is warranted - there is strong evidence that
children who walk and bicycle to school accrue physical and mental
health benefits. Many studies and reviews have focused on the
association between AST or CIM and physical activity (e.g.,
{\textbf{???}}; {\textbf{???}}; {\textbf{???}}), with findings
consistently demonstrating that children who travel by walking or
bicycling to school are more active than their peers who do not use
active travel. More recently, researchers have been exploring the link
between transport and children's wellbeing ({\textbf{???}};
{\textbf{???}}), which has relevant applications to the study of school
travel and satisfaction (see {\textbf{???}}). CIM is also important for
different domains of children's health and wellbeing ({\textbf{???}}).
It offers benefits such as increasing traffic and safety skills,
boosting spatial awareness when navigating public spaces, and providing
more opportunity for social interaction with peers ({\textbf{???}}).

\hypertarget{encouraging-adoption-of-active-school-travel}{%
\subsection{1.4. Encouraging adoption of active school
travel}\label{encouraging-adoption-of-active-school-travel}}

To increase rates of walking and bicycling independently to school,
Riazi et al.~({\textbf{???}}) state: ``it will be vital for
interventions to target modifiable factors, including children's and
parents' perceptions of their social environment.'' Parents play the
important role of ``gatekeeper'' by either granting or restricting CIM
licenses, meaning whether children can travel alone ({\textbf{???}}).
For this reason, stakeholders involved in STP produce information
targeted for both children and parents, and aim to involve the broader
community in their efforts to increase the number of children walking
and bicycling to school..

However, the ways in which interventions like STP are framed to their
target audience can ultimately influence how they are received and
whether they result in behaviour change. The correlates of AST are
important knowledge for policymakers because they identify points of
intervention and potential benefits that ought to be communicated to the
public encourage adoption of AST and to build support for new planning
paradigms. What is less clear is how CIM plays into the consideration of
policymakers when they act on the objective of increasing AST.

Any goals for AST, and also CIM, ought to be clearly articulated and
reflected in transportation plans and policies to guide initiatives.
Presently, however, there has been no study to date that explores how
Canadian municipalities and schools frame and discuss AST with the
public. Content analysis is one method to analyze how particular issues
are framed to groups of people, for instance parents or educators who
might be inclined to support AST. It attempts to understand how
information presented from a ``communicator'' leads the ``receiver'' to
a desired response ({\textbf{???}}). In a recent paper ({\textbf{???}}),
framing analysis was applied to review municipal policies addressing
climate change in four western Canadian cities. Natural language
processing (NLP) was used for a similar purpose to examine content in
general plans from Californian cities ({\textbf{???}}). The way policy
issues are framed is important to understand because it plays a role in
either altering or preserving the existing social perceptions.

\hypertarget{study-aim}{%
\subsection{1.5. Study aim}\label{study-aim}}

In 2017, the provincial government of Ontario in Canada issued funding
to Green Communities Canada (GCC), a non-profit organization, to launch
the \emph{Ontario Active School Travel} (OAST) program. The program
provides funding for school and community-based initiatives and supports
stakeholders in municipalities across the province to implement STP and
other interventions aimed at increasing AST. As of 2021, OAST has funded
\emph{X} projects in Ontario. GCC continues has funded projects across
Ontario led by collaborative groups involving school boards, municipal
or regional governments, and regional transportation consortia. The
latter are dedicated transportation bodies that deliver efficient and
effective transportation services, which generally focus on providing
the school busing service to families in their associated region.

The aim of this paper is to analyze how AST is framed by STP
stakeholders in Ontario, Canada. We used topic modelling and qualitative
content analysis to examine how the benefits and barriers of AST are
presented to the public and which solutions for improving AST are
identified in local policy documents from Ontario municipalities and
school boards. We compared these documents to a selection of studies on
AST to explore the extent to which research findings have trickled down
to inform policy and planning for AST interventions.

\hypertarget{data}{%
\section{2. Data}\label{data}}

\hypertarget{data-retrieval}{%
\subsection{2.1. Data retrieval}\label{data-retrieval}}

\hypertarget{policy-documents}{%
\subsubsection{2.1.1. Policy documents}\label{policy-documents}}

We then assembled a collection of publicly available documents that were
sourced online from the main stakeholder groups involved in STP
initiatives in Ontario: i) English school boards; ii) municipal
government; and iii) transportation consortia. Non-profit organizations,
police services, and advocacy groups are other stakeholders who may play
a role in supporting AST and/or STP, but this study does not include any
documents from these groups because they are not consistently
participating in initiatives.

The search was guided first by a list of all English school boards
across Ontario. The websites of each school board were searched for
pages related to transportation or school travel. These pages were
manually downloaded. Next, we collected documents by searching municipal
government and transportation consortia websites. The latter were
identified based on geographic area (i.e., the municipalities and/or
transportation consortia who are in the same geographic area of each
school board). Pages related to active transportation or school travel
were manually downloaded. Webpages were included in the corpus if they
were easy to find. This primary criteria was important since our
analysis pertains to how such issues are framed to the public. Thus,
these pages ought to be easy to find, which we defined as requiring no
more than 2-4 separate links from the initial Google search.

The initial corpus of policy documents included 64 relevant webpages
(i.e., one page or more) from all main stakeholder groups. It is
important to note that school boards, municipalities, and transportation
consortia may or may not publish information about their involvement in
AST and STP efforts on their respective websites or in policy documents.
Search results are summarized in Table \ref{tab:policy-documents}.

\begin{table}

\caption{\label{tab:policy-documents}\label{tab:search-results}Search results from the main STP stakeholder groups.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{}l|>{\raggedright\arraybackslash}p{30em}|>{}l}
\toprule
Stakeholder & Total & Included\\
\midrule
\cellcolor{gray!6}{\textbf{English school boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{31}\\
\textbf{Municipalities or regions} & 62 & 25\\
\cellcolor{gray!6}{\textbf{Transportation consortia}} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{8}\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{academic-papers}{%
\subsubsection{2.2.1. Academic papers}\label{academic-papers}}

\hypertarget{data-cleaning}{%
\subsection{2.2. Data cleaning}\label{data-cleaning}}

A multi-step process was conducted to ensure that the analysis captured
as much content as possible from both the policy documents (n = 64) and
academic papers (n = 233). To begin, the webpages, which were manually
downloaded in portable document format (PDF), were trimmed so that pages
that only consisted of tables, figures, or references were removed. Many
academic papers were in a two-column format, which is not ideal for
conversion to \texttt{txt}. We adapted a procedure
(https://stackoverflow.com/questions/42541849/extract-text-from-two-column-pdf-with-r)
to read the two-column PDF documents so that they would be converted
correctly. Four academic papers did not join sufficiently and were taken
out of the corpus due to the substantial time required to manually
correct their inconsistencies.

Next, we converted the trimmed PDF documents into \texttt{txt} files so
that they could be imported in \texttt{R} for topic modelling. We then
proceeded to a manual cleaning phase where we removed any remaining
tables, figures, references, headers/footings, and captions that could
not be trimmed. Manual corrections were also required for certain pages
in academic papers that remained in two-column format after the
conversion process. This typically occurred on pages that had a table or
figure which disrupted the text. Finally, we reviewed all of the
documents to remove hyphenation by line breaks and to keep hyphenated
words together on the same line. Any ligatures (e.g., combinations of
characters or letters that were not properly detected during the
conversion process) were fixed by inserting the unicode sequence of
character to replace the missing sequence of characters.

We also manually removed any extraneous material in the academic papers
that did not pertain to AST specifically. This included footnotes,
references, acknowledgments, and conflict of interest statements in the
academic papers. We removed all phone numbers, inserted links to other
webpages, personal names, and content not to specific to AST from the
policy documents that were retrieved from the websites of school boards,
municipalities, and transportation consortia.

In the final step before analysis, we removed all blank spaces,
punctuation, capitalization, and numbers. English stop words, which are
common words such as \emph{and} or \emph{the} as identified in a
predetermined list by Lewis et al.~({\textbf{???}}) and other frequent
terms in the documents like ``school'' and location names were removed
from the corpora.

\hypertarget{methods}{%
\section{3. Methods}\label{methods}}

\hypertarget{natural-language-processing}{%
\subsection{3.1. Natural language
processing}\label{natural-language-processing}}

Natural language processing

Silge and Robinson ({\textbf{???}}) is

We've been using the unnest\_tokens function to tokenize by word, or
sometimes by sentence, which is useful for the kinds of sentiment and
frequency analyses we've been doing so far. But we can also use the
function to tokenize into consecutive sequences of words, called
n-grams. By seeing how often word X is followed by word Y, we can then
build a model of the relationships between them.

We do this by adding the token = ``ngrams'' option to unnest\_tokens(),
and setting n to the number of words we wish to capture in each n-gram.
When we set n to 2, we are examining pairs of two consecutive words,
often called ``bigrams'':

\hypertarget{content-analysis}{%
\subsection{3.2. Content analysis}\label{content-analysis}}

Content analysis is a method to examine content from texts including the
message itself, the sender(s) of the message, the recipients of the
message, or the impact of the message ({\textbf{???}}). Words or phrases
are the unit of analysis. \emph{Qualitative} content analysis

\hypertarget{reproducibility}{%
\subsection{3.3. Reproducibility}\label{reproducibility}}

This paper is an example of open and reproducible research that uses
only open software. All data were obtained from publicly available
sources and organized in the form of a data package. Following best
practices in spatial data science ({\textbf{???}}), the code and data
needed to reproduce or conduct a similar analysis for other regions in
North America or elsewhere are available for download.

\hypertarget{results}{%
\section{4. Results}\label{results}}

\hypertarget{word-and-document-frequency}{%
\subsection{4.1. Word and document
frequency}\label{word-and-document-frequency}}

We analyzed word and document frequency for each corpus. Table
\ref{tab:word-table} presents the most common terms found in the
municipal, transportation consortia, school board, and academic
documents.

\begin{table}

\caption{\label{tab:word-table}\label{tab:word-table}Top 25 terms identified in each corpora. Document frequencies are also indicated.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lcclcclcclcc}
\toprule
\multicolumn{3}{c}{Municipalities} & \multicolumn{3}{c}{School Boards} & \multicolumn{3}{c}{Transportation Consortia} & \multicolumn{3}{c}{Academic Papers} \\
\cmidrule(l{3pt}r{3pt}){1-3} \cmidrule(l{3pt}r{3pt}){4-6} \cmidrule(l{3pt}r{3pt}){7-9} \cmidrule(l{3pt}r{3pt}){10-12}
Term & Count (n) & Documents (n) & Term & Count (n) & Documents (n) & Term & Count (n) & Documents (n) & Term & Count (n) & Documents (n)\\
\midrule
\cellcolor{gray!6}{active} & \cellcolor{gray!6}{248} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{active} & \cellcolor{gray!6}{124} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{active} & \cellcolor{gray!6}{67} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{5137} & \cellcolor{gray!6}{222}\\
travel & 126 & 20 & bus & 120 & 20 & walking & 55 & 8 & parents & 3946 & 211\\
\cellcolor{gray!6}{walking} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{119} & \cellcolor{gray!6}{30} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{49} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{distance} & \cellcolor{gray!6}{3271} & \cellcolor{gray!6}{205}\\
bike & 87 & 15 & travel & 103 & 11 & travel & 41 & 8 & students & 2960 & 173\\
\cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{78} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{student} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{2753} & \cellcolor{gray!6}{171}\\
\addlinespace
safety & 71 & 21 & information & 65 & 21 & safety & 32 & 6 & environment & 2631 & 202\\
\cellcolor{gray!6}{health} & \cellcolor{gray!6}{65} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{schools} & \cellcolor{gray!6}{61} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{help} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{activity} & \cellcolor{gray!6}{2371} & \cellcolor{gray!6}{209}\\
physical & 63 & 18 & board & 61 & 26 & schools & 25 & 9 & traffic & 2353 & 208\\
\cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{59} & \cellcolor{gray!6}{20} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{57} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{children} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{choice} & \cellcolor{gray!6}{2299} & \cellcolor{gray!6}{169}\\
road & 56 & 13 & walk & 53 & 13 & community & 24 & 7 & physical & 2256 & 215\\
\addlinespace
\cellcolor{gray!6}{activity} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{district} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{bus} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{trips} & \cellcolor{gray!6}{2194} & \cellcolor{gray!6}{170}\\
schools & 52 & 14 & weather & 40 & 11 & route & 17 & 5 & car & 2148 & 195\\
\cellcolor{gray!6}{children} & \cellcolor{gray!6}{47} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{40} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{zone} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{2140} & \cellcolor{gray!6}{204}\\
plan & 45 & 16 & safe & 39 & 19 & resources & 16 & 6 & time & 2101 & 218\\
\cellcolor{gray!6}{students} & \cellcolor{gray!6}{44} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{services} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{factors} & \cellcolor{gray!6}{2101} & \cellcolor{gray!6}{216}\\
\addlinespace
walk & 43 & 18 & planning & 37 & 7 & safe & 15 & 5 & child & 2085 & 187\\
\cellcolor{gray!6}{public} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{parents} & \cellcolor{gray!6}{32} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{200}\\
will & 38 & 15 & sustainable & 31 & 8 & physical & 15 & 7 & public & 1983 & 208\\
\cellcolor{gray!6}{community} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{may} & \cellcolor{gray!6}{30} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{age} & \cellcolor{gray!6}{1783} & \cellcolor{gray!6}{211}\\
safe & 34 & 16 & children & 30 & 14 & traffic & 13 & 6 & urban & 1768 & 200\\
\addlinespace
\cellcolor{gray!6}{benefits} & \cellcolor{gray!6}{32} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{support} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{home} & \cellcolor{gray!6}{1715} & \cellcolor{gray!6}{199}\\
play & 31 & 2 & child & 29 & 12 & families & 13 & 5 & social & 1713 & 191\\
\cellcolor{gray!6}{resources} & \cellcolor{gray!6}{30} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{cancellations} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{way} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{different} & \cellcolor{gray!6}{1713} & \cellcolor{gray!6}{215}\\
healthy & 29 & 16 & routes & 28 & 14 & student & 12 & 5 & mobility & 1659 & 138\\
\cellcolor{gray!6}{routes} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{physical} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{significant} & \cellcolor{gray!6}{1650} & \cellcolor{gray!6}{208}\\
\bottomrule
\multicolumn{12}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{12}{l}{\rule{0pt}{1em} }\\
\multicolumn{12}{l}{\rule{0pt}{1em}\textsuperscript{a} Count (n) refers to the total number of times the term is found in the corpora}\\
\multicolumn{12}{l}{\rule{0pt}{1em}\textsuperscript{b} Documents (n) refers to the total number of documents that feature the term}\\
\end{tabular}}
\end{table}

\hypertarget{bigrams-and-correlations}{%
\subsection{4.2. Bigrams and
correlations}\label{bigrams-and-correlations}}

Bigrams for each policy corpora are shown in Figures
\ref{fig:city-bigrams}, \ref{fig:consortia-bigrams}, and
\ref{fig:school-bigrams}. These figures help to make further sense of
the word frequencies reported above, and highlight the main ideas that
are presented to the public in each of the policy corpora.
Municipalities primarily discuss ``physical activity'' (n = 53) and
``public health'' (n = 19) in the context of active travel. In addition,
``travel planning'' (n = 19), ``bike lanes'' (n = 16), and ``safe
routes'' (n = 14) are also identified, conceivably as interventions and
built environment factors that support AST. Key issues related to AST
such as ``traffic safety'' (n = 10), ``air quality'' (n = 9), and
``greenhouse gases'' (n = 9) are conveyed to the public but in fewer
documents. Similar word bigrams are found in school board documents:
``travel planning'' (n = 33), ``safe routes'' (n = 15), ``physical
activity'' (n = 10), and ``public health'' (n = 10) are among the most
common bigrams. Unlike other STP stakeholders, school boards also
consider ``inclement weather'' (n = 24) ``bus cancellations'' (n = 13).
This is likely because many students in Ontario travel by school bus and
this information is presented alongside AST. Finally, transportation
consortia documents highlight ``physical activity'' (n = 10),
``pedestrian safety'' (n = 8), ``crossing guards'' (n = 6), ``travel
planning'' (n = 6), and ``walk zones'' (n = 6). Bicycling is notably
absent from transportation consortia documents.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/city-visual-1}

}

\caption{Most common bigrams found in the municipal or regional government documents.}\label{fig:city-visual}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/consortia-visual-1}

}

\caption{Most common bigrams found in the transportation consortia documents.}\label{fig:consortia-visual}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/school-visual-1}

}

\caption{Most common bigrams found in the school board documents.}\label{fig:school-visual}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/policy-visual-1}

}

\caption{Most common bigrams found in all of the policy documents (i.e., school board, municipality, and transportation consortia combined.}\label{fig:policy-visual}
\end{figure}

The academic corpora includes several common bigrams that were also
found in the policy documents including ``physical activity'' (n =
1566), which is the top bigram, ``traffic safety'' (n = 308), and ``safe
routes'' (n = 268). However, many other factors relating to AST are
identified in the research literature that are not presented to the
public through policy documents. After ``physical activity'', ``built
environment'' (n = 1175), ``independent mobility'' (n = 774), and
``urban form'' (n = 352) are the most frequent pairs of consecutive
words. Academic papers also often discuss ``distance home'' (n = 258),
``car ownership'' (n = 254), ``household income'' (n = 254), and
``population density'' (n = 205), which are factors that have been known
to influence AST. It is evident that many papers investigate gender
differences in AST given that ``boys girls'' (n = 211) is a common
bigram. Finally, the presence of ``statistically significant'' on the
list of top-25 bigrams underscores the importance of identifying factors
that are not due to chance but that likely influence AST.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/academic-visual-1}

}

\caption{Most common bigrams found in the academic papers.}\label{fig:academic-visual}
\end{figure}

\hypertarget{qualitative-findings-of-policy-documents}{%
\subsection{4.3. Qualitative findings of policy
documents}\label{qualitative-findings-of-policy-documents}}

We used the most common bigrams from the policy corpus (see Figure
\ref{fig:policy-visual}), which includes all documents from
municipalities, transportation consortia, and school boards, as
categories of codes for qualitative content analysis. This means that we
interpreted the bigrams to represent the main ideas that STP
stakeholders are communicating to the public about AST.

\hypertarget{discussion}{%
\section{5. Discussion}\label{discussion}}

\hypertarget{framing-of-ast-in-policy-documents}{%
\subsection{5.1. Framing of AST in policy
documents}\label{framing-of-ast-in-policy-documents}}

The presence of ``travel planning'' among the top pairs of consecutive
words for municipalities, school boards, and transportation consortia
reflects the

\hypertarget{framing-of-ast-in-academic-papers}{%
\subsection{5.2. Framing of AST in academic
papers}\label{framing-of-ast-in-academic-papers}}

Notably absent from the policy corpora is children's independent
mobility (CIM). AST is one of the most common opportunities for children
to travel without adult supervision on a regular basis, yet STP
stakeholders do not discuss this topic. CIM was first described by
Hillman et al.~({\textbf{???}}) as the freedom of children to travel and
play within their neighborhood and city without the presence of adults.
The ability of children to reach destinations such as school or local
parks by walking or bicycling on their own is a growing area of research
that is related to and often overlaps with the body of literature on
AST.

In a study conducted in multiple Canadian cities, Riazi et
al.~({\textbf{???}}) found that a range of factors such as child grade,
car ownership, and parental perceptions of safety and environment were
associated with CIM. Parental perceptions of children's autonomy also
influences CIM ({\textbf{???}}). In addition to independent trips to
school, children also travel by walking or bicycling on their own to
other non-school destinations such as outdoor spaces (i.e., parks,
playgrounds), the homes of family members or friends, shopping places,
and libraries, to name a few ({\textbf{???}}; {\textbf{???}}).

\hypertarget{implications-for-school-travel-planning}{%
\subsection{5.3. Implications for School Travel
Planning}\label{implications-for-school-travel-planning}}

School boards and educators are an influential contributor to AST and
STP efforts in Canada.

\hypertarget{limitations}{%
\subsection{5.4. Limitations}\label{limitations}}

\hypertarget{conclusion}{%
\section{6.1. Conclusion}\label{conclusion}}

\hypertarget{future-research}{%
\subsection{6.1. Future research}\label{future-research}}

\hypertarget{acknowledgments}{%
\section{Acknowledgments}\label{acknowledgments}}

This research was completed using open software, and the authors wish to
acknowledge the developers of the following \texttt{R} packages:
\texttt{dplyr} ({\textbf{???}}), \texttt{ggraph} ({\textbf{???}}),
\texttt{ggplot2} ({\textbf{???}}), \texttt{igraph} ({\textbf{???}}),
\texttt{pdftools} ({\textbf{???}}), \texttt{readr} ({\textbf{???}}),
\texttt{reshape2} ({\textbf{???}}), \texttt{stringr} ({\textbf{???}}),
\texttt{text2vec} ({\textbf{???}}), \texttt{textdata} ({\textbf{???}}),
\texttt{tidyr} ({\textbf{???}}), \texttt{tidytext} ({\textbf{???}}),
\texttt{tm} ({\textbf{???}}), \texttt{tools} ({\textbf{???}}),
\texttt{topicmodels} ({\textbf{???}}), \texttt{widyr} ({\textbf{???}}),
\texttt{word2vec} ({\textbf{???}}), \texttt{wordcloud} ({\textbf{???}}),
\texttt{DiagrammeR} ({\textbf{???}}), and \texttt{kableextra}
({\textbf{???}}).

\hypertarget{references}{%
\section{References}\label{references}}

\end{document}

### 2021-07-09 AST-Framing-Ontario/AST-Framing-Ontario.Rmd

@@
 
+```{r}
+MunicipalTextDF <- data.frame(text = sapply(municipal_corpus, as.character), stringsAsFactors = FALSE)
+
+M_it_train = itoken(MunicipalTextDF$text, progressbar = FALSE)
+municipal_vocab = create_vocabulary(M_it_train)
+
+municipal_vocab <- prune_vocabulary(municipal_vocab, term_count_min = 5)
+municipal_vocab
+```
+
+```{r}
+ConsortiumTextDF <- data.frame(text = sapply(consortium_corpus, as.character), stringsAsFactors = FALSE)
+
+C_it_train = itoken(ConsortiumTextDF$text, progressbar = FALSE)
+consortium_vocab = create_vocabulary(C_it_train)
+
+consortium_vocab <- prune_vocabulary(consortium_vocab, term_count_min = 5)
+consortium_vocab
+```
+
+```{r}
+SchoolTextDF <- data.frame(text = sapply(school_corpus, as.character), stringsAsFactors = FALSE)
+
+S_it_train = itoken(SchoolTextDF$text, progressbar = FALSE)
+school_vocab = create_vocabulary(S_it_train)
+
+school_vocab <- prune_vocabulary(school_vocab, term_count_min = 5)
+school_vocab
+```
+
+```{r}
+PolicyTextDF <- data.frame(text = sapply(policy_corpus, as.character), stringsAsFactors = FALSE)
+
+P_it_train = itoken(PolicyTextDF$text, progressbar = FALSE)
+policy_vocab = create_vocabulary(P_it_train)
+
+policy_vocab <- prune_vocabulary(policy_vocab, term_count_min = 5)
+policy_vocab
+```
+
 ```{r city-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the municipal or regional government documents."}

### 2021-07-09 AST-Framing-Ontario/Data Pre-Processesing Roughwork.rmd

@@
 
+Word Pairs and Correlation
+
 ```{r}
@@
 ```
+
 ```{r}

### 2021-07-09 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Update kwic code with raw policy corpus
If using the cleaned policy corpus, the context around the keyword (as identified using the kwic function from quanteda) is somewhat distorted as stop words and punctuation have been removed. Using the raw policy corpus (not cleaned) yields more useful information.

@@
 ```{r policy-concordance, echo=FALSE}
-# Import VCorpus created by tm package
+# Import raw policy VCorpus (not cleaned of stop words or punctuation) created by tm package
 
-policy_quanteda <- tm::VCorpus(tm::VectorSource(policy_corpus))
+policy_quanteda <- tm::VCorpus(tm::VectorSource(raw_policy_corpus))
 policy_quanteda <- corpus(policy_quanteda)
@@
 
-kwic_pol_physical <- kwic(tokens(policy_quanteda), pattern = "physical")
-kwic_pol_mental <- kwic(tokens(policy_quanteda), pattern = "mental")
-kwic_pol_air <- kwic(tokens(policy_quanteda), pattern = "air")
-kwic_pol_traffic <- kwic(tokens(policy_quanteda), pattern = "traffic")
-kwic_pol_safety <- kwic(tokens(policy_quanteda), pattern = "safety")
-kwic_pol_health <- kwic(tokens(policy_quanteda), pattern = "health")
-kwic_pol_emissions <- kwic(tokens(policy_quanteda), pattern = "emissions")
-kwic_pol_routes <- kwic(tokens(policy_quanteda), pattern = "routes")
-kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes")
-kwic_pol_zone <- kwic(tokens(policy_quanteda), pattern = "zone")
-kwic_pol_bus <- kwic(tokens(policy_quanteda), pattern = "bus")
-kwic_pol_comm <- kwic(tokens(policy_quanteda), pattern = "community")
-kwic_pol_ben <- kwic(tokens(policy_quanteda), pattern = "benefit")
-kwic_pol_wea <- kwic(tokens(policy_quanteda), pattern = "weather")
-kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes")
+kwic_pol_physical <- kwic(tokens(policy_quanteda), pattern = "physical", window = 10)
+kwic_pol_mental <- kwic(tokens(policy_quanteda), pattern = "mental", window = 10)
+kwic_pol_air <- kwic(tokens(policy_quanteda), pattern = "air", window = 10)
+kwic_pol_traffic <- kwic(tokens(policy_quanteda), pattern = "traffic", window = 10)
+kwic_pol_safety <- kwic(tokens(policy_quanteda), pattern = "safety", window = 10)
+kwic_pol_health <- kwic(tokens(policy_quanteda), pattern = "health", window = 10)
+kwic_pol_emissions <- kwic(tokens(policy_quanteda), pattern = "emissions", window = 10)
+kwic_pol_routes <- kwic(tokens(policy_quanteda), pattern = "routes", window = 10)
+kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes", window = 10)
+kwic_pol_zone <- kwic(tokens(policy_quanteda), pattern = "zone", window = 10)
+kwic_pol_bus <- kwic(tokens(policy_quanteda), pattern = "bus", window = 10)
+kwic_pol_comm <- kwic(tokens(policy_quanteda), pattern = "community", window = 10)
+kwic_pol_ben <- kwic(tokens(policy_quanteda), pattern = "benefit", window = 10)
+kwic_pol_wea <- kwic(tokens(policy_quanteda), pattern = "weather", window = 10)
+kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes", window = 10)
 ```

### 2021-08-06 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
KWIC completed and TM in progress

@@
 load(file= "Corpus .rda/policy_corpus.rda")
+load(file= "Corpus .rda/raw_policy_corpus.rda")
 ```
@@
 
-Natural language processing [see @silgetextmining2021]
-
-Topic modelling
-
 ## 3.2. Reproducibility
@@
 ```{r top-word-frequencies, echo=FALSE}
-municipal_words <- municipal_vocab %>% slice(1939:1915)
-school_words <- school_vocab %>% slice(1861:1837)
+municipal_words <- municipal_vocab %>% slice(1938:1914)
+school_words <- school_vocab %>% slice(1812:1788)
 consortia_words <- consortium_vocab[-c(971),] %>% slice(993:968)
-academic_words <- academic_vocab[-c(1309, 1304),] %>% slice(1311:1285)
+academic_words <- academic_vocab[-c(1302, 1297),] %>% slice(1304:1278)
 ```
@@
 municipal_lda_num <- FindTopicsNumber(
-  municipal_dtm, # Check with other DTM
-  topics = seq(from = 5, to = 20, by = 2),
+  municipal_dtm, 
+  topics = seq(from = 1, to = 10, by = 1),
   metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
@@
 school_lda_num <- FindTopicsNumber(
-  school_dtm, # Check with other DTM
-  topics = seq(from = 5, to = 20, by = 2),
+  school_dtm, 
+  topics = seq(from = 1, to = 10, by = 1),
   metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
@@
 consortia_lda_num <- FindTopicsNumber(
-  consortia_dtm, # Check with other DTM
-  topics = seq(from = 5, to = 20, by = 2),
+  consortia_dtm, 
+  topics = seq(from = 1, to = 10, by = 1),
   metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
@@
 policy_lda_num <- FindTopicsNumber(
-  policy_dtm, # Check with other DTM
-  topics = seq(from = 5, to = 20, by = 2),
+  policy_dtm,
+  topics = seq(from = 1, to = 10, by = 1),
   metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
@@
 )
+```
+
+```{r topics-academic, echo=FALSE, cache=TRUE}
+# DO NOT RUN EVERY TIME - takes approximately 20 minutes
 
 #academic_lda_num <- FindTopicsNumber(
-  #academic_dtm, # Check with other DTM
+  #academic_dtm, 
   #topics = seq(from = 2, to = 50, by = 5),
@@
 
-#FindTopicsNumber_plot(municipal_lda_num)
+FindTopicsNumber_plot(municipal_lda_num)
 FindTopicsNumber_plot(school_lda_num)
-#FindTopicsNumber_plot(consortia_lda_num)
-#FindTopicsNumber_plot(policy_lda_num)
-#FindTopicsNumber_plot(academic_lda_num)
+FindTopicsNumber_plot(consortia_lda_num)
+FindTopicsNumber_plot(policy_lda_num)
+#(academic_lda_num)
 
-# The output suggests that there are 9 topics in the municipal corpus
-# The output suggests that there are 9 topics in the school corpus
-# The output suggests that there are 7 topics in the municipal corpus
-# The output suggests that there are 9 topics in the municipal corpus
-# The output suggests that there are ? topics in the municipal corpus
+# The graphs suggest that there are 7 topics for the municipal corpora
+# The graphs suggest that there are 7 topics for the school corpora
+# The graphs suggest that there are 5 topics for the municipal corpora
+# The graphs suggest that there are 5 topics for the policy corpora
+# The graphs suggest that there are 22 topics for the academic corpora
 ```
@@
 ```{r corpus-lda-model, echo=FALSE}
-municipal_lda <- LDA(municipal_dtm, k = 9)
-school_lda <- LDA(school_dtm, k = 9)
-consortia_lda <- LDA(consortia_dtm, k = 7)
-policy_lda <- LDA(policy_dtm, k = 9)
-#academic_lda <- LDA(academic_dtm, k = ?)
+municipal_lda <- LDA(municipal_dtm, k = 3, control=list(seed = 1, verbose = 25))
+
+school_lda <- LDA(school_dtm, k = 3, control=list(seed = 1, verbose = 25))
+
+consortia_lda <- LDA(consortia_dtm, k = 3, control=list(seed = 1, verbose = 25))
+
+policy_lda <- LDA(policy_dtm, k = 3, control=list(seed = 1, verbose = 25))
+
+#academic_lda <- LDA(academic_dtm, k = 22, control=list(seed = 1, verbose = 25))
 ```
@@
 
-```{r academic-terms, echo=FALSE}
+```{r academic-terms, echo=FALSE, cache=TRUE}
 # Do not run; number of topics is not yet determined
 
-academic_top_terms <- academic_topics %>%
-  group_by(topic) %>%
-  slice_max(beta, n = 10) %>% 
-  ungroup() %>%
-  arrange(topic, -beta)
+#academic_top_terms <- academic_topics %>%
+  #group_by(topic) %>%
+  #slice_max(beta, n = 10) %>% 
+  #ungroup() %>%
+  #arrange(topic, -beta)
 
-academic_top_terms %>%
-  mutate(term = reorder_within(term, beta, topic)) %>%
-  ggplot(aes(beta, term, fill = factor(topic))) +
-  geom_col(show.legend = FALSE) +
-  facet_wrap(~ topic, scales = "free") +
-  scale_y_reordered()
+#academic_top_terms %>%
+  #mutate(term = reorder_within(term, beta, topic)) %>%
+  #ggplot(aes(beta, term, fill = factor(topic))) +
+  #geom_col(show.legend = FALSE) +
+  #facet_wrap(~ topic, scales = "free") +
+  #scale_y_reordered()
 ```
@@
 policy_documents <- tidy(policy_lda, matrix = "gamma")
-academic_documents <- tidy(academic_lda, matrix = "gamma")
+#academic_documents <- tidy(academic_lda, matrix = "gamma")
 ```
@@
 
-## 5.1. Framing of AST in policy documents
+## 5.1. Implications for School Travel Planning
 
-The presence of _travel planning_ among the top pairs of consecutive words for municipalities, school boards, and transportation consortia reflects the priority given to this intervention in Ontario.
-
-## 5.2. Framing of AST in academic papers
-
-Notably absent from the policy corpora is _children's independent mobility_ (CIM).
-AST is one of the most common opportunities for children to travel without adult supervision on a regular basis, yet STP stakeholders do not discuss this topic.
-CIM was first described by Hillman et al.
-[-@hillmanOneFalseMove1990] as the freedom of children to travel and play within their neighborhood and city without the presence of adults.
-The ability of children to reach destinations such as school or local parks by walking or bicycling on their own is a growing area of research that is related to and often overlaps with the body of literature on AST.
-
-In a study conducted in multiple Canadian cities, Riazi et al.
-[-@riaziCorrelatesChildrenIndependent2019] found that a range of factors such as child grade, car ownership, and parental perceptions of safety and environment were associated with CIM.
-Parental perceptions of children's autonomy also influences CIM [@alparoneChildrenIndependentMobility2012].
-In addition to independent trips to school, children also travel by walking or bicycling on their own to other non-school destinations such as outdoor spaces (i.e., parks, playgrounds), the homes of family members or friends, shopping places, and libraries, to name a few [@badlandAssessingNeighbourhoodDestination2015; @villanuevaWhereChildrenTravel2013a].
-
-## 5.3. Implications for School Travel Planning
-
-School boards and educators are an influential contributor to AST and STP efforts in Canada.
-
-## 5.4. Limitations
+## 5.2. Limitations
 

### 2021-08-06 AST-Framing-Ontario/AST-Framing-Ontario.tex
KWIC completed and TM in progress

@@
 \bibliographystyle{elsarticle-harv}
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\usepackage{graphicx}
 \ifxetex
@@
 community in their efforts to increase the number of children walking
-and bicycling to school..
+and bicycling to school.
 
@@
 climate change in four western Canadian cities. Natural language
-processing (NLP) was used for a similar purpose to examine content in
-general plans from Californian cities ({\textbf{???}}). The way policy
-issues are framed is important to understand because it plays a role in
-either altering or preserving the existing social perceptions.
+processing (NLP) has also been used for a similar purpose to examine
+content in general plans from Californian cities ({\textbf{???}}). The
+way policy issues are framed is ultimately important to understand
+because it plays a role in either altering or preserving the existing
+social perceptions.
 
@@
 The aim of this paper is to analyze how AST is framed by STP
-stakeholders in Ontario, Canada. We used topic modelling and qualitative
-content analysis to examine how the benefits and barriers of AST are
-presented to the public and which solutions for improving AST are
-identified in local policy documents from Ontario municipalities and
-school boards. We compared these documents to a selection of studies on
-AST to explore the extent to which research findings have trickled down
-to inform policy and planning for AST interventions.
+stakeholders in Ontario, Canada. We used text mining and topic modelling
+to examine how local policy documents from Ontario municipalities and
+school boards present and communicate the benefits and barriers of AST
+and the solutions for improving AST. We compared the findings from these
+documents to a selection of studies on AST and explored the extent to
+which research findings have trickled down to inform policy and planning
+for increasing AST.
 
@@
 
-We then assembled a collection of publicly available documents that were
+We assembled a collection of publicly available documents that were
 sourced online from the main stakeholder groups involved in STP
-initiatives in Ontario: i) English school boards; ii) municipal
-government; and iii) transportation consortia. Non-profit organizations,
-police services, and advocacy groups are other stakeholders who may play
-a role in supporting AST and/or STP, but this study does not include any
-documents from these groups because they are not consistently
-participating in initiatives.
+initiatives in Ontario: i) school boards (public and English-speaking
+only); ii) municipal governments; and iii) transportation consortia.
+Non-profit organizations, police services, and advocacy groups are other
+stakeholders who may play a role in supporting AST and/or STP, but this
+study does not include any documents from these groups because they are
+not consistently participating in initiatives.
 
-The search was guided first by a list of all English school boards
-across Ontario. The websites of each school board were searched for
-pages related to transportation or school travel. These pages were
-manually downloaded. Next, we collected documents by searching municipal
-government and transportation consortia websites. The latter were
-identified based on geographic area (i.e., the municipalities and/or
-transportation consortia who are in the same geographic area of each
-school board). Pages related to active transportation or school travel
-were manually downloaded. Webpages were included in the corpus if they
-were easy to find. This primary criteria was important since our
-analysis pertains to how such issues are framed to the public. Thus,
-these pages ought to be easy to find, which we defined as requiring no
-more than 2-4 separate links from the initial Google search.
+The search was guided first by a list of all English public school
+boards across Ontario. The websites of each school board were manually
+searched for pages related to school transportation or travel. Any pages
+relevant to these topics were manually downloaded. Next, we collected
+documents by searching municipal government and transportation consortia
+websites. The latter were identified based on geographic area (i.e., the
+municipalities and/or transportation consortia who are in the same
+geographic area of each school board). Pages related to active or school
+travel were manually downloaded. Webpages from STP stakeholder websites
+were included in our analysis if they were easy to find. This primary
+criteria was important since our analysis pertains to how such issues
+are framed to the public. Thus, we included only webpages that were easy
+to find, which we defined as requiring no more than 2-4 separate links
+from the initial Google search.
 
 The initial corpus of policy documents included 64 relevant webpages
-(i.e., one page or more) from all main stakeholder groups. It is
+(i.e., one page or more) from all STP stakeholder groups. It is
 important to note that school boards, municipalities, and transportation
 consortia may or may not publish information about their involvement in
-AST and STP efforts on their respective websites or in policy documents.
-Search results are summarized in Table \ref{tab:policy-documents}.
+AST and STP efforts on their respective websites or in policy documents,
+which means that some of these groups for particular regions in Ontario
+are not included in our analysis. Search results are summarized in Table
+\ref{tab:policy-documents}.
 
@@
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{>{}l|>{\raggedright\arraybackslash}p{30em}|>{}l}
+\begin{tabular}[t]{>{}l|l|>{}l}
 \toprule
@@
 \midrule
-\cellcolor{gray!6}{\textbf{English school boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{31}\\
-\textbf{Municipalities or regions} & 62 & 25\\
+\cellcolor{gray!6}{\textbf{School boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{31}\\
+\textbf{Municipalities} & 62 & 25\\
 \cellcolor{gray!6}{\textbf{Transportation consortia}} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{8}\\
@@
 Next, we converted the trimmed PDF documents into \texttt{txt} files so
-that they could be imported in \texttt{R} for topic modelling. We then
-proceeded to a manual cleaning phase where we removed any remaining
-tables, figures, references, headers/footings, and captions that could
-not be trimmed. Manual corrections were also required for certain pages
-in academic papers that remained in two-column format after the
-conversion process. This typically occurred on pages that had a table or
-figure which disrupted the text. Finally, we reviewed all of the
-documents to remove hyphenation by line breaks and to keep hyphenated
-words together on the same line. Any ligatures (e.g., combinations of
-characters or letters that were not properly detected during the
-conversion process) were fixed by inserting the unicode sequence of
-character to replace the missing sequence of characters.
+that they could be imported in R for analysis. We then proceeded to a
+manual cleaning phase where we removed any remaining tables, figures,
+references, headers/footings, and captions that could not be trimmed.
+Manual corrections were also required for certain pages in academic
+papers that remained in two-column format after the conversion process.
+This typically occurred on pages that had a table or figure which
+disrupted the text. Finally, we reviewed all of the documents to remove
+hyphenation by line breaks and to keep hyphenated words together on the
+same line. Any ligatures (e.g., combinations of characters or letters
+that were not properly detected during the conversion process) were
+fixed by inserting the unicode sequence of character to replace the
+missing sequence of characters.
 
@@
 
-In the final step before analysis, we removed all blank spaces,
-punctuation, capitalization, and numbers. English stop words, which are
-common words such as \emph{and} or \emph{the} as identified in a
-predetermined list by Lewis et al.~({\textbf{???}}) and other frequent
-terms in the documents like ``school'' and location names were removed
-from the corpora.
+In the final step, we removed all blank spaces, punctuation,
+capitalization, and numbers. English stop words, which are common words
+such as \emph{and} or \emph{the} as identified in a predetermined list
+by Lewis et al.~({\textbf{???}}) and other frequent terms in the
+documents like ``school'' and specific location names, were removed from
+the corpora.
 
@@
 
-Natural language processing
-
-Silge and Robinson ({\textbf{???}}) is
-
-We've been using the unnest\_tokens function to tokenize by word, or
-sometimes by sentence, which is useful for the kinds of sentiment and
-frequency analyses we've been doing so far. But we can also use the
-function to tokenize into consecutive sequences of words, called
-n-grams. By seeing how often word X is followed by word Y, we can then
-build a model of the relationships between them.
-
-We do this by adding the token = ``ngrams'' option to unnest\_tokens(),
-and setting n to the number of words we wish to capture in each n-gram.
-When we set n to 2, we are examining pairs of two consecutive words,
-often called ``bigrams'':
-
-\hypertarget{content-analysis}{%
-\subsection{3.2. Content analysis}\label{content-analysis}}
-
-Content analysis is a method to examine content from texts including the
-message itself, the sender(s) of the message, the recipients of the
-message, or the impact of the message ({\textbf{???}}). Words or phrases
-are the unit of analysis. \emph{Qualitative} content analysis
-
 \hypertarget{reproducibility}{%
-\subsection{3.3. Reproducibility}\label{reproducibility}}
+\subsection{3.2. Reproducibility}\label{reproducibility}}
 
@@
 
-We analyzed word and document frequency for each corpus. Table
-\ref{tab:word-table} presents the most common terms found in the
+We analyzed word and document frequency for each corpora. Table
+\ref{tab:word-table} shows the most frequent terms found in the
 municipal, transportation consortia, school board, and academic
-documents.
+documents. As expected, STP documents and academic papers reference
+\emph{active travel}, \emph{walking}, \emph{biking} or \emph{cycling},
+and \emph{students} more than other terms. Each corpora also has
+\emph{safety} and \emph{traffic} as common words which suggests
+congruence on these key factors between the research literature and how
+AST is framed to the public. The word \emph{physical} is present in each
+corpus which could refer to either \emph{physical activity},
+\emph{physical health}, or the \emph{physical environment}. Furthermore,
+documents from STP stakeholders discuss \emph{resources},
+\emph{information}, and \emph{services} about school travel. In the
+section below, the context in which these terms appear is explored
+further through their concordance. Unlike the academic papers, STP
+stakeholder documents include the words \emph{route} or \emph{routes}.
+This could reflect their role in identifying safe routes to school to
+share with parents or families, as well as the STP emphasis on making
+the physical environment safer for AST. The academic corpora differs
+from the policy documents in that \emph{parents} and \emph{distance} are
+the second and third most common terms. In addition, \emph{time},
+\emph{factors}, \emph{environment}, and \emph{age} are also identified
+in academic papers. These words are absent from the list of common words
+in policy documents. Table \ref{tab:word-table} indicates that the
+research corpora discusses a broader range of determinants of AST than
+the policy documents. The number of references for each term in the
+academic papers is also significantly higher due to the inclusion of
+more documents.
 
@@
 travel & 126 & 20 & bus & 120 & 20 & walking & 55 & 8 & parents & 3946 & 211\\
-\cellcolor{gray!6}{walking} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{119} & \cellcolor{gray!6}{30} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{49} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{distance} & \cellcolor{gray!6}{3271} & \cellcolor{gray!6}{205}\\
-bike & 87 & 15 & travel & 103 & 11 & travel & 41 & 8 & students & 2960 & 173\\
-\cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{78} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{student} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{2753} & \cellcolor{gray!6}{171}\\
+\cellcolor{gray!6}{walking} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{travel} & \cellcolor{gray!6}{103} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{49} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{distance} & \cellcolor{gray!6}{3271} & \cellcolor{gray!6}{205}\\
+bike & 87 & 15 & information & 65 & 21 & travel & 41 & 8 & students & 2960 & 173\\
+\cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{78} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{57} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{2753} & \cellcolor{gray!6}{171}\\
 \addlinespace
-safety & 71 & 21 & information & 65 & 21 & safety & 32 & 6 & environment & 2631 & 202\\
-\cellcolor{gray!6}{health} & \cellcolor{gray!6}{65} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{schools} & \cellcolor{gray!6}{61} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{help} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{activity} & \cellcolor{gray!6}{2371} & \cellcolor{gray!6}{209}\\
-physical & 63 & 18 & board & 61 & 26 & schools & 25 & 9 & traffic & 2353 & 208\\
-\cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{59} & \cellcolor{gray!6}{20} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{57} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{children} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{choice} & \cellcolor{gray!6}{2299} & \cellcolor{gray!6}{169}\\
-road & 56 & 13 & walk & 53 & 13 & community & 24 & 7 & physical & 2256 & 215\\
+safety & 71 & 21 & walk & 53 & 13 & safety & 32 & 6 & environment & 2631 & 202\\
+\cellcolor{gray!6}{health} & \cellcolor{gray!6}{65} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{weather} & \cellcolor{gray!6}{40} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{help} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{activity} & \cellcolor{gray!6}{2371} & \cellcolor{gray!6}{209}\\
+physical & 63 & 18 & safety & 40 & 19 & schools & 25 & 9 & traffic & 2353 & 208\\
+\cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{59} & \cellcolor{gray!6}{20} & \cellcolor{gray!6}{safe} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{children} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{choice} & \cellcolor{gray!6}{2299} & \cellcolor{gray!6}{169}\\
+road & 56 & 13 & services & 37 & 17 & community & 24 & 7 & physical & 2256 & 215\\
 \addlinespace
-\cellcolor{gray!6}{activity} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{district} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{bus} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{trips} & \cellcolor{gray!6}{2194} & \cellcolor{gray!6}{170}\\
-schools & 52 & 14 & weather & 40 & 11 & route & 17 & 5 & car & 2148 & 195\\
-\cellcolor{gray!6}{children} & \cellcolor{gray!6}{47} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{40} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{zone} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{2140} & \cellcolor{gray!6}{204}\\
-plan & 45 & 16 & safe & 39 & 19 & resources & 16 & 6 & time & 2101 & 218\\
-\cellcolor{gray!6}{students} & \cellcolor{gray!6}{44} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{services} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{factors} & \cellcolor{gray!6}{2101} & \cellcolor{gray!6}{216}\\
+\cellcolor{gray!6}{activity} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{bus} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{trips} & \cellcolor{gray!6}{2194} & \cellcolor{gray!6}{170}\\
+schools & 52 & 14 & parents & 32 & 17 & route & 17 & 5 & car & 2148 & 195\\
+\cellcolor{gray!6}{children} & \cellcolor{gray!6}{47} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{sustainable} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{zone} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{2140} & \cellcolor{gray!6}{204}\\
+plan & 45 & 16 & children & 31 & 14 & resources & 16 & 6 & time & 2101 & 218\\
+\cellcolor{gray!6}{students} & \cellcolor{gray!6}{44} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{child} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{factors} & \cellcolor{gray!6}{2101} & \cellcolor{gray!6}{216}\\
 \addlinespace
-walk & 43 & 18 & planning & 37 & 7 & safe & 15 & 5 & child & 2085 & 187\\
-\cellcolor{gray!6}{public} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{parents} & \cellcolor{gray!6}{32} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{200}\\
-will & 38 & 15 & sustainable & 31 & 8 & physical & 15 & 7 & public & 1983 & 208\\
-\cellcolor{gray!6}{community} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{may} & \cellcolor{gray!6}{30} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{age} & \cellcolor{gray!6}{1783} & \cellcolor{gray!6}{211}\\
-safe & 34 & 16 & children & 30 & 14 & traffic & 13 & 6 & urban & 1768 & 200\\
+walk & 43 & 18 & day & 29 & 13 & safe & 15 & 5 & child & 2085 & 187\\
+\cellcolor{gray!6}{public} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{routes} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{200}\\
+community & 37 & 19 & physical & 28 & 11 & physical & 15 & 7 & public & 1983 & 208\\
+\cellcolor{gray!6}{safe} & \cellcolor{gray!6}{34} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{health} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{age} & \cellcolor{gray!6}{1783} & \cellcolor{gray!6}{211}\\
+benefits & 32 & 17 & inclement & 25 & 11 & traffic & 13 & 6 & urban & 1768 & 200\\
 \addlinespace
-\cellcolor{gray!6}{benefits} & \cellcolor{gray!6}{32} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{support} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{home} & \cellcolor{gray!6}{1715} & \cellcolor{gray!6}{199}\\
-play & 31 & 2 & child & 29 & 12 & families & 13 & 5 & social & 1713 & 191\\
-\cellcolor{gray!6}{resources} & \cellcolor{gray!6}{30} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{cancellations} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{way} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{different} & \cellcolor{gray!6}{1713} & \cellcolor{gray!6}{215}\\
-healthy & 29 & 16 & routes & 28 & 14 & student & 12 & 5 & mobility & 1659 & 138\\
-\cellcolor{gray!6}{routes} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{physical} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{significant} & \cellcolor{gray!6}{1650} & \cellcolor{gray!6}{208}\\
+\cellcolor{gray!6}{play} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{eligibility} & \cellcolor{gray!6}{24} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{support} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{home} & \cellcolor{gray!6}{1715} & \cellcolor{gray!6}{199}\\
+resources & 30 & 13 & consortium & 24 & 9 & families & 13 & 5 & social & 1713 & 191\\
+\cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{way} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{different} & \cellcolor{gray!6}{1713} & \cellcolor{gray!6}{215}\\
+routes & 27 & 13 & service & 22 & 11 & student & 12 & 5 & mobility & 1659 & 138\\
+\cellcolor{gray!6}{lanes} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{•} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{significant} & \cellcolor{gray!6}{1650} & \cellcolor{gray!6}{208}\\
 \bottomrule
@@
 
-\hypertarget{bigrams-and-correlations}{%
+\hypertarget{bigrams-and-concordances}{%
 \subsection{4.2. Bigrams and
-correlations}\label{bigrams-and-correlations}}
+concordances}\label{bigrams-and-concordances}}
 
-Bigrams for each policy corpora are shown in Figures
-\ref{fig:city-bigrams}, \ref{fig:consortia-bigrams}, and
-\ref{fig:school-bigrams}. These figures help to make further sense of
-the word frequencies reported above, and highlight the main ideas that
-are presented to the public in each of the policy corpora.
-Municipalities primarily discuss ``physical activity'' (n = 53) and
-``public health'' (n = 19) in the context of active travel. In addition,
-``travel planning'' (n = 19), ``bike lanes'' (n = 16), and ``safe
-routes'' (n = 14) are also identified, conceivably as interventions and
-built environment factors that support AST. Key issues related to AST
-such as ``traffic safety'' (n = 10), ``air quality'' (n = 9), and
-``greenhouse gases'' (n = 9) are conveyed to the public but in fewer
-documents. Similar word bigrams are found in school board documents:
-``travel planning'' (n = 33), ``safe routes'' (n = 15), ``physical
-activity'' (n = 10), and ``public health'' (n = 10) are among the most
-common bigrams. Unlike other STP stakeholders, school boards also
-consider ``inclement weather'' (n = 24) ``bus cancellations'' (n = 13).
-This is likely because many students in Ontario travel by school bus and
-this information is presented alongside AST. Finally, transportation
-consortia documents highlight ``physical activity'' (n = 10),
-``pedestrian safety'' (n = 8), ``crossing guards'' (n = 6), ``travel
-planning'' (n = 6), and ``walk zones'' (n = 6). Bicycling is notably
-absent from transportation consortia documents.
+Bigrams for each policy corpora that occur more than 5 times are shown
+in Figures \ref{fig:city-visual}, \ref{fig:consortia-visual}, and
+\ref{fig:school-visual}. These figures help to make further sense of the
+word frequencies reported above, and highlight the main ideas that are
+presented to the public in each of the policy corpora. Municipalities
+primarily discuss \emph{physical activity} (n = 53) and \emph{public
+health} (n = 19) in the context of active travel. In addition,
+\emph{travel planning} (n = 19), \emph{bike lanes} (n = 16), and
+\emph{safe routes} (n = 14) are also identified, conceivably as
+interventions and built environment factors that support AST. Key issues
+related to transport such as \emph{traffic safety} (n = 10), \emph{air
+quality} (n = 9), and \emph{greenhouse gases} (n = 9) are conveyed to
+the public through AST documents. It is not surprising to find this
+focus in AST documents given that municipalities in Ontario are
+concerned about climate change and have increasingly looked to active
+modes of travel to offset transport-related emissions in urban areas.
+
+Similar word bigrams are found in school board documents: \emph{travel
+planning} (n = 33), \emph{safe routes} (n = 15), \emph{physical
+activity} (n = 10), and \emph{public health} (n = 10) are among the most
+common bigrams. Both municipalities and school boards in Ontario seem to
+emphasize what can be or has been done to improve AST (i.e., policy or
+planning changes), while outlining some of the benefits of AST at the
+individual- or community-level to potentially encourage behaviour change
+(i.e., physical activity for children or improved air quality). Unlike
+other STP stakeholders, school boards also consider \emph{inclement
+weather} (n = 24) and \emph{bus cancellations} (n = 13). This is likely
+because many students in Ontario travel to school by bus and this
+information is presented alongside AST options. Finally, transportation
+consortia documents highlight topics such as \emph{physical activity} (n
+= 10), \emph{pedestrian safety} (n = 8), \emph{crossing guards} (n = 6),
+\emph{travel planning} (n = 6), and \emph{walk zones} (n = 6). Biking or
+cycling is notably absent from transportation consortia documents.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{MunicipalTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(municipal_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}
+
+\NormalTok{M_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(MunicipalTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
+\NormalTok{municipal_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(M_it_train)}
+
+\NormalTok{municipal_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(municipal_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
+\NormalTok{municipal_vocab}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Number of docs: 28 
+## 0 stopwords:  ... 
+## ngram_min = 1; ngram_max = 1 
+## Vocabulary: 
+##            term term_count doc_count
+##   1:        abc          5         1
+##   2: accessible          5         5
+##   3:     adding          5         3
+##   4:   addition          5         3
+##   5:       ages          5         4
+##  ---                                
+## 350:    cycling         78        22
+## 351:       bike         87        15
+## 352:    walking         90        25
+## 353:     travel        126        20
+## 354:     active        248        26
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{ConsortiumTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(consortium_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}
+
+\NormalTok{C_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(ConsortiumTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
+\NormalTok{consortium_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(C_it_train)}
+
+\NormalTok{consortium_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(consortium_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
+\NormalTok{consortium_vocab}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Number of docs: 9 
+## 0 stopwords:  ... 
+## ngram_min = 1; ngram_max = 1 
+## Vocabulary: 
+##           term term_count doc_count
+##   1:    around          5         4
+##   2:    assist          5         2
+##   3:    choice          5         3
+##   4: classroom          5         1
+##   5: committee          5         1
+##  ---                               
+## 124:  students         39         9
+## 125:    travel         41         8
+## 126:      walk         49         8
+## 127:   walking         55         8
+## 128:    active         67         7
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{SchoolTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(school_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}
+
+\NormalTok{S_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(SchoolTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
+\NormalTok{school_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(S_it_train)}
+
+\NormalTok{school_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(school_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
+\NormalTok{school_vocab}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Number of docs: 32 
+## 0 stopwords:  ... 
+## ngram_min = 1; ngram_max = 1 
+## Vocabulary: 
+##                term term_count doc_count
+##   1:       academic          5         4
+##   2: administration          5         4
+##   3:      alternate          5         3
+##   4:       assigned          5         2
+##   5:         attend          5         5
+##  ---                                    
+## 264:        walking         57        17
+## 265:    information         65        21
+## 266:         travel        103        11
+## 267:            bus        120        20
+## 268:         active        124        13
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{PolicyTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(policy_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}
+
+\NormalTok{P_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(PolicyTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
+\NormalTok{policy_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(P_it_train)}
+
+\NormalTok{policy_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(policy_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
+\NormalTok{policy_vocab}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Number of docs: 69 
+## 0 stopwords:  ... 
+## ngram_min = 1; ngram_max = 1 
+## Vocabulary: 
+##           term term_count doc_count
+##   1:       abc          5         1
+##   2: according          5         4
+##   3:  actively          5         4
+##   4:  addition          5         3
+##   5: addresses          5         3
+##  ---                               
+## 698:      walk        145        39
+## 699:       bus        164        35
+## 700:   walking        202        50
+## 701:    travel        270        39
+## 702:    active        439        46
+\end{verbatim}
 
@@
 
-The academic corpora includes several common bigrams that were also
-found in the policy documents including ``physical activity'' (n =
-1566), which is the top bigram, ``traffic safety'' (n = 308), and ``safe
-routes'' (n = 268). However, many other factors relating to AST are
-identified in the research literature that are not presented to the
-public through policy documents. After ``physical activity'', ``built
-environment'' (n = 1175), ``independent mobility'' (n = 774), and
-``urban form'' (n = 352) are the most frequent pairs of consecutive
-words. Academic papers also often discuss ``distance home'' (n = 258),
-``car ownership'' (n = 254), ``household income'' (n = 254), and
-``population density'' (n = 205), which are factors that have been known
-to influence AST. It is evident that many papers investigate gender
-differences in AST given that ``boys girls'' (n = 211) is a common
-bigram. Finally, the presence of ``statistically significant'' on the
-list of top-25 bigrams underscores the importance of identifying factors
-that are not due to chance but that likely influence AST.
+We combined all of the municipality, school board, and transportation
+consortia documents into one ``policy'' corpora. This enabled us to
+examine and visualize the most common bigrams found across all of the
+STP material in Ontario. Figure \ref{fig:policy-visual} shows all of the
+bigrams that occur more than 10 times in the corpora. In addition to the
+common bigrams already identified above, we also found \emph{mental
+health}, \emph{walk day}, and \emph{green communities} as common pairs
+of consecutive words. Overall, policy documents from STP stakeholders
+focus on four key areas: i) benefits or impacts of AST; ii) mechanisms
+of intervention; iii) concerns or considerations; and iv) supports for
+AST.
 
-\begin{figure}
+We analyzed bigrams in the academic corpora separately to make
+comparisons with the policy corpora. Figure \ref{fig:academic-visual}
+indicates that the academic corpora includes several common bigrams that
+were also found in the policy documents including \emph{physical
+activity} (n = 1566), which is the top bigram, \emph{traffic safety} (n
+= 308), and \emph{safe routes} (n = 268). However, many other factors
+relating to AST are identified in the research literature that are not
+presented to the public through policy documents. After \emph{physical
+activity}, \emph{built environment} (n = 1175), \emph{independent
+mobility} (n = 774), and \emph{urban form} (n = 352) are the most
+frequent pairs of consecutive words. Academic papers also often discuss
+\emph{distance home} (n = 258), \emph{car ownership} (n = 254),
+\emph{household income} (n = 254), and \emph{population density} (n =
+205), which are factors that have been found to influence AST. It is
+evident that many papers investigate gender differences in AST given
+that \emph{boys girls} (n = 211) is another common bigram. Finally, the
+presence of \emph{statistically significant} among the top bigrams
+underscores that researchers aim to identify determinants that are not
+due to chance but that likely influence AST. The academic corpora
+focuses on a greater range of topics than found in the STP material.
 
-{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/academic-visual-1}
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{ggraph}\NormalTok{(academic_bigram_graph, }\DataTypeTok{layout =} \StringTok{"fr"}\NormalTok{) }\OperatorTok{+}
+\StringTok{  }\KeywordTok{geom_edge_link}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{edge_alpha =}\NormalTok{ n), }\DataTypeTok{show.legend =} \OtherTok{FALSE}\NormalTok{,}
+                 \DataTypeTok{arrow =}\NormalTok{ a, }\DataTypeTok{end_cap =} \KeywordTok{circle}\NormalTok{(.}\DecValTok{07}\NormalTok{, }\StringTok{'inches'}\NormalTok{)) }\OperatorTok{+}
+\StringTok{  }\KeywordTok{geom_node_point}\NormalTok{(}\DataTypeTok{color =} \StringTok{"lightgreen"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{4}\NormalTok{) }\OperatorTok{+}
+\StringTok{  }\KeywordTok{geom_node_text}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ name), }\DataTypeTok{repel =} \OtherTok{TRUE}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{theme_void}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
 
-}
+\includegraphics{AST-Framing-Ontario_files/figure-latex/unnamed-chunk-10-1.pdf}
 
-\caption{Most common bigrams found in the academic papers.}\label{fig:academic-visual}
-\end{figure}
+We interpreted the most common bigrams from the policy corpora (see
+Figure \ref{fig:policy-visual}), which includes all documents from
+municipalities, transportation consortia, and school boards, as the main
+ideas that STP stakeholders are focusing on and communicating to the
+public about AST. We used the \texttt{kwic} function from the R
+\emph{quanteda} package to identify and better understand identify the
+context of these key themes.
 
-\hypertarget{qualitative-findings-of-policy-documents}{%
-\subsection{4.3. Qualitative findings of policy
-documents}\label{qualitative-findings-of-policy-documents}}
+\begin{table}
+\centering
+\begin{tabular}[t]{>{}l|l|>{\raggedright\arraybackslash}p{30em}}
+\hline
+Terms & Stakeholder & Context\\
+\hline
+\textbf{Physical health} & School Board & ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.\\
+\hline
+\textbf{Emissions} & Municipality & Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.\\
+\hline
+\end{tabular}
+\end{table}
 
-We used the most common bigrams from the policy corpus (see Figure
-\ref{fig:policy-visual}), which includes all documents from
-municipalities, transportation consortia, and school boards, as
-categories of codes for qualitative content analysis. This means that we
-interpreted the bigrams to represent the main ideas that STP
-stakeholders are communicating to the public about AST.
+\hypertarget{topic-modelling}{%
+\subsection{4.3. Topic modelling}\label{topic-modelling}}
+
+\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-1.pdf}
+\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-2.pdf}
+\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-3.pdf}
+\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-4.pdf}
+
+\begin{verbatim}
+## final e step document 28
+\end{verbatim}
+
+\begin{verbatim}
+## final e step document 32
+\end{verbatim}
+
+\begin{verbatim}
+## final e step document 9
+\end{verbatim}
+
+\begin{verbatim}
+## final e step document 69
+\end{verbatim}
+
+\includegraphics{AST-Framing-Ontario_files/figure-latex/municipal-terms-1.pdf}
+
+\includegraphics{AST-Framing-Ontario_files/figure-latex/school-terms-1.pdf}
+
+\includegraphics{AST-Framing-Ontario_files/figure-latex/consortia-terms-1.pdf}
+
+\includegraphics{AST-Framing-Ontario_files/figure-latex/policy-terms-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{#municipal_beta <- municipal_topics %>%}
+  \CommentTok{#mutate(topic = paste0("topic", topic)) %>%}
+  \CommentTok{#pivot_wider(names_from = topic, values_from = beta) %>% }
+  \CommentTok{#filter(topic1 > .001 | topic2 > .001) %>%}
+  \CommentTok{#mutate(log_ratio = log2(topic2 / topic1))}
+\CommentTok{#municipal_beta}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Identify topics by document across each corpora}
+
+\NormalTok{municipal_documents <-}\StringTok{ }\KeywordTok{tidy}\NormalTok{(municipal_lda, }\DataTypeTok{matrix =} \StringTok{"gamma"}\NormalTok{)}
+\NormalTok{school_documents <-}\StringTok{ }\KeywordTok{tidy}\NormalTok{(school_lda, }\DataTypeTok{matrix =} \StringTok{"gamma"}\NormalTok{)}
+\NormalTok{consortia_documents <-}\StringTok{ }\KeywordTok{tidy}\NormalTok{(consortia_lda, }\DataTypeTok{matrix =} \StringTok{"gamma"}\NormalTok{)}
+\NormalTok{policy_documents <-}\StringTok{ }\KeywordTok{tidy}\NormalTok{(policy_lda, }\DataTypeTok{matrix =} \StringTok{"gamma"}\NormalTok{)}
+\CommentTok{#academic_documents <- tidy(academic_lda, matrix = "gamma")}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
-\hypertarget{framing-of-ast-in-policy-documents}{%
-\subsection{5.1. Framing of AST in policy
-documents}\label{framing-of-ast-in-policy-documents}}
-
-The presence of ``travel planning'' among the top pairs of consecutive
-words for municipalities, school boards, and transportation consortia
-reflects the
-
-\hypertarget{framing-of-ast-in-academic-papers}{%
-\subsection{5.2. Framing of AST in academic
-papers}\label{framing-of-ast-in-academic-papers}}
-
-Notably absent from the policy corpora is children's independent
-mobility (CIM). AST is one of the most common opportunities for children
-to travel without adult supervision on a regular basis, yet STP
-stakeholders do not discuss this topic. CIM was first described by
-Hillman et al.~({\textbf{???}}) as the freedom of children to travel and
-play within their neighborhood and city without the presence of adults.
-The ability of children to reach destinations such as school or local
-parks by walking or bicycling on their own is a growing area of research
-that is related to and often overlaps with the body of literature on
-AST.
-
-In a study conducted in multiple Canadian cities, Riazi et
-al.~({\textbf{???}}) found that a range of factors such as child grade,
-car ownership, and parental perceptions of safety and environment were
-associated with CIM. Parental perceptions of children's autonomy also
-influences CIM ({\textbf{???}}). In addition to independent trips to
-school, children also travel by walking or bicycling on their own to
-other non-school destinations such as outdoor spaces (i.e., parks,
-playgrounds), the homes of family members or friends, shopping places,
-and libraries, to name a few ({\textbf{???}}; {\textbf{???}}).
-
 \hypertarget{implications-for-school-travel-planning}{%
-\subsection{5.3. Implications for School Travel
+\subsection{5.1. Implications for School Travel
 Planning}\label{implications-for-school-travel-planning}}
 
-School boards and educators are an influential contributor to AST and
-STP efforts in Canada.
-
 \hypertarget{limitations}{%
-\subsection{5.4. Limitations}\label{limitations}}
+\subsection{5.2. Limitations}\label{limitations}}
 

### 2021-08-06 AST-Framing-Ontario/Data Pre-Processesing.rmd
Create a raw policy corpus (not cleaned) to be used for kwic
New policy corpus created

@@
 
+## 3.4. Create corpus for concordances
+
+Before removing stop words and punctuation, create a corpus to use for identifying keywords in context.
+
+```{r}
+raw_policy_corpus <- policy_corpus
+```
+
 ## 3.4. Clean corpus
@@
 save(policy_corpus, file= "Corpus .rda/policy_corpus.rda")
+save(raw_policy_corpus, file= "Corpus .rda/raw_policy_corpus.rda")
 ```

### 2021-11-26 AST-Framing-Ontario/AST-Framing-Ontario.Rmd

@@
 
-## 1.1. School travel planning in Canada
+Walking and bicycling to school, commonly known as active school travel (AST), has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020].
+In response to this trend, school travel planning has become a popular intervention across Canada that has resulted in mixed success with some schools reporting an increase in AST [e.g., @buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014], while others did not observe a change in behaviour [@buttazzoniPromotingActiveSchool2019] or needed more time and resources to be effective [@mammenPuttingSchoolTravel2015].
 
-Walking and bicycling to school, commonly known as active school travel or active school transportation (AST), has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020].
-This trend has prompted a multi-sector response to identify strategies to increase AST, the most popular of which is a growing interest in school travel planning across Canada.
+School travel planning (STP) is a "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@mammenSchoolTravelPlanning2014].
+This five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities that alleviate concerns and encourage AST [@faulknerSchoolTravelPlans2018].
+STP facilitators and committee members generally intervene at the school through a range of activities such as educational strategies, in-person events or programs, improvements to the school site, and enforcement [@mammenActiveSchoolTravel2014].
 
-School travel planning (STP) is a "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health [@mammenSchoolTravelPlanning2014].
-Parents and parent councils also typically have a role in supporting or implementing STP.
-The intervention encourages participation from the broader community and collaboration between involved stakeholders, who contribute their expertise to remove "school-specific" barriers to AST and to identify strategies for promoting and encouraging AST.
-STP may also involve other stakeholders including local advocacy groups or environmental organizations who are familiar with the state of AST at the community-level.
-Buliung et al.
-[-@buliungSchoolTravelPlanning2011] piloted an STP intervention at 12 schools in 4 Canadian provinces and reported that it increased AST rates and led to a "mobilization of diverse community resources".
-Since this seminal study, STP interventions have become increasingly popular and common at schools across Canada and have even attracted funding from provincial governments.
+How STP is framed to a target audience may influence how this intervention is received and whether it encourages the audience to support it or participate.
+In particular, STP stakeholders make choices about the points of intervention and potential benefits that ought to be communicated to the public to facilitate adoption of AST.
+Educational strategies, which account for approximately one quarter of STP strategies implemented at Canadian schools [@mammenActiveSchoolTravel2014], need to effectively engage multiple audiences – parents, students, politicians – on the issue, challenges, and benefits of AST.
+Promotional materials, therefore, should reflect current knowledge from research about school travel and the built environment, as well as local content specific to factors that influence travel decisions for parents, in order to effectively engage the public in advocating for improving AST or to expose parents and the community to essential information that may prompt behaviour change.
 
-## 1.2. Correlates of active school travel
+On the one hand, parents have been found to express different understandings, nomenclature, and conceptualizations than planners of the factors that influence school travel [@buliungLivingJourneySchool2021].
+However, it is unknown to what degree there is concurrence between STP materials presented to the public and the literature on school travel and parental perceptions, and how the complexity of the AST issue is presented to the public.
 
-Factors that influence AST are typically conceptualized according to the socioecological model whereby children's travel behaviour is understood within the context of their household, social, and built environments [see @mitraIndependentMobilityMode2013].
-At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018].
-There is some evidence that gender is a determinant of AST [@babbChildrenActiveTravel2017; @larsenInfluencePhysicalEnvironment2009], although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
-Distance between home and school is associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
-Car ownership is an important household-level influence on AST [@pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], as is household income [@pontEnvironmentalCorrelatesChildren2009].
-Parental perceptions of the environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and children's skills [@ghekiereInsightsChildrenIndependent2017] also influence whether they allow their children to walk or cycle to school.
-Finally, many studies have found that the quality of the built environment [@ikedaAssociationsChildrenActive2018; @kimBuiltNaturalEnvironmental2020] and active travel infrastructure [@pontEnvironmentalCorrelatesChildren2009] facilitate AST.
-Concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012].
-The consensus is that all of these factors are interrelated and that interventions ought to target multiple factors in order to increase walking and bicycling levels to school.
+The aim of this paper is to fill this research gap by analyzing how AST is framed by STP stakeholders in Ontario, Canada.
+We used text mining and topic modelling to examine how local policy documents from Ontario municipalities and school boards present and communicate the benefits and barriers of AST and the solutions for improving AST.
+We compared the findings from these documents to a selection of studies on AST and explored the extent to which there is concurrence between research findings to date and promotional materials shared with the public to increase AST.
 
-## 1.3. Benefits of AST
+2. Literature Review
+======================
 
-The desire to increase AST is warranted - there is strong evidence that children who walk and bicycle to school accrue physical and mental health benefits.
-Many studies and reviews have focused on the association between AST or CIM and physical activity [e.g., @faulknerActiveSchoolTransport2009; @mitraChildrenActivitytransportationLifestyles2017; @schoeppeAssociationsChildrenActive2015], with findings consistently demonstrating that children who travel by walking or bicycling to school are more active than their peers who do not use active travel.
-More recently, researchers have been exploring the link between transport and children's wellbeing [@babbChildrenActiveTravel2017; @waygoodTransportChildrenWellbeing2020], which has relevant applications to the study of school travel and satisfaction [see @vandenbergFactorsAffectingParental2020].
-CIM is also important for different domains of children's health and wellbeing [@riaziChildrenIndependentMobility2018].
-It offers benefits such as increasing traffic and safety skills, boosting spatial awareness when navigating public spaces, and providing more opportunity for social interaction with peers [@schoeppeAssociationsChildrenIndependent2014].
-
-## 1.4. Encouraging adoption of active school travel
-
-To increase rates of walking and bicycling independently to school, Riazi et al.
-[-@riaziCorrelatesChildrenIndependent2019] state: "it will be vital for interventions to target modifiable factors, including children's and parents' perceptions of their social environment." Parents play the important role of "gatekeeper" by either granting or restricting CIM licenses, meaning whether children can travel alone [@sharminAssociationBuiltEnvironment2017].
-For this reason, stakeholders involved in STP produce information targeted for both children and parents, and aim to involve the broader community in their efforts to increase the number of children walking and bicycling to school.
-
-However, the ways in which interventions like STP are framed to their target audience can ultimately influence how they are received and whether they result in behaviour change.
-The correlates of AST are important knowledge for policymakers because they identify points of intervention and potential benefits that ought to be communicated to the public encourage adoption of AST and to build support for new planning paradigms.
-What is less clear is how CIM plays into the consideration of policymakers when they act on the objective of increasing AST.
-
-Any goals for AST, and also CIM, ought to be clearly articulated and reflected in transportation plans and policies to guide initiatives.
-Presently, however, there has been no study to date that explores how Canadian municipalities and schools frame and discuss AST with the public.
-Content analysis is one method to analyze how particular issues are framed to groups of people, for instance parents or educators who might be inclined to support AST.
-It attempts to understand how information presented from a "communicator" leads the "receiver" to a desired response [@reynardGrowthResilienceHow2021].
-In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review municipal policies addressing climate change in four western Canadian cities.
-Natural language processing (NLP) has also been used for a similar purpose to examine content in general plans from Californian cities [@brinkleyWhatPlanUsing2021].
-The way policy issues are framed is ultimately important to understand because it plays a role in either altering or preserving the existing social perceptions.
-
-## 1.5. Study aim
-
-In 2017, the provincial government of Ontario in Canada issued funding to Green Communities Canada (GCC), a non-profit organization, to launch the _Ontario Active School Travel_ (OAST) program.
-The program provides funding for school and community-based initiatives and supports stakeholders in municipalities across the province to implement STP and other interventions aimed at increasing AST.
-As of 2021, OAST has funded _X_ projects in Ontario.
-GCC continues has funded projects across Ontario led by collaborative groups involving school boards, municipal or regional governments, and regional transportation consortia.
-The latter are dedicated transportation bodies that deliver efficient and effective transportation services, which generally focus on providing the school busing service to families in their associated region.
-
-The aim of this paper is to analyze how AST is framed by STP stakeholders in Ontario, Canada.
-We used text mining and topic modelling to examine how local policy documents from Ontario municipalities and school boards present and communicate the benefits and barriers of AST and the solutions for improving AST.
-We compared the findings from these documents to a selection of studies on AST and explored the extent to which research findings have trickled down to inform policy and planning for increasing AST.
-
-2. Data
+3. Data
 ===============
 
-## 2.1. Data retrieval
+## 3.1. Data retrieval
 
-### 2.1.1. Policy documents
+### 3.1.1. Policy documents
 
 We assembled a collection of publicly available documents that were sourced online from the main stakeholder groups involved in STP initiatives in Ontario: i) school boards (public and English-speaking only); ii) municipal governments; and iii) transportation consortia.
-Non-profit organizations, police services, and advocacy groups are other stakeholders who may play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in initiatives.
+Non-profit organizations, police services, and advocacy groups are other stakeholders who may play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all initiatives.
 
@@
 Next, we collected documents by searching municipal government and transportation consortia websites.
-The latter were identified based on geographic area (i.e., the municipalities and/or transportation consortia who are in the same geographic area of each school board).
+The latter were identified based on geographic area (i.e., the municipalities and/or transportation consortia that are in the same geographic area of each school board).
 Pages related to active or school travel were manually downloaded.
@@
 
-### 2.2.1. Academic papers
+### 3.2.1. Academic papers
 
-## 2.2. Data cleaning
+__To be completed by Dr. Paez__
+
+## 3.2. Data cleaning
 
@@
 
-3. Methods
+4. Methods
 ===============
 
-## 3.1. Natural language processing
+## 4.1. Framing analysis
 
-## 3.2. Reproducibility
+Issues that pertain to public health or wellbeing are often presented to the public through particular frames to influence perceptions or behaviours.
+Gamson and Modigliani [-@gamsonChangingCulture1987] conceptualize a frame as a “central organizing idea or story line that provides meaning” to a particular phenomenon.
+A frame can enable individuals "to locate, perceive, identify, and label" information pertaining to various dimensions of an issue [@goffmanFrameAnalysisEssay1974].
+Scholars in the field of political communications have proposed that communicators, such as the media or an institution, construct the narrative of a frame for policy positions or public issues in order to activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
+Framing can be used to position existing solutions as suitable to address particular issues [@mahFramecriticalPolicyAnalysis2014], which may prevent the public from being aware of other policy approaches that challenge the status quo to bring about more radical change.
+The way policy issues are framed is ultimately important to understand because it plays a role in either altering or preserving the existing social perceptions.
+
+Framing of issues is an important step in developing health policy.
+An obvious example over the past decade is the framing of climate change as a public health issue [e.g., @ depouxCommunicatingClimateChange2017; @maibachReframingClimateChange2010; @weathersDevelopmentsFramingClimate2016] to increase public engagement and reception of the issue.
+Transport planners also use different frames to guide the extent to which transport policies can be adapted to address climate change.
+In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review the representation of issues such as mobility and social exclusion in municipal policies from four western Canadian cities under the current circumstances of climate change.
+The authors found four primary frames: “The Growing City”, “If You Build It, They Will Come”, “Better City for All”, and a “the Resilient City”.
+Each frame presented the nature, opportunities, and challenges of climate change in different ways which set the stage for the types of mitigation and adaptation strategies that cities were proposing to address this issue.
+
+Given the range of factors at multiple levels of the socioecological model that influence school travel, it is important to understand how walking and bicycling to school are framed to the public.
+Is active school travel framed as a public health or environmental issue?
+Is it framed as both?
+Do proposed solutions to increase AST focus primarily on the intrapersonal and interpersonal factors, meaning that behaviour change must ultimately result from different decisions made by the individual or the household?
+Or is the decline in AST framed as an issue that must be addressed through changes in the built environment?
+These are the types of questions that we aim to answer in this paper.
+To our knowledge, this topic has not be addressed in the school travel literature to date.
+
+## 4.2. Topic modelling
+
+The topic modelling analysis was conducted in R.
+We primarily used the following packages: `topicmodels` [@R-topicmodels], `word2vec` [@R-word2vec], and `wordcloud` [@R-wordcloud] to examine content in the documents that were sourced for this project.
+These packages have functions for determining the frequency of specific words in each document, relationships (e.g., pairs of adjacent terms) and correlations between words, and estimating Latent Dirichlet allocation (LDA) models to classify documents according to the topics that are contained within them.
+We describe in the section below how we used these functions to produce our results.
+
+## 4.3. Reproducibility
 
@@
 
-4. Results
+5. Results
 ===============
 
-## 4.1. Word and document frequency
+## 5.1. Word and document frequency
 
@@
 
-## 4.2. Bigrams and concordances
+## 5.2. Bigrams and concordances
 
@@
 
-```{r}
+```{r, include=FALSE}
 MunicipalTextDF <- data.frame(text = sapply(municipal_corpus, as.character), stringsAsFactors = FALSE)
@@
 
-```{r}
+```{r, include=FALSE}
 ConsortiumTextDF <- data.frame(text = sapply(consortium_corpus, as.character), stringsAsFactors = FALSE)
@@
 
-```{r}
+```{r, include=FALSE}
 SchoolTextDF <- data.frame(text = sapply(school_corpus, as.character), stringsAsFactors = FALSE)
@@
 
-```{r}
+```{r, include=FALSE}
 PolicyTextDF <- data.frame(text = sapply(policy_corpus, as.character), stringsAsFactors = FALSE)
@@
 
-```{r policy-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in all of the policy documents (i.e., school board, municipality, and transportation consortia combined."}
+```{r policy-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined)."}
 ggraph(policy_bigram_graph, layout = "fr") +
@@
 
-We combined all of the municipality, school board, and transportation consortia documents into one "policy" corpora.
-This enabled us to examine and visualize the most common bigrams found across all of the STP material in Ontario.
+We then combined all municipality, school board, and transportation consortia documents into one "policy" corpora.
+This enabled us to examine and visualize the most common bigrams found across all of the STP material in Ontario that was collected for this study.
 Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the corpora.
 In addition to the common bigrams already identified above, we also found _mental health_, _walk day_, and _green communities_ as common pairs of consecutive words.
-Overall, policy documents from STP stakeholders focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or considerations; and iv) supports for AST.
+Overall, policy documents from STP stakeholders seem to focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or considerations; and iv) supports for AST.
 
@@
 
-```{r academic-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the academic papers."}
+```{r, include=FALSE}
 academic_bigrams_separated <- academic_bigrams %>%
@@
 
-```{r}
+```{r, academic-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the academic papers.}
 ggraph(academic_bigram_graph, layout = "fr") +
@@
 We interpreted the most common bigrams from the policy corpora (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholders are focusing on and communicating to the public about AST.
-We used the `kwic` function from the R _quanteda_ package to identify and better understand identify the context of these key themes.
+We then used the `kwic` function from the R _quanteda_ package to identify and better understand the context of these key themes.
+Table \ref{tab:policy-concordance} presents examples of the key themes that were extracted from select policy documents to demonstrate how the most common bigrams are communicated to the public.
 
@@
 kwic_pol_wea <- kwic(tokens(policy_quanteda), pattern = "weather", window = 10)
-kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes", window = 10)
 ```
@@
 text_tbl <- data.frame(
-  Terms = c("Physical health", "Emissions"),
-  Stakeholder = c("School Board", "Municipality"),
+  Terms = c("Air Quality", "Benefit", "Bus", "Community", "Emissions", "Health", "Lanes", "Mental Health", "Physical Health"),
+  Stakeholder = c("School Board", "Municipality", "School Board", "School Board", "Consortia", "Municipality", "Municipality", "Municipality", "Municipality"),
   Context = c(
+    "Active transportation [...] improves air quality.",
+    "Stronger bones and muscles, improved self-esteem and sense of well-being while reducing stress and risk of chronic disease all benefit those who use active transportation.",
+    "While taking part in a walking school bus, your child will enjoy seeing friends on the way to school.
+They will be active more often.
+This is also a great opportunity for your child to socialize with school friends in a monitored and safe way where they can practice social distancing, modelled by a leader.",
+    "Engage community stakeholders (school boards, municipalities, police, public health professionals, parents/guardians, administrators, educators and children) to work together to identify and to solve their school travel needs.",
+    "An active school commute also reduces congestion in school zones and contributes to reducing greenhouse gas emissions – it’s a win-win for everyone!",
+    "Active School Travel allows school-aged children the chance to participate in moderate to intense physical activity.
+This is linked with lower body mass index and improved cardiovascular health.",
+    "We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments.",
     "ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.",
@@
 
-## 4.3. Topic modelling
+## 5.3. Topic modelling
 
-```{r corpus-dtm, echo=FALSE}
+```{r corpus-dtm, include=FALSE}
 # Create DTM from corpus
@@
 
-```{r topics-number, echo=FALSE}
+```{r topics-number, include=FALSE}
 # Select number of topics for each LDA model using `ldatuning`
@@
   municipal_dtm, 
-  topics = seq(from = 1, to = 10, by = 1),
+  topics = seq(from = 2, to = 15, by = 1),
   metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
@@
   school_dtm, 
-  topics = seq(from = 1, to = 10, by = 1),
+  topics = seq(from = 2, to = 15, by = 1),
   metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
@@
   consortia_dtm, 
-  topics = seq(from = 1, to = 10, by = 1),
+  topics = seq(from = 2, to = 15, by = 1),
   metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
@@
   policy_dtm,
-  topics = seq(from = 1, to = 10, by = 1),
+  topics = seq(from = 2, to = 15, by = 1),
   metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
@@
 
-```{r topics-academic, echo=FALSE, cache=TRUE}
+```{r topics-academic, include=FALSE, cache=TRUE}
 # DO NOT RUN EVERY TIME - takes approximately 20 minutes
 
-#academic_lda_num <- FindTopicsNumber(
-  #academic_dtm, 
-  #topics = seq(from = 2, to = 50, by = 5),
-  #metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
-  #method = "Gibbs",
+academic_lda_num <- FindTopicsNumber(
+  academic_dtm, 
+  topics = seq(from = 2, to = 25, by = 1),
+  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  method = "Gibbs")
   #control = list(seed = 77),
@@
 FindTopicsNumber_plot(policy_lda_num)
-#(academic_lda_num)
+FindTopicsNumber_plot(academic_lda_num)
 
-# The graphs suggest that there are 7 topics for the municipal corpora
-# The graphs suggest that there are 7 topics for the school corpora
-# The graphs suggest that there are 5 topics for the municipal corpora
+# The graphs suggest that there are 4 topics for the municipal corpora
+# The graphs suggest that there are 4 topics for the school corpora
+# The graphs suggest that there are 4 topics for the municipal corpora
 # The graphs suggest that there are 5 topics for the policy corpora
-# The graphs suggest that there are 22 topics for the academic corpora
+# The graphs suggest that there are 17 topics for the academic corpora
 ```
 
-```{r corpus-lda-model, echo=FALSE}
-municipal_lda <- LDA(municipal_dtm, k = 3, control=list(seed = 1, verbose = 25))
+```{r corpus-lda-model, include=FALSE}
+municipal_lda <- LDA(municipal_dtm, k = 4, method = "Gibbs", control = NULL, model = NULL)
 
-school_lda <- LDA(school_dtm, k = 3, control=list(seed = 1, verbose = 25))
+school_lda <- LDA(school_dtm, k = 4, method = "Gibbs", control = NULL, model = NULL)
 
-consortia_lda <- LDA(consortia_dtm, k = 3, control=list(seed = 1, verbose = 25))
+consortia_lda <- LDA(consortia_dtm, k = 4, method = "Gibbs", control = NULL, model = NULL)
 
-policy_lda <- LDA(policy_dtm, k = 3, control=list(seed = 1, verbose = 25))
+policy_lda <- LDA(policy_dtm, k = 5, method = "Gibbs", control = NULL, model = NULL)
 
-#academic_lda <- LDA(academic_dtm, k = 22, control=list(seed = 1, verbose = 25))
+academic_lda <- LDA(academic_dtm, k = 19, method = "Gibbs", control = NULL, model = NULL)
 ```
 
-```{r municipal-topics, echo=FALSE}
+```{r municipal-topics, include=FALSE}
 municipal_topics <- tidy(municipal_lda, matrix = "beta")
@@
 policy_topics <- tidy(policy_lda, matrix = "beta")
-#academic_topics <- tidy(academic_lda, matrix = "beta")
+academic_topics <- tidy(academic_lda, matrix = "beta")
 ```
@@
 ```{r academic-terms, echo=FALSE, cache=TRUE}
-# Do not run; number of topics is not yet determined
 
-#academic_top_terms <- academic_topics %>%
-  #group_by(topic) %>%
-  #slice_max(beta, n = 10) %>% 
-  #ungroup() %>%
-  #arrange(topic, -beta)
+academic_top_terms <- academic_topics %>%
+  group_by(topic) %>%
+  slice_max(beta, n = 10) %>% 
+  ungroup() %>%
+  arrange(topic, -beta)
 
-#academic_top_terms %>%
-  #mutate(term = reorder_within(term, beta, topic)) %>%
-  #ggplot(aes(beta, term, fill = factor(topic))) +
-  #geom_col(show.legend = FALSE) +
-  #facet_wrap(~ topic, scales = "free") +
-  #scale_y_reordered()
+academic_top_terms %>%
+  mutate(term = reorder_within(term, beta, topic)) %>%
+  ggplot(aes(beta, term, fill = factor(topic))) +
+  geom_col(show.legend = FALSE) +
+  facet_wrap(~ topic, scales = "free") +
+  scale_y_reordered()
 ```
 
-```{r}
-#municipal_beta <- municipal_topics %>%
-  #mutate(topic = paste0("topic", topic)) %>%
-  #pivot_wider(names_from = topic, values_from = beta) %>% 
-  #filter(topic1 > .001 | topic2 > .001) %>%
-  #mutate(log_ratio = log2(topic2 / topic1))
-#municipal_beta
-```
+Finally, we conducted topic modelling to examine the different topics found in the policy and academic corpora.
+We focused on the policy corpora, instead of individually assessing the municipal, school, and consortia corpus, so that we could report on the primary and secondary frames used across all documents put out by STP stakeholders in Ontario.
+To determine the number of discrete topics in each corpus, we used the ldatuning package.
+We then used the `LDA` function from the topicmodels package to estimate an LDA model for each group of documents.
+The policy corpora, which combined all documents from municipalities, schools, and transportation consortia, had 5 topics.
+The academic corpora had 17 topics.
+Figures \ref{fig: policy-terms} and \ref{fig: academic-terms} present the main terms that are associated with the topics found in each corpus.
 
-```{r document-matrix}
-# Identify topics by document across each corpora
+In the policy corpus, we identified the following topics: (1) resources for walking, (2) busing information and eligibility; (3) benefits of active travel; (4) bicycling and the environment; and (5) supporting active travel.
+These findings reveal that STP stakeholders are sending the message that walking and bicycling to school as healthy travel modes for students, particularly as a means to get physical activity.
+We also found that there is information shared to support parents and students in using active modes to school such as the availability of cycling lanes or route tips for walking.
+STP stakeholders appear to be communicating that AST is possible and safe as a result of improvements to the built environment and available resources for parents and children.
+A final focus in the policy documents is on various efforts that are underway to support active travel including route planning.
 
-municipal_documents <- tidy(municipal_lda, matrix = "gamma")
-school_documents <- tidy(school_lda, matrix = "gamma")
-consortia_documents <- tidy(consortia_lda, matrix = "gamma")
-policy_documents <- tidy(policy_lda, matrix = "gamma")
-#academic_documents <- tidy(academic_lda, matrix = "gamma")
-```
+We expected to find a higher number of topics in the academic corpus due to the larger number of documents in the corpora and the diversity of content examined in existing literature about school travel.
+The following topics were identified, which touch upon a broader range of factors that are associated with or related to AST than are found in the policy corpus: (1) __unclear__ (2) AST in Ontario and Canada; (3) __unclear__; (4) children’s independent mobility; (5) safe routes to school programs; (6) commuting and distance; (7) density in the built environment and walking routes; (8) __unclear__; (9) walking interventions; (10) bicycling influences; (11) interpersonal and household influences on trips; (12) behaviours and attitudes; (13) __unclear__; (14) __unclear__; (15) walking distance; (16) __unclear__;  (17) physical activity measures or results; (18) bicycling attitudes; and (19) __unclear__.
 
-5. Discussion
+The policy corpus primarily frames AST as a health and environmental issue.
+Many municipal and school documents position walking, bicycling, or rolling to school as beneficial to individual health, including improvements to physical activity levels or mental health, and to the broader community through a reduction in traffic and vehicle emissions.
+> _If you live in a walk zone, the best way to get to school is by walking or biking.
+This promotes physical activity, helps the environment and minimizes traffic around schools during busy times._ (City of Barrie)
+
+> _Walking to school is a great way to add physical activity into your child’s busy day._ (Region of Haldimand-Norfolk Region)
+
+> _Active school travel is a great way for children to be physically active, which is associated with improved physical and mental health, while making school zones safer, by reducing traffic volumes at and around schools._(Region of Leeds, Grenville and Lanark)
+
+> _The WCDSB supports active transportation as the preferred method of transportation to school because it is a healthy choice that has proven links to greater student achievement._ (Waterloo Catholic District School Board)
+
+We found that some of these documents make direct references to topics found in research on school travel and the built environment.
+For example, some policy documents identify programs that have been researched in the literature and found to be effective, such as walking school buses, or explain how an increase in AST will reduce parent safety concerns.
+> _ For their health, safety, environment and community: Kids learn healthy habits and concentrate better in class; One less car (yours) reduces traffic and parking problems in school zones; Teach your kids about traffic safety; Start a walking school bus; your kids make friends in every grade, and that can prevent bullying._ (City of Guelph)
+
+> _There are lots of benefits in the classroom for children that walk or cycle to school on a regular basis.
+Some of these benefits include improved concentration and better coping with stress.
+Being outside helps to prevent feelings of isolation and increases their social interactions.
+Walking and biking to school can also save you money and lead to fewer cars on the road._ (City of Ottawa)
+
+The secondary frame for AST in municipal documents is the opportunity or prospect of behaviour change.
+Some cities and schools explain how children and parents can leave the car at home and make the journey to school on foot or by bike by describing efforts to make AST safer.
+This frame enables the public to evaluate their own travel decisions and to access resources (e.g., walking skills checklist) that will help them make AST a first choice.
+Some documents communicate what is being done by the municipalities or schools, like school travel planning, while others emphasize the active role of the parent in creating opportunities for AST in their household or neighbourhood.
+> _School Travel Planning is a community-based approach that aims to increase the number of students and adults choosing active and sustainable travel to get to and from school.
+This approach addresses concerns about safety, physical activity, and the environment._ (City of Hamilton)
+
+> _A way to make sure your child is safe while walking to school is with a 'walking school bus.' Here are some tips for a walking school bus: Invite families who live nearby to walk; Pick a route and take a test walk; Take side streets and paths that are less busy with traffic; Decide how often the group will walk together; Talk with your boss to adjust your day; Have fun!
+(City of Ottawa)
+
+> Help your students get started on the right foot -encourage them to walk or bike to school when possible.
+Even leaving the car a block or two and walking the rest of the way helps.
+It’s good for the environment and your health,  and teaches your child independence and community awareness._ (Halton District School Board)
+
+> _Today, as more and more of our neighbourhoods are being retrofitted with new sidewalks and bike lanes, pedestrian crossovers, street lights, reduced speed limits and/or crossing guards, the walk or bike ride to and from school has never been easier, safer or healthier._  (Hamilton-Wentworth District Catholic School Board)
+
+> _Want to boost your child’s mental and physical health?
+Ottawa Public Health, City of Ottawa, and OSTA have produced a tipsheet for parents about “active transportation” to school – fitting walking and wheeling into your daily routine._ (Ottawa-Carleton District School Board)
+
+Finally, many municipalities, schools, and consortia make no mention of active school travel on their main website pages for active transportation.
+Nonetheless, some municipalities explain how changes to the built environment are being implemented to facilitate active travel.
+Schools or consortia that do not refer to AST simply provide information about the busing service available to families in the region.
+Inclement weather and impacts to busing is a common topic addressed in those documents.
+> _We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments._ (City of Brantford)
+
+> _The City of Burlington ensures all cyclists, pedestrians and drivers have access to safe and accessible transportation services and programs_ (City of Burlington)
+
+6. Discussion
 ===============
 
-## 5.1. Implications for School Travel Planning
+## 6.1. Framing in STP documents
 
-## 5.2. Limitations
+We analyzed how AST is framed in documents available to the public on the websites of STP stakeholders in Ontario.
+We found that AST is primarily framed as beneficial to the health and wellbeing of children and to environmental sustainability.
+This was confirmed by the most common bigrams identified in the policy corpora, as well as the topics identified by the LDA model.
+Many studies and reviews have focused on the association between AST and physical activity [e.g., @faulknerActiveSchoolTransport2009; @mitraChildrenActivitytransportationLifestyles2017; @schoeppeAssociationsChildrenActive2015], with findings consistently demonstrating that children who travel by walking or bicycling to school are more active than their peers who do not use active travel.
+More recently, researchers have been exploring the link between transport and children's wellbeing [@babbChildrenActiveTravel2017; @waygoodTransportChildrenWellbeing2020], which has relevant applications to the study of school travel and satisfaction [see @vandenbergFactorsAffectingParental2020].
+We concluded that STP promotional materials have high concurrence with this topic in the research on school travel and the built environment.
+Framing AST as a health issue is certainly warranted - there is strong evidence that children who walk and bicycle to school accrue physical and mental health benefits.
+Furthermore, concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012].
+Parents often have concerns about traffic volume, speed, and congestion around schools [@lingRelationshipMotorVehicle2021; @rothmanSchoolEnvironmentStudent2017], therefore the framing of AST as an environmental issue is in alignment with evidence from existing studies.
 
-6.1. Conclusion
+The secondary frame of AST is that it is a behaviour that can and should be adopted by children and parents given the environmental and program supports available in the community.
+STP stakeholders emphasize that parents can access resources or trips to support their children in commuting by active modes to school.
+They also share information about interventions such as school travel plans and bicycle lanes to frame AST as safe and practical.
+However, STP materials neglect to address many intrapersonal and household factors that influence or predict AST.
+At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018], but AST is not framed as an activity for children based on age.
+STP stakeholders may wish to emphasize to parents that older children have greater traffic safety and cognitive abilities to navigate their own routes to school.
+There is also some evidence that gender is a determinant of AST [@babbChildrenActiveTravel2017; @larsenInfluencePhysicalEnvironment2009], although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
+STP materials do not discuss this determinant of AST but it may be helpful to identify strategies or messages that alleviate specific concerns that relate to a child's gender.
+
+Furthermore, distance between home and school is the factor most associated with AST in existing research [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
+This topic is not addressed substantively in the policy corpus, perhaps due to the inability of STP stakeholders to directly intervene in residential location.
+Parental perceptions of the environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and children's skills [@ghekiereInsightsChildrenIndependent2017] also influence whether they allow their children to walk or cycle to school.
+STP documents do a sufficiently good job at communicated how an increase in AST could improve traffic safety in school zones and how new infrastructure improvements give children the ability to safely travel.
+This messaging has high concurrence with studies that have found that the quality of the built environment [@ikedaAssociationsChildrenActive2018; @kimBuiltNaturalEnvironmental2020] and active travel infrastructure [@pontEnvironmentalCorrelatesChildren2009] facilitate AST.
+
+To increase rates of walking and bicycling independently to school, Riazi et al.
+[-@riaziCorrelatesChildrenIndependent2019] state: "it will be vital for interventions to target modifiable factors, including children's and parents' perceptions of their social environment." We argue that STP messaging should also target multiple modifiable factors, in addition to the health and environmental benefits.
+Parents play the important role of "gatekeeper" by either granting or restricting their child's mobility [@sharminAssociationBuiltEnvironment2017].
+For this reason, stakeholders involved in STP should produce more information that specifically responds to parents' perceived barriers and challenges.
+For example, STP materials could explain how known concerns in a particular municipality or school area have been addressed through local solutions.
+
+## 6.2. Implications for school travel planning
+
+Many municipalities, schools, and transportation consortia use similar content in their public documents about AST.
+It would be worthwhile for STP stakeholders to adapt generic content so that it is more specific to factors associated with AST or parental perceptions about barriers to AST in the local context.
+Rothman et al.
+[-@rothmanDeclineActiveSchool2018a] note that local solutions to address specific school challenges are worthwhile, and we extend this recommendation to include local context in STP messaging about AST.
+
+## 6.3. Limitations
+
+7. Conclusion
 ===============
 
-## 6.1. Future research
+## 7.1. Future research
+
+Future studies may investigate how parents and policymakers outside the field of public health respond to the ways in which AST is framed in STP documents.
+It would be helpful to know which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST.
+This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.
 

### 2021-11-26 AST-Framing-Ontario/AST-Framing-Ontario.Rmd

@@
 ---
-title: How do school travel planning stakeholders frame active school travel in Ontario, Canada?
+title: The framing of active school travel in Ontario, Canada as a health and built environment issue
 author:
@@
 
-journal: "Journal of Transport & Health"
+journal: "Social Science & Medicine"
 date: "`r Sys.Date()`"
@@
 
-Walking and bicycling to school, commonly known as active school travel (AST), has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020].
-In response to this trend, school travel planning has become a popular intervention across Canada that has resulted in mixed success with some schools reporting an increase in AST [e.g., @buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014], while others did not observe a change in behaviour [@buttazzoniPromotingActiveSchool2019] or needed more time and resources to be effective [@mammenPuttingSchoolTravel2015].
-
-School travel planning (STP) is a "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@mammenSchoolTravelPlanning2014].
-This five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities that alleviate concerns and encourage AST [@faulknerSchoolTravelPlans2018].
-STP facilitators and committee members generally intervene at the school through a range of activities such as educational strategies, in-person events or programs, improvements to the school site, and enforcement [@mammenActiveSchoolTravel2014].
-
-How STP is framed to a target audience may influence how this intervention is received and whether it encourages the audience to support it or participate.
-In particular, STP stakeholders make choices about the points of intervention and potential benefits that ought to be communicated to the public to facilitate adoption of AST.
-Educational strategies, which account for approximately one quarter of STP strategies implemented at Canadian schools [@mammenActiveSchoolTravel2014], need to effectively engage multiple audiences – parents, students, politicians – on the issue, challenges, and benefits of AST.
-Promotional materials, therefore, should reflect current knowledge from research about school travel and the built environment, as well as local content specific to factors that influence travel decisions for parents, in order to effectively engage the public in advocating for improving AST or to expose parents and the community to essential information that may prompt behaviour change.
-
-On the one hand, parents have been found to express different understandings, nomenclature, and conceptualizations than planners of the factors that influence school travel [@buliungLivingJourneySchool2021].
-However, it is unknown to what degree there is concurrence between STP materials presented to the public and the literature on school travel and parental perceptions, and how the complexity of the AST issue is presented to the public.
-
-The aim of this paper is to fill this research gap by analyzing how AST is framed by STP stakeholders in Ontario, Canada.
-We used text mining and topic modelling to examine how local policy documents from Ontario municipalities and school boards present and communicate the benefits and barriers of AST and the solutions for improving AST.
-We compared the findings from these documents to a selection of studies on AST and explored the extent to which there is concurrence between research findings to date and promotional materials shared with the public to increase AST.
+Rates of walking and bicycling to school, commonly known as active school travel (AST), have been declining in Canada and the United States for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013], Denmark [@jensenHowObtainHealthy2008], and Japan [@waygoodChapterSixteenJapan2020].
+However, the appetite for AST may be high in many Canadian communities.
+For instance, 40% of children in a study conducted in Toronto, Ontario who are driven to school would like to travel by bicycle instead [@laroucheRatherBikeSchool2016a].
+But the study reported that less than 3% actually do, despite the vast majority having access to a bicycle and living within a short and bikeable distance to school.
+Another study based in London, Ontario reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012].
+From a public health perspective, this represents a huge opportunity to improve health and wellbeing if more children could use active modes to school.
+
+In response to this trend, the Government of Ontario, in Canada, created a fund in 2017 to support communities across the province in developing AST initiatives.
+Green Communities Canada runs the program, called _Ontario Active School Travel_, and determines the projects that will be funded with their support [@GreenCommunities2016].
+As of December 2021, OAST has funded and provided resources for over 20 projects across Ontario.
+Many communities implemented school travel planning (STP), along with encouragement activities like walking school buses or developed resources for schools and parents, among other actions [see @GreenCommunitiesProjects].
+In this context, STP is a popular "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014].
+The five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities following the 5 E's that alleviate concerns about AST and make AST safer and more convenient [@buliungSchoolTravelPlanning2011; @langUnderstandingModalChoice2011].
+
+How AST is framed by STP stakeholders to a target audience, like parents or the general public, may raise awareness about the issue and influence how walking and bicycling to school are perceived.
+Gamson and Modigliani [-@gamsonChangingCulture1987] define a frame as a “central organizing idea or story line that provides meaning” to a particular phenomenon.
+A frame can enable individuals "to locate, perceive, identify, and label" information pertaining to various dimensions of an issue [@goffmanFrameAnalysisEssay1974].
+Therefore, stakeholder groups involved in STP efforts can play a role in shaping public perception about AST in such a way that it attracts greater attention and becomes a "problem" that needs to be addressed through behaviour change or by new policies.
+We also contend that the ways in which the AST issue is framed can affect the policy process, as outlined in Kingdon's [-@kingdonAgendasAlternativesPublic1984] Multiple Streams Framework (MSF), through all three streams (i.e., problem, policy, and politics).
+This framing can ultimately impact financial contributions and potential solutions to address the decline of AST in Canada.
+
+After significant investment of human and financial resources to boost rates of AST in Ontario over the past few years, we ask the following questions: How is AST framed?
+What benefits of AST are communicated to the public?
+What solutions are proposed to increase rates of AST?
+Do proposed solutions focus primarily on the intrapersonal and interpersonal factors, meaning that behaviour change must ultimately result from the individual or household making different travel decisions?
+Or is AST framed as an issue that must be addressed through changes in the built environment or at the policy level?
+
+In this paper, we use text mining and topic modelling to examine how three STP stakeholder groups in Ontario (i.e., municipalities, school boards, and transportation consortia) frame the issue of AST.
+We assembled a corpus of texts from webpages that can be considered an important source of information for the general public or parents who are interested in AST.
+We examine word frequency, bigrams, and concordances in these selected documents, and also identify key topics presented by each stakeholder group.
+We then compare the findings from these documents to a selection of studies on AST and explore the extent to which there is concordance between the literature on AST and materials shared with the public.
 
@@
 
+## 2.1. Benefits of active school travel
+
+The benefits of AST are valuable information to communicate to the public in order to convey the importance of this issue.
+The desire to increase AST in Canada is certainly warranted - there is compelling evidence that children who actively commute to school earn physical and mental health benefits.
+Faulkner et al.
+[-@faulknerActiveSchoolTransport2009] concluded from their systematic review that children who travel on foot or by bicycle to school generally have higher levels of physical activity than their peers who are driven to school.
+However, Schoeppe et al.
+[-@schoeppeAssociationsChildrenActive2015] reported no association between AST and physical activity.
+This relationship could be dose-dependent, meaning that children would have to travel longer distances to accumulate physical activity.
+A walking distance of 1000-1600 metres to school has been found to contribute to overall levels of physical activity for boys [@faulknerSchoolTravelChildren2013].
+The daily routine of travelling to school can be a good opportunity for children to regularly build physical activity into their schedule [@mitraIndependentMobilityMode2013].
+Research has also shown that using active modes to school contributes to improvements in cardiovascular fitness [@borrestadExperiencesRandomisedControlled2012].
+
+More recently, there has been literature exploring the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020], with relevant applications to the study of travel satisfaction [@vandenbergFactorsAffectingParental2020; @westmanChildrenTravelSchool2017].
+Being driven to school reduces community interactions for children which may impact their social wellbeing [@waygoodChildrenTravelIncidental2015], whereas walking and bicycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021].
+This is something that children highly value about travel [@zwertsHowChildrenView2010a] and indicates that social connections through travel are important for their wellbeing.
+AST also provides opportunities for children to engage with the natural environment [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015] which can improve their mental or emotional wellbeing.
+
+## 2.2. Factors that influence active school travel and mode choice
+
+Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behaviour is understood within the context of their household, social, neighbourhood, and policy environments.
+Individual characteristics of the child are also determinants.
+The SEM comes from the field of public health and is a useful framework for understanding complex health behaviours, including travel habits such as walking or bicycling to school, because it identifies multiple determinants that need to be addressed by interventions to facilitate behaviour change.
+The consensus in the literature is that various factors are interrelated and that interventions should target multiple levels in order to increase levels of healthy and physically active modes of travel to school [@mitraIndependentMobilityMode2013].
+Rather than describing an extensive list of factors that influence AST and mode choice in Canada, which has been covered elsewhere [e.g., @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], we briefly discuss a few potentially modifiable determinants that may be targeted for change through STP.
+
+At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018] as parents typically escort younger children.
+There is some evidence that gender is a determinant of AST [@larsenInfluencePhysicalEnvironment2009], with boys being more likely to travel using active modes than girls, although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
+Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], which indicates that shifting parental perceptions and habits is important.
+Convenience and inclement weather have been cited by parents as barriers to AST [@buliungSchoolTravelPlanning2011].
+Parental perceptions of the built or school environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and their children's skills [@ghekiereInsightsChildrenIndependent2017] also influence whether they allow their children to walk or bicycle to school.
+
+Distance between home and school is most strongly associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
+Many studies have also found that the quality of the built environment along the route to school and around the school site [@ikedaAssociationsChildrenActive2018; @kimBuiltNaturalEnvironmental2020; @rothmanActiveSchoolTransportation2021] and provision of active travel infrastructure [@chenPromotingActiveStudent2018a; @pontEnvironmentalCorrelatesChildren2009] facilitate AST.
+Canadian youth report that they feel most safe bicycling on streets in their neighbourhood or that have low volumes of traffic [@TACbikeinfra2020].
+Finally, concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012], which highlights that the volume and speed of cars can be a concern or deterrent for AST.
+
+## 2.3. School travel planning in Canada
+
+School travel planning (STP) has been implemented in Canada since at least the late 2000s.
+Within the STP process, facilitators generally establish multi-sector committees who intervene at the participating school through a range of activities related to the 5E's such as _education_ strategies, _encouragement_ through in-person events or programs, _engineering_ improvements to or around the school site, and _enforcement_ of traffic speeds around schools [@langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
+The first large-scale evaluation of STP as an intervention in Canada took place at twelve schools across the country, including four in Ontario, using parental surveys to measure changes in travel behaviour and perceptions [@buliungSchoolTravelPlanning2011].
+Since then, there have been other assessments of both the efficacy of STP [@buttazzoniPromotingActiveSchool2019; @mammenActiveSchoolTravel2014] and the process of implementing such programs in Ontario [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015].
+STP facilitators have recommended that additional time and resources are needed to improve the efficacy of STP [@mammenPuttingSchoolTravel2015], which highlights that long-term and sustained efforts driven at the policy level are required to address declining rates of AST.
+
+The ways in which AST is framed seem particularly important to shift parental attitudes and perceptions given their reported influence on children's travel mode to school.
+STP activities heavily focus on education or encouragement [@buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014; @buttazzoniSupportingActiveSchool2018], but parents may not always be receptive to the goals of STP and may be resistant to behaviour change [see @buttazzoniSupportingActiveSchool2018].
+Parents have been found to express different understandings, language, and perceptions than planners of the built environment determinants that influence school travel [@buliungLivingJourneySchool2021].
+This is also true when it comes to other factors like convenience of different modes to school [@langUnderstandingModalChoice2011].
+STP stakeholder groups must pay special attention to parents' understanding of the decline of AST as a problem, which may affect their receptivity to proposed solutions.
+
+The “central organizing idea or story line" of AST, to apply the definition from Gamson and Modigliani [-@gamsonChangingCulture1987], could also affect broader support in the community.
+Municipal representatives are perceived to be instrumental but the involvement of other stakeholder groups (e.g., busing consortium representatives and local residents) can be lacking [@buttazzoniSupportingActiveSchool2018].
+In Ontario, it would be reasonable to say that AST has become a policy issue on the education and public health agendas over this time as evidenced by the financial contribution from the provincial government.
+The support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the "policy stream" [see @kingdonAgendasAlternativesPublic1984] has been well engaged.
+It is unknown to what degree the general public (i.e., local residents) has been exposed to messaging about AST, which could affect their participation in the STP process as desired by STP facilitators [@buttazzoniSupportingActiveSchool2018].
+
+The success of STP interventions would likely depend on parental judgments of factors that are related to school travel, as well as support from key policy makers.
+For example, parents have been found to view mixed land use as conducive for driving, despite transport planners viewing neighbourhoods with mixed uses as key for encouraging more active travel [@buliungLivingJourneySchool2021].
+Therefore, stakeholder groups involved in STP must make important choices about the proposed solutions and potential benefits that ought to be communicated to parents and the general public about AST to convey its importance as a policy issue and to facilitate adoption of AST.
+Publicly available content about AST, therefore, needs to effectively engage multiple audiences on this policy issue including parents, children, politicians, and school representatives.
+This information should reflect current knowledge from research on school travel, plus content specific to local factors that influence AST, so that the challenges of AST are adequately defined and the opportunities or solutions to address the problems are clear.
+However, it is unknown to what degree STP materials presented to the general public reflect the scope of evidence from the literature on AST.
+
 3. Data
@@
 
-We assembled a collection of publicly available documents that were sourced online from the main stakeholder groups involved in STP initiatives in Ontario: i) school boards (public and English-speaking only); ii) municipal governments; and iii) transportation consortia.
-Non-profit organizations, police services, and advocacy groups are other stakeholders who may play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all initiatives.
-
-The search was guided first by a list of all English public school boards across Ontario.
-The websites of each school board were manually searched for pages related to school transportation or travel.
+We assembled a collection of publicly available documents that were sourced online from the main stakeholder groups involved in STP initiatives in Ontario: i) school boards (public or Catholic and English-speaking only); ii) municipal governments; and iii) transportation consortia.
+The latter are a unique group of entities sanctioned by Ontario's Ministry of Education in Ontario 2006.
+Each consortium involves a collaboration between regions and school boards; the consortium's objective is to deliver more efficient and timely transportation services to schools in each region [@ministryeducation2006].
+Non-profit organizations, police services, and advocacy groups are other stakeholders who often play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all initiatives across Ontario.
+
+The search was guided first by a list of all English public and Catholic school boards across Ontario.
+The websites of each school board were manually searched for pages related to school transport or travel.
 Any pages relevant to these topics were manually downloaded.
 Next, we collected documents by searching municipal government and transportation consortia websites.
-The latter were identified based on geographic area (i.e., the municipalities and/or transportation consortia that are in the same geographic area of each school board).
-Pages related to active or school travel were manually downloaded.
-Webpages from STP stakeholder websites were included in our analysis if they were easy to find.
-This primary criteria was important since our analysis pertains to how such issues are framed to the public.
-Thus, we included only webpages that were easy to find, which we defined as requiring no more than 2-4 separate links from the initial Google search.
-
-The initial corpus of policy documents included 64 relevant webpages (i.e., one page or more) from all STP stakeholder groups.
-It is important to note that school boards, municipalities, and transportation consortia may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents, which means that some of these groups for particular regions in Ontario are not included in our analysis.
+These were identified based on geographic area (i.e., the municipalities and/or transportation consortia that are in the same geographic area of each school board).
+Webpages related to active transport or school travel were manually downloaded.
+
+Webpages from STP stakeholder groups were included in our analysis if they were easy to find.
+This primary criterion was important since our analysis pertains to how such issues are framed to the general public.
+Thus, we included only webpages that were readily accessible, which we defined as requiring no more than 2-4 separate links from the initial Google search.
+
+The initial corpus of documents from STP stakeholder groups included 69 relevant webpages (i.e., one page or more) from all STP stakeholder groups.
+We refer to these as policy documents throughout the paper.
+It is important to note that school boards, municipalities, and transportation consortia may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents.
 Search results are summarized in Table \ref{tab:policy-documents}.
@@
   Total = c("62", "62", "39"),
-  Included = c("31", "25", "8")
+  Included = c("32", "28", "9")
 )
@@
 
-### 3.2.1. Academic papers
+### 3.1.2. Academic papers
 
@@
 
-A multi-step process was conducted to ensure that the analysis captured as much content as possible from both the policy documents (n = 64) and academic papers (n = 233).
+A multi-step process was conducted to ensure that the analysis captured as much text as possible from both the policy documents (n = 64) and academic papers (n = 233).
 To begin, the webpages, which were manually downloaded in portable document format (PDF), were trimmed so that pages that only consisted of tables, figures, or references were removed.
@@
 Finally, we reviewed all of the documents to remove hyphenation by line breaks and to keep hyphenated words together on the same line.
-Any ligatures (e.g., combinations of characters or letters that were not properly detected during the conversion process) were fixed by inserting the unicode sequence of character to replace the missing sequence of characters.
+Any ligatures (e.g., combinations of characters or letters that were not properly detected during the conversion process) were fixed by replacing the unicode sequence of character by inserting the missing sequence of characters.
 
@@
 Issues that pertain to public health or wellbeing are often presented to the public through particular frames to influence perceptions or behaviours.
-Gamson and Modigliani [-@gamsonChangingCulture1987] conceptualize a frame as a “central organizing idea or story line that provides meaning” to a particular phenomenon.
-A frame can enable individuals "to locate, perceive, identify, and label" information pertaining to various dimensions of an issue [@goffmanFrameAnalysisEssay1974].
+As previously mentioned, a frame is a "central organizing idea or story line that provides meaning" to a public issue or phenomenon [@gamsonChangingCulture1987].
 Scholars in the field of political communications have proposed that communicators, such as the media or an institution, construct the narrative of a frame for policy positions or public issues in order to activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
-Framing can be used to position existing solutions as suitable to address particular issues [@mahFramecriticalPolicyAnalysis2014], which may prevent the public from being aware of other policy approaches that challenge the status quo to bring about more radical change.
+Organized groups of stakeholders can employ similar methods to attract attention to particular issues.
+Framing can be used to position existing solutions as suitable to address particular issues [@mahFramecriticalPolicyAnalysis2014], which may prevent the public from being aware of other policy approaches that challenge the status quo.
 The way policy issues are framed is ultimately important to understand because it plays a role in either altering or preserving the existing social perceptions.
+This, in turn, can affect whether issues are put on the agenda of policy makers and can determine which solutions are proposed to address the problem [@kingdonAgendasAlternativesPublic1984].
 
 Framing of issues is an important step in developing health policy.
-An obvious example over the past decade is the framing of climate change as a public health issue [e.g., @ depouxCommunicatingClimateChange2017; @maibachReframingClimateChange2010; @weathersDevelopmentsFramingClimate2016] to increase public engagement and reception of the issue.
-Transport planners also use different frames to guide the extent to which transport policies can be adapted to address climate change.
+An obvious example over the past decade is the framing of climate change as a public health issue [e.g., @depouxCommunicatingClimateChange2017; @maibachReframingClimateChange2010; @weathersDevelopmentsFramingClimate2016] to increase public engagement and awareness of the issue.
+This framing has slowly advanced this issue on public policy agendas as public attention puts pressure on the policy stream to adopt frameworks for action.
+For example, transport planners also use different frames to guide the extent to which transport policies can be adapted to address climate change.
 In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review the representation of issues such as mobility and social exclusion in municipal policies from four western Canadian cities under the current circumstances of climate change.
-The authors found four primary frames: “The Growing City”, “If You Build It, They Will Come”, “Better City for All”, and a “the Resilient City”.
+The authors found four primary frames: “The Growing City”, “If You Build It, They Will Come”, “Better City for All”, and a “the Resilient City” [@reynardGrowthResilienceHow2021].
 Each frame presented the nature, opportunities, and challenges of climate change in different ways which set the stage for the types of mitigation and adaptation strategies that cities were proposing to address this issue.
 
-Given the range of factors at multiple levels of the socioecological model that influence school travel, it is important to understand how walking and bicycling to school are framed to the public.
-Is active school travel framed as a public health or environmental issue?
-Is it framed as both?
-Do proposed solutions to increase AST focus primarily on the intrapersonal and interpersonal factors, meaning that behaviour change must ultimately result from different decisions made by the individual or the household?
-Or is the decline in AST framed as an issue that must be addressed through changes in the built environment?
-These are the types of questions that we aim to answer in this paper.
-To our knowledge, this topic has not be addressed in the school travel literature to date.
+In a similar way, we hypothesize that STP stakeholder groups in Ontario have framed AST in particular ways to effectively engage multiple audiences on this policy issue including parents, local residents, school representatives, and municipal representatives.
+These groups are likely identifying points of intervention and potential opportunities to build support for and encourage AST.
 
@@
 
-The topic modelling analysis was conducted in R.
-We primarily used the following packages: `topicmodels` [@R-topicmodels], `word2vec` [@R-word2vec], and `wordcloud` [@R-wordcloud] to examine content in the documents that were sourced for this project.
-These packages have functions for determining the frequency of specific words in each document, relationships (e.g., pairs of adjacent terms) and correlations between words, and estimating Latent Dirichlet allocation (LDA) models to classify documents according to the topics that are contained within them.
-We describe in the section below how we used these functions to produce our results.
+We use topic modelling in R to conduct the framing analysis.
+Topic modelling is a machine learning technique that can identify what language and concepts are being communicated by analyzing text.
+This method is more practical for researchers working with large amounts of text because it replaces the manual coding of topics that would normally take place to analyze or summarize textual data [@jacobiQuantitativeAnalysisLarge2016].
+In the data pre-processing phase, we tokenize the text in the documents and create a document-term matrix so that it is in the correct format for analysis.
+We primarily use the following packages: `tidytext` [@R-tidytext], `topicmodels` [@R-topicmodels], `word2vec` [@R-word2vec], and `wordcloud` [@R-wordcloud] to examine text in the documents that were sourced for this project.
+These packages have functions for determining the frequency of specific words in each document or relationships (e.g., pairs of adjacent terms called bigrams) and correlations between words.
+These methods can reveal what language and concepts are being communicated to the general public.
+Topic modelling is a popular method for analyzing text from social media platforms [@albalawiUsingTopicModeling2020] or news articles [@jacobiQuantitativeAnalysisLarge2016].
+We estimate latent Dirichlet allocation (LDA) models to classify both the STP and documents according to the topics that are contained within them.
+This method "treats each document as a mixture of topics, and each topic as a mixture of words" [@silgeTextMining2021].
+The model's output is "a set of topics consisting of clusters of words that co-occur in these documents according to certain patterns" [@jacobiQuantitativeAnalysisLarge2016].
+Researchers must then interpret the identified topics, as done after other methods of manual coding.
+We also compare the topics between the policy documents and the academic papers, and use our interpretation to answer the questions outlined above that guide this paper.
+This methodology is not familiar to many, so we describe in more detail below how we used specific functions and code in R to produce our results.
 
@@
 
-We analyzed word and document frequency for each corpora.
+We analyzed word and document frequency for each set of documents (i.e., corpus).
 Table \ref{tab:word-table} shows the most frequent terms found in the municipal, transportation consortia, school board, and academic documents.
-As expected, STP documents and academic papers reference _active travel_, _walking_, _biking_ or _cycling_, and _students_ more than other terms.
-Each corpora also has _safety_ and _traffic_ as common words which suggests congruence on these key factors between the research literature and how AST is framed to the public.
-The word _physical_ is present in each corpus which could refer to either _physical activity_, _physical health_, or the _physical environment_.
-Furthermore, documents from STP stakeholders discuss _resources_, _information_, and _services_ about school travel.
-In the section below, the context in which these terms appear is explored further through their concordance.
-Unlike the academic papers, STP stakeholder documents include the words _route_ or _routes_.
-This could reflect their role in identifying safe routes to school to share with parents or families, as well as the STP emphasis on making the physical environment safer for AST.
-The academic corpora differs from the policy documents in that _parents_ and _distance_ are the second and third most common terms.
-In addition, _time_, _factors_, _environment_, and _age_ are also identified in academic papers.
+As expected, policy documents and academic papers reference _active travel_, _walking_, _biking_ or _cycling_, and _students_ more than other terms.
+Each corpus also has _safety_ and _traffic_ as common words which suggests congruence on these key factors between the research literature and how AST is framed to the public.
+The word _physical_ is present in each corpus, but it's not clear what this refers to (e.g, _physical activity_, _physical health_, or the _physical environment_).
+Furthermore, documents from STP stakeholder groups discuss _resources_, _information_, and _services_ about school travel.
+In the section below, the context in which these terms are discussed is explored further.
+
+Unlike the academic papers, policy documents include the words _route_ or _routes_ as frequent terms.
+This could reflect the role of STP stakeholder groups in identifying safe routes to school to share with parents or families, as well as the STP emphasis on making the physical environment safer for AST.
+The academic corpus differs from the policy documents in that _parents_ and _distance_ are the second and third most common terms.
+In addition, _time_, _factors_, _environment_, and _age_ are also identified in the academic papers.
 These words are absent from the list of common words in policy documents.
-Table \ref{tab:word-table} indicates that the research corpora discusses a broader range of determinants of AST than the policy documents.
+Table \ref{tab:word-table} indicates that the academic corpus discusses a broader range of determinants of AST than the policy documents.
 The number of references for each term in the academic papers is also significantly higher due to the inclusion of more documents.
@@
 
-Bigrams for each policy corpora that occur more than 5 times are shown in Figures \ref{fig:city-visual},  \ref{fig:consortia-visual}, and \ref{fig:school-visual}.
+Bigrams refer to a pair of consecutive words.
+We use the `unnest_tokens` function from the _tidytext_ package to determine the bigrams.
+Figures \ref{fig:city-visual}, \ref{fig:consortia-visual}, and \ref{fig:school-visual} show the bigrams that occur more than 5 times for each set of policy documents.
 These figures help to make further sense of the word frequencies reported above, and highlight the main ideas that are presented to the public in each of the policy corpora.
-Municipalities primarily discuss _physical activity_ (n = 53) and _public health_ (n = 19) in the context of active travel.
-In addition, _travel planning_ (n = 19), _bike lanes_ (n = 16), and _safe routes_ (n = 14) are also identified, conceivably as interventions and built environment factors that support AST.
-Key issues related to transport such as _traffic safety_ (n = 10), _air quality_ (n = 9), and _greenhouse gases_ (n = 9) are conveyed to the public through AST documents.
-It is not surprising to find this focus in AST documents given that municipalities in Ontario are concerned about climate change and have increasingly looked to active modes of travel to offset transport-related emissions in urban areas.
+Municipalities primarily discuss _physical activity_ (n = 53) and _public health_ (n = 19) in the context of AST.
+In addition, _travel planning_ (n = 19), _bike lanes_ (n = 16), and _safe routes_ (n = 14) are also identified, conceivably as either proposed solutions or built environment factors that support AST.
+Key issues related to transport such as _traffic safety_ (n = 10), _air quality_ (n = 9), and _greenhouse gases_ (n = 9) are conveyed to the public through these policy documents.
+It is not surprising to find this focus given that municipalities in Ontario are concerned about climate change and have increasingly looked to active modes of travel to offset transport-related emissions in urban areas.
 
@@
 Biking or cycling is notably absent from transportation consortia documents.
+Overall, the policy documents There appears convey an emphasis on the built environment, rather than household decision-making.
 
@@
 
-We then combined all municipality, school board, and transportation consortia documents into one "policy" corpora.
-This enabled us to examine and visualize the most common bigrams found across all of the STP material in Ontario that was collected for this study.
-Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the corpora.
-In addition to the common bigrams already identified above, we also found _mental health_, _walk day_, and _green communities_ as common pairs of consecutive words.
-Overall, policy documents from STP stakeholders seem to focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or considerations; and iv) supports for AST.
-
-We analyzed bigrams in the academic corpora separately to make comparisons with the policy corpora.
-Figure \ref{fig:academic-visual} indicates that the academic corpora includes several common bigrams that were also found in the policy documents including _physical activity_ (n = 1566), which is the top bigram, _traffic safety_ (n = 308), and _safe routes_ (n = 268).
-However, many other factors relating to AST are identified in the research literature that are not presented to the public through policy documents.
+We then combine all municipality, school board, and transportation consortia documents into one "policy" corpus.
+This enabled us to examine and visualize the most common bigrams found across all of the material in Ontario that was collected for this study.
+Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the policy corpus.
+In addition to the bigrams already identified above, we also found _mental health_, _walk day_, and _green communities_ as common pairs of consecutive words.
+The latter terms represent the significant involvement of the non-profit organization in supporting AST initiatives through the Ontario Active School Travel program.
+Overall, the policy documents from STP stakeholder groups seem to focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or considerations; and iv) supports for AST.
+This interpretation indicates that the general public accessing information about AST in Ontario is informed about an adequate range of content related to this issue.
+
+Next, we analyze bigrams in the academic corpus separately to make comparisons with the policy corpus.
+Figure \ref{fig:academic-visual} indicates that academic papers include several common bigrams that were also found in the policy documents including _physical activity_ (n = 1566), which is the top bigram, _traffic safety_ (n = 308), and _safe routes_ (n = 268).
+However, many other factors are identified in the research literature that are not presented to the general public through policy documents.
 After _physical activity_, _built environment_ (n = 1175), _independent mobility_ (n = 774), and _urban form_ (n = 352) are the most frequent pairs of consecutive words.
@@
 It is evident that many papers investigate gender differences in AST given that _boys girls_ (n = 211) is another common bigram.
-Finally, the presence of _statistically significant_ among the top bigrams underscores that researchers aim to identify determinants that are not due to chance but that likely influence AST.
-The academic corpora focuses on a greater range of topics than found in the STP material.
+Finally, the presence of _statistically significant_ among the top bigrams underscores that some researchers aim to identify determinants using statistical measures.
+We find that the academic corpus focuses on a greater range of topics than found in the policy documents.
 
@@
 
-```{r, academic-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the academic papers.}
+```{r, academic-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the academic papers."}
 ggraph(academic_bigram_graph, layout = "fr") +
@@
 
-We interpreted the most common bigrams from the policy corpora (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholders are focusing on and communicating to the public about AST.
-We then used the `kwic` function from the R _quanteda_ package to identify and better understand the context of these key themes.
-Table \ref{tab:policy-concordance} presents examples of the key themes that were extracted from select policy documents to demonstrate how the most common bigrams are communicated to the public.
+We interpret the most common bigrams from the policy corpus (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholder groups are focusing on and communicating to the public about AST.
+We then use the `kwic` function from the _quanteda_ package to better understand the context of these key ideas.
+Table \ref{tab:policy-concordance} presents some examples of the context that was extracted from select policy documents to demonstrate how the most common bigrams are communicated to the public.
 
@@
 text_tbl <- data.frame(
-  Terms = c("Air Quality", "Benefit", "Bus", "Community", "Emissions", "Health", "Lanes", "Mental Health", "Physical Health"),
+  Terms = c("Air Quality", "Benefit", "Walking School Bus", "Community", "Emissions", "Health", "Lanes", "Mental Health", "Physical Health"),
   Stakeholder = c("School Board", "Municipality", "School Board", "School Board", "Consortia", "Municipality", "Municipality", "Municipality", "Municipality"),
@@
 This is also a great opportunity for your child to socialize with school friends in a monitored and safe way where they can practice social distancing, modelled by a leader.",
-    "Engage community stakeholders (school boards, municipalities, police, public health professionals, parents/guardians, administrators, educators and children) to work together to identify and to solve their school travel needs.",
+    "Help your students get started on the right foot - encourage them to walk or bike to school when possible.
+Even leaving the car a block or two and walking the rest of the way helps.
+It’s good for the environment and your health, and teaches your child independence and community awareness.",
     "An active school commute also reduces congestion in school zones and contributes to reducing greenhouse gas emissions – it’s a win-win for everyone!",
@@
 
-academic_lda_num <- FindTopicsNumber(
-  academic_dtm, 
-  topics = seq(from = 2, to = 25, by = 1),
-  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
-  method = "Gibbs")
+#academic_lda_num <- FindTopicsNumber(
+  #academic_dtm, 
+  #topics = seq(from = 2, to = 25, by = 1),
+  #metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  #method = "Gibbs")
   #control = list(seed = 77),
@@
 FindTopicsNumber_plot(policy_lda_num)
-FindTopicsNumber_plot(academic_lda_num)
+#FindTopicsNumber_plot(academic_lda_num)
 
@@
 
-policy_lda <- LDA(policy_dtm, k = 5, method = "Gibbs", control = NULL, model = NULL)
-
-academic_lda <- LDA(academic_dtm, k = 19, method = "Gibbs", control = NULL, model = NULL)
+policy_lda <- LDA(policy_dtm, k = 7, method = "Gibbs", control = NULL, model = NULL)
+
+academic_lda <- LDA(academic_dtm, k = 17, method = "Gibbs", control = NULL, model = NULL)
 ```
@@
 
-```{r municipal-terms, echo=FALSE}
+```{r municipal-terms, include=FALSE}
 municipal_top_terms <- municipal_topics %>%
@@
 
-```{r school-terms, echo=FALSE}
+```{r school-terms, include=FALSE}
 school_top_terms <- school_topics %>%
@@
 
-```{r consortia-terms, echo=FALSE}
+```{r consortia-terms, include=FALSE}
 consortia_top_terms <- consortia_topics %>%
@@
 
-Finally, we conducted topic modelling to examine the different topics found in the policy and academic corpora.
-We focused on the policy corpora, instead of individually assessing the municipal, school, and consortia corpus, so that we could report on the primary and secondary frames used across all documents put out by STP stakeholders in Ontario.
-To determine the number of discrete topics in each corpus, we used the ldatuning package.
-We then used the `LDA` function from the topicmodels package to estimate an LDA model for each group of documents.
-The policy corpora, which combined all documents from municipalities, schools, and transportation consortia, had 5 topics.
-The academic corpora had 17 topics.
+Finally, we conduct topic modelling to examine the different topics found in the policy and academic corpora.
+We focus on the policy corpus, instead of individually assessing the municipal, school, and consortia documents, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario.
+To determine the number of discrete topics in each corpus, we use the _ldatuning_ package.
+We then use the `LDA` function from the _topicmodels_ package to estimate an LDA model for each group of documents.
+The parameters from the _ldatuning_ package suggest that the policy corpus has between 7 and 9 topics and the academic corpus has between 17 and 25 topics.
+After running the LDA model for the academic corpus, it was too difficult to interpret a minimum of 17 topics based on the clusters of words that were identified.
+We experimented with the model by adjusting the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap.
 Figures \ref{fig: policy-terms} and \ref{fig: academic-terms} present the main terms that are associated with the topics found in each corpus.
 
-In the policy corpus, we identified the following topics: (1) resources for walking, (2) busing information and eligibility; (3) benefits of active travel; (4) bicycling and the environment; and (5) supporting active travel.
-These findings reveal that STP stakeholders are sending the message that walking and bicycling to school as healthy travel modes for students, particularly as a means to get physical activity.
+In the policy corpus, we interpret the following topics based on the cluster of words: (1) resources for walking, (2) busing information and eligibility; (3) benefits of active travel; (4) bicycling and the environment; and (5) supporting active travel.
+These topics indicate that STP stakeholder groups are sending the message that walking and bicycling to school are healthy travel modes for students, particularly as a means to get physical activity.
 We also found that there is information shared to support parents and students in using active modes to school such as the availability of cycling lanes or route tips for walking.
-STP stakeholders appear to be communicating that AST is possible and safe as a result of improvements to the built environment and available resources for parents and children.
-A final focus in the policy documents is on various efforts that are underway to support active travel including route planning.
-
-We expected to find a higher number of topics in the academic corpus due to the larger number of documents in the corpora and the diversity of content examined in existing literature about school travel.
-The following topics were identified, which touch upon a broader range of factors that are associated with or related to AST than are found in the policy corpus: (1) __unclear__ (2) AST in Ontario and Canada; (3) __unclear__; (4) children’s independent mobility; (5) safe routes to school programs; (6) commuting and distance; (7) density in the built environment and walking routes; (8) __unclear__; (9) walking interventions; (10) bicycling influences; (11) interpersonal and household influences on trips; (12) behaviours and attitudes; (13) __unclear__; (14) __unclear__; (15) walking distance; (16) __unclear__;  (17) physical activity measures or results; (18) bicycling attitudes; and (19) __unclear__.
-
-The policy corpus primarily frames AST as a health and environmental issue.
-Many municipal and school documents position walking, bicycling, or rolling to school as beneficial to individual health, including improvements to physical activity levels or mental health, and to the broader community through a reduction in traffic and vehicle emissions.
+
+The academic corpus has a higher number of topics likely due to the volume of papers that were sourced.
+The following topics were identified based on the clusters of words: (1) __unclear__ (2) AST in Ontario and Canada; (3) __unclear__; (4) children’s independent mobility; (5) safe routes to school programs; (6) commuting and distance; (7) density in the built environment and walking routes; (8) __unclear__; (9) walking interventions; (10) bicycling influences; (11) interpersonal and household influences on trips; (12) behaviours and attitudes; (13) __unclear__; (14) __unclear__; (15) walking distance; (16) __unclear__;  (17) physical activity measures or results; (18) bicycling attitudes; and (19) __unclear__.
+
+We conclude that the policy corpus primarily frames AST as a health and environmental issue.
+Policy documents do not reflect the diversity of content found in the academic papers and instead focus on a few factors.
+STP stakeholder groups appear to position walking, bicycling, or rolling to school as beneficial to individual health, as an opportunity for physical activity or to improve mental health, and to the broader community through a reduction in traffic and vehicle emissions.
+Here, we present some examples from the policy documents to illustrate how the health and environmental frames are communicated:
+
 > _If you live in a walk zone, the best way to get to school is by walking or biking.
@@
 
-We found that some of these documents make direct references to topics found in research on school travel and the built environment.
-For example, some policy documents identify programs that have been researched in the literature and found to be effective, such as walking school buses, or explain how an increase in AST will reduce parent safety concerns.
+However by examining document frequency (see Section 5.1), we found that some terms are not present in all policy documents.
+This suggests that although documents pertain to the subject of active travel or school travel, some stakeholders across Ontario are not disseminating information about AST.
+For example, a document may discuss active travel but not to school or school travel but only by bus and not by active modes.
+We manually searched the policy corpus and found that 48% of documents mention AST and 16% mention STP.
+This confirms that many municipalities, school boards, and transportation consortia are not promoting AST through their webpages or indicating their involvement in the STP process.
+Instead, inclement weather and impacts to busing is a common topic addressed in school board and transportation consortia documents.
+
+Furthermore, we found that some policy documents make direct reference to topics found in the academic papers.
+For example, some policy documents encourage AST programs that have been researched and evaluated in the literature, such as walking school buses, or explain how an increase in AST will reduce parent safety concerns.
+
 > _ For their health, safety, environment and community: Kids learn healthy habits and concentrate better in class; One less car (yours) reduces traffic and parking problems in school zones; Teach your kids about traffic safety; Start a walking school bus; your kids make friends in every grade, and that can prevent bullying._ (City of Guelph)
@@
 
-The secondary frame for AST in municipal documents is the opportunity or prospect of behaviour change.
+The secondary frame for AST in policy documents is the opportunity or prospect of behaviour change.
 Some cities and schools explain how children and parents can leave the car at home and make the journey to school on foot or by bike by describing efforts to make AST safer.
-This frame enables the public to evaluate their own travel decisions and to access resources (e.g., walking skills checklist) that will help them make AST a first choice.
-Some documents communicate what is being done by the municipalities or schools, like school travel planning, while others emphasize the active role of the parent in creating opportunities for AST in their household or neighbourhood.
+This frame encourages the public to evaluate their own travel decisions and to access resources (e.g., walking skills checklist) that will help them make AST a first choice.
+Some documents emphasize the role of the parent in creating opportunities for AST in their household or neighbourhood, however few documents address the main barriers as perceived by parents (e.g., distance, travel arrangements for multiple people, or convenience).
+Examples of this secondary frame include:
+
+> _A way to make sure your child is safe while walking to school is with a 'walking school bus.' Here are some tips for a walking school bus: Invite families who live nearby to walk; Pick a route and take a test walk; Take side streets and paths that are less busy with traffic; Decide how often the group will walk together; Talk with your boss to adjust your day; Have fun!
+(City of Ottawa)
+
+> Help your students get started on the right foot - encourage them to walk or bike to school when possible.
+Even leaving the car a block or two and walking the rest of the way helps.
+It’s good for the environment and your health,  and teaches your child independence and community awareness._ (Halton District School Board)
+
+> _Want to boost your child’s mental and physical health?
+Ottawa Public Health, City of Ottawa, and OSTA have produced a tipsheet for parents about “active transportation” to school – fitting walking and wheeling into your daily routine._ (Ottawa-Carleton District School Board)
+
+Finally, the policy documents discuss proposed solutions to encourage AST.
+STP stakeholder groups seem to be communicating that AST is possible and safe as a result of improvements to the built environment and available resources for parents and children.
+A final focus in the policy documents is on various efforts that are underway to support active travel including route planning.
+
 > _School Travel Planning is a community-based approach that aims to increase the number of students and adults choosing active and sustainable travel to get to and from school.
@@
 
-> _A way to make sure your child is safe while walking to school is with a 'walking school bus.' Here are some tips for a walking school bus: Invite families who live nearby to walk; Pick a route and take a test walk; Take side streets and paths that are less busy with traffic; Decide how often the group will walk together; Talk with your boss to adjust your day; Have fun!
-(City of Ottawa)
-
-> Help your students get started on the right foot -encourage them to walk or bike to school when possible.
-Even leaving the car a block or two and walking the rest of the way helps.
-It’s good for the environment and your health,  and teaches your child independence and community awareness._ (Halton District School Board)
-
 > _Today, as more and more of our neighbourhoods are being retrofitted with new sidewalks and bike lanes, pedestrian crossovers, street lights, reduced speed limits and/or crossing guards, the walk or bike ride to and from school has never been easier, safer or healthier._  (Hamilton-Wentworth District Catholic School Board)
-
-> _Want to boost your child’s mental and physical health?
-Ottawa Public Health, City of Ottawa, and OSTA have produced a tipsheet for parents about “active transportation” to school – fitting walking and wheeling into your daily routine._ (Ottawa-Carleton District School Board)
-
-Finally, many municipalities, schools, and consortia make no mention of active school travel on their main website pages for active transportation.
-Nonetheless, some municipalities explain how changes to the built environment are being implemented to facilitate active travel.
-Schools or consortia that do not refer to AST simply provide information about the busing service available to families in the region.
-Inclement weather and impacts to busing is a common topic addressed in those documents.
-> _We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments._ (City of Brantford)
-
-> _The City of Burlington ensures all cyclists, pedestrians and drivers have access to safe and accessible transportation services and programs_ (City of Burlington)
 
@@
 
-We analyzed how AST is framed in documents available to the public on the websites of STP stakeholders in Ontario.
+Using topic modelling, we analyzed how AST is framed in documents available to the general public on the websites of STP stakeholder groups in Ontario.
 We found that AST is primarily framed as beneficial to the health and wellbeing of children and to environmental sustainability.
-This was confirmed by the most common bigrams identified in the policy corpora, as well as the topics identified by the LDA model.
-Many studies and reviews have focused on the association between AST and physical activity [e.g., @faulknerActiveSchoolTransport2009; @mitraChildrenActivitytransportationLifestyles2017; @schoeppeAssociationsChildrenActive2015], with findings consistently demonstrating that children who travel by walking or bicycling to school are more active than their peers who do not use active travel.
-More recently, researchers have been exploring the link between transport and children's wellbeing [@babbChildrenActiveTravel2017; @waygoodTransportChildrenWellbeing2020], which has relevant applications to the study of school travel and satisfaction [see @vandenbergFactorsAffectingParental2020].
-We concluded that STP promotional materials have high concurrence with this topic in the research on school travel and the built environment.
-Framing AST as a health issue is certainly warranted - there is strong evidence that children who walk and bicycle to school accrue physical and mental health benefits.
-Furthermore, concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012].
-Parents often have concerns about traffic volume, speed, and congestion around schools [@lingRelationshipMotorVehicle2021; @rothmanSchoolEnvironmentStudent2017], therefore the framing of AST as an environmental issue is in alignment with evidence from existing studies.
-
-The secondary frame of AST is that it is a behaviour that can and should be adopted by children and parents given the environmental and program supports available in the community.
-STP stakeholders emphasize that parents can access resources or trips to support their children in commuting by active modes to school.
-They also share information about interventions such as school travel plans and bicycle lanes to frame AST as safe and practical.
-However, STP materials neglect to address many intrapersonal and household factors that influence or predict AST.
-At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018], but AST is not framed as an activity for children based on age.
-STP stakeholders may wish to emphasize to parents that older children have greater traffic safety and cognitive abilities to navigate their own routes to school.
-There is also some evidence that gender is a determinant of AST [@babbChildrenActiveTravel2017; @larsenInfluencePhysicalEnvironment2009], although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
-STP materials do not discuss this determinant of AST but it may be helpful to identify strategies or messages that alleviate specific concerns that relate to a child's gender.
-
-Furthermore, distance between home and school is the factor most associated with AST in existing research [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
-This topic is not addressed substantively in the policy corpus, perhaps due to the inability of STP stakeholders to directly intervene in residential location.
-Parental perceptions of the environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and children's skills [@ghekiereInsightsChildrenIndependent2017] also influence whether they allow their children to walk or cycle to school.
-STP documents do a sufficiently good job at communicated how an increase in AST could improve traffic safety in school zones and how new infrastructure improvements give children the ability to safely travel.
-This messaging has high concurrence with studies that have found that the quality of the built environment [@ikedaAssociationsChildrenActive2018; @kimBuiltNaturalEnvironmental2020] and active travel infrastructure [@pontEnvironmentalCorrelatesChildren2009] facilitate AST.
+This was confirmed by the most common bigrams identified in the policy corpus, as well as the topics identified by the LDA model.
+The policy documents adequately reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015].
+STP stakeholder groups also communicate that increasing AST may reduce traffic near and around schools which could alleviate parental concerns about traffic safety.
+The potential outcomes of increased AST are highlighted which may be persuasive arguments to motivate behaviour change, which is the secondary frame of AST that we interpreted based on the LDA models.
+
+The proposed solutions to the problem of declining AST that are communicated to the general public are mostly educational (e.g., safety tips or maps of safe routes) and engineering changes (e.g., traffic calming or bicycle lanes).
+These solutions have to sufficiently address real and perceived concerns that pose barriers to AST in order to encourage adoption.
+In most documents, the emphasis is on providing parents with resources that help them switch modes for the school commute and/or on reassuring them that the built environment has become safer and friendlier to active travelers.
+
+However, the policy documents noticeably lacked a focus on individual and household level determinants of AST.
+For example, the role of convenience and inclement weather in shaping household travel decisions [@buliungSchoolTravelPlanning2011] or the age at which children become allowed to travel by active modes or independently [@mammenUnderstandingDriveEscort2012] were not discussed.
+Given the range of factors that influence AST in a Canadian setting [_inter alia_, see @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], STP stakeholder groups must decide which points of intervention that they can reasonably have some influence towards.
+This should also depend on the local context so that barriers to AST as perceived by parents are addressed.
+It could be that STP stakeholder groups perceive to have more control over the micro-scale elements of the built environment, like traffic calming, rather than the ability to influence the number of trips to different destinations that households need to make.
+STP stakeholders are also unable to intervene in residential location, which affects distance to school.
 
@@
 
-Future studies may investigate how parents and policymakers outside the field of public health respond to the ways in which AST is framed in STP documents.
+Future studies may investigate how parents and policy makers outside the field of public health respond to the ways in which AST is framed in STP documents.
 It would be helpful to know which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST.

### 2021-11-26 AST-Framing-Ontario/AST-Framing-Ontario.tex

@@
 \usepackage{graphicx}
-\usepackage{booktabs} % book-quality tables
 %%%%%%%%%%%%%%%% end my additions to header
@@
 \bibliographystyle{elsarticle-harv}
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{graphicx}
@@
 
-\hypertarget{school-travel-planning-in-canada}{%
-\subsection{1.1. School travel planning in
-Canada}\label{school-travel-planning-in-canada}}
-
 Walking and bicycling to school, commonly known as active school travel
-or active school transportation (AST), has been declining in Canada and
-North America for decades ({\textbf{???}}), with levels much lower than
-other developed countries like The Netherlands ({\textbf{???}}) and
-Japan ({\textbf{???}}). This trend has prompted a multi-sector response
-to identify strategies to increase AST, the most popular of which is a
-growing interest in school travel planning across Canada.
+(AST), has been declining in Canada and North America for decades
+({\textbf{???}}), with levels much lower than other developed countries
+like The Netherlands ({\textbf{???}}) and Japan ({\textbf{???}}). In
+response to this trend, school travel planning has become a popular
+intervention across Canada that has resulted in mixed success with some
+schools reporting an increase in AST (e.g., {\textbf{???}}; Mammen et
+al., 2014), while others did not observe a change in behaviour
+(Buttazzoni et al., 2019) or needed more time and resources to be
+effective ({\textbf{???}}).
 
@@
 diverse sectors including education, planning, transportation, and
-public health ({\textbf{???}}). Parents and parent councils also
-typically have a role in supporting or implementing STP. The
-intervention encourages participation from the broader community and
-collaboration between involved stakeholders, who contribute their
-expertise to remove ``school-specific'' barriers to AST and to identify
-strategies for promoting and encouraging AST. STP may also involve other
-stakeholders including local advocacy groups or environmental
-organizations who are familiar with the state of AST at the
-community-level. Buliung et al.~({\textbf{???}}) piloted an STP
-intervention at 12 schools in 4 Canadian provinces and reported that it
-increased AST rates and led to a ``mobilization of diverse community
-resources''. Since this seminal study, STP interventions have become
-increasingly popular and common at schools across Canada and have even
-attracted funding from provincial governments.
+public health to develop action plans ({\textbf{???}}). This five-step
+process involves identifying barriers to AST based on the local context
+and implementing approaches or activities that alleviate concerns and
+encourage AST ({\textbf{???}}). STP facilitators and committee members
+generally intervene at the school through a range of activities such as
+educational strategies, in-person events or programs, improvements to
+the school site, and enforcement (Mammen et al., 2014).
 
-\hypertarget{correlates-of-active-school-travel}{%
-\subsection{1.2. Correlates of active school
-travel}\label{correlates-of-active-school-travel}}
+How STP is framed to a target audience may influence how this
+intervention is received and whether it encourages the audience to
+support it or participate. In particular, STP stakeholders make choices
+about the points of intervention and potential benefits that ought to be
+communicated to the public to facilitate adoption of AST. Educational
+strategies, which account for approximately one quarter of STP
+strategies implemented at Canadian schools (Mammen et al., 2014), need
+to effectively engage multiple audiences -- parents, students,
+politicians -- on the issue, challenges, and benefits of AST.
+Promotional materials, therefore, should reflect current knowledge from
+research about school travel and the built environment, as well as local
+content specific to factors that influence travel decisions for parents,
+in order to effectively engage the public in advocating for improving
+AST or to expose parents and the community to essential information that
+may prompt behaviour change.
 
-Factors that influence AST are typically conceptualized according to the
-socioecological model whereby children's travel behaviour is understood
-within the context of their household, social, and built environments
-(see {\textbf{???}}). At the individual level, older child age is often
-associated with AST ({\textbf{???}}; {\textbf{???}}; {\textbf{???}}).
-There is some evidence that gender is a determinant of AST
-({\textbf{???}}; {\textbf{???}}), although this is not a strong or
-consistent finding ({\textbf{???}}; {\textbf{???}}). Distance between
-home and school is associated with AST ({\textbf{???}}; {\textbf{???}};
-{\textbf{???}}; {\textbf{???}}) with less AST reported among children
-who have to travel farther to school. Car ownership is an important
-household-level influence on AST ({\textbf{???}}; {\textbf{???}};
-{\textbf{???}}), as is household income ({\textbf{???}}). Parental
-perceptions of the environment ({\textbf{???}}; {\textbf{???}}) and
-children's skills ({\textbf{???}}) also influence whether they allow
-their children to walk or cycle to school. Finally, many studies have
-found that the quality of the built environment ({\textbf{???}};
-{\textbf{???}}) and active travel infrastructure ({\textbf{???}})
-facilitate AST. Concerns about traffic and strangers have been reported
-by parents who drive their children to school ({\textbf{???}}). The
-consensus is that all of these factors are interrelated and that
-interventions ought to target multiple factors in order to increase
-walking and bicycling levels to school.
+On the one hand, parents have been found to express different
+understandings, nomenclature, and conceptualizations than planners of
+the factors that influence school travel (Buliung et al., 2021).
+However, it is unknown to what degree there is concurrence between STP
+materials presented to the public and the literature on school travel
+and parental perceptions, and how the complexity of the AST issue is
+presented to the public.
 
-\hypertarget{benefits-of-ast}{%
-\subsection{1.3. Benefits of AST}\label{benefits-of-ast}}
+The aim of this paper is to fill this research gap by analyzing how AST
+is framed by STP stakeholders in Ontario, Canada. We used text mining
+and topic modelling to examine how local policy documents from Ontario
+municipalities and school boards present and communicate the benefits
+and barriers of AST and the solutions for improving AST. We compared the
+findings from these documents to a selection of studies on AST and
+explored the extent to which there is concurrence between research
+findings to date and promotional materials shared with the public to
+increase AST.
 
-The desire to increase AST is warranted - there is strong evidence that
-children who walk and bicycle to school accrue physical and mental
-health benefits. Many studies and reviews have focused on the
-association between AST or CIM and physical activity (e.g.,
-{\textbf{???}}; {\textbf{???}}; {\textbf{???}}), with findings
-consistently demonstrating that children who travel by walking or
-bicycling to school are more active than their peers who do not use
-active travel. More recently, researchers have been exploring the link
-between transport and children's wellbeing ({\textbf{???}};
-{\textbf{???}}), which has relevant applications to the study of school
-travel and satisfaction (see {\textbf{???}}). CIM is also important for
-different domains of children's health and wellbeing ({\textbf{???}}).
-It offers benefits such as increasing traffic and safety skills,
-boosting spatial awareness when navigating public spaces, and providing
-more opportunity for social interaction with peers ({\textbf{???}}).
-
-\hypertarget{encouraging-adoption-of-active-school-travel}{%
-\subsection{1.4. Encouraging adoption of active school
-travel}\label{encouraging-adoption-of-active-school-travel}}
-
-To increase rates of walking and bicycling independently to school,
-Riazi et al.~({\textbf{???}}) state: ``it will be vital for
-interventions to target modifiable factors, including children's and
-parents' perceptions of their social environment.'' Parents play the
-important role of ``gatekeeper'' by either granting or restricting CIM
-licenses, meaning whether children can travel alone ({\textbf{???}}).
-For this reason, stakeholders involved in STP produce information
-targeted for both children and parents, and aim to involve the broader
-community in their efforts to increase the number of children walking
-and bicycling to school.
-
-However, the ways in which interventions like STP are framed to their
-target audience can ultimately influence how they are received and
-whether they result in behaviour change. The correlates of AST are
-important knowledge for policymakers because they identify points of
-intervention and potential benefits that ought to be communicated to the
-public encourage adoption of AST and to build support for new planning
-paradigms. What is less clear is how CIM plays into the consideration of
-policymakers when they act on the objective of increasing AST.
-
-Any goals for AST, and also CIM, ought to be clearly articulated and
-reflected in transportation plans and policies to guide initiatives.
-Presently, however, there has been no study to date that explores how
-Canadian municipalities and schools frame and discuss AST with the
-public. Content analysis is one method to analyze how particular issues
-are framed to groups of people, for instance parents or educators who
-might be inclined to support AST. It attempts to understand how
-information presented from a ``communicator'' leads the ``receiver'' to
-a desired response ({\textbf{???}}). In a recent paper ({\textbf{???}}),
-framing analysis was applied to review municipal policies addressing
-climate change in four western Canadian cities. Natural language
-processing (NLP) has also been used for a similar purpose to examine
-content in general plans from Californian cities ({\textbf{???}}). The
-way policy issues are framed is ultimately important to understand
-because it plays a role in either altering or preserving the existing
-social perceptions.
-
-\hypertarget{study-aim}{%
-\subsection{1.5. Study aim}\label{study-aim}}
-
-In 2017, the provincial government of Ontario in Canada issued funding
-to Green Communities Canada (GCC), a non-profit organization, to launch
-the \emph{Ontario Active School Travel} (OAST) program. The program
-provides funding for school and community-based initiatives and supports
-stakeholders in municipalities across the province to implement STP and
-other interventions aimed at increasing AST. As of 2021, OAST has funded
-\emph{X} projects in Ontario. GCC continues has funded projects across
-Ontario led by collaborative groups involving school boards, municipal
-or regional governments, and regional transportation consortia. The
-latter are dedicated transportation bodies that deliver efficient and
-effective transportation services, which generally focus on providing
-the school busing service to families in their associated region.
-
-The aim of this paper is to analyze how AST is framed by STP
-stakeholders in Ontario, Canada. We used text mining and topic modelling
-to examine how local policy documents from Ontario municipalities and
-school boards present and communicate the benefits and barriers of AST
-and the solutions for improving AST. We compared the findings from these
-documents to a selection of studies on AST and explored the extent to
-which research findings have trickled down to inform policy and planning
-for increasing AST.
+\hypertarget{literature-review}{%
+\section{2. Literature Review}\label{literature-review}}
 
 \hypertarget{data}{%
-\section{2. Data}\label{data}}
+\section{3. Data}\label{data}}
 
 \hypertarget{data-retrieval}{%
-\subsection{2.1. Data retrieval}\label{data-retrieval}}
+\subsection{3.1. Data retrieval}\label{data-retrieval}}
 
 \hypertarget{policy-documents}{%
-\subsubsection{2.1.1. Policy documents}\label{policy-documents}}
+\subsubsection{3.1.1. Policy documents}\label{policy-documents}}
 
@@
 study does not include any documents from these groups because they are
-not consistently participating in initiatives.
+not consistently participating in all initiatives.
 
@@
 websites. The latter were identified based on geographic area (i.e., the
-municipalities and/or transportation consortia who are in the same
+municipalities and/or transportation consortia that are in the same
 geographic area of each school board). Pages related to active or school
@@
 \hypertarget{academic-papers}{%
-\subsubsection{2.2.1. Academic papers}\label{academic-papers}}
+\subsubsection{3.2.1. Academic papers}\label{academic-papers}}
+
+\textbf{To be completed by Dr.~Paez}
 
 \hypertarget{data-cleaning}{%
-\subsection{2.2. Data cleaning}\label{data-cleaning}}
+\subsection{3.2. Data cleaning}\label{data-cleaning}}
 
@@
 \hypertarget{methods}{%
-\section{3. Methods}\label{methods}}
+\section{4. Methods}\label{methods}}
 
-\hypertarget{natural-language-processing}{%
-\subsection{3.1. Natural language
-processing}\label{natural-language-processing}}
+\hypertarget{framing-analysis}{%
+\subsection{4.1. Framing analysis}\label{framing-analysis}}
+
+Issues that pertain to public health or wellbeing are often presented to
+the public through particular frames to influence perceptions or
+behaviours. Gamson and Modigliani ({\textbf{???}}) conceptualize a frame
+as a ``central organizing idea or story line that provides meaning'' to
+a particular phenomenon. A frame can enable individuals ``to locate,
+perceive, identify, and label'' information pertaining to various
+dimensions of an issue (Goffman, 1974). Scholars in the field of
+political communications have proposed that communicators, such as the
+media or an institution, construct the narrative of a frame for policy
+positions or public issues in order to activate or restrict a particular
+response in the intended audience (Pan and Kosicki, 1993). Framing can
+be used to position existing solutions as suitable to address particular
+issues (Mah et al., 2014), which may prevent the public from being aware
+of other policy approaches that challenge the status quo to bring about
+more radical change. The way policy issues are framed is ultimately
+important to understand because it plays a role in either altering or
+preserving the existing social perceptions.
+
+Framing of issues is an important step in developing health policy. An
+obvious example over the past decade is the framing of climate change as
+a public health issue (e.g., @ depouxCommunicatingClimateChange2017;
+Maibach et al., 2010; Weathers and Kendall, 2016) to increase public
+engagement and reception of the issue. Transport planners also use
+different frames to guide the extent to which transport policies can be
+adapted to address climate change. In a recent paper ({\textbf{???}}),
+framing analysis was applied to review the representation of issues such
+as mobility and social exclusion in municipal policies from four western
+Canadian cities under the current circumstances of climate change. The
+authors found four primary frames: ``The Growing City'', ``If You Build
+It, They Will Come'', ``Better City for All'', and a ``the Resilient
+City''. Each frame presented the nature, opportunities, and challenges
+of climate change in different ways which set the stage for the types of
+mitigation and adaptation strategies that cities were proposing to
+address this issue.
+
+Given the range of factors at multiple levels of the socioecological
+model that influence school travel, it is important to understand how
+walking and bicycling to school are framed to the public. Is active
+school travel framed as a public health or environmental issue? Is it
+framed as both? Do proposed solutions to increase AST focus primarily on
+the intrapersonal and interpersonal factors, meaning that behaviour
+change must ultimately result from different decisions made by the
+individual or the household? Or is the decline in AST framed as an issue
+that must be addressed through changes in the built environment? These
+are the types of questions that we aim to answer in this paper. To our
+knowledge, this topic has not be addressed in the school travel
+literature to date.
+
+\hypertarget{topic-modelling}{%
+\subsection{4.2. Topic modelling}\label{topic-modelling}}
+
+The topic modelling analysis was conducted in R. We primarily used the
+following packages: \texttt{topicmodels} ({\textbf{???}}),
+\texttt{word2vec} ({\textbf{???}}), and \texttt{wordcloud}
+({\textbf{???}}) to examine content in the documents that were sourced
+for this project. These packages have functions for determining the
+frequency of specific words in each document, relationships (e.g., pairs
+of adjacent terms) and correlations between words, and estimating Latent
+Dirichlet allocation (LDA) models to classify documents according to the
+topics that are contained within them. We describe in the section below
+how we used these functions to produce our results.
 
 \hypertarget{reproducibility}{%
-\subsection{3.2. Reproducibility}\label{reproducibility}}
+\subsection{4.3. Reproducibility}\label{reproducibility}}
 
@@
 \hypertarget{results}{%
-\section{4. Results}\label{results}}
+\section{5. Results}\label{results}}
 
 \hypertarget{word-and-document-frequency}{%
-\subsection{4.1. Word and document
+\subsection{5.1. Word and document
 frequency}\label{word-and-document-frequency}}
@@
 \hypertarget{bigrams-and-concordances}{%
-\subsection{4.2. Bigrams and
+\subsection{5.2. Bigrams and
 concordances}\label{bigrams-and-concordances}}
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{MunicipalTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(municipal_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}
-
-\NormalTok{M_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(MunicipalTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
-\NormalTok{municipal_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(M_it_train)}
-
-\NormalTok{municipal_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(municipal_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
-\NormalTok{municipal_vocab}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Number of docs: 28 
-## 0 stopwords:  ... 
-## ngram_min = 1; ngram_max = 1 
-## Vocabulary: 
-##            term term_count doc_count
-##   1:        abc          5         1
-##   2: accessible          5         5
-##   3:     adding          5         3
-##   4:   addition          5         3
-##   5:       ages          5         4
-##  ---                                
-## 350:    cycling         78        22
-## 351:       bike         87        15
-## 352:    walking         90        25
-## 353:     travel        126        20
-## 354:     active        248        26
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{ConsortiumTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(consortium_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}
-
-\NormalTok{C_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(ConsortiumTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
-\NormalTok{consortium_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(C_it_train)}
-
-\NormalTok{consortium_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(consortium_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
-\NormalTok{consortium_vocab}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Number of docs: 9 
-## 0 stopwords:  ... 
-## ngram_min = 1; ngram_max = 1 
-## Vocabulary: 
-##           term term_count doc_count
-##   1:    around          5         4
-##   2:    assist          5         2
-##   3:    choice          5         3
-##   4: classroom          5         1
-##   5: committee          5         1
-##  ---                               
-## 124:  students         39         9
-## 125:    travel         41         8
-## 126:      walk         49         8
-## 127:   walking         55         8
-## 128:    active         67         7
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{SchoolTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(school_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}
-
-\NormalTok{S_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(SchoolTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
-\NormalTok{school_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(S_it_train)}
-
-\NormalTok{school_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(school_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
-\NormalTok{school_vocab}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Number of docs: 32 
-## 0 stopwords:  ... 
-## ngram_min = 1; ngram_max = 1 
-## Vocabulary: 
-##                term term_count doc_count
-##   1:       academic          5         4
-##   2: administration          5         4
-##   3:      alternate          5         3
-##   4:       assigned          5         2
-##   5:         attend          5         5
-##  ---                                    
-## 264:        walking         57        17
-## 265:    information         65        21
-## 266:         travel        103        11
-## 267:            bus        120        20
-## 268:         active        124        13
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{PolicyTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(policy_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}
-
-\NormalTok{P_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(PolicyTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
-\NormalTok{policy_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(P_it_train)}
-
-\NormalTok{policy_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(policy_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
-\NormalTok{policy_vocab}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Number of docs: 69 
-## 0 stopwords:  ... 
-## ngram_min = 1; ngram_max = 1 
-## Vocabulary: 
-##           term term_count doc_count
-##   1:       abc          5         1
-##   2: according          5         4
-##   3:  actively          5         4
-##   4:  addition          5         3
-##   5: addresses          5         3
-##  ---                               
-## 698:      walk        145        39
-## 699:       bus        164        35
-## 700:   walking        202        50
-## 701:    travel        270        39
-## 702:    active        439        46
-\end{verbatim}
-
 \begin{figure}
@@
 
-\caption{Most common bigrams found in all of the policy documents (i.e., school board, municipality, and transportation consortia combined.}\label{fig:policy-visual}
+\caption{Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined).}\label{fig:policy-visual}
 \end{figure}
 
-We combined all of the municipality, school board, and transportation
+We then combined all municipality, school board, and transportation
 consortia documents into one ``policy'' corpora. This enabled us to
 examine and visualize the most common bigrams found across all of the
-STP material in Ontario. Figure \ref{fig:policy-visual} shows all of the
-bigrams that occur more than 10 times in the corpora. In addition to the
-common bigrams already identified above, we also found \emph{mental
-health}, \emph{walk day}, and \emph{green communities} as common pairs
-of consecutive words. Overall, policy documents from STP stakeholders
-focus on four key areas: i) benefits or impacts of AST; ii) mechanisms
-of intervention; iii) concerns or considerations; and iv) supports for
-AST.
+STP material in Ontario that was collected for this study. Figure
+\ref{fig:policy-visual} shows all of the bigrams that occur more than 10
+times in the corpora. In addition to the common bigrams already
+identified above, we also found \emph{mental health}, \emph{walk day},
+and \emph{green communities} as common pairs of consecutive words.
+Overall, policy documents from STP stakeholders seem to focus on four
+key areas: i) benefits or impacts of AST; ii) mechanisms of
+intervention; iii) concerns or considerations; and iv) supports for AST.
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{ggraph}\NormalTok{(academic_bigram_graph, }\DataTypeTok{layout =} \StringTok{"fr"}\NormalTok{) }\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_edge_link}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{edge_alpha =}\NormalTok{ n), }\DataTypeTok{show.legend =} \OtherTok{FALSE}\NormalTok{,}
-                 \DataTypeTok{arrow =}\NormalTok{ a, }\DataTypeTok{end_cap =} \KeywordTok{circle}\NormalTok{(.}\DecValTok{07}\NormalTok{, }\StringTok{'inches'}\NormalTok{)) }\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_node_point}\NormalTok{(}\DataTypeTok{color =} \StringTok{"lightgreen"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{4}\NormalTok{) }\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_node_text}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ name), }\DataTypeTok{repel =} \OtherTok{TRUE}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{theme_void}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
+\begin{figure}
 
-\includegraphics{AST-Framing-Ontario_files/figure-latex/unnamed-chunk-10-1.pdf}
+{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/academic-visual-1}
+
+}
+
+\caption{Most common bigrams found in the academic papers.}\label{fig:academic-visual}
+\end{figure}
 
@@
 ideas that STP stakeholders are focusing on and communicating to the
-public about AST. We used the \texttt{kwic} function from the R
-\emph{quanteda} package to identify and better understand identify the
-context of these key themes.
+public about AST. We then used the \texttt{kwic} function from the R
+\emph{quanteda} package to identify and better understand the context of
+these key themes. Table \ref{tab:policy-concordance} presents examples
+of the key themes that were extracted from select policy documents to
+demonstrate how the most common bigrams are communicated to the public.
 
@@
 \hline
-\textbf{Physical health} & School Board & ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.\\
+\textbf{Air Quality} & School Board & Active transportation [...] improves air quality.\\
 \hline
-\textbf{Emissions} & Municipality & Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.\\
+\textbf{Benefit} & Municipality & Stronger bones and muscles, improved self-esteem and sense of well-being while reducing stress and risk of chronic disease all benefit those who use active transportation.\\
+\hline
+\textbf{Bus} & School Board & While taking part in a walking school bus, your child will enjoy seeing friends on the way to school.
+They will be active more often.
+This is also a great opportunity for your child to socialize with school friends in a monitored and safe way where they can practice social distancing, modelled by a leader.\\
+\hline
+\textbf{Community} & School Board & Engage community stakeholders (school boards, municipalities, police, public health professionals, parents/guardians, administrators, educators and children) to work together to identify and to solve their school travel needs.\\
+\hline
+\textbf{Emissions} & Consortia & An active school commute also reduces congestion in school zones and contributes to reducing greenhouse gas emissions – it’s a win-win for everyone!\\
+\hline
+\textbf{Health} & Municipality & Active School Travel allows school-aged children the chance to participate in moderate to intense physical activity.
+This is linked with lower body mass index and improved cardiovascular health.\\
+\hline
+\textbf{Lanes} & Municipality & We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments.\\
+\hline
+\textbf{Mental Health} & Municipality & ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.\\
+\hline
+\textbf{Physical Health} & Municipality & Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.\\
 \hline
@@
 
-\hypertarget{topic-modelling}{%
-\subsection{4.3. Topic modelling}\label{topic-modelling}}
+\hypertarget{topic-modelling-1}{%
+\subsection{5.3. Topic modelling}\label{topic-modelling-1}}
+
+\begin{verbatim}
+## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
+## "none")` instead.
+\end{verbatim}
 
 \includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-1.pdf}
+
+\begin{verbatim}
+## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
+## "none")` instead.
+\end{verbatim}
+
 \includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-2.pdf}
+
+\begin{verbatim}
+## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
+## "none")` instead.
+\end{verbatim}
+
 \includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-3.pdf}
+
+\begin{verbatim}
+## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
+## "none")` instead.
+\end{verbatim}
+
 \includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-4.pdf}
@@
 \begin{verbatim}
-## final e step document 28
+## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
+## "none")` instead.
 \end{verbatim}
 
-\begin{verbatim}
-## final e step document 32
-\end{verbatim}
-
-\begin{verbatim}
-## final e step document 9
-\end{verbatim}
-
-\begin{verbatim}
-## final e step document 69
-\end{verbatim}
+\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-5.pdf}
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{#municipal_beta <- municipal_topics %>%}
-  \CommentTok{#mutate(topic = paste0("topic", topic)) %>%}
-  \CommentTok{#pivot_wider(names_from = topic, values_from = beta) %>% }
-  \CommentTok{#filter(topic1 > .001 | topic2 > .001) %>%}
-  \CommentTok{#mutate(log_ratio = log2(topic2 / topic1))}
-\CommentTok{#municipal_beta}
-\end{Highlighting}
-\end{Shaded}
+\includegraphics{AST-Framing-Ontario_files/figure-latex/academic-terms-1.pdf}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# Identify topics by document across each corpora}
+Finally, we conducted topic modelling to examine the different topics
+found in the policy and academic corpora. We focused on the policy
+corpora, instead of individually assessing the municipal, school, and
+consortia corpus, so that we could report on the primary and secondary
+frames used across all documents put out by STP stakeholders in Ontario.
+To determine the number of discrete topics in each corpus, we used the
+ldatuning package. We then used the \texttt{LDA} function from the
+topicmodels package to estimate an LDA model for each group of
+documents. The policy corpora, which combined all documents from
+municipalities, schools, and transportation consortia, had 5 topics. The
+academic corpora had 17 topics. Figures \ref{fig: policy-terms} and
+\ref{fig: academic-terms} present the main terms that are associated
+with the topics found in each corpus.
 
-\NormalTok{municipal_documents <-}\StringTok{ }\KeywordTok{tidy}\NormalTok{(municipal_lda, }\DataTypeTok{matrix =} \StringTok{"gamma"}\NormalTok{)}
-\NormalTok{school_documents <-}\StringTok{ }\KeywordTok{tidy}\NormalTok{(school_lda, }\DataTypeTok{matrix =} \StringTok{"gamma"}\NormalTok{)}
-\NormalTok{consortia_documents <-}\StringTok{ }\KeywordTok{tidy}\NormalTok{(consortia_lda, }\DataTypeTok{matrix =} \StringTok{"gamma"}\NormalTok{)}
-\NormalTok{policy_documents <-}\StringTok{ }\KeywordTok{tidy}\NormalTok{(policy_lda, }\DataTypeTok{matrix =} \StringTok{"gamma"}\NormalTok{)}
-\CommentTok{#academic_documents <- tidy(academic_lda, matrix = "gamma")}
-\end{Highlighting}
-\end{Shaded}
+In the policy corpus, we identified the following topics: (1) resources
+for walking, (2) busing information and eligibility; (3) benefits of
+active travel; (4) bicycling and the environment; and (5) supporting
+active travel. These findings reveal that STP stakeholders are sending
+the message that walking and bicycling to school as healthy travel modes
+for students, particularly as a means to get physical activity. We also
+found that there is information shared to support parents and students
+in using active modes to school such as the availability of cycling
+lanes or route tips for walking. STP stakeholders appear to be
+communicating that AST is possible and safe as a result of improvements
+to the built environment and available resources for parents and
+children. A final focus in the policy documents is on various efforts
+that are underway to support active travel including route planning.
+
+We expected to find a higher number of topics in the academic corpus due
+to the larger number of documents in the corpora and the diversity of
+content examined in existing literature about school travel. The
+following topics were identified, which touch upon a broader range of
+factors that are associated with or related to AST than are found in the
+policy corpus: (1) \textbf{unclear} (2) AST in Ontario and Canada; (3)
+\textbf{unclear}; (4) children's independent mobility; (5) safe routes
+to school programs; (6) commuting and distance; (7) density in the built
+environment and walking routes; (8) \textbf{unclear}; (9) walking
+interventions; (10) bicycling influences; (11) interpersonal and
+household influences on trips; (12) behaviours and attitudes; (13)
+\textbf{unclear}; (14) \textbf{unclear}; (15) walking distance; (16)
+\textbf{unclear}; (17) physical activity measures or results; (18)
+bicycling attitudes; and (19) \textbf{unclear}.
+
+The policy corpus primarily frames AST as a health and environmental
+issue. Many municipal and school documents position walking, bicycling,
+or rolling to school as beneficial to individual health, including
+improvements to physical activity levels or mental health, and to the
+broader community through a reduction in traffic and vehicle emissions.
+\textgreater{} \emph{If you live in a walk zone, the best way to get to
+school is by walking or biking. This promotes physical activity, helps
+the environment and minimizes traffic around schools during busy times.}
+(City of Barrie)
+
+\begin{quote}
+\emph{Walking to school is a great way to add physical activity into
+your child's busy day.} (Region of Haldimand-Norfolk Region)
+\end{quote}
+
+\begin{quote}
+\emph{Active school travel is a great way for children to be physically
+active, which is associated with improved physical and mental health,
+while making school zones safer, by reducing traffic volumes at and
+around schools.}(Region of Leeds, Grenville and Lanark)
+\end{quote}
+
+\begin{quote}
+\emph{The WCDSB supports active transportation as the preferred method
+of transportation to school because it is a healthy choice that has
+proven links to greater student achievement.} (Waterloo Catholic
+District School Board)
+\end{quote}
+
+We found that some of these documents make direct references to topics
+found in research on school travel and the built environment. For
+example, some policy documents identify programs that have been
+researched in the literature and found to be effective, such as walking
+school buses, or explain how an increase in AST will reduce parent
+safety concerns. \textgreater{} \_ For their health, safety, environment
+and community: Kids learn healthy habits and concentrate better in
+class; One less car (yours) reduces traffic and parking problems in
+school zones; Teach your kids about traffic safety; Start a walking
+school bus; your kids make friends in every grade, and that can prevent
+bullying.\_ (City of Guelph)
+
+\begin{quote}
+\emph{There are lots of benefits in the classroom for children that walk
+or cycle to school on a regular basis. Some of these benefits include
+improved concentration and better coping with stress. Being outside
+helps to prevent feelings of isolation and increases their social
+interactions. Walking and biking to school can also save you money and
+lead to fewer cars on the road.} (City of Ottawa)
+\end{quote}
+
+The secondary frame for AST in municipal documents is the opportunity or
+prospect of behaviour change. Some cities and schools explain how
+children and parents can leave the car at home and make the journey to
+school on foot or by bike by describing efforts to make AST safer. This
+frame enables the public to evaluate their own travel decisions and to
+access resources (e.g., walking skills checklist) that will help them
+make AST a first choice. Some documents communicate what is being done
+by the municipalities or schools, like school travel planning, while
+others emphasize the active role of the parent in creating opportunities
+for AST in their household or neighbourhood. \textgreater{} \emph{School
+Travel Planning is a community-based approach that aims to increase the
+number of students and adults choosing active and sustainable travel to
+get to and from school. This approach addresses concerns about safety,
+physical activity, and the environment.} (City of Hamilton)
+
+\begin{quote}
+\_A way to make sure your child is safe while walking to school is with
+a `walking school bus.' Here are some tips for a walking school bus:
+Invite families who live nearby to walk; Pick a route and take a test
+walk; Take side streets and paths that are less busy with traffic;
+Decide how often the group will walk together; Talk with your boss to
+adjust your day; Have fun! (City of Ottawa)
+\end{quote}
+
+\begin{quote}
+Help your students get started on the right foot -encourage them to walk
+or bike to school when possible. Even leaving the car a block or two and
+walking the rest of the way helps. It's good for the environment and
+your health, and teaches your child independence and community
+awareness.\_ (Halton District School Board)
+\end{quote}
+
+\begin{quote}
+\emph{Today, as more and more of our neighbourhoods are being
+retrofitted with new sidewalks and bike lanes, pedestrian crossovers,
+street lights, reduced speed limits and/or crossing guards, the walk or
+bike ride to and from school has never been easier, safer or healthier.}
+(Hamilton-Wentworth District Catholic School Board)
+\end{quote}
+
+\begin{quote}
+\emph{Want to boost your child's mental and physical health? Ottawa
+Public Health, City of Ottawa, and OSTA have produced a tipsheet for
+parents about ``active transportation'' to school -- fitting walking and
+wheeling into your daily routine.} (Ottawa-Carleton District School
+Board)
+\end{quote}
+
+Finally, many municipalities, schools, and consortia make no mention of
+active school travel on their main website pages for active
+transportation. Nonetheless, some municipalities explain how changes to
+the built environment are being implemented to facilitate active travel.
+Schools or consortia that do not refer to AST simply provide information
+about the busing service available to families in the region. Inclement
+weather and impacts to busing is a common topic addressed in those
+documents. \textgreater{} \emph{We are continuing to build on the
+cycling and pedestrian network by adding more bike lanes, building
+multi-use paths and encouraging developments to provide better
+pedestrian/cycling environments.} (City of Brantford)
+
+\begin{quote}
+\emph{The City of Burlington ensures all cyclists, pedestrians and
+drivers have access to safe and accessible transportation services and
+programs} (City of Burlington)
+\end{quote}
 
 \hypertarget{discussion}{%
-\section{5. Discussion}\label{discussion}}
+\section{6. Discussion}\label{discussion}}
+
+\hypertarget{framing-in-stp-documents}{%
+\subsection{6.1. Framing in STP
+documents}\label{framing-in-stp-documents}}
+
+We analyzed how AST is framed in documents available to the public on
+the websites of STP stakeholders in Ontario. We found that AST is
+primarily framed as beneficial to the health and wellbeing of children
+and to environmental sustainability. This was confirmed by the most
+common bigrams identified in the policy corpora, as well as the topics
+identified by the LDA model. Many studies and reviews have focused on
+the association between AST and physical activity (e.g., Faulkner et
+al., 2009; Mitra et al., 2017; Schoeppe et al., 2015), with findings
+consistently demonstrating that children who travel by walking or
+bicycling to school are more active than their peers who do not use
+active travel. More recently, researchers have been exploring the link
+between transport and children's wellbeing (Babb et al., 2017), which
+has relevant applications to the study of school travel and satisfaction
+(see van den Berg et al., 2020). We concluded that STP promotional
+materials have high concurrence with this topic in the research on
+school travel and the built environment. Framing AST as a health issue
+is certainly warranted - there is strong evidence that children who walk
+and bicycle to school accrue physical and mental health benefits.
+Furthermore, concerns about traffic and strangers have been reported by
+parents who drive their children to school (Mammen et al., 2012).
+Parents often have concerns about traffic volume, speed, and congestion
+around schools (Ling et al., 2021; Rothman et al., 2017), therefore the
+framing of AST as an environmental issue is in alignment with evidence
+from existing studies.
+
+The secondary frame of AST is that it is a behaviour that can and should
+be adopted by children and parents given the environmental and program
+supports available in the community. STP stakeholders emphasize that
+parents can access resources or trips to support their children in
+commuting by active modes to school. They also share information about
+interventions such as school travel plans and bicycle lanes to frame AST
+as safe and practical. However, STP materials neglect to address many
+intrapersonal and household factors that influence or predict AST. At
+the individual level, older child age is often associated with AST
+({\textbf{???}}; Mammen et al., 2012; Wilson et al., 2018), but AST is
+not framed as an activity for children based on age. STP stakeholders
+may wish to emphasize to parents that older children have greater
+traffic safety and cognitive abilities to navigate their own routes to
+school. There is also some evidence that gender is a determinant of AST
+({\textbf{???}}; Babb et al., 2017), although this is not a strong or
+consistent finding ({\textbf{???}}; Schoeppe et al., 2015). STP
+materials do not discuss this determinant of AST but it may be helpful
+to identify strategies or messages that alleviate specific concerns that
+relate to a child's gender.
+
+Furthermore, distance between home and school is the factor most
+associated with AST in existing research ({\textbf{???}}; Ikeda et al.,
+2018; Mammen et al., 2012; Pont et al., 2009) with less AST reported
+among children who have to travel farther to school. This topic is not
+addressed substantively in the policy corpus, perhaps due to the
+inability of STP stakeholders to directly intervene in residential
+location. Parental perceptions of the environment (De Meester et al.,
+2014; Panter et al., 2010) and children's skills (Ghekiere et al., 2017)
+also influence whether they allow their children to walk or cycle to
+school. STP documents do a sufficiently good job at communicated how an
+increase in AST could improve traffic safety in school zones and how new
+infrastructure improvements give children the ability to safely travel.
+This messaging has high concurrence with studies that have found that
+the quality of the built environment (Ikeda et al., 2018; Kim and Lee,
+2020) and active travel infrastructure (Pont et al., 2009) facilitate
+AST.
+
+To increase rates of walking and bicycling independently to school,
+Riazi et al.~(2019) state: ``it will be vital for interventions to
+target modifiable factors, including children's and parents' perceptions
+of their social environment.'' We argue that STP messaging should also
+target multiple modifiable factors, in addition to the health and
+environmental benefits. Parents play the important role of
+``gatekeeper'' by either granting or restricting their child's mobility
+(Sharmin and Kamruzzaman, 2017). For this reason, stakeholders involved
+in STP should produce more information that specifically responds to
+parents' perceived barriers and challenges. For example, STP materials
+could explain how known concerns in a particular municipality or school
+area have been addressed through local solutions.
 
 \hypertarget{implications-for-school-travel-planning}{%
-\subsection{5.1. Implications for School Travel
-Planning}\label{implications-for-school-travel-planning}}
+\subsection{6.2. Implications for school travel
+planning}\label{implications-for-school-travel-planning}}
+
+Many municipalities, schools, and transportation consortia use similar
+content in their public documents about AST. It would be worthwhile for
+STP stakeholders to adapt generic content so that it is more specific to
+factors associated with AST or parental perceptions about barriers to
+AST in the local context. Rothman et al.~(2018) note that local
+solutions to address specific school challenges are worthwhile, and we
+extend this recommendation to include local context in STP messaging
+about AST.
 
 \hypertarget{limitations}{%
-\subsection{5.2. Limitations}\label{limitations}}
+\subsection{6.3. Limitations}\label{limitations}}
 
 \hypertarget{conclusion}{%
-\section{6.1. Conclusion}\label{conclusion}}
+\section{7. Conclusion}\label{conclusion}}
 
 \hypertarget{future-research}{%
-\subsection{6.1. Future research}\label{future-research}}
+\subsection{7.1. Future research}\label{future-research}}
+
+Future studies may investigate how parents and policymakers outside the
+field of public health respond to the ways in which AST is framed in STP
+documents. It would be helpful to know which frames would most encourage
+behaviour change or increase political support for interventions that
+address barriers to AST. This type of information could ensure that
+educational strategies and promotional materials increase buy-in for
+their target audience.
 
@@
 \hypertarget{references}{%
-\section{References}\label{references}}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-babbChildrenActiveTravel2017}{}%
+Babb, C., Olaru, D., Curtis, C., Robertson, D., 2017. Children's active
+travel, local activity spaces and wellbeing: A case study in Perth, WA.
+Travel Behaviour and Society 9, 81--94.
+doi:\href{https://doi.org/10.1016/j.tbs.2017.06.002}{10.1016/j.tbs.2017.06.002}
+
+\leavevmode\hypertarget{ref-buliungLivingJourneySchool2021}{}%
+Buliung, R., Hess, P., Flowers, L., Moola, F.J., Faulkner, G., 2021.
+Living the journey to school: Conceptual asymmetry between parents and
+planners on the journey to school. Social Science \& Medicine 284,
+114237.
+doi:\href{https://doi.org/10.1016/j.socscimed.2021.114237}{10.1016/j.socscimed.2021.114237}
+
+\leavevmode\hypertarget{ref-buttazzoniPromotingActiveSchool2019}{}%
+Buttazzoni, A.N., Clark, A.F., Seabrook, J.A., Gilliland, J.A., 2019.
+Promoting active school travel in elementary schools: A regional case
+study of the school travel planning intervention. Journal of Transport
+\& Health 12, 206--219.
+doi:\href{https://doi.org/10.1016/j.jth.2019.01.007}{10.1016/j.jth.2019.01.007}
+
+\leavevmode\hypertarget{ref-demeesterParentalPerceivedNeighborhood2014}{}%
+De Meester, F., Van Dyck, D., De Bourdeaudhuij, I., Cardon, G., 2014.
+Parental perceived neighborhood attributes: Associations with active
+transport and physical activity among 10-12 year old children and the
+mediating role of independent mobility. BMC public health 14, 631.
+doi:\href{https://doi.org/10.1186/1471-2458-14-631}{10.1186/1471-2458-14-631}
+
+\leavevmode\hypertarget{ref-faulknerActiveSchoolTransport2009}{}%
+Faulkner, G.E.J., Buliung, R.N., Flora, P.K., Fusco, C., 2009. Active
+school transport, physical activity levels and body weight of children
+and youth: A systematic review. Preventive Medicine 48, 3--8.
+doi:\href{https://doi.org/10.1016/j.ypmed.2008.10.017}{10.1016/j.ypmed.2008.10.017}
+
+\leavevmode\hypertarget{ref-ghekiereInsightsChildrenIndependent2017}{}%
+Ghekiere, A., Deforche, B., Carver, A., Mertens, L., de Geus, B.,
+Clarys, P., Cardon, G., De Bourdeaudhuij, I., Van Cauwenberg, J., 2017.
+Insights into children's independent mobility for transportation
+cyclingWhich socio-ecological factors matter? Journal of Science and
+Medicine in Sport 20, 267--272.
+doi:\href{https://doi.org/10.1016/j.jsams.2016.08.002}{10.1016/j.jsams.2016.08.002}
+
+\leavevmode\hypertarget{ref-goffmanFrameAnalysisEssay1974}{}%
+Goffman, E., 1974. Frame analysis: An essay on the organization of
+experience, Frame analysis: An essay on the organization of experience.
+Harvard University Press, Cambridge, MA, US.
+
+\leavevmode\hypertarget{ref-ikedaAssociationsChildrenActive2018}{}%
+Ikeda, E., Hinckson, E., Witten, K., Smith, M., 2018. Associations of
+children's active school travel with perceptions of the physical
+environment and characteristics of the social environment: A systematic
+review. Health \& Place 54, 118--131.
+doi:\href{https://doi.org/10.1016/j.healthplace.2018.09.009}{10.1016/j.healthplace.2018.09.009}
+
+\leavevmode\hypertarget{ref-kimBuiltNaturalEnvironmental2020}{}%
+Kim, Y.-J., Lee, C., 2020. Built and Natural Environmental Correlates of
+Parental Safety Concerns for Children's Active Travel to School.
+International Journal of Environmental Research and Public Health 17.
+doi:\href{https://doi.org/10.3390/ijerph17020517}{10.3390/ijerph17020517}
+
+\leavevmode\hypertarget{ref-lingRelationshipMotorVehicle2021}{}%
+Ling, R., Rothman, L., Hagel, B., Macarthur, C., Winters, M., Churchill,
+T., HubkaRao, T., Macpherson, A., Cloutier, M.-S., Howard, A., 2021. The
+relationship between motor vehicle speed and active school
+transportation at elementary schools in Calgary and Toronto, Canada.
+Journal of Transport \& Health 21, 101034.
+doi:\href{https://doi.org/10.1016/j.jth.2021.101034}{10.1016/j.jth.2021.101034}
+
+\leavevmode\hypertarget{ref-mahFramecriticalPolicyAnalysis2014}{}%
+Mah, C.L., Hamill, C., Rondeau, K., McIntyre, L., 2014. A frame-critical
+policy analysis of Canada's response to the World Food Summit 19982008.
+Archives of Public Health 72, 41.
+doi:\href{https://doi.org/10.1186/2049-3258-72-41}{10.1186/2049-3258-72-41}
+
+\leavevmode\hypertarget{ref-maibachReframingClimateChange2010}{}%
+Maibach, E.W., Nisbet, M., Baldwin, P., Akerlof, K., Diao, G., 2010.
+Reframing climate change as a public health issue: An exploratory study
+of public reactions. BMC Public Health 10, 1--11.
+doi:\href{https://doi.org/10.1186/1471-2458-10-299}{10.1186/1471-2458-10-299}
+
+\leavevmode\hypertarget{ref-mammenUnderstandingDriveEscort2012}{}%
+Mammen, G., Faulkner, G., Buliung, R., Lay, J., 2012. Understanding the
+drive to escort: A cross-sectional analysis examining parental attitudes
+towards children's school travel and independent mobility. BMC public
+health 12, 862.
+doi:\href{https://doi.org/10.1186/1471-2458-12-862}{10.1186/1471-2458-12-862}
+
+\leavevmode\hypertarget{ref-mammenActiveSchoolTravel2014}{}%
+Mammen, G., Stone, M.R., Faulkner, G., Ramanathan, S., Buliung, R.,
+O'Brien, C., Kennedy, J., 2014. Active school travel: An evaluation of
+the Canadian school travel planning intervention. Preventive Medicine
+60, 55--59.
+doi:\href{https://doi.org/10.1016/j.ypmed.2013.12.008}{10.1016/j.ypmed.2013.12.008}
+
+\leavevmode\hypertarget{ref-mitraChildrenActivitytransportationLifestyles2017}{}%
+Mitra, R., Cantello, I.D., Buliung, R.N., Faulkner, G.E.J., 2017.
+Children's activity-transportation lifestyles, physical activity levels
+and social-ecological correlates in Toronto, Canada. Journal of
+Transport \& Health 6, 289--298.
+doi:\href{https://doi.org/10.1016/j.jth.2017.03.010}{10.1016/j.jth.2017.03.010}
+
+\leavevmode\hypertarget{ref-panFramingAnalysisApproach1993}{}%
+Pan, Z., Kosicki, G.M., 1993. Framing analysis: An approach to news
+discourse. Political Communication 10, 55--75.
+doi:\href{https://doi.org/10.1080/10584609.1993.9962963}{10.1080/10584609.1993.9962963}
+
+\leavevmode\hypertarget{ref-panterAttitudesSocialSupport2010}{}%
+Panter, J.R., Jones, A.P., Sluijs, E.M.F. van, Griffin, S.J., 2010.
+Attitudes, social support and environmental perceptions as predictors of
+active commuting behaviour in school children. Journal of Epidemiology
+\& Community Health 64, 41--48.
+doi:\href{https://doi.org/10.1136/jech.2009.086918}{10.1136/jech.2009.086918}
+
+\leavevmode\hypertarget{ref-pontEnvironmentalCorrelatesChildren2009}{}%
+Pont, K., Ziviani, J., Wadley, D., Bennett, S., Abbott, R., 2009.
+Environmental correlates of children's active transportation: A
+systematic literature review. Health \& Place 15, 849--862.
+doi:\href{https://doi.org/10.1016/j.healthplace.2009.02.002}{10.1016/j.healthplace.2009.02.002}
+
+\leavevmode\hypertarget{ref-riaziCorrelatesChildrenIndependent2019}{}%
+Riazi, N.A., Blanchette, S., Trudeau, F., Larouche, R., Tremblay, M.S.,
+Faulkner, G., 2019. Correlates of Children's Independent Mobility in
+Canada: A Multi-Site Study. International Journal of Environmental
+Research and Public Health 16.
+doi:\href{https://doi.org/10.3390/ijerph16162862}{10.3390/ijerph16162862}
+
+\leavevmode\hypertarget{ref-rothmanSchoolEnvironmentStudent2017}{}%
+Rothman, L., Buliung, R., Howard, A., Macarthur, C., Macpherson, A.,
+2017. The school environment and student car drop-off at elementary
+schools. Travel Behaviour and Society 9, 50--57.
+doi:\href{https://doi.org/10.1016/j.tbs.2017.03.001}{10.1016/j.tbs.2017.03.001}
+
+\leavevmode\hypertarget{ref-rothmanDeclineActiveSchool2018a}{}%
+Rothman, L., Macpherson, A.K., Ross, T., Buliung, R.N., 2018. The
+decline in active school transportation (AST): A systematic review of
+the factors related to AST and changes in school transport over time in
+North America. Preventive Medicine 111, 314--322.
+doi:\href{https://doi.org/10.1016/j.ypmed.2017.11.018}{10.1016/j.ypmed.2017.11.018}
+
+\leavevmode\hypertarget{ref-schoeppeAssociationsChildrenActive2015}{}%
+Schoeppe, S., Duncan, M.J., Badland, H.M., Oliver, M., Browne, M., 2015.
+Associations between children׳s active travel and levels of physical
+activity and sedentary behavior. Journal of Transport \& Health 2,
+336--342.
+doi:\href{https://doi.org/10.1016/j.jth.2015.05.001}{10.1016/j.jth.2015.05.001}
+
+\leavevmode\hypertarget{ref-sharminAssociationBuiltEnvironment2017}{}%
+Sharmin, S., Kamruzzaman, M., 2017. Association between the built
+environment and children's independent mobility: A meta-analytic review.
+Journal of Transport Geography 61, 104--117.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2017.04.004}{10.1016/j.jtrangeo.2017.04.004}
+
+\leavevmode\hypertarget{ref-vandenbergFactorsAffectingParental2020}{}%
+van den Berg, P., Waygood, E.O.D., van de Craats, I., Kemperman, A.,
+2020. Factors affecting parental safety perception, satisfaction with
+school travel and mood in primary school children in the Netherlands.
+Journal of Transport \& Health 16, 100837.
+doi:\href{https://doi.org/10.1016/j.jth.2020.100837}{10.1016/j.jth.2020.100837}
+
+\leavevmode\hypertarget{ref-weathersDevelopmentsFramingClimate2016}{}%
+Weathers, M.R., Kendall, B.E., 2016. Developments in the Framing of
+Climate Change as a Public Health Issue in US Newspapers. Environmental
+Communication 10, 593--611.
+doi:\href{https://doi.org/10.1080/17524032.2015.1050436}{10.1080/17524032.2015.1050436}
+
+\leavevmode\hypertarget{ref-wilsonUnderstandingChildParent2018}{}%
+Wilson, K., Clark, A.F., Gilliland, J.A., 2018. Understanding child and
+parent perceptions of barriers influencing children's active school
+travel. BMC public health 18, 1053.
+doi:\href{https://doi.org/10.1186/s12889-018-5874-y}{10.1186/s12889-018-5874-y}
 

### 2021-11-26 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Fixed an error in the references that prevented the Rmd file AST-framing-Ontario from knitting

@@
 
-```{r city-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the municipal or regional government documents."}
+```{r city-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:city-visual}Most common bigrams found in the municipal or regional government documents."}
 ggraph(municipal_bigram_graph, layout = "fr") +
@@
 
-```{r consortia-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the transportation consortia documents."}
+```{r consortia-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:consortia-visual}Most common bigrams found in the transportation consortia documents."}
 ggraph(consortium_bigram_graph, layout = "fr") +
@@
 
-```{r school-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the school board documents."}
+```{r school-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:school-visual}Most common bigrams found in the school board documents."}
 ggraph(school_bigram_graph, layout = "fr") +
@@
 
-```{r policy-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined)."}
+```{r policy-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:policy-visual}Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined)."}
 ggraph(policy_bigram_graph, layout = "fr") +
@@
 
-```{r, academic-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the academic papers."}
+```{r, academic-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:academic-visual}Most common bigrams found in the academic papers."}
 ggraph(academic_bigram_graph, layout = "fr") +
@@
 
-kbl(text_tbl) %>%
+kbl(text_tbl,
+    booktabs = TRUE,
+    caption = "\\label{tab:policy-concordance}CAPTION THIS TABLE") %>%
   kable_paper(full_width = F) %>%
+  kable_styling(latex_options = c("striped")) %>%
   column_spec(1, bold = T) %>%
-  column_spec(3, width = "30em")
+  column_spec(3, width = "20em")
 ```
@@
 
-```{r corpus-lda-model, include=FALSE}
+```{r corpus-lda-model, cache = TRUE, include=FALSE}
 municipal_lda <- LDA(municipal_dtm, k = 4, method = "Gibbs", control = NULL, model = NULL)
@@
 
-```{r policy-terms, echo=FALSE}
+```{r policy-terms, echo=FALSE, out.width="1\\linewidth", fig.cap="\\label{fig:policy-terms}CAPTION THIS FIGURE"}
 policy_top_terms <- policy_topics %>%
@@
 
-```{r academic-terms, echo=FALSE, cache=TRUE}
+```{r academic-terms, echo=FALSE, out.width="1\\linewidth", cache=TRUE, fig.cap="\\label{fig:academic-terms}CAPTION THIS FIGURE"}
 
@@
 We experimented with the model by adjusting the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap.
-Figures \ref{fig: policy-terms} and \ref{fig: academic-terms} present the main terms that are associated with the topics found in each corpus.
+Figures \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main terms that are associated with the topics found in each corpus.
 

### 2021-11-26 AST-Framing-Ontario/AST-Framing-Ontario.tex
Fixed an error in the references that prevented the Rmd file AST-framing-Ontario from knitting

@@
 
-  \journal{Journal of Transport \& Health} % Sets Journal name
+  \journal{Social Science \& Medicine} % Sets Journal name
 
@@
 \usepackage{graphicx}
+\usepackage{booktabs} % book-quality tables
 %%%%%%%%%%%%%%%% end my additions to header
@@
             pdfauthor={},
-            pdftitle={How do school travel planning stakeholders frame active school travel in Ontario, Canada?},
+            pdftitle={The framing of active school travel in Ontario, Canada as a health and built environment issue},
             colorlinks=false,
@@
 % Pandoc citation processing
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+% for Pandoc 2.8 to 2.10.1
+\newenvironment{cslreferences}%
+  {}%
+  {\par}
+% For Pandoc 2.11+
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 
-  \title{How do school travel planning stakeholders frame active school travel in
-Ontario, Canada?}
+  \title{The framing of active school travel in Ontario, Canada as a
+health and built environment issue}
     \author[Some Department]{Author 1\corref{1}}
@@
    \ead{author6@example.com} 
-      \address[Some Department]{Department, Street, City, Province, Postal Code}
-    \address[Another University]{Department, Street, City, Province, Postal Code}
+      \address[Some Department]{Department, Street, City, Province,
+Postal Code}
+    \address[Another University]{Department, Street, City, Province,
+Postal Code}
     \address[Some Institute]{Street, City, Province, Postal Code}
-    \address[Some University]{Department, Street, City, Province, Postal Code}
+    \address[Some University]{Department, Street, City, Province, Postal
+Code}
       \cortext[1]{Corresponding Author}
@@
 
-Walking and bicycling to school, commonly known as active school travel
-(AST), has been declining in Canada and North America for decades
-({\textbf{???}}), with levels much lower than other developed countries
-like The Netherlands ({\textbf{???}}) and Japan ({\textbf{???}}). In
-response to this trend, school travel planning has become a popular
-intervention across Canada that has resulted in mixed success with some
-schools reporting an increase in AST (e.g., {\textbf{???}}; Mammen et
-al., 2014), while others did not observe a change in behaviour
-(Buttazzoni et al., 2019) or needed more time and resources to be
-effective ({\textbf{???}}).
-
-School travel planning (STP) is a ``school-specific'' intervention led
-by a facilitator that brings together a committee of stakeholders from
-diverse sectors including education, planning, transportation, and
-public health to develop action plans ({\textbf{???}}). This five-step
-process involves identifying barriers to AST based on the local context
-and implementing approaches or activities that alleviate concerns and
-encourage AST ({\textbf{???}}). STP facilitators and committee members
-generally intervene at the school through a range of activities such as
-educational strategies, in-person events or programs, improvements to
-the school site, and enforcement (Mammen et al., 2014).
-
-How STP is framed to a target audience may influence how this
-intervention is received and whether it encourages the audience to
-support it or participate. In particular, STP stakeholders make choices
-about the points of intervention and potential benefits that ought to be
-communicated to the public to facilitate adoption of AST. Educational
-strategies, which account for approximately one quarter of STP
-strategies implemented at Canadian schools (Mammen et al., 2014), need
-to effectively engage multiple audiences -- parents, students,
-politicians -- on the issue, challenges, and benefits of AST.
-Promotional materials, therefore, should reflect current knowledge from
-research about school travel and the built environment, as well as local
-content specific to factors that influence travel decisions for parents,
-in order to effectively engage the public in advocating for improving
-AST or to expose parents and the community to essential information that
-may prompt behaviour change.
-
-On the one hand, parents have been found to express different
-understandings, nomenclature, and conceptualizations than planners of
-the factors that influence school travel (Buliung et al., 2021).
-However, it is unknown to what degree there is concurrence between STP
-materials presented to the public and the literature on school travel
-and parental perceptions, and how the complexity of the AST issue is
-presented to the public.
-
-The aim of this paper is to fill this research gap by analyzing how AST
-is framed by STP stakeholders in Ontario, Canada. We used text mining
-and topic modelling to examine how local policy documents from Ontario
-municipalities and school boards present and communicate the benefits
-and barriers of AST and the solutions for improving AST. We compared the
-findings from these documents to a selection of studies on AST and
-explored the extent to which there is concurrence between research
-findings to date and promotional materials shared with the public to
-increase AST.
+Rates of walking and bicycling to school, commonly known as active
+school travel (AST), have been declining in Canada and the United States
+for decades (\textbf{rothmanDeclineActiveSchool2018?}), with levels much
+lower than other developed countries like The Netherlands
+(\textbf{vangoeverdenSchoolTravelBehaviour2013?}), Denmark
+(\textbf{jensenHowObtainHealthy2008?}), and Japan
+(\textbf{waygoodChapterSixteenJapan2020?}). However, the appetite for
+AST may be high in many Canadian communities. For instance, 40\% of
+children in a study conducted in Toronto, Ontario who are driven to
+school would like to travel by bicycle instead
+(\textbf{laroucheRatherBikeSchool2016a?}). But the study reported that
+less than 3\% actually do, despite the vast majority having access to a
+bicycle and living within a short and bikeable distance to school.
+Another study based in London, Ontario reported similar findings with
+respect to children's preference for active travel
+(\textbf{larsenRouteBasedAnalysisCapture2012?}). From a public health
+perspective, this represents a huge opportunity to improve health and
+wellbeing if more children could use active modes to school.
+
+In response to this trend, the Government of Ontario, in Canada, created
+a fund in 2017 to support communities across the province in developing
+AST initiatives. Green Communities Canada runs the program, called
+\emph{Ontario Active School Travel}, and determines the projects that
+will be funded with their support (\textbf{GreenCommunities2016?}). As
+of December 2021, OAST has funded and provided resources for over 20
+projects across Ontario. Many communities implemented school travel
+planning (STP), along with encouragement activities like walking school
+buses or developed resources for schools and parents, among other
+actions (see \textbf{GreenCommunitiesProjects?}). In this context, STP
+is a popular ``school-specific'' intervention led by a facilitator that
+brings together a committee of stakeholders from diverse sectors
+including education, planning, transportation, and public health to
+develop action plans (\textbf{buliungSchoolTravelPlanning2011?};
+\textbf{mammenSchoolTravelPlanning2014?}). The five-step process
+involves identifying barriers to AST based on the local context and
+implementing approaches or activities following the 5 E's that alleviate
+concerns about AST and make AST safer and more convenient
+(\textbf{buliungSchoolTravelPlanning2011?};
+\textbf{langUnderstandingModalChoice2011?}).
+
+How AST is framed by STP stakeholders to a target audience, like parents
+or the general public, may raise awareness about the issue and influence
+how walking and bicycling to school are perceived. Gamson and Modigliani
+(\textbf{gamsonChangingCulture1987?}) define a frame as a ``central
+organizing idea or story line that provides meaning'' to a particular
+phenomenon. A frame can enable individuals ``to locate, perceive,
+identify, and label'' information pertaining to various dimensions of an
+issue (Goffman, 1974). Therefore, stakeholder groups involved in STP
+efforts can play a role in shaping public perception about AST in such a
+way that it attracts greater attention and becomes a ``problem'' that
+needs to be addressed through behaviour change or by new policies. We
+also contend that the ways in which the AST issue is framed can affect
+the policy process, as outlined in Kingdon's
+(\textbf{kingdonAgendasAlternativesPublic1984?}) Multiple Streams
+Framework (MSF), through all three streams (i.e., problem, policy, and
+politics). This framing can ultimately impact financial contributions
+and potential solutions to address the decline of AST in Canada.
+
+After significant investment of human and financial resources to boost
+rates of AST in Ontario over the past few years, we ask the following
+questions: How is AST framed? What benefits of AST are communicated to
+the public? What solutions are proposed to increase rates of AST? Do
+proposed solutions focus primarily on the intrapersonal and
+interpersonal factors, meaning that behaviour change must ultimately
+result from the individual or household making different travel
+decisions? Or is AST framed as an issue that must be addressed through
+changes in the built environment or at the policy level?
+
+In this paper, we use text mining and topic modelling to examine how
+three STP stakeholder groups in Ontario (i.e., municipalities, school
+boards, and transportation consortia) frame the issue of AST. We
+assembled a corpus of texts from webpages that can be considered an
+important source of information for the general public or parents who
+are interested in AST. We examine word frequency, bigrams, and
+concordances in these selected documents, and also identify key topics
+presented by each stakeholder group. We then compare the findings from
+these documents to a selection of studies on AST and explore the extent
+to which there is concordance between the literature on AST and
+materials shared with the public.
 
@@
 
+\hypertarget{benefits-of-active-school-travel}{%
+\subsection{2.1. Benefits of active school
+travel}\label{benefits-of-active-school-travel}}
+
+The benefits of AST are valuable information to communicate to the
+public in order to convey the importance of this issue. The desire to
+increase AST in Canada is certainly warranted - there is compelling
+evidence that children who actively commute to school earn physical and
+mental health benefits. Faulkner et al. (2009) concluded from their
+systematic review that children who travel on foot or by bicycle to
+school generally have higher levels of physical activity than their
+peers who are driven to school. However, Schoeppe et al. (2015) reported
+no association between AST and physical activity. This relationship
+could be dose-dependent, meaning that children would have to travel
+longer distances to accumulate physical activity. A walking distance of
+1000-1600 metres to school has been found to contribute to overall
+levels of physical activity for boys
+(\textbf{faulknerSchoolTravelChildren2013?}). The daily routine of
+travelling to school can be a good opportunity for children to regularly
+build physical activity into their schedule
+(\textbf{mitraIndependentMobilityMode2013?}). Research has also shown
+that using active modes to school contributes to improvements in
+cardiovascular fitness
+(\textbf{borrestadExperiencesRandomisedControlled2012?}).
+
+More recently, there has been literature exploring the link between
+transport and children's wellbeing
+(\textbf{waygoodTransportChildrenWellbeing2020?}), with relevant
+applications to the study of travel satisfaction (van den Berg et al.,
+2020; \textbf{westmanChildrenTravelSchool2017?}). Being driven to school
+reduces community interactions for children which may impact their
+social wellbeing (\textbf{waygoodChildrenTravelIncidental2015?}),
+whereas walking and bicycling give children opportunities to socialize
+with friends or siblings
+(\textbf{michailChildrenExperiencesTheir2021?}). This is something that
+children highly value about travel
+(\textbf{zwertsHowChildrenView2010a?}) and indicates that social
+connections through travel are important for their wellbeing. AST also
+provides opportunities for children to engage with the natural
+environment (\textbf{fuscoUnderstandingChildrenPerceptions2012?};
+\textbf{romeroChildrenExperiencesEnjoyment2015?}) which can improve
+their mental or emotional wellbeing.
+
+\hypertarget{factors-that-influence-active-school-travel-and-mode-choice}{%
+\subsection{2.2. Factors that influence active school travel and mode
+choice}\label{factors-that-influence-active-school-travel-and-mode-choice}}
+
+Factors that influence AST have been presented and organized using a
+socio-ecological model (SEM)
+(\textbf{mitraIndependentMobilityMode2013?}) or systems model
+(\textbf{badlandDevelopmentSystemsModel2016?}) whereby children's travel
+behaviour is understood within the context of their household, social,
+neighbourhood, and policy environments. Individual characteristics of
+the child are also determinants. The SEM comes from the field of public
+health and is a useful framework for understanding complex health
+behaviours, including travel habits such as walking or bicycling to
+school, because it identifies multiple determinants that need to be
+addressed by interventions to facilitate behaviour change. The consensus
+in the literature is that various factors are interrelated and that
+interventions should target multiple levels in order to increase levels
+of healthy and physically active modes of travel to school
+(\textbf{mitraIndependentMobilityMode2013?}). Rather than describing an
+extensive list of factors that influence AST and mode choice in Canada,
+which has been covered elsewhere (e.g., Mammen et al., 2012; Wilson et
+al., 2018; \textbf{mitraIndependentMobilityMode2013?};
+\textbf{rothmanDeclineActiveSchool2018?}), we briefly discuss a few
+potentially modifiable determinants that may be targeted for change
+through STP.
+
+At the individual level, older child age is often associated with AST
+(Mammen et al., 2012; Wilson et al., 2018;
+\textbf{starkExploringIndependentActive2018?}) as parents typically
+escort younger children. There is some evidence that gender is a
+determinant of AST (\textbf{larsenInfluencePhysicalEnvironment2009?}),
+with boys being more likely to travel using active modes than girls,
+although this is not a strong or consistent finding (Schoeppe et al.,
+2015; \textbf{rothmanDeclineActiveSchool2018?}). Children's mode choice
+to school is strongly influenced by their parents' travel behaviours and
+the complexity of their household's travel needs (Buliung et al., 2021),
+which indicates that shifting parental perceptions and habits is
+important. Convenience and inclement weather have been cited by parents
+as barriers to AST (\textbf{buliungSchoolTravelPlanning2011?}). Parental
+perceptions of the built or school environment (De Meester et al., 2014;
+Panter et al., 2010) and their children's skills (Ghekiere et al., 2017)
+also influence whether they allow their children to walk or bicycle to
+school.
+
+Distance between home and school is most strongly associated with AST
+(Ikeda et al., 2018; Mammen et al., 2012; Pont et al., 2009;
+\textbf{rothmanDeclineActiveSchool2018?}) with less AST reported among
+children who have to travel farther to school. Many studies have also
+found that the quality of the built environment along the route to
+school and around the school site (Ikeda et al., 2018; Kim and Lee,
+2020; \textbf{rothmanActiveSchoolTransportation2021?}) and provision of
+active travel infrastructure (Pont et al., 2009;
+\textbf{chenPromotingActiveStudent2018a?}) facilitate AST. Canadian
+youth report that they feel most safe bicycling on streets in their
+neighbourhood or that have low volumes of traffic
+(\textbf{TACbikeinfra2020?}). Finally, concerns about traffic and
+strangers have been reported by parents who drive their children to
+school (Mammen et al., 2012), which highlights that the volume and speed
+of cars can be a concern or deterrent for AST.
+
+\hypertarget{school-travel-planning-in-canada}{%
+\subsection{2.3. School travel planning in
+Canada}\label{school-travel-planning-in-canada}}
+
+School travel planning (STP) has been implemented in Canada since at
+least the late 2000s. Within the STP process, facilitators generally
+establish multi-sector committees who intervene at the participating
+school through a range of activities related to the 5E's such as
+\emph{education} strategies, \emph{encouragement} through in-person
+events or programs, \emph{engineering} improvements to or around the
+school site, and \emph{enforcement} of traffic speeds around schools
+(Mammen et al., 2014; \textbf{langUnderstandingModalChoice2011?}). The
+first large-scale evaluation of STP as an intervention in Canada took
+place at twelve schools across the country, including four in Ontario,
+using parental surveys to measure changes in travel behaviour and
+perceptions (\textbf{buliungSchoolTravelPlanning2011?}). Since then,
+there have been other assessments of both the efficacy of STP
+(Buttazzoni et al., 2019; Mammen et al., 2014) and the process of
+implementing such programs in Ontario (Buttazzoni et al., 2018;
+\textbf{mammenPuttingSchoolTravel2015?}). STP facilitators have
+recommended that additional time and resources are needed to improve the
+efficacy of STP (\textbf{mammenPuttingSchoolTravel2015?}), which
+highlights that long-term and sustained efforts driven at the policy
+level are required to address declining rates of AST.
+
+The ways in which AST is framed seem particularly important to shift
+parental attitudes and perceptions given their reported influence on
+children's travel mode to school. STP activities heavily focus on
+education or encouragement (Buttazzoni et al., 2018; Mammen et al.,
+2014; \textbf{buliungSchoolTravelPlanning2011?}), but parents may not
+always be receptive to the goals of STP and may be resistant to
+behaviour change (see Buttazzoni et al., 2018). Parents have been found
+to express different understandings, language, and perceptions than
+planners of the built environment determinants that influence school
+travel (Buliung et al., 2021). This is also true when it comes to other
+factors like convenience of different modes to school
+(\textbf{langUnderstandingModalChoice2011?}). STP stakeholder groups
+must pay special attention to parents' understanding of the decline of
+AST as a problem, which may affect their receptivity to proposed
+solutions.
+
+The ``central organizing idea or story line'' of AST, to apply the
+definition from Gamson and Modigliani
+(\textbf{gamsonChangingCulture1987?}), could also affect broader support
+in the community. Municipal representatives are perceived to be
+instrumental but the involvement of other stakeholder groups (e.g.,
+busing consortium representatives and local residents) can be lacking
+(Buttazzoni et al., 2018). In Ontario, it would be reasonable to say
+that AST has become a policy issue on the education and public health
+agendas over this time as evidenced by the financial contribution from
+the provincial government. The support from a range of municipal
+representatives (see Buttazzoni et al., 2018;
+\textbf{mammenPuttingSchoolTravel2015?}) demonstrates that the ``policy
+stream'' (see \textbf{kingdonAgendasAlternativesPublic1984?}) has been
+well engaged. It is unknown to what degree the general public (i.e.,
+local residents) has been exposed to messaging about AST, which could
+affect their participation in the STP process as desired by STP
+facilitators (Buttazzoni et al., 2018).
+
+The success of STP interventions would likely depend on parental
+judgments of factors that are related to school travel, as well as
+support from key policy makers. For example, parents have been found to
+view mixed land use as conducive for driving, despite transport planners
+viewing neighbourhoods with mixed uses as key for encouraging more
+active travel (Buliung et al., 2021). Therefore, stakeholder groups
+involved in STP must make important choices about the proposed solutions
+and potential benefits that ought to be communicated to parents and the
+general public about AST to convey its importance as a policy issue and
+to facilitate adoption of AST. Publicly available content about AST,
+therefore, needs to effectively engage multiple audiences on this policy
+issue including parents, children, politicians, and school
+representatives. This information should reflect current knowledge from
+research on school travel, plus content specific to local factors that
+influence AST, so that the challenges of AST are adequately defined and
+the opportunities or solutions to address the problems are clear.
+However, it is unknown to what degree STP materials presented to the
+general public reflect the scope of evidence from the literature on AST.
+
 \hypertarget{data}{%
@@
 sourced online from the main stakeholder groups involved in STP
-initiatives in Ontario: i) school boards (public and English-speaking
-only); ii) municipal governments; and iii) transportation consortia.
-Non-profit organizations, police services, and advocacy groups are other
-stakeholders who may play a role in supporting AST and/or STP, but this
-study does not include any documents from these groups because they are
-not consistently participating in all initiatives.
-
-The search was guided first by a list of all English public school
-boards across Ontario. The websites of each school board were manually
-searched for pages related to school transportation or travel. Any pages
-relevant to these topics were manually downloaded. Next, we collected
-documents by searching municipal government and transportation consortia
-websites. The latter were identified based on geographic area (i.e., the
-municipalities and/or transportation consortia that are in the same
-geographic area of each school board). Pages related to active or school
-travel were manually downloaded. Webpages from STP stakeholder websites
-were included in our analysis if they were easy to find. This primary
-criteria was important since our analysis pertains to how such issues
-are framed to the public. Thus, we included only webpages that were easy
-to find, which we defined as requiring no more than 2-4 separate links
-from the initial Google search.
-
-The initial corpus of policy documents included 64 relevant webpages
-(i.e., one page or more) from all STP stakeholder groups. It is
-important to note that school boards, municipalities, and transportation
-consortia may or may not publish information about their involvement in
-AST and STP efforts on their respective websites or in policy documents,
-which means that some of these groups for particular regions in Ontario
-are not included in our analysis. Search results are summarized in Table
+initiatives in Ontario: i) school boards (public or Catholic and
+English-speaking only); ii) municipal governments; and iii)
+transportation consortia. The latter are a unique group of entities
+sanctioned by Ontario's Ministry of Education in Ontario 2006. Each
+consortium involves a collaboration between regions and school boards;
+the consortium's objective is to deliver more efficient and timely
+transportation services to schools in each region
+(\textbf{ministryeducation2006?}). Non-profit organizations, police
+services, and advocacy groups are other stakeholders who often play a
+role in supporting AST and/or STP, but this study does not include any
+documents from these groups because they are not consistently
+participating in all initiatives across Ontario.
+
+The search was guided first by a list of all English public and Catholic
+school boards across Ontario. The websites of each school board were
+manually searched for pages related to school transport or travel. Any
+pages relevant to these topics were manually downloaded. Next, we
+collected documents by searching municipal government and transportation
+consortia websites. These were identified based on geographic area
+(i.e., the municipalities and/or transportation consortia that are in
+the same geographic area of each school board). Webpages related to
+active transport or school travel were manually downloaded.
+
+Webpages from STP stakeholder groups were included in our analysis if
+they were easy to find. This primary criterion was important since our
+analysis pertains to how such issues are framed to the general public.
+Thus, we included only webpages that were readily accessible, which we
+defined as requiring no more than 2-4 separate links from the initial
+Google search.
+
+The initial corpus of documents from STP stakeholder groups included 69
+relevant webpages (i.e., one page or more) from all STP stakeholder
+groups. We refer to these as policy documents throughout the paper. It
+is important to note that school boards, municipalities, and
+transportation consortia may or may not publish information about their
+involvement in AST and STP efforts on their respective websites or in
+policy documents. Search results are summarized in Table
 \ref{tab:policy-documents}.
@@
 \midrule
-\cellcolor{gray!6}{\textbf{School boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{31}\\
-\textbf{Municipalities} & 62 & 25\\
-\cellcolor{gray!6}{\textbf{Transportation consortia}} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{8}\\
+\cellcolor{gray!6}{\textbf{School boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{32}\\
+\textbf{Municipalities} & 62 & 28\\
+\cellcolor{gray!6}{\textbf{Transportation consortia}} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9}\\
 \bottomrule
@@
 \hypertarget{academic-papers}{%
-\subsubsection{3.2.1. Academic papers}\label{academic-papers}}
+\subsubsection{3.1.2. Academic papers}\label{academic-papers}}
 
@@
 A multi-step process was conducted to ensure that the analysis captured
-as much content as possible from both the policy documents (n = 64) and
+as much text as possible from both the policy documents (n = 64) and
 academic papers (n = 233). To begin, the webpages, which were manually
@@
 that were not properly detected during the conversion process) were
-fixed by inserting the unicode sequence of character to replace the
+fixed by replacing the unicode sequence of character by inserting the
 missing sequence of characters.
@@
 such as \emph{and} or \emph{the} as identified in a predetermined list
-by Lewis et al.~({\textbf{???}}) and other frequent terms in the
+by Lewis et al. (\textbf{R-tm?}) and other frequent terms in the
 documents like ``school'' and specific location names, were removed from
@@
 the public through particular frames to influence perceptions or
-behaviours. Gamson and Modigliani ({\textbf{???}}) conceptualize a frame
-as a ``central organizing idea or story line that provides meaning'' to
-a particular phenomenon. A frame can enable individuals ``to locate,
-perceive, identify, and label'' information pertaining to various
-dimensions of an issue (Goffman, 1974). Scholars in the field of
-political communications have proposed that communicators, such as the
-media or an institution, construct the narrative of a frame for policy
-positions or public issues in order to activate or restrict a particular
-response in the intended audience (Pan and Kosicki, 1993). Framing can
-be used to position existing solutions as suitable to address particular
-issues (Mah et al., 2014), which may prevent the public from being aware
-of other policy approaches that challenge the status quo to bring about
-more radical change. The way policy issues are framed is ultimately
-important to understand because it plays a role in either altering or
-preserving the existing social perceptions.
+behaviours. As previously mentioned, a frame is a ``central organizing
+idea or story line that provides meaning'' to a public issue or
+phenomenon (\textbf{gamsonChangingCulture1987?}). Scholars in the field
+of political communications have proposed that communicators, such as
+the media or an institution, construct the narrative of a frame for
+policy positions or public issues in order to activate or restrict a
+particular response in the intended audience (Pan and Kosicki, 1993).
+Organized groups of stakeholders can employ similar methods to attract
+attention to particular issues. Framing can be used to position existing
+solutions as suitable to address particular issues (Mah et al., 2014),
+which may prevent the public from being aware of other policy approaches
+that challenge the status quo. The way policy issues are framed is
+ultimately important to understand because it plays a role in either
+altering or preserving the existing social perceptions. This, in turn,
+can affect whether issues are put on the agenda of policy makers and can
+determine which solutions are proposed to address the problem
+(\textbf{kingdonAgendasAlternativesPublic1984?}).
 
@@
 obvious example over the past decade is the framing of climate change as
-a public health issue (e.g., @ depouxCommunicatingClimateChange2017;
-Maibach et al., 2010; Weathers and Kendall, 2016) to increase public
-engagement and reception of the issue. Transport planners also use
+a public health issue (e.g., Depoux et al., 2017; Maibach et al., 2010;
+Weathers and Kendall, 2016) to increase public engagement and awareness
+of the issue. This framing has slowly advanced this issue on public
+policy agendas as public attention puts pressure on the policy stream to
+adopt frameworks for action. For example, transport planners also use
 different frames to guide the extent to which transport policies can be
-adapted to address climate change. In a recent paper ({\textbf{???}}),
-framing analysis was applied to review the representation of issues such
-as mobility and social exclusion in municipal policies from four western
-Canadian cities under the current circumstances of climate change. The
-authors found four primary frames: ``The Growing City'', ``If You Build
-It, They Will Come'', ``Better City for All'', and a ``the Resilient
-City''. Each frame presented the nature, opportunities, and challenges
-of climate change in different ways which set the stage for the types of
-mitigation and adaptation strategies that cities were proposing to
-address this issue.
-
-Given the range of factors at multiple levels of the socioecological
-model that influence school travel, it is important to understand how
-walking and bicycling to school are framed to the public. Is active
-school travel framed as a public health or environmental issue? Is it
-framed as both? Do proposed solutions to increase AST focus primarily on
-the intrapersonal and interpersonal factors, meaning that behaviour
-change must ultimately result from different decisions made by the
-individual or the household? Or is the decline in AST framed as an issue
-that must be addressed through changes in the built environment? These
-are the types of questions that we aim to answer in this paper. To our
-knowledge, this topic has not be addressed in the school travel
-literature to date.
+adapted to address climate change. In a recent paper
+(\textbf{reynardGrowthResilienceHow2021?}), framing analysis was applied
+to review the representation of issues such as mobility and social
+exclusion in municipal policies from four western Canadian cities under
+the current circumstances of climate change. The authors found four
+primary frames: ``The Growing City,'' ``If You Build It, They Will
+Come,'' ``Better City for All,'' and a ``the Resilient City''
+(\textbf{reynardGrowthResilienceHow2021?}). Each frame presented the
+nature, opportunities, and challenges of climate change in different
+ways which set the stage for the types of mitigation and adaptation
+strategies that cities were proposing to address this issue.
+
+In a similar way, we hypothesize that STP stakeholder groups in Ontario
+have framed AST in particular ways to effectively engage multiple
+audiences on this policy issue including parents, local residents,
+school representatives, and municipal representatives. These groups are
+likely identifying points of intervention and potential opportunities to
+build support for and encourage AST.
 
@@
 
-The topic modelling analysis was conducted in R. We primarily used the
-following packages: \texttt{topicmodels} ({\textbf{???}}),
-\texttt{word2vec} ({\textbf{???}}), and \texttt{wordcloud}
-({\textbf{???}}) to examine content in the documents that were sourced
-for this project. These packages have functions for determining the
-frequency of specific words in each document, relationships (e.g., pairs
-of adjacent terms) and correlations between words, and estimating Latent
-Dirichlet allocation (LDA) models to classify documents according to the
-topics that are contained within them. We describe in the section below
-how we used these functions to produce our results.
+We use topic modelling in R to conduct the framing analysis. Topic
+modelling is a machine learning technique that can identify what
+language and concepts are being communicated by analyzing text. This
+method is more practical for researchers working with large amounts of
+text because it replaces the manual coding of topics that would normally
+take place to analyze or summarize textual data
+(\textbf{jacobiQuantitativeAnalysisLarge2016?}). In the data
+pre-processing phase, we tokenize the text in the documents and create a
+document-term matrix so that it is in the correct format for analysis.
+We primarily use the following packages: \texttt{tidytext}
+(\textbf{R-tidytext?}), \texttt{topicmodels} (\textbf{R-topicmodels?}),
+\texttt{word2vec} (\textbf{R-word2vec?}), and \texttt{wordcloud}
+(\textbf{R-wordcloud?}) to examine text in the documents that were
+sourced for this project. These packages have functions for determining
+the frequency of specific words in each document or relationships (e.g.,
+pairs of adjacent terms called bigrams) and correlations between words.
+These methods can reveal what language and concepts are being
+communicated to the general public. Topic modelling is a popular method
+for analyzing text from social media platforms
+(\textbf{albalawiUsingTopicModeling2020?}) or news articles
+(\textbf{jacobiQuantitativeAnalysisLarge2016?}). We estimate latent
+Dirichlet allocation (LDA) models to classify both the STP and documents
+according to the topics that are contained within them. This method
+``treats each document as a mixture of topics, and each topic as a
+mixture of words'' (\textbf{silgeTextMining2021?}). The model's output
+is ``a set of topics consisting of clusters of words that co-occur in
+these documents according to certain patterns''
+(\textbf{jacobiQuantitativeAnalysisLarge2016?}). Researchers must then
+interpret the identified topics, as done after other methods of manual
+coding. We also compare the topics between the policy documents and the
+academic papers, and use our interpretation to answer the questions
+outlined above that guide this paper. This methodology is not familiar
+to many, so we describe in more detail below how we used specific
+functions and code in R to produce our results.
 
@@
 sources and organized in the form of a data package. Following best
-practices in spatial data science ({\textbf{???}}), the code and data
-needed to reproduce or conduct a similar analysis for other regions in
-North America or elsewhere are available for download.
+practices in spatial data science (\textbf{brunsdon2020opening?}), the
+code and data needed to reproduce or conduct a similar analysis for
+other regions in North America or elsewhere are available for download.
 
@@
 
-We analyzed word and document frequency for each corpora. Table
-\ref{tab:word-table} shows the most frequent terms found in the
-municipal, transportation consortia, school board, and academic
-documents. As expected, STP documents and academic papers reference
+We analyzed word and document frequency for each set of documents (i.e.,
+corpus). Table \ref{tab:word-table} shows the most frequent terms found
+in the municipal, transportation consortia, school board, and academic
+documents. As expected, policy documents and academic papers reference
 \emph{active travel}, \emph{walking}, \emph{biking} or \emph{cycling},
-and \emph{students} more than other terms. Each corpora also has
+and \emph{students} more than other terms. Each corpus also has
 \emph{safety} and \emph{traffic} as common words which suggests
@@
 AST is framed to the public. The word \emph{physical} is present in each
-corpus which could refer to either \emph{physical activity},
-\emph{physical health}, or the \emph{physical environment}. Furthermore,
-documents from STP stakeholders discuss \emph{resources},
-\emph{information}, and \emph{services} about school travel. In the
-section below, the context in which these terms appear is explored
-further through their concordance. Unlike the academic papers, STP
-stakeholder documents include the words \emph{route} or \emph{routes}.
-This could reflect their role in identifying safe routes to school to
+corpus, but it's not clear what this refers to (e.g, \emph{physical
+activity}, \emph{physical health}, or the \emph{physical environment}).
+Furthermore, documents from STP stakeholder groups discuss
+\emph{resources}, \emph{information}, and \emph{services} about school
+travel. In the section below, the context in which these terms are
+discussed is explored further.
+
+Unlike the academic papers, policy documents include the words
+\emph{route} or \emph{routes} as frequent terms. This could reflect the
+role of STP stakeholder groups in identifying safe routes to school to
 share with parents or families, as well as the STP emphasis on making
-the physical environment safer for AST. The academic corpora differs
-from the policy documents in that \emph{parents} and \emph{distance} are
-the second and third most common terms. In addition, \emph{time},
+the physical environment safer for AST. The academic corpus differs from
+the policy documents in that \emph{parents} and \emph{distance} are the
+second and third most common terms. In addition, \emph{time},
 \emph{factors}, \emph{environment}, and \emph{age} are also identified
-in academic papers. These words are absent from the list of common words
-in policy documents. Table \ref{tab:word-table} indicates that the
-research corpora discusses a broader range of determinants of AST than
+in the academic papers. These words are absent from the list of common
+words in policy documents. Table \ref{tab:word-table} indicates that the
+academic corpus discusses a broader range of determinants of AST than
 the policy documents. The number of references for each term in the
@@
 
-Bigrams for each policy corpora that occur more than 5 times are shown
-in Figures \ref{fig:city-visual}, \ref{fig:consortia-visual}, and
-\ref{fig:school-visual}. These figures help to make further sense of the
-word frequencies reported above, and highlight the main ideas that are
-presented to the public in each of the policy corpora. Municipalities
-primarily discuss \emph{physical activity} (n = 53) and \emph{public
-health} (n = 19) in the context of active travel. In addition,
-\emph{travel planning} (n = 19), \emph{bike lanes} (n = 16), and
-\emph{safe routes} (n = 14) are also identified, conceivably as
-interventions and built environment factors that support AST. Key issues
-related to transport such as \emph{traffic safety} (n = 10), \emph{air
-quality} (n = 9), and \emph{greenhouse gases} (n = 9) are conveyed to
-the public through AST documents. It is not surprising to find this
-focus in AST documents given that municipalities in Ontario are
-concerned about climate change and have increasingly looked to active
-modes of travel to offset transport-related emissions in urban areas.
+Bigrams refer to a pair of consecutive words. We use the
+\texttt{unnest\_tokens} function from the \emph{tidytext} package to
+determine the bigrams. Figures \ref{fig:city-visual},
+\ref{fig:consortia-visual}, and \ref{fig:school-visual} show the bigrams
+that occur more than 5 times for each set of policy documents. These
+figures help to make further sense of the word frequencies reported
+above, and highlight the main ideas that are presented to the public in
+each of the policy corpora. Municipalities primarily discuss
+\emph{physical activity} (n = 53) and \emph{public health} (n = 19) in
+the context of AST. In addition, \emph{travel planning} (n = 19),
+\emph{bike lanes} (n = 16), and \emph{safe routes} (n = 14) are also
+identified, conceivably as either proposed solutions or built
+environment factors that support AST. Key issues related to transport
+such as \emph{traffic safety} (n = 10), \emph{air quality} (n = 9), and
+\emph{greenhouse gases} (n = 9) are conveyed to the public through these
+policy documents. It is not surprising to find this focus given that
+municipalities in Ontario are concerned about climate change and have
+increasingly looked to active modes of travel to offset
+transport-related emissions in urban areas.
 
@@
 cycling is notably absent from transportation consortia documents.
+Overall, the policy documents There appears convey an emphasis on the
+built environment, rather than household decision-making.
 
@@
 
-\caption{Most common bigrams found in the municipal or regional government documents.}\label{fig:city-visual}
+\caption{\label{fig:city-visual}Most common bigrams found in the municipal or regional government documents.}\label{fig:city-visual}
 \end{figure}
@@
 
-\caption{Most common bigrams found in the transportation consortia documents.}\label{fig:consortia-visual}
+\caption{\label{fig:consortia-visual}Most common bigrams found in the transportation consortia documents.}\label{fig:consortia-visual}
 \end{figure}
@@
 
-\caption{Most common bigrams found in the school board documents.}\label{fig:school-visual}
+\caption{\label{fig:school-visual}Most common bigrams found in the school board documents.}\label{fig:school-visual}
 \end{figure}
@@
 
-\caption{Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined).}\label{fig:policy-visual}
+\caption{\label{fig:policy-visual}Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined).}\label{fig:policy-visual}
 \end{figure}
 
-We then combined all municipality, school board, and transportation
-consortia documents into one ``policy'' corpora. This enabled us to
+We then combine all municipality, school board, and transportation
+consortia documents into one ``policy'' corpus. This enabled us to
 examine and visualize the most common bigrams found across all of the
-STP material in Ontario that was collected for this study. Figure
+material in Ontario that was collected for this study. Figure
 \ref{fig:policy-visual} shows all of the bigrams that occur more than 10
-times in the corpora. In addition to the common bigrams already
+times in the policy corpus. In addition to the bigrams already
 identified above, we also found \emph{mental health}, \emph{walk day},
-and \emph{green communities} as common pairs of consecutive words.
-Overall, policy documents from STP stakeholders seem to focus on four
-key areas: i) benefits or impacts of AST; ii) mechanisms of
-intervention; iii) concerns or considerations; and iv) supports for AST.
-
-We analyzed bigrams in the academic corpora separately to make
-comparisons with the policy corpora. Figure \ref{fig:academic-visual}
-indicates that the academic corpora includes several common bigrams that
-were also found in the policy documents including \emph{physical
-activity} (n = 1566), which is the top bigram, \emph{traffic safety} (n
-= 308), and \emph{safe routes} (n = 268). However, many other factors
-relating to AST are identified in the research literature that are not
-presented to the public through policy documents. After \emph{physical
-activity}, \emph{built environment} (n = 1175), \emph{independent
-mobility} (n = 774), and \emph{urban form} (n = 352) are the most
-frequent pairs of consecutive words. Academic papers also often discuss
-\emph{distance home} (n = 258), \emph{car ownership} (n = 254),
-\emph{household income} (n = 254), and \emph{population density} (n =
-205), which are factors that have been found to influence AST. It is
-evident that many papers investigate gender differences in AST given
-that \emph{boys girls} (n = 211) is another common bigram. Finally, the
-presence of \emph{statistically significant} among the top bigrams
-underscores that researchers aim to identify determinants that are not
-due to chance but that likely influence AST. The academic corpora
-focuses on a greater range of topics than found in the STP material.
+and \emph{green communities} as common pairs of consecutive words. The
+latter terms represent the significant involvement of the non-profit
+organization in supporting AST initiatives through the Ontario Active
+School Travel program. Overall, the policy documents from STP
+stakeholder groups seem to focus on four key areas: i) benefits or
+impacts of AST; ii) mechanisms of intervention; iii) concerns or
+considerations; and iv) supports for AST. This interpretation indicates
+that the general public accessing information about AST in Ontario is
+informed about an adequate range of content related to this issue.
+
+Next, we analyze bigrams in the academic corpus separately to make
+comparisons with the policy corpus. Figure \ref{fig:academic-visual}
+indicates that academic papers include several common bigrams that were
+also found in the policy documents including \emph{physical activity} (n
+= 1566), which is the top bigram, \emph{traffic safety} (n = 308), and
+\emph{safe routes} (n = 268). However, many other factors are identified
+in the research literature that are not presented to the general public
+through policy documents. After \emph{physical activity}, \emph{built
+environment} (n = 1175), \emph{independent mobility} (n = 774), and
+\emph{urban form} (n = 352) are the most frequent pairs of consecutive
+words. Academic papers also often discuss \emph{distance home} (n =
+258), \emph{car ownership} (n = 254), \emph{household income} (n = 254),
+and \emph{population density} (n = 205), which are factors that have
+been found to influence AST. It is evident that many papers investigate
+gender differences in AST given that \emph{boys girls} (n = 211) is
+another common bigram. Finally, the presence of \emph{statistically
+significant} among the top bigrams underscores that some researchers aim
+to identify determinants using statistical measures. We find that the
+academic corpus focuses on a greater range of topics than found in the
+policy documents.
 
@@
 
-\caption{Most common bigrams found in the academic papers.}\label{fig:academic-visual}
+\caption{\label{fig:academic-visual}Most common bigrams found in the academic papers.}\label{fig:academic-visual}
 \end{figure}
 
-We interpreted the most common bigrams from the policy corpora (see
-Figure \ref{fig:policy-visual}), which includes all documents from
+We interpret the most common bigrams from the policy corpus (see Figure
+\ref{fig:policy-visual}), which includes all documents from
 municipalities, transportation consortia, and school boards, as the main
-ideas that STP stakeholders are focusing on and communicating to the
-public about AST. We then used the \texttt{kwic} function from the R
-\emph{quanteda} package to identify and better understand the context of
-these key themes. Table \ref{tab:policy-concordance} presents examples
-of the key themes that were extracted from select policy documents to
-demonstrate how the most common bigrams are communicated to the public.
+ideas that STP stakeholder groups are focusing on and communicating to
+the public about AST. We then use the \texttt{kwic} function from the
+\emph{quanteda} package to better understand the context of these key
+ideas. Table \ref{tab:policy-concordance} presents some examples of the
+context that was extracted from select policy documents to demonstrate
+how the most common bigrams are communicated to the public.
 
 \begin{table}
+
+\caption{\label{tab:content-table}\label{tab:policy-concordance}CAPTION THIS TABLE}
 \centering
-\begin{tabular}[t]{>{}l|l|>{\raggedright\arraybackslash}p{30em}}
-\hline
+\begin{tabular}[t]{>{}ll>{\raggedright\arraybackslash}p{20em}}
+\toprule
 Terms & Stakeholder & Context\\
-\hline
-\textbf{Air Quality} & School Board & Active transportation [...] improves air quality.\\
-\hline
+\midrule
+\textbf{\cellcolor{gray!6}{Air Quality}} & \cellcolor{gray!6}{School Board} & \cellcolor{gray!6}{Active transportation [...] improves air quality.}\\
 \textbf{Benefit} & Municipality & Stronger bones and muscles, improved self-esteem and sense of well-being while reducing stress and risk of chronic disease all benefit those who use active transportation.\\
-\hline
-\textbf{Bus} & School Board & While taking part in a walking school bus, your child will enjoy seeing friends on the way to school.
+\textbf{\cellcolor{gray!6}{Walking School Bus}} & \cellcolor{gray!6}{School Board} & \cellcolor{gray!6}{While taking part in a walking school bus, your child will enjoy seeing friends on the way to school.
 They will be active more often.
-This is also a great opportunity for your child to socialize with school friends in a monitored and safe way where they can practice social distancing, modelled by a leader.\\
-\hline
-\textbf{Community} & School Board & Engage community stakeholders (school boards, municipalities, police, public health professionals, parents/guardians, administrators, educators and children) to work together to identify and to solve their school travel needs.\\
-\hline
-\textbf{Emissions} & Consortia & An active school commute also reduces congestion in school zones and contributes to reducing greenhouse gas emissions – it’s a win-win for everyone!\\
-\hline
+This is also a great opportunity for your child to socialize with school friends in a monitored and safe way where they can practice social distancing, modelled by a leader.}\\
+\textbf{Community} & School Board & Help your students get started on the right foot - encourage them to walk or bike to school when possible.
+Even leaving the car a block or two and walking the rest of the way helps.
+It’s good for the environment and your health, and teaches your child independence and community awareness.\\
+\textbf{\cellcolor{gray!6}{Emissions}} & \cellcolor{gray!6}{Consortia} & \cellcolor{gray!6}{An active school commute also reduces congestion in school zones and contributes to reducing greenhouse gas emissions – it’s a win-win for everyone!}\\
+\addlinespace
 \textbf{Health} & Municipality & Active School Travel allows school-aged children the chance to participate in moderate to intense physical activity.
 This is linked with lower body mass index and improved cardiovascular health.\\
-\hline
-\textbf{Lanes} & Municipality & We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments.\\
-\hline
+\textbf{\cellcolor{gray!6}{Lanes}} & \cellcolor{gray!6}{Municipality} & \cellcolor{gray!6}{We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments.}\\
 \textbf{Mental Health} & Municipality & ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.\\
-\hline
-\textbf{Physical Health} & Municipality & Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.\\
-\hline
+\textbf{\cellcolor{gray!6}{Physical Health}} & \cellcolor{gray!6}{Municipality} & \cellcolor{gray!6}{Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.}\\
+\bottomrule
 \end{tabular}
@@
 
-\begin{verbatim}
-## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
-## "none")` instead.
-\end{verbatim}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-5.pdf}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/municipal-terms-1.pdf}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/school-terms-1.pdf}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/consortia-terms-1.pdf}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/policy-terms-1.pdf}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/academic-terms-1.pdf}
-
-Finally, we conducted topic modelling to examine the different topics
-found in the policy and academic corpora. We focused on the policy
-corpora, instead of individually assessing the municipal, school, and
-consortia corpus, so that we could report on the primary and secondary
-frames used across all documents put out by STP stakeholders in Ontario.
-To determine the number of discrete topics in each corpus, we used the
-ldatuning package. We then used the \texttt{LDA} function from the
-topicmodels package to estimate an LDA model for each group of
-documents. The policy corpora, which combined all documents from
-municipalities, schools, and transportation consortia, had 5 topics. The
-academic corpora had 17 topics. Figures \ref{fig: policy-terms} and
-\ref{fig: academic-terms} present the main terms that are associated
-with the topics found in each corpus.
-
-In the policy corpus, we identified the following topics: (1) resources
-for walking, (2) busing information and eligibility; (3) benefits of
-active travel; (4) bicycling and the environment; and (5) supporting
-active travel. These findings reveal that STP stakeholders are sending
-the message that walking and bicycling to school as healthy travel modes
-for students, particularly as a means to get physical activity. We also
-found that there is information shared to support parents and students
-in using active modes to school such as the availability of cycling
-lanes or route tips for walking. STP stakeholders appear to be
-communicating that AST is possible and safe as a result of improvements
-to the built environment and available resources for parents and
-children. A final focus in the policy documents is on various efforts
-that are underway to support active travel including route planning.
-
-We expected to find a higher number of topics in the academic corpus due
-to the larger number of documents in the corpora and the diversity of
-content examined in existing literature about school travel. The
-following topics were identified, which touch upon a broader range of
-factors that are associated with or related to AST than are found in the
-policy corpus: (1) \textbf{unclear} (2) AST in Ontario and Canada; (3)
-\textbf{unclear}; (4) children's independent mobility; (5) safe routes
-to school programs; (6) commuting and distance; (7) density in the built
-environment and walking routes; (8) \textbf{unclear}; (9) walking
-interventions; (10) bicycling influences; (11) interpersonal and
-household influences on trips; (12) behaviours and attitudes; (13)
-\textbf{unclear}; (14) \textbf{unclear}; (15) walking distance; (16)
-\textbf{unclear}; (17) physical activity measures or results; (18)
-bicycling attitudes; and (19) \textbf{unclear}.
-
-The policy corpus primarily frames AST as a health and environmental
-issue. Many municipal and school documents position walking, bicycling,
-or rolling to school as beneficial to individual health, including
-improvements to physical activity levels or mental health, and to the
-broader community through a reduction in traffic and vehicle emissions.
-\textgreater{} \emph{If you live in a walk zone, the best way to get to
-school is by walking or biking. This promotes physical activity, helps
-the environment and minimizes traffic around schools during busy times.}
+\begin{figure}
+\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/policy-terms-1} \caption{\label{fig:policy-terms}CAPTION THIS FIGURE}\label{fig:policy-terms}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/academic-terms-1} \caption{\label{fig:academic-terms}CAPTION THIS FIGURE}\label{fig:academic-terms}
+\end{figure}
+
+Finally, we conduct topic modelling to examine the different topics
+found in the policy and academic corpora. We focus on the policy corpus,
+instead of individually assessing the municipal, school, and consortia
+documents, so that we could report on the various frames used across all
+documents put out by STP stakeholder groups in Ontario. To determine the
+number of discrete topics in each corpus, we use the \emph{ldatuning}
+package. We then use the \texttt{LDA} function from the
+\emph{topicmodels} package to estimate an LDA model for each group of
+documents. The parameters from the \emph{ldatuning} package suggest that
+the policy corpus has between 7 and 9 topics and the academic corpus has
+between 17 and 25 topics. After running the LDA model for the academic
+corpus, it was too difficult to interpret a minimum of 17 topics based
+on the clusters of words that were identified. We experimented with the
+model by adjusting the number of topics and found that there were 9
+distinct topics that could be interpreted, after which there was too
+much overlap. Figures \ref{fig:policy-terms} and
+\ref{fig:academic-terms} present the main terms that are associated with
+the topics found in each corpus.
+
+In the policy corpus, we interpret the following topics based on the
+cluster of words: (1) resources for walking, (2) busing information and
+eligibility; (3) benefits of active travel; (4) bicycling and the
+environment; and (5) supporting active travel. These topics indicate
+that STP stakeholder groups are sending the message that walking and
+bicycling to school are healthy travel modes for students, particularly
+as a means to get physical activity. We also found that there is
+information shared to support parents and students in using active modes
+to school such as the availability of cycling lanes or route tips for
+walking.
+
+The academic corpus has a higher number of topics likely due to the
+volume of papers that were sourced. The following topics were identified
+based on the clusters of words: (1) \textbf{unclear} (2) AST in Ontario
+and Canada; (3) \textbf{unclear}; (4) children's independent mobility;
+(5) safe routes to school programs; (6) commuting and distance; (7)
+density in the built environment and walking routes; (8)
+\textbf{unclear}; (9) walking interventions; (10) bicycling influences;
+(11) interpersonal and household influences on trips; (12) behaviours
+and attitudes; (13) \textbf{unclear}; (14) \textbf{unclear}; (15)
+walking distance; (16) \textbf{unclear}; (17) physical activity measures
+or results; (18) bicycling attitudes; and (19) \textbf{unclear}.
+
+We conclude that the policy corpus primarily frames AST as a health and
+environmental issue. Policy documents do not reflect the diversity of
+content found in the academic papers and instead focus on a few factors.
+STP stakeholder groups appear to position walking, bicycling, or rolling
+to school as beneficial to individual health, as an opportunity for
+physical activity or to improve mental health, and to the broader
+community through a reduction in traffic and vehicle emissions. Here, we
+present some examples from the policy documents to illustrate how the
+health and environmental frames are communicated:
+
+\begin{quote}
+\emph{If you live in a walk zone, the best way to get to school is by
+walking or biking. This promotes physical activity, helps the
+environment and minimizes traffic around schools during busy times.}
 (City of Barrie)
+\end{quote}
 
@@
 
-We found that some of these documents make direct references to topics
-found in research on school travel and the built environment. For
-example, some policy documents identify programs that have been
-researched in the literature and found to be effective, such as walking
-school buses, or explain how an increase in AST will reduce parent
-safety concerns. \textgreater{} \_ For their health, safety, environment
-and community: Kids learn healthy habits and concentrate better in
-class; One less car (yours) reduces traffic and parking problems in
-school zones; Teach your kids about traffic safety; Start a walking
-school bus; your kids make friends in every grade, and that can prevent
-bullying.\_ (City of Guelph)
+However by examining document frequency (see Section 5.1), we found that
+some terms are not present in all policy documents. This suggests that
+although documents pertain to the subject of active travel or school
+travel, some stakeholders across Ontario are not disseminating
+information about AST. For example, a document may discuss active travel
+but not to school or school travel but only by bus and not by active
+modes. We manually searched the policy corpus and found that 48\% of
+documents mention AST and 16\% mention STP. This confirms that many
+municipalities, school boards, and transportation consortia are not
+promoting AST through their webpages or indicating their involvement in
+the STP process. Instead, inclement weather and impacts to busing is a
+common topic addressed in school board and transportation consortia
+documents.
+
+Furthermore, we found that some policy documents make direct reference
+to topics found in the academic papers. For example, some policy
+documents encourage AST programs that have been researched and evaluated
+in the literature, such as walking school buses, or explain how an
+increase in AST will reduce parent safety concerns.
+
+\begin{quote}
+\_ For their health, safety, environment and community: Kids learn
+healthy habits and concentrate better in class; One less car (yours)
+reduces traffic and parking problems in school zones; Teach your kids
+about traffic safety; Start a walking school bus; your kids make friends
+in every grade, and that can prevent bullying.\_ (City of Guelph)
+\end{quote}
 
@@
 
-The secondary frame for AST in municipal documents is the opportunity or
+The secondary frame for AST in policy documents is the opportunity or
 prospect of behaviour change. Some cities and schools explain how
@@
 school on foot or by bike by describing efforts to make AST safer. This
-frame enables the public to evaluate their own travel decisions and to
-access resources (e.g., walking skills checklist) that will help them
-make AST a first choice. Some documents communicate what is being done
-by the municipalities or schools, like school travel planning, while
-others emphasize the active role of the parent in creating opportunities
-for AST in their household or neighbourhood. \textgreater{} \emph{School
-Travel Planning is a community-based approach that aims to increase the
-number of students and adults choosing active and sustainable travel to
-get to and from school. This approach addresses concerns about safety,
-physical activity, and the environment.} (City of Hamilton)
+frame encourages the public to evaluate their own travel decisions and
+to access resources (e.g., walking skills checklist) that will help them
+make AST a first choice. Some documents emphasize the role of the parent
+in creating opportunities for AST in their household or neighbourhood,
+however few documents address the main barriers as perceived by parents
+(e.g., distance, travel arrangements for multiple people, or
+convenience). Examples of this secondary frame include:
 
@@
 \begin{quote}
-Help your students get started on the right foot -encourage them to walk
-or bike to school when possible. Even leaving the car a block or two and
-walking the rest of the way helps. It's good for the environment and
-your health, and teaches your child independence and community
+Help your students get started on the right foot - encourage them to
+walk or bike to school when possible. Even leaving the car a block or
+two and walking the rest of the way helps. It's good for the environment
+and your health, and teaches your child independence and community
 awareness.\_ (Halton District School Board)
+\end{quote}
+
+\begin{quote}
+\emph{Want to boost your child's mental and physical health? Ottawa
+Public Health, City of Ottawa, and OSTA have produced a tipsheet for
+parents about ``active transportation'' to school -- fitting walking and
+wheeling into your daily routine.} (Ottawa-Carleton District School
+Board)
+\end{quote}
+
+Finally, the policy documents discuss proposed solutions to encourage
+AST. STP stakeholder groups seem to be communicating that AST is
+possible and safe as a result of improvements to the built environment
+and available resources for parents and children. A final focus in the
+policy documents is on various efforts that are underway to support
+active travel including route planning.
+
+\begin{quote}
+\emph{School Travel Planning is a community-based approach that aims to
+increase the number of students and adults choosing active and
+sustainable travel to get to and from school. This approach addresses
+concerns about safety, physical activity, and the environment.} (City of
+Hamilton)
 \end{quote}
@@
 
-\begin{quote}
-\emph{Want to boost your child's mental and physical health? Ottawa
-Public Health, City of Ottawa, and OSTA have produced a tipsheet for
-parents about ``active transportation'' to school -- fitting walking and
-wheeling into your daily routine.} (Ottawa-Carleton District School
-Board)
-\end{quote}
-
-Finally, many municipalities, schools, and consortia make no mention of
-active school travel on their main website pages for active
-transportation. Nonetheless, some municipalities explain how changes to
-the built environment are being implemented to facilitate active travel.
-Schools or consortia that do not refer to AST simply provide information
-about the busing service available to families in the region. Inclement
-weather and impacts to busing is a common topic addressed in those
-documents. \textgreater{} \emph{We are continuing to build on the
-cycling and pedestrian network by adding more bike lanes, building
-multi-use paths and encouraging developments to provide better
-pedestrian/cycling environments.} (City of Brantford)
-
-\begin{quote}
-\emph{The City of Burlington ensures all cyclists, pedestrians and
-drivers have access to safe and accessible transportation services and
-programs} (City of Burlington)
-\end{quote}
-
 \hypertarget{discussion}{%
@@
 
-We analyzed how AST is framed in documents available to the public on
-the websites of STP stakeholders in Ontario. We found that AST is
-primarily framed as beneficial to the health and wellbeing of children
-and to environmental sustainability. This was confirmed by the most
-common bigrams identified in the policy corpora, as well as the topics
-identified by the LDA model. Many studies and reviews have focused on
-the association between AST and physical activity (e.g., Faulkner et
-al., 2009; Mitra et al., 2017; Schoeppe et al., 2015), with findings
-consistently demonstrating that children who travel by walking or
-bicycling to school are more active than their peers who do not use
-active travel. More recently, researchers have been exploring the link
-between transport and children's wellbeing (Babb et al., 2017), which
-has relevant applications to the study of school travel and satisfaction
-(see van den Berg et al., 2020). We concluded that STP promotional
-materials have high concurrence with this topic in the research on
-school travel and the built environment. Framing AST as a health issue
-is certainly warranted - there is strong evidence that children who walk
-and bicycle to school accrue physical and mental health benefits.
-Furthermore, concerns about traffic and strangers have been reported by
-parents who drive their children to school (Mammen et al., 2012).
-Parents often have concerns about traffic volume, speed, and congestion
-around schools (Ling et al., 2021; Rothman et al., 2017), therefore the
-framing of AST as an environmental issue is in alignment with evidence
-from existing studies.
-
-The secondary frame of AST is that it is a behaviour that can and should
-be adopted by children and parents given the environmental and program
-supports available in the community. STP stakeholders emphasize that
-parents can access resources or trips to support their children in
-commuting by active modes to school. They also share information about
-interventions such as school travel plans and bicycle lanes to frame AST
-as safe and practical. However, STP materials neglect to address many
-intrapersonal and household factors that influence or predict AST. At
-the individual level, older child age is often associated with AST
-({\textbf{???}}; Mammen et al., 2012; Wilson et al., 2018), but AST is
-not framed as an activity for children based on age. STP stakeholders
-may wish to emphasize to parents that older children have greater
-traffic safety and cognitive abilities to navigate their own routes to
-school. There is also some evidence that gender is a determinant of AST
-({\textbf{???}}; Babb et al., 2017), although this is not a strong or
-consistent finding ({\textbf{???}}; Schoeppe et al., 2015). STP
-materials do not discuss this determinant of AST but it may be helpful
-to identify strategies or messages that alleviate specific concerns that
-relate to a child's gender.
-
-Furthermore, distance between home and school is the factor most
-associated with AST in existing research ({\textbf{???}}; Ikeda et al.,
-2018; Mammen et al., 2012; Pont et al., 2009) with less AST reported
-among children who have to travel farther to school. This topic is not
-addressed substantively in the policy corpus, perhaps due to the
-inability of STP stakeholders to directly intervene in residential
-location. Parental perceptions of the environment (De Meester et al.,
-2014; Panter et al., 2010) and children's skills (Ghekiere et al., 2017)
-also influence whether they allow their children to walk or cycle to
-school. STP documents do a sufficiently good job at communicated how an
-increase in AST could improve traffic safety in school zones and how new
-infrastructure improvements give children the ability to safely travel.
-This messaging has high concurrence with studies that have found that
-the quality of the built environment (Ikeda et al., 2018; Kim and Lee,
-2020) and active travel infrastructure (Pont et al., 2009) facilitate
-AST.
+Using topic modelling, we analyzed how AST is framed in documents
+available to the general public on the websites of STP stakeholder
+groups in Ontario. We found that AST is primarily framed as beneficial
+to the health and wellbeing of children and to environmental
+sustainability. This was confirmed by the most common bigrams identified
+in the policy corpus, as well as the topics identified by the LDA model.
+The policy documents adequately reflect the evidence that AST
+contributes positively to children's physical health (see Faulkner et
+al., 2009; Schoeppe et al., 2015). STP stakeholder groups also
+communicate that increasing AST may reduce traffic near and around
+schools which could alleviate parental concerns about traffic safety.
+The potential outcomes of increased AST are highlighted which may be
+persuasive arguments to motivate behaviour change, which is the
+secondary frame of AST that we interpreted based on the LDA models.
+
+The proposed solutions to the problem of declining AST that are
+communicated to the general public are mostly educational (e.g., safety
+tips or maps of safe routes) and engineering changes (e.g., traffic
+calming or bicycle lanes). These solutions have to sufficiently address
+real and perceived concerns that pose barriers to AST in order to
+encourage adoption. In most documents, the emphasis is on providing
+parents with resources that help them switch modes for the school
+commute and/or on reassuring them that the built environment has become
+safer and friendlier to active travelers.
+
+However, the policy documents noticeably lacked a focus on individual
+and household level determinants of AST. For example, the role of
+convenience and inclement weather in shaping household travel decisions
+(\textbf{buliungSchoolTravelPlanning2011?}) or the age at which children
+become allowed to travel by active modes or independently (Mammen et
+al., 2012) were not discussed. Given the range of factors that influence
+AST in a Canadian setting (\emph{inter alia}, see Mammen et al., 2012;
+Wilson et al., 2018; \textbf{mitraIndependentMobilityMode2013?};
+\textbf{rothmanDeclineActiveSchool2018?}), STP stakeholder groups must
+decide which points of intervention that they can reasonably have some
+influence towards. This should also depend on the local context so that
+barriers to AST as perceived by parents are addressed. It could be that
+STP stakeholder groups perceive to have more control over the
+micro-scale elements of the built environment, like traffic calming,
+rather than the ability to influence the number of trips to different
+destinations that households need to make. STP stakeholders are also
+unable to intervene in residential location, which affects distance to
+school.
 
 To increase rates of walking and bicycling independently to school,
-Riazi et al.~(2019) state: ``it will be vital for interventions to
+Riazi et al. (2019) state: ``it will be vital for interventions to
 target modifiable factors, including children's and parents' perceptions
@@
 factors associated with AST or parental perceptions about barriers to
-AST in the local context. Rothman et al.~(2018) note that local
+AST in the local context. Rothman et al. (2018) note that local
 solutions to address specific school challenges are worthwhile, and we
@@
 
-Future studies may investigate how parents and policymakers outside the
+Future studies may investigate how parents and policy makers outside the
 field of public health respond to the ways in which AST is framed in STP
@@
 acknowledge the developers of the following \texttt{R} packages:
-\texttt{dplyr} ({\textbf{???}}), \texttt{ggraph} ({\textbf{???}}),
-\texttt{ggplot2} ({\textbf{???}}), \texttt{igraph} ({\textbf{???}}),
-\texttt{pdftools} ({\textbf{???}}), \texttt{readr} ({\textbf{???}}),
-\texttt{reshape2} ({\textbf{???}}), \texttt{stringr} ({\textbf{???}}),
-\texttt{text2vec} ({\textbf{???}}), \texttt{textdata} ({\textbf{???}}),
-\texttt{tidyr} ({\textbf{???}}), \texttt{tidytext} ({\textbf{???}}),
-\texttt{tm} ({\textbf{???}}), \texttt{tools} ({\textbf{???}}),
-\texttt{topicmodels} ({\textbf{???}}), \texttt{widyr} ({\textbf{???}}),
-\texttt{word2vec} ({\textbf{???}}), \texttt{wordcloud} ({\textbf{???}}),
-\texttt{DiagrammeR} ({\textbf{???}}), and \texttt{kableextra}
-({\textbf{???}}).
+\texttt{dplyr} (\textbf{R-dplyr?}), \texttt{ggraph}
+(\textbf{R-ggraph?}), \texttt{ggplot2} (\textbf{R-ggplot2?}),
+\texttt{igraph} (\textbf{R-igraph?}), \texttt{pdftools}
+(\textbf{R-pdftools?}), \texttt{readr} (\textbf{R-readr?}),
+\texttt{reshape2} (\textbf{R-reshape2?}), \texttt{stringr}
+(\textbf{R-stringr?}), \texttt{text2vec} (\textbf{R-text2vec?}),
+\texttt{textdata} (\textbf{R-textdata?}), \texttt{tidyr}
+(\textbf{R-tidyr?}), \texttt{tidytext} (\textbf{R-tidytext?}),
+\texttt{tm} (\textbf{R-tm?}), \texttt{tools} (\textbf{R-tools?}),
+\texttt{topicmodels} (\textbf{R-topicmodels?}), \texttt{widyr}
+(\textbf{R-widyr?}), \texttt{word2vec} (\textbf{R-word2vec?}),
+\texttt{wordcloud} (\textbf{R-wordcloud?}), \texttt{DiagrammeR}
+(\textbf{R-diagrammeR?}), and \texttt{kableextra}
+(\textbf{R-kableextra?}).
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-babbChildrenActiveTravel2017}{}%
-Babb, C., Olaru, D., Curtis, C., Robertson, D., 2017. Children's active
-travel, local activity spaces and wellbeing: A case study in Perth, WA.
-Travel Behaviour and Society 9, 81--94.
-doi:\href{https://doi.org/10.1016/j.tbs.2017.06.002}{10.1016/j.tbs.2017.06.002}
-
+\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-buliungLivingJourneySchool2021}{}%
@@
 
+\leavevmode\hypertarget{ref-buttazzoniSupportingActiveSchool2018}{}%
+Buttazzoni, A.N., Coen, S.E., Gilliland, J.A., 2018. Supporting active
+school travel: A qualitative analysis of implementing a regional safe
+routes to school program. Social Science \& Medicine 212, 181--190.
+doi:\href{https://doi.org/10.1016/j.socscimed.2018.07.032}{10.1016/j.socscimed.2018.07.032}
+
 \leavevmode\hypertarget{ref-demeesterParentalPerceivedNeighborhood2014}{}%
@@
 
+\leavevmode\hypertarget{ref-depouxCommunicatingClimateChange2017}{}%
+Depoux, A., Hémono, M., Puig-Malet, S., Pédron, R., Flahault, A., 2017.
+Communicating climate change and health in the media. Public Health
+Reviews 38, 7.
+doi:\href{https://doi.org/10.1186/s40985-016-0044-1}{10.1186/s40985-016-0044-1}
+
 \leavevmode\hypertarget{ref-faulknerActiveSchoolTransport2009}{}%
@@
 Insights into children's independent mobility for transportation
-cyclingWhich socio-ecological factors matter? Journal of Science and
+cycling{{Which}} socio-ecological factors matter? Journal of Science and
 Medicine in Sport 20, 267--272.
@@
 experience, Frame analysis: An essay on the organization of experience.
-Harvard University Press, Cambridge, MA, US.
+{Harvard University Press}, {Cambridge, MA, US}.
 
@@
 \leavevmode\hypertarget{ref-kimBuiltNaturalEnvironmental2020}{}%
-Kim, Y.-J., Lee, C., 2020. Built and Natural Environmental Correlates of
-Parental Safety Concerns for Children's Active Travel to School.
-International Journal of Environmental Research and Public Health 17.
+Kim, Y.-J., Lee, C., 2020. Built and {Natural Environmental Correlates}
+of {Parental Safety Concerns} for {Children}'s {Active Travel} to
+{School}. International Journal of Environmental Research and Public
+Health 17.
 doi:\href{https://doi.org/10.3390/ijerph17020517}{10.3390/ijerph17020517}
-
-\leavevmode\hypertarget{ref-lingRelationshipMotorVehicle2021}{}%
-Ling, R., Rothman, L., Hagel, B., Macarthur, C., Winters, M., Churchill,
-T., HubkaRao, T., Macpherson, A., Cloutier, M.-S., Howard, A., 2021. The
-relationship between motor vehicle speed and active school
-transportation at elementary schools in Calgary and Toronto, Canada.
-Journal of Transport \& Health 21, 101034.
-doi:\href{https://doi.org/10.1016/j.jth.2021.101034}{10.1016/j.jth.2021.101034}
 
@@
 Mah, C.L., Hamill, C., Rondeau, K., McIntyre, L., 2014. A frame-critical
-policy analysis of Canada's response to the World Food Summit 19982008.
-Archives of Public Health 72, 41.
+policy analysis of {Canada}'s response to the {World Food Summit}
+1998{}. Archives of Public Health 72, 41.
 doi:\href{https://doi.org/10.1186/2049-3258-72-41}{10.1186/2049-3258-72-41}
@@
 O'Brien, C., Kennedy, J., 2014. Active school travel: An evaluation of
-the Canadian school travel planning intervention. Preventive Medicine
+the {Canadian} school travel planning intervention. Preventive Medicine
 60, 55--59.
 doi:\href{https://doi.org/10.1016/j.ypmed.2013.12.008}{10.1016/j.ypmed.2013.12.008}
-
-\leavevmode\hypertarget{ref-mitraChildrenActivitytransportationLifestyles2017}{}%
-Mitra, R., Cantello, I.D., Buliung, R.N., Faulkner, G.E.J., 2017.
-Children's activity-transportation lifestyles, physical activity levels
-and social-ecological correlates in Toronto, Canada. Journal of
-Transport \& Health 6, 289--298.
-doi:\href{https://doi.org/10.1016/j.jth.2017.03.010}{10.1016/j.jth.2017.03.010}
 
@@
 Riazi, N.A., Blanchette, S., Trudeau, F., Larouche, R., Tremblay, M.S.,
-Faulkner, G., 2019. Correlates of Children's Independent Mobility in
-Canada: A Multi-Site Study. International Journal of Environmental
+Faulkner, G., 2019. Correlates of {Children}'s {Independent Mobility} in
+{Canada}: A {Multi}-{Site Study}. International Journal of Environmental
 Research and Public Health 16.
@@
 
-\leavevmode\hypertarget{ref-rothmanSchoolEnvironmentStudent2017}{}%
-Rothman, L., Buliung, R., Howard, A., Macarthur, C., Macpherson, A.,
-2017. The school environment and student car drop-off at elementary
-schools. Travel Behaviour and Society 9, 50--57.
-doi:\href{https://doi.org/10.1016/j.tbs.2017.03.001}{10.1016/j.tbs.2017.03.001}
-
 \leavevmode\hypertarget{ref-rothmanDeclineActiveSchool2018a}{}%
 Rothman, L., Macpherson, A.K., Ross, T., Buliung, R.N., 2018. The
-decline in active school transportation (AST): A systematic review of
-the factors related to AST and changes in school transport over time in
-North America. Preventive Medicine 111, 314--322.
+decline in active school transportation ({AST}): A systematic review of
+the factors related to {AST} and changes in school transport over time
+in {North America}. Preventive Medicine 111, 314--322.
 doi:\href{https://doi.org/10.1016/j.ypmed.2017.11.018}{10.1016/j.ypmed.2017.11.018}
@@
 Schoeppe, S., Duncan, M.J., Badland, H.M., Oliver, M., Browne, M., 2015.
-Associations between children׳s active travel and levels of physical
+Associations between children's active travel and levels of physical
 activity and sedentary behavior. Journal of Transport \& Health 2,
@@
 \leavevmode\hypertarget{ref-sharminAssociationBuiltEnvironment2017}{}%
-Sharmin, S., Kamruzzaman, M., 2017. Association between the built
+Sharmin, S., Kamruzzaman, Md., 2017. Association between the built
 environment and children's independent mobility: A meta-analytic review.
@@
 2020. Factors affecting parental safety perception, satisfaction with
-school travel and mood in primary school children in the Netherlands.
+school travel and mood in primary school children in the {Netherlands}.
 Journal of Transport \& Health 16, 100837.
@@
 \leavevmode\hypertarget{ref-weathersDevelopmentsFramingClimate2016}{}%
-Weathers, M.R., Kendall, B.E., 2016. Developments in the Framing of
-Climate Change as a Public Health Issue in US Newspapers. Environmental
-Communication 10, 593--611.
+Weathers, M.R., Kendall, B.E., 2016. Developments in the {Framing} of
+{Climate Change} as a {Public Health Issue} in {US Newspapers}.
+Environmental Communication 10, 593--611.
 doi:\href{https://doi.org/10.1080/17524032.2015.1050436}{10.1080/17524032.2015.1050436}
@@
 
+\end{CSLReferences}
+
 \end{document}

### 2021-12-01 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Discussion and conclusion completed, references updated

@@
 date: "`r Sys.Date()`"
-bibliography: mybibfile.bib
+bibliography: bibliography.bib
 linenumbers: false
@@
 
-Rates of walking and bicycling to school, commonly known as active school travel (AST), have been declining in Canada and the United States for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013], Denmark [@jensenHowObtainHealthy2008], and Japan [@waygoodChapterSixteenJapan2020].
+Rates of walking and bicycling to school, commonly known as active school travel (AST), have been declining in Canada and the United States for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013], Denmark [@jensenHowObtainHealthy2008], and Japan [@waygoodJapanMaintainingHigh2020].
 However, the appetite for AST may be high in many Canadian communities.
-For instance, 40% of children in a study conducted in Toronto, Ontario who are driven to school would like to travel by bicycle instead [@laroucheRatherBikeSchool2016a].
+For instance, 40% of children in a study conducted in Toronto, Ontario who are driven to school would like to travel by bicycle instead [@laroucheRatherBikeSchool2016].
 But the study reported that less than 3% actually do, despite the vast majority having access to a bicycle and living within a short and bikeable distance to school.
@@
 Green Communities Canada runs the program, called _Ontario Active School Travel_, and determines the projects that will be funded with their support [@GreenCommunities2016].
-As of December 2021, OAST has funded and provided resources for over 20 projects across Ontario.
+As of December 2021, OAST has awarded over 2 million Canadian dollars and provided resources for over 25 projects across Ontario.
 Many communities implemented school travel planning (STP), along with encouragement activities like walking school buses or developed resources for schools and parents, among other actions [see @GreenCommunitiesProjects].
@@
 Being driven to school reduces community interactions for children which may impact their social wellbeing [@waygoodChildrenTravelIncidental2015], whereas walking and bicycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021].
-This is something that children highly value about travel [@zwertsHowChildrenView2010a] and indicates that social connections through travel are important for their wellbeing.
+This is something that children highly value about travel [@zwertsHowChildrenView2010] and indicates that social connections through travel are important for their wellbeing.
 AST also provides opportunities for children to engage with the natural environment [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015] which can improve their mental or emotional wellbeing.
@@
 At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018] as parents typically escort younger children.
-There is some evidence that gender is a determinant of AST [@larsenInfluencePhysicalEnvironment2009], with boys being more likely to travel using active modes than girls, although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
+There is evidence that gender is a determinant of AST, with boys being more likely to travel using active modes than girls, although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
 Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], which indicates that shifting parental perceptions and habits is important.
 Convenience and inclement weather have been cited by parents as barriers to AST [@buliungSchoolTravelPlanning2011].
-Parental perceptions of the built or school environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and their children's skills [@ghekiereInsightsChildrenIndependent2017] also influence whether they allow their children to walk or bicycle to school.
+Parental perceptions of the built or school environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and their children's skills [@mammenUnderstandingDriveEscort2012] also influence whether they allow their children to walk or bicycle to school.
 
 Distance between home and school is most strongly associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
-Many studies have also found that the quality of the built environment along the route to school and around the school site [@ikedaAssociationsChildrenActive2018; @kimBuiltNaturalEnvironmental2020; @rothmanActiveSchoolTransportation2021] and provision of active travel infrastructure [@chenPromotingActiveStudent2018a; @pontEnvironmentalCorrelatesChildren2009] facilitate AST.
+Many studies have also found that the quality of the built environment along the route to school and around the school site [@ikedaAssociationsChildrenActive2018; @rothmanActiveSchoolTransportation2021] and provision of active travel infrastructure [@chenPromotingActiveStudent2018; @pontEnvironmentalCorrelatesChildren2009] facilitate AST.
 Canadian youth report that they feel most safe bicycling on streets in their neighbourhood or that have low volumes of traffic [@TACbikeinfra2020].
@@
 The latter are a unique group of entities sanctioned by Ontario's Ministry of Education in Ontario 2006.
-Each consortium involves a collaboration between regions and school boards; the consortium's objective is to deliver more efficient and timely transportation services to schools in each region [@ministryeducation2006].
+Each consortium involves a collaboration between regions and school boards; the consortium's objective is to deliver more efficient and timely transportation services to schools in each region.
 Non-profit organizations, police services, and advocacy groups are other stakeholders who often play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all initiatives across Ontario.
@@
     booktabs = TRUE,
-    caption = "\\label{tab:policy-concordance}CAPTION THIS TABLE") %>%
+    caption = "\\label{tab:policy-concordance}The context of key terms that were identified as common bigrams.") %>%
   kable_paper(full_width = F) %>%
@@
 ```{r topics-academic, include=FALSE, cache=TRUE}
-# DO NOT RUN EVERY TIME - takes approximately 20 minutes
-
-#academic_lda_num <- FindTopicsNumber(
-  #academic_dtm, 
-  #topics = seq(from = 2, to = 25, by = 1),
-  #metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
-  #method = "Gibbs")
+#DO NOT RUN EVERY TIME - takes approximately 20 minutes
+
+academic_lda_num <- FindTopicsNumber(
+  academic_dtm, 
+  topics = seq(from = 2, to = 25, by = 1),
+  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  method = "Gibbs")
   #control = list(seed = 77),
@@
 FindTopicsNumber_plot(policy_lda_num)
-#FindTopicsNumber_plot(academic_lda_num)
+FindTopicsNumber_plot(academic_lda_num)
 
@@
 
-academic_lda <- LDA(academic_dtm, k = 17, method = "Gibbs", control = NULL, model = NULL)
+academic_lda <- LDA(academic_dtm, k = 11, method = "Gibbs", control = NULL, model = NULL)
 ```
@@
 
-```{r policy-terms, echo=FALSE, out.width="1\\linewidth", fig.cap="\\label{fig:policy-terms}CAPTION THIS FIGURE"}
+```{r policy-terms, echo=FALSE, out.width="1\\linewidth", fig.cap="\\label{fig:policy-terms}Topics identified in the policy corpus according to clusters of words."}
 policy_top_terms <- policy_topics %>%
@@
 
-```{r academic-terms, echo=FALSE, out.width="1\\linewidth", cache=TRUE, fig.cap="\\label{fig:academic-terms}CAPTION THIS FIGURE"}
+```{r academic-terms, echo=FALSE, out.width="1\\linewidth", cache=TRUE, fig.cap="\\label{fig:academic-terms}Topics identified in the academic corpus according to clusters of words."}
 
@@
 After running the LDA model for the academic corpus, it was too difficult to interpret a minimum of 17 topics based on the clusters of words that were identified.
-We experimented with the model by adjusting the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap.
+We experimented with the model by adjusting and evaluating the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap.
 Figures \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main terms that are associated with the topics found in each corpus.
 
-In the policy corpus, we interpret the following topics based on the cluster of words: (1) resources for walking, (2) busing information and eligibility; (3) benefits of active travel; (4) bicycling and the environment; and (5) supporting active travel.
+In the policy corpus, we interpret the following topics based on the cluster of words: (1) resources for walking; (2) walking; (3) supporting active travel; (4) bicycling and the environment; (5) benefits of active travel; (6) safety; and (7) busing information and eligibility.
 These topics indicate that STP stakeholder groups are sending the message that walking and bicycling to school are healthy travel modes for students, particularly as a means to get physical activity.
 We also found that there is information shared to support parents and students in using active modes to school such as the availability of cycling lanes or route tips for walking.
+STP stakeholder groups are appear to be addressing the issue of safety.
 
 The academic corpus has a higher number of topics likely due to the volume of papers that were sourced.
-The following topics were identified based on the clusters of words: (1) __unclear__ (2) AST in Ontario and Canada; (3) __unclear__; (4) children’s independent mobility; (5) safe routes to school programs; (6) commuting and distance; (7) density in the built environment and walking routes; (8) __unclear__; (9) walking interventions; (10) bicycling influences; (11) interpersonal and household influences on trips; (12) behaviours and attitudes; (13) __unclear__; (14) __unclear__; (15) walking distance; (16) __unclear__;  (17) physical activity measures or results; (18) bicycling attitudes; and (19) __unclear__.
+The following topics were identified based on the clusters of words: (1) built environment (2) walking distance; (3) AST interventions; (4) parental barriers to walking; (5) behaviours and attitudes; (6) bicycling; (7) social environment; (8) children's independent mobility; (9) modeling trip choice; (10) adolescents and physical activity; and (11) safe routes to school programs.
+This corpus reflects a broader range of topics than the policy corpus.
 
@@
 STP stakeholder groups seem to be communicating that AST is possible and safe as a result of improvements to the built environment and available resources for parents and children.
-A final focus in the policy documents is on various efforts that are underway to support active travel including route planning.
+A final focus in the policy documents is on various efforts that are underway to support AST including route planning.
+A few examples include:
 
@@
 Using topic modelling, we analyzed how AST is framed in documents available to the general public on the websites of STP stakeholder groups in Ontario.
-We found that AST is primarily framed as beneficial to the health and wellbeing of children and to environmental sustainability.
+We found that AST is primarily framed to parents as beneficial to the health and wellbeing of children and to environmental sustainability.
 This was confirmed by the most common bigrams identified in the policy corpus, as well as the topics identified by the LDA model.
-The policy documents adequately reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015].
-STP stakeholder groups also communicate that increasing AST may reduce traffic near and around schools which could alleviate parental concerns about traffic safety.
-The potential outcomes of increased AST are highlighted which may be persuasive arguments to motivate behaviour change, which is the secondary frame of AST that we interpreted based on the LDA models.
-
-The proposed solutions to the problem of declining AST that are communicated to the general public are mostly educational (e.g., safety tips or maps of safe routes) and engineering changes (e.g., traffic calming or bicycle lanes).
-These solutions have to sufficiently address real and perceived concerns that pose barriers to AST in order to encourage adoption.
-In most documents, the emphasis is on providing parents with resources that help them switch modes for the school commute and/or on reassuring them that the built environment has become safer and friendlier to active travelers.
-
-However, the policy documents noticeably lacked a focus on individual and household level determinants of AST.
+The policy documents adequately reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance and cognitive development need to be studied further to produce stronger evidence [@westmanChapterThreeTravel2020].
+STP stakeholder groups also communicate that increasing AST may reduce traffic near and around schools.
+This presumably is communicated to alleviate parental concerns about traffic and safety [@eversParentSafetyPerceptions2014; @mammenUnderstandingDriveEscort2012; @rothmanAssociationsParentsPerception2015; @wilsonUnderstandingChildParent2018] or reduce the frequency of risky behaviours from drivers around schools [@rothmanSchoolEnvironmentStudent2017].
+However, the documents do not explain why declining rates of AST are a problem for the particular community or convey any urgency to this issue so that it attracts the attention of parents, the general public, or policy makers.
+Communicating the potential outcomes of increased AST may be persuasive arguments to motivate behaviour change, but these documents do not appear to encourage parents or the general public to view their behaviour as problematic or unhealthy for their children's development.
+For example, Canadian parents who escort their children to school have reported concerns about traffic volume around schools [@mammenUnderstandingDriveEscort2012], but may not recognize that their own behaviour contributes to the problem that is perceived to prevent their child from safely walking or bicycling to school [@collinsSafeJourneysEnterprising2001].
+
+The secondary frame of AST that we interpreted based on the LDA model is the opportunity or prospect of behaviour change.
+STP stakeholder groups identified different ways that parents could encourage or support their child(ren) to commute to school by using active modes.
+Some school boards and municipalities also shared resources such as walking tip sheets and guidance for starting a walking school bus.
+Other advice included dropping children off one or two blocks away from school so that they could walk or bike part of the trip.
+The general emphasis is communicating information that could change parental perceptions about the ease of their children using active modes to school, which may be seen by STP stakeholder groups as a "modifiable" factor [see @riaziCorrelatesChildrenIndependent2019].
+In turn, this could encourage parents to modify their routines and incorporate opportunities for their children to use active modes to school.
+
+We found that interpersonal behaviour changes achieved through educational strategies and engineering changes (e.g., traffic calming measures, reduced speed limits, etc.) are communicated to the general public as potential solutions to address the decline of AST.
+This reflects findings from the AST literature [@panterAttitudesSocialSupport2010], but these solutions have to sufficiently address real and perceived barriers from parents about the household environment and the built environment (see Section 2.2).
+In most documents, STP stakeholder groups provide parents with resources that help them switch modes for the school commute and/or on reassure them that the built environment has become safer and friendlier to active travelers as a result of infrastructure or policy improvements.
+As previously noted, the documents do not appear to present a strong "call to action" that urges behaviour change for parents or the general public, which may affect the success of STP interventions.
+On the other hand, the emphasis on engineering changes may reflect the strong engagement of the "policy stream" [@kingdonAgendasAlternativesPublic1984] and the feasible options to address the problem, since engineering staff and municipal representatives are common STP stakeholders [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015].
+
+Given the range of factors that influence AST in a Canadian setting [_inter alia_, see @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], STP stakeholder groups must decide which points of intervention that they can reasonably have some influence towards.
+This would also depend on the local context to ensure that barriers to AST as perceived by parents are addressed.
+It could be that STP stakeholder groups perceive to have more control over micro-scale elements of the built environment, like traffic calming measures or speed limits, rather "non-modifiable" factors like street density or land use mix.
+It would certainly be much more difficult for STP stakeholder groups to influence the number of trips to different destinations that households need to make or to intervene in residential location, which affects distance to school.
+A focus on changing parental perceptions is recommended by many scholars since parents are the "gatekeeper" for children's mobility, but the information communicated by STP stakeholder groups in Ontario should reflect a broader range of factors that influence AST.
+
+## 6.2. Implications for school travel planning
+
+There is also a noticeable lack of focus on individual and interpersonal determinants of AST in the policy documents.
 For example, the role of convenience and inclement weather in shaping household travel decisions [@buliungSchoolTravelPlanning2011] or the age at which children become allowed to travel by active modes or independently [@mammenUnderstandingDriveEscort2012] were not discussed.
-Given the range of factors that influence AST in a Canadian setting [_inter alia_, see @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], STP stakeholder groups must decide which points of intervention that they can reasonably have some influence towards.
-This should also depend on the local context so that barriers to AST as perceived by parents are addressed.
-It could be that STP stakeholder groups perceive to have more control over the micro-scale elements of the built environment, like traffic calming, rather than the ability to influence the number of trips to different destinations that households need to make.
-STP stakeholders are also unable to intervene in residential location, which affects distance to school.
-
-To increase rates of walking and bicycling independently to school, Riazi et al.
-[-@riaziCorrelatesChildrenIndependent2019] state: "it will be vital for interventions to target modifiable factors, including children's and parents' perceptions of their social environment." We argue that STP messaging should also target multiple modifiable factors, in addition to the health and environmental benefits.
-Parents play the important role of "gatekeeper" by either granting or restricting their child's mobility [@sharminAssociationBuiltEnvironment2017].
-For this reason, stakeholders involved in STP should produce more information that specifically responds to parents' perceived barriers and challenges.
+The desire to escort children to school, which has been noted by parents as a reason to continue driving [@westmanWhatDrivesThem2017], is also not adequately addressed by STP stakeholder groups.
+The complexity of travel arrangements that must be coordinated by households [see @buliungLivingJourneySchool2021] and the dominant parenting culture to protect children from risk [@riaziChildrenIndependentMobility2018] are likewise overlooked.
+STP stakeholders may wish to emphasize to parents that older children have greater traffic safety and cognitive abilities to navigate their own routes to school, which could encourage parents to develop their child(ren)'s travel skills over time.
+Additional attention should be paid to the reasons why parents perceive driving to be more convenient.
+
+Coming back to Kingdon's Multiple Streams Framework [-@kingdonAgendasAlternativesPublic1984], we posited that STP stakeholder groups need to raise awareness about the AST issue among parents and the general public through the problem stream.
+This could influence perceptions about the issue and encourage behaviour change.
+Based on the policy documents, it is not obvious that AST has declined significantly over the past few decades in Canada or that this issue merits urgent attention.
+Many municipalities, schools, and transportation consortia in Ontario use similar content in their public documents about AST.
+It would be worthwhile for STP stakeholder groups to frame the decline of AST as a "problem" worth addressing with information specific to each local context.
+STP stakeholders also need to ensure that their communication accounts for the ways in which Canadian parents perceive the built environment in different ways than planners [see @buliungLivingJourneySchool2021].
+If there is "conceptual asymmetry" as Buliung et al.
+[-@buliungLivingJourneySchool2021] identified, the materials disseminated by STP stakeholders may not resonate or reach parents.
+Future research or STP activities should investigate how parents or the general public respond to messages or information that encourages the adoption of AST and evaluate how effective they are to motivate behaviour change.
+It would be helpful to know which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST.
+This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.
+
+Although the "policy stream" appears to have been adequately engaged in Ontario communities, it could be that the decline of AST has not been sufficiently framed as "problematic" to warrant more widespread awareness or solutions.
+If Canadian STP stakeholder groups wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different material that communicates why this issue is important to the general public, regardless of whether they currently have children commuting to/from school.
+The "political steam" could also be further engaged by working with advocacy groups who could attract more support from a broader coalition of individuals.
+
+Finally, Rothman et al.
+[-@rothmanDeclineActiveSchool2018] note that local solutions to address specific school challenges are needed, and we extend this recommendation to include local context in STP messaging about AST.
+Instead of generic content about AST, stakeholders involved in STP should produce more information that specifically responds to parents' perceived barriers and challenges that were identified in that local context.
 For example, STP materials could explain how known concerns in a particular municipality or school area have been addressed through local solutions.
-
-## 6.2. Implications for school travel planning
-
-Many municipalities, schools, and transportation consortia use similar content in their public documents about AST.
-It would be worthwhile for STP stakeholders to adapt generic content so that it is more specific to factors associated with AST or parental perceptions about barriers to AST in the local context.
-Rothman et al.
-[-@rothmanDeclineActiveSchool2018a] note that local solutions to address specific school challenges are worthwhile, and we extend this recommendation to include local context in STP messaging about AST.
+This could reflect that solutions have been identified based on what was heard from the community.
 
 ## 6.3. Limitations
+
+A limitation of this study is that we only analyzed texts that were easily accessible to the general public on the websites of STP stakeholder groups in Ontario.
+Parents likely receive information about AST directly from schools, which may contain more content that reflects the local barriers to AST.
 
@@
 
-## 7.1. Future research
-
-Future studies may investigate how parents and policy makers outside the field of public health respond to the ways in which AST is framed in STP documents.
-It would be helpful to know which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST.
-This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.
-
-Acknowledgments
-===================
-
-This research was completed using open software, and the authors wish to acknowledge the developers of the following `R` packages: `dplyr` [@R-dplyr], `ggraph` [@R-ggraph], `ggplot2` [@R-ggplot2], `igraph` [@R-igraph], `pdftools` [@R-pdftools], `readr` [@R-readr], `reshape2` [@R-reshape2], `stringr` [@R-stringr], `text2vec` [@R-text2vec], `textdata` [@R-textdata], `tidyr` [@R-tidyr], `tidytext` [@R-tidytext], `tm` [@R-tm], `tools` [@R-tools], `topicmodels` [@R-topicmodels], `widyr` [@R-widyr], `word2vec` [@R-word2vec], `wordcloud` [@R-wordcloud], `DiagrammeR` [@R-diagrammeR], and `kableextra` [@R-kableextra].
+We used text mining and topic modelling to examine how different school travel planning stakeholder (STP) groups in Ontario frame the issue of AST.
+STP stakeholder groups frame AST as a health and environmental issue that can be addressed through household behaviour change and engineering solutions.
+Policy documents reveal that STP stakeholder groups are focusing on "modifiable factors" such as parental perceptions or micro-scale elements in the built environment to increase rates of AST.
+However, AST may not be framed sufficiently as a "problem" that requires urgent intervention, which may impact how parents respond to behaviour change initiatives and limit awareness in the general public.
+In their public materials about AST, STP stakeholder groups should present solutions for a broader range of factors that influence AST and emphasize why AST rates should increase in local communities.
 

### 2021-12-01 AST-Framing-Ontario/AST-Framing-Ontario.tex
Discussion and conclusion completed, references updated

@@
 % Pandoc citation processing
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 
-  \title{The framing of active school travel in Ontario, Canada as a
-health and built environment issue}
+  \title{The framing of active school travel in Ontario, Canada as a health and
+built environment issue}
     \author[Some Department]{Author 1\corref{1}}
@@
    \ead{author6@example.com} 
-      \address[Some Department]{Department, Street, City, Province,
-Postal Code}
-    \address[Another University]{Department, Street, City, Province,
-Postal Code}
+      \address[Some Department]{Department, Street, City, Province, Postal Code}
+    \address[Another University]{Department, Street, City, Province, Postal Code}
     \address[Some Institute]{Street, City, Province, Postal Code}
-    \address[Some University]{Department, Street, City, Province, Postal
-Code}
+    \address[Some University]{Department, Street, City, Province, Postal Code}
       \cortext[1]{Corresponding Author}
@@
 school travel (AST), have been declining in Canada and the United States
-for decades (\textbf{rothmanDeclineActiveSchool2018?}), with levels much
-lower than other developed countries like The Netherlands
-(\textbf{vangoeverdenSchoolTravelBehaviour2013?}), Denmark
-(\textbf{jensenHowObtainHealthy2008?}), and Japan
-(\textbf{waygoodChapterSixteenJapan2020?}). However, the appetite for
-AST may be high in many Canadian communities. For instance, 40\% of
-children in a study conducted in Toronto, Ontario who are driven to
-school would like to travel by bicycle instead
-(\textbf{laroucheRatherBikeSchool2016a?}). But the study reported that
-less than 3\% actually do, despite the vast majority having access to a
-bicycle and living within a short and bikeable distance to school.
-Another study based in London, Ontario reported similar findings with
-respect to children's preference for active travel
-(\textbf{larsenRouteBasedAnalysisCapture2012?}). From a public health
-perspective, this represents a huge opportunity to improve health and
-wellbeing if more children could use active modes to school.
+for decades (Rothman et al., 2018), with levels much lower than other
+developed countries like The Netherlands (van Goeverden and de Boer,
+2013), Denmark (Jensen, 2008), and Japan (Waygood and Taniguchi, 2020).
+However, the appetite for AST may be high in many Canadian communities.
+For instance, 40\% of children in a study conducted in Toronto, Ontario
+who are driven to school would like to travel by bicycle instead
+(Larouche et al., 2016). But the study reported that less than 3\%
+actually do, despite the vast majority having access to a bicycle and
+living within a short and bikeable distance to school. Another study
+based in London, Ontario reported similar findings with respect to
+children's preference for active travel (Larsen et al., 2012). From a
+public health perspective, this represents a huge opportunity to improve
+health and wellbeing if more children could use active modes to school.
 
@@
 \emph{Ontario Active School Travel}, and determines the projects that
-will be funded with their support (\textbf{GreenCommunities2016?}). As
-of December 2021, OAST has funded and provided resources for over 20
-projects across Ontario. Many communities implemented school travel
-planning (STP), along with encouragement activities like walking school
-buses or developed resources for schools and parents, among other
-actions (see \textbf{GreenCommunitiesProjects?}). In this context, STP
-is a popular ``school-specific'' intervention led by a facilitator that
-brings together a committee of stakeholders from diverse sectors
-including education, planning, transportation, and public health to
-develop action plans (\textbf{buliungSchoolTravelPlanning2011?};
-\textbf{mammenSchoolTravelPlanning2014?}). The five-step process
-involves identifying barriers to AST based on the local context and
-implementing approaches or activities following the 5 E's that alleviate
-concerns about AST and make AST safer and more convenient
-(\textbf{buliungSchoolTravelPlanning2011?};
-\textbf{langUnderstandingModalChoice2011?}).
+will be funded with their support (Canada, 2020a). As of December 2021,
+OAST has awarded over 2 million Canadian dollars and provided resources
+for over 25 projects across Ontario. Many communities implemented school
+travel planning (STP), along with encouragement activities like walking
+school buses or developed resources for schools and parents, among other
+actions (see Canada, 2020b). In this context, STP is a popular
+``school-specific'' intervention led by a facilitator that brings
+together a committee of stakeholders from diverse sectors including
+education, planning, transportation, and public health to develop action
+plans (Buliung et al., 2011; Mammen, M. R. Stone, Ron Buliung, et al.,
+2014). The five-step process involves identifying barriers to AST based
+on the local context and implementing approaches or activities following
+the 5 E's that alleviate concerns about AST and make AST safer and more
+convenient (Buliung et al., 2011; Lang et al., 2011).
 
@@
 how walking and bicycling to school are perceived. Gamson and Modigliani
-(\textbf{gamsonChangingCulture1987?}) define a frame as a ``central
-organizing idea or story line that provides meaning'' to a particular
-phenomenon. A frame can enable individuals ``to locate, perceive,
-identify, and label'' information pertaining to various dimensions of an
-issue (Goffman, 1974). Therefore, stakeholder groups involved in STP
-efforts can play a role in shaping public perception about AST in such a
-way that it attracts greater attention and becomes a ``problem'' that
-needs to be addressed through behaviour change or by new policies. We
-also contend that the ways in which the AST issue is framed can affect
-the policy process, as outlined in Kingdon's
-(\textbf{kingdonAgendasAlternativesPublic1984?}) Multiple Streams
-Framework (MSF), through all three streams (i.e., problem, policy, and
-politics). This framing can ultimately impact financial contributions
-and potential solutions to address the decline of AST in Canada.
+(1987) define a frame as a ``central organizing idea or story line that
+provides meaning'' to a particular phenomenon. A frame can enable
+individuals ``to locate, perceive, identify, and label'' information
+pertaining to various dimensions of an issue (Goffman, 1974). Therefore,
+stakeholder groups involved in STP efforts can play a role in shaping
+public perception about AST in such a way that it attracts greater
+attention and becomes a ``problem'' that needs to be addressed through
+behaviour change or by new policies. We also contend that the ways in
+which the AST issue is framed can affect the policy process, as outlined
+in Kingdon's (1984) Multiple Streams Framework (MSF), through all three
+streams (i.e., problem, policy, and politics). This framing can
+ultimately impact financial contributions and potential solutions to
+address the decline of AST in Canada.
 
@@
 evidence that children who actively commute to school earn physical and
-mental health benefits. Faulkner et al. (2009) concluded from their
+mental health benefits. Faulkner et al.~(2009) concluded from their
 systematic review that children who travel on foot or by bicycle to
 school generally have higher levels of physical activity than their
-peers who are driven to school. However, Schoeppe et al. (2015) reported
+peers who are driven to school. However, Schoeppe et al.~(2015) reported
 no association between AST and physical activity. This relationship
@@
 1000-1600 metres to school has been found to contribute to overall
-levels of physical activity for boys
-(\textbf{faulknerSchoolTravelChildren2013?}). The daily routine of
-travelling to school can be a good opportunity for children to regularly
-build physical activity into their schedule
-(\textbf{mitraIndependentMobilityMode2013?}). Research has also shown
-that using active modes to school contributes to improvements in
-cardiovascular fitness
-(\textbf{borrestadExperiencesRandomisedControlled2012?}).
+levels of physical activity for boys (Faulkner et al., 2013). The daily
+routine of travelling to school can be a good opportunity for children
+to regularly build physical activity into their schedule (Mitra, 2013).
+Research has also shown that using active modes to school contributes to
+improvements in cardiovascular fitness (Børrestad et al., 2012).
 
 More recently, there has been literature exploring the link between
-transport and children's wellbeing
-(\textbf{waygoodTransportChildrenWellbeing2020?}), with relevant
+transport and children's wellbeing (Waygood et al., 2020), with relevant
 applications to the study of travel satisfaction (van den Berg et al.,
-2020; \textbf{westmanChildrenTravelSchool2017?}). Being driven to school
-reduces community interactions for children which may impact their
-social wellbeing (\textbf{waygoodChildrenTravelIncidental2015?}),
-whereas walking and bicycling give children opportunities to socialize
-with friends or siblings
-(\textbf{michailChildrenExperiencesTheir2021?}). This is something that
-children highly value about travel
-(\textbf{zwertsHowChildrenView2010a?}) and indicates that social
-connections through travel are important for their wellbeing. AST also
-provides opportunities for children to engage with the natural
-environment (\textbf{fuscoUnderstandingChildrenPerceptions2012?};
-\textbf{romeroChildrenExperiencesEnjoyment2015?}) which can improve
-their mental or emotional wellbeing.
+2020; Westman, Olsson, et al., 2017). Being driven to school reduces
+community interactions for children which may impact their social
+wellbeing (Waygood and Friman, 2015), whereas walking and bicycling give
+children opportunities to socialize with friends or siblings (Michail et
+al., 2021). This is something that children highly value about travel
+(Zwerts et al., 2010) and indicates that social connections through
+travel are important for their wellbeing. AST also provides
+opportunities for children to engage with the natural environment (Fusco
+et al., 2012; Romero, 2015) which can improve their mental or emotional
+wellbeing.
 
@@
 Factors that influence AST have been presented and organized using a
-socio-ecological model (SEM)
-(\textbf{mitraIndependentMobilityMode2013?}) or systems model
-(\textbf{badlandDevelopmentSystemsModel2016?}) whereby children's travel
-behaviour is understood within the context of their household, social,
-neighbourhood, and policy environments. Individual characteristics of
-the child are also determinants. The SEM comes from the field of public
-health and is a useful framework for understanding complex health
-behaviours, including travel habits such as walking or bicycling to
-school, because it identifies multiple determinants that need to be
-addressed by interventions to facilitate behaviour change. The consensus
-in the literature is that various factors are interrelated and that
+socio-ecological model (SEM) (Mitra, 2013) or systems model (Badland et
+al., 2016) whereby children's travel behaviour is understood within the
+context of their household, social, neighbourhood, and policy
+environments. Individual characteristics of the child are also
+determinants. The SEM comes from the field of public health and is a
+useful framework for understanding complex health behaviours, including
+travel habits such as walking or bicycling to school, because it
+identifies multiple determinants that need to be addressed by
+interventions to facilitate behaviour change. The consensus in the
+literature is that various factors are interrelated and that
 interventions should target multiple levels in order to increase levels
-of healthy and physically active modes of travel to school
-(\textbf{mitraIndependentMobilityMode2013?}). Rather than describing an
-extensive list of factors that influence AST and mode choice in Canada,
-which has been covered elsewhere (e.g., Mammen et al., 2012; Wilson et
-al., 2018; \textbf{mitraIndependentMobilityMode2013?};
-\textbf{rothmanDeclineActiveSchool2018?}), we briefly discuss a few
-potentially modifiable determinants that may be targeted for change
-through STP.
+of healthy and physically active modes of travel to school (Mitra,
+2013). Rather than describing an extensive list of factors that
+influence AST and mode choice in Canada, which has been covered
+elsewhere (e.g., Mammen et al., 2012; Mitra, 2013; Rothman et al., 2018;
+Wilson et al., 2018), we briefly discuss a few potentially modifiable
+determinants that may be targeted for change through STP.
 
 At the individual level, older child age is often associated with AST
-(Mammen et al., 2012; Wilson et al., 2018;
-\textbf{starkExploringIndependentActive2018?}) as parents typically
-escort younger children. There is some evidence that gender is a
-determinant of AST (\textbf{larsenInfluencePhysicalEnvironment2009?}),
-with boys being more likely to travel using active modes than girls,
-although this is not a strong or consistent finding (Schoeppe et al.,
-2015; \textbf{rothmanDeclineActiveSchool2018?}). Children's mode choice
-to school is strongly influenced by their parents' travel behaviours and
-the complexity of their household's travel needs (Buliung et al., 2021),
-which indicates that shifting parental perceptions and habits is
-important. Convenience and inclement weather have been cited by parents
-as barriers to AST (\textbf{buliungSchoolTravelPlanning2011?}). Parental
+(Mammen et al., 2012; Stark et al., 2018; Wilson et al., 2018) as
+parents typically escort younger children. There is evidence that gender
+is a determinant of AST, with boys being more likely to travel using
+active modes than girls, although this is not a strong or consistent
+finding (Rothman et al., 2018; Schoeppe et al., 2015). Children's mode
+choice to school is strongly influenced by their parents' travel
+behaviours and the complexity of their household's travel needs (Buliung
+et al., 2021), which indicates that shifting parental perceptions and
+habits is important. Convenience and inclement weather have been cited
+by parents as barriers to AST (Buliung et al., 2011). Parental
 perceptions of the built or school environment (De Meester et al., 2014;
-Panter et al., 2010) and their children's skills (Ghekiere et al., 2017)
+Panter et al., 2010) and their children's skills (Mammen et al., 2012)
 also influence whether they allow their children to walk or bicycle to
@@
 Distance between home and school is most strongly associated with AST
-(Ikeda et al., 2018; Mammen et al., 2012; Pont et al., 2009;
-\textbf{rothmanDeclineActiveSchool2018?}) with less AST reported among
-children who have to travel farther to school. Many studies have also
-found that the quality of the built environment along the route to
-school and around the school site (Ikeda et al., 2018; Kim and Lee,
-2020; \textbf{rothmanActiveSchoolTransportation2021?}) and provision of
-active travel infrastructure (Pont et al., 2009;
-\textbf{chenPromotingActiveStudent2018a?}) facilitate AST. Canadian
-youth report that they feel most safe bicycling on streets in their
-neighbourhood or that have low volumes of traffic
-(\textbf{TACbikeinfra2020?}). Finally, concerns about traffic and
-strangers have been reported by parents who drive their children to
-school (Mammen et al., 2012), which highlights that the volume and speed
-of cars can be a concern or deterrent for AST.
+(Ikeda et al., 2018; Mammen et al., 2012; Pont et al., 2009; Rothman et
+al., 2018) with less AST reported among children who have to travel
+farther to school. Many studies have also found that the quality of the
+built environment along the route to school and around the school site
+(Ikeda et al., 2018; Rothman et al., 2021) and provision of active
+travel infrastructure (Chen et al., 2018; Pont et al., 2009) facilitate
+AST. Canadian youth report that they feel most safe bicycling on streets
+in their neighbourhood or that have low volumes of traffic
+({\textbf{???}}). Finally, concerns about traffic and strangers have
+been reported by parents who drive their children to school (Mammen et
+al., 2012), which highlights that the volume and speed of cars can be a
+concern or deterrent for AST.
 
@@
 school site, and \emph{enforcement} of traffic speeds around schools
-(Mammen et al., 2014; \textbf{langUnderstandingModalChoice2011?}). The
+(Lang et al., 2011; Mammen, M. R. Stone, G. Faulkner, et al., 2014). The
 first large-scale evaluation of STP as an intervention in Canada took
@@
 using parental surveys to measure changes in travel behaviour and
-perceptions (\textbf{buliungSchoolTravelPlanning2011?}). Since then,
-there have been other assessments of both the efficacy of STP
-(Buttazzoni et al., 2019; Mammen et al., 2014) and the process of
-implementing such programs in Ontario (Buttazzoni et al., 2018;
-\textbf{mammenPuttingSchoolTravel2015?}). STP facilitators have
-recommended that additional time and resources are needed to improve the
-efficacy of STP (\textbf{mammenPuttingSchoolTravel2015?}), which
-highlights that long-term and sustained efforts driven at the policy
-level are required to address declining rates of AST.
+perceptions (Buliung et al., 2011). Since then, there have been other
+assessments of both the efficacy of STP (Buttazzoni et al., 2019;
+Mammen, M. R. Stone, G. Faulkner, et al., 2014) and the process of
+implementing such programs in Ontario (Buttazzoni et al., 2018; Mammen
+et al., 2015). STP facilitators have recommended that additional time
+and resources are needed to improve the efficacy of STP (Mammen et al.,
+2015), which highlights that long-term and sustained efforts driven at
+the policy level are required to address declining rates of AST.
 
@@
 children's travel mode to school. STP activities heavily focus on
-education or encouragement (Buttazzoni et al., 2018; Mammen et al.,
-2014; \textbf{buliungSchoolTravelPlanning2011?}), but parents may not
-always be receptive to the goals of STP and may be resistant to
+education or encouragement (Buliung et al., 2011; Buttazzoni et al.,
+2018; Mammen, M. R. Stone, G. Faulkner, et al., 2014), but parents may
+not always be receptive to the goals of STP and may be resistant to
 behaviour change (see Buttazzoni et al., 2018). Parents have been found
@@
 travel (Buliung et al., 2021). This is also true when it comes to other
-factors like convenience of different modes to school
-(\textbf{langUnderstandingModalChoice2011?}). STP stakeholder groups
-must pay special attention to parents' understanding of the decline of
-AST as a problem, which may affect their receptivity to proposed
-solutions.
+factors like convenience of different modes to school (Lang et al.,
+2011). STP stakeholder groups must pay special attention to parents'
+understanding of the decline of AST as a problem, which may affect their
+receptivity to proposed solutions.
 
 The ``central organizing idea or story line'' of AST, to apply the
-definition from Gamson and Modigliani
-(\textbf{gamsonChangingCulture1987?}), could also affect broader support
-in the community. Municipal representatives are perceived to be
+definition from Gamson and Modigliani (1987), could also affect broader
+support in the community. Municipal representatives are perceived to be
 instrumental but the involvement of other stakeholder groups (e.g.,
@@
 the provincial government. The support from a range of municipal
-representatives (see Buttazzoni et al., 2018;
-\textbf{mammenPuttingSchoolTravel2015?}) demonstrates that the ``policy
-stream'' (see \textbf{kingdonAgendasAlternativesPublic1984?}) has been
+representatives (see Buttazzoni et al., 2018; Mammen et al., 2015)
+demonstrates that the ``policy stream'' (see Kingdon, 1984) has been
 well engaged. It is unknown to what degree the general public (i.e.,
@@
 the consortium's objective is to deliver more efficient and timely
-transportation services to schools in each region
-(\textbf{ministryeducation2006?}). Non-profit organizations, police
-services, and advocacy groups are other stakeholders who often play a
-role in supporting AST and/or STP, but this study does not include any
-documents from these groups because they are not consistently
-participating in all initiatives across Ontario.
+transportation services to schools in each region. Non-profit
+organizations, police services, and advocacy groups are other
+stakeholders who often play a role in supporting AST and/or STP, but
+this study does not include any documents from these groups because they
+are not consistently participating in all initiatives across Ontario.
 
@@
 such as \emph{and} or \emph{the} as identified in a predetermined list
-by Lewis et al. (\textbf{R-tm?}) and other frequent terms in the
+by Lewis et al.~({\textbf{???}}) and other frequent terms in the
 documents like ``school'' and specific location names, were removed from
@@
 idea or story line that provides meaning'' to a public issue or
-phenomenon (\textbf{gamsonChangingCulture1987?}). Scholars in the field
-of political communications have proposed that communicators, such as
-the media or an institution, construct the narrative of a frame for
-policy positions or public issues in order to activate or restrict a
-particular response in the intended audience (Pan and Kosicki, 1993).
-Organized groups of stakeholders can employ similar methods to attract
-attention to particular issues. Framing can be used to position existing
-solutions as suitable to address particular issues (Mah et al., 2014),
-which may prevent the public from being aware of other policy approaches
-that challenge the status quo. The way policy issues are framed is
-ultimately important to understand because it plays a role in either
-altering or preserving the existing social perceptions. This, in turn,
-can affect whether issues are put on the agenda of policy makers and can
-determine which solutions are proposed to address the problem
-(\textbf{kingdonAgendasAlternativesPublic1984?}).
+phenomenon (Gamson and Modigliani, 1987). Scholars in the field of
+political communications have proposed that communicators, such as the
+media or an institution, construct the narrative of a frame for policy
+positions or public issues in order to activate or restrict a particular
+response in the intended audience (Pan and Kosicki, 1993). Organized
+groups of stakeholders can employ similar methods to attract attention
+to particular issues. Framing can be used to position existing solutions
+as suitable to address particular issues (Mah et al., 2014), which may
+prevent the public from being aware of other policy approaches that
+challenge the status quo. The way policy issues are framed is ultimately
+important to understand because it plays a role in either altering or
+preserving the existing social perceptions. This, in turn, can affect
+whether issues are put on the agenda of policy makers and can determine
+which solutions are proposed to address the problem (Kingdon, 1984).
 
@@
 different frames to guide the extent to which transport policies can be
-adapted to address climate change. In a recent paper
-(\textbf{reynardGrowthResilienceHow2021?}), framing analysis was applied
-to review the representation of issues such as mobility and social
-exclusion in municipal policies from four western Canadian cities under
-the current circumstances of climate change. The authors found four
-primary frames: ``The Growing City,'' ``If You Build It, They Will
-Come,'' ``Better City for All,'' and a ``the Resilient City''
-(\textbf{reynardGrowthResilienceHow2021?}). Each frame presented the
+adapted to address climate change. In a recent paper (Reynard et al.,
+2021), framing analysis was applied to review the representation of
+issues such as mobility and social exclusion in municipal policies from
+four western Canadian cities under the current circumstances of climate
+change. The authors found four primary frames: ``The Growing City'',
+``If You Build It, They Will Come'', ``Better City for All'', and a
+``the Resilient City'' (Reynard et al., 2021). Each frame presented the
 nature, opportunities, and challenges of climate change in different
@@
 text because it replaces the manual coding of topics that would normally
-take place to analyze or summarize textual data
-(\textbf{jacobiQuantitativeAnalysisLarge2016?}). In the data
-pre-processing phase, we tokenize the text in the documents and create a
-document-term matrix so that it is in the correct format for analysis.
-We primarily use the following packages: \texttt{tidytext}
-(\textbf{R-tidytext?}), \texttt{topicmodels} (\textbf{R-topicmodels?}),
-\texttt{word2vec} (\textbf{R-word2vec?}), and \texttt{wordcloud}
-(\textbf{R-wordcloud?}) to examine text in the documents that were
-sourced for this project. These packages have functions for determining
-the frequency of specific words in each document or relationships (e.g.,
+take place to analyze or summarize textual data (Jacobi et al., 2016).
+In the data pre-processing phase, we tokenize the text in the documents
+and create a document-term matrix so that it is in the correct format
+for analysis. We primarily use the following packages: \texttt{tidytext}
+({\textbf{???}}), \texttt{topicmodels} ({\textbf{???}}),
+\texttt{word2vec} ({\textbf{???}}), and \texttt{wordcloud}
+({\textbf{???}}) to examine text in the documents that were sourced for
+this project. These packages have functions for determining the
+frequency of specific words in each document or relationships (e.g.,
 pairs of adjacent terms called bigrams) and correlations between words.
@@
 communicated to the general public. Topic modelling is a popular method
-for analyzing text from social media platforms
-(\textbf{albalawiUsingTopicModeling2020?}) or news articles
-(\textbf{jacobiQuantitativeAnalysisLarge2016?}). We estimate latent
-Dirichlet allocation (LDA) models to classify both the STP and documents
-according to the topics that are contained within them. This method
-``treats each document as a mixture of topics, and each topic as a
-mixture of words'' (\textbf{silgeTextMining2021?}). The model's output
-is ``a set of topics consisting of clusters of words that co-occur in
-these documents according to certain patterns''
-(\textbf{jacobiQuantitativeAnalysisLarge2016?}). Researchers must then
-interpret the identified topics, as done after other methods of manual
-coding. We also compare the topics between the policy documents and the
-academic papers, and use our interpretation to answer the questions
-outlined above that guide this paper. This methodology is not familiar
-to many, so we describe in more detail below how we used specific
-functions and code in R to produce our results.
+for analyzing text from social media platforms (Albalawi et al., 2020)
+or news articles (Jacobi et al., 2016). We estimate latent Dirichlet
+allocation (LDA) models to classify both the STP and documents according
+to the topics that are contained within them. This method ``treats each
+document as a mixture of topics, and each topic as a mixture of words''
+(Silge and Robinson, 2021). The model's output is ``a set of topics
+consisting of clusters of words that co-occur in these documents
+according to certain patterns'' (Jacobi et al., 2016). Researchers must
+then interpret the identified topics, as done after other methods of
+manual coding. We also compare the topics between the policy documents
+and the academic papers, and use our interpretation to answer the
+questions outlined above that guide this paper. This methodology is not
+familiar to many, so we describe in more detail below how we used
+specific functions and code in R to produce our results.
 
@@
 sources and organized in the form of a data package. Following best
-practices in spatial data science (\textbf{brunsdon2020opening?}), the
-code and data needed to reproduce or conduct a similar analysis for
-other regions in North America or elsewhere are available for download.
+practices in spatial data science ({\textbf{???}}), the code and data
+needed to reproduce or conduct a similar analysis for other regions in
+North America or elsewhere are available for download.
 
@@
 
-\caption{\label{tab:content-table}\label{tab:policy-concordance}CAPTION THIS TABLE}
+\caption{\label{tab:content-table}\label{tab:policy-concordance}The context of key terms that were identified as common bigrams.}
 \centering
@@
 
+\begin{verbatim}
+## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
+## "none")` instead.
+\end{verbatim}
+
+\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-5.pdf}
+
 \begin{figure}
-\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/policy-terms-1} \caption{\label{fig:policy-terms}CAPTION THIS FIGURE}\label{fig:policy-terms}
+\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/policy-terms-1} \caption{\label{fig:policy-terms}Topics identified in the policy corpus according to clusters of words.}\label{fig:policy-terms}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/academic-terms-1} \caption{\label{fig:academic-terms}CAPTION THIS FIGURE}\label{fig:academic-terms}
+\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/academic-terms-1} \caption{\label{fig:academic-terms}Topics identified in the academic corpus according to clusters of words.}\label{fig:academic-terms}
 \end{figure}
@@
 on the clusters of words that were identified. We experimented with the
-model by adjusting the number of topics and found that there were 9
-distinct topics that could be interpreted, after which there was too
-much overlap. Figures \ref{fig:policy-terms} and
+model by adjusting and evaluating the number of topics and found that
+there were 9 distinct topics that could be interpreted, after which
+there was too much overlap. Figures \ref{fig:policy-terms} and
 \ref{fig:academic-terms} present the main terms that are associated with
@@
 In the policy corpus, we interpret the following topics based on the
-cluster of words: (1) resources for walking, (2) busing information and
-eligibility; (3) benefits of active travel; (4) bicycling and the
-environment; and (5) supporting active travel. These topics indicate
-that STP stakeholder groups are sending the message that walking and
-bicycling to school are healthy travel modes for students, particularly
-as a means to get physical activity. We also found that there is
-information shared to support parents and students in using active modes
-to school such as the availability of cycling lanes or route tips for
-walking.
+cluster of words: (1) resources for walking; (2) walking; (3) supporting
+active travel; (4) bicycling and the environment; (5) benefits of active
+travel; (6) safety; and (7) busing information and eligibility. These
+topics indicate that STP stakeholder groups are sending the message that
+walking and bicycling to school are healthy travel modes for students,
+particularly as a means to get physical activity. We also found that
+there is information shared to support parents and students in using
+active modes to school such as the availability of cycling lanes or
+route tips for walking. STP stakeholder groups are appear to be
+addressing the issue of safety.
 
@@
 volume of papers that were sourced. The following topics were identified
-based on the clusters of words: (1) \textbf{unclear} (2) AST in Ontario
-and Canada; (3) \textbf{unclear}; (4) children's independent mobility;
-(5) safe routes to school programs; (6) commuting and distance; (7)
-density in the built environment and walking routes; (8)
-\textbf{unclear}; (9) walking interventions; (10) bicycling influences;
-(11) interpersonal and household influences on trips; (12) behaviours
-and attitudes; (13) \textbf{unclear}; (14) \textbf{unclear}; (15)
-walking distance; (16) \textbf{unclear}; (17) physical activity measures
-or results; (18) bicycling attitudes; and (19) \textbf{unclear}.
+based on the clusters of words: (1) built environment (2) walking
+distance; (3) AST interventions; (4) parental barriers to walking; (5)
+behaviours and attitudes; (6) bicycling; (7) social environment; (8)
+children's independent mobility; (9) modeling trip choice; (10)
+adolescents and physical activity; and (11) safe routes to school
+programs. This corpus reflects a broader range of topics than the policy
+corpus.
 
@@
 and available resources for parents and children. A final focus in the
-policy documents is on various efforts that are underway to support
-active travel including route planning.
+policy documents is on various efforts that are underway to support AST
+including route planning. A few examples include:
 
@@
 available to the general public on the websites of STP stakeholder
-groups in Ontario. We found that AST is primarily framed as beneficial
-to the health and wellbeing of children and to environmental
+groups in Ontario. We found that AST is primarily framed to parents as
+beneficial to the health and wellbeing of children and to environmental
 sustainability. This was confirmed by the most common bigrams identified
@@
 contributes positively to children's physical health (see Faulkner et
-al., 2009; Schoeppe et al., 2015). STP stakeholder groups also
-communicate that increasing AST may reduce traffic near and around
-schools which could alleviate parental concerns about traffic safety.
-The potential outcomes of increased AST are highlighted which may be
-persuasive arguments to motivate behaviour change, which is the
-secondary frame of AST that we interpreted based on the LDA models.
-
-The proposed solutions to the problem of declining AST that are
-communicated to the general public are mostly educational (e.g., safety
-tips or maps of safe routes) and engineering changes (e.g., traffic
-calming or bicycle lanes). These solutions have to sufficiently address
-real and perceived concerns that pose barriers to AST in order to
-encourage adoption. In most documents, the emphasis is on providing
+al., 2009; Schoeppe et al., 2015), although the statements regarding the
+benefits of AST to children's school performance and cognitive
+development need to be studied further to produce stronger evidence
+({\textbf{???}}). STP stakeholder groups also communicate that
+increasing AST may reduce traffic near and around schools. This
+presumably is communicated to alleviate parental concerns about traffic
+and safety (Evers et al., 2014; Mammen et al., 2012; Rothman et al.,
+2015; Wilson et al., 2018) or reduce the frequency of risky behaviours
+from drivers around schools (Rothman et al., 2017). However, the
+documents do not explain why declining rates of AST are a problem for
+the particular community or convey any urgency to this issue so that it
+attracts the attention of parents, the general public, or policy makers.
+Communicating the potential outcomes of increased AST may be persuasive
+arguments to motivate behaviour change, but these documents do not
+appear to encourage parents or the general public to view their
+behaviour as problematic or unhealthy for their children's development.
+For example, Canadian parents who escort their children to school have
+reported concerns about traffic volume around schools (Mammen et al.,
+2012), but may not recognize that their own behaviour contributes to the
+problem that is perceived to prevent their child from safely walking or
+bicycling to school (Collins and Kearns, 2001).
+
+The secondary frame of AST that we interpreted based on the LDA model is
+the opportunity or prospect of behaviour change. STP stakeholder groups
+identified different ways that parents could encourage or support their
+child(ren) to commute to school by using active modes. Some school
+boards and municipalities also shared resources such as walking tip
+sheets and guidance for starting a walking school bus. Other advice
+included dropping children off one or two blocks away from school so
+that they could walk or bike part of the trip. The general emphasis is
+communicating information that could change parental perceptions about
+the ease of their children using active modes to school, which may be
+seen by STP stakeholder groups as a ``modifiable'' factor (see Riazi et
+al., 2019). In turn, this could encourage parents to modify their
+routines and incorporate opportunities for their children to use active
+modes to school.
+
+We found that interpersonal behaviour changes achieved through
+educational strategies and engineering changes (e.g., traffic calming
+measures, reduced speed limits, etc.) are communicated to the general
+public as potential solutions to address the decline of AST. This
+reflects findings from the AST literature (Panter et al., 2010), but
+these solutions have to sufficiently address real and perceived barriers
+from parents about the household environment and the built environment
+(see Section 2.2). In most documents, STP stakeholder groups provide
 parents with resources that help them switch modes for the school
-commute and/or on reassuring them that the built environment has become
-safer and friendlier to active travelers.
-
-However, the policy documents noticeably lacked a focus on individual
-and household level determinants of AST. For example, the role of
-convenience and inclement weather in shaping household travel decisions
-(\textbf{buliungSchoolTravelPlanning2011?}) or the age at which children
-become allowed to travel by active modes or independently (Mammen et
-al., 2012) were not discussed. Given the range of factors that influence
-AST in a Canadian setting (\emph{inter alia}, see Mammen et al., 2012;
-Wilson et al., 2018; \textbf{mitraIndependentMobilityMode2013?};
-\textbf{rothmanDeclineActiveSchool2018?}), STP stakeholder groups must
-decide which points of intervention that they can reasonably have some
-influence towards. This should also depend on the local context so that
-barriers to AST as perceived by parents are addressed. It could be that
-STP stakeholder groups perceive to have more control over the
-micro-scale elements of the built environment, like traffic calming,
-rather than the ability to influence the number of trips to different
-destinations that households need to make. STP stakeholders are also
-unable to intervene in residential location, which affects distance to
-school.
-
-To increase rates of walking and bicycling independently to school,
-Riazi et al. (2019) state: ``it will be vital for interventions to
-target modifiable factors, including children's and parents' perceptions
-of their social environment.'' We argue that STP messaging should also
-target multiple modifiable factors, in addition to the health and
-environmental benefits. Parents play the important role of
-``gatekeeper'' by either granting or restricting their child's mobility
-(Sharmin and Kamruzzaman, 2017). For this reason, stakeholders involved
-in STP should produce more information that specifically responds to
-parents' perceived barriers and challenges. For example, STP materials
-could explain how known concerns in a particular municipality or school
-area have been addressed through local solutions.
+commute and/or on reassure them that the built environment has become
+safer and friendlier to active travelers as a result of infrastructure
+or policy improvements. As previously noted, the documents do not appear
+to present a strong ``call to action'' that urges behaviour change for
+parents or the general public, which may affect the success of STP
+interventions. On the other hand, the emphasis on engineering changes
+may reflect the strong engagement of the ``policy stream'' (Kingdon,
+1984) and the feasible options to address the problem, since engineering
+staff and municipal representatives are common STP stakeholders
+(Buttazzoni et al., 2018; Mammen et al., 2015).
+
+Given the range of factors that influence AST in a Canadian setting
+(\emph{inter alia}, see Mammen et al., 2012; Mitra, 2013; Rothman et
+al., 2018; Wilson et al., 2018), STP stakeholder groups must decide
+which points of intervention that they can reasonably have some
+influence towards. This would also depend on the local context to ensure
+that barriers to AST as perceived by parents are addressed. It could be
+that STP stakeholder groups perceive to have more control over
+micro-scale elements of the built environment, like traffic calming
+measures or speed limits, rather ``non-modifiable'' factors like street
+density or land use mix. It would certainly be much more difficult for
+STP stakeholder groups to influence the number of trips to different
+destinations that households need to make or to intervene in residential
+location, which affects distance to school. A focus on changing parental
+perceptions is recommended by many scholars since parents are the
+``gatekeeper'' for children's mobility, but the information communicated
+by STP stakeholder groups in Ontario should reflect a broader range of
+factors that influence AST.
 
@@
 
-Many municipalities, schools, and transportation consortia use similar
-content in their public documents about AST. It would be worthwhile for
-STP stakeholders to adapt generic content so that it is more specific to
-factors associated with AST or parental perceptions about barriers to
-AST in the local context. Rothman et al. (2018) note that local
-solutions to address specific school challenges are worthwhile, and we
-extend this recommendation to include local context in STP messaging
-about AST.
+There is also a noticeable lack of focus on individual and interpersonal
+determinants of AST in the policy documents. For example, the role of
+convenience and inclement weather in shaping household travel decisions
+(Buliung et al., 2011) or the age at which children become allowed to
+travel by active modes or independently (Mammen et al., 2012) were not
+discussed. The desire to escort children to school, which has been noted
+by parents as a reason to continue driving (Westman, Friman, et al.,
+2017), is also not adequately addressed by STP stakeholder groups. The
+complexity of travel arrangements that must be coordinated by households
+(see Buliung et al., 2021) and the dominant parenting culture to protect
+children from risk ({\textbf{???}}) are likewise overlooked. STP
+stakeholders may wish to emphasize to parents that older children have
+greater traffic safety and cognitive abilities to navigate their own
+routes to school, which could encourage parents to develop their
+child(ren)'s travel skills over time. Additional attention should be
+paid to the reasons why parents perceive driving to be more convenient.
+
+Coming back to Kingdon's Multiple Streams Framework (1984), we posited
+that STP stakeholder groups need to raise awareness about the AST issue
+among parents and the general public through the problem stream. This
+could influence perceptions about the issue and encourage behaviour
+change. Based on the policy documents, it is not obvious that AST has
+declined significantly over the past few decades in Canada or that this
+issue merits urgent attention. Many municipalities, schools, and
+transportation consortia in Ontario use similar content in their public
+documents about AST. It would be worthwhile for STP stakeholder groups
+to frame the decline of AST as a ``problem'' worth addressing with
+information specific to each local context. STP stakeholders also need
+to ensure that their communication accounts for the ways in which
+Canadian parents perceive the built environment in different ways than
+planners (see Buliung et al., 2021). If there is ``conceptual
+asymmetry'' as Buliung et al.~(2021) identified, the materials
+disseminated by STP stakeholders may not resonate or reach parents.
+Future research or STP activities should investigate how parents or the
+general public respond to messages or information that encourages the
+adoption of AST and evaluate how effective they are to motivate
+behaviour change. It would be helpful to know which frames would most
+encourage behaviour change or increase political support for
+interventions that address barriers to AST. This type of information
+could ensure that educational strategies and promotional materials
+increase buy-in for their target audience.
+
+Although the ``policy stream'' appears to have been adequately engaged
+in Ontario communities, it could be that the decline of AST has not been
+sufficiently framed as ``problematic'' to warrant more widespread
+awareness or solutions. If Canadian STP stakeholder groups wish to
+involve more local residents in their efforts (Buttazzoni et al., 2018),
+it would also be worthwhile for them to produce different material that
+communicates why this issue is important to the general public,
+regardless of whether they currently have children commuting to/from
+school. The ``political steam'' could also be further engaged by working
+with advocacy groups who could attract more support from a broader
+coalition of individuals.
+
+Finally, Rothman et al.~(2018) note that local solutions to address
+specific school challenges are needed, and we extend this recommendation
+to include local context in STP messaging about AST. Instead of generic
+content about AST, stakeholders involved in STP should produce more
+information that specifically responds to parents' perceived barriers
+and challenges that were identified in that local context. For example,
+STP materials could explain how known concerns in a particular
+municipality or school area have been addressed through local solutions.
+This could reflect that solutions have been identified based on what was
+heard from the community.
 
@@
 
+A limitation of this study is that we only analyzed texts that were
+easily accessible to the general public on the websites of STP
+stakeholder groups in Ontario. Parents likely receive information about
+AST directly from schools, which may contain more content that reflects
+the local barriers to AST.
+
 \hypertarget{conclusion}{%
@@
 
-\hypertarget{future-research}{%
-\subsection{7.1. Future research}\label{future-research}}
-
-Future studies may investigate how parents and policy makers outside the
-field of public health respond to the ways in which AST is framed in STP
-documents. It would be helpful to know which frames would most encourage
-behaviour change or increase political support for interventions that
-address barriers to AST. This type of information could ensure that
-educational strategies and promotional materials increase buy-in for
-their target audience.
-
-\hypertarget{acknowledgments}{%
-\section{Acknowledgments}\label{acknowledgments}}
-
-This research was completed using open software, and the authors wish to
-acknowledge the developers of the following \texttt{R} packages:
-\texttt{dplyr} (\textbf{R-dplyr?}), \texttt{ggraph}
-(\textbf{R-ggraph?}), \texttt{ggplot2} (\textbf{R-ggplot2?}),
-\texttt{igraph} (\textbf{R-igraph?}), \texttt{pdftools}
-(\textbf{R-pdftools?}), \texttt{readr} (\textbf{R-readr?}),
-\texttt{reshape2} (\textbf{R-reshape2?}), \texttt{stringr}
-(\textbf{R-stringr?}), \texttt{text2vec} (\textbf{R-text2vec?}),
-\texttt{textdata} (\textbf{R-textdata?}), \texttt{tidyr}
-(\textbf{R-tidyr?}), \texttt{tidytext} (\textbf{R-tidytext?}),
-\texttt{tm} (\textbf{R-tm?}), \texttt{tools} (\textbf{R-tools?}),
-\texttt{topicmodels} (\textbf{R-topicmodels?}), \texttt{widyr}
-(\textbf{R-widyr?}), \texttt{word2vec} (\textbf{R-word2vec?}),
-\texttt{wordcloud} (\textbf{R-wordcloud?}), \texttt{DiagrammeR}
-(\textbf{R-diagrammeR?}), and \texttt{kableextra}
-(\textbf{R-kableextra?}).
+We used text mining and topic modelling to examine how different school
+travel planning stakeholder (STP) groups in Ontario frame the issue of
+AST. STP stakeholder groups frame AST as a health and environmental
+issue that can be addressed through household behaviour change and
+engineering solutions. Policy documents reveal that STP stakeholder
+groups are focusing on ``modifiable factors'' such as parental
+perceptions or micro-scale elements in the built environment to increase
+rates of AST. However, AST may not be framed sufficiently as a
+``problem'' that requires urgent intervention, which may impact how
+parents respond to behaviour change initiatives and limit awareness in
+the general public. In their public materials about AST, STP stakeholder
+groups should present solutions for a broader range of factors that
+influence AST and emphasize why AST rates should increase in local
+communities.
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-albalawiUsingTopicModeling2020}{}%
+Albalawi, R., Yeap, T.H., Benyoucef, M., 2020. Using Topic Modeling
+Methods for Short-Text Data: A Comparative Analysis. Frontiers in
+Artificial Intelligence 3, 42.
+doi:\href{https://doi.org/10.3389/frai.2020.00042}{10.3389/frai.2020.00042}
+
+\leavevmode\hypertarget{ref-badlandDevelopmentSystemsModel2016}{}%
+Badland, H., Kearns, R., Carroll, P., Oliver, M., Mavoa, S., Donovan,
+P., Parker, K., Chaudhury, M., Lin, E.-Y., Witten, K., 2016. Development
+of a systems model to visualise the complexity of children's independent
+mobility. Children's Geographies 14, 91--100.
+doi:\href{https://doi.org/10.1080/14733285.2015.1021240}{10.1080/14733285.2015.1021240}
+
+\leavevmode\hypertarget{ref-buliungSchoolTravelPlanning2011}{}%
+Buliung, R., Faulkner, G., Beesley, T., Kennedy, J., 2011. School Travel
+Planning: Mobilizing School and Community Resources to Encourage Active
+School Transportation. Journal of School Health 81, 704--712.
+doi:\href{https://doi.org/10.1111/j.1746-1561.2011.00647.x}{10.1111/j.1746-1561.2011.00647.x}
+
 \leavevmode\hypertarget{ref-buliungLivingJourneySchool2021}{}%
@@
 
+\leavevmode\hypertarget{ref-borrestadExperiencesRandomisedControlled2012}{}%
+Børrestad, L.A.B., Østergaard, L., Andersen, L.B., Bere, E., 2012.
+Experiences from a randomised, controlled trial on cycling to school:
+Does cycling increase cardiorespiratory fitness? Scandinavian Journal of
+Public Health 40, 245--252.
+doi:\href{https://doi.org/10.1177/1403494812443606}{10.1177/1403494812443606}
+
+\leavevmode\hypertarget{ref-GreenCommunities2016}{}%
+Canada, G.C., 2020a. Ontario active school travel fund {[}WWW
+Document{]}. URL
+\url{https://ontarioactiveschooltravel.ca/ontario-active-school-travel-fund/}
+
+\leavevmode\hypertarget{ref-GreenCommunitiesProjects}{}%
+Canada, G.C., 2020b. OAST fund project directory {[}WWW Document{]}. URL
+\url{https://ontarioactiveschooltravel.ca/wp-content/uploads/2020/10/OAST-Fund-Matrix-Directory.pdf}
+
+\leavevmode\hypertarget{ref-chenPromotingActiveStudent2018}{}%
+Chen, P., Jiao, J., Xu, M., Gao, X., Bischak, C., 2018. Promoting active
+student travel: A longitudinal study. Journal of Transport Geography 70,
+265--274.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2018.06.015}{10.1016/j.jtrangeo.2018.06.015}
+
+\leavevmode\hypertarget{ref-collinsSafeJourneysEnterprising2001}{}%
+Collins, D.C.A., Kearns, R.A., 2001. The safe journeys of an
+enterprising school: Negotiating landscapes of opportunity and risk.
+Health \& Place 7, 293--306.
+doi:\href{https://doi.org/10.1016/S1353-8292(01)00021-1}{10.1016/S1353-8292(01)00021-1}
+
 \leavevmode\hypertarget{ref-demeesterParentalPerceivedNeighborhood2014}{}%
@@
 
+\leavevmode\hypertarget{ref-eversParentSafetyPerceptions2014}{}%
+Evers, C., Boles, S., Johnson-Shelton, D., Schlossberg, M., Richey, D.,
+2014. Parent safety perceptions of child walking routes. Journal of
+Transport \& Health 1, 108--115.
+doi:\href{https://doi.org/10.1016/j.jth.2014.03.003}{10.1016/j.jth.2014.03.003}
+
 \leavevmode\hypertarget{ref-faulknerActiveSchoolTransport2009}{}%
@@
 
-\leavevmode\hypertarget{ref-ghekiereInsightsChildrenIndependent2017}{}%
-Ghekiere, A., Deforche, B., Carver, A., Mertens, L., de Geus, B.,
-Clarys, P., Cardon, G., De Bourdeaudhuij, I., Van Cauwenberg, J., 2017.
-Insights into children's independent mobility for transportation
-cycling{{Which}} socio-ecological factors matter? Journal of Science and
-Medicine in Sport 20, 267--272.
-doi:\href{https://doi.org/10.1016/j.jsams.2016.08.002}{10.1016/j.jsams.2016.08.002}
+\leavevmode\hypertarget{ref-faulknerSchoolTravelChildren2013}{}%
+Faulkner, G., Stone, M., Buliung, R., Wong, B., Mitra, R., 2013. School
+travel and children's physical activity: A cross-sectional study
+examining the influence of distance. BMC public health 13, 1166.
+doi:\href{https://doi.org/10.1186/1471-2458-13-1166}{10.1186/1471-2458-13-1166}
+
+\leavevmode\hypertarget{ref-fuscoUnderstandingChildrenPerceptions2012}{}%
+Fusco, C., Moola, F., Faulkner, G., Buliung, R., Richichi, V., 2012.
+Toward an understanding of children's perceptions of their transport
+geographies: (Non)Active school travel and visual representations of the
+built environment. Journal of Transport Geography, Special Section On
+Child \& Youth Mobility 20, 62--70.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2011.07.001}{10.1016/j.jtrangeo.2011.07.001}
+
+\leavevmode\hypertarget{ref-gamsonChangingCulture1987}{}%
+Gamson, W.A., Modigliani, A., 1987. The changing culture of affirmative
+action. JAI Press.
 
@@
 experience, Frame analysis: An essay on the organization of experience.
-{Harvard University Press}, {Cambridge, MA, US}.
+Harvard University Press, Cambridge, MA, US.
 
@@
 
-\leavevmode\hypertarget{ref-kimBuiltNaturalEnvironmental2020}{}%
-Kim, Y.-J., Lee, C., 2020. Built and {Natural Environmental Correlates}
-of {Parental Safety Concerns} for {Children}'s {Active Travel} to
-{School}. International Journal of Environmental Research and Public
-Health 17.
-doi:\href{https://doi.org/10.3390/ijerph17020517}{10.3390/ijerph17020517}
+\leavevmode\hypertarget{ref-jacobiQuantitativeAnalysisLarge2016}{}%
+Jacobi, C., van Atteveldt, W., Welbers, K., 2016. Quantitative analysis
+of large amounts of journalistic texts using topic modelling. Digital
+Journalism 4, 89--106.
+doi:\href{https://doi.org/10.1080/21670811.2015.1093271}{10.1080/21670811.2015.1093271}
+
+\leavevmode\hypertarget{ref-jensenHowObtainHealthy2008}{}%
+Jensen, S.U., 2008. How to obtain a healthy journey to school.
+Transportation Research Part A: Policy and Practice 42, 475--486.
+doi:\href{https://doi.org/10.1016/j.tra.2007.12.001}{10.1016/j.tra.2007.12.001}
+
+\leavevmode\hypertarget{ref-kingdonAgendasAlternativesPublic1984}{}%
+Kingdon, J.W. (Ed.), 1984. Agendas, alternatives and public policies.
+Pearson.
+
+\leavevmode\hypertarget{ref-langUnderstandingModalChoice2011}{}%
+Lang, D., Collins, D., Kearns, R., 2011. Understanding modal choice for
+the trip to school. Journal of Transport Geography 19, 509--514.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2010.05.005}{10.1016/j.jtrangeo.2010.05.005}
+
+\leavevmode\hypertarget{ref-laroucheRatherBikeSchool2016}{}%
+Larouche, R., Stone, M., Buliung, R.N., Faulkner, G., 2016. ''I'd rather
+bike to school!'': Profiling children who would prefer to cycle to
+school. Journal of Transport \& Health 3, 377--385.
+doi:\href{https://doi.org/10.1016/j.jth.2016.06.010}{10.1016/j.jth.2016.06.010}
+
+\leavevmode\hypertarget{ref-larsenRouteBasedAnalysisCapture2012}{}%
+Larsen, K., Gilliland, J., Hess, P.M., 2012. Route-Based Analysis to
+Capture the Environmental Influences on a Child's Mode of Travel between
+Home and School. Annals of the Association of American Geographers 102,
+1348--1365.
+doi:\href{https://doi.org/10.1080/00045608.2011.627059}{10.1080/00045608.2011.627059}
 
@@
 Mah, C.L., Hamill, C., Rondeau, K., McIntyre, L., 2014. A frame-critical
-policy analysis of {Canada}'s response to the {World Food Summit}
-1998{}. Archives of Public Health 72, 41.
+policy analysis of Canada's response to the World Food Summit 19982008.
+Archives of Public Health 72, 41.
 doi:\href{https://doi.org/10.1186/2049-3258-72-41}{10.1186/2049-3258-72-41}
@@
 
+\leavevmode\hypertarget{ref-mammenSchoolTravelPlanning2014}{}%
+Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2014. School travel
+planning in Canada: Identifying child, family, and school-level
+characteristics associated with travel mode shift from driving to active
+school travel. Journal of Transport \& Health, Walking \& Cycling: The
+contributions of health and transport geography 1, 288--294.
+doi:\href{https://doi.org/10.1016/j.jth.2014.09.004}{10.1016/j.jth.2014.09.004}
+
+\leavevmode\hypertarget{ref-mammenPuttingSchoolTravel2015}{}%
+Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2015. ''Putting
+school travel on the map'': Facilitators and barriers to implementing
+school travel planning in Canada. Journal of Transport \& Health 2,
+318--326.
+doi:\href{https://doi.org/10.1016/j.jth.2015.05.003}{10.1016/j.jth.2015.05.003}
+
 \leavevmode\hypertarget{ref-mammenActiveSchoolTravel2014}{}%
@@
 O'Brien, C., Kennedy, J., 2014. Active school travel: An evaluation of
-the {Canadian} school travel planning intervention. Preventive Medicine
+the Canadian school travel planning intervention. Preventive Medicine
 60, 55--59.
 doi:\href{https://doi.org/10.1016/j.ypmed.2013.12.008}{10.1016/j.ypmed.2013.12.008}
+
+\leavevmode\hypertarget{ref-michailChildrenExperiencesTheir2021}{}%
+Michail, N., Ozbil, A., Parnell, R., Wilkie, S., 2021. Children's
+Experiences of Their Journey to School: Integrating Behaviour Change
+Frameworks to Inform the Role of the Built Environment in Active School
+Travel Promotion. International Journal of Environmental Research and
+Public Health 18, 4992.
+doi:\href{https://doi.org/10.3390/ijerph18094992}{10.3390/ijerph18094992}
+
+\leavevmode\hypertarget{ref-mitraIndependentMobilityMode2013}{}%
+Mitra, R., 2013. Independent Mobility and Mode Choice for School
+Transportation: A Review and Framework for Future Research. Transport
+Reviews 33, 21--43.
+doi:\href{https://doi.org/10.1080/01441647.2012.743490}{10.1080/01441647.2012.743490}
 
@@
 
+\leavevmode\hypertarget{ref-reynardGrowthResilienceHow2021}{}%
+Reynard, D., Collins, D., Shirgaokar, M., 2021. Growth over resilience:
+How Canadian municipalities frame the challenge of reducing carbon
+emissions. Local Environment 0, 1--13.
+doi:\href{https://doi.org/10.1080/13549839.2021.1892046}{10.1080/13549839.2021.1892046}
+
 \leavevmode\hypertarget{ref-riaziCorrelatesChildrenIndependent2019}{}%
 Riazi, N.A., Blanchette, S., Trudeau, F., Larouche, R., Tremblay, M.S.,
-Faulkner, G., 2019. Correlates of {Children}'s {Independent Mobility} in
-{Canada}: A {Multi}-{Site Study}. International Journal of Environmental
+Faulkner, G., 2019. Correlates of Children's Independent Mobility in
+Canada: A Multi-Site Study. International Journal of Environmental
 Research and Public Health 16.
@@
 
-\leavevmode\hypertarget{ref-rothmanDeclineActiveSchool2018a}{}%
+\leavevmode\hypertarget{ref-romeroChildrenExperiencesEnjoyment2015}{}%
+Romero, V., 2015. Children׳s experiences: Enjoyment and fun as
+additional encouragement for walking to school. Journal of Transport \&
+Health 2, 230--237.
+doi:\href{https://doi.org/10.1016/j.jth.2015.01.002}{10.1016/j.jth.2015.01.002}
+
+\leavevmode\hypertarget{ref-rothmanSchoolEnvironmentStudent2017}{}%
+Rothman, L., Buliung, R., Howard, A., Macarthur, C., Macpherson, A.,
+2017. The school environment and student car drop-off at elementary
+schools. Travel Behaviour and Society 9, 50--57.
+doi:\href{https://doi.org/10.1016/j.tbs.2017.03.001}{10.1016/j.tbs.2017.03.001}
+
+\leavevmode\hypertarget{ref-rothmanAssociationsParentsPerception2015}{}%
+Rothman, L., Buliung, R., To, T., Macarthur, C., Macpherson, A., Howard,
+A., 2015. Associations between parents׳ perception of traffic danger,
+the built environment and walking to school. Journal of Transport \&
+Health 2, 327--335.
+doi:\href{https://doi.org/10.1016/j.jth.2015.05.004}{10.1016/j.jth.2015.05.004}
+
+\leavevmode\hypertarget{ref-rothmanActiveSchoolTransportation2021}{}%
+Rothman, L., Hagel, B., Howard, A., Cloutier, M.S., Macpherson, A.,
+Aguirre, A.N., McCormack, G.R., Fuselli, P., Buliung, R., HubkaRao, T.,
+Ling, R., Zanotto, M., Rancourt, M., Winters, M., 2021. Active school
+transportation and the built environment across Canadian cities:
+Findings from the child active transportation safety and the environment
+(CHASE) study. Preventive Medicine 146, 106470.
+doi:\href{https://doi.org/10.1016/j.ypmed.2021.106470}{10.1016/j.ypmed.2021.106470}
+
+\leavevmode\hypertarget{ref-rothmanDeclineActiveSchool2018}{}%
 Rothman, L., Macpherson, A.K., Ross, T., Buliung, R.N., 2018. The
-decline in active school transportation ({AST}): A systematic review of
-the factors related to {AST} and changes in school transport over time
-in {North America}. Preventive Medicine 111, 314--322.
+decline in active school transportation (AST): A systematic review of
+the factors related to AST and changes in school transport over time in
+North America. Preventive Medicine 111, 314--322.
 doi:\href{https://doi.org/10.1016/j.ypmed.2017.11.018}{10.1016/j.ypmed.2017.11.018}
@@
 Schoeppe, S., Duncan, M.J., Badland, H.M., Oliver, M., Browne, M., 2015.
-Associations between children's active travel and levels of physical
+Associations between children׳s active travel and levels of physical
 activity and sedentary behavior. Journal of Transport \& Health 2,
@@
 
-\leavevmode\hypertarget{ref-sharminAssociationBuiltEnvironment2017}{}%
-Sharmin, S., Kamruzzaman, Md., 2017. Association between the built
-environment and children's independent mobility: A meta-analytic review.
-Journal of Transport Geography 61, 104--117.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2017.04.004}{10.1016/j.jtrangeo.2017.04.004}
+\leavevmode\hypertarget{ref-silgeTextMining2021}{}%
+Silge, J., Robinson, D., 2021. Text Mining with R.
+
+\leavevmode\hypertarget{ref-starkExploringIndependentActive2018}{}%
+Stark, J., Frühwirth, J., Aschauer, F., 2018. Exploring independent and
+active mobility in primary school children in Vienna. Journal of
+Transport Geography 68, 31--41.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2018.02.007}{10.1016/j.jtrangeo.2018.02.007}
 
@@
 2020. Factors affecting parental safety perception, satisfaction with
-school travel and mood in primary school children in the {Netherlands}.
+school travel and mood in primary school children in the Netherlands.
 Journal of Transport \& Health 16, 100837.
@@
 
+\leavevmode\hypertarget{ref-vangoeverdenSchoolTravelBehaviour2013}{}%
+van Goeverden, C.D., de Boer, E., 2013. School travel behaviour in the
+Netherlands and Flanders. Transport Policy, ''Understanding behavioural
+change: An international perspective on sustainable travel behaviours
+and their motivations'': Selected Papers from the 12th World Conference
+on Transportation Research 26, 73--84.
+doi:\href{https://doi.org/10.1016/j.tranpol.2013.01.004}{10.1016/j.tranpol.2013.01.004}
+
+\leavevmode\hypertarget{ref-waygoodChildrenTravelIncidental2015}{}%
+Waygood, E.O.D., Friman, M., 2015. Children's travel and incidental
+community connections. Travel Behaviour and Society 2, 174--181.
+doi:\href{https://doi.org/10.1016/j.tbs.2015.03.003}{10.1016/j.tbs.2015.03.003}
+
+\leavevmode\hypertarget{ref-waygoodTransportChildrenWellbeing2020}{}%
+Waygood, E.O.D., Friman, M., Olsson, L.E., Mitra, R. (Eds.), 2020.
+Transport and Children's Wellbeing, in: Transport and Children's
+Wellbeing. Elsevier, pp. i--ii.
+doi:\href{https://doi.org/10.1016/B978-0-12-814694-1.09993-0}{10.1016/B978-0-12-814694-1.09993-0}
+
+\leavevmode\hypertarget{ref-waygoodJapanMaintainingHigh2020}{}%
+Waygood, E.O.D., Taniguchi, A., 2020. Japan: Maintaining high levels of
+walking, in: Waygood, E.O.D., Friman, M., Olsson, L.E., Mitra, R.
+(Eds.), Transport and Children's Wellbeing. Elsevier, pp. 297--316.
+doi:\href{https://doi.org/10.1016/B978-0-12-814694-1.00016-6}{10.1016/B978-0-12-814694-1.00016-6}
+
 \leavevmode\hypertarget{ref-weathersDevelopmentsFramingClimate2016}{}%
-Weathers, M.R., Kendall, B.E., 2016. Developments in the {Framing} of
-{Climate Change} as a {Public Health Issue} in {US Newspapers}.
-Environmental Communication 10, 593--611.
+Weathers, M.R., Kendall, B.E., 2016. Developments in the Framing of
+Climate Change as a Public Health Issue in US Newspapers. Environmental
+Communication 10, 593--611.
 doi:\href{https://doi.org/10.1080/17524032.2015.1050436}{10.1080/17524032.2015.1050436}
+
+\leavevmode\hypertarget{ref-westmanWhatDrivesThem2017}{}%
+Westman, J., Friman, M., Olsson, L.E., 2017. What Drives Them to
+Drive?Parents' Reasons for Choosing the Car to Take Their Children to
+School. Frontiers in Psychology 8.
+doi:\href{https://doi.org/10.3389/fpsyg.2017.01970}{10.3389/fpsyg.2017.01970}
+
+\leavevmode\hypertarget{ref-westmanChildrenTravelSchool2017}{}%
+Westman, J., Olsson, L.E., Gärling, T., Friman, M., 2017. Children's
+travel to school: Satisfaction, current mood, and cognitive performance.
+Transportation 44, 1365--1382.
+doi:\href{https://doi.org/10.1007/s11116-016-9705-7}{10.1007/s11116-016-9705-7}
 
@@
 
-\end{CSLReferences}
+\leavevmode\hypertarget{ref-zwertsHowChildrenView2010}{}%
+Zwerts, E., Allaert, G., Janssens, D., Wets, G., Witlox, F., 2010. How
+children view their travel behaviour: A case study from Flanders
+(Belgium). Journal of Transport Geography 18, 702--710.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2009.10.002}{10.1016/j.jtrangeo.2009.10.002}
 

### 2022-01-25 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Revised paper based on co-authors feedback

@@
 ```{r load-data, include=FALSE}
-load(file= "Corpus .rda/academic_corpus.rda")
+load(file= "Corpus .rda/academic_corpus_repaired.rda")
 load(file= "Corpus .rda/municipal_corpus.rda")
@@
 
-Rates of walking and bicycling to school, commonly known as active school travel (AST), have been declining in Canada and the United States for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013], Denmark [@jensenHowObtainHealthy2008], and Japan [@waygoodJapanMaintainingHigh2020].
+Rates of walking and bicycling to school, commonly known as active school travel (AST), have been declining in Canada and the United States for decades [@rothmanDeclineActiveSchool2018].
 However, the appetite for AST may be high in many Canadian communities.
 For instance, 40% of children in a study conducted in Toronto, Ontario who are driven to school would like to travel by bicycle instead [@laroucheRatherBikeSchool2016].
-But the study reported that less than 3% actually do, despite the vast majority having access to a bicycle and living within a short and bikeable distance to school.
+The study also reported that less than 3% of respondents actually cycled, despite the vast majority having access to a bicycle and living within a short and bikeable distance to school.
 Another study based in London, Ontario reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012].
-From a public health perspective, this represents a huge opportunity to improve health and wellbeing if more children could use active modes to school.
+From a public health perspective, this represents a major opportunity to improve health and wellbeing if more children could use active modes to school.
 
 In response to this trend, the Government of Ontario, in Canada, created a fund in 2017 to support communities across the province in developing AST initiatives.
-Green Communities Canada runs the program, called _Ontario Active School Travel_, and determines the projects that will be funded with their support [@GreenCommunities2016].
-As of December 2021, OAST has awarded over 2 million Canadian dollars and provided resources for over 25 projects across Ontario.
-Many communities implemented school travel planning (STP), along with encouragement activities like walking school buses or developed resources for schools and parents, among other actions [see @GreenCommunitiesProjects].
-In this context, STP is a popular "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014].
-The five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities following the 5 E's that alleviate concerns about AST and make AST safer and more convenient [@buliungSchoolTravelPlanning2011; @langUnderstandingModalChoice2011].
-
-How AST is framed by STP stakeholders to a target audience, like parents or the general public, may raise awareness about the issue and influence how walking and bicycling to school are perceived.
+Green Communities Canada runs the program, called _Ontario Active School Travel_ [@GreenCommunities2016].
+As of December 2021, OAST has awarded over $2 million and provided resources to over 25 projects across Ontario.
+Many communities implemented school travel planning (STP), along with encouraging activities like walking school buses and developed resources for schools and parents, among other actions [see @GreenCommunitiesProjects].
+In this context, STP is a popular "school-specific" intervention led by a facilitator who brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014].
+The five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities following the 4E's that make AST safer and more convenient: 1) setup of the program; 2) data collection and problem identification; 3) action planning; 4) implementation; 5) monitoring and evaluation [@buliungSchoolTravelPlanning2011; @langUnderstandingModalChoice2011].
+
+How AST is framed by STP stakeholders to a target audience, like parents or the general public, may raise awareness of the issue and influence how walking and bicycling to school are perceived.
 Gamson and Modigliani [-@gamsonChangingCulture1987] define a frame as a “central organizing idea or story line that provides meaning” to a particular phenomenon.
 A frame can enable individuals "to locate, perceive, identify, and label" information pertaining to various dimensions of an issue [@goffmanFrameAnalysisEssay1974].
-Therefore, stakeholder groups involved in STP efforts can play a role in shaping public perception about AST in such a way that it attracts greater attention and becomes a "problem" that needs to be addressed through behaviour change or by new policies.
-We also contend that the ways in which the AST issue is framed can affect the policy process, as outlined in Kingdon's [-@kingdonAgendasAlternativesPublic1984] Multiple Streams Framework (MSF), through all three streams (i.e., problem, policy, and politics).
-This framing can ultimately impact financial contributions and potential solutions to address the decline of AST in Canada.
-
-After significant investment of human and financial resources to boost rates of AST in Ontario over the past few years, we ask the following questions: How is AST framed?
-What benefits of AST are communicated to the public?
+Therefore, stakeholders involved in STP efforts can play a role in shaping public perception about AST in such a way that it attracts greater attention and is recognized as a "problem" that needs to be addressed through behaviour change or new policies.
+
+After significant investment of human and financial resources to boost rates of AST in Ontario over the past few years, we ask this central question: How is AST framed to the public?
+The following questions are subsidiary and help us address this main question: What benefits of AST are communicated to the public?
 What solutions are proposed to increase rates of AST?
-Do proposed solutions focus primarily on the intrapersonal and interpersonal factors, meaning that behaviour change must ultimately result from the individual or household making different travel decisions?
-Or is AST framed as an issue that must be addressed through changes in the built environment or at the policy level?
-
-In this paper, we use text mining and topic modelling to examine how three STP stakeholder groups in Ontario (i.e., municipalities, school boards, and transportation consortia) frame the issue of AST.
-We assembled a corpus of texts from webpages that can be considered an important source of information for the general public or parents who are interested in AST.
+
+In this paper, we use natural language processing to examine how three STP stakeholder groups in Ontario (municipalities, school boards, and transportation consortia) frame the issue of AST.
+We assembled a corpus of texts from webpages that present information for the general public or parents who are interested in AST.
 We examine word frequency, bigrams, and concordances in these selected documents, and also identify key topics presented by each stakeholder group.
@@
 However, Schoeppe et al.
-[-@schoeppeAssociationsChildrenActive2015] reported no association between AST and physical activity.
+[-@schoeppeAssociationsChildrenActive2015] reported no association between AST and physical activity in their cross-sectional study.
 This relationship could be dose-dependent, meaning that children would have to travel longer distances to accumulate physical activity.
@@
 More recently, there has been literature exploring the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020], with relevant applications to the study of travel satisfaction [@vandenbergFactorsAffectingParental2020; @westmanChildrenTravelSchool2017].
-Being driven to school reduces community interactions for children which may impact their social wellbeing [@waygoodChildrenTravelIncidental2015], whereas walking and bicycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021].
-This is something that children highly value about travel [@zwertsHowChildrenView2010] and indicates that social connections through travel are important for their wellbeing.
-AST also provides opportunities for children to engage with the natural environment [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015] which can improve their mental or emotional wellbeing.
+Being driven to school reduces community interactions for children which may negatively impact their social wellbeing [@waygoodChildrenTravelIncidental2015], whereas walking and bicycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021].
+This is something that children value highly about travel [@zwertsHowChildrenView2010] which indicates that social connections through travel are important for their wellbeing.
+AST also provides opportunities for children to engage with the natural environment [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015].
 
@@
 
-Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behaviour is understood within the context of their household, social, neighbourhood, and policy environments.
-Individual characteristics of the child are also determinants.
+Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behaviour is understood within the context of household, social, neighbourhood, and policy environments.
 The SEM comes from the field of public health and is a useful framework for understanding complex health behaviours, including travel habits such as walking or bicycling to school, because it identifies multiple determinants that need to be addressed by interventions to facilitate behaviour change.
-The consensus in the literature is that various factors are interrelated and that interventions should target multiple levels in order to increase levels of healthy and physically active modes of travel to school [@mitraIndependentMobilityMode2013].
-Rather than describing an extensive list of factors that influence AST and mode choice in Canada, which has been covered elsewhere [e.g., @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], we briefly discuss a few potentially modifiable determinants that may be targeted for change through STP.
-
-At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018] as parents typically escort younger children.
+The consensus in the literature is that interventions should target multiple levels in order to increase levels of healthy and physically active modes of travel to school [@mitraIndependentMobilityMode2013].
+Rather than describing an extensive list of factors that influence AST and mode choice in Canada [e.g., @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], we discuss a few potentially modifiable determinants that may be targeted for change through STP.
+
+At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018].
 There is evidence that gender is a determinant of AST, with boys being more likely to travel using active modes than girls, although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
-Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], which indicates that shifting parental perceptions and habits is important.
+Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], as well as the frequency of parental support [@mahDoesParentalSupport2017a], which indicates that shifting parental perceptions and habits is important.
 Convenience and inclement weather have been cited by parents as barriers to AST [@buliungSchoolTravelPlanning2011].
-Parental perceptions of the built or school environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and their children's skills [@mammenUnderstandingDriveEscort2012] also influence whether they allow their children to walk or bicycle to school.
+Parental perceptions of the built or school environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and their children's skills [@mammenUnderstandingDriveEscort2012; @faulknerWhatQuickestEasiest2010] also influence mode choice to school.
 
@@
 School travel planning (STP) has been implemented in Canada since at least the late 2000s.
-Within the STP process, facilitators generally establish multi-sector committees who intervene at the participating school through a range of activities related to the 5E's such as _education_ strategies, _encouragement_ through in-person events or programs, _engineering_ improvements to or around the school site, and _enforcement_ of traffic speeds around schools [@langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
+Within the STP process, facilitators generally establish multi-sector committees who intervene at the participating school through a range of activities related to the 4E's consisting of _education_ strategies, _encouragement_ through in-person events or programs, _engineering_ improvements to or around the school site, and _enforcement_ of traffic speeds around schools [@langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
 The first large-scale evaluation of STP as an intervention in Canada took place at twelve schools across the country, including four in Ontario, using parental surveys to measure changes in travel behaviour and perceptions [@buliungSchoolTravelPlanning2011].
-Since then, there have been other assessments of both the efficacy of STP [@buttazzoniPromotingActiveSchool2019; @mammenActiveSchoolTravel2014] and the process of implementing such programs in Ontario [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015].
+Assessments of the efficacy of STP [@buttazzoniPromotingActiveSchool2019; @mammenActiveSchoolTravel2014] indicate that it has the potential to encourage behaviour change and adoption of AST.
 STP facilitators have recommended that additional time and resources are needed to improve the efficacy of STP [@mammenPuttingSchoolTravel2015], which highlights that long-term and sustained efforts driven at the policy level are required to address declining rates of AST.
 
-The ways in which AST is framed seem particularly important to shift parental attitudes and perceptions given their reported influence on children's travel mode to school.
-STP activities heavily focus on education or encouragement [@buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014; @buttazzoniSupportingActiveSchool2018], but parents may not always be receptive to the goals of STP and may be resistant to behaviour change [see @buttazzoniSupportingActiveSchool2018].
+How AST is framed seems particularly important to shift parental attitudes and perceptions given their reported influence on children's travel mode to school.
+STP activities heavily focus on education or encouragement [@buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014; @buttazzoniSupportingActiveSchool2018], but parents may not always be receptive to the goals of STP and may be resistant to behaviour change [@buttazzoniSupportingActiveSchool2018].
 Parents have been found to express different understandings, language, and perceptions than planners of the built environment determinants that influence school travel [@buliungLivingJourneySchool2021].
 This is also true when it comes to other factors like convenience of different modes to school [@langUnderstandingModalChoice2011].
-STP stakeholder groups must pay special attention to parents' understanding of the decline of AST as a problem, which may affect their receptivity to proposed solutions.
-
-The “central organizing idea or story line" of AST, to apply the definition from Gamson and Modigliani [-@gamsonChangingCulture1987], could also affect broader support in the community.
+STP stakeholders must pay special attention to parents' understanding of the decline of AST as a problem, which may affect their receptivity to proposed solutions.
+
+The “central organizing idea or story line" of AST, to apply the definition of framing from Gamson and Modigliani [-@gamsonChangingCulture1987], could also affect broader support in the community.
 Municipal representatives are perceived to be instrumental but the involvement of other stakeholder groups (e.g., busing consortium representatives and local residents) can be lacking [@buttazzoniSupportingActiveSchool2018].
 In Ontario, it would be reasonable to say that AST has become a policy issue on the education and public health agendas over this time as evidenced by the financial contribution from the provincial government.
-The support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the "policy stream" [see @kingdonAgendasAlternativesPublic1984] has been well engaged.
-It is unknown to what degree the general public (i.e., local residents) has been exposed to messaging about AST, which could affect their participation in the STP process as desired by STP facilitators [@buttazzoniSupportingActiveSchool2018].
+The support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
+However, it is unknown to what degree the general public (i.e., local residents) has been exposed to messaging about AST.
 
@@
 For example, parents have been found to view mixed land use as conducive for driving, despite transport planners viewing neighbourhoods with mixed uses as key for encouraging more active travel [@buliungLivingJourneySchool2021].
-Therefore, stakeholder groups involved in STP must make important choices about the proposed solutions and potential benefits that ought to be communicated to parents and the general public about AST to convey its importance as a policy issue and to facilitate adoption of AST.
-Publicly available content about AST, therefore, needs to effectively engage multiple audiences on this policy issue including parents, children, politicians, and school representatives.
+Therefore, stakeholders involved in STP must make conscious choices about the proposed solutions and potential benefits of AST that are communicated to parents and the general public to convey its importance as a policy issue and to facilitate adoption of AST.
+Publicly available content about AST needs to effectively engage multiple audiences on this policy issue, including parents, children, politicians, and school representatives.
 This information should reflect current knowledge from research on school travel, plus content specific to local factors that influence AST, so that the challenges of AST are adequately defined and the opportunities or solutions to address the problems are clear.
-However, it is unknown to what degree STP materials presented to the general public reflect the scope of evidence from the literature on AST.
 
@@
 The latter are a unique group of entities sanctioned by Ontario's Ministry of Education in Ontario 2006.
-Each consortium involves a collaboration between regions and school boards; the consortium's objective is to deliver more efficient and timely transportation services to schools in each region.
+Each consortium involves a collaboration between municipal regions and school boards; the consortium's objective is to deliver more efficient and timely transportation services to schools in each region.
 Non-profit organizations, police services, and advocacy groups are other stakeholders who often play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all initiatives across Ontario.
@@
 This primary criterion was important since our analysis pertains to how such issues are framed to the general public.
-Thus, we included only webpages that were readily accessible, which we defined as requiring no more than 2-4 separate links from the initial Google search.
+Thus, we included only webpages that were readily accessible, which we defined as requiring no more than 4 separate links from the initial Google search.
 
@@
   Total = c("62", "62", "39"),
-  Included = c("32", "28", "9")
+  Retrieved = c("32", "28", "9")
 )
@@
 Finally, we reviewed all of the documents to remove hyphenation by line breaks and to keep hyphenated words together on the same line.
-Any ligatures (e.g., combinations of characters or letters that were not properly detected during the conversion process) were fixed by replacing the unicode sequence of character by inserting the missing sequence of characters.
+Any ligatures (e.g., combinations of characters or letters that were not properly detected during the conversion process) were fixed.
 
@@
 As previously mentioned, a frame is a "central organizing idea or story line that provides meaning" to a public issue or phenomenon [@gamsonChangingCulture1987].
-Scholars in the field of political communications have proposed that communicators, such as the media or an institution, construct the narrative of a frame for policy positions or public issues in order to activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
+Scholars in the field of political communications have proposed that communicators, such as the media or institutions, construct the narrative of a frame for policy positions or public issues in order to activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
 Organized groups of stakeholders can employ similar methods to attract attention to particular issues.
@@
 The way policy issues are framed is ultimately important to understand because it plays a role in either altering or preserving the existing social perceptions.
-This, in turn, can affect whether issues are put on the agenda of policy makers and can determine which solutions are proposed to address the problem [@kingdonAgendasAlternativesPublic1984].
+Finally, the ideas that are communicated by a particular frame can be either positive or negative [@waygoodCO2ValenceFraming2018].
+There is evidence that negative framing may be more effective at motivating individuals to change transport modes to reduce CO2 emissions [@waygoodCO2ValenceFraming2018].
 
@@
 This framing has slowly advanced this issue on public policy agendas as public attention puts pressure on the policy stream to adopt frameworks for action.
-For example, transport planners also use different frames to guide the extent to which transport policies can be adapted to address climate change.
+For example, transport planners use different frames to guide the extent to which transport policies can be adapted to address climate change.
 In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review the representation of issues such as mobility and social exclusion in municipal policies from four western Canadian cities under the current circumstances of climate change.
@@
 
-In a similar way, we hypothesize that STP stakeholder groups in Ontario have framed AST in particular ways to effectively engage multiple audiences on this policy issue including parents, local residents, school representatives, and municipal representatives.
+In a similar way, we hypothesize that STP stakeholder groups in Ontario have framed AST in particular ways to engage multiple audiences on this policy issue including parents, local residents, school representatives, and municipal representatives.
 These groups are likely identifying points of intervention and potential opportunities to build support for and encourage AST.
 
-## 4.2. Topic modelling
+## 4.2. Process
 
@@
 Topic modelling is a machine learning technique that can identify what language and concepts are being communicated by analyzing text.
-This method is more practical for researchers working with large amounts of text because it replaces the manual coding of topics that would normally take place to analyze or summarize textual data [@jacobiQuantitativeAnalysisLarge2016].
+This method is practical for researchers working with large amounts of text because it replaces the manual coding of topics that would normally take place to analyze or summarize textual data [@jacobiQuantitativeAnalysisLarge2016].
 In the data pre-processing phase, we tokenize the text in the documents and create a document-term matrix so that it is in the correct format for analysis.
@@
 These methods can reveal what language and concepts are being communicated to the general public.
-Topic modelling is a popular method for analyzing text from social media platforms [@albalawiUsingTopicModeling2020] or news articles [@jacobiQuantitativeAnalysisLarge2016].
-We estimate latent Dirichlet allocation (LDA) models to classify both the STP and documents according to the topics that are contained within them.
+Topic modelling is a popular method for analyzing text from social media platforms [@albalawiUsingTopicModeling2020] and news articles [@jacobiQuantitativeAnalysisLarge2016].
+We estimate latent Dirichlet allocation (LDA) models to classify both the STP and academic documents according to the topics that are contained within them.
 This method "treats each document as a mixture of topics, and each topic as a mixture of words" [@silgeTextMining2021].
@@
 Table \ref{tab:word-table} shows the most frequent terms found in the municipal, transportation consortia, school board, and academic documents.
-As expected, policy documents and academic papers reference _active travel_, _walking_, _biking_ or _cycling_, and _students_ more than other terms.
-Each corpus also has _safety_ and _traffic_ as common words which suggests congruence on these key factors between the research literature and how AST is framed to the public.
+As expected, policy documents and academic papers reference _active_, _travel_, _walking_, _biking_ or _cycling_, and _students_ more than other terms.
+Each corpus also has _safety_ and _traffic_ as common words which suggests that such concerns are a common reason given for parents driving their children to school.
 The word _physical_ is present in each corpus, but it's not clear what this refers to (e.g, _physical activity_, _physical health_, or the _physical environment_).
 Furthermore, documents from STP stakeholder groups discuss _resources_, _information_, and _services_ about school travel.
-In the section below, the context in which these terms are discussed is explored further.
-
 Unlike the academic papers, policy documents include the words _route_ or _routes_ as frequent terms.
-This could reflect the role of STP stakeholder groups in identifying safe routes to school to share with parents or families, as well as the STP emphasis on making the physical environment safer for AST.
+This could indicate the presence of "safe routes to school" in the policy corpus, as well as the role of STP stakeholder groups in identifying safe routes to school to share with parents or families.
+In the section below, the context in which these terms are used is explored further.
+
 The academic corpus differs from the policy documents in that _parents_ and _distance_ are the second and third most common terms.
 In addition, _time_, _factors_, _environment_, and _age_ are also identified in the academic papers.
+The prevalence of these terms is consistent with an academic focus on exploring the variables that influence mode choice.
 These words are absent from the list of common words in policy documents.
@@
 # Create new data frame with the cleaned corpus 
-AcademicTextDF <- data.frame(text = sapply(academic_corpus, as.character), stringsAsFactors = FALSE)
+AcademicTextDF <- data.frame(text = sapply(academic_corpus_repaired, as.character), stringsAsFactors = FALSE)
 
@@
 consortia_words <- consortium_vocab[-c(971),] %>% slice(993:968)
-academic_words <- academic_vocab[-c(1302, 1297),] %>% slice(1304:1278)
+academic_words <- academic_vocab[-c(1289, 1284),] %>% slice(1291:1265)
 ```
@@
 
+However by examining document frequency, we found that some terms are not present in all policy documents.
+This suggests that although documents pertain to the subject of school travel, some stakeholders across Ontario are not disseminating information about AST.
+For example, a document may discuss active travel but not to school.
+Some documents present school travel options by bus but not by active modes.
+We manually searched the policy corpus and found that 48% of documents mention AST and 16% mention STP.
+This confirms that many municipalities, school boards, and transportation consortia are not promoting AST through their webpages or indicating their involvement in the STP process.
+Instead, inclement weather and its impacts on busing is a common topic addressed in school board and transportation consortia documents.
+
 ## 5.2. Bigrams and concordances
@@
 Bigrams refer to a pair of consecutive words.
-We use the `unnest_tokens` function from the _tidytext_ package to determine the bigrams.
+We used the `unnest_tokens` function from the _tidytext_ package to determine the bigrams.
 Figures \ref{fig:city-visual}, \ref{fig:consortia-visual}, and \ref{fig:school-visual} show the bigrams that occur more than 5 times for each set of policy documents.
 These figures help to make further sense of the word frequencies reported above, and highlight the main ideas that are presented to the public in each of the policy corpora.
+The directional arrows indicate the arrangement of the words (e.g., active travel and not travel active) and the colour gradient of the arrows corresponds to the most frequently mentioned pairs (e.g., bigrams with darker arrows are found more often).
+
 Municipalities primarily discuss _physical activity_ (n = 53) and _public health_ (n = 19) in the context of AST.
@@
 Finally, transportation consortia documents highlight topics such as _physical activity_ (n = 10), _pedestrian safety_ (n = 8), _crossing guards_ (n = 6), _travel planning_ (n = 6), and _walk zones_ (n = 6).
-Biking or cycling is notably absent from transportation consortia documents.
-Overall, the policy documents There appears convey an emphasis on the built environment, rather than household decision-making.
+Biking and cycling are notably absent from transportation consortia documents.
+Overall, the policy documents appear to convey an emphasis on the built environment, rather than household decision-making.
 
@@
 # Converting corpus to tidytext data type 
-td_academic_corpus <- tidy(academic_corpus)
+td_academic_corpus <- tidy(academic_corpus_repaired)
 
@@
 
-```{r city-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:city-visual}Most common bigrams found in the municipal or regional government documents."}
+```{r city-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:city-visual}Most common bigrams found in the municipal and regional government documents."}
 ggraph(municipal_bigram_graph, layout = "fr") +
@@
 
-We then combine all municipality, school board, and transportation consortia documents into one "policy" corpus.
+We then combined all municipality, school board, and transportation consortia documents into one "policy" corpus.
 This enabled us to examine and visualize the most common bigrams found across all of the material in Ontario that was collected for this study.
@@
 In addition to the bigrams already identified above, we also found _mental health_, _walk day_, and _green communities_ as common pairs of consecutive words.
-The latter terms represent the significant involvement of the non-profit organization in supporting AST initiatives through the Ontario Active School Travel program.
+_Green Communities Canada_ is a non-profit organization that has significantly supported AST initiatives through the Ontario Active School Travel program so the high frequency of this term in the policy corpus is not surprising.
 Overall, the policy documents from STP stakeholder groups seem to focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or considerations; and iv) supports for AST.
-This interpretation indicates that the general public accessing information about AST in Ontario is informed about an adequate range of content related to this issue.
-
-Next, we analyze bigrams in the academic corpus separately to make comparisons with the policy corpus.
+This interpretation indicates that the general public accessing information about AST in Ontario is informed about a wide range of content related to this issue.
+
+Next, we analyzed bigrams in the academic corpus separately to make comparisons with the policy corpus.
 Figure \ref{fig:academic-visual} indicates that academic papers include several common bigrams that were also found in the policy documents including _physical activity_ (n = 1566), which is the top bigram, _traffic safety_ (n = 308), and _safe routes_ (n = 268).
@@
 Academic papers also often discuss _distance home_ (n = 258), _car ownership_ (n = 254), _household income_ (n = 254), and _population density_ (n = 205), which are factors that have been found to influence AST.
-It is evident that many papers investigate gender differences in AST given that _boys girls_ (n = 211) is another common bigram.
+Many papers also investigate gender differences in AST given that _boys girls_ (n = 211) is another common bigram.
 Finally, the presence of _statistically significant_ among the top bigrams underscores that some researchers aim to identify determinants using statistical measures.
-We find that the academic corpus focuses on a greater range of topics than found in the policy documents.
+We found that the academic corpus focuses on a greater range of topics than found in the policy documents.
 
@@
 
-We interpret the most common bigrams from the policy corpus (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholder groups are focusing on and communicating to the public about AST.
-We then use the `kwic` function from the _quanteda_ package to better understand the context of these key ideas.
-Table \ref{tab:policy-concordance} presents some examples of the context that was extracted from select policy documents to demonstrate how the most common bigrams are communicated to the public.
+We interpreted the most common bigrams from the policy corpus (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholder groups are focusing on and communicating to the public about AST.
+We then used the `kwic` function from the _quanteda_ package to better understand the context of these key ideas.
+Table \ref{tab:policy-concordance} presents some examples of the context that were extracted from select policy documents to demonstrate how the most common bigrams are communicated to the public.
 
@@
     "We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments.",
-    "ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.",
+    "Active and Sustainable School Travel (ASST) not only improves physical and mental health but contributes to a healthier environment and safer streets.",
     "Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.")
@@
 policy_dtm <- DocumentTermMatrix(policy_corpus)
-academic_dtm <- DocumentTermMatrix(academic_corpus)
+academic_dtm <- DocumentTermMatrix(academic_corpus_repaired)
 ```
@@
 
-```{r evaluate-lda, echo=FALSE}
+```{r evaluate-lda, include=FALSE}
 
@@
 
-Finally, we conduct topic modelling to examine the different topics found in the policy and academic corpora.
-We focus on the policy corpus, instead of individually assessing the municipal, school, and consortia documents, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario.
-To determine the number of discrete topics in each corpus, we use the _ldatuning_ package.
-We then use the `LDA` function from the _topicmodels_ package to estimate an LDA model for each group of documents.
+Finally, we conducted topic modelling to examine the different topics found in the policy and academic corpora.
+We focused on the policy corpus, instead of assessing the municipal, school, and consortia documents separately, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario.
+To determine the number of discrete topics in each corpus, we used the _ldatuning_ package.
+We then used the `LDA` (latent Dirichlet allocation) function from the _topicmodels_ package to estimate an LDA model for each group of documents.
 The parameters from the _ldatuning_ package suggest that the policy corpus has between 7 and 9 topics and the academic corpus has between 17 and 25 topics.
@@
 
-In the policy corpus, we interpret the following topics based on the cluster of words: (1) resources for walking; (2) walking; (3) supporting active travel; (4) bicycling and the environment; (5) benefits of active travel; (6) safety; and (7) busing information and eligibility.
-These topics indicate that STP stakeholder groups are sending the message that walking and bicycling to school are healthy travel modes for students, particularly as a means to get physical activity.
-We also found that there is information shared to support parents and students in using active modes to school such as the availability of cycling lanes or route tips for walking.
-STP stakeholder groups are appear to be addressing the issue of safety.
-
-The academic corpus has a higher number of topics likely due to the volume of papers that were sourced.
+In the policy corpus, we identified the following topics based on the cluster of words: (1) resources for walking; (2) walking; (3) supporting active travel; (4) bicycling and the environment; (5) benefits of active travel; (6) safety; and (7) busing information and eligibility.
+These topics indicate that STP stakeholder groups are sending the message that walking and bicycling to school are healthy travel modes for students, particularly in terms of physical activity.
+We also found that information is shared to support parents and students in using active modes to school, for example regarding the availability of cycling lanes and tips for route choice for walking.
+
+The academic corpus has a higher number of topics likely due to the volume of papers included.
 The following topics were identified based on the clusters of words: (1) built environment (2) walking distance; (3) AST interventions; (4) parental barriers to walking; (5) behaviours and attitudes; (6) bicycling; (7) social environment; (8) children's independent mobility; (9) modeling trip choice; (10) adolescents and physical activity; and (11) safe routes to school programs.
@@
 
-We conclude that the policy corpus primarily frames AST as a health and environmental issue.
-Policy documents do not reflect the diversity of content found in the academic papers and instead focus on a few factors.
-STP stakeholder groups appear to position walking, bicycling, or rolling to school as beneficial to individual health, as an opportunity for physical activity or to improve mental health, and to the broader community through a reduction in traffic and vehicle emissions.
-Here, we present some examples from the policy documents to illustrate how the health and environmental frames are communicated:
+## 5.4. Frames
+
+Based on the identified  bigrams and topics, we determined that the policy corpus primarily frames AST as a health and environmental issue.
+STP stakeholder groups appear to position walking, bicycling, or rolling to school as beneficial to individual health, via physical activity and improved mental health, and to the broader community through a reduction in traffic and vehicle emissions.
+Here, we present some examples from the policy documents to illustrate how the health and environmental frame is communicated:
 
@@
 
-> _Walking to school is a great way to add physical activity into your child’s busy day._ (Region of Haldimand-Norfolk Region)
-
 > _Active school travel is a great way for children to be physically active, which is associated with improved physical and mental health, while making school zones safer, by reducing traffic volumes at and around schools._(Region of Leeds, Grenville and Lanark)
@@
 
-However by examining document frequency (see Section 5.1), we found that some terms are not present in all policy documents.
-This suggests that although documents pertain to the subject of active travel or school travel, some stakeholders across Ontario are not disseminating information about AST.
-For example, a document may discuss active travel but not to school or school travel but only by bus and not by active modes.
-We manually searched the policy corpus and found that 48% of documents mention AST and 16% mention STP.
-This confirms that many municipalities, school boards, and transportation consortia are not promoting AST through their webpages or indicating their involvement in the STP process.
-Instead, inclement weather and impacts to busing is a common topic addressed in school board and transportation consortia documents.
-
-Furthermore, we found that some policy documents make direct reference to topics found in the academic papers.
-For example, some policy documents encourage AST programs that have been researched and evaluated in the literature, such as walking school buses, or explain how an increase in AST will reduce parent safety concerns.
-
-> _ For their health, safety, environment and community: Kids learn healthy habits and concentrate better in class; One less car (yours) reduces traffic and parking problems in school zones; Teach your kids about traffic safety; Start a walking school bus; your kids make friends in every grade, and that can prevent bullying._ (City of Guelph)
+Furthermore, we found that policy documents make claims about the benefits of AST that are consistent with the findings of academic research and evaluation.
+
+> _For their health, safety, environment and community: Kids learn healthy habits and concentrate better in class; One less car (yours) reduces traffic and parking problems in school zones; Teach your kids about traffic safety; Start a walking school bus; your kids make friends in every grade, and that can prevent bullying._ (City of Guelph)
 
@@
 
-The secondary frame for AST in policy documents is the opportunity or prospect of behaviour change.
-Some cities and schools explain how children and parents can leave the car at home and make the journey to school on foot or by bike by describing efforts to make AST safer.
+The secondary frame in policy documents is that AST is accessible and feasible for children and parents.
+The documents indicate that there is an opportunity for or prospect of behaviour change.
+Some cities and schools explain how children and parents can leave the car at home and make the journey to school on foot or by bike.
 This frame encourages the public to evaluate their own travel decisions and to access resources (e.g., walking skills checklist) that will help them make AST a first choice.
-Some documents emphasize the role of the parent in creating opportunities for AST in their household or neighbourhood, however few documents address the main barriers as perceived by parents (e.g., distance, travel arrangements for multiple people, or convenience).
 Examples of this secondary frame include:
 
-> _A way to make sure your child is safe while walking to school is with a 'walking school bus.' Here are some tips for a walking school bus: Invite families who live nearby to walk; Pick a route and take a test walk; Take side streets and paths that are less busy with traffic; Decide how often the group will walk together; Talk with your boss to adjust your day; Have fun!
-(City of Ottawa)
+> _A way to make sure your child is safe while walking to school is with a 'walking school bus.' Here are some tips for a walking school bus: Invite families who live nearby to walk; Pick a route and take a test walk; Take side streets and paths that are less busy with traffic; Decide how often the group will walk together; Talk with your boss to adjust your day; Have fun!_ (City of Ottawa)
 
@@
 
-Finally, the policy documents discuss proposed solutions to encourage AST.
-STP stakeholder groups seem to be communicating that AST is possible and safe as a result of improvements to the built environment and available resources for parents and children.
-A final focus in the policy documents is on various efforts that are underway to support AST including route planning.
-A few examples include:
+Finally, both AST frames present solutions to encourage AST.
+STP stakeholder groups seem to be communicating that AST is a healthy and easy option as a result of policy changes (e.g., available resources for parents and children) and improvements to the built environment.
+This could include examples of various efforts that are underway to support AST including route planning.
 
@@
 
-## 6.1. Framing in STP documents
-
-Using topic modelling, we analyzed how AST is framed in documents available to the general public on the websites of STP stakeholder groups in Ontario.
+## 6.1. Current AST frames in Ontario
+
+Using natural language processing techniques, we analyzed how AST is framed in 69 documents available to the public on the websites of STP stakeholder groups in Ontario.
+Two main frames in the policy corpus were identified based on the most common bigrams and topics from the LDA model.
+
 We found that AST is primarily framed to parents as beneficial to the health and wellbeing of children and to environmental sustainability.
-This was confirmed by the most common bigrams identified in the policy corpus, as well as the topics identified by the LDA model.
-The policy documents adequately reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance and cognitive development need to be studied further to produce stronger evidence [@westmanChapterThreeTravel2020].
+The policy documents reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance are less well-supported in the extant literature [@westmanChapterThreeTravel2020].
 STP stakeholder groups also communicate that increasing AST may reduce traffic near and around schools.
-This presumably is communicated to alleviate parental concerns about traffic and safety [@eversParentSafetyPerceptions2014; @mammenUnderstandingDriveEscort2012; @rothmanAssociationsParentsPerception2015; @wilsonUnderstandingChildParent2018] or reduce the frequency of risky behaviours from drivers around schools [@rothmanSchoolEnvironmentStudent2017].
-However, the documents do not explain why declining rates of AST are a problem for the particular community or convey any urgency to this issue so that it attracts the attention of parents, the general public, or policy makers.
-Communicating the potential outcomes of increased AST may be persuasive arguments to motivate behaviour change, but these documents do not appear to encourage parents or the general public to view their behaviour as problematic or unhealthy for their children's development.
-For example, Canadian parents who escort their children to school have reported concerns about traffic volume around schools [@mammenUnderstandingDriveEscort2012], but may not recognize that their own behaviour contributes to the problem that is perceived to prevent their child from safely walking or bicycling to school [@collinsSafeJourneysEnterprising2001].
-
-The secondary frame of AST that we interpreted based on the LDA model is the opportunity or prospect of behaviour change.
-STP stakeholder groups identified different ways that parents could encourage or support their child(ren) to commute to school by using active modes.
+This is conveyed presumably to alleviate parental concerns about traffic and safety [@eversParentSafetyPerceptions2014; @mammenUnderstandingDriveEscort2012; @rothmanAssociationsParentsPerception2015; @wilsonUnderstandingChildParent2018] or to reduce the frequency of risky behaviours from drivers around schools [@rothmanSchoolEnvironmentStudent2017].
+
+In the secondary frame, AST is presented as an accessible and feasible way for children to travel to and from school.
+Children and parents are encouraged to adopt new travel behaviours.
+STP stakeholder groups identified different ways that parents could encourage or support their children to commute to school by using active modes.
 Some school boards and municipalities also shared resources such as walking tip sheets and guidance for starting a walking school bus.
 Other advice included dropping children off one or two blocks away from school so that they could walk or bike part of the trip.
-The general emphasis is communicating information that could change parental perceptions about the ease of their children using active modes to school, which may be seen by STP stakeholder groups as a "modifiable" factor [see @riaziCorrelatesChildrenIndependent2019].
+The general emphasis of this frame is communicating information that could change parental perceptions about the ease of their children using active modes to school, which may be seen by STP stakeholder groups as a "modifiable" factor [see @riaziCorrelatesChildrenIndependent2019].
 In turn, this could encourage parents to modify their routines and incorporate opportunities for their children to use active modes to school.
 
-We found that interpersonal behaviour changes achieved through educational strategies and engineering changes (e.g., traffic calming measures, reduced speed limits, etc.) are communicated to the general public as potential solutions to address the decline of AST.
-This reflects findings from the AST literature [@panterAttitudesSocialSupport2010], but these solutions have to sufficiently address real and perceived barriers from parents about the household environment and the built environment (see Section 2.2).
-In most documents, STP stakeholder groups provide parents with resources that help them switch modes for the school commute and/or on reassure them that the built environment has become safer and friendlier to active travelers as a result of infrastructure or policy improvements.
-As previously noted, the documents do not appear to present a strong "call to action" that urges behaviour change for parents or the general public, which may affect the success of STP interventions.
-On the other hand, the emphasis on engineering changes may reflect the strong engagement of the "policy stream" [@kingdonAgendasAlternativesPublic1984] and the feasible options to address the problem, since engineering staff and municipal representatives are common STP stakeholders [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015].
-
-Given the range of factors that influence AST in a Canadian setting [_inter alia_, see @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], STP stakeholder groups must decide which points of intervention that they can reasonably have some influence towards.
-This would also depend on the local context to ensure that barriers to AST as perceived by parents are addressed.
-It could be that STP stakeholder groups perceive to have more control over micro-scale elements of the built environment, like traffic calming measures or speed limits, rather "non-modifiable" factors like street density or land use mix.
-It would certainly be much more difficult for STP stakeholder groups to influence the number of trips to different destinations that households need to make or to intervene in residential location, which affects distance to school.
-A focus on changing parental perceptions is recommended by many scholars since parents are the "gatekeeper" for children's mobility, but the information communicated by STP stakeholder groups in Ontario should reflect a broader range of factors that influence AST.
+Both frames present the AST issue in a positive light.
+Neither frame appears to explain why declining rates of AST are a problem or convey any urgency to this issue so that it attracts the attention of parents, the general public, or policy makers.
+Communicating the potential outcomes of increased AST may be persuasive arguments to motivate behaviour change, but these frames do not seem to encourage parents or the general public to view their current behaviour as problematic or unhealthy for their children's development and their community.
+Thus, behaviour change is presented as an option for some but not an imperative for all.
+For example, parents who drive their children to school have reported concerns about traffic volume around schools [@mammenUnderstandingDriveEscort2012], but may not recognize that their own behaviour contributes to the problem that is perceived to prevent their child from safely walking or bicycling to school [@collinsSafeJourneysEnterprising2001].
+Reynard et al.
+[-@reynardGrowthResilienceHow2021] similarly found in their analysis of Canadian municipal documents that one of the dominant frames presented the adoption of behaviours to help mitigate the climate crisis as a choice but not "the expected norm".
+
+We found that the proposed solutions in the secondary frame to increase AST align with different levels of the socioecological model: 1) behaviour change from individuals or households making different travel decisions; 2) policies like STP that create resources for AST; and 3) engineering solutions like bicycle lanes.
+This reflects findings from the AST literature that a range of solutions are needed to address different factors that influence AST [_inter alia, see_ @mitraIndependentMobilityMode2013; @panterAttitudesSocialSupport2010].
+The recognition of engineering changes may reflect the strong engagement of the "policy stream" [@kingdonAgendasAlternativesPublic1984] since engineering staff and municipal representatives are common STP stakeholders in Canada [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015], as well as the evidence that the built environment influences mode choice to school.
+Although it is beyond the scope of this paper to assess whether the proposed solutions are perceived to be sufficient by parents for increasing AST.
 
@@
 
-There is also a noticeable lack of focus on individual and interpersonal determinants of AST in the policy documents.
-For example, the role of convenience and inclement weather in shaping household travel decisions [@buliungSchoolTravelPlanning2011] or the age at which children become allowed to travel by active modes or independently [@mammenUnderstandingDriveEscort2012] were not discussed.
-The desire to escort children to school, which has been noted by parents as a reason to continue driving [@westmanWhatDrivesThem2017], is also not adequately addressed by STP stakeholder groups.
-The complexity of travel arrangements that must be coordinated by households [see @buliungLivingJourneySchool2021] and the dominant parenting culture to protect children from risk [@riaziChildrenIndependentMobility2018] are likewise overlooked.
-STP stakeholders may wish to emphasize to parents that older children have greater traffic safety and cognitive abilities to navigate their own routes to school, which could encourage parents to develop their child(ren)'s travel skills over time.
-Additional attention should be paid to the reasons why parents perceive driving to be more convenient.
-
-Coming back to Kingdon's Multiple Streams Framework [-@kingdonAgendasAlternativesPublic1984], we posited that STP stakeholder groups need to raise awareness about the AST issue among parents and the general public through the problem stream.
-This could influence perceptions about the issue and encourage behaviour change.
-Based on the policy documents, it is not obvious that AST has declined significantly over the past few decades in Canada or that this issue merits urgent attention.
-Many municipalities, schools, and transportation consortia in Ontario use similar content in their public documents about AST.
-It would be worthwhile for STP stakeholder groups to frame the decline of AST as a "problem" worth addressing with information specific to each local context.
-STP stakeholders also need to ensure that their communication accounts for the ways in which Canadian parents perceive the built environment in different ways than planners [see @buliungLivingJourneySchool2021].
-If there is "conceptual asymmetry" as Buliung et al.
-[-@buliungLivingJourneySchool2021] identified, the materials disseminated by STP stakeholders may not resonate or reach parents.
-Future research or STP activities should investigate how parents or the general public respond to messages or information that encourages the adoption of AST and evaluate how effective they are to motivate behaviour change.
-It would be helpful to know which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST.
+STP stakeholders should problematize the significant decline in AST that has occurred over recent decades in Canada and emphasize that this issue merits urgent behaviour change.
+A study investigating the influence of different valence framings of CO2 emissions on transport mode shift found that positive framing can be less effective than negative framing [@waygoodCO2ValenceFraming2018].
+Policy documents should make it clear that continued use of nonactive modes to school can deprive children of opportunities to increase physical activity and to gain health and social benefits.
+
+There is a noticeable lack of focus on certain household determinants of AST in the two frames that needs to be addressed.
+For example, the role of convenience and inclement weather in shaping household travel decisions [@buliungSchoolTravelPlanning2011] and the complexity of travel arrangements that must be coordinated by households [see @buliungLivingJourneySchool2021] were not found to be discussed.
+The desire to escort children to school, which has been noted by parents as a reason to continue driving [@westmanWhatDrivesThem2017], is also not adequately addressed by STP stakeholders.
+Parental assessment of a child's ability to handle the journey to school was likewise overlooked despite its role in decision making for mode choice to school [@faulknerWhatQuickestEasiest2010].
+Framing AST as a developmental opportunity or a rite of passage that children have been denied could challenge the prevailing culture of risk which discourages parents from letting their children use active modes to school.
+In communities with low AST uptake, STP stakeholders may wish to emphasize the negative effects of parents continuing to drive children to and from school.
+A negative framing that challenges the social norm of driving could be more motivational to shift modes, which would be consistent with other findings [@waygoodCO2ValenceFraming2018].
+
+Future research and evaluation by STP stakeholders should investigate how parents or the general public respond to messages or information that encourages the adoption of AST and evaluate which are most effective.
+It would be helpful to understand which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST.
 This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.
-
-Although the "policy stream" appears to have been adequately engaged in Ontario communities, it could be that the decline of AST has not been sufficiently framed as "problematic" to warrant more widespread awareness or solutions.
-If Canadian STP stakeholder groups wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different material that communicates why this issue is important to the general public, regardless of whether they currently have children commuting to/from school.
-The "political steam" could also be further engaged by working with advocacy groups who could attract more support from a broader coalition of individuals.
-
-Finally, Rothman et al.
-[-@rothmanDeclineActiveSchool2018] note that local solutions to address specific school challenges are needed, and we extend this recommendation to include local context in STP messaging about AST.
-Instead of generic content about AST, stakeholders involved in STP should produce more information that specifically responds to parents' perceived barriers and challenges that were identified in that local context.
-For example, STP materials could explain how known concerns in a particular municipality or school area have been addressed through local solutions.
-This could reflect that solutions have been identified based on what was heard from the community.
+If Canadian STP stakeholders wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different materials that communicate why this issue is important to the general public, regardless of whether they currently have children commuting to/from school.
+The "political stream" could also be further engaged by working with advocacy groups who could attract more support from a broader coalition of individuals.
+
+We also contend that the ways in which the AST issue is framed can affect the policy process, as outlined in Kingdon's [-@kingdonAgendasAlternativesPublic1984] Multiple Streams Framework (MSF), through all three streams (i.e., problem, policy, and politics).
+This framing can ultimately impact the timing and success of a "window of opportunity" to enact policy changes that address the decline of AST in Canada.
 
@@
 
-A limitation of this study is that we only analyzed texts that were easily accessible to the general public on the websites of STP stakeholder groups in Ontario.
+A limitation of this study is that we only analyzed texts that were easily accessible to the general public on the websites of STP stakeholders in Ontario.
 Parents likely receive information about AST directly from schools, which may contain more content that reflects the local barriers to AST.
@@
 
-We used text mining and topic modelling to examine how different school travel planning stakeholder (STP) groups in Ontario frame the issue of AST.
-STP stakeholder groups frame AST as a health and environmental issue that can be addressed through household behaviour change and engineering solutions.
-Policy documents reveal that STP stakeholder groups are focusing on "modifiable factors" such as parental perceptions or micro-scale elements in the built environment to increase rates of AST.
+We used natural language processing techniques to examine how different school travel planning (STP) stakeholders in Ontario frame the issue of AST.
+STP stakeholders frame AST as an accessible and feasible way to travel to school that is valuable to children's health and to the environment.
+STP stakeholders are communicating that this issue can be addressed through household behaviour change and policy solutions.
+Policy documents reveal that STP stakeholders are focusing on "modifiable factors" such as parental perceptions or micro-scale elements in the built environment to increase rates of AST.
 However, AST may not be framed sufficiently as a "problem" that requires urgent intervention, which may impact how parents respond to behaviour change initiatives and limit awareness in the general public.
-In their public materials about AST, STP stakeholder groups should present solutions for a broader range of factors that influence AST and emphasize why AST rates should increase in local communities.
+In their public materials about AST, STP stakeholders emphasize why AST rates should increase in local communities and how the negative effects of nonactive modes to school may impact children's health and wellbeing.
+
+Acknowledgments
+===================
+
+This research was completed using open software, and the authors wish to acknowledge the developers of the following `R` packages: `dplyr` [@R-dplyr], `ggraph` [@R-ggraph], `ggplot2` [@R-ggplot2], `igraph` [@R-igraph], `pdftools` [@R-pdftools], `readr` [@R-readr], `reshape2` [@R-reshape2], `stringr` [@R-stringr], `text2vec` [@R-text2vec], `textdata` [@R-textdata], `tidyr` [@R-tidyr], `tidytext` [@R-tidytext], `tm` [@R-tm], `tools` [@R-tools], `topicmodels` [@R-topicmodels], `widyr` [@R-widyr], `word2vec` [@R-word2vec], `wordcloud` [@R-wordcloud], `DiagrammeR` [@R-diagrammeR], and `kableextra` [@R-kableextra].
 

### 2022-01-27 AST-Framing-Ontario/AST-Framing-Ontario.tex

@@
 \bibliographystyle{elsarticle-harv}
-\usepackage{graphicx}
 \ifxetex
@@
 OAST has awarded over 2 million Canadian dollars and provided resources
-for over 25 projects across Ontario. Many communities implemented school
+to over 25 projects across Ontario. Many communities implemented school
 travel planning (STP), along with encouragement activities like walking
@@
 
-In this paper, we use text mining and topic modelling to examine how
-three STP stakeholder groups in Ontario (i.e., municipalities, school
-boards, and transportation consortia) frame the issue of AST. We
-assembled a corpus of texts from webpages that can be considered an
-important source of information for the general public or parents who
-are interested in AST. We examine word frequency, bigrams, and
-concordances in these selected documents, and also identify key topics
-presented by each stakeholder group. We then compare the findings from
-these documents to a selection of studies on AST and explore the extent
-to which there is concordance between the literature on AST and
-materials shared with the public.
+In this paper, we use natural language processing to examine how three
+STP stakeholder groups in Ontario (i.e., municipalities, school boards,
+and transportation consortia) frame the issue of AST. We assembled a
+corpus of texts from webpages that can be considered an important source
+of information for the general public or parents who are interested in
+AST. We examine word frequency, bigrams, and concordances in these
+selected documents, and also identify key topics presented by each
+stakeholder group. We then compare the findings from these documents to
+a selection of studies on AST and explore the extent to which there is
+concordance between the literature on AST and materials shared with the
+public.
 
@@
 2013). Rather than describing an extensive list of factors that
-influence AST and mode choice in Canada, which has been covered
-elsewhere (e.g., Mammen et al., 2012; Mitra, 2013; Rothman et al., 2018;
-Wilson et al., 2018), we briefly discuss a few potentially modifiable
-determinants that may be targeted for change through STP.
+influence AST and mode choice in Canada (e.g., Mammen et al., 2012;
+Mitra, 2013; Rothman et al., 2018; Wilson et al., 2018), we discuss a
+few potentially modifiable determinants that may be targeted for change
+through STP.
 
@@
 demonstrates that the ``policy stream'' (see Kingdon, 1984) has been
-well engaged. It is unknown to what degree the general public (i.e.,
-local residents) has been exposed to messaging about AST, which could
-affect their participation in the STP process as desired by STP
-facilitators (Buttazzoni et al., 2018).
+well engaged. However, it is unknown to what degree the general public
+(i.e., local residents) has been exposed to messaging about AST, or how
+they view the AST issue, which could affect their participation in the
+STP process as desired by STP facilitators (Buttazzoni et al., 2018).
 
@@
 involved in STP must make important choices about the proposed solutions
-and potential benefits that ought to be communicated to parents and the
-general public about AST to convey its importance as a policy issue and
-to facilitate adoption of AST. Publicly available content about AST,
+and potential benefits of AST that ought to be communicated to parents
+and the general public to convey its importance as a policy issue and to
+facilitate adoption of AST. Publicly available content about AST,
 therefore, needs to effectively engage multiple audiences on this policy
@@
 \midrule
-\cellcolor{gray!6}{active} & \cellcolor{gray!6}{248} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{active} & \cellcolor{gray!6}{124} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{active} & \cellcolor{gray!6}{67} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{5137} & \cellcolor{gray!6}{222}\\
-travel & 126 & 20 & bus & 120 & 20 & walking & 55 & 8 & parents & 3946 & 211\\
-\cellcolor{gray!6}{walking} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{travel} & \cellcolor{gray!6}{103} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{49} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{distance} & \cellcolor{gray!6}{3271} & \cellcolor{gray!6}{205}\\
-bike & 87 & 15 & information & 65 & 21 & travel & 41 & 8 & students & 2960 & 173\\
-\cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{78} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{57} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{2753} & \cellcolor{gray!6}{171}\\
+\cellcolor{gray!6}{active} & \cellcolor{gray!6}{248} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{active} & \cellcolor{gray!6}{124} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{active} & \cellcolor{gray!6}{67} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{5059} & \cellcolor{gray!6}{220}\\
+travel & 126 & 20 & bus & 120 & 20 & walking & 55 & 8 & parents & 3927 & 209\\
+\cellcolor{gray!6}{walking} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{travel} & \cellcolor{gray!6}{103} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{49} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{distance} & \cellcolor{gray!6}{3252} & \cellcolor{gray!6}{203}\\
+bike & 87 & 15 & information & 65 & 21 & travel & 41 & 8 & students & 2956 & 171\\
+\cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{78} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{57} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{2739} & \cellcolor{gray!6}{170}\\
 \addlinespace
-safety & 71 & 21 & walk & 53 & 13 & safety & 32 & 6 & environment & 2631 & 202\\
-\cellcolor{gray!6}{health} & \cellcolor{gray!6}{65} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{weather} & \cellcolor{gray!6}{40} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{help} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{activity} & \cellcolor{gray!6}{2371} & \cellcolor{gray!6}{209}\\
-physical & 63 & 18 & safety & 40 & 19 & schools & 25 & 9 & traffic & 2353 & 208\\
-\cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{59} & \cellcolor{gray!6}{20} & \cellcolor{gray!6}{safe} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{children} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{choice} & \cellcolor{gray!6}{2299} & \cellcolor{gray!6}{169}\\
-road & 56 & 13 & services & 37 & 17 & community & 24 & 7 & physical & 2256 & 215\\
+safety & 71 & 21 & walk & 53 & 13 & safety & 32 & 6 & environment & 2585 & 200\\
+\cellcolor{gray!6}{health} & \cellcolor{gray!6}{65} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{weather} & \cellcolor{gray!6}{40} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{help} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{2334} & \cellcolor{gray!6}{206}\\
+physical & 63 & 18 & safety & 40 & 19 & schools & 25 & 9 & choice & 2295 & 167\\
+\cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{59} & \cellcolor{gray!6}{20} & \cellcolor{gray!6}{safe} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{children} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{activity} & \cellcolor{gray!6}{2265} & \cellcolor{gray!6}{207}\\
+road & 56 & 13 & services & 37 & 17 & community & 24 & 7 & physical & 2238 & 213\\
 \addlinespace
-\cellcolor{gray!6}{activity} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{bus} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{trips} & \cellcolor{gray!6}{2194} & \cellcolor{gray!6}{170}\\
-schools & 52 & 14 & parents & 32 & 17 & route & 17 & 5 & car & 2148 & 195\\
-\cellcolor{gray!6}{children} & \cellcolor{gray!6}{47} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{sustainable} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{zone} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{2140} & \cellcolor{gray!6}{204}\\
-plan & 45 & 16 & children & 31 & 14 & resources & 16 & 6 & time & 2101 & 218\\
-\cellcolor{gray!6}{students} & \cellcolor{gray!6}{44} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{child} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{factors} & \cellcolor{gray!6}{2101} & \cellcolor{gray!6}{216}\\
+\cellcolor{gray!6}{activity} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{bus} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{trips} & \cellcolor{gray!6}{2164} & \cellcolor{gray!6}{168}\\
+schools & 52 & 14 & parents & 32 & 17 & route & 17 & 5 & car & 2140 & 193\\
+\cellcolor{gray!6}{children} & \cellcolor{gray!6}{47} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{sustainable} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{zone} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{2111} & \cellcolor{gray!6}{202}\\
+plan & 45 & 16 & children & 31 & 14 & resources & 16 & 6 & time & 2091 & 216\\
+\cellcolor{gray!6}{students} & \cellcolor{gray!6}{44} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{child} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{factors} & \cellcolor{gray!6}{2083} & \cellcolor{gray!6}{214}\\
 \addlinespace
-walk & 43 & 18 & day & 29 & 13 & safe & 15 & 5 & child & 2085 & 187\\
-\cellcolor{gray!6}{public} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{routes} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{200}\\
-community & 37 & 19 & physical & 28 & 11 & physical & 15 & 7 & public & 1983 & 208\\
-\cellcolor{gray!6}{safe} & \cellcolor{gray!6}{34} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{health} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{age} & \cellcolor{gray!6}{1783} & \cellcolor{gray!6}{211}\\
-benefits & 32 & 17 & inclement & 25 & 11 & traffic & 13 & 6 & urban & 1768 & 200\\
+walk & 43 & 18 & day & 29 & 13 & safe & 15 & 5 & child & 2060 & 185\\
+\cellcolor{gray!6}{public} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{routes} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{1985} & \cellcolor{gray!6}{198}\\
+community & 37 & 19 & physical & 28 & 11 & physical & 15 & 7 & public & 1973 & 206\\
+\cellcolor{gray!6}{safe} & \cellcolor{gray!6}{34} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{health} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{age} & \cellcolor{gray!6}{1774} & \cellcolor{gray!6}{209}\\
+benefits & 32 & 17 & inclement & 25 & 11 & traffic & 13 & 6 & urban & 1749 & 198\\
 \addlinespace
-\cellcolor{gray!6}{play} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{eligibility} & \cellcolor{gray!6}{24} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{support} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{home} & \cellcolor{gray!6}{1715} & \cellcolor{gray!6}{199}\\
-resources & 30 & 13 & consortium & 24 & 9 & families & 13 & 5 & social & 1713 & 191\\
-\cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{way} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{different} & \cellcolor{gray!6}{1713} & \cellcolor{gray!6}{215}\\
-routes & 27 & 13 & service & 22 & 11 & student & 12 & 5 & mobility & 1659 & 138\\
-\cellcolor{gray!6}{lanes} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{•} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{significant} & \cellcolor{gray!6}{1650} & \cellcolor{gray!6}{208}\\
+\cellcolor{gray!6}{play} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{eligibility} & \cellcolor{gray!6}{24} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{support} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{different} & \cellcolor{gray!6}{1695} & \cellcolor{gray!6}{213}\\
+resources & 30 & 13 & consortium & 24 & 9 & families & 13 & 5 & home & 1691 & 197\\
+\cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{way} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{social} & \cellcolor{gray!6}{1672} & \cellcolor{gray!6}{189}\\
+routes & 27 & 13 & service & 22 & 11 & student & 12 & 5 & significant & 1644 & 206\\
+\cellcolor{gray!6}{lanes} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{•} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{mobility} & \cellcolor{gray!6}{1634} & \cellcolor{gray!6}{136}\\
 \bottomrule
@@
 
-\begin{verbatim}
-## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
-## "none")` instead.
-\end{verbatim}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-1.pdf}
-
-\begin{verbatim}
-## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
-## "none")` instead.
-\end{verbatim}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-2.pdf}
-
-\begin{verbatim}
-## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
-## "none")` instead.
-\end{verbatim}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-3.pdf}
-
-\begin{verbatim}
-## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
-## "none")` instead.
-\end{verbatim}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-4.pdf}
-
-\begin{verbatim}
-## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
-## "none")` instead.
-\end{verbatim}
-
-\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-5.pdf}
-
 \begin{figure}
@@
 
-Using topic modelling, we analyzed how AST is framed in documents
-available to the general public on the websites of STP stakeholder
-groups in Ontario. We found that AST is primarily framed to parents as
-beneficial to the health and wellbeing of children and to environmental
-sustainability. This was confirmed by the most common bigrams identified
-in the policy corpus, as well as the topics identified by the LDA model.
-The policy documents adequately reflect the evidence that AST
-contributes positively to children's physical health (see Faulkner et
-al., 2009; Schoeppe et al., 2015), although the statements regarding the
-benefits of AST to children's school performance and cognitive
-development need to be studied further to produce stronger evidence
-({\textbf{???}}). STP stakeholder groups also communicate that
-increasing AST may reduce traffic near and around schools. This
-presumably is communicated to alleviate parental concerns about traffic
-and safety (Evers et al., 2014; Mammen et al., 2012; Rothman et al.,
-2015; Wilson et al., 2018) or reduce the frequency of risky behaviours
-from drivers around schools (Rothman et al., 2017). However, the
-documents do not explain why declining rates of AST are a problem for
-the particular community or convey any urgency to this issue so that it
-attracts the attention of parents, the general public, or policy makers.
-Communicating the potential outcomes of increased AST may be persuasive
-arguments to motivate behaviour change, but these documents do not
-appear to encourage parents or the general public to view their
-behaviour as problematic or unhealthy for their children's development.
-For example, Canadian parents who escort their children to school have
-reported concerns about traffic volume around schools (Mammen et al.,
-2012), but may not recognize that their own behaviour contributes to the
-problem that is perceived to prevent their child from safely walking or
-bicycling to school (Collins and Kearns, 2001).
+Using natural language processing techniques, we analyzed how AST is
+framed in documents available to the general public on the websites of
+STP stakeholder groups in Ontario. We found that AST is primarily framed
+to parents as beneficial to the health and wellbeing of children and to
+environmental sustainability. This was confirmed by the most common
+bigrams identified in the policy corpus, as well as the topics
+identified by the LDA model. The policy documents adequately reflect the
+evidence that AST contributes positively to children's physical health
+(see Faulkner et al., 2009; Schoeppe et al., 2015), although the
+statements regarding the benefits of AST to children's school
+performance and cognitive development need to be studied further to
+produce stronger evidence ({\textbf{???}}). STP stakeholder groups also
+communicate that increasing AST may reduce traffic near and around
+schools. This presumably is communicated to alleviate parental concerns
+about traffic and safety (Evers et al., 2014; Mammen et al., 2012;
+Rothman et al., 2015; Wilson et al., 2018) or reduce the frequency of
+risky behaviours from drivers around schools (Rothman et al., 2017).
+However, the documents do not explain why declining rates of AST are a
+problem for the particular community or convey any urgency to this issue
+so that it attracts the attention of parents, the general public, or
+policy makers. Communicating the potential outcomes of increased AST may
+be persuasive arguments to motivate behaviour change, but these
+documents do not appear to encourage parents or the general public to
+view their behaviour as problematic or unhealthy for their children's
+development. For example, parents who escort their children to school
+have reported concerns about traffic volume around schools (Mammen et
+al., 2012), but may not recognize that their own behaviour contributes
+to the problem that is perceived to prevent their child from safely
+walking or bicycling to school (Collins and Kearns, 2001).
 
@@
 measures or speed limits, rather ``non-modifiable'' factors like street
-density or land use mix. It would certainly be much more difficult for
-STP stakeholder groups to influence the number of trips to different
+density or land use mix. It would also certainly be much more difficult
+for STP stakeholder groups to influence the number of trips to different
 destinations that households need to make or to intervene in residential
@@
 
-There is also a noticeable lack of focus on individual and interpersonal
+There is a noticeable lack of focus on individual and interpersonal
 determinants of AST in the policy documents. For example, the role of
@@
 involve more local residents in their efforts (Buttazzoni et al., 2018),
-it would also be worthwhile for them to produce different material that
-communicates why this issue is important to the general public,
+it would also be worthwhile for them to produce different materials that
+communicate why this issue is important to the general public,
 regardless of whether they currently have children commuting to/from
-school. The ``political steam'' could also be further engaged by working
-with advocacy groups who could attract more support from a broader
-coalition of individuals.
+school. The ``political stream'' could also be further engaged by
+working with advocacy groups who could attract more support from a
+broader coalition of individuals.
 
@@
 
-We used text mining and topic modelling to examine how different school
-travel planning stakeholder (STP) groups in Ontario frame the issue of
-AST. STP stakeholder groups frame AST as a health and environmental
-issue that can be addressed through household behaviour change and
-engineering solutions. Policy documents reveal that STP stakeholder
-groups are focusing on ``modifiable factors'' such as parental
-perceptions or micro-scale elements in the built environment to increase
-rates of AST. However, AST may not be framed sufficiently as a
+We used natural language processing techniques to examine how different
+school travel planning stakeholder (STP) groups in Ontario frame the
+issue of AST. STP stakeholder groups frame AST as a health and
+environmental issue that can be addressed through household behaviour
+change and engineering solutions. Policy documents reveal that STP
+stakeholder groups are focusing on ``modifiable factors'' such as
+parental perceptions or micro-scale elements in the built environment to
+increase rates of AST. However, AST may not be framed sufficiently as a
 ``problem'' that requires urgent intervention, which may impact how
@@
 communities.
+
+\hypertarget{acknowledgments}{%
+\section{Acknowledgments}\label{acknowledgments}}
+
+This research was completed using open software, and the authors wish to
+acknowledge the developers of the following \texttt{R} packages:
+\texttt{dplyr} ({\textbf{???}}), \texttt{ggraph} ({\textbf{???}}),
+\texttt{ggplot2} ({\textbf{???}}), \texttt{igraph} ({\textbf{???}}),
+\texttt{pdftools} ({\textbf{???}}), \texttt{readr} ({\textbf{???}}),
+\texttt{reshape2} ({\textbf{???}}), \texttt{stringr} ({\textbf{???}}),
+\texttt{text2vec} ({\textbf{???}}), \texttt{textdata} ({\textbf{???}}),
+\texttt{tidyr} ({\textbf{???}}), \texttt{tidytext} ({\textbf{???}}),
+\texttt{tm} ({\textbf{???}}), \texttt{tools} ({\textbf{???}}),
+\texttt{topicmodels} ({\textbf{???}}), \texttt{widyr} ({\textbf{???}}),
+\texttt{word2vec} ({\textbf{???}}), \texttt{wordcloud} ({\textbf{???}}),
+\texttt{DiagrammeR} ({\textbf{???}}), and \texttt{kableextra}
+({\textbf{???}}).
 
@@
 \leavevmode\hypertarget{ref-romeroChildrenExperiencesEnjoyment2015}{}%
-Romero, V., 2015. Children׳s experiences: Enjoyment and fun as
+Romero, V., 2015. Children's experiences: Enjoyment and fun as
 additional encouragement for walking to school. Journal of Transport \&
@@
 Rothman, L., Buliung, R., To, T., Macarthur, C., Macpherson, A., Howard,
-A., 2015. Associations between parents׳ perception of traffic danger,
+A., 2015. Associations between parents' perception of traffic danger,
 the built environment and walking to school. Journal of Transport \&

### 2022-01-28 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Antonio's edits of latest version of paper

@@
 ---
-title: The framing of active school travel in Ontario, Canada as a health and built environment issue
+title: The framing of active school travel in Ontario, Canada, as a health and built environment issue
 author:
@@
 date: "`r Sys.Date()`"
-bibliography: bibliography.bib
+bibliography: [bibliography.bib, packages.bib]
 linenumbers: false
@@
 However, the appetite for AST may be high in many Canadian communities.
-For instance, 40% of children in a study conducted in Toronto, Ontario who are driven to school would like to travel by bicycle instead [@laroucheRatherBikeSchool2016].
+For instance, in a study conducted in Toronto, Ontario, 40% of children who are driven to school would like to travel by bicycle instead [@laroucheRatherBikeSchool2016].
 The study also reported that less than 3% of respondents actually cycled, despite the vast majority having access to a bicycle and living within a short and bikeable distance to school.
-Another study based in London, Ontario reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012].
-From a public health perspective, this represents a major opportunity to improve health and wellbeing if more children could use active modes to school.
-
-In response to this trend, the Government of Ontario, in Canada, created a fund in 2017 to support communities across the province in developing AST initiatives.
+Another study based in London, Ontario, reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012].
+From a public health perspective, increasing the use of active modes to school represents a major opportunity to improve children's health and wellbeing.
+
+The Government of Ontario, in Canada, has striven to promote this trend, and created a fund in 2017 to support communities across the province to develop AST initiatives.
 Green Communities Canada runs the program, called _Ontario Active School Travel_ [@GreenCommunities2016].
-As of December 2021, OAST has awarded over $2 million and provided resources to over 25 projects across Ontario.
+As of December 2021, OAST has awarded over CAD 2 million and provided resources to over 25 projects across Ontario.
 Many communities implemented school travel planning (STP), along with encouraging activities like walking school buses and developed resources for schools and parents, among other actions [see @GreenCommunitiesProjects].
@@
 In this paper, we use natural language processing to examine how three STP stakeholder groups in Ontario (municipalities, school boards, and transportation consortia) frame the issue of AST.
-We assembled a corpus of texts from webpages that present information for the general public or parents who are interested in AST.
+We assembled a corpus of texts from public sources that present information for the general public or parents who are interested in AST.
 We examine word frequency, bigrams, and concordances in these selected documents, and also identify key topics presented by each stakeholder group.
@@
 
-The benefits of AST are valuable information to communicate to the public in order to convey the importance of this issue.
-The desire to increase AST in Canada is certainly warranted - there is compelling evidence that children who actively commute to school earn physical and mental health benefits.
+There is value in communicating the benefits of AST to the public in order to convey the importance of this issue.
+The desire to increase AST in Canada is certainly warranted - there is compelling evidence of the physical and mental health benefits that children who actively commute to school attain.
 Faulkner et al.
@@
 The daily routine of travelling to school can be a good opportunity for children to regularly build physical activity into their schedule [@mitraIndependentMobilityMode2013].
-Research has also shown that using active modes to school contributes to improvements in cardiovascular fitness [@borrestadExperiencesRandomisedControlled2012].
-
-More recently, there has been literature exploring the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020], with relevant applications to the study of travel satisfaction [@vandenbergFactorsAffectingParental2020; @westmanChildrenTravelSchool2017].
-Being driven to school reduces community interactions for children which may negatively impact their social wellbeing [@waygoodChildrenTravelIncidental2015], whereas walking and bicycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021].
-This is something that children value highly about travel [@zwertsHowChildrenView2010] which indicates that social connections through travel are important for their wellbeing.
-AST also provides opportunities for children to engage with the natural environment [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015].
+Research has also shown that using active modes to school contributes to improve cardiovascular fitness [@borrestadExperiencesRandomisedControlled2012].
+
+More recently, the literature has explored the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020], with relevant applications to the study of travel satisfaction [@vandenbergFactorsAffectingParental2020; @westmanChildrenTravelSchool2017].
+Being driven to school reduces community interactions for children, which may negatively impact their social wellbeing [@waygoodChildrenTravelIncidental2015].
+In contrast, walking and cycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021].
+This is something that children seem to value [@zwertsHowChildrenView2010] and that tracks with findings among university students [@paezEnjoyment2010].
+More generally, social connections through travel appear to be important for wellbeing.
+Furthermore, AST can provide opportunities for children to engage with natural environments [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015].
 
@@
 Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behaviour is understood within the context of household, social, neighbourhood, and policy environments.
-The SEM comes from the field of public health and is a useful framework for understanding complex health behaviours, including travel habits such as walking or bicycling to school, because it identifies multiple determinants that need to be addressed by interventions to facilitate behaviour change.
+The SEM comes from the field of public health and is a useful framework for understanding complex health behaviours, such as walking and cycling habits, This model helps to identify multiple determinants that need to be addressed by interventions to facilitate behaviour change.
 The consensus in the literature is that interventions should target multiple levels in order to increase levels of healthy and physically active modes of travel to school [@mitraIndependentMobilityMode2013].
@@
 
-At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018].
-There is evidence that gender is a determinant of AST, with boys being more likely to travel using active modes than girls, although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
-Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], as well as the frequency of parental support [@mahDoesParentalSupport2017a], which indicates that shifting parental perceptions and habits is important.
+At the individual level, age is often positively associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018].
+There is evidence that gender is a determinant of AST, and that boys are more likely to travel using active modes than girls, although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
+Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], as well as the frequency of parental support [@mahDoesParentalSupport2017a].
+This indicates that shifting parental perceptions and habits is important.
 Convenience and inclement weather have been cited by parents as barriers to AST [@buliungSchoolTravelPlanning2011].
@@
 
-Distance between home and school is most strongly associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
+Distance between home and school is most strongly associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school - low density suburban development tends to increase the need for movement, and the reliance on motorized modes [@farberRunning2011].
 Many studies have also found that the quality of the built environment along the route to school and around the school site [@ikedaAssociationsChildrenActive2018; @rothmanActiveSchoolTransportation2021] and provision of active travel infrastructure [@chenPromotingActiveStudent2018; @pontEnvironmentalCorrelatesChildren2009] facilitate AST.
@@
 STP activities heavily focus on education or encouragement [@buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014; @buttazzoniSupportingActiveSchool2018], but parents may not always be receptive to the goals of STP and may be resistant to behaviour change [@buttazzoniSupportingActiveSchool2018].
-Parents have been found to express different understandings, language, and perceptions than planners of the built environment determinants that influence school travel [@buliungLivingJourneySchool2021].
+Parents have been found to express different understandings, language, and perceptions than planners of how the built environment can influence school travel [@buliungLivingJourneySchool2021].
 This is also true when it comes to other factors like convenience of different modes to school [@langUnderstandingModalChoice2011].
@@
 The “central organizing idea or story line" of AST, to apply the definition of framing from Gamson and Modigliani [-@gamsonChangingCulture1987], could also affect broader support in the community.
-Municipal representatives are perceived to be instrumental but the involvement of other stakeholder groups (e.g., busing consortium representatives and local residents) can be lacking [@buttazzoniSupportingActiveSchool2018].
-In Ontario, it would be reasonable to say that AST has become a policy issue on the education and public health agendas over this time as evidenced by the financial contribution from the provincial government.
-The support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
+Municipal representatives are perceived to be instrumental but the involvement of other stakeholder groups (e.g., busing consortia representatives and local residents) can be lacking [@buttazzoniSupportingActiveSchool2018].
+In Ontario, it is reasonable to say that AST has become a policy issue on the education and public health agendas, supported, albeit in a modest way, by financial contributions from the provincial government^[To put the CAD 2 million invested by the province in the Ontario Active School Travel program, a city such as Hamilton budgeted in excess of CAD 91 million on road maintenance and construction in 2016 alone; see: https://www.hamilton.ca/budget-finance/city-budgets/2016-tax-and-rate-budgets].
+Still, the support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
 However, it is unknown to what degree the general public (i.e., local residents) has been exposed to messaging about AST.
@@
   column_spec(3, border_left = T) %>%
-  kable_styling(latex_options = c("striped", "scale_down"))
+  kable_styling(latex_options = c("striped"))
 ```
@@
 
-__To be completed by Dr. Paez__
+We conducted a search on Web of Science for scholarly papers on the topic of travel to school.
+We limited our search to the fields of public health, transportation, planning, urban studies, and geography.
+This initial corpus was curated by the authors to ensure that all documents were relevant; for example, some hits in our search were not full papers but conference reports, or they dealt with travel to school only peripherally.
+After this step, we assembled a collection of 227 journal articles for analysis.
 
@@
 
-A multi-step process was conducted to ensure that the analysis captured as much text as possible from both the policy documents (n = 64) and academic papers (n = 233).
+A multi-step process was conducted to ensure that the analysis captured as much text as possible from both the policy documents (n = 64) and academic papers (n = 227).
 To begin, the webpages, which were manually downloaded in portable document format (PDF), were trimmed so that pages that only consisted of tables, figures, or references were removed.
 Many academic papers were in a two-column format, which is not ideal for conversion to `txt`.
-We adapted a procedure (https://stackoverflow.com/questions/42541849/extract-text-from-two-column-pdf-with-r) to read the two-column PDF documents so that they would be converted correctly.
+Two-column PDF documents were processed to extract the text in the correct sequence.
 Four academic papers did not join sufficiently and were taken out of the corpus due to the substantial time required to manually correct their inconsistencies.
 
-Next, we converted the trimmed PDF documents into `txt` files so that they could be imported in R for analysis.
-We then proceeded to a manual cleaning phase where we removed any remaining tables, figures, references, headers/footings, and captions that could not be trimmed.
+Next, we converted the trimmed PDF documents into `txt` files so that they could be imported for analysis in `R`.
+The next phase was to manually remove any remaining tables, figures, references, headers/footings, and captions that could not be trimmed.
 Manual corrections were also required for certain pages in academic papers that remained in two-column format after the conversion process.
-This typically occurred on pages that had a table or figure which disrupted the text.
+This typically occurred on pages that had a table or figure that disrupted the text.
 Finally, we reviewed all of the documents to remove hyphenation by line breaks and to keep hyphenated words together on the same line.
@@
 This included footnotes, references, acknowledgments, and conflict of interest statements in the academic papers.
-We removed all phone numbers, inserted links to other webpages, personal names, and content not to specific to AST from the policy documents that were retrieved from the websites of school boards, municipalities, and transportation consortia.
+We removed all phone numbers, inserted links to other webpages, personal names, and content not specific to AST from the policy documents that were retrieved from the websites of school boards, municipalities, and transportation consortia.
 
@@
 
-We use topic modelling in R to conduct the framing analysis.
-Topic modelling is a machine learning technique that can identify what language and concepts are being communicated by analyzing text.
+We use topic modelling in `R` to conduct the framing analysis.
+Topic modelling is a machine learning technique used to analyze text to identify the language and concepts being communicated.
 This method is practical for researchers working with large amounts of text because it replaces the manual coding of topics that would normally take place to analyze or summarize textual data [@jacobiQuantitativeAnalysisLarge2016].
@@
 These packages have functions for determining the frequency of specific words in each document or relationships (e.g., pairs of adjacent terms called bigrams) and correlations between words.
-These methods can reveal what language and concepts are being communicated to the general public.
 Topic modelling is a popular method for analyzing text from social media platforms [@albalawiUsingTopicModeling2020] and news articles [@jacobiQuantitativeAnalysisLarge2016].
@@
 Researchers must then interpret the identified topics, as done after other methods of manual coding.
-We also compare the topics between the policy documents and the academic papers, and use our interpretation to answer the questions outlined above that guide this paper.
-This methodology is not familiar to many, so we describe in more detail below how we used specific functions and code in R to produce our results.
+We also compare the topics between the policy documents and the academic papers, and use our interpretation to answer our research question.
+We describe in more detail the functions and code in `R`  that we used.
 
@@
 This paper is an example of open and reproducible research that uses only open software.
-All data were obtained from publicly available sources and organized in the form of a data package.
-Following best practices in spatial data science [@brunsdon2020opening], the code and data needed to reproduce or conduct a similar analysis for other regions in North America or elsewhere are available for download.
+All data are organized in the form of an open data product [@arribasOpen2021].
+Following best practices in spatial data science [@brunsdon2020opening], the code and data needed to reproduce our research or conduct a similar analysis for other regions are available for download.
 
@@
 
-We analyzed word and document frequency for each set of documents (i.e., corpus).
+We analyzed word and document frequency for each corpus of text.
 Table \ref{tab:word-table} shows the most frequent terms found in the municipal, transportation consortia, school board, and academic documents.
-As expected, policy documents and academic papers reference _active_, _travel_, _walking_, _biking_ or _cycling_, and _students_ more than other terms.
+Policy documents and academic papers reference _active_, _travel_, _walking_, _biking_ or _cycling_, and _students_ more than other terms.
 Each corpus also has _safety_ and _traffic_ as common words which suggests that such concerns are a common reason given for parents driving their children to school.
@@
 Table \ref{tab:word-table} indicates that the academic corpus discusses a broader range of determinants of AST than the policy documents.
-The number of references for each term in the academic papers is also significantly higher due to the inclusion of more documents.
+The number of references for each term in the academic papers is also substantially higher due to the inclusion of more documents.
 
@@
 
-However by examining document frequency, we found that some terms are not present in all policy documents.
-This suggests that although documents pertain to the subject of school travel, some stakeholders across Ontario are not disseminating information about AST.
+Examination of document frequency reveals terms that are not present in all policy documents.
+This suggests that although documents pertain to the subject of school travel, not all stakeholders across Ontario are disseminating information about AST.
 For example, a document may discuss active travel but not to school.
@@
 We manually searched the policy corpus and found that 48% of documents mention AST and 16% mention STP.
-This confirms that many municipalities, school boards, and transportation consortia are not promoting AST through their webpages or indicating their involvement in the STP process.
+This confirms that many municipalities, school boards, and transportation consortia do not promote AST through their webpages or indicate their involvement in the STP process.
 Instead, inclement weather and its impacts on busing is a common topic addressed in school board and transportation consortia documents.
@@
 Bigrams refer to a pair of consecutive words.
-We used the `unnest_tokens` function from the _tidytext_ package to determine the bigrams.
 Figures \ref{fig:city-visual}, \ref{fig:consortia-visual}, and \ref{fig:school-visual} show the bigrams that occur more than 5 times for each set of policy documents.
@@
 Key issues related to transport such as _traffic safety_ (n = 10), _air quality_ (n = 9), and _greenhouse gases_ (n = 9) are conveyed to the public through these policy documents.
-It is not surprising to find this focus given that municipalities in Ontario are concerned about climate change and have increasingly looked to active modes of travel to offset transport-related emissions in urban areas.
-
-Similar word bigrams are found in school board documents: _travel planning_ (n = 33), _safe routes_ (n = 15), _physical activity_ (n = 10), and _public health_ (n = 10) are among the most common bigrams.
+It is not surprising to find this focus given that municipalities in Ontario are concerned about climate change and have increasingly looked to active travel to offset transport-related emissions in urban areas.
+
+Similar bigrams are found in school board documents: _travel planning_ (n = 33), _safe routes_ (n = 15), _physical activity_ (n = 10), and _public health_ (n = 10) are among the most common.
 Both municipalities and school boards in Ontario seem to emphasize what can be or has been done to improve AST (i.e., policy or planning changes), while outlining some of the benefits of AST at the individual- or community-level to potentially encourage behaviour change (i.e., physical activity for children or improved air quality).
 Unlike other STP stakeholders, school boards also consider _inclement weather_ (n = 24) and _bus cancellations_ (n = 13).
-This is likely because many students in Ontario travel to school by bus and this information is presented alongside AST options.
+Most likely this is because school boards are mandated to provide transportation to school in Ontario (typically by bus) and this information is presented alongside AST options.
 Finally, transportation consortia documents highlight topics such as _physical activity_ (n = 10), _pedestrian safety_ (n = 8), _crossing guards_ (n = 6), _travel planning_ (n = 6), and _walk zones_ (n = 6).
@@
 
-We then combined all municipality, school board, and transportation consortia documents into one "policy" corpus.
+We then combined all municipality, school board, and transportation consortia documents into one "policy+practice" corpus.
 This enabled us to examine and visualize the most common bigrams found across all of the material in Ontario that was collected for this study.
-Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the policy corpus.
+Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the policy+practice corpus.
 In addition to the bigrams already identified above, we also found _mental health_, _walk day_, and _green communities_ as common pairs of consecutive words.
-_Green Communities Canada_ is a non-profit organization that has significantly supported AST initiatives through the Ontario Active School Travel program so the high frequency of this term in the policy corpus is not surprising.
+_Green Communities Canada_ is a non-profit organization that has significantly supported AST initiatives through the Ontario Active School Travel program so the high frequency of this term in the policy+practice corpus is not surprising.
 Overall, the policy documents from STP stakeholder groups seem to focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or considerations; and iv) supports for AST.
@@
 
-Next, we analyzed bigrams in the academic corpus separately to make comparisons with the policy corpus.
+Next, we analyzed bigrams in the academic corpus separately to make comparisons with the policy+practice corpus.
 Figure \ref{fig:academic-visual} indicates that academic papers include several common bigrams that were also found in the policy documents including _physical activity_ (n = 1566), which is the top bigram, _traffic safety_ (n = 308), and _safe routes_ (n = 268).
@@
 Many papers also investigate gender differences in AST given that _boys girls_ (n = 211) is another common bigram.
-Finally, the presence of _statistically significant_ among the top bigrams underscores that some researchers aim to identify determinants using statistical measures.
+Finally, the presence of _statistically significant_ among the top bigrams underscores that researchers often aim to identify associations using statistical measures.
 We found that the academic corpus focuses on a greater range of topics than found in the policy documents.
@@
 
-We interpreted the most common bigrams from the policy corpus (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholder groups are focusing on and communicating to the public about AST.
-We then used the `kwic` function from the _quanteda_ package to better understand the context of these key ideas.
-Table \ref{tab:policy-concordance} presents some examples of the context that were extracted from select policy documents to demonstrate how the most common bigrams are communicated to the public.
+We interpreted the most common bigrams from the policy+practice corpus (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholder groups focus on and communicate to the public about AST.
+We then examined the context of these key ideas by extracting words-in-context from the corpora.
+Table \ref{tab:policy-concordance} presents some examples from select policy documents that illustrate how the most common bigrams are communicated to the public.
 
@@
 
-Finally, we conducted topic modelling to examine the different topics found in the policy and academic corpora.
-We focused on the policy corpus, instead of assessing the municipal, school, and consortia documents separately, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario.
-To determine the number of discrete topics in each corpus, we used the _ldatuning_ package.
-We then used the `LDA` (latent Dirichlet allocation) function from the _topicmodels_ package to estimate an LDA model for each group of documents.
-The parameters from the _ldatuning_ package suggest that the policy corpus has between 7 and 9 topics and the academic corpus has between 17 and 25 topics.
-After running the LDA model for the academic corpus, it was too difficult to interpret a minimum of 17 topics based on the clusters of words that were identified.
-We experimented with the model by adjusting and evaluating the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap.
+For the final part of our analysis, we conducted topic modelling to examine the different topics found in the policy and academic corpora.
+We focused on the policy+practice corpus, instead of assessing the municipal, school, and consortia documents separately, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario.
+We then estimated Latent Dirillecth Allocation (LDA) models for each corpus.
+Parameter tuning suggests that the policy+practice corpus has between 7 and 9 topics and the academic corpus has between 17 and 25 topics.
+After running the LDA model for the academic corpus, we realized the difficulty of interpreting a minimum of 17 topics based on the clusters of words that were identified.
+We experimented with the model by adjusting and evaluating the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap for the clusters to be meaningfully interpreted.
 Figures \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main terms that are associated with the topics found in each corpus.
 
-In the policy corpus, we identified the following topics based on the cluster of words: (1) resources for walking; (2) walking; (3) supporting active travel; (4) bicycling and the environment; (5) benefits of active travel; (6) safety; and (7) busing information and eligibility.
+In the policy+practice corpus, we identified the following topics based on the cluster of words: (1) resources for walking; (2) walking; (3) support for active travel; (4) bicycling and the environment; (5) benefits of active travel; (6) safety; and (7) busing information and eligibility.
 These topics indicate that STP stakeholder groups are sending the message that walking and bicycling to school are healthy travel modes for students, particularly in terms of physical activity.
@@
 The following topics were identified based on the clusters of words: (1) built environment (2) walking distance; (3) AST interventions; (4) parental barriers to walking; (5) behaviours and attitudes; (6) bicycling; (7) social environment; (8) children's independent mobility; (9) modeling trip choice; (10) adolescents and physical activity; and (11) safe routes to school programs.
-This corpus reflects a broader range of topics than the policy corpus.
+This corpus reflects a broader range of topics than the policy+practice corpus.
 
@@
 
-Based on the identified  bigrams and topics, we determined that the policy corpus primarily frames AST as a health and environmental issue.
+Based on the identified  bigrams and topics, we determined that the policy+practice corpus primarily frames AST as a health and environmental issue.
 STP stakeholder groups appear to position walking, bicycling, or rolling to school as beneficial to individual health, via physical activity and improved mental health, and to the broader community through a reduction in traffic and vehicle emissions.
-Here, we present some examples from the policy documents to illustrate how the health and environmental frame is communicated:
+Here, we present some examples from the policy documents that illustrate how the health and environmental frame is communicated:
 
@@
 Using natural language processing techniques, we analyzed how AST is framed in 69 documents available to the public on the websites of STP stakeholder groups in Ontario.
-Two main frames in the policy corpus were identified based on the most common bigrams and topics from the LDA model.
+Two main frames in the policy+practice corpus were identified based on the most common bigrams and topics from the LDA model.
 

### 2022-01-28 AST-Framing-Ontario/AST-Framing-Ontario.tex
Antonio's edits of latest version of paper

@@
 \usepackage{lineno} % add
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
@@
             pdfauthor={},
-            pdftitle={The framing of active school travel in Ontario, Canada as a health and built environment issue},
+            pdftitle={The framing of active school travel in Ontario, Canada, as a health and built environment issue},
             colorlinks=false,
@@
 
+% tightlist command for lists without linebreak
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
 % Pandoc citation processing
-
-% Pandoc header
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+% for Pandoc 2.8 to 2.10.1
+\newenvironment{cslreferences}%
+  {}%
+  {\par}
+% For Pandoc 2.11+
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
 \usepackage{booktabs}
@@
 \begin{document}
+
 \begin{frontmatter}
 
-  \title{The framing of active school travel in Ontario, Canada as a health and
-built environment issue}
+  \title{The framing of active school travel in Ontario, Canada, as a
+health and built environment issue}
     \author[Some Department]{Author 1\corref{1}}
@@
 school travel (AST), have been declining in Canada and the United States
-for decades (Rothman et al., 2018), with levels much lower than other
-developed countries like The Netherlands (van Goeverden and de Boer,
-2013), Denmark (Jensen, 2008), and Japan (Waygood and Taniguchi, 2020).
-However, the appetite for AST may be high in many Canadian communities.
-For instance, 40\% of children in a study conducted in Toronto, Ontario
-who are driven to school would like to travel by bicycle instead
-(Larouche et al., 2016). But the study reported that less than 3\%
-actually do, despite the vast majority having access to a bicycle and
-living within a short and bikeable distance to school. Another study
-based in London, Ontario reported similar findings with respect to
-children's preference for active travel (Larsen et al., 2012). From a
-public health perspective, this represents a huge opportunity to improve
-health and wellbeing if more children could use active modes to school.
-
-In response to this trend, the Government of Ontario, in Canada, created
-a fund in 2017 to support communities across the province in developing
-AST initiatives. Green Communities Canada runs the program, called
-\emph{Ontario Active School Travel}, and determines the projects that
-will be funded with their support (Canada, 2020a). As of December 2021,
-OAST has awarded over 2 million Canadian dollars and provided resources
-to over 25 projects across Ontario. Many communities implemented school
-travel planning (STP), along with encouragement activities like walking
-school buses or developed resources for schools and parents, among other
-actions (see Canada, 2020b). In this context, STP is a popular
-``school-specific'' intervention led by a facilitator that brings
-together a committee of stakeholders from diverse sectors including
-education, planning, transportation, and public health to develop action
-plans (Buliung et al., 2011; Mammen, M. R. Stone, Ron Buliung, et al.,
-2014). The five-step process involves identifying barriers to AST based
-on the local context and implementing approaches or activities following
-the 5 E's that alleviate concerns about AST and make AST safer and more
-convenient (Buliung et al., 2011; Lang et al., 2011).
+for decades (Rothman et al., 2018). However, the appetite for AST may be
+high in many Canadian communities. For instance, in a study conducted in
+Toronto, Ontario, 40\% of children who are driven to school would like
+to travel by bicycle instead (Larouche et al., 2016). The study also
+reported that less than 3\% of respondents actually cycled, despite the
+vast majority having access to a bicycle and living within a short and
+bikeable distance to school. Another study based in London, Ontario,
+reported similar findings with respect to children's preference for
+active travel (Larsen et al., 2012). From a public health perspective,
+increasing the use of active modes to school represents a major
+opportunity to improve children's health and wellbeing.
+
+The Government of Ontario, in Canada, has striven to promote this trend,
+and created a fund in 2017 to support communities across the province to
+develop AST initiatives. Green Communities Canada runs the program,
+called \emph{Ontario Active School Travel} (Canada, 2020a). As of
+December 2021, OAST has awarded over CAD 2 million and provided
+resources to over 25 projects across Ontario. Many communities
+implemented school travel planning (STP), along with encouraging
+activities like walking school buses and developed resources for schools
+and parents, among other actions (see Canada, 2020b). In this context,
+STP is a popular ``school-specific'' intervention led by a facilitator
+who brings together a committee of stakeholders from diverse sectors
+including education, planning, transportation, and public health to
+develop action plans (Buliung et al., 2011; Mammen et al., 2014a). The
+five-step process involves identifying barriers to AST based on the
+local context and implementing approaches or activities following the
+4E's that make AST safer and more convenient: 1) setup of the program;
+2) data collection and problem identification; 3) action planning; 4)
+implementation; 5) monitoring and evaluation (Buliung et al., 2011; Lang
+et al., 2011).
 
 How AST is framed by STP stakeholders to a target audience, like parents
-or the general public, may raise awareness about the issue and influence
+or the general public, may raise awareness of the issue and influence
 how walking and bicycling to school are perceived. Gamson and Modigliani
@@
 pertaining to various dimensions of an issue (Goffman, 1974). Therefore,
-stakeholder groups involved in STP efforts can play a role in shaping
-public perception about AST in such a way that it attracts greater
-attention and becomes a ``problem'' that needs to be addressed through
-behaviour change or by new policies. We also contend that the ways in
-which the AST issue is framed can affect the policy process, as outlined
-in Kingdon's (1984) Multiple Streams Framework (MSF), through all three
-streams (i.e., problem, policy, and politics). This framing can
-ultimately impact financial contributions and potential solutions to
-address the decline of AST in Canada.
+stakeholders involved in STP efforts can play a role in shaping public
+perception about AST in such a way that it attracts greater attention
+and is recognized as a ``problem'' that needs to be addressed through
+behaviour change or new policies.
 
 After significant investment of human and financial resources to boost
-rates of AST in Ontario over the past few years, we ask the following
-questions: How is AST framed? What benefits of AST are communicated to
-the public? What solutions are proposed to increase rates of AST? Do
-proposed solutions focus primarily on the intrapersonal and
-interpersonal factors, meaning that behaviour change must ultimately
-result from the individual or household making different travel
-decisions? Or is AST framed as an issue that must be addressed through
-changes in the built environment or at the policy level?
+rates of AST in Ontario over the past few years, we ask this central
+question: How is AST framed to the public? The following questions are
+subsidiary and help us address this main question: What benefits of AST
+are communicated to the public? What solutions are proposed to increase
+rates of AST?
 
 In this paper, we use natural language processing to examine how three
-STP stakeholder groups in Ontario (i.e., municipalities, school boards,
-and transportation consortia) frame the issue of AST. We assembled a
-corpus of texts from webpages that can be considered an important source
-of information for the general public or parents who are interested in
-AST. We examine word frequency, bigrams, and concordances in these
-selected documents, and also identify key topics presented by each
-stakeholder group. We then compare the findings from these documents to
-a selection of studies on AST and explore the extent to which there is
-concordance between the literature on AST and materials shared with the
-public.
+STP stakeholder groups in Ontario (municipalities, school boards, and
+transportation consortia) frame the issue of AST. We assembled a corpus
+of texts from public sources that present information for the general
+public or parents who are interested in AST. We examine word frequency,
+bigrams, and concordances in these selected documents, and also identify
+key topics presented by each stakeholder group. We then compare the
+findings from these documents to a selection of studies on AST and
+explore the extent to which there is concordance between the literature
+on AST and materials shared with the public.
 
@@
 
-The benefits of AST are valuable information to communicate to the
-public in order to convey the importance of this issue. The desire to
-increase AST in Canada is certainly warranted - there is compelling
-evidence that children who actively commute to school earn physical and
-mental health benefits. Faulkner et al.~(2009) concluded from their
-systematic review that children who travel on foot or by bicycle to
-school generally have higher levels of physical activity than their
-peers who are driven to school. However, Schoeppe et al.~(2015) reported
-no association between AST and physical activity. This relationship
-could be dose-dependent, meaning that children would have to travel
-longer distances to accumulate physical activity. A walking distance of
-1000-1600 metres to school has been found to contribute to overall
-levels of physical activity for boys (Faulkner et al., 2013). The daily
-routine of travelling to school can be a good opportunity for children
-to regularly build physical activity into their schedule (Mitra, 2013).
-Research has also shown that using active modes to school contributes to
-improvements in cardiovascular fitness (Børrestad et al., 2012).
-
-More recently, there has been literature exploring the link between
-transport and children's wellbeing (Waygood et al., 2020), with relevant
+There is value in communicating the benefits of AST to the public in
+order to convey the importance of this issue. The desire to increase AST
+in Canada is certainly warranted - there is compelling evidence of the
+physical and mental health benefits that children who actively commute
+to school attain. Faulkner et al. (2009) concluded from their systematic
+review that children who travel on foot or by bicycle to school
+generally have higher levels of physical activity than their peers who
+are driven to school. However, Schoeppe et al. (2015) reported no
+association between AST and physical activity in their cross-sectional
+study. This relationship could be dose-dependent, meaning that children
+would have to travel longer distances to accumulate physical activity. A
+walking distance of 1000-1600 metres to school has been found to
+contribute to overall levels of physical activity for boys (Faulkner et
+al., 2013). The daily routine of travelling to school can be a good
+opportunity for children to regularly build physical activity into their
+schedule (Mitra, 2013). Research has also shown that using active modes
+to school contributes to improve cardiovascular fitness (Børrestad et
+al., 2012).
+
+More recently, the literature has explored the link between transport
+and children's wellbeing (Waygood et al., 2020), with relevant
 applications to the study of travel satisfaction (van den Berg et al.,
-2020; Westman, Olsson, et al., 2017). Being driven to school reduces
-community interactions for children which may impact their social
-wellbeing (Waygood and Friman, 2015), whereas walking and bicycling give
-children opportunities to socialize with friends or siblings (Michail et
-al., 2021). This is something that children highly value about travel
-(Zwerts et al., 2010) and indicates that social connections through
-travel are important for their wellbeing. AST also provides
-opportunities for children to engage with the natural environment (Fusco
-et al., 2012; Romero, 2015) which can improve their mental or emotional
-wellbeing.
+2020; Westman et al., 2017b). Being driven to school reduces community
+interactions for children, which may negatively impact their social
+wellbeing (Waygood and Friman, 2015). In contrast, walking and cycling
+give children opportunities to socialize with friends or siblings
+(Michail et al., 2021). This is something that children seem to value
+(Zwerts et al., 2010) and that tracks with findings among university
+students (Paez and Whalen, 2010). More generally, social connections
+through travel appear to be important for wellbeing. Furthermore, AST
+can provide opportunities for children to engage with natural
+environments (Fusco et al., 2012; Romero, 2015).
 
@@
 al., 2016) whereby children's travel behaviour is understood within the
-context of their household, social, neighbourhood, and policy
-environments. Individual characteristics of the child are also
-determinants. The SEM comes from the field of public health and is a
-useful framework for understanding complex health behaviours, including
-travel habits such as walking or bicycling to school, because it
-identifies multiple determinants that need to be addressed by
-interventions to facilitate behaviour change. The consensus in the
-literature is that various factors are interrelated and that
-interventions should target multiple levels in order to increase levels
-of healthy and physically active modes of travel to school (Mitra,
-2013). Rather than describing an extensive list of factors that
-influence AST and mode choice in Canada (e.g., Mammen et al., 2012;
-Mitra, 2013; Rothman et al., 2018; Wilson et al., 2018), we discuss a
-few potentially modifiable determinants that may be targeted for change
-through STP.
-
-At the individual level, older child age is often associated with AST
-(Mammen et al., 2012; Stark et al., 2018; Wilson et al., 2018) as
-parents typically escort younger children. There is evidence that gender
-is a determinant of AST, with boys being more likely to travel using
-active modes than girls, although this is not a strong or consistent
-finding (Rothman et al., 2018; Schoeppe et al., 2015). Children's mode
-choice to school is strongly influenced by their parents' travel
-behaviours and the complexity of their household's travel needs (Buliung
-et al., 2021), which indicates that shifting parental perceptions and
-habits is important. Convenience and inclement weather have been cited
-by parents as barriers to AST (Buliung et al., 2011). Parental
-perceptions of the built or school environment (De Meester et al., 2014;
-Panter et al., 2010) and their children's skills (Mammen et al., 2012)
-also influence whether they allow their children to walk or bicycle to
+context of household, social, neighbourhood, and policy environments.
+The SEM comes from the field of public health and is a useful framework
+for understanding complex health behaviours, such as walking and cycling
+habits, This model helps to identify multiple determinants that need to
+be addressed by interventions to facilitate behaviour change. The
+consensus in the literature is that interventions should target multiple
+levels in order to increase levels of healthy and physically active
+modes of travel to school (Mitra, 2013). Rather than describing an
+extensive list of factors that influence AST and mode choice in Canada
+(e.g., Mammen et al., 2012; Mitra, 2013; Rothman et al., 2018; Wilson et
+al., 2018), we discuss a few potentially modifiable determinants that
+may be targeted for change through STP.
+
+At the individual level, age is often positively associated with AST
+(Mammen et al., 2012; Stark et al., 2018; Wilson et al., 2018). There is
+evidence that gender is a determinant of AST, and that boys are more
+likely to travel using active modes than girls, although this is not a
+strong or consistent finding (Rothman et al., 2018; Schoeppe et al.,
+2015). Children's mode choice to school is strongly influenced by their
+parents' travel behaviours and the complexity of their household's
+travel needs (Buliung et al., 2021), as well as the frequency of
+parental support (\textbf{mahDoesParentalSupport2017a?}). This indicates
+that shifting parental perceptions and habits is important. Convenience
+and inclement weather have been cited by parents as barriers to AST
+(Buliung et al., 2011). Parental perceptions of the built or school
+environment (De Meester et al., 2014; Panter et al., 2010) and their
+children's skills (Mammen et al., 2012;
+\textbf{faulknerWhatQuickestEasiest2010?}) also influence mode choice to
 school.
@@
 al., 2018) with less AST reported among children who have to travel
-farther to school. Many studies have also found that the quality of the
-built environment along the route to school and around the school site
-(Ikeda et al., 2018; Rothman et al., 2021) and provision of active
-travel infrastructure (Chen et al., 2018; Pont et al., 2009) facilitate
-AST. Canadian youth report that they feel most safe bicycling on streets
-in their neighbourhood or that have low volumes of traffic
-({\textbf{???}}). Finally, concerns about traffic and strangers have
-been reported by parents who drive their children to school (Mammen et
-al., 2012), which highlights that the volume and speed of cars can be a
-concern or deterrent for AST.
+farther to school - low density suburban development tends to increase
+the need for movement, and the reliance on motorized modes (Farber and
+Páez, 2011). Many studies have also found that the quality of the built
+environment along the route to school and around the school site (Ikeda
+et al., 2018; Rothman et al., 2021) and provision of active travel
+infrastructure (Chen et al., 2018; Pont et al., 2009) facilitate AST.
+Canadian youth report that they feel most safe bicycling on streets in
+their neighbourhood or that have low volumes of traffic
+(\textbf{TACbikeinfra2020?}). Finally, concerns about traffic and
+strangers have been reported by parents who drive their children to
+school (Mammen et al., 2012), which highlights that the volume and speed
+of cars can be a concern or deterrent for AST.
 
@@
 establish multi-sector committees who intervene at the participating
-school through a range of activities related to the 5E's such as
+school through a range of activities related to the 4E's consisting of
 \emph{education} strategies, \emph{encouragement} through in-person
@@
 school site, and \emph{enforcement} of traffic speeds around schools
-(Lang et al., 2011; Mammen, M. R. Stone, G. Faulkner, et al., 2014). The
-first large-scale evaluation of STP as an intervention in Canada took
-place at twelve schools across the country, including four in Ontario,
-using parental surveys to measure changes in travel behaviour and
-perceptions (Buliung et al., 2011). Since then, there have been other
-assessments of both the efficacy of STP (Buttazzoni et al., 2019;
-Mammen, M. R. Stone, G. Faulkner, et al., 2014) and the process of
-implementing such programs in Ontario (Buttazzoni et al., 2018; Mammen
-et al., 2015). STP facilitators have recommended that additional time
-and resources are needed to improve the efficacy of STP (Mammen et al.,
-2015), which highlights that long-term and sustained efforts driven at
-the policy level are required to address declining rates of AST.
-
-The ways in which AST is framed seem particularly important to shift
-parental attitudes and perceptions given their reported influence on
-children's travel mode to school. STP activities heavily focus on
-education or encouragement (Buliung et al., 2011; Buttazzoni et al.,
-2018; Mammen, M. R. Stone, G. Faulkner, et al., 2014), but parents may
-not always be receptive to the goals of STP and may be resistant to
-behaviour change (see Buttazzoni et al., 2018). Parents have been found
-to express different understandings, language, and perceptions than
-planners of the built environment determinants that influence school
-travel (Buliung et al., 2021). This is also true when it comes to other
-factors like convenience of different modes to school (Lang et al.,
-2011). STP stakeholder groups must pay special attention to parents'
+(Lang et al., 2011; Mammen et al., 2014b). The first large-scale
+evaluation of STP as an intervention in Canada took place at twelve
+schools across the country, including four in Ontario, using parental
+surveys to measure changes in travel behaviour and perceptions (Buliung
+et al., 2011). Assessments of the efficacy of STP (Buttazzoni et al.,
+2019; Mammen et al., 2014b) indicate that it has the potential to
+encourage behaviour change and adoption of AST. STP facilitators have
+recommended that additional time and resources are needed to improve the
+efficacy of STP (Mammen et al., 2015), which highlights that long-term
+and sustained efforts driven at the policy level are required to address
+declining rates of AST.
+
+How AST is framed seems particularly important to shift parental
+attitudes and perceptions given their reported influence on children's
+travel mode to school. STP activities heavily focus on education or
+encouragement (Buliung et al., 2011; Buttazzoni et al., 2018; Mammen et
+al., 2014b), but parents may not always be receptive to the goals of STP
+and may be resistant to behaviour change (Buttazzoni et al., 2018).
+Parents have been found to express different understandings, language,
+and perceptions than planners of how the built environment can influence
+school travel (Buliung et al., 2021). This is also true when it comes to
+other factors like convenience of different modes to school (Lang et
+al., 2011). STP stakeholders must pay special attention to parents'
 understanding of the decline of AST as a problem, which may affect their
@@
 The ``central organizing idea or story line'' of AST, to apply the
-definition from Gamson and Modigliani (1987), could also affect broader
-support in the community. Municipal representatives are perceived to be
-instrumental but the involvement of other stakeholder groups (e.g.,
-busing consortium representatives and local residents) can be lacking
-(Buttazzoni et al., 2018). In Ontario, it would be reasonable to say
-that AST has become a policy issue on the education and public health
-agendas over this time as evidenced by the financial contribution from
-the provincial government. The support from a range of municipal
-representatives (see Buttazzoni et al., 2018; Mammen et al., 2015)
-demonstrates that the ``policy stream'' (see Kingdon, 1984) has been
-well engaged. However, it is unknown to what degree the general public
-(i.e., local residents) has been exposed to messaging about AST, or how
-they view the AST issue, which could affect their participation in the
-STP process as desired by STP facilitators (Buttazzoni et al., 2018).
+definition of framing from Gamson and Modigliani (1987), could also
+affect broader support in the community. Municipal representatives are
+perceived to be instrumental but the involvement of other stakeholder
+groups (e.g., busing consortia representatives and local residents) can
+be lacking (Buttazzoni et al., 2018). In Ontario, it is reasonable to
+say that AST has become a policy issue on the education and public
+health agendas, supported, albeit in a modest way, by financial
+contributions from the provincial government\footnote{To put the CAD 2
+  million invested by the province in the Ontario Active School Travel
+  program, a city such as Hamilton budgeted in excess of CAD 91 million
+  on road maintenance and construction in 2016 alone; see:
+  https://www.hamilton.ca/budget-finance/city-budgets/2016-tax-and-rate-budgets}.
+Still, the support from a range of municipal representatives (see
+Buttazzoni et al., 2018; Mammen et al., 2015) demonstrates that the AST
+issue is on the political agenda. However, it is unknown to what degree
+the general public (i.e., local residents) has been exposed to messaging
+about AST.
 
@@
 viewing neighbourhoods with mixed uses as key for encouraging more
-active travel (Buliung et al., 2021). Therefore, stakeholder groups
-involved in STP must make important choices about the proposed solutions
-and potential benefits of AST that ought to be communicated to parents
-and the general public to convey its importance as a policy issue and to
-facilitate adoption of AST. Publicly available content about AST,
-therefore, needs to effectively engage multiple audiences on this policy
-issue including parents, children, politicians, and school
-representatives. This information should reflect current knowledge from
-research on school travel, plus content specific to local factors that
-influence AST, so that the challenges of AST are adequately defined and
-the opportunities or solutions to address the problems are clear.
-However, it is unknown to what degree STP materials presented to the
-general public reflect the scope of evidence from the literature on AST.
+active travel (Buliung et al., 2021). Therefore, stakeholders involved
+in STP must make conscious choices about the proposed solutions and
+potential benefits of AST that are communicated to parents and the
+general public to convey its importance as a policy issue and to
+facilitate adoption of AST. Publicly available content about AST needs
+to effectively engage multiple audiences on this policy issue, including
+parents, children, politicians, and school representatives. This
+information should reflect current knowledge from research on school
+travel, plus content specific to local factors that influence AST, so
+that the challenges of AST are adequately defined and the opportunities
+or solutions to address the problems are clear.
 
@@
 sanctioned by Ontario's Ministry of Education in Ontario 2006. Each
-consortium involves a collaboration between regions and school boards;
-the consortium's objective is to deliver more efficient and timely
-transportation services to schools in each region. Non-profit
+consortium involves a collaboration between municipal regions and school
+boards; the consortium's objective is to deliver more efficient and
+timely transportation services to schools in each region. Non-profit
 organizations, police services, and advocacy groups are other
@@
 Thus, we included only webpages that were readily accessible, which we
-defined as requiring no more than 2-4 separate links from the initial
+defined as requiring no more than 4 separate links from the initial
 Google search.
@@
 \centering
-\resizebox{\linewidth}{!}{
 \begin{tabular}[t]{>{}l|l|>{}l}
 \toprule
-Stakeholder & Total & Included\\
+Stakeholder & Total & Retrieved\\
 \midrule
@@
 \bottomrule
-\end{tabular}}
+\end{tabular}
 \end{table}
@@
 
-\textbf{To be completed by Dr.~Paez}
+We conducted a search on Web of Science for scholarly papers on the
+topic of travel to school. We limited our search to the fields of public
+health, transportation, planning, urban studies, and geography. This
+initial corpus was curated by the authors to ensure that all documents
+were relevant; for example, some hits in our search were not full papers
+but conference reports, or they dealt with travel to school only
+peripherally. After this step, we assembled a collection of 227 journal
+articles for analysis.
 
@@
 as much text as possible from both the policy documents (n = 64) and
-academic papers (n = 233). To begin, the webpages, which were manually
+academic papers (n = 227). To begin, the webpages, which were manually
 downloaded in portable document format (PDF), were trimmed so that pages
@@
 academic papers were in a two-column format, which is not ideal for
-conversion to \texttt{txt}. We adapted a procedure
-(https://stackoverflow.com/questions/42541849/extract-text-from-two-column-pdf-with-r)
-to read the two-column PDF documents so that they would be converted
-correctly. Four academic papers did not join sufficiently and were taken
-out of the corpus due to the substantial time required to manually
-correct their inconsistencies.
+conversion to \texttt{txt}. Two-column PDF documents were processed to
+extract the text in the correct sequence. Four academic papers did not
+join sufficiently and were taken out of the corpus due to the
+substantial time required to manually correct their inconsistencies.
 
 Next, we converted the trimmed PDF documents into \texttt{txt} files so
-that they could be imported in R for analysis. We then proceeded to a
-manual cleaning phase where we removed any remaining tables, figures,
-references, headers/footings, and captions that could not be trimmed.
-Manual corrections were also required for certain pages in academic
-papers that remained in two-column format after the conversion process.
-This typically occurred on pages that had a table or figure which
-disrupted the text. Finally, we reviewed all of the documents to remove
+that they could be imported for analysis in \texttt{R}. The next phase
+was to manually remove any remaining tables, figures, references,
+headers/footings, and captions that could not be trimmed. Manual
+corrections were also required for certain pages in academic papers that
+remained in two-column format after the conversion process. This
+typically occurred on pages that had a table or figure that disrupted
+the text. Finally, we reviewed all of the documents to remove
 hyphenation by line breaks and to keep hyphenated words together on the
@@
 that were not properly detected during the conversion process) were
-fixed by replacing the unicode sequence of character by inserting the
-missing sequence of characters.
+fixed.
 
@@
 academic papers. We removed all phone numbers, inserted links to other
-webpages, personal names, and content not to specific to AST from the
+webpages, personal names, and content not specific to AST from the
 policy documents that were retrieved from the websites of school boards,
@@
 such as \emph{and} or \emph{the} as identified in a predetermined list
-by Lewis et al.~({\textbf{???}}) and other frequent terms in the
-documents like ``school'' and specific location names, were removed from
-the corpora.
+by Lewis et al. (Feinerer and Hornik, 2020) and other frequent terms in
+the documents like ``school'' and specific location names, were removed
+from the corpora.
 
@@
 political communications have proposed that communicators, such as the
-media or an institution, construct the narrative of a frame for policy
+media or institutions, construct the narrative of a frame for policy
 positions or public issues in order to activate or restrict a particular
@@
 important to understand because it plays a role in either altering or
-preserving the existing social perceptions. This, in turn, can affect
-whether issues are put on the agenda of policy makers and can determine
-which solutions are proposed to address the problem (Kingdon, 1984).
+preserving the existing social perceptions. Finally, the ideas that are
+communicated by a particular frame can be either positive or negative
+(\textbf{waygoodCO2ValenceFraming2018?}). There is evidence that
+negative framing may be more effective at motivating individuals to
+change transport modes to reduce CO2 emissions
+(\textbf{waygoodCO2ValenceFraming2018?}).
 
@@
 policy agendas as public attention puts pressure on the policy stream to
-adopt frameworks for action. For example, transport planners also use
+adopt frameworks for action. For example, transport planners use
 different frames to guide the extent to which transport policies can be
@@
 four western Canadian cities under the current circumstances of climate
-change. The authors found four primary frames: ``The Growing City'',
-``If You Build It, They Will Come'', ``Better City for All'', and a
+change. The authors found four primary frames: ``The Growing City,''
+``If You Build It, They Will Come,'' ``Better City for All,'' and a
 ``the Resilient City'' (Reynard et al., 2021). Each frame presented the
@@
 In a similar way, we hypothesize that STP stakeholder groups in Ontario
-have framed AST in particular ways to effectively engage multiple
-audiences on this policy issue including parents, local residents,
-school representatives, and municipal representatives. These groups are
-likely identifying points of intervention and potential opportunities to
-build support for and encourage AST.
-
-\hypertarget{topic-modelling}{%
-\subsection{4.2. Topic modelling}\label{topic-modelling}}
-
-We use topic modelling in R to conduct the framing analysis. Topic
-modelling is a machine learning technique that can identify what
-language and concepts are being communicated by analyzing text. This
-method is more practical for researchers working with large amounts of
-text because it replaces the manual coding of topics that would normally
-take place to analyze or summarize textual data (Jacobi et al., 2016).
-In the data pre-processing phase, we tokenize the text in the documents
-and create a document-term matrix so that it is in the correct format
-for analysis. We primarily use the following packages: \texttt{tidytext}
-({\textbf{???}}), \texttt{topicmodels} ({\textbf{???}}),
-\texttt{word2vec} ({\textbf{???}}), and \texttt{wordcloud}
-({\textbf{???}}) to examine text in the documents that were sourced for
-this project. These packages have functions for determining the
-frequency of specific words in each document or relationships (e.g.,
-pairs of adjacent terms called bigrams) and correlations between words.
-These methods can reveal what language and concepts are being
-communicated to the general public. Topic modelling is a popular method
-for analyzing text from social media platforms (Albalawi et al., 2020)
-or news articles (Jacobi et al., 2016). We estimate latent Dirichlet
-allocation (LDA) models to classify both the STP and documents according
-to the topics that are contained within them. This method ``treats each
-document as a mixture of topics, and each topic as a mixture of words''
-(Silge and Robinson, 2021). The model's output is ``a set of topics
-consisting of clusters of words that co-occur in these documents
-according to certain patterns'' (Jacobi et al., 2016). Researchers must
-then interpret the identified topics, as done after other methods of
-manual coding. We also compare the topics between the policy documents
-and the academic papers, and use our interpretation to answer the
-questions outlined above that guide this paper. This methodology is not
-familiar to many, so we describe in more detail below how we used
-specific functions and code in R to produce our results.
+have framed AST in particular ways to engage multiple audiences on this
+policy issue including parents, local residents, school representatives,
+and municipal representatives. These groups are likely identifying
+points of intervention and potential opportunities to build support for
+and encourage AST.
+
+\hypertarget{process}{%
+\subsection{4.2. Process}\label{process}}
+
+We use topic modelling in \texttt{R} to conduct the framing analysis.
+Topic modelling is a machine learning technique used to analyze text to
+identify the language and concepts being communicated. This method is
+practical for researchers working with large amounts of text because it
+replaces the manual coding of topics that would normally take place to
+analyze or summarize textual data (Jacobi et al., 2016). In the data
+pre-processing phase, we tokenize the text in the documents and create a
+document-term matrix so that it is in the correct format for analysis.
+We primarily use the following packages: \texttt{tidytext} (Robinson and
+Silge, 2021), \texttt{topicmodels} (Grün and Hornik, 2021),
+\texttt{word2vec} (Wijffels, 2021), and \texttt{wordcloud} (Fellows,
+2018) to examine text in the documents that were sourced for this
+project. These packages have functions for determining the frequency of
+specific words in each document or relationships (e.g., pairs of
+adjacent terms called bigrams) and correlations between words. Topic
+modelling is a popular method for analyzing text from social media
+platforms (Albalawi et al., 2020) and news articles (Jacobi et al.,
+2016). We estimate latent Dirichlet allocation (LDA) models to classify
+both the STP and academic documents according to the topics that are
+contained within them. This method ``treats each document as a mixture
+of topics, and each topic as a mixture of words'' (Silge and Robinson,
+2021). The model's output is ``a set of topics consisting of clusters of
+words that co-occur in these documents according to certain patterns''
+(Jacobi et al., 2016). Researchers must then interpret the identified
+topics, as done after other methods of manual coding. We also compare
+the topics between the policy documents and the academic papers, and use
+our interpretation to answer our research question. We describe in more
+detail the functions and code in \texttt{R} that we used.
 
@@
 This paper is an example of open and reproducible research that uses
-only open software. All data were obtained from publicly available
-sources and organized in the form of a data package. Following best
-practices in spatial data science ({\textbf{???}}), the code and data
-needed to reproduce or conduct a similar analysis for other regions in
-North America or elsewhere are available for download.
+only open software. All data are organized in the form of an open data
+product (Arribas-Bel et al., 2021). Following best practices in spatial
+data science (\textbf{brunsdon2020opening?}), the code and data needed
+to reproduce our research or conduct a similar analysis for other
+regions are available for download.
 
@@
 
-We analyzed word and document frequency for each set of documents (i.e.,
-corpus). Table \ref{tab:word-table} shows the most frequent terms found
-in the municipal, transportation consortia, school board, and academic
-documents. As expected, policy documents and academic papers reference
-\emph{active travel}, \emph{walking}, \emph{biking} or \emph{cycling},
-and \emph{students} more than other terms. Each corpus also has
-\emph{safety} and \emph{traffic} as common words which suggests
-congruence on these key factors between the research literature and how
-AST is framed to the public. The word \emph{physical} is present in each
-corpus, but it's not clear what this refers to (e.g, \emph{physical
-activity}, \emph{physical health}, or the \emph{physical environment}).
+We analyzed word and document frequency for each corpus of text. Table
+\ref{tab:word-table} shows the most frequent terms found in the
+municipal, transportation consortia, school board, and academic
+documents. Policy documents and academic papers reference \emph{active},
+\emph{travel}, \emph{walking}, \emph{biking} or \emph{cycling}, and
+\emph{students} more than other terms. Each corpus also has
+\emph{safety} and \emph{traffic} as common words which suggests that
+such concerns are a common reason given for parents driving their
+children to school. The word \emph{physical} is present in each corpus,
+but it's not clear what this refers to (e.g, \emph{physical activity},
+\emph{physical health}, or the \emph{physical environment}).
 Furthermore, documents from STP stakeholder groups discuss
 \emph{resources}, \emph{information}, and \emph{services} about school
-travel. In the section below, the context in which these terms are
-discussed is explored further.
-
-Unlike the academic papers, policy documents include the words
-\emph{route} or \emph{routes} as frequent terms. This could reflect the
-role of STP stakeholder groups in identifying safe routes to school to
-share with parents or families, as well as the STP emphasis on making
-the physical environment safer for AST. The academic corpus differs from
-the policy documents in that \emph{parents} and \emph{distance} are the
-second and third most common terms. In addition, \emph{time},
-\emph{factors}, \emph{environment}, and \emph{age} are also identified
-in the academic papers. These words are absent from the list of common
-words in policy documents. Table \ref{tab:word-table} indicates that the
-academic corpus discusses a broader range of determinants of AST than
-the policy documents. The number of references for each term in the
-academic papers is also significantly higher due to the inclusion of
-more documents.
+travel. Unlike the academic papers, policy documents include the words
+\emph{route} or \emph{routes} as frequent terms. This could indicate the
+presence of ``safe routes to school'' in the policy corpus, as well as
+the role of STP stakeholder groups in identifying safe routes to school
+to share with parents or families. In the section below, the context in
+which these terms are used is explored further.
+
+The academic corpus differs from the policy documents in that
+\emph{parents} and \emph{distance} are the second and third most common
+terms. In addition, \emph{time}, \emph{factors}, \emph{environment}, and
+\emph{age} are also identified in the academic papers. The prevalence of
+these terms is consistent with an academic focus on exploring the
+variables that influence mode choice. These words are absent from the
+list of common words in policy documents. Table \ref{tab:word-table}
+indicates that the academic corpus discusses a broader range of
+determinants of AST than the policy documents. The number of references
+for each term in the academic papers is also substantially higher due to
+the inclusion of more documents.
 
@@
 
+Examination of document frequency reveals terms that are not present in
+all policy documents. This suggests that although documents pertain to
+the subject of school travel, not all stakeholders across Ontario are
+disseminating information about AST. For example, a document may discuss
+active travel but not to school. Some documents present school travel
+options by bus but not by active modes. We manually searched the policy
+corpus and found that 48\% of documents mention AST and 16\% mention
+STP. This confirms that many municipalities, school boards, and
+transportation consortia do not promote AST through their webpages or
+indicate their involvement in the STP process. Instead, inclement
+weather and its impacts on busing is a common topic addressed in school
+board and transportation consortia documents.
+
 \hypertarget{bigrams-and-concordances}{%
@@
 
-Bigrams refer to a pair of consecutive words. We use the
-\texttt{unnest\_tokens} function from the \emph{tidytext} package to
-determine the bigrams. Figures \ref{fig:city-visual},
-\ref{fig:consortia-visual}, and \ref{fig:school-visual} show the bigrams
-that occur more than 5 times for each set of policy documents. These
-figures help to make further sense of the word frequencies reported
-above, and highlight the main ideas that are presented to the public in
-each of the policy corpora. Municipalities primarily discuss
-\emph{physical activity} (n = 53) and \emph{public health} (n = 19) in
-the context of AST. In addition, \emph{travel planning} (n = 19),
-\emph{bike lanes} (n = 16), and \emph{safe routes} (n = 14) are also
-identified, conceivably as either proposed solutions or built
-environment factors that support AST. Key issues related to transport
-such as \emph{traffic safety} (n = 10), \emph{air quality} (n = 9), and
-\emph{greenhouse gases} (n = 9) are conveyed to the public through these
-policy documents. It is not surprising to find this focus given that
-municipalities in Ontario are concerned about climate change and have
-increasingly looked to active modes of travel to offset
-transport-related emissions in urban areas.
-
-Similar word bigrams are found in school board documents: \emph{travel
+Bigrams refer to a pair of consecutive words. Figures
+\ref{fig:city-visual}, \ref{fig:consortia-visual}, and
+\ref{fig:school-visual} show the bigrams that occur more than 5 times
+for each set of policy documents. These figures help to make further
+sense of the word frequencies reported above, and highlight the main
+ideas that are presented to the public in each of the policy corpora.
+The directional arrows indicate the arrangement of the words (e.g.,
+active travel and not travel active) and the colour gradient of the
+arrows corresponds to the most frequently mentioned pairs (e.g., bigrams
+with darker arrows are found more often).
+
+Municipalities primarily discuss \emph{physical activity} (n = 53) and
+\emph{public health} (n = 19) in the context of AST. In addition,
+\emph{travel planning} (n = 19), \emph{bike lanes} (n = 16), and
+\emph{safe routes} (n = 14) are also identified, conceivably as either
+proposed solutions or built environment factors that support AST. Key
+issues related to transport such as \emph{traffic safety} (n = 10),
+\emph{air quality} (n = 9), and \emph{greenhouse gases} (n = 9) are
+conveyed to the public through these policy documents. It is not
+surprising to find this focus given that municipalities in Ontario are
+concerned about climate change and have increasingly looked to active
+travel to offset transport-related emissions in urban areas.
+
+Similar bigrams are found in school board documents: \emph{travel
 planning} (n = 33), \emph{safe routes} (n = 15), \emph{physical
 activity} (n = 10), and \emph{public health} (n = 10) are among the most
-common bigrams. Both municipalities and school boards in Ontario seem to
+common. Both municipalities and school boards in Ontario seem to
 emphasize what can be or has been done to improve AST (i.e., policy or
@@
 other STP stakeholders, school boards also consider \emph{inclement
-weather} (n = 24) and \emph{bus cancellations} (n = 13). This is likely
-because many students in Ontario travel to school by bus and this
-information is presented alongside AST options. Finally, transportation
-consortia documents highlight topics such as \emph{physical activity} (n
-= 10), \emph{pedestrian safety} (n = 8), \emph{crossing guards} (n = 6),
-\emph{travel planning} (n = 6), and \emph{walk zones} (n = 6). Biking or
-cycling is notably absent from transportation consortia documents.
-Overall, the policy documents There appears convey an emphasis on the
-built environment, rather than household decision-making.
+weather} (n = 24) and \emph{bus cancellations} (n = 13). Most likely
+this is because school boards are mandated to provide transportation to
+school in Ontario (typically by bus) and this information is presented
+alongside AST options. Finally, transportation consortia documents
+highlight topics such as \emph{physical activity} (n = 10),
+\emph{pedestrian safety} (n = 8), \emph{crossing guards} (n = 6),
+\emph{travel planning} (n = 6), and \emph{walk zones} (n = 6). Biking
+and cycling are notably absent from transportation consortia documents.
+Overall, the policy documents appear to convey an emphasis on the built
+environment, rather than household decision-making.
 
@@
 
-\caption{\label{fig:city-visual}Most common bigrams found in the municipal or regional government documents.}\label{fig:city-visual}
+\caption{\label{fig:city-visual}Most common bigrams found in the municipal and regional government documents.}\label{fig:city-visual}
 \end{figure}
@@
 
-We then combine all municipality, school board, and transportation
-consortia documents into one ``policy'' corpus. This enabled us to
-examine and visualize the most common bigrams found across all of the
+We then combined all municipality, school board, and transportation
+consortia documents into one ``policy+practice'' corpus. This enabled us
+to examine and visualize the most common bigrams found across all of the
 material in Ontario that was collected for this study. Figure
 \ref{fig:policy-visual} shows all of the bigrams that occur more than 10
-times in the policy corpus. In addition to the bigrams already
+times in the policy+practice corpus. In addition to the bigrams already
 identified above, we also found \emph{mental health}, \emph{walk day},
-and \emph{green communities} as common pairs of consecutive words. The
-latter terms represent the significant involvement of the non-profit
-organization in supporting AST initiatives through the Ontario Active
-School Travel program. Overall, the policy documents from STP
-stakeholder groups seem to focus on four key areas: i) benefits or
-impacts of AST; ii) mechanisms of intervention; iii) concerns or
+and \emph{green communities} as common pairs of consecutive words.
+\emph{Green Communities Canada} is a non-profit organization that has
+significantly supported AST initiatives through the Ontario Active
+School Travel program so the high frequency of this term in the
+policy+practice corpus is not surprising. Overall, the policy documents
+from STP stakeholder groups seem to focus on four key areas: i) benefits
+or impacts of AST; ii) mechanisms of intervention; iii) concerns or
 considerations; and iv) supports for AST. This interpretation indicates
 that the general public accessing information about AST in Ontario is
-informed about an adequate range of content related to this issue.
-
-Next, we analyze bigrams in the academic corpus separately to make
-comparisons with the policy corpus. Figure \ref{fig:academic-visual}
-indicates that academic papers include several common bigrams that were
-also found in the policy documents including \emph{physical activity} (n
-= 1566), which is the top bigram, \emph{traffic safety} (n = 308), and
-\emph{safe routes} (n = 268). However, many other factors are identified
-in the research literature that are not presented to the general public
-through policy documents. After \emph{physical activity}, \emph{built
-environment} (n = 1175), \emph{independent mobility} (n = 774), and
-\emph{urban form} (n = 352) are the most frequent pairs of consecutive
-words. Academic papers also often discuss \emph{distance home} (n =
-258), \emph{car ownership} (n = 254), \emph{household income} (n = 254),
-and \emph{population density} (n = 205), which are factors that have
-been found to influence AST. It is evident that many papers investigate
-gender differences in AST given that \emph{boys girls} (n = 211) is
-another common bigram. Finally, the presence of \emph{statistically
-significant} among the top bigrams underscores that some researchers aim
-to identify determinants using statistical measures. We find that the
-academic corpus focuses on a greater range of topics than found in the
-policy documents.
+informed about a wide range of content related to this issue.
+
+Next, we analyzed bigrams in the academic corpus separately to make
+comparisons with the policy+practice corpus. Figure
+\ref{fig:academic-visual} indicates that academic papers include several
+common bigrams that were also found in the policy documents including
+\emph{physical activity} (n = 1566), which is the top bigram,
+\emph{traffic safety} (n = 308), and \emph{safe routes} (n = 268).
+However, many other factors are identified in the research literature
+that are not presented to the general public through policy documents.
+After \emph{physical activity}, \emph{built environment} (n = 1175),
+\emph{independent mobility} (n = 774), and \emph{urban form} (n = 352)
+are the most frequent pairs of consecutive words. Academic papers also
+often discuss \emph{distance home} (n = 258), \emph{car ownership} (n =
+254), \emph{household income} (n = 254), and \emph{population density}
+(n = 205), which are factors that have been found to influence AST. Many
+papers also investigate gender differences in AST given that \emph{boys
+girls} (n = 211) is another common bigram. Finally, the presence of
+\emph{statistically significant} among the top bigrams underscores that
+researchers often aim to identify associations using statistical
+measures. We found that the academic corpus focuses on a greater range
+of topics than found in the policy documents.
 
@@
 
-We interpret the most common bigrams from the policy corpus (see Figure
-\ref{fig:policy-visual}), which includes all documents from
+We interpreted the most common bigrams from the policy+practice corpus
+(see Figure \ref{fig:policy-visual}), which includes all documents from
 municipalities, transportation consortia, and school boards, as the main
-ideas that STP stakeholder groups are focusing on and communicating to
-the public about AST. We then use the \texttt{kwic} function from the
-\emph{quanteda} package to better understand the context of these key
-ideas. Table \ref{tab:policy-concordance} presents some examples of the
-context that was extracted from select policy documents to demonstrate
-how the most common bigrams are communicated to the public.
+ideas that STP stakeholder groups focus on and communicate to the public
+about AST. We then examined the context of these key ideas by extracting
+words-in-context from the corpora. Table \ref{tab:policy-concordance}
+presents some examples from select policy documents that illustrate how
+the most common bigrams are communicated to the public.
 
@@
 \textbf{\cellcolor{gray!6}{Lanes}} & \cellcolor{gray!6}{Municipality} & \cellcolor{gray!6}{We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments.}\\
-\textbf{Mental Health} & Municipality & ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.\\
+\textbf{Mental Health} & Municipality & Active and Sustainable School Travel (ASST) not only improves physical and mental health but contributes to a healthier environment and safer streets.\\
 \textbf{\cellcolor{gray!6}{Physical Health}} & \cellcolor{gray!6}{Municipality} & \cellcolor{gray!6}{Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.}\\
@@
 
-\hypertarget{topic-modelling-1}{%
-\subsection{5.3. Topic modelling}\label{topic-modelling-1}}
+\hypertarget{topic-modelling}{%
+\subsection{5.3. Topic modelling}\label{topic-modelling}}
 
@@
 
-Finally, we conduct topic modelling to examine the different topics
-found in the policy and academic corpora. We focus on the policy corpus,
-instead of individually assessing the municipal, school, and consortia
-documents, so that we could report on the various frames used across all
-documents put out by STP stakeholder groups in Ontario. To determine the
-number of discrete topics in each corpus, we use the \emph{ldatuning}
-package. We then use the \texttt{LDA} function from the
-\emph{topicmodels} package to estimate an LDA model for each group of
-documents. The parameters from the \emph{ldatuning} package suggest that
-the policy corpus has between 7 and 9 topics and the academic corpus has
-between 17 and 25 topics. After running the LDA model for the academic
-corpus, it was too difficult to interpret a minimum of 17 topics based
-on the clusters of words that were identified. We experimented with the
-model by adjusting and evaluating the number of topics and found that
-there were 9 distinct topics that could be interpreted, after which
-there was too much overlap. Figures \ref{fig:policy-terms} and
+For the final part of our analysis, we conducted topic modelling to
+examine the different topics found in the policy and academic corpora.
+We focused on the policy+practice corpus, instead of assessing the
+municipal, school, and consortia documents separately, so that we could
+report on the various frames used across all documents put out by STP
+stakeholder groups in Ontario. We then estimated Latent Dirillecth
+Allocation (LDA) models for each corpus. Parameter tuning suggests that
+the policy+practice corpus has between 7 and 9 topics and the academic
+corpus has between 17 and 25 topics. After running the LDA model for the
+academic corpus, we realized the difficulty of interpreting a minimum of
+17 topics based on the clusters of words that were identified. We
+experimented with the model by adjusting and evaluating the number of
+topics and found that there were 9 distinct topics that could be
+interpreted, after which there was too much overlap for the clusters to
+be meaningfully interpreted. Figures \ref{fig:policy-terms} and
 \ref{fig:academic-terms} present the main terms that are associated with
@@
 
-In the policy corpus, we interpret the following topics based on the
-cluster of words: (1) resources for walking; (2) walking; (3) supporting
-active travel; (4) bicycling and the environment; (5) benefits of active
-travel; (6) safety; and (7) busing information and eligibility. These
-topics indicate that STP stakeholder groups are sending the message that
-walking and bicycling to school are healthy travel modes for students,
-particularly as a means to get physical activity. We also found that
-there is information shared to support parents and students in using
-active modes to school such as the availability of cycling lanes or
-route tips for walking. STP stakeholder groups are appear to be
-addressing the issue of safety.
+In the policy+practice corpus, we identified the following topics based
+on the cluster of words: (1) resources for walking; (2) walking; (3)
+support for active travel; (4) bicycling and the environment; (5)
+benefits of active travel; (6) safety; and (7) busing information and
+eligibility. These topics indicate that STP stakeholder groups are
+sending the message that walking and bicycling to school are healthy
+travel modes for students, particularly in terms of physical activity.
+We also found that information is shared to support parents and students
+in using active modes to school, for example regarding the availability
+of cycling lanes and tips for route choice for walking.
 
 The academic corpus has a higher number of topics likely due to the
-volume of papers that were sourced. The following topics were identified
-based on the clusters of words: (1) built environment (2) walking
-distance; (3) AST interventions; (4) parental barriers to walking; (5)
-behaviours and attitudes; (6) bicycling; (7) social environment; (8)
-children's independent mobility; (9) modeling trip choice; (10)
-adolescents and physical activity; and (11) safe routes to school
-programs. This corpus reflects a broader range of topics than the policy
-corpus.
-
-We conclude that the policy corpus primarily frames AST as a health and
-environmental issue. Policy documents do not reflect the diversity of
-content found in the academic papers and instead focus on a few factors.
-STP stakeholder groups appear to position walking, bicycling, or rolling
-to school as beneficial to individual health, as an opportunity for
-physical activity or to improve mental health, and to the broader
+volume of papers included. The following topics were identified based on
+the clusters of words: (1) built environment (2) walking distance; (3)
+AST interventions; (4) parental barriers to walking; (5) behaviours and
+attitudes; (6) bicycling; (7) social environment; (8) children's
+independent mobility; (9) modeling trip choice; (10) adolescents and
+physical activity; and (11) safe routes to school programs. This corpus
+reflects a broader range of topics than the policy+practice corpus.
+
+\hypertarget{frames}{%
+\subsection{5.4. Frames}\label{frames}}
+
+Based on the identified bigrams and topics, we determined that the
+policy+practice corpus primarily frames AST as a health and
+environmental issue. STP stakeholder groups appear to position walking,
+bicycling, or rolling to school as beneficial to individual health, via
+physical activity and improved mental health, and to the broader
 community through a reduction in traffic and vehicle emissions. Here, we
-present some examples from the policy documents to illustrate how the
-health and environmental frames are communicated:
+present some examples from the policy documents that illustrate how the
+health and environmental frame is communicated:
 
@@
 \begin{quote}
-\emph{Walking to school is a great way to add physical activity into
-your child's busy day.} (Region of Haldimand-Norfolk Region)
-\end{quote}
-
-\begin{quote}
 \emph{Active school travel is a great way for children to be physically
@@
 
-However by examining document frequency (see Section 5.1), we found that
-some terms are not present in all policy documents. This suggests that
-although documents pertain to the subject of active travel or school
-travel, some stakeholders across Ontario are not disseminating
-information about AST. For example, a document may discuss active travel
-but not to school or school travel but only by bus and not by active
-modes. We manually searched the policy corpus and found that 48\% of
-documents mention AST and 16\% mention STP. This confirms that many
-municipalities, school boards, and transportation consortia are not
-promoting AST through their webpages or indicating their involvement in
-the STP process. Instead, inclement weather and impacts to busing is a
-common topic addressed in school board and transportation consortia
-documents.
-
-Furthermore, we found that some policy documents make direct reference
-to topics found in the academic papers. For example, some policy
-documents encourage AST programs that have been researched and evaluated
-in the literature, such as walking school buses, or explain how an
-increase in AST will reduce parent safety concerns.
+Furthermore, we found that policy documents make claims about the
+benefits of AST that are consistent with the findings of academic
+research and evaluation.
 
 \begin{quote}
-\_ For their health, safety, environment and community: Kids learn
+\emph{For their health, safety, environment and community: Kids learn
 healthy habits and concentrate better in class; One less car (yours)
@@
 about traffic safety; Start a walking school bus; your kids make friends
-in every grade, and that can prevent bullying.\_ (City of Guelph)
+in every grade, and that can prevent bullying.} (City of Guelph)
 \end{quote}
@@
 
-The secondary frame for AST in policy documents is the opportunity or
-prospect of behaviour change. Some cities and schools explain how
-children and parents can leave the car at home and make the journey to
-school on foot or by bike by describing efforts to make AST safer. This
-frame encourages the public to evaluate their own travel decisions and
-to access resources (e.g., walking skills checklist) that will help them
-make AST a first choice. Some documents emphasize the role of the parent
-in creating opportunities for AST in their household or neighbourhood,
-however few documents address the main barriers as perceived by parents
-(e.g., distance, travel arrangements for multiple people, or
-convenience). Examples of this secondary frame include:
+The secondary frame in policy documents is that AST is accessible and
+feasible for children and parents. The documents indicate that there is
+an opportunity for or prospect of behaviour change. Some cities and
+schools explain how children and parents can leave the car at home and
+make the journey to school on foot or by bike. This frame encourages the
+public to evaluate their own travel decisions and to access resources
+(e.g., walking skills checklist) that will help them make AST a first
+choice. Examples of this secondary frame include:
 
 \begin{quote}
-\_A way to make sure your child is safe while walking to school is with
-a `walking school bus.' Here are some tips for a walking school bus:
-Invite families who live nearby to walk; Pick a route and take a test
-walk; Take side streets and paths that are less busy with traffic;
+\emph{A way to make sure your child is safe while walking to school is
+with a `walking school bus.' Here are some tips for a walking school
+bus: Invite families who live nearby to walk; Pick a route and take a
+test walk; Take side streets and paths that are less busy with traffic;
 Decide how often the group will walk together; Talk with your boss to
-adjust your day; Have fun! (City of Ottawa)
+adjust your day; Have fun!} (City of Ottawa)
 \end{quote}
@@
 
-Finally, the policy documents discuss proposed solutions to encourage
-AST. STP stakeholder groups seem to be communicating that AST is
-possible and safe as a result of improvements to the built environment
-and available resources for parents and children. A final focus in the
-policy documents is on various efforts that are underway to support AST
-including route planning. A few examples include:
+Finally, both AST frames present solutions to encourage AST. STP
+stakeholder groups seem to be communicating that AST is a healthy and
+easy option as a result of policy changes (e.g., available resources for
+parents and children) and improvements to the built environment. This
+could include examples of various efforts that are underway to support
+AST including route planning.
 
@@
 
-\hypertarget{framing-in-stp-documents}{%
-\subsection{6.1. Framing in STP
-documents}\label{framing-in-stp-documents}}
+\hypertarget{current-ast-frames-in-ontario}{%
+\subsection{6.1. Current AST frames in
+Ontario}\label{current-ast-frames-in-ontario}}
 
 Using natural language processing techniques, we analyzed how AST is
-framed in documents available to the general public on the websites of
-STP stakeholder groups in Ontario. We found that AST is primarily framed
-to parents as beneficial to the health and wellbeing of children and to
-environmental sustainability. This was confirmed by the most common
-bigrams identified in the policy corpus, as well as the topics
-identified by the LDA model. The policy documents adequately reflect the
-evidence that AST contributes positively to children's physical health
-(see Faulkner et al., 2009; Schoeppe et al., 2015), although the
-statements regarding the benefits of AST to children's school
-performance and cognitive development need to be studied further to
-produce stronger evidence ({\textbf{???}}). STP stakeholder groups also
-communicate that increasing AST may reduce traffic near and around
-schools. This presumably is communicated to alleviate parental concerns
-about traffic and safety (Evers et al., 2014; Mammen et al., 2012;
-Rothman et al., 2015; Wilson et al., 2018) or reduce the frequency of
-risky behaviours from drivers around schools (Rothman et al., 2017).
-However, the documents do not explain why declining rates of AST are a
-problem for the particular community or convey any urgency to this issue
-so that it attracts the attention of parents, the general public, or
-policy makers. Communicating the potential outcomes of increased AST may
-be persuasive arguments to motivate behaviour change, but these
-documents do not appear to encourage parents or the general public to
-view their behaviour as problematic or unhealthy for their children's
-development. For example, parents who escort their children to school
-have reported concerns about traffic volume around schools (Mammen et
-al., 2012), but may not recognize that their own behaviour contributes
-to the problem that is perceived to prevent their child from safely
-walking or bicycling to school (Collins and Kearns, 2001).
-
-The secondary frame of AST that we interpreted based on the LDA model is
-the opportunity or prospect of behaviour change. STP stakeholder groups
+framed in 69 documents available to the public on the websites of STP
+stakeholder groups in Ontario. Two main frames in the policy+practice
+corpus were identified based on the most common bigrams and topics from
+the LDA model.
+
+We found that AST is primarily framed to parents as beneficial to the
+health and wellbeing of children and to environmental sustainability.
+The policy documents reflect the evidence that AST contributes
+positively to children's physical health (see Faulkner et al., 2009;
+Schoeppe et al., 2015), although the statements regarding the benefits
+of AST to children's school performance are less well-supported in the
+extant literature (\textbf{westmanChapterThreeTravel2020?}). STP
+stakeholder groups also communicate that increasing AST may reduce
+traffic near and around schools. This is conveyed presumably to
+alleviate parental concerns about traffic and safety (Evers et al.,
+2014; Mammen et al., 2012; Rothman et al., 2015; Wilson et al., 2018) or
+to reduce the frequency of risky behaviours from drivers around schools
+(Rothman et al., 2017).
+
+In the secondary frame, AST is presented as an accessible and feasible
+way for children to travel to and from school. Children and parents are
+encouraged to adopt new travel behaviours. STP stakeholder groups
 identified different ways that parents could encourage or support their
-child(ren) to commute to school by using active modes. Some school
-boards and municipalities also shared resources such as walking tip
-sheets and guidance for starting a walking school bus. Other advice
-included dropping children off one or two blocks away from school so
-that they could walk or bike part of the trip. The general emphasis is
-communicating information that could change parental perceptions about
-the ease of their children using active modes to school, which may be
-seen by STP stakeholder groups as a ``modifiable'' factor (see Riazi et
-al., 2019). In turn, this could encourage parents to modify their
+children to commute to school by using active modes. Some school boards
+and municipalities also shared resources such as walking tip sheets and
+guidance for starting a walking school bus. Other advice included
+dropping children off one or two blocks away from school so that they
+could walk or bike part of the trip. The general emphasis of this frame
+is communicating information that could change parental perceptions
+about the ease of their children using active modes to school, which may
+be seen by STP stakeholder groups as a ``modifiable'' factor (see Riazi
+et al., 2019). In turn, this could encourage parents to modify their
 routines and incorporate opportunities for their children to use active
@@
 
-We found that interpersonal behaviour changes achieved through
-educational strategies and engineering changes (e.g., traffic calming
-measures, reduced speed limits, etc.) are communicated to the general
-public as potential solutions to address the decline of AST. This
-reflects findings from the AST literature (Panter et al., 2010), but
-these solutions have to sufficiently address real and perceived barriers
-from parents about the household environment and the built environment
-(see Section 2.2). In most documents, STP stakeholder groups provide
-parents with resources that help them switch modes for the school
-commute and/or on reassure them that the built environment has become
-safer and friendlier to active travelers as a result of infrastructure
-or policy improvements. As previously noted, the documents do not appear
-to present a strong ``call to action'' that urges behaviour change for
-parents or the general public, which may affect the success of STP
-interventions. On the other hand, the emphasis on engineering changes
-may reflect the strong engagement of the ``policy stream'' (Kingdon,
-1984) and the feasible options to address the problem, since engineering
-staff and municipal representatives are common STP stakeholders
-(Buttazzoni et al., 2018; Mammen et al., 2015).
-
-Given the range of factors that influence AST in a Canadian setting
-(\emph{inter alia}, see Mammen et al., 2012; Mitra, 2013; Rothman et
-al., 2018; Wilson et al., 2018), STP stakeholder groups must decide
-which points of intervention that they can reasonably have some
-influence towards. This would also depend on the local context to ensure
-that barriers to AST as perceived by parents are addressed. It could be
-that STP stakeholder groups perceive to have more control over
-micro-scale elements of the built environment, like traffic calming
-measures or speed limits, rather ``non-modifiable'' factors like street
-density or land use mix. It would also certainly be much more difficult
-for STP stakeholder groups to influence the number of trips to different
-destinations that households need to make or to intervene in residential
-location, which affects distance to school. A focus on changing parental
-perceptions is recommended by many scholars since parents are the
-``gatekeeper'' for children's mobility, but the information communicated
-by STP stakeholder groups in Ontario should reflect a broader range of
-factors that influence AST.
+Both frames present the AST issue in a positive light. Neither frame
+appears to explain why declining rates of AST are a problem or convey
+any urgency to this issue so that it attracts the attention of parents,
+the general public, or policy makers. Communicating the potential
+outcomes of increased AST may be persuasive arguments to motivate
+behaviour change, but these frames do not seem to encourage parents or
+the general public to view their current behaviour as problematic or
+unhealthy for their children's development and their community. Thus,
+behaviour change is presented as an option for some but not an
+imperative for all. For example, parents who drive their children to
+school have reported concerns about traffic volume around schools
+(Mammen et al., 2012), but may not recognize that their own behaviour
+contributes to the problem that is perceived to prevent their child from
+safely walking or bicycling to school (Collins and Kearns, 2001).
+Reynard et al. (2021) similarly found in their analysis of Canadian
+municipal documents that one of the dominant frames presented the
+adoption of behaviours to help mitigate the climate crisis as a choice
+but not ``the expected norm.''
+
+We found that the proposed solutions in the secondary frame to increase
+AST align with different levels of the socioecological model: 1)
+behaviour change from individuals or households making different travel
+decisions; 2) policies like STP that create resources for AST; and 3)
+engineering solutions like bicycle lanes. This reflects findings from
+the AST literature that a range of solutions are needed to address
+different factors that influence AST (\emph{inter alia, see} Mitra,
+2013; Panter et al., 2010). The recognition of engineering changes may
+reflect the strong engagement of the ``policy stream'' (Kingdon, 1984)
+since engineering staff and municipal representatives are common STP
+stakeholders in Canada (Buttazzoni et al., 2018; Mammen et al., 2015),
+as well as the evidence that the built environment influences mode
+choice to school. Although it is beyond the scope of this paper to
+assess whether the proposed solutions are perceived to be sufficient by
+parents for increasing AST.
 
@@
 
-There is a noticeable lack of focus on individual and interpersonal
-determinants of AST in the policy documents. For example, the role of
-convenience and inclement weather in shaping household travel decisions
-(Buliung et al., 2011) or the age at which children become allowed to
-travel by active modes or independently (Mammen et al., 2012) were not
-discussed. The desire to escort children to school, which has been noted
-by parents as a reason to continue driving (Westman, Friman, et al.,
-2017), is also not adequately addressed by STP stakeholder groups. The
-complexity of travel arrangements that must be coordinated by households
-(see Buliung et al., 2021) and the dominant parenting culture to protect
-children from risk ({\textbf{???}}) are likewise overlooked. STP
-stakeholders may wish to emphasize to parents that older children have
-greater traffic safety and cognitive abilities to navigate their own
-routes to school, which could encourage parents to develop their
-child(ren)'s travel skills over time. Additional attention should be
-paid to the reasons why parents perceive driving to be more convenient.
-
-Coming back to Kingdon's Multiple Streams Framework (1984), we posited
-that STP stakeholder groups need to raise awareness about the AST issue
-among parents and the general public through the problem stream. This
-could influence perceptions about the issue and encourage behaviour
-change. Based on the policy documents, it is not obvious that AST has
-declined significantly over the past few decades in Canada or that this
-issue merits urgent attention. Many municipalities, schools, and
-transportation consortia in Ontario use similar content in their public
-documents about AST. It would be worthwhile for STP stakeholder groups
-to frame the decline of AST as a ``problem'' worth addressing with
-information specific to each local context. STP stakeholders also need
-to ensure that their communication accounts for the ways in which
-Canadian parents perceive the built environment in different ways than
-planners (see Buliung et al., 2021). If there is ``conceptual
-asymmetry'' as Buliung et al.~(2021) identified, the materials
-disseminated by STP stakeholders may not resonate or reach parents.
-Future research or STP activities should investigate how parents or the
-general public respond to messages or information that encourages the
-adoption of AST and evaluate how effective they are to motivate
-behaviour change. It would be helpful to know which frames would most
+STP stakeholders should problematize the significant decline in AST that
+has occurred over recent decades in Canada and emphasize that this issue
+merits urgent behaviour change. A study investigating the influence of
+different valence framings of CO2 emissions on transport mode shift
+found that positive framing can be less effective than negative framing
+(\textbf{waygoodCO2ValenceFraming2018?}). Policy documents should make
+it clear that continued use of nonactive modes to school can deprive
+children of opportunities to increase physical activity and to gain
+health and social benefits.
+
+There is a noticeable lack of focus on certain household determinants of
+AST in the two frames that needs to be addressed. For example, the role
+of convenience and inclement weather in shaping household travel
+decisions (Buliung et al., 2011) and the complexity of travel
+arrangements that must be coordinated by households (see Buliung et al.,
+2021) were not found to be discussed. The desire to escort children to
+school, which has been noted by parents as a reason to continue driving
+(Westman et al., 2017a), is also not adequately addressed by STP
+stakeholders. Parental assessment of a child's ability to handle the
+journey to school was likewise overlooked despite its role in decision
+making for mode choice to school
+(\textbf{faulknerWhatQuickestEasiest2010?}). Framing AST as a
+developmental opportunity or a rite of passage that children have been
+denied could challenge the prevailing culture of risk which discourages
+parents from letting their children use active modes to school. In
+communities with low AST uptake, STP stakeholders may wish to emphasize
+the negative effects of parents continuing to drive children to and from
+school. A negative framing that challenges the social norm of driving
+could be more motivational to shift modes, which would be consistent
+with other findings (\textbf{waygoodCO2ValenceFraming2018?}).
+
+Future research and evaluation by STP stakeholders should investigate
+how parents or the general public respond to messages or information
+that encourages the adoption of AST and evaluate which are most
+effective. It would be helpful to understand which frames would most
 encourage behaviour change or increase political support for
@@
 could ensure that educational strategies and promotional materials
-increase buy-in for their target audience.
-
-Although the ``policy stream'' appears to have been adequately engaged
-in Ontario communities, it could be that the decline of AST has not been
-sufficiently framed as ``problematic'' to warrant more widespread
-awareness or solutions. If Canadian STP stakeholder groups wish to
-involve more local residents in their efforts (Buttazzoni et al., 2018),
-it would also be worthwhile for them to produce different materials that
-communicate why this issue is important to the general public,
-regardless of whether they currently have children commuting to/from
-school. The ``political stream'' could also be further engaged by
-working with advocacy groups who could attract more support from a
+increase buy-in for their target audience. If Canadian STP stakeholders
+wish to involve more local residents in their efforts (Buttazzoni et
+al., 2018), it would also be worthwhile for them to produce different
+materials that communicate why this issue is important to the general
+public, regardless of whether they currently have children commuting
+to/from school. The ``political stream'' could also be further engaged
+by working with advocacy groups who could attract more support from a
 broader coalition of individuals.
 
-Finally, Rothman et al.~(2018) note that local solutions to address
-specific school challenges are needed, and we extend this recommendation
-to include local context in STP messaging about AST. Instead of generic
-content about AST, stakeholders involved in STP should produce more
-information that specifically responds to parents' perceived barriers
-and challenges that were identified in that local context. For example,
-STP materials could explain how known concerns in a particular
-municipality or school area have been addressed through local solutions.
-This could reflect that solutions have been identified based on what was
-heard from the community.
+We also contend that the ways in which the AST issue is framed can
+affect the policy process, as outlined in Kingdon's (1984) Multiple
+Streams Framework (MSF), through all three streams (i.e., problem,
+policy, and politics). This framing can ultimately impact the timing and
+success of a ``window of opportunity'' to enact policy changes that
+address the decline of AST in Canada.
 
@@
 easily accessible to the general public on the websites of STP
-stakeholder groups in Ontario. Parents likely receive information about
-AST directly from schools, which may contain more content that reflects
-the local barriers to AST.
+stakeholders in Ontario. Parents likely receive information about AST
+directly from schools, which may contain more content that reflects the
+local barriers to AST.
 
@@
 We used natural language processing techniques to examine how different
-school travel planning stakeholder (STP) groups in Ontario frame the
-issue of AST. STP stakeholder groups frame AST as a health and
-environmental issue that can be addressed through household behaviour
-change and engineering solutions. Policy documents reveal that STP
-stakeholder groups are focusing on ``modifiable factors'' such as
-parental perceptions or micro-scale elements in the built environment to
-increase rates of AST. However, AST may not be framed sufficiently as a
-``problem'' that requires urgent intervention, which may impact how
-parents respond to behaviour change initiatives and limit awareness in
-the general public. In their public materials about AST, STP stakeholder
-groups should present solutions for a broader range of factors that
-influence AST and emphasize why AST rates should increase in local
-communities.
+school travel planning (STP) stakeholders in Ontario frame the issue of
+AST. STP stakeholders frame AST as an accessible and feasible way to
+travel to school that is valuable to children's health and to the
+environment. STP stakeholders are communicating that this issue can be
+addressed through household behaviour change and policy solutions.
+Policy documents reveal that STP stakeholders are focusing on
+``modifiable factors'' such as parental perceptions or micro-scale
+elements in the built environment to increase rates of AST. However, AST
+may not be framed sufficiently as a ``problem'' that requires urgent
+intervention, which may impact how parents respond to behaviour change
+initiatives and limit awareness in the general public. In their public
+materials about AST, STP stakeholders emphasize why AST rates should
+increase in local communities and how the negative effects of nonactive
+modes to school may impact children's health and wellbeing.
 
@@
 acknowledge the developers of the following \texttt{R} packages:
-\texttt{dplyr} ({\textbf{???}}), \texttt{ggraph} ({\textbf{???}}),
-\texttt{ggplot2} ({\textbf{???}}), \texttt{igraph} ({\textbf{???}}),
-\texttt{pdftools} ({\textbf{???}}), \texttt{readr} ({\textbf{???}}),
-\texttt{reshape2} ({\textbf{???}}), \texttt{stringr} ({\textbf{???}}),
-\texttt{text2vec} ({\textbf{???}}), \texttt{textdata} ({\textbf{???}}),
-\texttt{tidyr} ({\textbf{???}}), \texttt{tidytext} ({\textbf{???}}),
-\texttt{tm} ({\textbf{???}}), \texttt{tools} ({\textbf{???}}),
-\texttt{topicmodels} ({\textbf{???}}), \texttt{widyr} ({\textbf{???}}),
-\texttt{word2vec} ({\textbf{???}}), \texttt{wordcloud} ({\textbf{???}}),
-\texttt{DiagrammeR} ({\textbf{???}}), and \texttt{kableextra}
-({\textbf{???}}).
+\texttt{dplyr} (Wickham et al., 2021b), \texttt{ggraph} (Pedersen,
+2021), \texttt{ggplot2} (Wickham et al., 2021a), \texttt{igraph} (file.,
+2021), \texttt{pdftools} (Ooms, 2021), \texttt{readr} (Wickham et al.,
+2021c), \texttt{reshape2} (Wickham, 2020), \texttt{stringr} (Wickham,
+2019), \texttt{text2vec} (Selivanov et al., 2020), \texttt{textdata}
+(Hvitfeldt, 2020), \texttt{tidyr} (Wickham, 2021), \texttt{tidytext}
+(Robinson and Silge, 2021), \texttt{tm} (Feinerer and Hornik, 2020),
+\texttt{tools} (\textbf{R-tools?}), \texttt{topicmodels} (Grün and
+Hornik, 2021), \texttt{widyr} (Robinson, 2021), \texttt{word2vec}
+(Wijffels, 2021), \texttt{wordcloud} (Fellows, 2018),
+\texttt{DiagrammeR} (\textbf{R-diagrammeR?}), and \texttt{kableextra}
+(\textbf{R-kableextra?}).
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-albalawiUsingTopicModeling2020}{}%
-Albalawi, R., Yeap, T.H., Benyoucef, M., 2020. Using Topic Modeling
-Methods for Short-Text Data: A Comparative Analysis. Frontiers in
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-albalawiUsingTopicModeling2020}{}}%
+Albalawi, R., Yeap, T.H., Benyoucef, M., 2020. Using {Topic Modeling
+Methods} for {Short}-{Text Data}: A {Comparative Analysis}. Frontiers in
 Artificial Intelligence 3, 42.
@@
 
-\leavevmode\hypertarget{ref-badlandDevelopmentSystemsModel2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-arribasOpen2021}{}}%
+Arribas-Bel, D., Green, M., Rowe, F., Singleton, A., 2021. Open data
+products-a framework for creating valuable analysis ready data. Journal
+of Geographical Systems 23, 497--514.
+doi:\href{https://doi.org/10.1007/s10109-021-00363-5}{10.1007/s10109-021-00363-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-badlandDevelopmentSystemsModel2016}{}}%
 Badland, H., Kearns, R., Carroll, P., Oliver, M., Mavoa, S., Donovan,
@@
 
-\leavevmode\hypertarget{ref-buliungSchoolTravelPlanning2011}{}%
-Buliung, R., Faulkner, G., Beesley, T., Kennedy, J., 2011. School Travel
-Planning: Mobilizing School and Community Resources to Encourage Active
-School Transportation. Journal of School Health 81, 704--712.
+\leavevmode\vadjust pre{\hypertarget{ref-borrestadExperiencesRandomisedControlled2012}{}}%
+Børrestad, L.A.B., Østergaard, L., Andersen, L.B., Bere, E., 2012.
+Experiences from a randomised, controlled trial on cycling to school:
+Does cycling increase cardiorespiratory fitness? Scandinavian Journal of
+Public Health 40, 245--252.
+doi:\href{https://doi.org/10.1177/1403494812443606}{10.1177/1403494812443606}
+
+\leavevmode\vadjust pre{\hypertarget{ref-buliungSchoolTravelPlanning2011}{}}%
+Buliung, R., Faulkner, G., Beesley, T., Kennedy, J., 2011. School
+{Travel Planning}: Mobilizing {School} and {Community Resources} to
+{Encourage Active School Transportation}. Journal of School Health 81,
+704--712.
 doi:\href{https://doi.org/10.1111/j.1746-1561.2011.00647.x}{10.1111/j.1746-1561.2011.00647.x}
 
-\leavevmode\hypertarget{ref-buliungLivingJourneySchool2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-buliungLivingJourneySchool2021}{}}%
 Buliung, R., Hess, P., Flowers, L., Moola, F.J., Faulkner, G., 2021.
@@
 
-\leavevmode\hypertarget{ref-buttazzoniPromotingActiveSchool2019}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-buttazzoniPromotingActiveSchool2019}{}}%
 Buttazzoni, A.N., Clark, A.F., Seabrook, J.A., Gilliland, J.A., 2019.
@@
 
-\leavevmode\hypertarget{ref-buttazzoniSupportingActiveSchool2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-buttazzoniSupportingActiveSchool2018}{}}%
 Buttazzoni, A.N., Coen, S.E., Gilliland, J.A., 2018. Supporting active
@@
 
-\leavevmode\hypertarget{ref-borrestadExperiencesRandomisedControlled2012}{}%
-Børrestad, L.A.B., Østergaard, L., Andersen, L.B., Bere, E., 2012.
-Experiences from a randomised, controlled trial on cycling to school:
-Does cycling increase cardiorespiratory fitness? Scandinavian Journal of
-Public Health 40, 245--252.
-doi:\href{https://doi.org/10.1177/1403494812443606}{10.1177/1403494812443606}
-
-\leavevmode\hypertarget{ref-GreenCommunities2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-GreenCommunities2016}{}}%
 Canada, G.C., 2020a. Ontario active school travel fund {[}WWW
@@
 
-\leavevmode\hypertarget{ref-GreenCommunitiesProjects}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-GreenCommunitiesProjects}{}}%
 Canada, G.C., 2020b. OAST fund project directory {[}WWW Document{]}. URL
@@
 
-\leavevmode\hypertarget{ref-chenPromotingActiveStudent2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chenPromotingActiveStudent2018}{}}%
 Chen, P., Jiao, J., Xu, M., Gao, X., Bischak, C., 2018. Promoting active
@@
 
-\leavevmode\hypertarget{ref-collinsSafeJourneysEnterprising2001}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-collinsSafeJourneysEnterprising2001}{}}%
 Collins, D.C.A., Kearns, R.A., 2001. The safe journeys of an
@@
 
-\leavevmode\hypertarget{ref-demeesterParentalPerceivedNeighborhood2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-demeesterParentalPerceivedNeighborhood2014}{}}%
 De Meester, F., Van Dyck, D., De Bourdeaudhuij, I., Cardon, G., 2014.
@@
 
-\leavevmode\hypertarget{ref-depouxCommunicatingClimateChange2017}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-depouxCommunicatingClimateChange2017}{}}%
 Depoux, A., Hémono, M., Puig-Malet, S., Pédron, R., Flahault, A., 2017.
@@
 
-\leavevmode\hypertarget{ref-eversParentSafetyPerceptions2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-eversParentSafetyPerceptions2014}{}}%
 Evers, C., Boles, S., Johnson-Shelton, D., Schlossberg, M., Richey, D.,
@@
 
-\leavevmode\hypertarget{ref-faulknerActiveSchoolTransport2009}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-farberRunning2011}{}}%
+Farber, S., Páez, A., 2011. Running to stay in place: The time-use
+implications of automobile oriented land-use and travel. Journal of
+Transport Geography 19, 782--793.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2010.09.008}{10.1016/j.jtrangeo.2010.09.008}
+
+\leavevmode\vadjust pre{\hypertarget{ref-faulknerActiveSchoolTransport2009}{}}%
 Faulkner, G.E.J., Buliung, R.N., Flora, P.K., Fusco, C., 2009. Active
@@
 
-\leavevmode\hypertarget{ref-faulknerSchoolTravelChildren2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-faulknerSchoolTravelChildren2013}{}}%
 Faulkner, G., Stone, M., Buliung, R., Wong, B., Mitra, R., 2013. School
@@
 
-\leavevmode\hypertarget{ref-fuscoUnderstandingChildrenPerceptions2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tm}{}}%
+Feinerer, I., Hornik, K., 2020. Tm: Text mining package.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-wordcloud}{}}%
+Fellows, I., 2018. Wordcloud: Word clouds.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-igraph}{}}%
+file., S.A., 2021. Igraph: Network analysis and visualization.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fuscoUnderstandingChildrenPerceptions2012}{}}%
 Fusco, C., Moola, F., Faulkner, G., Buliung, R., Richichi, V., 2012.
 Toward an understanding of children's perceptions of their transport
-geographies: (Non)Active school travel and visual representations of the
-built environment. Journal of Transport Geography, Special Section On
-Child \& Youth Mobility 20, 62--70.
+geographies: (Non)active school travel and visual representations of the
+built environment. Journal of Transport Geography, Special {section On
+Child} \& {Youth Mobility} 20, 62--70.
 doi:\href{https://doi.org/10.1016/j.jtrangeo.2011.07.001}{10.1016/j.jtrangeo.2011.07.001}
 
-\leavevmode\hypertarget{ref-gamsonChangingCulture1987}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gamsonChangingCulture1987}{}}%
 Gamson, W.A., Modigliani, A., 1987. The changing culture of affirmative
@@
 
-\leavevmode\hypertarget{ref-goffmanFrameAnalysisEssay1974}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-goffmanFrameAnalysisEssay1974}{}}%
 Goffman, E., 1974. Frame analysis: An essay on the organization of
 experience, Frame analysis: An essay on the organization of experience.
-Harvard University Press, Cambridge, MA, US.
-
-\leavevmode\hypertarget{ref-ikedaAssociationsChildrenActive2018}{}%
+{Harvard University Press}, {Cambridge, MA, US}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-topicmodels}{}}%
+Grün, B., Hornik, K., 2021. Topicmodels: Topic models.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-textdata}{}}%
+Hvitfeldt, E., 2020. Textdata: Download and load various text datasets.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ikedaAssociationsChildrenActive2018}{}}%
 Ikeda, E., Hinckson, E., Witten, K., Smith, M., 2018. Associations of
@@
 
-\leavevmode\hypertarget{ref-jacobiQuantitativeAnalysisLarge2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-jacobiQuantitativeAnalysisLarge2016}{}}%
 Jacobi, C., van Atteveldt, W., Welbers, K., 2016. Quantitative analysis
@@
 
-\leavevmode\hypertarget{ref-jensenHowObtainHealthy2008}{}%
-Jensen, S.U., 2008. How to obtain a healthy journey to school.
-Transportation Research Part A: Policy and Practice 42, 475--486.
-doi:\href{https://doi.org/10.1016/j.tra.2007.12.001}{10.1016/j.tra.2007.12.001}
-
-\leavevmode\hypertarget{ref-kingdonAgendasAlternativesPublic1984}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kingdonAgendasAlternativesPublic1984}{}}%
 Kingdon, J.W. (Ed.), 1984. Agendas, alternatives and public policies.
@@
 
-\leavevmode\hypertarget{ref-langUnderstandingModalChoice2011}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-langUnderstandingModalChoice2011}{}}%
 Lang, D., Collins, D., Kearns, R., 2011. Understanding modal choice for
@@
 
-\leavevmode\hypertarget{ref-laroucheRatherBikeSchool2016}{}%
-Larouche, R., Stone, M., Buliung, R.N., Faulkner, G., 2016. ''I'd rather
-bike to school!'': Profiling children who would prefer to cycle to
-school. Journal of Transport \& Health 3, 377--385.
+\leavevmode\vadjust pre{\hypertarget{ref-laroucheRatherBikeSchool2016}{}}%
+Larouche, R., Stone, M., Buliung, R.N., Faulkner, G., 2016. ''{I}'d
+rather bike to school!'': Profiling children who would prefer to cycle
+to school. Journal of Transport \& Health 3, 377--385.
 doi:\href{https://doi.org/10.1016/j.jth.2016.06.010}{10.1016/j.jth.2016.06.010}
 
-\leavevmode\hypertarget{ref-larsenRouteBasedAnalysisCapture2012}{}%
-Larsen, K., Gilliland, J., Hess, P.M., 2012. Route-Based Analysis to
-Capture the Environmental Influences on a Child's Mode of Travel between
-Home and School. Annals of the Association of American Geographers 102,
-1348--1365.
+\leavevmode\vadjust pre{\hypertarget{ref-larsenRouteBasedAnalysisCapture2012}{}}%
+Larsen, K., Gilliland, J., Hess, P.M., 2012. Route-{Based Analysis} to
+{Capture} the {Environmental Influences} on a {Child}'s {Mode} of
+{Travel} between {Home} and {School}. Annals of the Association of
+American Geographers 102, 1348--1365.
 doi:\href{https://doi.org/10.1080/00045608.2011.627059}{10.1080/00045608.2011.627059}
 
-\leavevmode\hypertarget{ref-mahFramecriticalPolicyAnalysis2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mahFramecriticalPolicyAnalysis2014}{}}%
 Mah, C.L., Hamill, C., Rondeau, K., McIntyre, L., 2014. A frame-critical
-policy analysis of Canada's response to the World Food Summit 19982008.
-Archives of Public Health 72, 41.
+policy analysis of {Canada}'s response to the {World Food Summit}
+1998\textendash 2008. Archives of Public Health 72, 41.
 doi:\href{https://doi.org/10.1186/2049-3258-72-41}{10.1186/2049-3258-72-41}
 
-\leavevmode\hypertarget{ref-maibachReframingClimateChange2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-maibachReframingClimateChange2010}{}}%
 Maibach, E.W., Nisbet, M., Baldwin, P., Akerlof, K., Diao, G., 2010.
@@
 
-\leavevmode\hypertarget{ref-mammenUnderstandingDriveEscort2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mammenUnderstandingDriveEscort2012}{}}%
 Mammen, G., Faulkner, G., Buliung, R., Lay, J., 2012. Understanding the
@@
 
-\leavevmode\hypertarget{ref-mammenSchoolTravelPlanning2014}{}%
-Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2014. School travel
-planning in Canada: Identifying child, family, and school-level
+\leavevmode\vadjust pre{\hypertarget{ref-mammenSchoolTravelPlanning2014}{}}%
+Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2014a. School travel
+planning in {Canada}: Identifying child, family, and school-level
 characteristics associated with travel mode shift from driving to active
-school travel. Journal of Transport \& Health, Walking \& Cycling: The
+school travel. Journal of Transport \& Health, Walking \& {Cycling}: The
 contributions of health and transport geography 1, 288--294.
@@
 
-\leavevmode\hypertarget{ref-mammenPuttingSchoolTravel2015}{}%
-Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2015. ''Putting
+\leavevmode\vadjust pre{\hypertarget{ref-mammenPuttingSchoolTravel2015}{}}%
+Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2015. ''{Putting}
 school travel on the map'': Facilitators and barriers to implementing
-school travel planning in Canada. Journal of Transport \& Health 2,
+school travel planning in {Canada}. Journal of Transport \& Health 2,
 318--326.
@@
 
-\leavevmode\hypertarget{ref-mammenActiveSchoolTravel2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mammenActiveSchoolTravel2014}{}}%
 Mammen, G., Stone, M.R., Faulkner, G., Ramanathan, S., Buliung, R.,
-O'Brien, C., Kennedy, J., 2014. Active school travel: An evaluation of
-the Canadian school travel planning intervention. Preventive Medicine
+O'Brien, C., Kennedy, J., 2014b. Active school travel: An evaluation of
+the {Canadian} school travel planning intervention. Preventive Medicine
 60, 55--59.
@@
 
-\leavevmode\hypertarget{ref-michailChildrenExperiencesTheir2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-michailChildrenExperiencesTheir2021}{}}%
 Michail, N., Ozbil, A., Parnell, R., Wilkie, S., 2021. Children's
-Experiences of Their Journey to School: Integrating Behaviour Change
-Frameworks to Inform the Role of the Built Environment in Active School
-Travel Promotion. International Journal of Environmental Research and
-Public Health 18, 4992.
+{Experiences} of {Their Journey} to {School}: Integrating {Behaviour
+Change Frameworks} to {Inform} the {Role} of the {Built Environment} in
+{Active School Travel Promotion}. International Journal of Environmental
+Research and Public Health 18, 4992.
 doi:\href{https://doi.org/10.3390/ijerph18094992}{10.3390/ijerph18094992}
 
-\leavevmode\hypertarget{ref-mitraIndependentMobilityMode2013}{}%
-Mitra, R., 2013. Independent Mobility and Mode Choice for School
-Transportation: A Review and Framework for Future Research. Transport
-Reviews 33, 21--43.
+\leavevmode\vadjust pre{\hypertarget{ref-mitraIndependentMobilityMode2013}{}}%
+Mitra, R., 2013. Independent {Mobility} and {Mode Choice} for {School
+Transportation}: A {Review} and {Framework} for {Future Research}.
+Transport Reviews 33, 21--43.
 doi:\href{https://doi.org/10.1080/01441647.2012.743490}{10.1080/01441647.2012.743490}
 
-\leavevmode\hypertarget{ref-panFramingAnalysisApproach1993}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-pdftools}{}}%
+Ooms, J., 2021. Pdftools: Text extraction, rendering and converting of
+PDF documents.
+
+\leavevmode\vadjust pre{\hypertarget{ref-paezEnjoyment2010}{}}%
+Paez, A., Whalen, K., 2010. Enjoyment of commute: A comparison of
+different transportation modes. Transportation Research Part a-Policy
+and Practice 44, 537--549.
+doi:\href{https://doi.org/10.1016/j.tra.2010.04.003}{10.1016/j.tra.2010.04.003}
+
+\leavevmode\vadjust pre{\hypertarget{ref-panFramingAnalysisApproach1993}{}}%
 Pan, Z., Kosicki, G.M., 1993. Framing analysis: An approach to news
@@
 
-\leavevmode\hypertarget{ref-panterAttitudesSocialSupport2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-panterAttitudesSocialSupport2010}{}}%
 Panter, J.R., Jones, A.P., Sluijs, E.M.F. van, Griffin, S.J., 2010.
@@
 
-\leavevmode\hypertarget{ref-pontEnvironmentalCorrelatesChildren2009}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggraph}{}}%
+Pedersen, T.L., 2021. Ggraph: An implementation of grammar of graphics
+for graphs and networks.
+
+\leavevmode\vadjust pre{\hypertarget{ref-pontEnvironmentalCorrelatesChildren2009}{}}%
 Pont, K., Ziviani, J., Wadley, D., Bennett, S., Abbott, R., 2009.
@@
 
-\leavevmode\hypertarget{ref-reynardGrowthResilienceHow2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-reynardGrowthResilienceHow2021}{}}%
 Reynard, D., Collins, D., Shirgaokar, M., 2021. Growth over resilience:
-How Canadian municipalities frame the challenge of reducing carbon
+How {Canadian} municipalities frame the challenge of reducing carbon
 emissions. Local Environment 0, 1--13.
@@
 
-\leavevmode\hypertarget{ref-riaziCorrelatesChildrenIndependent2019}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-riaziCorrelatesChildrenIndependent2019}{}}%
 Riazi, N.A., Blanchette, S., Trudeau, F., Larouche, R., Tremblay, M.S.,
-Faulkner, G., 2019. Correlates of Children's Independent Mobility in
-Canada: A Multi-Site Study. International Journal of Environmental
+Faulkner, G., 2019. Correlates of {Children}'s {Independent Mobility} in
+{Canada}: A {Multi}-{Site Study}. International Journal of Environmental
 Research and Public Health 16.
@@
 
-\leavevmode\hypertarget{ref-romeroChildrenExperiencesEnjoyment2015}{}%
-Romero, V., 2015. Children's experiences: Enjoyment and fun as
+\leavevmode\vadjust pre{\hypertarget{ref-R-widyr}{}}%
+Robinson, D., 2021. Widyr: Widen, process, then re-tidy data.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidytext}{}}%
+Robinson, D., Silge, J., 2021. Tidytext: Text mining using dplyr,
+ggplot2, and other tidy tools.
+
+\leavevmode\vadjust pre{\hypertarget{ref-romeroChildrenExperiencesEnjoyment2015}{}}%
+Romero, V., 2015. {Children}'s experiences: Enjoyment and fun as
 additional encouragement for walking to school. Journal of Transport \&
@@
 
-\leavevmode\hypertarget{ref-rothmanSchoolEnvironmentStudent2017}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rothmanSchoolEnvironmentStudent2017}{}}%
 Rothman, L., Buliung, R., Howard, A., Macarthur, C., Macpherson, A.,
@@
 
-\leavevmode\hypertarget{ref-rothmanAssociationsParentsPerception2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rothmanAssociationsParentsPerception2015}{}}%
 Rothman, L., Buliung, R., To, T., Macarthur, C., Macpherson, A., Howard,
@@
 
-\leavevmode\hypertarget{ref-rothmanActiveSchoolTransportation2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rothmanActiveSchoolTransportation2021}{}}%
 Rothman, L., Hagel, B., Howard, A., Cloutier, M.S., Macpherson, A.,
@@
 Ling, R., Zanotto, M., Rancourt, M., Winters, M., 2021. Active school
-transportation and the built environment across Canadian cities:
+transportation and the built environment across {Canadian} cities:
 Findings from the child active transportation safety and the environment
-(CHASE) study. Preventive Medicine 146, 106470.
+({CHASE}) study. Preventive Medicine 146, 106470.
 doi:\href{https://doi.org/10.1016/j.ypmed.2021.106470}{10.1016/j.ypmed.2021.106470}
 
-\leavevmode\hypertarget{ref-rothmanDeclineActiveSchool2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rothmanDeclineActiveSchool2018}{}}%
 Rothman, L., Macpherson, A.K., Ross, T., Buliung, R.N., 2018. The
-decline in active school transportation (AST): A systematic review of
-the factors related to AST and changes in school transport over time in
-North America. Preventive Medicine 111, 314--322.
+decline in active school transportation ({AST}): A systematic review of
+the factors related to {AST} and changes in school transport over time
+in {North America}. Preventive Medicine 111, 314--322.
 doi:\href{https://doi.org/10.1016/j.ypmed.2017.11.018}{10.1016/j.ypmed.2017.11.018}
 
-\leavevmode\hypertarget{ref-schoeppeAssociationsChildrenActive2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-schoeppeAssociationsChildrenActive2015}{}}%
 Schoeppe, S., Duncan, M.J., Badland, H.M., Oliver, M., Browne, M., 2015.
@@
 
-\leavevmode\hypertarget{ref-silgeTextMining2021}{}%
-Silge, J., Robinson, D., 2021. Text Mining with R.
-
-\leavevmode\hypertarget{ref-starkExploringIndependentActive2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-text2vec}{}}%
+Selivanov, D., Bickel, M., Wang, Q., 2020. text2vec: Modern text mining
+framework for r.
+
+\leavevmode\vadjust pre{\hypertarget{ref-silgeTextMining2021}{}}%
+Silge, J., Robinson, D., 2021. Text {Mining} with {R}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-starkExploringIndependentActive2018}{}}%
 Stark, J., Frühwirth, J., Aschauer, F., 2018. Exploring independent and
-active mobility in primary school children in Vienna. Journal of
+active mobility in primary school children in {Vienna}. Journal of
 Transport Geography 68, 31--41.
@@
 
-\leavevmode\hypertarget{ref-vandenbergFactorsAffectingParental2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-vandenbergFactorsAffectingParental2020}{}}%
 van den Berg, P., Waygood, E.O.D., van de Craats, I., Kemperman, A.,
 2020. Factors affecting parental safety perception, satisfaction with
-school travel and mood in primary school children in the Netherlands.
+school travel and mood in primary school children in the {Netherlands}.
 Journal of Transport \& Health 16, 100837.
@@
 
-\leavevmode\hypertarget{ref-vangoeverdenSchoolTravelBehaviour2013}{}%
-van Goeverden, C.D., de Boer, E., 2013. School travel behaviour in the
-Netherlands and Flanders. Transport Policy, ''Understanding behavioural
-change: An international perspective on sustainable travel behaviours
-and their motivations'': Selected Papers from the 12th World Conference
-on Transportation Research 26, 73--84.
-doi:\href{https://doi.org/10.1016/j.tranpol.2013.01.004}{10.1016/j.tranpol.2013.01.004}
-
-\leavevmode\hypertarget{ref-waygoodChildrenTravelIncidental2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-waygoodChildrenTravelIncidental2015}{}}%
 Waygood, E.O.D., Friman, M., 2015. Children's travel and incidental
@@
 
-\leavevmode\hypertarget{ref-waygoodTransportChildrenWellbeing2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-waygoodTransportChildrenWellbeing2020}{}}%
 Waygood, E.O.D., Friman, M., Olsson, L.E., Mitra, R. (Eds.), 2020.
-Transport and Children's Wellbeing, in: Transport and Children's
-Wellbeing. Elsevier, pp. i--ii.
+Transport and {Children}'s {Wellbeing}, in: Transport and {Children}'s
+{Wellbeing}. {Elsevier}, pp. i--ii.
 doi:\href{https://doi.org/10.1016/B978-0-12-814694-1.09993-0}{10.1016/B978-0-12-814694-1.09993-0}
 
-\leavevmode\hypertarget{ref-waygoodJapanMaintainingHigh2020}{}%
-Waygood, E.O.D., Taniguchi, A., 2020. Japan: Maintaining high levels of
-walking, in: Waygood, E.O.D., Friman, M., Olsson, L.E., Mitra, R.
-(Eds.), Transport and Children's Wellbeing. Elsevier, pp. 297--316.
-doi:\href{https://doi.org/10.1016/B978-0-12-814694-1.00016-6}{10.1016/B978-0-12-814694-1.00016-6}
-
-\leavevmode\hypertarget{ref-weathersDevelopmentsFramingClimate2016}{}%
-Weathers, M.R., Kendall, B.E., 2016. Developments in the Framing of
-Climate Change as a Public Health Issue in US Newspapers. Environmental
-Communication 10, 593--611.
+\leavevmode\vadjust pre{\hypertarget{ref-weathersDevelopmentsFramingClimate2016}{}}%
+Weathers, M.R., Kendall, B.E., 2016. Developments in the {Framing} of
+{Climate Change} as a {Public Health Issue} in {US Newspapers}.
+Environmental Communication 10, 593--611.
 doi:\href{https://doi.org/10.1080/17524032.2015.1050436}{10.1080/17524032.2015.1050436}
 
-\leavevmode\hypertarget{ref-westmanWhatDrivesThem2017}{}%
-Westman, J., Friman, M., Olsson, L.E., 2017. What Drives Them to
-Drive?Parents' Reasons for Choosing the Car to Take Their Children to
-School. Frontiers in Psychology 8.
+\leavevmode\vadjust pre{\hypertarget{ref-westmanWhatDrivesThem2017}{}}%
+Westman, J., Friman, M., Olsson, L.E., 2017a. What {Drives Them} to
+{Drive}?\textemdash{{Parents}}' {Reasons} for {Choosing} the {Car} to
+{Take Their Children} to {School}. Frontiers in Psychology 8.
 doi:\href{https://doi.org/10.3389/fpsyg.2017.01970}{10.3389/fpsyg.2017.01970}
 
-\leavevmode\hypertarget{ref-westmanChildrenTravelSchool2017}{}%
-Westman, J., Olsson, L.E., Gärling, T., Friman, M., 2017. Children's
+\leavevmode\vadjust pre{\hypertarget{ref-westmanChildrenTravelSchool2017}{}}%
+Westman, J., Olsson, L.E., Gärling, T., Friman, M., 2017b. Children's
 travel to school: Satisfaction, current mood, and cognitive performance.
@@
 
-\leavevmode\hypertarget{ref-wilsonUnderstandingChildParent2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
+Wickham, H., 2019. Stringr: Simple, consistent wrappers for common
+string operations.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-reshape2}{}}%
+Wickham, H., 2020. reshape2: Flexibly reshape data: A reboot of the
+reshape package.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
+Wickham, H., 2021. Tidyr: Tidy messy data.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
+Wickham, H., Chang, W., Henry, L., Pedersen, T.L., Takahashi, K., Wilke,
+C., Woo, K., Yutani, H., Dunnington, D., 2021a. ggplot2: Create elegant
+data visualisations using the grammar of graphics.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
+Wickham, H., François, R., Henry, L., Müller, K., 2021b. Dplyr: A
+grammar of data manipulation.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
+Wickham, H., Hester, J., Bryan, J., 2021c. Readr: Read rectangular text
+data.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-word2vec}{}}%
+Wijffels, J., 2021. word2vec: Distributed representations of words.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wilsonUnderstandingChildParent2018}{}}%
 Wilson, K., Clark, A.F., Gilliland, J.A., 2018. Understanding child and
@@
 
-\leavevmode\hypertarget{ref-zwertsHowChildrenView2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-zwertsHowChildrenView2010}{}}%
 Zwerts, E., Allaert, G., Janssens, D., Wets, G., Witlox, F., 2010. How
-children view their travel behaviour: A case study from Flanders
-(Belgium). Journal of Transport Geography 18, 702--710.
+children view their travel behaviour: A case study from {Flanders}
+({Belgium}). Journal of Transport Geography 18, 702--710.
 doi:\href{https://doi.org/10.1016/j.jtrangeo.2009.10.002}{10.1016/j.jtrangeo.2009.10.002}
 
+\end{CSLReferences}
+
 \end{document}

### 2022-04-22 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Revised version of paper

@@
 ---
-title: The framing of active school travel in Ontario, Canada, as a health and built environment issue
+title: How is active school travel framed in Ontario, Canada?
 author:
@@
 abstract: |
-  This is the abstract.
-
-  It consists of two paragraphs.
+
+  Active school travel (AST) has been increasingly encouraged by various stakeholders in Ontario, Canada through efforts such as school travel planning.
+Education strategies like workshops or resources that promote AST are commonly implemented.
+The framing of AST through such strategies may influence how walking and bicycling to school are perceived by parents.
+It may also draw attention to AST as an issue affecting children's health which could motivate behaviour change.
+We used natural language processing, including topic modelling, to examine how AST is framed in publicly available documents from Ontario stakeholders involved in school travel planning.
+We then compared the findings from these documents to a selection of studies on AST and explored similarities between the two.
+We found that AST is framed in two ways: i) as a health and environmental issue; and ii) as an accessible and feasible transport option for children and parents.
+The frames encourage children and parents to adopt AST given its health and environmental benefits by providing resources to support behaviour change.
+The benefits of AST and strategies to support AST that are communicated by stakeholders are consistent with the evidence from academic research.
+While these frames present AST in a positive light, they may not encourage parents to view current household travel behaviours as unhealthy for their children or their community.
+Stakeholders promoting AST in Ontario should further problematize the decline of AST and challenge the norm of driving children to school.
+
+  Keywords: active school travel, school travel planning; natural language processing; framing analysis; education strategies
 
@@
 
-  ***Background***:  
-  ***Methods***:  
-  ***Results***: 
-  ***Conclusions***:
-
 \newpage
@@
 However, the appetite for AST may be high in many Canadian communities.
-For instance, in a study conducted in Toronto, Ontario, 40% of children who are driven to school would like to travel by bicycle instead [@laroucheRatherBikeSchool2016].
+For instance, in a study conducted in Toronto, Ontario, 40% of children who were driven to school stated they would like to travel by bicycle instead [@laroucheRatherBikeSchool2016].
 The study also reported that less than 3% of respondents actually cycled, despite the vast majority having access to a bicycle and living within a short and bikeable distance to school.
@@
 In this context, STP is a popular "school-specific" intervention led by a facilitator who brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014].
-The five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities following the 4E's that make AST safer and more convenient: 1) setup of the program; 2) data collection and problem identification; 3) action planning; 4) implementation; 5) monitoring and evaluation [@buliungSchoolTravelPlanning2011; @langUnderstandingModalChoice2011].
+The five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities that make AST safer and more convenient: 1) setup of the program; 2) data collection and problem identification; 3) action planning; 4) implementation; 5) monitoring and evaluation [@buliungSchoolTravelPlanning2011; @langUnderstandingModalChoice2011].
 
@@
 Being driven to school reduces community interactions for children, which may negatively impact their social wellbeing [@waygoodChildrenTravelIncidental2015].
-In contrast, walking and cycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021].
-This is something that children seem to value [@zwertsHowChildrenView2010] and that tracks with findings among university students [@paezEnjoyment2010].
+In contrast, walking and bicycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021] and increase positive emotions that contribute to wellbeing [@ramanathanHappinessMotionEmotions2014a].
+This is something that children seem to value [@zwertsHowChildrenView2010] and that tracks with findings among university students [@paezEnjoymentCommuteComparison2010].
 More generally, social connections through travel appear to be important for wellbeing.
@@
 Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behaviour is understood within the context of household, social, neighbourhood, and policy environments.
-The SEM comes from the field of public health and is a useful framework for understanding complex health behaviours, such as walking and cycling habits, This model helps to identify multiple determinants that need to be addressed by interventions to facilitate behaviour change.
+The SEM comes from the field of public health and is a useful framework for understanding complex health behaviours, such as walking and bicycling habits, This model helps to identify multiple determinants that need to be addressed by interventions to facilitate behaviour change.
 The consensus in the literature is that interventions should target multiple levels in order to increase levels of healthy and physically active modes of travel to school [@mitraIndependentMobilityMode2013].
@@
 There is evidence that gender is a determinant of AST, and that boys are more likely to travel using active modes than girls, although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
-Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], as well as the frequency of parental support [@mahDoesParentalSupport2017a].
+Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], as well as daily parental support [@mahDoesParentalSupport2017a].
 This indicates that shifting parental perceptions and habits is important.
@@
 
-Distance between home and school is most strongly associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school - low density suburban development tends to increase the need for movement, and the reliance on motorized modes [@farberRunning2011].
+Distance between home and school is most negatively associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school - low density suburban development tends to increase the need for movement, and the reliance on motorized modes [@farberRunning2011].
 Many studies have also found that the quality of the built environment along the route to school and around the school site [@ikedaAssociationsChildrenActive2018; @rothmanActiveSchoolTransportation2021] and provision of active travel infrastructure [@chenPromotingActiveStudent2018; @pontEnvironmentalCorrelatesChildren2009] facilitate AST.
@@
 School travel planning (STP) has been implemented in Canada since at least the late 2000s.
-Within the STP process, facilitators generally establish multi-sector committees who intervene at the participating school through a range of activities related to the 4E's consisting of _education_ strategies, _encouragement_ through in-person events or programs, _engineering_ improvements to or around the school site, and _enforcement_ of traffic speeds around schools [@langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
+Within the STP process, facilitators generally establish multi-sector committees which intervene at the participating school through a range of activities related to the 4E's consisting of _education_ strategies, _encouragement_ through in-person events or programs, _engineering_ improvements to or around the school site, and _enforcement_ of traffic speeds around schools [@langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
 The first large-scale evaluation of STP as an intervention in Canada took place at twelve schools across the country, including four in Ontario, using parental surveys to measure changes in travel behaviour and perceptions [@buliungSchoolTravelPlanning2011].
+Following the intervention, active travel rates increased across all schools and 14% of parents reported a perceived reduction in traffic outside the school [@buliungSchoolTravelPlanning2011].
 Assessments of the efficacy of STP [@buttazzoniPromotingActiveSchool2019; @mammenActiveSchoolTravel2014] indicate that it has the potential to encourage behaviour change and adoption of AST.
@@
 
-How AST is framed seems particularly important to shift parental attitudes and perceptions given their reported influence on children's travel mode to school.
+How AST is framed seems particularly important to shift parental attitudes and perceptions, given their reported influence on children's travel mode to school.
 STP activities heavily focus on education or encouragement [@buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014; @buttazzoniSupportingActiveSchool2018], but parents may not always be receptive to the goals of STP and may be resistant to behaviour change [@buttazzoniSupportingActiveSchool2018].
@@
 Municipal representatives are perceived to be instrumental but the involvement of other stakeholder groups (e.g., busing consortia representatives and local residents) can be lacking [@buttazzoniSupportingActiveSchool2018].
-In Ontario, it is reasonable to say that AST has become a policy issue on the education and public health agendas, supported, albeit in a modest way, by financial contributions from the provincial government^[To put the CAD 2 million invested by the province in the Ontario Active School Travel program, a city such as Hamilton budgeted in excess of CAD 91 million on road maintenance and construction in 2016 alone; see: https://www.hamilton.ca/budget-finance/city-budgets/2016-tax-and-rate-budgets].
+In Ontario, it is reasonable to say that AST has become a policy issue on the education and public health agendas, supported, albeit in a modest way, by financial contributions from the provincial government^[To put the CAD 2 million invested by the province in the Ontario Active School Travel program in perspective, a city such as Hamilton budgeted in excess of CAD 91 million on road maintenance and construction in 2016 alone; see: https://www.hamilton.ca/budget-finance/city-budgets/2016-tax-and-rate-budgets].
 Still, the support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
@@
 This information should reflect current knowledge from research on school travel, plus content specific to local factors that influence AST, so that the challenges of AST are adequately defined and the opportunities or solutions to address the problems are clear.
+
+## 2.4. Framing Analysis
+
+Issues that pertain to public health or wellbeing are often presented to the public through particular frames to influence perceptions or behaviours.
+As previously mentioned, a frame is a "central organizing idea or story line that provides meaning" to a public issue or phenomenon [@gamsonChangingCulture1987].
+Scholars in the field of political communications have proposed that communicators, such as the media or institutions, construct the narrative of a frame for policy positions or public issues in order to activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
+Organized groups of stakeholders can employ similar methods to attract attention to particular issues.
+Framing can be used to position existing solutions as suitable to address particular issues [@mahFramecriticalPolicyAnalysis2014], which may prevent the public from being aware of other policy approaches that challenge the status quo.
+The way policy issues are framed is ultimately important to understand because it plays a role in either altering or preserving the existing social perceptions.
+Finally, the ideas that are communicated by a particular frame can be either positive or negative [@waygoodCO2ValenceFraming2018].
+There is evidence that negative framing may be more effective at motivating individuals to change transport modes to reduce CO2 emissions [@waygoodCO2ValenceFraming2018].
+
+Framing of issues is an important step in developing health policy.
+An obvious example over the past decade is the framing of climate change as a public health issue [e.g., @depouxCommunicatingClimateChange2017; @maibachReframingClimateChange2010; @weathersDevelopmentsFramingClimate2016] to increase public engagement and awareness of the issue.
+This framing has slowly advanced this issue on public policy agendas as public attention puts pressure on the policy stream to adopt frameworks for action.
+For example, transport planners use different frames to guide the extent to which transport policies can be adapted to address climate change.
+In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review the representation of issues such as mobility and social exclusion in municipal policies from four western Canadian cities under the current circumstances of climate change.
+The authors found four primary frames: “The Growing City”, “If You Build It, They Will Come”, “Better City for All”, and a “the Resilient City” [@reynardGrowthResilienceHow2021].
+Each frame presented the nature, opportunities, and challenges of climate change in different ways which set the stage for the types of mitigation and adaptation strategies that cities were proposing to address this issue.
+
+In a similar way, we hypothesize that STP stakeholder groups in Ontario have framed AST in particular ways to engage multiple audiences on this policy issue including parents, local residents, school representatives, and municipal representatives.
+These groups are likely identifying points of intervention and potential opportunities to build support for and encourage AST.
 
@@
 
-The initial corpus of documents from STP stakeholder groups included 69 relevant webpages (i.e., one page or more) from all STP stakeholder groups.
+The initial corpus of documents from STP stakeholder groups included 69 relevant webpages (i.e., one page or more).
 We refer to these as policy documents throughout the paper.
@@
 
-We also manually removed any extraneous material in the academic papers that did not pertain to AST specifically.
-This included footnotes, references, acknowledgments, and conflict of interest statements in the academic papers.
-We removed all phone numbers, inserted links to other webpages, personal names, and content not specific to AST from the policy documents that were retrieved from the websites of school boards, municipalities, and transportation consortia.
-
+We also manually removed any extraneous material that did not pertain to AST specifically.
+For the academic papers, this included footnotes, references, acknowledgments, and conflict of interest statements.
+For the policy+practice documents, it included phone numbers, inserted links to other webpages, personal names, and content not specific to AST.
 In the final step, we removed all blank spaces, punctuation, capitalization, and numbers.
-English stop words, which are common words such as _and_ or _the_ as identified in a predetermined list by Lewis et al.
-[@R-tm] and other frequent terms in the documents like "school" and specific location names, were removed from the corpora.
+English stop words, which are common words such as _and_ or _the_ as identified in a predetermined list by Feinerer and Hornik [-@R-tm] and other frequent terms in the documents like "school" and specific location names, were removed from the corpora.
 
@@
 
-## 4.1. Framing analysis
-
-Issues that pertain to public health or wellbeing are often presented to the public through particular frames to influence perceptions or behaviours.
-As previously mentioned, a frame is a "central organizing idea or story line that provides meaning" to a public issue or phenomenon [@gamsonChangingCulture1987].
-Scholars in the field of political communications have proposed that communicators, such as the media or institutions, construct the narrative of a frame for policy positions or public issues in order to activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
-Organized groups of stakeholders can employ similar methods to attract attention to particular issues.
-Framing can be used to position existing solutions as suitable to address particular issues [@mahFramecriticalPolicyAnalysis2014], which may prevent the public from being aware of other policy approaches that challenge the status quo.
-The way policy issues are framed is ultimately important to understand because it plays a role in either altering or preserving the existing social perceptions.
-Finally, the ideas that are communicated by a particular frame can be either positive or negative [@waygoodCO2ValenceFraming2018].
-There is evidence that negative framing may be more effective at motivating individuals to change transport modes to reduce CO2 emissions [@waygoodCO2ValenceFraming2018].
-
-Framing of issues is an important step in developing health policy.
-An obvious example over the past decade is the framing of climate change as a public health issue [e.g., @depouxCommunicatingClimateChange2017; @maibachReframingClimateChange2010; @weathersDevelopmentsFramingClimate2016] to increase public engagement and awareness of the issue.
-This framing has slowly advanced this issue on public policy agendas as public attention puts pressure on the policy stream to adopt frameworks for action.
-For example, transport planners use different frames to guide the extent to which transport policies can be adapted to address climate change.
-In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review the representation of issues such as mobility and social exclusion in municipal policies from four western Canadian cities under the current circumstances of climate change.
-The authors found four primary frames: “The Growing City”, “If You Build It, They Will Come”, “Better City for All”, and a “the Resilient City” [@reynardGrowthResilienceHow2021].
-Each frame presented the nature, opportunities, and challenges of climate change in different ways which set the stage for the types of mitigation and adaptation strategies that cities were proposing to address this issue.
-
-In a similar way, we hypothesize that STP stakeholder groups in Ontario have framed AST in particular ways to engage multiple audiences on this policy issue including parents, local residents, school representatives, and municipal representatives.
-These groups are likely identifying points of intervention and potential opportunities to build support for and encourage AST.
-
-## 4.2. Process
+## 4.1. Process of Framing Analysis
 
@@
 Researchers must then interpret the identified topics, as done after other methods of manual coding.
-We also compare the topics between the policy documents and the academic papers, and use our interpretation to answer our research question.
+We also compare the topics between the policy documents and the academic papers to interpret what is being communicated by STP stakeholders.
 We describe in more detail the functions and code in `R`  that we used.
@@
 This paper is an example of open and reproducible research that uses only open software.
-All data are organized in the form of an open data product [@arribasOpen2021].
-Following best practices in spatial data science [@brunsdon2020opening], the code and data needed to reproduce our research or conduct a similar analysis for other regions are available for download.
+Following best practices in spatial data science [@brunsdon2020opening], the code and data needed to reproduce our research or conduct a similar analysis for other regions are available for download upon request.
 
@@
 Policy documents and academic papers reference _active_, _travel_, _walking_, _biking_ or _cycling_, and _students_ more than other terms.
-Each corpus also has _safety_ and _traffic_ as common words which suggests that such concerns are a common reason given for parents driving their children to school.
+Each corpus also has _safety_ and _traffic_ as common words which suggests that these are common concerns for parents.
 The word _physical_ is present in each corpus, but it's not clear what this refers to (e.g, _physical activity_, _physical health_, or the _physical environment_).
@@
       align = c("l", "c", "c", "l", "c", "c", "l", "c", "c", "l", "c", "c"), 
-      caption = "\\label{tab:word-table}Top 25 terms identified in each corpora. Document frequencies are also indicated.") %>%
+      caption = "\\label{tab:word-table}Top 25 terms identified in each corpus. Document frequencies are also indicated.") %>%
   kable_styling(latex_options = c("striped", "scale_down")) %>%
@@
 _Green Communities Canada_ is a non-profit organization that has significantly supported AST initiatives through the Ontario Active School Travel program so the high frequency of this term in the policy+practice corpus is not surprising.
-Overall, the policy documents from STP stakeholder groups seem to focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or considerations; and iv) supports for AST.
+Overall, the policy documents from STP stakeholder groups seem to focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or barriers; and iv) supports for AST.
 This interpretation indicates that the general public accessing information about AST in Ontario is informed about a wide range of content related to this issue.
@@
 Many papers also investigate gender differences in AST given that _boys girls_ (n = 211) is another common bigram.
-Finally, the presence of _statistically significant_ among the top bigrams underscores that researchers often aim to identify associations using statistical measures.
-We found that the academic corpus focuses on a greater range of topics than found in the policy documents.
+Finally, the presence of _statistically significant_ among the top bigrams indicates that researchers often aim to identify associations using statistical measures.
+We found that the academic corpus focuses on a greater range of topics than found in the policy+practice documents.
 
@@
     "Active and Sustainable School Travel (ASST) not only improves physical and mental health but contributes to a healthier environment and safer streets.",
-    "Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.")
+    "Encouraging Active Transportation promotes physical health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.")
 )
@@
 
-# The graphs suggest that there are 4 topics for the municipal corpora
-# The graphs suggest that there are 4 topics for the school corpora
-# The graphs suggest that there are 4 topics for the municipal corpora
-# The graphs suggest that there are 5 topics for the policy corpora
-# The graphs suggest that there are 17 topics for the academic corpora
+# The graphs suggest that there are 7-10 topics for the municipal corpora
+# The graphs suggest that there are 7-10 topics for the school corpora
+# The graphs suggest that there are 8-10 topics for the consortia corpora
+# The graphs suggest that there are 9-13 topics for the policy corpora
+# The graphs suggest that there are 17-21 topics for the academic corpora
 ```
@@
 
-policy_lda <- LDA(policy_dtm, k = 7, method = "Gibbs", control = NULL, model = NULL)
+policy_lda <- LDA(policy_dtm, k = 9, method = "Gibbs", control = NULL, model = NULL)
 
@@
 
-```{r policy-terms, echo=FALSE, out.width="1\\linewidth", fig.cap="\\label{fig:policy-terms}Topics identified in the policy corpus according to clusters of words."}
+```{r policy-terms, echo=FALSE, out.width="1\\linewidth", fig.cap="\\label{fig:policy-terms}Topics identified in the policy+practice corpus according to clusters of words.
+The per-word-per-topic probabilities are shown by beta."}
 policy_top_terms <- policy_topics %>%
@@
 
-```{r academic-terms, echo=FALSE, out.width="1\\linewidth", cache=TRUE, fig.cap="\\label{fig:academic-terms}Topics identified in the academic corpus according to clusters of words."}
+```{r academic-terms, echo=FALSE, out.width="1\\linewidth", cache=TRUE, fig.cap="\\label{fig:academic-terms}Topics identified in the academic corpus according to clusters of words.
+The per-word-per-topic probabilities are shown by beta."}
 
@@
 For the final part of our analysis, we conducted topic modelling to examine the different topics found in the policy and academic corpora.
-We focused on the policy+practice corpus, instead of assessing the municipal, school, and consortia documents separately, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario.
-We then estimated Latent Dirillecth Allocation (LDA) models for each corpus.
-Parameter tuning suggests that the policy+practice corpus has between 7 and 9 topics and the academic corpus has between 17 and 25 topics.
+We focused on the policy/practice corpus, instead of assessing the municipal, school, and consortia documents separately, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario.
+We then estimated Latent Dirichlet Allocation (LDA) models for each corpus.
+Parameter tuning suggests that the policy+practice corpus has between 9 and 13 topics and the academic corpus has between 17 and 25 topics.
 After running the LDA model for the academic corpus, we realized the difficulty of interpreting a minimum of 17 topics based on the clusters of words that were identified.
-We experimented with the model by adjusting and evaluating the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap for the clusters to be meaningfully interpreted.
+We experimented with the model by adjusting the number of topics and evaluating the output of terms in each topic.
+We found that there were 9 distinct topics that could be interpreted in the policy corpus and 11 topics in the academic corpus, after which there was too much overlap for the clusters to be meaningfully interpreted.
 Figures \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main terms that are associated with the topics found in each corpus.
 
-In the policy+practice corpus, we identified the following topics based on the cluster of words: (1) resources for walking; (2) walking; (3) support for active travel; (4) bicycling and the environment; (5) benefits of active travel; (6) safety; and (7) busing information and eligibility.
+In the policy+practice corpus, we identified the following topics based on the cluster of words: (1) safety; (2) weather and busing; (3) active travel planning; (4) walking; (5) resources for walking; (6) bicycling; (7) active travel concerns; (8) benefits of active travel; and (9) busing logistics.
 These topics indicate that STP stakeholder groups are sending the message that walking and bicycling to school are healthy travel modes for students, particularly in terms of physical activity.
-We also found that information is shared to support parents and students in using active modes to school, for example regarding the availability of cycling lanes and tips for route choice for walking.
+We also found that information is shared to support parents and students in using active modes to school, for example regarding the availability of bicycling lanes and tips for route choice for walking.
 
 The academic corpus has a higher number of topics likely due to the volume of papers included.
-The following topics were identified based on the clusters of words: (1) built environment (2) walking distance; (3) AST interventions; (4) parental barriers to walking; (5) behaviours and attitudes; (6) bicycling; (7) social environment; (8) children's independent mobility; (9) modeling trip choice; (10) adolescents and physical activity; and (11) safe routes to school programs.
-This corpus reflects a broader range of topics than the policy+practice corpus.
+The following topics were identified based on the clusters of words: (1) physical activity; (2) safe routes to school for active travel; (3) behaviours and attitudes; (4) bicycling; (5) walking; (6) built environment; (7) trip choice; (8) active school travel interventions; (9) parents; (10) children's independent mobility; and (11) public health and policies.
+This corpus reflects a broader range of topics than the policy/practice corpus.
 
@@
 The secondary frame in policy documents is that AST is accessible and feasible for children and parents.
-The documents indicate that there is an opportunity for or prospect of behaviour change.
+Despite the emphasis on the logistics of busing in the topic modelling, the documents indicate that there is an opportunity for or prospect of behaviour change.
 Some cities and schools explain how children and parents can leave the car at home and make the journey to school on foot or by bike.
@@
 
-> Help your students get started on the right foot - encourage them to walk or bike to school when possible.
+> _Help your students get started on the right foot - encourage them to walk or bike to school when possible.
 Even leaving the car a block or two and walking the rest of the way helps.
@@
 We found that AST is primarily framed to parents as beneficial to the health and wellbeing of children and to environmental sustainability.
-The policy documents reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance are less well-supported in the extant literature [@westmanChapterThreeTravel2020].
+The policy documents reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance are less well-supported in the extant literature [@westmanTravelChildWellbeing2020].
 STP stakeholder groups also communicate that increasing AST may reduce traffic near and around schools.
@@
 The recognition of engineering changes may reflect the strong engagement of the "policy stream" [@kingdonAgendasAlternativesPublic1984] since engineering staff and municipal representatives are common STP stakeholders in Canada [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015], as well as the evidence that the built environment influences mode choice to school.
-Although it is beyond the scope of this paper to assess whether the proposed solutions are perceived to be sufficient by parents for increasing AST.
+However, it is beyond the scope of this paper to assess whether the proposed solutions are perceived to be sufficient by parents for increasing AST.
 
@@
 A study investigating the influence of different valence framings of CO2 emissions on transport mode shift found that positive framing can be less effective than negative framing [@waygoodCO2ValenceFraming2018].
+A negative framing that challenges the social norm of driving could be more motivational to shift modes, which would be consistent with other findings [see @waygoodCO2ValenceFraming2018].
 Policy documents should make it clear that continued use of nonactive modes to school can deprive children of opportunities to increase physical activity and to gain health and social benefits.
@@
 The desire to escort children to school, which has been noted by parents as a reason to continue driving [@westmanWhatDrivesThem2017], is also not adequately addressed by STP stakeholders.
-Parental assessment of a child's ability to handle the journey to school was likewise overlooked despite its role in decision making for mode choice to school [@faulknerWhatQuickestEasiest2010].
-Framing AST as a developmental opportunity or a rite of passage that children have been denied could challenge the prevailing culture of risk which discourages parents from letting their children use active modes to school.
-In communities with low AST uptake, STP stakeholders may wish to emphasize the negative effects of parents continuing to drive children to and from school.
-A negative framing that challenges the social norm of driving could be more motivational to shift modes, which would be consistent with other findings [@waygoodCO2ValenceFraming2018].
+Parental assessment of a child's ability to undertake the journey to school was likewise overlooked despite its role in decision making for mode choice to school [@faulknerWhatQuickestEasiest2010].
+Framing AST as a developmental opportunity or a rite of passage that children have been denied could challenge the prevailing culture of risk avoidance which discourages parents from letting their children use active modes to school.
 
@@
 If Canadian STP stakeholders wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different materials that communicate why this issue is important to the general public, regardless of whether they currently have children commuting to/from school.
-The "political stream" could also be further engaged by working with advocacy groups who could attract more support from a broader coalition of individuals.
-
-We also contend that the ways in which the AST issue is framed can affect the policy process, as outlined in Kingdon's [-@kingdonAgendasAlternativesPublic1984] Multiple Streams Framework (MSF), through all three streams (i.e., problem, policy, and politics).
-This framing can ultimately impact the timing and success of a "window of opportunity" to enact policy changes that address the decline of AST in Canada.
 
@@
 
-A limitation of this study is that we only analyzed texts that were easily accessible to the general public on the websites of STP stakeholders in Ontario.
-Parents likely receive information about AST directly from schools, which may contain more content that reflects the local barriers to AST.
+A limitation of this study is that we only analyzed English-language texts that were easily accessible to the general public on the websites of STP stakeholders in Ontario.
+We did not include French-language materials from Ontario's 12 French school boards (a mixture of public and Catholic schools).
+Parents likely receive information about AST directly from schools, which may contain more content that reflects the local barriers to AST, but these materials were not used in our analysis.
 
@@
 However, AST may not be framed sufficiently as a "problem" that requires urgent intervention, which may impact how parents respond to behaviour change initiatives and limit awareness in the general public.
-In their public materials about AST, STP stakeholders emphasize why AST rates should increase in local communities and how the negative effects of nonactive modes to school may impact children's health and wellbeing.
+In their public materials about AST, STP stakeholders should emphasize why AST rates should increase in local communities and how the negative effects of nonactive modes to school may impact children's health and wellbeing.
 

### 2022-04-22 AST-Framing-Ontario/AST-Framing-Ontario.tex
Revised version of paper

@@
             pdfauthor={},
-            pdftitle={The framing of active school travel in Ontario, Canada, as a health and built environment issue},
+            pdftitle={How is active school travel framed in Ontario, Canada?},
             colorlinks=false,
@@
 
-  \title{The framing of active school travel in Ontario, Canada, as a
-health and built environment issue}
+  \title{How is active school travel framed in Ontario, Canada?}
     \author[Some Department]{Author 1\corref{1}}
@@
   \begin{abstract}
-  This is the abstract.
-
-  It consists of two paragraphs.
+  Active school travel (AST) has been increasingly encouraged by various
+  stakeholders in Ontario, Canada through efforts such as school travel
+  planning. Education strategies like workshops or resources that
+  promote AST are commonly implemented. The framing of AST through such
+  strategies may influence how walking and bicycling to school are
+  perceived by parents. It may also draw attention to AST as an issue
+  affecting children's health which could motivate behaviour change. We
+  used natural language processing, including topic modelling, to
+  examine how AST is framed in publicly available documents from Ontario
+  stakeholders involved in school travel planning. We then compared the
+  findings from these documents to a selection of studies on AST and
+  explored similarities between the two. We found that AST is framed in
+  two ways: i) as a health and environmental issue; and ii) as an
+  accessible and feasible transport option for children and parents. The
+  frames encourage children and parents to adopt AST given its health
+  and environmental benefits by providing resources to support behaviour
+  change. The benefits of AST and strategies to support AST that are
+  communicated by stakeholders are consistent with the evidence from
+  academic research. While these frames present AST in a positive light,
+  they may not encourage parents to view current household travel
+  behaviours as unhealthy for their children or their community.
+  Stakeholders promoting AST in Ontario should further problematize the
+  decline of AST and challenge the norm of driving children to school.
+
+  Keywords: active school travel, school travel planning; natural
+  language processing; framing analysis; education strategies
   \end{abstract}
@@
  \end{frontmatter}
-
-\textbf{\emph{Background}}:\\
-\textbf{\emph{Methods}}:\\
-\textbf{\emph{Results}}: \textbf{\emph{Conclusions}}:
 
@@
 high in many Canadian communities. For instance, in a study conducted in
-Toronto, Ontario, 40\% of children who are driven to school would like
-to travel by bicycle instead (Larouche et al., 2016). The study also
-reported that less than 3\% of respondents actually cycled, despite the
-vast majority having access to a bicycle and living within a short and
-bikeable distance to school. Another study based in London, Ontario,
-reported similar findings with respect to children's preference for
-active travel (Larsen et al., 2012). From a public health perspective,
-increasing the use of active modes to school represents a major
-opportunity to improve children's health and wellbeing.
+Toronto, Ontario, 40\% of children who were driven to school stated they
+would like to travel by bicycle instead (Larouche et al., 2016). The
+study also reported that less than 3\% of respondents actually cycled,
+despite the vast majority having access to a bicycle and living within a
+short and bikeable distance to school. Another study based in London,
+Ontario, reported similar findings with respect to children's preference
+for active travel (Larsen et al., 2012). From a public health
+perspective, increasing the use of active modes to school represents a
+major opportunity to improve children's health and wellbeing.
 
@@
 develop AST initiatives. Green Communities Canada runs the program,
-called \emph{Ontario Active School Travel} (Canada, 2020a). As of
+called \emph{Ontario Active School Travel} (G. C. Canada, 2020). As of
 December 2021, OAST has awarded over CAD 2 million and provided
@@
 activities like walking school buses and developed resources for schools
-and parents, among other actions (see Canada, 2020b). In this context,
+and parents, among other actions (see Canada, 2021). In this context,
 STP is a popular ``school-specific'' intervention led by a facilitator
@@
 five-step process involves identifying barriers to AST based on the
-local context and implementing approaches or activities following the
-4E's that make AST safer and more convenient: 1) setup of the program;
-2) data collection and problem identification; 3) action planning; 4)
-implementation; 5) monitoring and evaluation (Buliung et al., 2011; Lang
-et al., 2011).
+local context and implementing approaches or activities that make AST
+safer and more convenient: 1) setup of the program; 2) data collection
+and problem identification; 3) action planning; 4) implementation; 5)
+monitoring and evaluation (Buliung et al., 2011; Lang et al., 2011).
 
@@
 interactions for children, which may negatively impact their social
-wellbeing (Waygood and Friman, 2015). In contrast, walking and cycling
+wellbeing (Waygood and Friman, 2015). In contrast, walking and bicycling
 give children opportunities to socialize with friends or siblings
-(Michail et al., 2021). This is something that children seem to value
-(Zwerts et al., 2010) and that tracks with findings among university
-students (Paez and Whalen, 2010). More generally, social connections
-through travel appear to be important for wellbeing. Furthermore, AST
-can provide opportunities for children to engage with natural
-environments (Fusco et al., 2012; Romero, 2015).
+(Michail et al., 2021) and increase positive emotions that contribute to
+wellbeing (Ramanathan et al., 2014). This is something that children
+seem to value (Zwerts et al., 2010) and that tracks with findings among
+university students (Páez and Whalen, 2010). More generally, social
+connections through travel appear to be important for wellbeing.
+Furthermore, AST can provide opportunities for children to engage with
+natural environments (Fusco et al., 2012; Romero, 2015).
 
@@
 The SEM comes from the field of public health and is a useful framework
-for understanding complex health behaviours, such as walking and cycling
-habits, This model helps to identify multiple determinants that need to
-be addressed by interventions to facilitate behaviour change. The
-consensus in the literature is that interventions should target multiple
-levels in order to increase levels of healthy and physically active
-modes of travel to school (Mitra, 2013). Rather than describing an
-extensive list of factors that influence AST and mode choice in Canada
-(e.g., Mammen et al., 2012; Mitra, 2013; Rothman et al., 2018; Wilson et
-al., 2018), we discuss a few potentially modifiable determinants that
-may be targeted for change through STP.
+for understanding complex health behaviours, such as walking and
+bicycling habits, This model helps to identify multiple determinants
+that need to be addressed by interventions to facilitate behaviour
+change. The consensus in the literature is that interventions should
+target multiple levels in order to increase levels of healthy and
+physically active modes of travel to school (Mitra, 2013). Rather than
+describing an extensive list of factors that influence AST and mode
+choice in Canada (e.g., Mammen et al., 2012; Mitra, 2013; Rothman et
+al., 2018; Wilson et al., 2018), we discuss a few potentially modifiable
+determinants that may be targeted for change through STP.
 
@@
 parents' travel behaviours and the complexity of their household's
-travel needs (Buliung et al., 2021), as well as the frequency of
-parental support (\textbf{mahDoesParentalSupport2017a?}). This indicates
-that shifting parental perceptions and habits is important. Convenience
-and inclement weather have been cited by parents as barriers to AST
-(Buliung et al., 2011). Parental perceptions of the built or school
-environment (De Meester et al., 2014; Panter et al., 2010) and their
-children's skills (Mammen et al., 2012;
-\textbf{faulknerWhatQuickestEasiest2010?}) also influence mode choice to
-school.
-
-Distance between home and school is most strongly associated with AST
+travel needs (Buliung et al., 2021), as well as daily parental support
+(Mah et al., 2017). This indicates that shifting parental perceptions
+and habits is important. Convenience and inclement weather have been
+cited by parents as barriers to AST (Buliung et al., 2011). Parental
+perceptions of the built or school environment (De Meester et al., 2014;
+Panter et al., 2010) and their children's skills (Faulkner et al., 2010;
+Mammen et al., 2012) also influence mode choice to school.
+
+Distance between home and school is most negatively associated with AST
 (Ikeda et al., 2018; Mammen et al., 2012; Pont et al., 2009; Rothman et
@@
 Canadian youth report that they feel most safe bicycling on streets in
-their neighbourhood or that have low volumes of traffic
-(\textbf{TACbikeinfra2020?}). Finally, concerns about traffic and
-strangers have been reported by parents who drive their children to
-school (Mammen et al., 2012), which highlights that the volume and speed
-of cars can be a concern or deterrent for AST.
+their neighbourhood or that have low volumes of traffic (T. A. of
+Canada, 2020). Finally, concerns about traffic and strangers have been
+reported by parents who drive their children to school (Mammen et al.,
+2012), which highlights that the volume and speed of cars can be a
+concern or deterrent for AST.
 
@@
 least the late 2000s. Within the STP process, facilitators generally
-establish multi-sector committees who intervene at the participating
+establish multi-sector committees which intervene at the participating
 school through a range of activities related to the 4E's consisting of
@@
 surveys to measure changes in travel behaviour and perceptions (Buliung
-et al., 2011). Assessments of the efficacy of STP (Buttazzoni et al.,
-2019; Mammen et al., 2014b) indicate that it has the potential to
-encourage behaviour change and adoption of AST. STP facilitators have
-recommended that additional time and resources are needed to improve the
-efficacy of STP (Mammen et al., 2015), which highlights that long-term
-and sustained efforts driven at the policy level are required to address
-declining rates of AST.
+et al., 2011). Following the intervention, active travel rates increased
+across all schools and 14\% of parents reported a perceived reduction in
+traffic outside the school (Buliung et al., 2011). Assessments of the
+efficacy of STP (Buttazzoni et al., 2019; Mammen et al., 2014b) indicate
+that it has the potential to encourage behaviour change and adoption of
+AST. STP facilitators have recommended that additional time and
+resources are needed to improve the efficacy of STP (Mammen et al.,
+2015), which highlights that long-term and sustained efforts driven at
+the policy level are required to address declining rates of AST.
 
 How AST is framed seems particularly important to shift parental
-attitudes and perceptions given their reported influence on children's
+attitudes and perceptions, given their reported influence on children's
 travel mode to school. STP activities heavily focus on education or
@@
   million invested by the province in the Ontario Active School Travel
-  program, a city such as Hamilton budgeted in excess of CAD 91 million
-  on road maintenance and construction in 2016 alone; see:
+  program in perspective, a city such as Hamilton budgeted in excess of
+  CAD 91 million on road maintenance and construction in 2016 alone;
+  see:
   https://www.hamilton.ca/budget-finance/city-budgets/2016-tax-and-rate-budgets}.
@@
 
-\hypertarget{data}{%
-\section{3. Data}\label{data}}
-
-\hypertarget{data-retrieval}{%
-\subsection{3.1. Data retrieval}\label{data-retrieval}}
-
-\hypertarget{policy-documents}{%
-\subsubsection{3.1.1. Policy documents}\label{policy-documents}}
-
-We assembled a collection of publicly available documents that were
-sourced online from the main stakeholder groups involved in STP
-initiatives in Ontario: i) school boards (public or Catholic and
-English-speaking only); ii) municipal governments; and iii)
-transportation consortia. The latter are a unique group of entities
-sanctioned by Ontario's Ministry of Education in Ontario 2006. Each
-consortium involves a collaboration between municipal regions and school
-boards; the consortium's objective is to deliver more efficient and
-timely transportation services to schools in each region. Non-profit
-organizations, police services, and advocacy groups are other
-stakeholders who often play a role in supporting AST and/or STP, but
-this study does not include any documents from these groups because they
-are not consistently participating in all initiatives across Ontario.
-
-The search was guided first by a list of all English public and Catholic
-school boards across Ontario. The websites of each school board were
-manually searched for pages related to school transport or travel. Any
-pages relevant to these topics were manually downloaded. Next, we
-collected documents by searching municipal government and transportation
-consortia websites. These were identified based on geographic area
-(i.e., the municipalities and/or transportation consortia that are in
-the same geographic area of each school board). Webpages related to
-active transport or school travel were manually downloaded.
-
-Webpages from STP stakeholder groups were included in our analysis if
-they were easy to find. This primary criterion was important since our
-analysis pertains to how such issues are framed to the general public.
-Thus, we included only webpages that were readily accessible, which we
-defined as requiring no more than 4 separate links from the initial
-Google search.
-
-The initial corpus of documents from STP stakeholder groups included 69
-relevant webpages (i.e., one page or more) from all STP stakeholder
-groups. We refer to these as policy documents throughout the paper. It
-is important to note that school boards, municipalities, and
-transportation consortia may or may not publish information about their
-involvement in AST and STP efforts on their respective websites or in
-policy documents. Search results are summarized in Table
-\ref{tab:policy-documents}.
-
-\begin{table}
-
-\caption{\label{tab:policy-documents}\label{tab:search-results}Search results from the main STP stakeholder groups.}
-\centering
-\begin{tabular}[t]{>{}l|l|>{}l}
-\toprule
-Stakeholder & Total & Retrieved\\
-\midrule
-\cellcolor{gray!6}{\textbf{School boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{32}\\
-\textbf{Municipalities} & 62 & 28\\
-\cellcolor{gray!6}{\textbf{Transportation consortia}} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9}\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\hypertarget{academic-papers}{%
-\subsubsection{3.1.2. Academic papers}\label{academic-papers}}
-
-We conducted a search on Web of Science for scholarly papers on the
-topic of travel to school. We limited our search to the fields of public
-health, transportation, planning, urban studies, and geography. This
-initial corpus was curated by the authors to ensure that all documents
-were relevant; for example, some hits in our search were not full papers
-but conference reports, or they dealt with travel to school only
-peripherally. After this step, we assembled a collection of 227 journal
-articles for analysis.
-
-\hypertarget{data-cleaning}{%
-\subsection{3.2. Data cleaning}\label{data-cleaning}}
-
-A multi-step process was conducted to ensure that the analysis captured
-as much text as possible from both the policy documents (n = 64) and
-academic papers (n = 227). To begin, the webpages, which were manually
-downloaded in portable document format (PDF), were trimmed so that pages
-that only consisted of tables, figures, or references were removed. Many
-academic papers were in a two-column format, which is not ideal for
-conversion to \texttt{txt}. Two-column PDF documents were processed to
-extract the text in the correct sequence. Four academic papers did not
-join sufficiently and were taken out of the corpus due to the
-substantial time required to manually correct their inconsistencies.
-
-Next, we converted the trimmed PDF documents into \texttt{txt} files so
-that they could be imported for analysis in \texttt{R}. The next phase
-was to manually remove any remaining tables, figures, references,
-headers/footings, and captions that could not be trimmed. Manual
-corrections were also required for certain pages in academic papers that
-remained in two-column format after the conversion process. This
-typically occurred on pages that had a table or figure that disrupted
-the text. Finally, we reviewed all of the documents to remove
-hyphenation by line breaks and to keep hyphenated words together on the
-same line. Any ligatures (e.g., combinations of characters or letters
-that were not properly detected during the conversion process) were
-fixed.
-
-We also manually removed any extraneous material in the academic papers
-that did not pertain to AST specifically. This included footnotes,
-references, acknowledgments, and conflict of interest statements in the
-academic papers. We removed all phone numbers, inserted links to other
-webpages, personal names, and content not specific to AST from the
-policy documents that were retrieved from the websites of school boards,
-municipalities, and transportation consortia.
-
-In the final step, we removed all blank spaces, punctuation,
-capitalization, and numbers. English stop words, which are common words
-such as \emph{and} or \emph{the} as identified in a predetermined list
-by Lewis et al. (Feinerer and Hornik, 2020) and other frequent terms in
-the documents like ``school'' and specific location names, were removed
-from the corpora.
-
-\hypertarget{methods}{%
-\section{4. Methods}\label{methods}}
-
 \hypertarget{framing-analysis}{%
-\subsection{4.1. Framing analysis}\label{framing-analysis}}
+\subsection{2.4. Framing Analysis}\label{framing-analysis}}
 
@@
 communicated by a particular frame can be either positive or negative
-(\textbf{waygoodCO2ValenceFraming2018?}). There is evidence that
-negative framing may be more effective at motivating individuals to
-change transport modes to reduce CO2 emissions
-(\textbf{waygoodCO2ValenceFraming2018?}).
+(Waygood and Avineri, 2018). There is evidence that negative framing may
+be more effective at motivating individuals to change transport modes to
+reduce CO2 emissions (Waygood and Avineri, 2018).
 
@@
 
-\hypertarget{process}{%
-\subsection{4.2. Process}\label{process}}
+\hypertarget{data}{%
+\section{3. Data}\label{data}}
+
+\hypertarget{data-retrieval}{%
+\subsection{3.1. Data retrieval}\label{data-retrieval}}
+
+\hypertarget{policy-documents}{%
+\subsubsection{3.1.1. Policy documents}\label{policy-documents}}
+
+We assembled a collection of publicly available documents that were
+sourced online from the main stakeholder groups involved in STP
+initiatives in Ontario: i) school boards (public or Catholic and
+English-speaking only); ii) municipal governments; and iii)
+transportation consortia. The latter are a unique group of entities
+sanctioned by Ontario's Ministry of Education in Ontario 2006. Each
+consortium involves a collaboration between municipal regions and school
+boards; the consortium's objective is to deliver more efficient and
+timely transportation services to schools in each region. Non-profit
+organizations, police services, and advocacy groups are other
+stakeholders who often play a role in supporting AST and/or STP, but
+this study does not include any documents from these groups because they
+are not consistently participating in all initiatives across Ontario.
+
+The search was guided first by a list of all English public and Catholic
+school boards across Ontario. The websites of each school board were
+manually searched for pages related to school transport or travel. Any
+pages relevant to these topics were manually downloaded. Next, we
+collected documents by searching municipal government and transportation
+consortia websites. These were identified based on geographic area
+(i.e., the municipalities and/or transportation consortia that are in
+the same geographic area of each school board). Webpages related to
+active transport or school travel were manually downloaded.
+
+Webpages from STP stakeholder groups were included in our analysis if
+they were easy to find. This primary criterion was important since our
+analysis pertains to how such issues are framed to the general public.
+Thus, we included only webpages that were readily accessible, which we
+defined as requiring no more than 4 separate links from the initial
+Google search.
+
+The initial corpus of documents from STP stakeholder groups included 69
+relevant webpages (i.e., one page or more). We refer to these as policy
+documents throughout the paper. It is important to note that school
+boards, municipalities, and transportation consortia may or may not
+publish information about their involvement in AST and STP efforts on
+their respective websites or in policy documents. Search results are
+summarized in Table \ref{tab:policy-documents}.
+
+\begin{table}
+
+\caption{\label{tab:policy-documents}\label{tab:search-results}Search results from the main STP stakeholder groups.}
+\centering
+\begin{tabular}[t]{>{}l|l|>{}l}
+\toprule
+Stakeholder & Total & Retrieved\\
+\midrule
+\cellcolor{gray!6}{\textbf{School boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{32}\\
+\textbf{Municipalities} & 62 & 28\\
+\cellcolor{gray!6}{\textbf{Transportation consortia}} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9}\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\hypertarget{academic-papers}{%
+\subsubsection{3.1.2. Academic papers}\label{academic-papers}}
+
+We conducted a search on Web of Science for scholarly papers on the
+topic of travel to school. We limited our search to the fields of public
+health, transportation, planning, urban studies, and geography. This
+initial corpus was curated by the authors to ensure that all documents
+were relevant; for example, some hits in our search were not full papers
+but conference reports, or they dealt with travel to school only
+peripherally. After this step, we assembled a collection of 227 journal
+articles for analysis.
+
+\hypertarget{data-cleaning}{%
+\subsection{3.2. Data cleaning}\label{data-cleaning}}
+
+A multi-step process was conducted to ensure that the analysis captured
+as much text as possible from both the policy documents (n = 64) and
+academic papers (n = 227). To begin, the webpages, which were manually
+downloaded in portable document format (PDF), were trimmed so that pages
+that only consisted of tables, figures, or references were removed. Many
+academic papers were in a two-column format, which is not ideal for
+conversion to \texttt{txt}. Two-column PDF documents were processed to
+extract the text in the correct sequence. Four academic papers did not
+join sufficiently and were taken out of the corpus due to the
+substantial time required to manually correct their inconsistencies.
+
+Next, we converted the trimmed PDF documents into \texttt{txt} files so
+that they could be imported for analysis in \texttt{R}. The next phase
+was to manually remove any remaining tables, figures, references,
+headers/footings, and captions that could not be trimmed. Manual
+corrections were also required for certain pages in academic papers that
+remained in two-column format after the conversion process. This
+typically occurred on pages that had a table or figure that disrupted
+the text. Finally, we reviewed all of the documents to remove
+hyphenation by line breaks and to keep hyphenated words together on the
+same line. Any ligatures (e.g., combinations of characters or letters
+that were not properly detected during the conversion process) were
+fixed.
+
+We also manually removed any extraneous material that did not pertain to
+AST specifically. For the academic papers, this included footnotes,
+references, acknowledgments, and conflict of interest statements. For
+the policy+practice documents, it included phone numbers, inserted links
+to other webpages, personal names, and content not specific to AST. In
+the final step, we removed all blank spaces, punctuation,
+capitalization, and numbers. English stop words, which are common words
+such as \emph{and} or \emph{the} as identified in a predetermined list
+by Feinerer and Hornik (2020) and other frequent terms in the documents
+like ``school'' and specific location names, were removed from the
+corpora.
+
+\hypertarget{methods}{%
+\section{4. Methods}\label{methods}}
+
+\hypertarget{process-of-framing-analysis}{%
+\subsection{4.1. Process of Framing
+Analysis}\label{process-of-framing-analysis}}
 
@@
 of topics, and each topic as a mixture of words'' (Silge and Robinson,
-2021). The model's output is ``a set of topics consisting of clusters of
+2022). The model's output is ``a set of topics consisting of clusters of
 words that co-occur in these documents according to certain patterns''
@@
 topics, as done after other methods of manual coding. We also compare
-the topics between the policy documents and the academic papers, and use
-our interpretation to answer our research question. We describe in more
-detail the functions and code in \texttt{R} that we used.
+the topics between the policy documents and the academic papers to
+interpret what is being communicated by STP stakeholders. We describe in
+more detail the functions and code in \texttt{R} that we used.
 
@@
 This paper is an example of open and reproducible research that uses
-only open software. All data are organized in the form of an open data
-product (Arribas-Bel et al., 2021). Following best practices in spatial
-data science (\textbf{brunsdon2020opening?}), the code and data needed
-to reproduce our research or conduct a similar analysis for other
-regions are available for download.
+only open software. Following best practices in spatial data science
+(Brunsdon and Comber, 2020), the code and data needed to reproduce our
+research or conduct a similar analysis for other regions are available
+for download upon request.
 
@@
 \emph{safety} and \emph{traffic} as common words which suggests that
-such concerns are a common reason given for parents driving their
-children to school. The word \emph{physical} is present in each corpus,
-but it's not clear what this refers to (e.g, \emph{physical activity},
-\emph{physical health}, or the \emph{physical environment}).
-Furthermore, documents from STP stakeholder groups discuss
-\emph{resources}, \emph{information}, and \emph{services} about school
-travel. Unlike the academic papers, policy documents include the words
-\emph{route} or \emph{routes} as frequent terms. This could indicate the
-presence of ``safe routes to school'' in the policy corpus, as well as
-the role of STP stakeholder groups in identifying safe routes to school
-to share with parents or families. In the section below, the context in
-which these terms are used is explored further.
+these are common concerns for parents. The word \emph{physical} is
+present in each corpus, but it's not clear what this refers to (e.g,
+\emph{physical activity}, \emph{physical health}, or the \emph{physical
+environment}). Furthermore, documents from STP stakeholder groups
+discuss \emph{resources}, \emph{information}, and \emph{services} about
+school travel. Unlike the academic papers, policy documents include the
+words \emph{route} or \emph{routes} as frequent terms. This could
+indicate the presence of ``safe routes to school'' in the policy corpus,
+as well as the role of STP stakeholder groups in identifying safe routes
+to school to share with parents or families. In the section below, the
+context in which these terms are used is explored further.
 
@@
 
-\caption{\label{tab:word-table}\label{tab:word-table}Top 25 terms identified in each corpora. Document frequencies are also indicated.}
+\caption{\label{tab:word-table}\label{tab:word-table}Top 25 terms identified in each corpus. Document frequencies are also indicated.}
 \centering
@@
 or impacts of AST; ii) mechanisms of intervention; iii) concerns or
-considerations; and iv) supports for AST. This interpretation indicates
-that the general public accessing information about AST in Ontario is
+barriers; and iv) supports for AST. This interpretation indicates that
+the general public accessing information about AST in Ontario is
 informed about a wide range of content related to this issue.
@@
 girls} (n = 211) is another common bigram. Finally, the presence of
-\emph{statistically significant} among the top bigrams underscores that
+\emph{statistically significant} among the top bigrams indicates that
 researchers often aim to identify associations using statistical
 measures. We found that the academic corpus focuses on a greater range
-of topics than found in the policy documents.
+of topics than found in the policy+practice documents.
 
@@
 \textbf{Mental Health} & Municipality & Active and Sustainable School Travel (ASST) not only improves physical and mental health but contributes to a healthier environment and safer streets.\\
-\textbf{\cellcolor{gray!6}{Physical Health}} & \cellcolor{gray!6}{Municipality} & \cellcolor{gray!6}{Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.}\\
+\textbf{\cellcolor{gray!6}{Physical Health}} & \cellcolor{gray!6}{Municipality} & \cellcolor{gray!6}{Encouraging Active Transportation promotes physical health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.}\\
 \bottomrule
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/policy-terms-1} \caption{\label{fig:policy-terms}Topics identified in the policy corpus according to clusters of words.}\label{fig:policy-terms}
+\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/policy-terms-1} \caption{\label{fig:policy-terms}Topics identified in the policy+practice corpus according to clusters of words.
+The per-word-per-topic probabilities are shown by beta.}\label{fig:policy-terms}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/academic-terms-1} \caption{\label{fig:academic-terms}Topics identified in the academic corpus according to clusters of words.}\label{fig:academic-terms}
+\includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/academic-terms-1} \caption{\label{fig:academic-terms}Topics identified in the academic corpus according to clusters of words.
+The per-word-per-topic probabilities are shown by beta.}\label{fig:academic-terms}
 \end{figure}
@@
 examine the different topics found in the policy and academic corpora.
-We focused on the policy+practice corpus, instead of assessing the
+We focused on the policy/practice corpus, instead of assessing the
 municipal, school, and consortia documents separately, so that we could
 report on the various frames used across all documents put out by STP
-stakeholder groups in Ontario. We then estimated Latent Dirillecth
+stakeholder groups in Ontario. We then estimated Latent Dirichlet
 Allocation (LDA) models for each corpus. Parameter tuning suggests that
-the policy+practice corpus has between 7 and 9 topics and the academic
+the policy+practice corpus has between 9 and 13 topics and the academic
 corpus has between 17 and 25 topics. After running the LDA model for the
@@
 17 topics based on the clusters of words that were identified. We
-experimented with the model by adjusting and evaluating the number of
-topics and found that there were 9 distinct topics that could be
-interpreted, after which there was too much overlap for the clusters to
-be meaningfully interpreted. Figures \ref{fig:policy-terms} and
-\ref{fig:academic-terms} present the main terms that are associated with
-the topics found in each corpus.
+experimented with the model by adjusting the number of topics and
+evaluating the output of terms in each topic. We found that there were 9
+distinct topics that could be interpreted in the policy corpus and 11
+topics in the academic corpus, after which there was too much overlap
+for the clusters to be meaningfully interpreted. Figures
+\ref{fig:policy-terms} and \ref{fig:academic-terms} present the main
+terms that are associated with the topics found in each corpus.
 
 In the policy+practice corpus, we identified the following topics based
-on the cluster of words: (1) resources for walking; (2) walking; (3)
-support for active travel; (4) bicycling and the environment; (5)
-benefits of active travel; (6) safety; and (7) busing information and
-eligibility. These topics indicate that STP stakeholder groups are
+on the cluster of words: (1) safety; (2) weather and busing; (3) active
+travel planning; (4) walking; (5) resources for walking; (6) bicycling;
+(7) active travel concerns; (8) benefits of active travel; and (9)
+busing logistics. These topics indicate that STP stakeholder groups are
 sending the message that walking and bicycling to school are healthy
@@
 in using active modes to school, for example regarding the availability
-of cycling lanes and tips for route choice for walking.
+of bicycling lanes and tips for route choice for walking.
 
@@
 volume of papers included. The following topics were identified based on
-the clusters of words: (1) built environment (2) walking distance; (3)
-AST interventions; (4) parental barriers to walking; (5) behaviours and
-attitudes; (6) bicycling; (7) social environment; (8) children's
-independent mobility; (9) modeling trip choice; (10) adolescents and
-physical activity; and (11) safe routes to school programs. This corpus
-reflects a broader range of topics than the policy+practice corpus.
+the clusters of words: (1) physical activity; (2) safe routes to school
+for active travel; (3) behaviours and attitudes; (4) bicycling; (5)
+walking; (6) built environment; (7) trip choice; (8) active school
+travel interventions; (9) parents; (10) children's independent mobility;
+and (11) public health and policies. This corpus reflects a broader
+range of topics than the policy/practice corpus.
 
@@
 The secondary frame in policy documents is that AST is accessible and
-feasible for children and parents. The documents indicate that there is
+feasible for children and parents. Despite the emphasis on the logistics
+of busing in the topic modelling, the documents indicate that there is
 an opportunity for or prospect of behaviour change. Some cities and
@@
 \begin{quote}
-Help your students get started on the right foot - encourage them to
-walk or bike to school when possible. Even leaving the car a block or
+\emph{Help your students get started on the right foot - encourage them
+to walk or bike to school when possible. Even leaving the car a block or
 two and walking the rest of the way helps. It's good for the environment
 and your health, and teaches your child independence and community
-awareness.\_ (Halton District School Board)
+awareness.} (Halton District School Board)
 \end{quote}
@@
 of AST to children's school performance are less well-supported in the
-extant literature (\textbf{westmanChapterThreeTravel2020?}). STP
-stakeholder groups also communicate that increasing AST may reduce
-traffic near and around schools. This is conveyed presumably to
-alleviate parental concerns about traffic and safety (Evers et al.,
-2014; Mammen et al., 2012; Rothman et al., 2015; Wilson et al., 2018) or
-to reduce the frequency of risky behaviours from drivers around schools
-(Rothman et al., 2017).
+extant literature (Westman et al., 2020). STP stakeholder groups also
+communicate that increasing AST may reduce traffic near and around
+schools. This is conveyed presumably to alleviate parental concerns
+about traffic and safety (Evers et al., 2014; Mammen et al., 2012;
+Rothman et al., 2015; Wilson et al., 2018) or to reduce the frequency of
+risky behaviours from drivers around schools (Rothman et al., 2017).
 
@@
 as well as the evidence that the built environment influences mode
-choice to school. Although it is beyond the scope of this paper to
+choice to school. However, it is beyond the scope of this paper to
 assess whether the proposed solutions are perceived to be sufficient by
@@
 found that positive framing can be less effective than negative framing
-(\textbf{waygoodCO2ValenceFraming2018?}). Policy documents should make
-it clear that continued use of nonactive modes to school can deprive
-children of opportunities to increase physical activity and to gain
-health and social benefits.
+(Waygood and Avineri, 2018). A negative framing that challenges the
+social norm of driving could be more motivational to shift modes, which
+would be consistent with other findings (see Waygood and Avineri, 2018).
+Policy documents should make it clear that continued use of nonactive
+modes to school can deprive children of opportunities to increase
+physical activity and to gain health and social benefits.
 
@@
 (Westman et al., 2017a), is also not adequately addressed by STP
-stakeholders. Parental assessment of a child's ability to handle the
+stakeholders. Parental assessment of a child's ability to undertake the
 journey to school was likewise overlooked despite its role in decision
-making for mode choice to school
-(\textbf{faulknerWhatQuickestEasiest2010?}). Framing AST as a
-developmental opportunity or a rite of passage that children have been
-denied could challenge the prevailing culture of risk which discourages
-parents from letting their children use active modes to school. In
-communities with low AST uptake, STP stakeholders may wish to emphasize
-the negative effects of parents continuing to drive children to and from
-school. A negative framing that challenges the social norm of driving
-could be more motivational to shift modes, which would be consistent
-with other findings (\textbf{waygoodCO2ValenceFraming2018?}).
+making for mode choice to school (Faulkner et al., 2010). Framing AST as
+a developmental opportunity or a rite of passage that children have been
+denied could challenge the prevailing culture of risk avoidance which
+discourages parents from letting their children use active modes to
+school.
 
@@
 public, regardless of whether they currently have children commuting
-to/from school. The ``political stream'' could also be further engaged
-by working with advocacy groups who could attract more support from a
-broader coalition of individuals.
-
-We also contend that the ways in which the AST issue is framed can
-affect the policy process, as outlined in Kingdon's (1984) Multiple
-Streams Framework (MSF), through all three streams (i.e., problem,
-policy, and politics). This framing can ultimately impact the timing and
-success of a ``window of opportunity'' to enact policy changes that
-address the decline of AST in Canada.
+to/from school.
 
@@
 
-A limitation of this study is that we only analyzed texts that were
-easily accessible to the general public on the websites of STP
-stakeholders in Ontario. Parents likely receive information about AST
+A limitation of this study is that we only analyzed English-language
+texts that were easily accessible to the general public on the websites
+of STP stakeholders in Ontario. We did not include French-language
+materials from Ontario's 12 French school boards (a mixture of public
+and Catholic schools). Parents likely receive information about AST
 directly from schools, which may contain more content that reflects the
-local barriers to AST.
+local barriers to AST, but these materials were not used in our
+analysis.
 
@@
 initiatives and limit awareness in the general public. In their public
-materials about AST, STP stakeholders emphasize why AST rates should
-increase in local communities and how the negative effects of nonactive
-modes to school may impact children's health and wellbeing.
+materials about AST, STP stakeholders should emphasize why AST rates
+should increase in local communities and how the negative effects of
+nonactive modes to school may impact children's health and wellbeing.
 
@@
 2021), \texttt{ggplot2} (Wickham et al., 2021a), \texttt{igraph} (file.,
-2021), \texttt{pdftools} (Ooms, 2021), \texttt{readr} (Wickham et al.,
+2022), \texttt{pdftools} (Ooms, 2021), \texttt{readr} (Wickham et al.,
 2021c), \texttt{reshape2} (Wickham, 2020), \texttt{stringr} (Wickham,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-albalawiUsingTopicModeling2020}{}}%
-Albalawi, R., Yeap, T.H., Benyoucef, M., 2020. Using {Topic Modeling
-Methods} for {Short}-{Text Data}: A {Comparative Analysis}. Frontiers in
+Albalawi, R., Yeap, T.H., Benyoucef, M., 2020. Using topic modeling
+methods for short-text data: A comparative analysis. Frontiers in
 Artificial Intelligence 3, 42.
 doi:\href{https://doi.org/10.3389/frai.2020.00042}{10.3389/frai.2020.00042}
-
-\leavevmode\vadjust pre{\hypertarget{ref-arribasOpen2021}{}}%
-Arribas-Bel, D., Green, M., Rowe, F., Singleton, A., 2021. Open data
-products-a framework for creating valuable analysis ready data. Journal
-of Geographical Systems 23, 497--514.
-doi:\href{https://doi.org/10.1007/s10109-021-00363-5}{10.1007/s10109-021-00363-5}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-brunsdon2020opening}{}}%
+Brunsdon, C., Comber, A., 2020. Opening practice: Supporting
+reproducibility and critical spatial data science. Journal of
+Geographical Systems.
+doi:\href{https://doi.org/10.1007/s10109-020-00334-2}{10.1007/s10109-020-00334-2}
+
 \leavevmode\vadjust pre{\hypertarget{ref-buliungSchoolTravelPlanning2011}{}}%
-Buliung, R., Faulkner, G., Beesley, T., Kennedy, J., 2011. School
-{Travel Planning}: Mobilizing {School} and {Community Resources} to
-{Encourage Active School Transportation}. Journal of School Health 81,
-704--712.
+Buliung, R., Faulkner, G., Beesley, T., Kennedy, J., 2011. School travel
+planning: Mobilizing school and community resources to encourage active
+school transportation. Journal of School Health 81, 704--712.
 doi:\href{https://doi.org/10.1111/j.1746-1561.2011.00647.x}{10.1111/j.1746-1561.2011.00647.x}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-GreenCommunities2016}{}}%
-Canada, G.C., 2020a. Ontario active school travel fund {[}WWW
+Canada, G.C., 2020. Ontario active school travel {[}WWW Document{]}. URL
+\url{https://ontarioactiveschooltravel.ca/about-ontario-active-school-travel/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-GreenCommunitiesProjects}{}}%
+Canada, G.C., 2021. Ontario active school travel fund {[}WWW
 Document{]}. URL
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-GreenCommunitiesProjects}{}}%
-Canada, G.C., 2020b. OAST fund project directory {[}WWW Document{]}. URL
-\url{https://ontarioactiveschooltravel.ca/wp-content/uploads/2020/10/OAST-Fund-Matrix-Directory.pdf}
+\leavevmode\vadjust pre{\hypertarget{ref-TACbikeinfra2020}{}}%
+Canada, T.A. of, 2020. Safety performance of bicycle infrastructure in
+canada {[}WWW Document{]}. URL
+\url{https://www.tac-atc.ca/en/publications/ptm-spbi-e}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-faulknerWhatQuickestEasiest2010}{}}%
+Faulkner, G.E., Richichi, V., Buliung, R.N., Fusco, C., Moola, F., 2010.
+What's "quickest and easiest?": Parental decision making about school
+trip mode. International Journal of Behavioral Nutrition and Physical
+Activity 7, 1--11.
+doi:\href{https://doi.org/10.1186/1479-5868-7-62}{10.1186/1479-5868-7-62}
+
 \leavevmode\vadjust pre{\hypertarget{ref-faulknerSchoolTravelChildren2013}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-igraph}{}}%
-file., S.A., 2021. Igraph: Network analysis and visualization.
+file., S.A., 2022. Igraph: Network analysis and visualization.
 
@@
 Gamson, W.A., Modigliani, A., 1987. The changing culture of affirmative
-action. JAI Press.
+action, in: Waygood, E.O.D., Friman, M., Olsson, L.E., Mitra, R. (Eds.),
+Research in Political Sociology. {JAI Press}, pp. 137--177.
 
@@
 Goffman, E., 1974. Frame analysis: An essay on the organization of
-experience, Frame analysis: An essay on the organization of experience.
-{Harvard University Press}, {Cambridge, MA, US}.
+experience, Frame analysis: {An} essay on the organization of
+experience. {Harvard University Press}, {Cambridge, MA, US}.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kingdonAgendasAlternativesPublic1984}{}}%
-Kingdon, J.W. (Ed.), 1984. Agendas, alternatives and public policies.
-Pearson.
+Kingdon, J.W., 1984. Agendas, alternatives, and public policies. {Harper
+Collins}.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-laroucheRatherBikeSchool2016}{}}%
-Larouche, R., Stone, M., Buliung, R.N., Faulkner, G., 2016. ''{I}'d
-rather bike to school!'': Profiling children who would prefer to cycle
-to school. Journal of Transport \& Health 3, 377--385.
+Larouche, R., Stone, M., Buliung, R.N., Faulkner, G., 2016. ''I'd rather
+bike to school!'': Profiling children who would prefer to cycle to
+school. Journal of Transport \& Health 3, 377--385.
 doi:\href{https://doi.org/10.1016/j.jth.2016.06.010}{10.1016/j.jth.2016.06.010}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-larsenRouteBasedAnalysisCapture2012}{}}%
-Larsen, K., Gilliland, J., Hess, P.M., 2012. Route-{Based Analysis} to
-{Capture} the {Environmental Influences} on a {Child}'s {Mode} of
-{Travel} between {Home} and {School}. Annals of the Association of
-American Geographers 102, 1348--1365.
-doi:\href{https://doi.org/10.1080/00045608.2011.627059}{10.1080/00045608.2011.627059}
+Larsen, K., Gilliland, J., Hess, P.M., 2012. Route-based analysis to
+capture the environmental influences on a child's mode of travel between
+home and school. Annals of the Association of American Geographers 102,
+1348--1365.
 
@@
 Mah, C.L., Hamill, C., Rondeau, K., McIntyre, L., 2014. A frame-critical
-policy analysis of {Canada}'s response to the {World Food Summit}
+policy analysis of canada's response to the world food summit
 1998\textendash 2008. Archives of Public Health 72, 41.
 doi:\href{https://doi.org/10.1186/2049-3258-72-41}{10.1186/2049-3258-72-41}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mahDoesParentalSupport2017a}{}}%
+Mah, S.K., Nettlefold, L., Macdonald, H.M., Winters, M., Race, D., Voss,
+C., McKay, H.A., 2017. Does parental support influence children's active
+school travel? Preventive Medicine Reports 6, 346--351.
+doi:\href{https://doi.org/10.1016/j.pmedr.2017.04.008}{10.1016/j.pmedr.2017.04.008}
 
@@
 Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2014a. School travel
-planning in {Canada}: Identifying child, family, and school-level
+planning in canada: Identifying child, family, and school-level
 characteristics associated with travel mode shift from driving to active
-school travel. Journal of Transport \& Health, Walking \& {Cycling}: The
-contributions of health and transport geography 1, 288--294.
+school travel. Journal of Transport \& Health 1, 288--294.
 doi:\href{https://doi.org/10.1016/j.jth.2014.09.004}{10.1016/j.jth.2014.09.004}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mammenPuttingSchoolTravel2015}{}}%
-Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2015. ''{Putting}
+Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2015. ''Putting
 school travel on the map'': Facilitators and barriers to implementing
-school travel planning in {Canada}. Journal of Transport \& Health 2,
+school travel planning in canada. Journal of Transport \& Health 2,
 318--326.
@@
 O'Brien, C., Kennedy, J., 2014b. Active school travel: An evaluation of
-the {Canadian} school travel planning intervention. Preventive Medicine
+the canadian school travel planning intervention. Preventive Medicine
 60, 55--59.
@@
 Michail, N., Ozbil, A., Parnell, R., Wilkie, S., 2021. Children's
-{Experiences} of {Their Journey} to {School}: Integrating {Behaviour
-Change Frameworks} to {Inform} the {Role} of the {Built Environment} in
-{Active School Travel Promotion}. International Journal of Environmental
-Research and Public Health 18, 4992.
+experiences of their journey to school: Integrating behaviour change
+frameworks to inform the role of the built environment in active school
+travel promotion. International Journal of Environmental Research and
+Public Health 18, 4992.
 doi:\href{https://doi.org/10.3390/ijerph18094992}{10.3390/ijerph18094992}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mitraIndependentMobilityMode2013}{}}%
-Mitra, R., 2013. Independent {Mobility} and {Mode Choice} for {School
-Transportation}: A {Review} and {Framework} for {Future Research}.
-Transport Reviews 33, 21--43.
+Mitra, R., 2013. Independent mobility and mode choice for school
+transportation: A review and framework for future research. Transport
+Reviews 33, 21--43.
 doi:\href{https://doi.org/10.1080/01441647.2012.743490}{10.1080/01441647.2012.743490}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-paezEnjoyment2010}{}}%
-Paez, A., Whalen, K., 2010. Enjoyment of commute: A comparison of
-different transportation modes. Transportation Research Part a-Policy
+\leavevmode\vadjust pre{\hypertarget{ref-paezEnjoymentCommuteComparison2010}{}}%
+Páez, A., Whalen, K., 2010. Enjoyment of commute: A comparison of
+different transportation modes. Transportation Research Part A: Policy
 and Practice 44, 537--549.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ramanathanHappinessMotionEmotions2014a}{}}%
+Ramanathan, S., O'Brien, C., Faulkner, G., Stone, M., 2014. Happiness in
+motion: Emotions, well-being, and active school travel. Journal of
+School Health 84, 516--523.
+doi:\href{https://doi.org/10.1111/josh.12172}{10.1111/josh.12172}
+
 \leavevmode\vadjust pre{\hypertarget{ref-reynardGrowthResilienceHow2021}{}}%
 Reynard, D., Collins, D., Shirgaokar, M., 2021. Growth over resilience:
-How {Canadian} municipalities frame the challenge of reducing carbon
+How canadian municipalities frame the challenge of reducing carbon
 emissions. Local Environment 0, 1--13.
@@
 Riazi, N.A., Blanchette, S., Trudeau, F., Larouche, R., Tremblay, M.S.,
-Faulkner, G., 2019. Correlates of {Children}'s {Independent Mobility} in
-{Canada}: A {Multi}-{Site Study}. International Journal of Environmental
+Faulkner, G., 2019. Correlates of children's independent mobility in
+canada: A multi-site study. International Journal of Environmental
 Research and Public Health 16.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-romeroChildrenExperiencesEnjoyment2015}{}}%
-Romero, V., 2015. {Children}'s experiences: Enjoyment and fun as
+Romero, V., 2015. Children's experiences: Enjoyment and fun as
 additional encouragement for walking to school. Journal of Transport \&
@@
 Rothman, L., Buliung, R., To, T., Macarthur, C., Macpherson, A., Howard,
-A., 2015. Associations between parents' perception of traffic danger,
-the built environment and walking to school. Journal of Transport \&
-Health 2, 327--335.
+A., 2015. Associations between parents perception of traffic danger, the
+built environment and walking to school. Journal of Transport \& Health
+2, 327--335.
 doi:\href{https://doi.org/10.1016/j.jth.2015.05.004}{10.1016/j.jth.2015.05.004}
@@
 Ling, R., Zanotto, M., Rancourt, M., Winters, M., 2021. Active school
-transportation and the built environment across {Canadian} cities:
+transportation and the built environment across canadian cities:
 Findings from the child active transportation safety and the environment
-({CHASE}) study. Preventive Medicine 146, 106470.
+(CHASE) study. Preventive Medicine 146, 106470.
 doi:\href{https://doi.org/10.1016/j.ypmed.2021.106470}{10.1016/j.ypmed.2021.106470}
@@
 Rothman, L., Macpherson, A.K., Ross, T., Buliung, R.N., 2018. The
-decline in active school transportation ({AST}): A systematic review of
-the factors related to {AST} and changes in school transport over time
-in {North America}. Preventive Medicine 111, 314--322.
+decline in active school transportation (AST): A systematic review of
+the factors related to AST and changes in school transport over time in
+north america. Preventive Medicine 111, 314--322.
 doi:\href{https://doi.org/10.1016/j.ypmed.2017.11.018}{10.1016/j.ypmed.2017.11.018}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-silgeTextMining2021}{}}%
-Silge, J., Robinson, D., 2021. Text {Mining} with {R}.
+Silge, J., Robinson, D., 2022. Text mining with r: A tidy approach
+{[}WWW Document{]}. URL \url{https://www.tidytextmining.com/}
 
@@
 Stark, J., Frühwirth, J., Aschauer, F., 2018. Exploring independent and
-active mobility in primary school children in {Vienna}. Journal of
+active mobility in primary school children in vienna. Journal of
 Transport Geography 68, 31--41.
@@
 2020. Factors affecting parental safety perception, satisfaction with
-school travel and mood in primary school children in the {Netherlands}.
+school travel and mood in primary school children in the netherlands.
 Journal of Transport \& Health 16, 100837.
 doi:\href{https://doi.org/10.1016/j.jth.2020.100837}{10.1016/j.jth.2020.100837}
+
+\leavevmode\vadjust pre{\hypertarget{ref-waygoodCO2ValenceFraming2018}{}}%
+Waygood, E.O.D., Avineri, E., 2018. CO2 valence framing: Is it really
+any different from just giving the amounts? Transportation Research Part
+D: Transport and Environment 63, 718--732.
+doi:\href{https://doi.org/10.1016/j.trd.2018.07.011}{10.1016/j.trd.2018.07.011}
 
@@
 Waygood, E.O.D., Friman, M., Olsson, L.E., Mitra, R. (Eds.), 2020.
-Transport and {Children}'s {Wellbeing}, in: Transport and {Children}'s
-{Wellbeing}. {Elsevier}, pp. i--ii.
+Transport and children's wellbeing. {Elsevier}, pp. i--ii.
 doi:\href{https://doi.org/10.1016/B978-0-12-814694-1.09993-0}{10.1016/B978-0-12-814694-1.09993-0}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-weathersDevelopmentsFramingClimate2016}{}}%
-Weathers, M.R., Kendall, B.E., 2016. Developments in the {Framing} of
-{Climate Change} as a {Public Health Issue} in {US Newspapers}.
-Environmental Communication 10, 593--611.
+Weathers, M.R., Kendall, B.E., 2016. Developments in the framing of
+climate change as a public health issue in US newspapers. Environmental
+Communication 10, 593--611.
 doi:\href{https://doi.org/10.1080/17524032.2015.1050436}{10.1080/17524032.2015.1050436}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-westmanWhatDrivesThem2017}{}}%
-Westman, J., Friman, M., Olsson, L.E., 2017a. What {Drives Them} to
-{Drive}?\textemdash{{Parents}}' {Reasons} for {Choosing} the {Car} to
-{Take Their Children} to {School}. Frontiers in Psychology 8.
+Westman, J., Friman, M., Olsson, L.E., 2017a. What drives them to drive?
+\textemdash Parents' reasons for choosing the car to take their children
+to school. Frontiers in Psychology 8.
 doi:\href{https://doi.org/10.3389/fpsyg.2017.01970}{10.3389/fpsyg.2017.01970}
+
+\leavevmode\vadjust pre{\hypertarget{ref-westmanTravelChildWellbeing2020}{}}%
+Westman, J., Friman, M., Olsson, L.E., 2020. Travel and child wellbeing:
+The psychological and cognitive domains, in: Waygood, E.O.D., Friman,
+M., Olsson, L.E., Mitra, R. (Eds.), Transport and Children's Wellbeing.
+{Elsevier}, pp. 41--59.
+doi:\href{https://doi.org/10.1016/B978-0-12-814694-1.00003-8}{10.1016/B978-0-12-814694-1.00003-8}
 
@@
 Zwerts, E., Allaert, G., Janssens, D., Wets, G., Witlox, F., 2010. How
-children view their travel behaviour: A case study from {Flanders}
-({Belgium}). Journal of Transport Geography 18, 702--710.
+children view their travel behaviour: A case study from flanders
+(belgium). Journal of Transport Geography, Special {section} on
+{Alternative Fuels} and {Vehicles} 18, 702--710.
 doi:\href{https://doi.org/10.1016/j.jtrangeo.2009.10.002}{10.1016/j.jtrangeo.2009.10.002}

### 2022-05-12 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Revised manuscript with reduced word count to meet journal's guidelines

@@
 For instance, in a study conducted in Toronto, Ontario, 40% of children who were driven to school stated they would like to travel by bicycle instead [@laroucheRatherBikeSchool2016].
-The study also reported that less than 3% of respondents actually cycled, despite the vast majority having access to a bicycle and living within a short and bikeable distance to school.
 Another study based in London, Ontario, reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012].
@@
 As of December 2021, OAST has awarded over CAD 2 million and provided resources to over 25 projects across Ontario.
-Many communities implemented school travel planning (STP), along with encouraging activities like walking school buses and developed resources for schools and parents, among other actions [see @GreenCommunitiesProjects].
+Many communities implemented school travel planning (STP) [see @GreenCommunitiesProjects].
 In this context, STP is a popular "school-specific" intervention led by a facilitator who brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014].
@@
 
-There is value in communicating the benefits of AST to the public in order to convey the importance of this issue.
 The desire to increase AST in Canada is certainly warranted - there is compelling evidence of the physical and mental health benefits that children who actively commute to school attain.
@@
 The daily routine of travelling to school can be a good opportunity for children to regularly build physical activity into their schedule [@mitraIndependentMobilityMode2013].
-Research has also shown that using active modes to school contributes to improve cardiovascular fitness [@borrestadExperiencesRandomisedControlled2012].
-
-More recently, the literature has explored the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020], with relevant applications to the study of travel satisfaction [@vandenbergFactorsAffectingParental2020; @westmanChildrenTravelSchool2017].
+
+More recently, the literature has explored the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020].
 Being driven to school reduces community interactions for children, which may negatively impact their social wellbeing [@waygoodChildrenTravelIncidental2015].
 In contrast, walking and bicycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021] and increase positive emotions that contribute to wellbeing [@ramanathanHappinessMotionEmotions2014a].
-This is something that children seem to value [@zwertsHowChildrenView2010] and that tracks with findings among university students [@paezEnjoymentCommuteComparison2010].
-More generally, social connections through travel appear to be important for wellbeing.
-Furthermore, AST can provide opportunities for children to engage with natural environments [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015].
+This is something that children seem to value [@zwertsHowChildrenView2010].
+AST can also provide opportunities for children to engage with natural environments [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015].
 
@@
 Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behaviour is understood within the context of household, social, neighbourhood, and policy environments.
-The SEM comes from the field of public health and is a useful framework for understanding complex health behaviours, such as walking and bicycling habits, This model helps to identify multiple determinants that need to be addressed by interventions to facilitate behaviour change.
-The consensus in the literature is that interventions should target multiple levels in order to increase levels of healthy and physically active modes of travel to school [@mitraIndependentMobilityMode2013].
+Th SEM helps to identify multiple determinants that need to be addressed by school-based interventions to increase AST, with the consensus being that interventions should target multiple levels [@mitraIndependentMobilityMode2013].
 Rather than describing an extensive list of factors that influence AST and mode choice in Canada [e.g., @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], we discuss a few potentially modifiable determinants that may be targeted for change through STP.
 
-At the individual level, age is often positively associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018].
-There is evidence that gender is a determinant of AST, and that boys are more likely to travel using active modes than girls, although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015].
 Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], as well as daily parental support [@mahDoesParentalSupport2017a].
@@
 
-Distance between home and school is most negatively associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school - low density suburban development tends to increase the need for movement, and the reliance on motorized modes [@farberRunning2011].
+Distance between home and school is most negatively associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
 Many studies have also found that the quality of the built environment along the route to school and around the school site [@ikedaAssociationsChildrenActive2018; @rothmanActiveSchoolTransportation2021] and provision of active travel infrastructure [@chenPromotingActiveStudent2018; @pontEnvironmentalCorrelatesChildren2009] facilitate AST.
@@
 Within the STP process, facilitators generally establish multi-sector committees which intervene at the participating school through a range of activities related to the 4E's consisting of _education_ strategies, _encouragement_ through in-person events or programs, _engineering_ improvements to or around the school site, and _enforcement_ of traffic speeds around schools [@langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
-The first large-scale evaluation of STP as an intervention in Canada took place at twelve schools across the country, including four in Ontario, using parental surveys to measure changes in travel behaviour and perceptions [@buliungSchoolTravelPlanning2011].
-Following the intervention, active travel rates increased across all schools and 14% of parents reported a perceived reduction in traffic outside the school [@buliungSchoolTravelPlanning2011].
+Following the first large-scale evaluation of STP as an intervention in Canada, AST rates increased across all schools and 14% of parents reported a perceived reduction in traffic outside the school [@buliungSchoolTravelPlanning2011].
 Assessments of the efficacy of STP [@buttazzoniPromotingActiveSchool2019; @mammenActiveSchoolTravel2014] indicate that it has the potential to encourage behaviour change and adoption of AST.
-STP facilitators have recommended that additional time and resources are needed to improve the efficacy of STP [@mammenPuttingSchoolTravel2015], which highlights that long-term and sustained efforts driven at the policy level are required to address declining rates of AST.
 
@@
 Municipal representatives are perceived to be instrumental but the involvement of other stakeholder groups (e.g., busing consortia representatives and local residents) can be lacking [@buttazzoniSupportingActiveSchool2018].
-In Ontario, it is reasonable to say that AST has become a policy issue on the education and public health agendas, supported, albeit in a modest way, by financial contributions from the provincial government^[To put the CAD 2 million invested by the province in the Ontario Active School Travel program in perspective, a city such as Hamilton budgeted in excess of CAD 91 million on road maintenance and construction in 2016 alone; see: https://www.hamilton.ca/budget-finance/city-budgets/2016-tax-and-rate-budgets].
+In Ontario, it is reasonable to say that AST has become a policy issue on the education and public health agendas, supported, albeit in a modest way, by financial contributions from the provincial government.
 Still, the support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
-However, it is unknown to what degree the general public (i.e., local residents) has been exposed to messaging about AST.
 
@@
 For example, parents have been found to view mixed land use as conducive for driving, despite transport planners viewing neighbourhoods with mixed uses as key for encouraging more active travel [@buliungLivingJourneySchool2021].
-Therefore, stakeholders involved in STP must make conscious choices about the proposed solutions and potential benefits of AST that are communicated to parents and the general public to convey its importance as a policy issue and to facilitate adoption of AST.
-Publicly available content about AST needs to effectively engage multiple audiences on this policy issue, including parents, children, politicians, and school representatives.
-This information should reflect current knowledge from research on school travel, plus content specific to local factors that influence AST, so that the challenges of AST are adequately defined and the opportunities or solutions to address the problems are clear.
+Therefore, stakeholders involved in STP must make conscious choices about the proposed solutions and potential benefits of AST that are communicated to parents and the general public through publicly available content to convey its importance as a policy issue and to facilitate adoption of AST.
 
@@
 Issues that pertain to public health or wellbeing are often presented to the public through particular frames to influence perceptions or behaviours.
-As previously mentioned, a frame is a "central organizing idea or story line that provides meaning" to a public issue or phenomenon [@gamsonChangingCulture1987].
 Scholars in the field of political communications have proposed that communicators, such as the media or institutions, construct the narrative of a frame for policy positions or public issues in order to activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
@@
 Finally, the ideas that are communicated by a particular frame can be either positive or negative [@waygoodCO2ValenceFraming2018].
-There is evidence that negative framing may be more effective at motivating individuals to change transport modes to reduce CO2 emissions [@waygoodCO2ValenceFraming2018].
+There is evidence that negative framing may be more effective at motivating individuals, for example, to change transport modes to reduce CO2 emissions [@waygoodCO2ValenceFraming2018].
 
@@
 An obvious example over the past decade is the framing of climate change as a public health issue [e.g., @depouxCommunicatingClimateChange2017; @maibachReframingClimateChange2010; @weathersDevelopmentsFramingClimate2016] to increase public engagement and awareness of the issue.
-This framing has slowly advanced this issue on public policy agendas as public attention puts pressure on the policy stream to adopt frameworks for action.
+This framing has slowly advanced this issue on public policy agendas as public attention puts pressure on policy makers to adopt frameworks for action.
 For example, transport planners use different frames to guide the extent to which transport policies can be adapted to address climate change.
@@
 We assembled a collection of publicly available documents that were sourced online from the main stakeholder groups involved in STP initiatives in Ontario: i) school boards (public or Catholic and English-speaking only); ii) municipal governments; and iii) transportation consortia.
-The latter are a unique group of entities sanctioned by Ontario's Ministry of Education in Ontario 2006.
-Each consortium involves a collaboration between municipal regions and school boards; the consortium's objective is to deliver more efficient and timely transportation services to schools in each region.
-Non-profit organizations, police services, and advocacy groups are other stakeholders who often play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all initiatives across Ontario.
+The latter involve a collaboration between municipal regions and school boards to deliver more efficient and timely transportation services to schools in each region.
+Non-profit organizations, police services, and advocacy groups are other stakeholders who often play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all STP initiatives across Ontario.
 
@@
 Any pages relevant to these topics were manually downloaded.
-Next, we collected documents by searching municipal government and transportation consortia websites.
-These were identified based on geographic area (i.e., the municipalities and/or transportation consortia that are in the same geographic area of each school board).
+Next, we searched municipal government and transportation consortia websites.
+These were identified based on geographic area.
 Webpages related to active transport or school travel were manually downloaded.
@@
 
-The initial corpus of documents from STP stakeholder groups included 69 relevant webpages (i.e., one page or more).
-We refer to these as policy documents throughout the paper.
+The initial corpus of documents from STP stakeholder groups included 69 relevant webpages.
+We refer to these as policy+practice documents throughout the paper.
 It is important to note that school boards, municipalities, and transportation consortia may or may not publish information about their involvement in AST and STP efforts on their respective websites or in policy documents.
@@
 
-We conducted a search on Web of Science for scholarly papers on the topic of travel to school.
+We conducted a search on Web of Science for scholarly papers on the topic of school travel.
 We limited our search to the fields of public health, transportation, planning, urban studies, and geography.
-This initial corpus was curated by the authors to ensure that all documents were relevant; for example, some hits in our search were not full papers but conference reports, or they dealt with travel to school only peripherally.
+This initial corpus was curated by the authors to ensure that all documents were relevant.
 After this step, we assembled a collection of 227 journal articles for analysis.
@@
 A multi-step process was conducted to ensure that the analysis captured as much text as possible from both the policy documents (n = 64) and academic papers (n = 227).
-To begin, the webpages, which were manually downloaded in portable document format (PDF), were trimmed so that pages that only consisted of tables, figures, or references were removed.
-Many academic papers were in a two-column format, which is not ideal for conversion to `txt`.
-Two-column PDF documents were processed to extract the text in the correct sequence.
-Four academic papers did not join sufficiently and were taken out of the corpus due to the substantial time required to manually correct their inconsistencies.
-
-Next, we converted the trimmed PDF documents into `txt` files so that they could be imported for analysis in `R`.
-The next phase was to manually remove any remaining tables, figures, references, headers/footings, and captions that could not be trimmed.
-Manual corrections were also required for certain pages in academic papers that remained in two-column format after the conversion process.
-This typically occurred on pages that had a table or figure that disrupted the text.
-Finally, we reviewed all of the documents to remove hyphenation by line breaks and to keep hyphenated words together on the same line.
-Any ligatures (e.g., combinations of characters or letters that were not properly detected during the conversion process) were fixed.
-
-We also manually removed any extraneous material that did not pertain to AST specifically.
-For the academic papers, this included footnotes, references, acknowledgments, and conflict of interest statements.
-For the policy+practice documents, it included phone numbers, inserted links to other webpages, personal names, and content not specific to AST.
+Webpages were manually downloaded in portable document format (PDF) and trimmed so that pages that only consisted of tables, figures, or references were removed.
+After converting into `txt` files adn importing for analysis in `R`, we manually removed any remaining tables, figures, references, headers/footings, and captions that could not be trimmed.
+We also manually removed any extraneous material that did not pertain to AST specifically (e.g., references, footnotes, weblinks, etc.).
 In the final step, we removed all blank spaces, punctuation, capitalization, and numbers.
@@
 This method is practical for researchers working with large amounts of text because it replaces the manual coding of topics that would normally take place to analyze or summarize textual data [@jacobiQuantitativeAnalysisLarge2016].
-In the data pre-processing phase, we tokenize the text in the documents and create a document-term matrix so that it is in the correct format for analysis.
 We primarily use the following packages: `tidytext` [@R-tidytext], `topicmodels` [@R-topicmodels], `word2vec` [@R-word2vec], and `wordcloud` [@R-wordcloud] to examine text in the documents that were sourced for this project.
-These packages have functions for determining the frequency of specific words in each document or relationships (e.g., pairs of adjacent terms called bigrams) and correlations between words.
-Topic modelling is a popular method for analyzing text from social media platforms [@albalawiUsingTopicModeling2020] and news articles [@jacobiQuantitativeAnalysisLarge2016].
+
 We estimate latent Dirichlet allocation (LDA) models to classify both the STP and academic documents according to the topics that are contained within them.
-This method "treats each document as a mixture of topics, and each topic as a mixture of words" [@silgeTextMining2021].
 The model's output is "a set of topics consisting of clusters of words that co-occur in these documents according to certain patterns" [@jacobiQuantitativeAnalysisLarge2016].
 Researchers must then interpret the identified topics, as done after other methods of manual coding.
-We also compare the topics between the policy documents and the academic papers to interpret what is being communicated by STP stakeholders.
 We describe in more detail the functions and code in `R`  that we used.
@@
 Each corpus also has _safety_ and _traffic_ as common words which suggests that these are common concerns for parents.
-The word _physical_ is present in each corpus, but it's not clear what this refers to (e.g, _physical activity_, _physical health_, or the _physical environment_).
+The word _physical_ is present in each corpus, but it's not clear what this refers to (e.g, _physical activity_, or the _physical environment_).
 Furthermore, documents from STP stakeholder groups discuss _resources_, _information_, and _services_ about school travel.
-Unlike the academic papers, policy documents include the words _route_ or _routes_ as frequent terms.
-This could indicate the presence of "safe routes to school" in the policy corpus, as well as the role of STP stakeholder groups in identifying safe routes to school to share with parents or families.
+Unlike the academic papers, policy+practice documents include the words _route_ or _routes_ as frequent terms.
+This could indicate the role of STP stakeholder groups in identifying safe routes to school to share with parents or families.
 In the section below, the context in which these terms are used is explored further.
@@
 The prevalence of these terms is consistent with an academic focus on exploring the variables that influence mode choice.
-These words are absent from the list of common words in policy documents.
+These words are absent from the list of common words in policy+practice documents.
 Table \ref{tab:word-table} indicates that the academic corpus discusses a broader range of determinants of AST than the policy documents.
@@
 This suggests that although documents pertain to the subject of school travel, not all stakeholders across Ontario are disseminating information about AST.
-For example, a document may discuss active travel but not to school.
-Some documents present school travel options by bus but not by active modes.
-We manually searched the policy corpus and found that 48% of documents mention AST and 16% mention STP.
-This confirms that many municipalities, school boards, and transportation consortia do not promote AST through their webpages or indicate their involvement in the STP process.
+We manually searched the policy+practice corpus and found that 48% of documents mention AST and 16% mention STP.
 Instead, inclement weather and its impacts on busing is a common topic addressed in school board and transportation consortia documents.
@@
 ## 5.2. Bigrams and concordances
-
-Bigrams refer to a pair of consecutive words.
-Figures \ref{fig:city-visual}, \ref{fig:consortia-visual}, and \ref{fig:school-visual} show the bigrams that occur more than 5 times for each set of policy documents.
-These figures help to make further sense of the word frequencies reported above, and highlight the main ideas that are presented to the public in each of the policy corpora.
-The directional arrows indicate the arrangement of the words (e.g., active travel and not travel active) and the colour gradient of the arrows corresponds to the most frequently mentioned pairs (e.g., bigrams with darker arrows are found more often).
-
-Municipalities primarily discuss _physical activity_ (n = 53) and _public health_ (n = 19) in the context of AST.
-In addition, _travel planning_ (n = 19), _bike lanes_ (n = 16), and _safe routes_ (n = 14) are also identified, conceivably as either proposed solutions or built environment factors that support AST.
-Key issues related to transport such as _traffic safety_ (n = 10), _air quality_ (n = 9), and _greenhouse gases_ (n = 9) are conveyed to the public through these policy documents.
-It is not surprising to find this focus given that municipalities in Ontario are concerned about climate change and have increasingly looked to active travel to offset transport-related emissions in urban areas.
-
-Similar bigrams are found in school board documents: _travel planning_ (n = 33), _safe routes_ (n = 15), _physical activity_ (n = 10), and _public health_ (n = 10) are among the most common.
-Both municipalities and school boards in Ontario seem to emphasize what can be or has been done to improve AST (i.e., policy or planning changes), while outlining some of the benefits of AST at the individual- or community-level to potentially encourage behaviour change (i.e., physical activity for children or improved air quality).
-Unlike other STP stakeholders, school boards also consider _inclement weather_ (n = 24) and _bus cancellations_ (n = 13).
-Most likely this is because school boards are mandated to provide transportation to school in Ontario (typically by bus) and this information is presented alongside AST options.
-Finally, transportation consortia documents highlight topics such as _physical activity_ (n = 10), _pedestrian safety_ (n = 8), _crossing guards_ (n = 6), _travel planning_ (n = 6), and _walk zones_ (n = 6).
-Biking and cycling are notably absent from transportation consortia documents.
-Overall, the policy documents appear to convey an emphasis on the built environment, rather than household decision-making.
 
@@
 
-```{r city-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:city-visual}Most common bigrams found in the municipal and regional government documents."}
+```{r city-visual, include=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:city-visual}Most common bigrams found in the municipal and regional government documents."}
 ggraph(municipal_bigram_graph, layout = "fr") +
@@
 
-```{r consortia-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:consortia-visual}Most common bigrams found in the transportation consortia documents."}
+```{r consortia-visual, include=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:consortia-visual}Most common bigrams found in the transportation consortia documents."}
 ggraph(consortium_bigram_graph, layout = "fr") +
@@
 
-```{r school-visual, echo=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:school-visual}Most common bigrams found in the school board documents."}
+```{r school-visual, include=FALSE, fig.align = 'center', out.width = "1\\linewidth", fig.cap = "\\label{fig:school-visual}Most common bigrams found in the school board documents."}
 ggraph(school_bigram_graph, layout = "fr") +
@@
 
-We then combined all municipality, school board, and transportation consortia documents into one "policy+practice" corpus.
+Bigrams refer to a pair of consecutive words.
+We combined all municipality, school board, and transportation consortia documents into one "policy+practice" corpus.
 This enabled us to examine and visualize the most common bigrams found across all of the material in Ontario that was collected for this study.
 Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the policy+practice corpus.
-In addition to the bigrams already identified above, we also found _mental health_, _walk day_, and _green communities_ as common pairs of consecutive words.
+This figure highlights the main ideas that are presented to the public in each of the policy corpora.
+The directional arrows indicate the arrangement of the words (e.g., active travel and not travel active) and the colour gradient of the arrows corresponds to the most frequently mentioned pairs (e.g., bigrams with darker arrows are found in the corpus more often).
+
+STP stakeholders discuss _physical activity_ and _public health_ in the context of AST.
+In addition, _travel planning_, _bike lanes_, and _safe routes_ are also identified, conceivably as either proposed solutions or built environment factors that support AST.
+Key issues related to transport such as _traffic safety_, _air quality_, and _greenhouse gases_ are conveyed to the public through these policy documents.
+It is not surprising to find this focus given that municipalities in Ontario are concerned about climate change and have increasingly looked to active travel to offset transport-related emissions in urban areas.
+We also found _mental health_, _walk zone_, and _green communities_ as common pairs of consecutive words.
 _Green Communities Canada_ is a non-profit organization that has significantly supported AST initiatives through the Ontario Active School Travel program so the high frequency of this term in the policy+practice corpus is not surprising.
@@
 Next, we analyzed bigrams in the academic corpus separately to make comparisons with the policy+practice corpus.
-Figure \ref{fig:academic-visual} indicates that academic papers include several common bigrams that were also found in the policy documents including _physical activity_ (n = 1566), which is the top bigram, _traffic safety_ (n = 308), and _safe routes_ (n = 268).
+Figure \ref{fig:academic-visual} indicates that academic papers include several common bigrams that were also found in the policy documents including _physical activity_, which is the top bigram, _traffic safety_, and _safe routes_.
 However, many other factors are identified in the research literature that are not presented to the general public through policy documents.
-After _physical activity_, _built environment_ (n = 1175), _independent mobility_ (n = 774), and _urban form_ (n = 352) are the most frequent pairs of consecutive words.
-Academic papers also often discuss _distance home_ (n = 258), _car ownership_ (n = 254), _household income_ (n = 254), and _population density_ (n = 205), which are factors that have been found to influence AST.
-Many papers also investigate gender differences in AST given that _boys girls_ (n = 211) is another common bigram.
+Terms like _built environment_, _independent mobility_, and _urban form_ are other frequent pairs of consecutive words.
+Academic papers also often discuss _distance home_, _car ownership_, _household income_, and _population density_, which are factors that have been found to influence AST.
 Finally, the presence of _statistically significant_ among the top bigrams indicates that researchers often aim to identify associations using statistical measures.
@@
 
-We interpreted the most common bigrams from the policy+practice corpus (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholder groups focus on and communicate to the public about AST.
+We interpreted the most common bigrams from the policy+practice corpus (see Figure \ref{fig:policy-visual}) as the main ideas that STP stakeholder groups focus on and communicate to the public about AST.
 We then examined the context of these key ideas by extracting words-in-context from the corpora.
@@
 text_tbl <- data.frame(
-  Terms = c("Air Quality", "Benefit", "Walking School Bus", "Community", "Emissions", "Health", "Lanes", "Mental Health", "Physical Health"),
+  Terms = c("Walking School Bus", "Community", "Emissions", "Health", "Mental Health"),
   Stakeholder = c("School Board", "Municipality", "School Board", "School Board", "Consortia", "Municipality", "Municipality", "Municipality", "Municipality"),
   Context = c(
-    "Active transportation [...] improves air quality.",
-    "Stronger bones and muscles, improved self-esteem and sense of well-being while reducing stress and risk of chronic disease all benefit those who use active transportation.",
     "While taking part in a walking school bus, your child will enjoy seeing friends on the way to school.
@@
 This is linked with lower body mass index and improved cardiovascular health.",
-    "We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments.",
-    "Active and Sustainable School Travel (ASST) not only improves physical and mental health but contributes to a healthier environment and safer streets.",
-    "Encouraging Active Transportation promotes physical health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.")
+    "Active and Sustainable School Travel (ASST) not only improves physical and mental health but contributes to a healthier environment and safer streets.")
 )
@@
 
-For the final part of our analysis, we conducted topic modelling to examine the different topics found in the policy and academic corpora.
-We focused on the policy/practice corpus, instead of assessing the municipal, school, and consortia documents separately, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario.
-We then estimated Latent Dirichlet Allocation (LDA) models for each corpus.
+For the final part of our analysis, we conducted topic modelling to examine the different topics found in the policy+practice and academic corpora.
+We estimated Latent Dirichlet Allocation (LDA) models for each corpus.
 Parameter tuning suggests that the policy+practice corpus has between 9 and 13 topics and the academic corpus has between 17 and 25 topics.
@@
 We experimented with the model by adjusting the number of topics and evaluating the output of terms in each topic.
-We found that there were 9 distinct topics that could be interpreted in the policy corpus and 11 topics in the academic corpus, after which there was too much overlap for the clusters to be meaningfully interpreted.
+We found that there were 9 distinct topics that could be interpreted in the policy+practice corpus and 11 topics in the academic corpus, after which there was too much overlap for the clusters to be meaningfully interpreted.
 Figures \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main terms that are associated with the topics found in each corpus.
@@
 The following topics were identified based on the clusters of words: (1) physical activity; (2) safe routes to school for active travel; (3) behaviours and attitudes; (4) bicycling; (5) walking; (6) built environment; (7) trip choice; (8) active school travel interventions; (9) parents; (10) children's independent mobility; and (11) public health and policies.
-This corpus reflects a broader range of topics than the policy/practice corpus.
+This corpus reflects a broader range of topics than the policy+practice corpus.
 
@@
 STP stakeholder groups appear to position walking, bicycling, or rolling to school as beneficial to individual health, via physical activity and improved mental health, and to the broader community through a reduction in traffic and vehicle emissions.
-Here, we present some examples from the policy documents that illustrate how the health and environmental frame is communicated:
-
-> _If you live in a walk zone, the best way to get to school is by walking or biking.
-This promotes physical activity, helps the environment and minimizes traffic around schools during busy times._ (City of Barrie)
+Here, we present an example that illustrates how the health and environmental frame is communicated:
 
@@
 
-> _The WCDSB supports active transportation as the preferred method of transportation to school because it is a healthy choice that has proven links to greater student achievement._ (Waterloo Catholic District School Board)
-
 Furthermore, we found that policy documents make claims about the benefits of AST that are consistent with the findings of academic research and evaluation.
-
-> _For their health, safety, environment and community: Kids learn healthy habits and concentrate better in class; One less car (yours) reduces traffic and parking problems in school zones; Teach your kids about traffic safety; Start a walking school bus; your kids make friends in every grade, and that can prevent bullying._ (City of Guelph)
 
@@
 
-> _A way to make sure your child is safe while walking to school is with a 'walking school bus.' Here are some tips for a walking school bus: Invite families who live nearby to walk; Pick a route and take a test walk; Take side streets and paths that are less busy with traffic; Decide how often the group will walk together; Talk with your boss to adjust your day; Have fun!_ (City of Ottawa)
-
 > _Help your students get started on the right foot - encourage them to walk or bike to school when possible.
@@
 
-> _Want to boost your child’s mental and physical health?
-Ottawa Public Health, City of Ottawa, and OSTA have produced a tipsheet for parents about “active transportation” to school – fitting walking and wheeling into your daily routine._ (Ottawa-Carleton District School Board)
-
 Finally, both AST frames present solutions to encourage AST.
@@
 This approach addresses concerns about safety, physical activity, and the environment._ (City of Hamilton)
-
-> _Today, as more and more of our neighbourhoods are being retrofitted with new sidewalks and bike lanes, pedestrian crossovers, street lights, reduced speed limits and/or crossing guards, the walk or bike ride to and from school has never been easier, safer or healthier._  (Hamilton-Wentworth District Catholic School Board)
 
@@
 Children and parents are encouraged to adopt new travel behaviours.
-STP stakeholder groups identified different ways that parents could encourage or support their children to commute to school by using active modes.
-Some school boards and municipalities also shared resources such as walking tip sheets and guidance for starting a walking school bus.
-Other advice included dropping children off one or two blocks away from school so that they could walk or bike part of the trip.
+STP stakeholder groups identified different ways that parents could encourage or support their children to commute to school by using active modes (e.g., walking tip sheets, walking school buses, etc.).
 The general emphasis of this frame is communicating information that could change parental perceptions about the ease of their children using active modes to school, which may be seen by STP stakeholder groups as a "modifiable" factor [see @riaziCorrelatesChildrenIndependent2019].
@@
 
-We found that the proposed solutions in the secondary frame to increase AST align with different levels of the socioecological model: 1) behaviour change from individuals or households making different travel decisions; 2) policies like STP that create resources for AST; and 3) engineering solutions like bicycle lanes.
+We found that the proposed solutions in the secondary frame to increase AST align with different levels of the SEM: 1) behaviour change from households making different travel decisions; 2) policies that create resources for AST; and 3) engineering solutions like bicycle lanes.
 This reflects findings from the AST literature that a range of solutions are needed to address different factors that influence AST [_inter alia, see_ @mitraIndependentMobilityMode2013; @panterAttitudesSocialSupport2010].
-The recognition of engineering changes may reflect the strong engagement of the "policy stream" [@kingdonAgendasAlternativesPublic1984] since engineering staff and municipal representatives are common STP stakeholders in Canada [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015], as well as the evidence that the built environment influences mode choice to school.
+The recognition of engineering changes may reflect the strong engagement of engineering staff and municipal representatives in the Canadian STP process [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015], as well as the evidence that the built environment influences mode choice to school.
 However, it is beyond the scope of this paper to assess whether the proposed solutions are perceived to be sufficient by parents for increasing AST.
@@
 STP stakeholders should problematize the significant decline in AST that has occurred over recent decades in Canada and emphasize that this issue merits urgent behaviour change.
-A study investigating the influence of different valence framings of CO2 emissions on transport mode shift found that positive framing can be less effective than negative framing [@waygoodCO2ValenceFraming2018].
-A negative framing that challenges the social norm of driving could be more motivational to shift modes, which would be consistent with other findings [see @waygoodCO2ValenceFraming2018].
+A negative framing that challenges the social norm of driving could be more motivational to shift transport modes, which would be consistent with other findings [see @waygoodCO2ValenceFraming2018].
 Policy documents should make it clear that continued use of nonactive modes to school can deprive children of opportunities to increase physical activity and to gain health and social benefits.
@@
 
-Acknowledgments
-===================
-
-This research was completed using open software, and the authors wish to acknowledge the developers of the following `R` packages: `dplyr` [@R-dplyr], `ggraph` [@R-ggraph], `ggplot2` [@R-ggplot2], `igraph` [@R-igraph], `pdftools` [@R-pdftools], `readr` [@R-readr], `reshape2` [@R-reshape2], `stringr` [@R-stringr], `text2vec` [@R-text2vec], `textdata` [@R-textdata], `tidyr` [@R-tidyr], `tidytext` [@R-tidytext], `tm` [@R-tm], `tools` [@R-tools], `topicmodels` [@R-topicmodels], `widyr` [@R-widyr], `word2vec` [@R-word2vec], `wordcloud` [@R-wordcloud], `DiagrammeR` [@R-diagrammeR], and `kableextra` [@R-kableextra].
-
 References

### 2022-05-13 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Edits to reduce word count

@@
 
-Rates of walking and bicycling to school, commonly known as active school travel (AST), have been declining in Canada and the United States for decades [@rothmanDeclineActiveSchool2018].
-However, the appetite for AST may be high in many Canadian communities.
-For instance, in a study conducted in Toronto, Ontario, 40% of children who were driven to school stated they would like to travel by bicycle instead [@laroucheRatherBikeSchool2016].
-Another study based in London, Ontario, reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012].
-From a public health perspective, increasing the use of active modes to school represents a major opportunity to improve children's health and wellbeing.
-
-The Government of Ontario, in Canada, has striven to promote this trend, and created a fund in 2017 to support communities across the province to develop AST initiatives.
-Green Communities Canada runs the program, called _Ontario Active School Travel_ [@GreenCommunities2016].
-As of December 2021, OAST has awarded over CAD 2 million and provided resources to over 25 projects across Ontario.
-Many communities implemented school travel planning (STP) [see @GreenCommunitiesProjects].
-In this context, STP is a popular "school-specific" intervention led by a facilitator who brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014].
-The five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities that make AST safer and more convenient: 1) setup of the program; 2) data collection and problem identification; 3) action planning; 4) implementation; 5) monitoring and evaluation [@buliungSchoolTravelPlanning2011; @langUnderstandingModalChoice2011].
-
-How AST is framed by STP stakeholders to a target audience, like parents or the general public, may raise awareness of the issue and influence how walking and bicycling to school are perceived.
+Walking and bicycling to school, commonly known as active school travel (AST), have declined in North America for decades [@rothmanDeclineActiveSchool2018], but the appetite for these modes is beginning to rise in many Canadian communities.
+For instance, research in Toronto, Ontario found that 40% of children who were driven to school would like to travel by bicycle instead [@laroucheRatherBikeSchool2016].
+Another study in London, Ontario, reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012].
+From a public health perspective, increasing active travel to school represents a major opportunity to improve children's health and wellbeing.
+
+To promote this trend, in 2017 the Government of Ontario began to support communities develop AST initiatives through a program called _Ontario Active School Travel_ (OAST).
+By 2021, the program, run by Green Communities Canada had awarded over CAD 2 million and provided resources to over 25 projects across Ontario [@GreenCommunities2016].
+A popular intervention in many communities is school travel planning (STP) [see @GreenCommunitiesProjects].
+In this context, STPs are "school-specific" interventions led by a facilitator who works with a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014].
+The five-step process involves identifying barriers to AST and implementing solutions or activities to make AST safer and more convenient: 1) setup of the program; 2) data collection and problem identification; 3) action planning; 4) implementation; 5) monitoring and evaluation [@buliungSchoolTravelPlanning2011; @langUnderstandingModalChoice2011].
+
+Framing AST by STP stakeholders to a target audience (e.g., parents or the general public) can raise awareness of the relevant issues and influence how active travel to school is perceived.
 Gamson and Modigliani [-@gamsonChangingCulture1987] define a frame as a “central organizing idea or story line that provides meaning” to a particular phenomenon.
 A frame can enable individuals "to locate, perceive, identify, and label" information pertaining to various dimensions of an issue [@goffmanFrameAnalysisEssay1974].
-Therefore, stakeholders involved in STP efforts can play a role in shaping public perception about AST in such a way that it attracts greater attention and is recognized as a "problem" that needs to be addressed through behaviour change or new policies.
-
-After significant investment of human and financial resources to boost rates of AST in Ontario over the past few years, we ask this central question: How is AST framed to the public?
+Therefore, stakeholders involved in STP efforts can play a role in shaping public perception about AST to attract greater attention and recognition as a "problem" that needs to be addressed through behaviour change or new policies.
+
+After significant investment of human and financial resources to boost rates of AST in Ontario over the past few years, in this paper we ask this central question: How is AST framed to the public in Ontario?
 The following questions are subsidiary and help us address this main question: What benefits of AST are communicated to the public?
-What solutions are proposed to increase rates of AST?
-
-In this paper, we use natural language processing to examine how three STP stakeholder groups in Ontario (municipalities, school boards, and transportation consortia) frame the issue of AST.
-We assembled a corpus of texts from public sources that present information for the general public or parents who are interested in AST.
+What solutions are proposed to increase AST?
+
+We approach this question by means of natural language processing, and examine how three STP stakeholder groups in Ontario (municipalities, school boards, and transportation consortia) frame AST.
+We assemble a corpus of texts from public sources that present information for the general public or parents who are interested in AST.
 We examine word frequency, bigrams, and concordances in these selected documents, and also identify key topics presented by each stakeholder group.
-We then compare the findings from these documents to a selection of studies on AST and explore the extent to which there is concordance between the literature on AST and materials shared with the public.
-
-2. Literature Review
+We then compare the findings from these documents to a selection of studies on AST and explore the extent to which there is concordance between the scholarly literature on AST and materials shared with the public.
+
+2. Literature Review: AST
 ======================
 
-## 2.1. Benefits of active school travel
-
-The desire to increase AST in Canada is certainly warranted - there is compelling evidence of the physical and mental health benefits that children who actively commute to school attain.
+The desire to increase AST in Canada is warranted given its potential physical and mental health benefits.
 Faulkner et al.
 [-@faulknerActiveSchoolTransport2009] concluded from their systematic review that children who travel on foot or by bicycle to school generally have higher levels of physical activity than their peers who are driven to school.
-However, Schoeppe et al.
-[-@schoeppeAssociationsChildrenActive2015] reported no association between AST and physical activity in their cross-sectional study.
-This relationship could be dose-dependent, meaning that children would have to travel longer distances to accumulate physical activity.
+This relationship could be dose-dependent, and contingent on sufficiently long trips to school to accumulate physical activity.
 A walking distance of 1000-1600 metres to school has been found to contribute to overall levels of physical activity for boys [@faulknerSchoolTravelChildren2013].
@@
 
-More recently, the literature has explored the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020].
+More recently, the link between transport and children's wellbeing has attracted interest too [@waygoodTransportChildrenWellbeing2020].
 Being driven to school reduces community interactions for children, which may negatively impact their social wellbeing [@waygoodChildrenTravelIncidental2015].
-In contrast, walking and bicycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021] and increase positive emotions that contribute to wellbeing [@ramanathanHappinessMotionEmotions2014a].
-This is something that children seem to value [@zwertsHowChildrenView2010].
+In contrast, walking and bicycling give children opportunities to socialize [@michailChildrenExperiencesTheir2021] and increase positive emotions that contribute to wellbeing [@ramanathanHappinessMotionEmotions2014a], a feeling that children seem to value [@zwertsHowChildrenView2010].
 AST can also provide opportunities for children to engage with natural environments [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015].
 
-## 2.2. Factors that influence active school travel and mode choice
-
 Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behaviour is understood within the context of household, social, neighbourhood, and policy environments.
-Th SEM helps to identify multiple determinants that need to be addressed by school-based interventions to increase AST, with the consensus being that interventions should target multiple levels [@mitraIndependentMobilityMode2013].
+The SEM helps to identify multiple determinants that need to be addressed by school-based interventions to increase AST, with the consensus being that interventions should target multiple levels [@mitraIndependentMobilityMode2013].
 Rather than describing an extensive list of factors that influence AST and mode choice in Canada [e.g., @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], we discuss a few potentially modifiable determinants that may be targeted for change through STP.
@@
 
-## 2.3. School travel planning in Canada
+3. School travel planning in Canada and relevance of framing analysis
+======================
 
 School travel planning (STP) has been implemented in Canada since at least the late 2000s.
-Within the STP process, facilitators generally establish multi-sector committees which intervene at the participating school through a range of activities related to the 4E's consisting of _education_ strategies, _encouragement_ through in-person events or programs, _engineering_ improvements to or around the school site, and _enforcement_ of traffic speeds around schools [@langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
-Following the first large-scale evaluation of STP as an intervention in Canada, AST rates increased across all schools and 14% of parents reported a perceived reduction in traffic outside the school [@buliungSchoolTravelPlanning2011].
-Assessments of the efficacy of STP [@buttazzoniPromotingActiveSchool2019; @mammenActiveSchoolTravel2014] indicate that it has the potential to encourage behaviour change and adoption of AST.
-
-How AST is framed seems particularly important to shift parental attitudes and perceptions, given their reported influence on children's travel mode to school.
-STP activities heavily focus on education or encouragement [@buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014; @buttazzoniSupportingActiveSchool2018], but parents may not always be receptive to the goals of STP and may be resistant to behaviour change [@buttazzoniSupportingActiveSchool2018].
-Parents have been found to express different understandings, language, and perceptions than planners of how the built environment can influence school travel [@buliungLivingJourneySchool2021].
-This is also true when it comes to other factors like convenience of different modes to school [@langUnderstandingModalChoice2011].
-STP stakeholders must pay special attention to parents' understanding of the decline of AST as a problem, which may affect their receptivity to proposed solutions.
-
-The “central organizing idea or story line" of AST, to apply the definition of framing from Gamson and Modigliani [-@gamsonChangingCulture1987], could also affect broader support in the community.
-Municipal representatives are perceived to be instrumental but the involvement of other stakeholder groups (e.g., busing consortia representatives and local residents) can be lacking [@buttazzoniSupportingActiveSchool2018].
-In Ontario, it is reasonable to say that AST has become a policy issue on the education and public health agendas, supported, albeit in a modest way, by financial contributions from the provincial government.
-Still, the support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
-
-The success of STP interventions would likely depend on parental judgments of factors that are related to school travel, as well as support from key policy makers.
-For example, parents have been found to view mixed land use as conducive for driving, despite transport planners viewing neighbourhoods with mixed uses as key for encouraging more active travel [@buliungLivingJourneySchool2021].
-Therefore, stakeholders involved in STP must make conscious choices about the proposed solutions and potential benefits of AST that are communicated to parents and the general public through publicly available content to convey its importance as a policy issue and to facilitate adoption of AST.
-
-## 2.4. Framing Analysis
-
-Issues that pertain to public health or wellbeing are often presented to the public through particular frames to influence perceptions or behaviours.
+Within the STP process, facilitators establish multi-sector committees which intervene at the participating school through a range of activities consisting of _[E]ducation_ strategies, _[E]ncouragement_ through in-person events or programs, _[E]ngineering_ improvements to or around the school site, and _[E]nforcement_ of traffic speeds around schools [or 4Es, @langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
+Following the first large-scale evaluation of STP as an intervention in Canada, AST rates increased and 14% of parents reported a perceived reduction in traffic outside the school [@buliungSchoolTravelPlanning2011].
+Assessments of the efficacy of STP [@buttazzoniPromotingActiveSchool2019; @mammenActiveSchoolTravel2014] indicate its potential to encourage behaviour change and adoption of AST.
+
+By providing a "central organizing idea or story line" [@gamsonChangingCulture1987] framing of AST seems particularly important to shift parental attitudes and perceptions, given their reported influence on children's travel mode to school.
 Scholars in the field of political communications have proposed that communicators, such as the media or institutions, construct the narrative of a frame for policy positions or public issues in order to activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
@@
 
-Framing of issues is an important step in developing health policy.
-An obvious example over the past decade is the framing of climate change as a public health issue [e.g., @depouxCommunicatingClimateChange2017; @maibachReframingClimateChange2010; @weathersDevelopmentsFramingClimate2016] to increase public engagement and awareness of the issue.
-This framing has slowly advanced this issue on public policy agendas as public attention puts pressure on policy makers to adopt frameworks for action.
-For example, transport planners use different frames to guide the extent to which transport policies can be adapted to address climate change.
-In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review the representation of issues such as mobility and social exclusion in municipal policies from four western Canadian cities under the current circumstances of climate change.
-The authors found four primary frames: “The Growing City”, “If You Build It, They Will Come”, “Better City for All”, and a “the Resilient City” [@reynardGrowthResilienceHow2021].
-Each frame presented the nature, opportunities, and challenges of climate change in different ways which set the stage for the types of mitigation and adaptation strategies that cities were proposing to address this issue.
-
-In a similar way, we hypothesize that STP stakeholder groups in Ontario have framed AST in particular ways to engage multiple audiences on this policy issue including parents, local residents, school representatives, and municipal representatives.
-These groups are likely identifying points of intervention and potential opportunities to build support for and encourage AST.
-
-3. Data
+Framing of AST could also affect broader support in the community.
+Municipal representatives are perceived to be instrumental but the involvement of other stakeholder groups (e.g., busing consortia representatives and local residents) can be lacking [@buttazzoniSupportingActiveSchool2018].
+In Ontario, it is reasonable to say that AST has become a policy issue on the education and public health agendas, supported, albeit in a modest way, by financial contributions from the provincial government.
+Still, the support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
+
+Since STP activities heavily focus on education or encouragement [@buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014; @buttazzoniSupportingActiveSchool2018], it is important that parents and communities are receptive to the goals of STP [@buttazzoniSupportingActiveSchool2018].
+Parents have been found to express different understandings, language, and perceptions than planners of how the built environment can influence school travel [@buliungLivingJourneySchool2021].
+This is also true when it comes to other factors like convenience of different modes to school [@langUnderstandingModalChoice2011].
+STP stakeholders must pay special attention to parents' understanding of the decline of AST as a problem, which may affect their receptivity to proposed solutions.
+
+The success of STP interventions would likely depend on parental judgments of factors that are related to school travel, as well as support from key policy makers.
+For example, parents have been found to view mixed land use as conducive for driving, despite transport planners viewing neighbourhoods with mixed uses as key for encouraging more active travel [@buliungLivingJourneySchool2021].
+Therefore, stakeholders involved in STP must make conscious choices about the proposed solutions and potential benefits of AST that are communicated to parents and the general public through publicly available content to convey its importance as a policy issue and to facilitate adoption of AST.
+
+4. Data
 ===============
 
-## 3.1. Data retrieval
-
-### 3.1.1. Policy documents
+## 4.1. Data retrieval
+
+### 4.1.1. Policy documents
 
@@
 The latter involve a collaboration between municipal regions and school boards to deliver more efficient and timely transportation services to schools in each region.
-Non-profit organizations, police services, and advocacy groups are other stakeholders who often play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all STP initiatives across Ontario.
+Non-profit organizations, police services, and advocacy groups are other stakeholders who often play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they do not consistently participate in STP initiatives in Ontario.
 
@@
 The websites of each school board were manually searched for pages related to school transport or travel.
-Any pages relevant to these topics were manually downloaded.
+Any pages relevant to these topics were downloaded.
 Next, we searched municipal government and transportation consortia websites.
 These were identified based on geographic area.
-Webpages related to active transport or school travel were manually downloaded.
-
-Webpages from STP stakeholder groups were included in our analysis if they were easy to find.
+Likewise, webpages related to active transport or school travel were downloaded.
+
+Webpages from STP stakeholder groups were included in our analysis if they were findable.
 This primary criterion was important since our analysis pertains to how such issues are framed to the general public.
-Thus, we included only webpages that were readily accessible, which we defined as requiring no more than 4 separate links from the initial Google search.
+Thus, we included only webpages that were readily accessible, which we defined as requiring no more than four links from the initial Google search to reach.
 
@@
 
-### 3.1.2. Academic papers
+### 4.1.2. Academic papers
 
@@
 This initial corpus was curated by the authors to ensure that all documents were relevant.
-After this step, we assembled a collection of 227 journal articles for analysis.
-
-## 3.2. Data cleaning
+After this step, 227 journal articles were readied for analysis.
+
+## 4.2. Data cleaning
 
@@
 Webpages were manually downloaded in portable document format (PDF) and trimmed so that pages that only consisted of tables, figures, or references were removed.
-After converting into `txt` files adn importing for analysis in `R`, we manually removed any remaining tables, figures, references, headers/footings, and captions that could not be trimmed.
+After converting into `txt` files and importing for analysis, we manually removed any remaining tables, figures, references, headers/footings, and captions that could not be trimmed.
 We also manually removed any extraneous material that did not pertain to AST specifically (e.g., references, footnotes, weblinks, etc.).
 In the final step, we removed all blank spaces, punctuation, capitalization, and numbers.
-English stop words, which are common words such as _and_ or _the_ as identified in a predetermined list by Feinerer and Hornik [-@R-tm] and other frequent terms in the documents like "school" and specific location names, were removed from the corpora.
-
-4. Methods
+English stop words (i.e., words such as _and_ or _the_) and other frequent terms in the documents like "school" and specific location names were removed from the corpora.
+
+5. Methods
 ===============
 
-## 4.1. Process of Framing Analysis
-
-We use topic modelling in `R` to conduct the framing analysis.
-Topic modelling is a machine learning technique used to analyze text to identify the language and concepts being communicated.
+## 5.1. Process of Framing Analysis
+
+We use topic modelling to analyze the documents retrieved.
+Topic modelling is a natural language processing technique used to analyze text to identify the language and concepts being communicated.
 This method is practical for researchers working with large amounts of text because it replaces the manual coding of topics that would normally take place to analyze or summarize textual data [@jacobiQuantitativeAnalysisLarge2016].
-We primarily use the following packages: `tidytext` [@R-tidytext], `topicmodels` [@R-topicmodels], `word2vec` [@R-word2vec], and `wordcloud` [@R-wordcloud] to examine text in the documents that were sourced for this project.
-
-We estimate latent Dirichlet allocation (LDA) models to classify both the STP and academic documents according to the topics that are contained within them.
+We primarily use the following software: `tidytext` [@R-tidytext], `topicmodels` [@R-topicmodels], `word2vec` [@R-word2vec], and `wordcloud` [@R-wordcloud].
+
+We estimate latent Dirichlet allocation (LDA) models to identify topics contained in both the STP and academic documents.
 The model's output is "a set of topics consisting of clusters of words that co-occur in these documents according to certain patterns" [@jacobiQuantitativeAnalysisLarge2016].
 Researchers must then interpret the identified topics, as done after other methods of manual coding.
-We describe in more detail the functions and code in `R`  that we used.
-
-## 4.3. Reproducibility
+
+## 5.3. Reproducibility
 
@@
 
-5. Results
+6. Results
 ===============
 
-## 5.1. Word and document frequency
+## 6.1. Word and document frequency
 
@@
 Examination of document frequency reveals terms that are not present in all policy documents.
-This suggests that although documents pertain to the subject of school travel, not all stakeholders across Ontario are disseminating information about AST.
+This suggests that although documents pertain to the subject of school travel, not all stakeholders across Ontario disseminate information about AST.
 We manually searched the policy+practice corpus and found that 48% of documents mention AST and 16% mention STP.
-Instead, inclement weather and its impacts on busing is a common topic addressed in school board and transportation consortia documents.
-
-## 5.2. Bigrams and concordances
+In contrast, inclement weather and its impacts on busing is a common topic addressed in school board and transportation consortia documents.
+
+## 6.2. Bigrams and concordances
 
@@
 Bigrams refer to a pair of consecutive words.
-We combined all municipality, school board, and transportation consortia documents into one "policy+practice" corpus.
-This enabled us to examine and visualize the most common bigrams found across all of the material in Ontario that was collected for this study.
+We combined all municipality, school board, and transportation consortia documents into the policy+practice.
 Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the policy+practice corpus.
@@
 
-## 5.3. Topic modelling
+## 6.3. Topic modelling
 
@@
 
-For the final part of our analysis, we conducted topic modelling to examine the different topics found in the policy+practice and academic corpora.
+We conducted topic modelling to examine the different topics found in the policy+practice and academic corpora.
 We estimated Latent Dirichlet Allocation (LDA) models for each corpus.
 Parameter tuning suggests that the policy+practice corpus has between 9 and 13 topics and the academic corpus has between 17 and 25 topics.
-After running the LDA model for the academic corpus, we realized the difficulty of interpreting a minimum of 17 topics based on the clusters of words that were identified.
+After running the LDA model for the academic corpus, we realized the difficulty of interpreting as many as 17 topics based on the clusters of words that were identified.
 We experimented with the model by adjusting the number of topics and evaluating the output of terms in each topic.
@@
 
-## 5.4. Frames
+## 6.4. Frames
 
@@
 
-6. Discussion
+7. Discussion
 ===============
 
-## 6.1. Current AST frames in Ontario
-
-Using natural language processing techniques, we analyzed how AST is framed in 69 documents available to the public on the websites of STP stakeholder groups in Ontario.
-Two main frames in the policy+practice corpus were identified based on the most common bigrams and topics from the LDA model.
-
-We found that AST is primarily framed to parents as beneficial to the health and wellbeing of children and to environmental sustainability.
+## 7.1. Current AST frames in Ontario
+
+Interpretation of the text assisted by natural language processing reveals that AST in Ontario is primarily framed to parents as beneficial to the health and wellbeing of children and to environmental sustainability.
 The policy documents reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance are less well-supported in the extant literature [@westmanTravelChildWellbeing2020].
@@
 
-## 6.2. Implications for school travel planning
+## 7.2. Implications for school travel planning
 
@@
 
-## 6.3. Limitations
+## 7.3. Limitations
 
@@
 
-7. Conclusion
+8. Conclusion
 ===============
 
-We used natural language processing techniques to examine how different school travel planning (STP) stakeholders in Ontario frame the issue of AST.
-STP stakeholders frame AST as an accessible and feasible way to travel to school that is valuable to children's health and to the environment.
+In this paper we examined how AST is framed in Ontario.
+Our analysis was supported by the use of natural language processing techniques, and reavealed that STP stakeholders frame AST as an accessible and feasible way to travel to school that is valuable to children's health and to the environment.
 STP stakeholders are communicating that this issue can be addressed through household behaviour change and policy solutions.

### 2022-09-07 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Edited for submission to TR-A Policy and Practice

@@
 author:
-  - name: Author 1
-    email: author1@example.com
-    affiliation: Some Department
+  - name: Elise Desjardins
+    email: desjae@mcmaster.ca
+    affiliation: McMaster University
+  - name: Jason Lam
+    email: lamj54@mcmaster.ca
+    affiliation: McMaster University
+  - name: Darcy Reynard 
+    email: reynard@ualberta.ca
+    affiliation: University of Alberta
+  - name: Damian Collins
+    email: damian.collins@ualberta.ca
+    affiliation: University of Alberta
+  - name: E. Owen D. Waygood
+    email: owen.waygood@polymtl.ca
+    affiliation: Polytechnique Montreal
+  - name: Antonio Paez
+    email: paezha@mcmaster.ca
+    affiliation: McMaster University
+    correspondingauthor: true
     footnote: 1
-  - name: Author 2
-    email: author2@example.com
-    affiliation: Some Department
-  - name: Author 3
-    email: author3@example.com
-    affiliation: Another University
-    footnote: 2
-  - name: Author 4
-    email: author4@example.com
-    affiliation: Some Institute
-    footnote: 2
-  - name: Author 5
-    email: author5@example.com
-    affiliation: Some University
-  - name: Author 6
-    email: author6@example.com
-    affiliation: Some Department
 address:
-  - code: Some Department
-    address: Department, Street, City, Province, Postal Code
-  - code: Another University
-    address: Department, Street, City, Province, Postal Code
-  - code: Some Institute
-    address: Street, City, Province, Postal Code
-  - code: Some University
-    address: Department, Street, City, Province, Postal Code
+  - code: McMaster University
+    address: School of Earth, Environment and Society, 1280 Main St. W, Hamilton, Ontario, Canada L8S 4K1
+  - code: University of Alberta
+    address: Department of Earth and Atmospheric Sciences, 1-26 Earth Sciences Building, Edmonton, Alberta, Canada T6G 2E3
+  - code: Polytechnique Montreal
+    address: Department of Civil, Geological and Mining Engineering, 2500, chemin de Polytechnique Montreal, Montreal, Quebec, Canada H3T 1J4
 footnote:
   - code: 1
-    text: "Corresponding Author"
-  - code: 2
-    text: "Equal contribution"
+    text: "Corresponding author."
 abstract: |
-
   Active school travel (AST) has been increasingly encouraged by various stakeholders in Ontario, Canada through efforts such as school travel planning.
@@
 Stakeholders promoting AST in Ontario should further problematize the decline of AST and challenge the norm of driving children to school.
-
-  Keywords: active school travel, school travel planning; natural language processing; framing analysis; education strategies
-
-journal: "Social Science & Medicine"
+keywords: 
+  - active school travel
+  - school travel planning
+  - natural language processing
+  - framing analysis
+journal: "Transportation Research Part A: Policy and Practice"
 date: "`r Sys.Date()`"
-bibliography: [bibliography.bib, packages.bib]
+classoption: preprint, 3p, authoryear
+bibliography: bibliography.bib
 linenumbers: false
-#numbersections: true
-csl: elsevier-harvard.csl
-output: rticles::elsevier_article
+numbersections: true
+# Use a CSL with `citation_package = "default"`
+# csl: https://www.zotero.org/styles/elsevier-harvard
+output: 
+  rticles::elsevier_article:
+    keep_tex: true
+    citation_package: natbib
 ---
@@
 
-1. Introduction
+Introduction
 ===============
@@
 
-2. Literature Review: AST
+Literature Review: AST
 ======================
@@
 
-3. School travel planning in Canada and relevance of framing analysis
+School travel planning in Canada and relevance of framing analysis
 ======================
@@
 
-4. Data
+Data
 ===============
 
-## 4.1. Data retrieval
-
-### 4.1.1. Policy documents
+## Data retrieval
+
+### Policy documents
 
@@
 
-### 4.1.2. Academic papers
+### Academic papers
 
@@
 
-## 4.2. Data cleaning
+## Data cleaning
 
@@
 
-5. Methods
+Methods
 ===============
 
-## 5.1. Process of Framing Analysis
+## Process of Framing Analysis
 
@@
 
-## 5.3. Reproducibility
+## Reproducibility
 
@@
 
-6. Results
+Results
 ===============
 
-## 6.1. Word and document frequency
+## Word and document frequency
 
@@
 
-## 6.2. Bigrams and concordances
+## Bigrams and concordances
 
@@
 text_tbl <- data.frame(
-  Terms = c("Walking School Bus", "Community", "Emissions", "Health", "Mental Health"),
-  Stakeholder = c("School Board", "Municipality", "School Board", "School Board", "Consortia", "Municipality", "Municipality", "Municipality", "Municipality"),
-  Context = c(
+  Terms = c("Air Quality", 
+            "Benefit", 
+            "Walking School Bus", 
+            "Community", 
+            "Emissions", 
+            "Health", 
+            "Lanes", 
+            "Mental Health", 
+            "Physical Health"),
+  Stakeholder = c("School Board", 
+                  "Municipality", 
+                  "School Board", 
+                  "School Board", 
+                  "Consortia", 
+                  "Municipality", 
+                  "Municipality", 
+                  "Municipality", 
+                  "Municipality"),
+  Context = c("Active transportation [...] improves air quality.",
+              "Stronger bones and muscles, improved self-esteem and sense of well-being while reducing stress and risk of chronic disease all benefit those who use active transportation.",
               "While taking part in a walking school bus, your child will enjoy seeing friends on the way to school.
@@
 This is linked with lower body mass index and improved cardiovascular health.",
-    "Active and Sustainable School Travel (ASST) not only improves physical and mental health but contributes to a healthier environment and safer streets.")
+              "We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments.",
+              "Active and Sustainable School Travel (ASST) not only improves physical and mental health but contributes to a healthier environment and safer streets.", 
+              "Encouraging Active Transportation promotes physical health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.")
 )
@@
 
-## 6.3. Topic modelling
+## Topic modelling
 
@@
   facet_wrap(~ topic, scales = "free") +
-  scale_y_reordered()
+  scale_y_reordered() +
+  theme(axis.text = element_text(size = 7),
+        axis.text.x = element_text(angle = 90))
 ```
@@
   facet_wrap(~ topic, scales = "free") +
-  scale_y_reordered()
+  scale_y_reordered() +
+  theme(axis.text.x = element_text(angle = 90))
 ```
@@
   facet_wrap(~ topic, scales = "free") +
-  scale_y_reordered()
+  scale_y_reordered() +
+  theme(axis.text = element_text(size = 6),
+        axis.text.x = element_text(angle = 90))
 ```
@@
 
-## 6.4. Frames
+## Frames
 
@@
 
-7. Discussion
+Discussion
 ===============
 
-## 7.1. Current AST frames in Ontario
+## Current AST frames in Ontario
 
@@
 
-## 7.2. Implications for school travel planning
+## Implications for school travel planning
 
@@
 
-## 7.3. Limitations
+## Limitations
 
@@
 
-8. Conclusion
+Conclusion
 ===============

### 2022-09-07 AST-Framing-Ontario/AST-Framing-Ontario.tex
Edited for submission to TR-A Policy and Practice

@@
-\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+\documentclass[preprint, 3p,
+authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
 %%% Begin My package additions %%%%%%%%%%%%%%%%%%%
+
 \usepackage[hyphens]{url}
 
-  \journal{Social Science \& Medicine} % Sets Journal name
+  \journal{Transportation Research Part A: Policy and
+Practice} % Sets Journal name
 
@@
 \IfFileExists{microtype.sty}{\usepackage{microtype}}{}
-\bibliographystyle{elsarticle-harv}
+\usepackage[]{natbib}
+\bibliographystyle{plainnat}
+
 \ifxetex
@@
             pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
-
-\setcounter{secnumdepth}{0}
+
+\setcounter{secnumdepth}{5}
 % Pandoc toggle for numbering sections (defaults to be off)
-\setcounter{secnumdepth}{0}
 
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% Pandoc citation processing
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
   \title{How is active school travel framed in Ontario, Canada?}
-    \author[Some Department]{Author 1\corref{1}}
-   \ead{author1@example.com} 
-    \author[Some Department]{Author 2}
-   \ead{author2@example.com} 
-    \author[Another University]{Author 3\corref{2}}
-   \ead{author3@example.com} 
-    \author[Some Institute]{Author 4\corref{2}}
-   \ead{author4@example.com} 
-    \author[Some University]{Author 5}
-   \ead{author5@example.com} 
-    \author[Some Department]{Author 6}
-   \ead{author6@example.com} 
-      \address[Some Department]{Department, Street, City, Province,
-Postal Code}
-    \address[Another University]{Department, Street, City, Province,
-Postal Code}
-    \address[Some Institute]{Street, City, Province, Postal Code}
-    \address[Some University]{Department, Street, City, Province, Postal
-Code}
-      \cortext[1]{Corresponding Author}
-    \cortext[2]{Equal contribution}
+    \author[McMaster University]{Elise Desjardins%
+  %
+  }
+   \ead{desjae@mcmaster.ca} 
+    \author[McMaster University]{Jason Lam%
+  %
+  }
+   \ead{lamj54@mcmaster.ca} 
+    \author[University of Alberta]{Darcy Reynard%
+  %
+  }
+   \ead{reynard@ualberta.ca} 
+    \author[University of Alberta]{Damian Collins%
+  %
+  }
+   \ead{damian.collins@ualberta.ca} 
+    \author[Polytechnique Montreal]{E. Owen D. Waygood%
+  %
+  }
+   \ead{owen.waygood@polymtl.ca} 
+    \author[McMaster University]{Antonio Paez%
+  \corref{cor1}%
+  \fnref{1}}
+   \ead{paezha@mcmaster.ca} 
+      \affiliation[McMaster University]{School of Earth, Environment and
+Society, 1280 Main St.~W, Hamilton, Ontario, Canada L8S 4K1}
+    \affiliation[University of Alberta]{Department of Earth and
+Atmospheric Sciences, 1-26 Earth Sciences Building, Edmonton, Alberta,
+Canada T6G 2E3}
+    \affiliation[Polytechnique Montreal]{Department of Civil, Geological
+and Mining Engineering, 2500, chemin de Polytechnique Montreal,
+Montreal, Quebec, Canada H3T 1J4}
+    \cortext[cor1]{Corresponding author}
+    \fntext[1]{Corresponding author.}
 
@@
   decline of AST and challenge the norm of driving children to school.
-
-  Keywords: active school travel, school travel planning; natural
-  language processing; framing analysis; education strategies
   \end{abstract}
+    \begin{keyword}
+    active school travel \sep school travel planning \sep natural
+language processing \sep 
+    framing analysis
+  \end{keyword}
 
@@
 \hypertarget{introduction}{%
-\section{1. Introduction}\label{introduction}}
-
-Rates of walking and bicycling to school, commonly known as active
-school travel (AST), have been declining in Canada and the United States
-for decades (Rothman et al., 2018). However, the appetite for AST may be
-high in many Canadian communities. For instance, in a study conducted in
-Toronto, Ontario, 40\% of children who were driven to school stated they
-would like to travel by bicycle instead (Larouche et al., 2016). The
-study also reported that less than 3\% of respondents actually cycled,
-despite the vast majority having access to a bicycle and living within a
-short and bikeable distance to school. Another study based in London,
-Ontario, reported similar findings with respect to children's preference
-for active travel (Larsen et al., 2012). From a public health
-perspective, increasing the use of active modes to school represents a
+\section{Introduction}\label{introduction}}
+
+Walking and bicycling to school, commonly known as active school travel
+(AST), have declined in North America for decades
+\citep{rothmanDeclineActiveSchool2018}, but the appetite for these modes
+is beginning to rise in many Canadian communities. For instance,
+research in Toronto, Ontario found that 40\% of children who were driven
+to school would like to travel by bicycle instead
+\citep{laroucheRatherBikeSchool2016}. Another study in London, Ontario,
+reported similar findings with respect to children's preference for
+active travel \citep{larsenRouteBasedAnalysisCapture2012}. From a public
+health perspective, increasing active travel to school represents a
 major opportunity to improve children's health and wellbeing.
 
-The Government of Ontario, in Canada, has striven to promote this trend,
-and created a fund in 2017 to support communities across the province to
-develop AST initiatives. Green Communities Canada runs the program,
-called \emph{Ontario Active School Travel} (G. C. Canada, 2020). As of
-December 2021, OAST has awarded over CAD 2 million and provided
-resources to over 25 projects across Ontario. Many communities
-implemented school travel planning (STP), along with encouraging
-activities like walking school buses and developed resources for schools
-and parents, among other actions (see Canada, 2021). In this context,
-STP is a popular ``school-specific'' intervention led by a facilitator
-who brings together a committee of stakeholders from diverse sectors
-including education, planning, transportation, and public health to
-develop action plans (Buliung et al., 2011; Mammen et al., 2014a). The
-five-step process involves identifying barriers to AST based on the
-local context and implementing approaches or activities that make AST
-safer and more convenient: 1) setup of the program; 2) data collection
-and problem identification; 3) action planning; 4) implementation; 5)
-monitoring and evaluation (Buliung et al., 2011; Lang et al., 2011).
-
-How AST is framed by STP stakeholders to a target audience, like parents
-or the general public, may raise awareness of the issue and influence
-how walking and bicycling to school are perceived. Gamson and Modigliani
-(1987) define a frame as a ``central organizing idea or story line that
-provides meaning'' to a particular phenomenon. A frame can enable
-individuals ``to locate, perceive, identify, and label'' information
-pertaining to various dimensions of an issue (Goffman, 1974). Therefore,
+To promote this trend, in 2017 the Government of Ontario began to
+support communities develop AST initiatives through a program called
+\emph{Ontario Active School Travel} (OAST). By 2021, the program, run by
+Green Communities Canada had awarded over CAD 2 million and provided
+resources to over 25 projects across Ontario
+\citep{GreenCommunities2016}. A popular intervention in many communities
+is school travel planning (STP) \citep[see][]{GreenCommunitiesProjects}.
+In this context, STPs are ``school-specific'' interventions led by a
+facilitator who works with a committee of stakeholders from diverse
+sectors including education, planning, transportation, and public health
+to develop action plans
+\citep{buliungSchoolTravelPlanning2011, mammenSchoolTravelPlanning2014}.
+The five-step process involves identifying barriers to AST and
+implementing solutions or activities to make AST safer and more
+convenient: 1) setup of the program; 2) data collection and problem
+identification; 3) action planning; 4) implementation; 5) monitoring and
+evaluation
+\citep{buliungSchoolTravelPlanning2011, langUnderstandingModalChoice2011}.
+
+Framing AST by STP stakeholders to a target audience (e.g., parents or
+the general public) can raise awareness of the relevant issues and
+influence how active travel to school is perceived. Gamson and
+Modigliani \citeyearpar{gamsonChangingCulture1987} define a frame as a
+``central organizing idea or story line that provides meaning'' to a
+particular phenomenon. A frame can enable individuals ``to locate,
+perceive, identify, and label'' information pertaining to various
+dimensions of an issue \citep{goffmanFrameAnalysisEssay1974}. Therefore,
 stakeholders involved in STP efforts can play a role in shaping public
-perception about AST in such a way that it attracts greater attention
-and is recognized as a ``problem'' that needs to be addressed through
-behaviour change or new policies.
+perception about AST to attract greater attention and recognition as a
+``problem'' that needs to be addressed through behaviour change or new
+policies.
 
 After significant investment of human and financial resources to boost
-rates of AST in Ontario over the past few years, we ask this central
-question: How is AST framed to the public? The following questions are
-subsidiary and help us address this main question: What benefits of AST
-are communicated to the public? What solutions are proposed to increase
-rates of AST?
-
-In this paper, we use natural language processing to examine how three
-STP stakeholder groups in Ontario (municipalities, school boards, and
-transportation consortia) frame the issue of AST. We assembled a corpus
-of texts from public sources that present information for the general
-public or parents who are interested in AST. We examine word frequency,
-bigrams, and concordances in these selected documents, and also identify
-key topics presented by each stakeholder group. We then compare the
-findings from these documents to a selection of studies on AST and
-explore the extent to which there is concordance between the literature
-on AST and materials shared with the public.
-
-\hypertarget{literature-review}{%
-\section{2. Literature Review}\label{literature-review}}
-
-\hypertarget{benefits-of-active-school-travel}{%
-\subsection{2.1. Benefits of active school
-travel}\label{benefits-of-active-school-travel}}
-
-There is value in communicating the benefits of AST to the public in
-order to convey the importance of this issue. The desire to increase AST
-in Canada is certainly warranted - there is compelling evidence of the
-physical and mental health benefits that children who actively commute
-to school attain. Faulkner et al. (2009) concluded from their systematic
-review that children who travel on foot or by bicycle to school
-generally have higher levels of physical activity than their peers who
-are driven to school. However, Schoeppe et al. (2015) reported no
-association between AST and physical activity in their cross-sectional
-study. This relationship could be dose-dependent, meaning that children
-would have to travel longer distances to accumulate physical activity. A
-walking distance of 1000-1600 metres to school has been found to
-contribute to overall levels of physical activity for boys (Faulkner et
-al., 2013). The daily routine of travelling to school can be a good
-opportunity for children to regularly build physical activity into their
-schedule (Mitra, 2013). Research has also shown that using active modes
-to school contributes to improve cardiovascular fitness (Børrestad et
-al., 2012).
-
-More recently, the literature has explored the link between transport
-and children's wellbeing (Waygood et al., 2020), with relevant
-applications to the study of travel satisfaction (van den Berg et al.,
-2020; Westman et al., 2017b). Being driven to school reduces community
-interactions for children, which may negatively impact their social
-wellbeing (Waygood and Friman, 2015). In contrast, walking and bicycling
-give children opportunities to socialize with friends or siblings
-(Michail et al., 2021) and increase positive emotions that contribute to
-wellbeing (Ramanathan et al., 2014). This is something that children
-seem to value (Zwerts et al., 2010) and that tracks with findings among
-university students (Páez and Whalen, 2010). More generally, social
-connections through travel appear to be important for wellbeing.
-Furthermore, AST can provide opportunities for children to engage with
-natural environments (Fusco et al., 2012; Romero, 2015).
-
-\hypertarget{factors-that-influence-active-school-travel-and-mode-choice}{%
-\subsection{2.2. Factors that influence active school travel and mode
-choice}\label{factors-that-influence-active-school-travel-and-mode-choice}}
+rates of AST in Ontario over the past few years, in this paper we ask
+this central question: How is AST framed to the public in Ontario? The
+following questions are subsidiary and help us address this main
+question: What benefits of AST are communicated to the public? What
+solutions are proposed to increase AST?
+
+We approach this question by means of natural language processing, and
+examine how three STP stakeholder groups in Ontario (municipalities,
+school boards, and transportation consortia) frame AST. We assemble a
+corpus of texts from public sources that present information for the
+general public or parents who are interested in AST. We examine word
+frequency, bigrams, and concordances in these selected documents, and
+also identify key topics presented by each stakeholder group. We then
+compare the findings from these documents to a selection of studies on
+AST and explore the extent to which there is concordance between the
+scholarly literature on AST and materials shared with the public.
+
+\hypertarget{literature-review-ast}{%
+\section{Literature Review: AST}\label{literature-review-ast}}
+
+The desire to increase AST in Canada is warranted given its potential
+physical and mental health benefits. Faulkner et al.
+\citeyearpar{faulknerActiveSchoolTransport2009} concluded from their
+systematic review that children who travel on foot or by bicycle to
+school generally have higher levels of physical activity than their
+peers who are driven to school. This relationship could be
+dose-dependent, and contingent on sufficiently long trips to school to
+accumulate physical activity. A walking distance of 1000-1600 metres to
+school has been found to contribute to overall levels of physical
+activity for boys \citep{faulknerSchoolTravelChildren2013}. The daily
+routine of travelling to school can be a good opportunity for children
+to regularly build physical activity into their schedule
+\citep{mitraIndependentMobilityMode2013}.
+
+More recently, the link between transport and children's wellbeing has
+attracted interest too \citep{waygoodTransportChildrenWellbeing2020}.
+Being driven to school reduces community interactions for children,
+which may negatively impact their social wellbeing
+\citep{waygoodChildrenTravelIncidental2015}. In contrast, walking and
+bicycling give children opportunities to socialize
+\citep{michailChildrenExperiencesTheir2021} and increase positive
+emotions that contribute to wellbeing
+\citep{ramanathanHappinessMotionEmotions2014a}, a feeling that children
+seem to value \citep{zwertsHowChildrenView2010}. AST can also provide
+opportunities for children to engage with natural environments
+\citep{fuscoUnderstandingChildrenPerceptions2012, romeroChildrenExperiencesEnjoyment2015}.
 
 Factors that influence AST have been presented and organized using a
-socio-ecological model (SEM) (Mitra, 2013) or systems model (Badland et
-al., 2016) whereby children's travel behaviour is understood within the
-context of household, social, neighbourhood, and policy environments.
-The SEM comes from the field of public health and is a useful framework
-for understanding complex health behaviours, such as walking and
-bicycling habits, This model helps to identify multiple determinants
-that need to be addressed by interventions to facilitate behaviour
-change. The consensus in the literature is that interventions should
-target multiple levels in order to increase levels of healthy and
-physically active modes of travel to school (Mitra, 2013). Rather than
-describing an extensive list of factors that influence AST and mode
-choice in Canada (e.g., Mammen et al., 2012; Mitra, 2013; Rothman et
-al., 2018; Wilson et al., 2018), we discuss a few potentially modifiable
-determinants that may be targeted for change through STP.
-
-At the individual level, age is often positively associated with AST
-(Mammen et al., 2012; Stark et al., 2018; Wilson et al., 2018). There is
-evidence that gender is a determinant of AST, and that boys are more
-likely to travel using active modes than girls, although this is not a
-strong or consistent finding (Rothman et al., 2018; Schoeppe et al.,
-2015). Children's mode choice to school is strongly influenced by their
+socio-ecological model (SEM) \citep{mitraIndependentMobilityMode2013} or
+systems model \citep{badlandDevelopmentSystemsModel2016} whereby
+children's travel behaviour is understood within the context of
+household, social, neighbourhood, and policy environments. The SEM helps
+to identify multiple determinants that need to be addressed by
+school-based interventions to increase AST, with the consensus being
+that interventions should target multiple levels
+\citep{mitraIndependentMobilityMode2013}. Rather than describing an
+extensive list of factors that influence AST and mode choice in Canada
+\citep[e.g.,][]{mammenUnderstandingDriveEscort2012, mitraIndependentMobilityMode2013, rothmanDeclineActiveSchool2018, wilsonUnderstandingChildParent2018},
+we discuss a few potentially modifiable determinants that may be
+targeted for change through STP.
+
+Children's mode choice to school is strongly influenced by their
 parents' travel behaviours and the complexity of their household's
-travel needs (Buliung et al., 2021), as well as daily parental support
-(Mah et al., 2017). This indicates that shifting parental perceptions
-and habits is important. Convenience and inclement weather have been
-cited by parents as barriers to AST (Buliung et al., 2011). Parental
-perceptions of the built or school environment (De Meester et al., 2014;
-Panter et al., 2010) and their children's skills (Faulkner et al., 2010;
-Mammen et al., 2012) also influence mode choice to school.
+travel needs \citep{buliungLivingJourneySchool2021}, as well as daily
+parental support \citep{mahDoesParentalSupport2017a}. This indicates
+that shifting parental perceptions and habits is important. Convenience
+and inclement weather have been cited by parents as barriers to AST
+\citep{buliungSchoolTravelPlanning2011}. Parental perceptions of the
+built or school environment
+\citep{demeesterParentalPerceivedNeighborhood2014, panterAttitudesSocialSupport2010}
+and their children's skills
+\citep{mammenUnderstandingDriveEscort2012, faulknerWhatQuickestEasiest2010}
+also influence mode choice to school.
 
 Distance between home and school is most negatively associated with AST
-(Ikeda et al., 2018; Mammen et al., 2012; Pont et al., 2009; Rothman et
-al., 2018) with less AST reported among children who have to travel
-farther to school - low density suburban development tends to increase
-the need for movement, and the reliance on motorized modes (Farber and
-Páez, 2011). Many studies have also found that the quality of the built
-environment along the route to school and around the school site (Ikeda
-et al., 2018; Rothman et al., 2021) and provision of active travel
-infrastructure (Chen et al., 2018; Pont et al., 2009) facilitate AST.
-Canadian youth report that they feel most safe bicycling on streets in
-their neighbourhood or that have low volumes of traffic (T. A. of
-Canada, 2020). Finally, concerns about traffic and strangers have been
-reported by parents who drive their children to school (Mammen et al.,
-2012), which highlights that the volume and speed of cars can be a
-concern or deterrent for AST.
-
-\hypertarget{school-travel-planning-in-canada}{%
-\subsection{2.3. School travel planning in
-Canada}\label{school-travel-planning-in-canada}}
+\citep{ikedaAssociationsChildrenActive2018, mammenUnderstandingDriveEscort2012, pontEnvironmentalCorrelatesChildren2009, rothmanDeclineActiveSchool2018}
+with less AST reported among children who have to travel farther to
+school. Many studies have also found that the quality of the built
+environment along the route to school and around the school site
+\citep{ikedaAssociationsChildrenActive2018, rothmanActiveSchoolTransportation2021}
+and provision of active travel infrastructure
+\citep{chenPromotingActiveStudent2018, pontEnvironmentalCorrelatesChildren2009}
+facilitate AST. Canadian youth report that they feel most safe bicycling
+on streets in their neighbourhood or that have low volumes of traffic
+\citep{TACbikeinfra2020}. Finally, concerns about traffic and strangers
+have been reported by parents who drive their children to school
+\citep{mammenUnderstandingDriveEscort2012}, which highlights that the
+volume and speed of cars can be a concern or deterrent for AST.
+
+\hypertarget{school-travel-planning-in-canada-and-relevance-of-framing-analysis}{%
+\section{School travel planning in Canada and relevance of framing
+analysis}\label{school-travel-planning-in-canada-and-relevance-of-framing-analysis}}
 
 School travel planning (STP) has been implemented in Canada since at
-least the late 2000s. Within the STP process, facilitators generally
-establish multi-sector committees which intervene at the participating
-school through a range of activities related to the 4E's consisting of
-\emph{education} strategies, \emph{encouragement} through in-person
-events or programs, \emph{engineering} improvements to or around the
-school site, and \emph{enforcement} of traffic speeds around schools
-(Lang et al., 2011; Mammen et al., 2014b). The first large-scale
-evaluation of STP as an intervention in Canada took place at twelve
-schools across the country, including four in Ontario, using parental
-surveys to measure changes in travel behaviour and perceptions (Buliung
-et al., 2011). Following the intervention, active travel rates increased
-across all schools and 14\% of parents reported a perceived reduction in
-traffic outside the school (Buliung et al., 2011). Assessments of the
-efficacy of STP (Buttazzoni et al., 2019; Mammen et al., 2014b) indicate
-that it has the potential to encourage behaviour change and adoption of
-AST. STP facilitators have recommended that additional time and
-resources are needed to improve the efficacy of STP (Mammen et al.,
-2015), which highlights that long-term and sustained efforts driven at
-the policy level are required to address declining rates of AST.
-
-How AST is framed seems particularly important to shift parental
-attitudes and perceptions, given their reported influence on children's
-travel mode to school. STP activities heavily focus on education or
-encouragement (Buliung et al., 2011; Buttazzoni et al., 2018; Mammen et
-al., 2014b), but parents may not always be receptive to the goals of STP
-and may be resistant to behaviour change (Buttazzoni et al., 2018).
-Parents have been found to express different understandings, language,
-and perceptions than planners of how the built environment can influence
-school travel (Buliung et al., 2021). This is also true when it comes to
-other factors like convenience of different modes to school (Lang et
-al., 2011). STP stakeholders must pay special attention to parents'
-understanding of the decline of AST as a problem, which may affect their
-receptivity to proposed solutions.
-
-The ``central organizing idea or story line'' of AST, to apply the
-definition of framing from Gamson and Modigliani (1987), could also
-affect broader support in the community. Municipal representatives are
-perceived to be instrumental but the involvement of other stakeholder
-groups (e.g., busing consortia representatives and local residents) can
-be lacking (Buttazzoni et al., 2018). In Ontario, it is reasonable to
-say that AST has become a policy issue on the education and public
-health agendas, supported, albeit in a modest way, by financial
-contributions from the provincial government\footnote{To put the CAD 2
-  million invested by the province in the Ontario Active School Travel
-  program in perspective, a city such as Hamilton budgeted in excess of
-  CAD 91 million on road maintenance and construction in 2016 alone;
-  see:
-  https://www.hamilton.ca/budget-finance/city-budgets/2016-tax-and-rate-budgets}.
-Still, the support from a range of municipal representatives (see
-Buttazzoni et al., 2018; Mammen et al., 2015) demonstrates that the AST
-issue is on the political agenda. However, it is unknown to what degree
-the general public (i.e., local residents) has been exposed to messaging
-about AST.
+least the late 2000s. Within the STP process, facilitators establish
+multi-sector committees which intervene at the participating school
+through a range of activities consisting of \emph{{[}E{]}ducation}
+strategies, \emph{{[}E{]}ncouragement} through in-person events or
+programs, \emph{{[}E{]}ngineering} improvements to or around the school
+site, and \emph{{[}E{]}nforcement} of traffic speeds around schools
+\citep[or
+4Es,][]{langUnderstandingModalChoice2011, mammenActiveSchoolTravel2014}.
+Following the first large-scale evaluation of STP as an intervention in
+Canada, AST rates increased and 14\% of parents reported a perceived
+reduction in traffic outside the school
+\citep{buliungSchoolTravelPlanning2011}. Assessments of the efficacy of
+STP
+\citep{buttazzoniPromotingActiveSchool2019, mammenActiveSchoolTravel2014}
+indicate its potential to encourage behaviour change and adoption of
+AST.
+
+By providing a ``central organizing idea or story line''
+\citep{gamsonChangingCulture1987} framing of AST seems particularly
+important to shift parental attitudes and perceptions, given their
+reported influence on children's travel mode to school. Scholars in the
+field of political communications have proposed that communicators, such
+as the media or institutions, construct the narrative of a frame for
+policy positions or public issues in order to activate or restrict a
+particular response in the intended audience
+\citep{panFramingAnalysisApproach1993}. Organized groups of stakeholders
+can employ similar methods to attract attention to particular issues.
+Framing can be used to position existing solutions as suitable to
+address particular issues \citep{mahFramecriticalPolicyAnalysis2014},
+which may prevent the public from being aware of other policy approaches
+that challenge the status quo. The way policy issues are framed is
+ultimately important to understand because it plays a role in either
+altering or preserving the existing social perceptions. Finally, the
+ideas that are communicated by a particular frame can be either positive
+or negative \citep{waygoodCO2ValenceFraming2018}. There is evidence that
+negative framing may be more effective at motivating individuals, for
+example, to change transport modes to reduce CO2 emissions
+\citep{waygoodCO2ValenceFraming2018}.
+
+Framing of AST could also affect broader support in the community.
+Municipal representatives are perceived to be instrumental but the
+involvement of other stakeholder groups (e.g., busing consortia
+representatives and local residents) can be lacking
+\citep{buttazzoniSupportingActiveSchool2018}. In Ontario, it is
+reasonable to say that AST has become a policy issue on the education
+and public health agendas, supported, albeit in a modest way, by
+financial contributions from the provincial government. Still, the
+support from a range of municipal representatives
+\citep[see][]{buttazzoniSupportingActiveSchool2018, mammenPuttingSchoolTravel2015}
+demonstrates that the AST issue is on the political agenda.
+
+Since STP activities heavily focus on education or encouragement
+\citep{buliungSchoolTravelPlanning2011, mammenActiveSchoolTravel2014, buttazzoniSupportingActiveSchool2018},
+it is important that parents and communities are receptive to the goals
+of STP \citep{buttazzoniSupportingActiveSchool2018}. Parents have been
+found to express different understandings, language, and perceptions
+than planners of how the built environment can influence school travel
+\citep{buliungLivingJourneySchool2021}. This is also true when it comes
+to other factors like convenience of different modes to school
+\citep{langUnderstandingModalChoice2011}. STP stakeholders must pay
+special attention to parents' understanding of the decline of AST as a
+problem, which may affect their receptivity to proposed solutions.
 
@@
 viewing neighbourhoods with mixed uses as key for encouraging more
-active travel (Buliung et al., 2021). Therefore, stakeholders involved
-in STP must make conscious choices about the proposed solutions and
-potential benefits of AST that are communicated to parents and the
-general public to convey its importance as a policy issue and to
-facilitate adoption of AST. Publicly available content about AST needs
-to effectively engage multiple audiences on this policy issue, including
-parents, children, politicians, and school representatives. This
-information should reflect current knowledge from research on school
-travel, plus content specific to local factors that influence AST, so
-that the challenges of AST are adequately defined and the opportunities
-or solutions to address the problems are clear.
-
-\hypertarget{framing-analysis}{%
-\subsection{2.4. Framing Analysis}\label{framing-analysis}}
-
-Issues that pertain to public health or wellbeing are often presented to
-the public through particular frames to influence perceptions or
-behaviours. As previously mentioned, a frame is a ``central organizing
-idea or story line that provides meaning'' to a public issue or
-phenomenon (Gamson and Modigliani, 1987). Scholars in the field of
-political communications have proposed that communicators, such as the
-media or institutions, construct the narrative of a frame for policy
-positions or public issues in order to activate or restrict a particular
-response in the intended audience (Pan and Kosicki, 1993). Organized
-groups of stakeholders can employ similar methods to attract attention
-to particular issues. Framing can be used to position existing solutions
-as suitable to address particular issues (Mah et al., 2014), which may
-prevent the public from being aware of other policy approaches that
-challenge the status quo. The way policy issues are framed is ultimately
-important to understand because it plays a role in either altering or
-preserving the existing social perceptions. Finally, the ideas that are
-communicated by a particular frame can be either positive or negative
-(Waygood and Avineri, 2018). There is evidence that negative framing may
-be more effective at motivating individuals to change transport modes to
-reduce CO2 emissions (Waygood and Avineri, 2018).
-
-Framing of issues is an important step in developing health policy. An
-obvious example over the past decade is the framing of climate change as
-a public health issue (e.g., Depoux et al., 2017; Maibach et al., 2010;
-Weathers and Kendall, 2016) to increase public engagement and awareness
-of the issue. This framing has slowly advanced this issue on public
-policy agendas as public attention puts pressure on the policy stream to
-adopt frameworks for action. For example, transport planners use
-different frames to guide the extent to which transport policies can be
-adapted to address climate change. In a recent paper (Reynard et al.,
-2021), framing analysis was applied to review the representation of
-issues such as mobility and social exclusion in municipal policies from
-four western Canadian cities under the current circumstances of climate
-change. The authors found four primary frames: ``The Growing City,''
-``If You Build It, They Will Come,'' ``Better City for All,'' and a
-``the Resilient City'' (Reynard et al., 2021). Each frame presented the
-nature, opportunities, and challenges of climate change in different
-ways which set the stage for the types of mitigation and adaptation
-strategies that cities were proposing to address this issue.
-
-In a similar way, we hypothesize that STP stakeholder groups in Ontario
-have framed AST in particular ways to engage multiple audiences on this
-policy issue including parents, local residents, school representatives,
-and municipal representatives. These groups are likely identifying
-points of intervention and potential opportunities to build support for
-and encourage AST.
+active travel \citep{buliungLivingJourneySchool2021}. Therefore,
+stakeholders involved in STP must make conscious choices about the
+proposed solutions and potential benefits of AST that are communicated
+to parents and the general public through publicly available content to
+convey its importance as a policy issue and to facilitate adoption of
+AST.
 
 \hypertarget{data}{%
-\section{3. Data}\label{data}}
+\section{Data}\label{data}}
 
 \hypertarget{data-retrieval}{%
-\subsection{3.1. Data retrieval}\label{data-retrieval}}
+\subsection{Data retrieval}\label{data-retrieval}}
 
 \hypertarget{policy-documents}{%
-\subsubsection{3.1.1. Policy documents}\label{policy-documents}}
+\subsubsection{Policy documents}\label{policy-documents}}
 
@@
 English-speaking only); ii) municipal governments; and iii)
-transportation consortia. The latter are a unique group of entities
-sanctioned by Ontario's Ministry of Education in Ontario 2006. Each
-consortium involves a collaboration between municipal regions and school
-boards; the consortium's objective is to deliver more efficient and
-timely transportation services to schools in each region. Non-profit
+transportation consortia. The latter involve a collaboration between
+municipal regions and school boards to deliver more efficient and timely
+transportation services to schools in each region. Non-profit
 organizations, police services, and advocacy groups are other
@@
 this study does not include any documents from these groups because they
-are not consistently participating in all initiatives across Ontario.
+do not consistently participate in STP initiatives in Ontario.
 
@@
 manually searched for pages related to school transport or travel. Any
-pages relevant to these topics were manually downloaded. Next, we
-collected documents by searching municipal government and transportation
-consortia websites. These were identified based on geographic area
-(i.e., the municipalities and/or transportation consortia that are in
-the same geographic area of each school board). Webpages related to
-active transport or school travel were manually downloaded.
+pages relevant to these topics were downloaded. Next, we searched
+municipal government and transportation consortia websites. These were
+identified based on geographic area. Likewise, webpages related to
+active transport or school travel were downloaded.
 
 Webpages from STP stakeholder groups were included in our analysis if
-they were easy to find. This primary criterion was important since our
+they were findable. This primary criterion was important since our
 analysis pertains to how such issues are framed to the general public.
 Thus, we included only webpages that were readily accessible, which we
-defined as requiring no more than 4 separate links from the initial
-Google search.
+defined as requiring no more than four links from the initial Google
+search to reach.
 
 The initial corpus of documents from STP stakeholder groups included 69
-relevant webpages (i.e., one page or more). We refer to these as policy
-documents throughout the paper. It is important to note that school
-boards, municipalities, and transportation consortia may or may not
-publish information about their involvement in AST and STP efforts on
-their respective websites or in policy documents. Search results are
+relevant webpages. We refer to these as policy+practice documents
+throughout the paper. It is important to note that school boards,
+municipalities, and transportation consortia may or may not publish
+information about their involvement in AST and STP efforts on their
+respective websites or in policy documents. Search results are
 summarized in Table \ref{tab:policy-documents}.
@@
 \hypertarget{academic-papers}{%
-\subsubsection{3.1.2. Academic papers}\label{academic-papers}}
+\subsubsection{Academic papers}\label{academic-papers}}
 
 We conducted a search on Web of Science for scholarly papers on the
-topic of travel to school. We limited our search to the fields of public
+topic of school travel. We limited our search to the fields of public
 health, transportation, planning, urban studies, and geography. This
 initial corpus was curated by the authors to ensure that all documents
-were relevant; for example, some hits in our search were not full papers
-but conference reports, or they dealt with travel to school only
-peripherally. After this step, we assembled a collection of 227 journal
-articles for analysis.
+were relevant. After this step, 227 journal articles were readied for
+analysis.
 
 \hypertarget{data-cleaning}{%
-\subsection{3.2. Data cleaning}\label{data-cleaning}}
+\subsection{Data cleaning}\label{data-cleaning}}
 
@@
 as much text as possible from both the policy documents (n = 64) and
-academic papers (n = 227). To begin, the webpages, which were manually
-downloaded in portable document format (PDF), were trimmed so that pages
-that only consisted of tables, figures, or references were removed. Many
-academic papers were in a two-column format, which is not ideal for
-conversion to \texttt{txt}. Two-column PDF documents were processed to
-extract the text in the correct sequence. Four academic papers did not
-join sufficiently and were taken out of the corpus due to the
-substantial time required to manually correct their inconsistencies.
-
-Next, we converted the trimmed PDF documents into \texttt{txt} files so
-that they could be imported for analysis in \texttt{R}. The next phase
-was to manually remove any remaining tables, figures, references,
-headers/footings, and captions that could not be trimmed. Manual
-corrections were also required for certain pages in academic papers that
-remained in two-column format after the conversion process. This
-typically occurred on pages that had a table or figure that disrupted
-the text. Finally, we reviewed all of the documents to remove
-hyphenation by line breaks and to keep hyphenated words together on the
-same line. Any ligatures (e.g., combinations of characters or letters
-that were not properly detected during the conversion process) were
-fixed.
-
-We also manually removed any extraneous material that did not pertain to
-AST specifically. For the academic papers, this included footnotes,
-references, acknowledgments, and conflict of interest statements. For
-the policy+practice documents, it included phone numbers, inserted links
-to other webpages, personal names, and content not specific to AST. In
-the final step, we removed all blank spaces, punctuation,
-capitalization, and numbers. English stop words, which are common words
-such as \emph{and} or \emph{the} as identified in a predetermined list
-by Feinerer and Hornik (2020) and other frequent terms in the documents
-like ``school'' and specific location names, were removed from the
-corpora.
+academic papers (n = 227). Webpages were manually downloaded in portable
+document format (PDF) and trimmed so that pages that only consisted of
+tables, figures, or references were removed. After converting into
+\texttt{txt} files and importing for analysis, we manually removed any
+remaining tables, figures, references, headers/footings, and captions
+that could not be trimmed. We also manually removed any extraneous
+material that did not pertain to AST specifically (e.g., references,
+footnotes, weblinks, etc.). In the final step, we removed all blank
+spaces, punctuation, capitalization, and numbers. English stop words
+(i.e., words such as \emph{and} or \emph{the}) and other frequent terms
+in the documents like ``school'' and specific location names were
+removed from the corpora.
 
 \hypertarget{methods}{%
-\section{4. Methods}\label{methods}}
+\section{Methods}\label{methods}}
 
 \hypertarget{process-of-framing-analysis}{%
-\subsection{4.1. Process of Framing
+\subsection{Process of Framing
 Analysis}\label{process-of-framing-analysis}}
 
-We use topic modelling in \texttt{R} to conduct the framing analysis.
-Topic modelling is a machine learning technique used to analyze text to
-identify the language and concepts being communicated. This method is
-practical for researchers working with large amounts of text because it
-replaces the manual coding of topics that would normally take place to
-analyze or summarize textual data (Jacobi et al., 2016). In the data
-pre-processing phase, we tokenize the text in the documents and create a
-document-term matrix so that it is in the correct format for analysis.
-We primarily use the following packages: \texttt{tidytext} (Robinson and
-Silge, 2021), \texttt{topicmodels} (Grün and Hornik, 2021),
-\texttt{word2vec} (Wijffels, 2021), and \texttt{wordcloud} (Fellows,
-2018) to examine text in the documents that were sourced for this
-project. These packages have functions for determining the frequency of
-specific words in each document or relationships (e.g., pairs of
-adjacent terms called bigrams) and correlations between words. Topic
-modelling is a popular method for analyzing text from social media
-platforms (Albalawi et al., 2020) and news articles (Jacobi et al.,
-2016). We estimate latent Dirichlet allocation (LDA) models to classify
-both the STP and academic documents according to the topics that are
-contained within them. This method ``treats each document as a mixture
-of topics, and each topic as a mixture of words'' (Silge and Robinson,
-2022). The model's output is ``a set of topics consisting of clusters of
-words that co-occur in these documents according to certain patterns''
-(Jacobi et al., 2016). Researchers must then interpret the identified
-topics, as done after other methods of manual coding. We also compare
-the topics between the policy documents and the academic papers to
-interpret what is being communicated by STP stakeholders. We describe in
-more detail the functions and code in \texttt{R} that we used.
+We use topic modelling to analyze the documents retrieved. Topic
+modelling is a natural language processing technique used to analyze
+text to identify the language and concepts being communicated. This
+method is practical for researchers working with large amounts of text
+because it replaces the manual coding of topics that would normally take
+place to analyze or summarize textual data
+\citep{jacobiQuantitativeAnalysisLarge2016}. We primarily use the
+following software: \texttt{tidytext} \citep{R-tidytext},
+\texttt{topicmodels} \citep{R-topicmodels}, \texttt{word2vec}
+\citep{R-word2vec}, and \texttt{wordcloud} \citep{R-wordcloud}.
+
+We estimate latent Dirichlet allocation (LDA) models to identify topics
+contained in both the STP and academic documents. The model's output is
+``a set of topics consisting of clusters of words that co-occur in these
+documents according to certain patterns''
+\citep{jacobiQuantitativeAnalysisLarge2016}. Researchers must then
+interpret the identified topics, as done after other methods of manual
+coding.
 
 \hypertarget{reproducibility}{%
-\subsection{4.3. Reproducibility}\label{reproducibility}}
+\subsection{Reproducibility}\label{reproducibility}}
 
@@
 only open software. Following best practices in spatial data science
-(Brunsdon and Comber, 2020), the code and data needed to reproduce our
+\citep{brunsdon2020opening}, the code and data needed to reproduce our
 research or conduct a similar analysis for other regions are available
@@
 \hypertarget{results}{%
-\section{5. Results}\label{results}}
+\section{Results}\label{results}}
 
 \hypertarget{word-and-document-frequency}{%
-\subsection{5.1. Word and document
+\subsection{Word and document
 frequency}\label{word-and-document-frequency}}
@@
 present in each corpus, but it's not clear what this refers to (e.g,
-\emph{physical activity}, \emph{physical health}, or the \emph{physical
-environment}). Furthermore, documents from STP stakeholder groups
-discuss \emph{resources}, \emph{information}, and \emph{services} about
-school travel. Unlike the academic papers, policy documents include the
-words \emph{route} or \emph{routes} as frequent terms. This could
-indicate the presence of ``safe routes to school'' in the policy corpus,
-as well as the role of STP stakeholder groups in identifying safe routes
+\emph{physical activity}, or the \emph{physical environment}).
+Furthermore, documents from STP stakeholder groups discuss
+\emph{resources}, \emph{information}, and \emph{services} about school
+travel. Unlike the academic papers, policy+practice documents include
+the words \emph{route} or \emph{routes} as frequent terms. This could
+indicate the role of STP stakeholder groups in identifying safe routes
 to school to share with parents or families. In the section below, the
@@
 variables that influence mode choice. These words are absent from the
-list of common words in policy documents. Table \ref{tab:word-table}
-indicates that the academic corpus discusses a broader range of
-determinants of AST than the policy documents. The number of references
-for each term in the academic papers is also substantially higher due to
-the inclusion of more documents.
+list of common words in policy+practice documents. Table
+\ref{tab:word-table} indicates that the academic corpus discusses a
+broader range of determinants of AST than the policy documents. The
+number of references for each term in the academic papers is also
+substantially higher due to the inclusion of more documents.
 
@@
 all policy documents. This suggests that although documents pertain to
-the subject of school travel, not all stakeholders across Ontario are
-disseminating information about AST. For example, a document may discuss
-active travel but not to school. Some documents present school travel
-options by bus but not by active modes. We manually searched the policy
-corpus and found that 48\% of documents mention AST and 16\% mention
-STP. This confirms that many municipalities, school boards, and
-transportation consortia do not promote AST through their webpages or
-indicate their involvement in the STP process. Instead, inclement
-weather and its impacts on busing is a common topic addressed in school
-board and transportation consortia documents.
+the subject of school travel, not all stakeholders across Ontario
+disseminate information about AST. We manually searched the
+policy+practice corpus and found that 48\% of documents mention AST and
+16\% mention STP. In contrast, inclement weather and its impacts on
+busing is a common topic addressed in school board and transportation
+consortia documents.
 
 \hypertarget{bigrams-and-concordances}{%
-\subsection{5.2. Bigrams and
-concordances}\label{bigrams-and-concordances}}
-
-Bigrams refer to a pair of consecutive words. Figures
-\ref{fig:city-visual}, \ref{fig:consortia-visual}, and
-\ref{fig:school-visual} show the bigrams that occur more than 5 times
-for each set of policy documents. These figures help to make further
-sense of the word frequencies reported above, and highlight the main
-ideas that are presented to the public in each of the policy corpora.
-The directional arrows indicate the arrangement of the words (e.g.,
-active travel and not travel active) and the colour gradient of the
-arrows corresponds to the most frequently mentioned pairs (e.g., bigrams
-with darker arrows are found more often).
-
-Municipalities primarily discuss \emph{physical activity} (n = 53) and
-\emph{public health} (n = 19) in the context of AST. In addition,
-\emph{travel planning} (n = 19), \emph{bike lanes} (n = 16), and
-\emph{safe routes} (n = 14) are also identified, conceivably as either
-proposed solutions or built environment factors that support AST. Key
-issues related to transport such as \emph{traffic safety} (n = 10),
-\emph{air quality} (n = 9), and \emph{greenhouse gases} (n = 9) are
-conveyed to the public through these policy documents. It is not
-surprising to find this focus given that municipalities in Ontario are
-concerned about climate change and have increasingly looked to active
-travel to offset transport-related emissions in urban areas.
-
-Similar bigrams are found in school board documents: \emph{travel
-planning} (n = 33), \emph{safe routes} (n = 15), \emph{physical
-activity} (n = 10), and \emph{public health} (n = 10) are among the most
-common. Both municipalities and school boards in Ontario seem to
-emphasize what can be or has been done to improve AST (i.e., policy or
-planning changes), while outlining some of the benefits of AST at the
-individual- or community-level to potentially encourage behaviour change
-(i.e., physical activity for children or improved air quality). Unlike
-other STP stakeholders, school boards also consider \emph{inclement
-weather} (n = 24) and \emph{bus cancellations} (n = 13). Most likely
-this is because school boards are mandated to provide transportation to
-school in Ontario (typically by bus) and this information is presented
-alongside AST options. Finally, transportation consortia documents
-highlight topics such as \emph{physical activity} (n = 10),
-\emph{pedestrian safety} (n = 8), \emph{crossing guards} (n = 6),
-\emph{travel planning} (n = 6), and \emph{walk zones} (n = 6). Biking
-and cycling are notably absent from transportation consortia documents.
-Overall, the policy documents appear to convey an emphasis on the built
-environment, rather than household decision-making.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/city-visual-1}
-
-}
-
-\caption{\label{fig:city-visual}Most common bigrams found in the municipal and regional government documents.}\label{fig:city-visual}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/consortia-visual-1}
-
-}
-
-\caption{\label{fig:consortia-visual}Most common bigrams found in the transportation consortia documents.}\label{fig:consortia-visual}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/school-visual-1}
-
-}
-
-\caption{\label{fig:school-visual}Most common bigrams found in the school board documents.}\label{fig:school-visual}
-\end{figure}
+\subsection{Bigrams and concordances}\label{bigrams-and-concordances}}
 
@@
 
-We then combined all municipality, school board, and transportation
-consortia documents into one ``policy+practice'' corpus. This enabled us
-to examine and visualize the most common bigrams found across all of the
-material in Ontario that was collected for this study. Figure
-\ref{fig:policy-visual} shows all of the bigrams that occur more than 10
-times in the policy+practice corpus. In addition to the bigrams already
-identified above, we also found \emph{mental health}, \emph{walk day},
-and \emph{green communities} as common pairs of consecutive words.
-\emph{Green Communities Canada} is a non-profit organization that has
-significantly supported AST initiatives through the Ontario Active
-School Travel program so the high frequency of this term in the
-policy+practice corpus is not surprising. Overall, the policy documents
-from STP stakeholder groups seem to focus on four key areas: i) benefits
-or impacts of AST; ii) mechanisms of intervention; iii) concerns or
-barriers; and iv) supports for AST. This interpretation indicates that
-the general public accessing information about AST in Ontario is
-informed about a wide range of content related to this issue.
+Bigrams refer to a pair of consecutive words. We combined all
+municipality, school board, and transportation consortia documents into
+the policy+practice. Figure \ref{fig:policy-visual} shows all of the
+bigrams that occur more than 10 times in the policy+practice corpus.
+This figure highlights the main ideas that are presented to the public
+in each of the policy corpora. The directional arrows indicate the
+arrangement of the words (e.g., active travel and not travel active) and
+the colour gradient of the arrows corresponds to the most frequently
+mentioned pairs (e.g., bigrams with darker arrows are found in the
+corpus more often).
+
+STP stakeholders discuss \emph{physical activity} and \emph{public
+health} in the context of AST. In addition, \emph{travel planning},
+\emph{bike lanes}, and \emph{safe routes} are also identified,
+conceivably as either proposed solutions or built environment factors
+that support AST. Key issues related to transport such as \emph{traffic
+safety}, \emph{air quality}, and \emph{greenhouse gases} are conveyed to
+the public through these policy documents. It is not surprising to find
+this focus given that municipalities in Ontario are concerned about
+climate change and have increasingly looked to active travel to offset
+transport-related emissions in urban areas. We also found \emph{mental
+health}, \emph{walk zone}, and \emph{green communities} as common pairs
+of consecutive words. \emph{Green Communities Canada} is a non-profit
+organization that has significantly supported AST initiatives through
+the Ontario Active School Travel program so the high frequency of this
+term in the policy+practice corpus is not surprising. Overall, the
+policy documents from STP stakeholder groups seem to focus on four key
+areas: i) benefits or impacts of AST; ii) mechanisms of intervention;
+iii) concerns or barriers; and iv) supports for AST. This interpretation
+indicates that the general public accessing information about AST in
+Ontario is informed about a wide range of content related to this issue.
 
@@
 common bigrams that were also found in the policy documents including
-\emph{physical activity} (n = 1566), which is the top bigram,
-\emph{traffic safety} (n = 308), and \emph{safe routes} (n = 268).
-However, many other factors are identified in the research literature
-that are not presented to the general public through policy documents.
-After \emph{physical activity}, \emph{built environment} (n = 1175),
-\emph{independent mobility} (n = 774), and \emph{urban form} (n = 352)
-are the most frequent pairs of consecutive words. Academic papers also
-often discuss \emph{distance home} (n = 258), \emph{car ownership} (n =
-254), \emph{household income} (n = 254), and \emph{population density}
-(n = 205), which are factors that have been found to influence AST. Many
-papers also investigate gender differences in AST given that \emph{boys
-girls} (n = 211) is another common bigram. Finally, the presence of
-\emph{statistically significant} among the top bigrams indicates that
-researchers often aim to identify associations using statistical
-measures. We found that the academic corpus focuses on a greater range
-of topics than found in the policy+practice documents.
+\emph{physical activity}, which is the top bigram, \emph{traffic
+safety}, and \emph{safe routes}. However, many other factors are
+identified in the research literature that are not presented to the
+general public through policy documents. Terms like \emph{built
+environment}, \emph{independent mobility}, and \emph{urban form} are
+other frequent pairs of consecutive words. Academic papers also often
+discuss \emph{distance home}, \emph{car ownership}, \emph{household
+income}, and \emph{population density}, which are factors that have been
+found to influence AST. Finally, the presence of \emph{statistically
+significant} among the top bigrams indicates that researchers often aim
+to identify associations using statistical measures. We found that the
+academic corpus focuses on a greater range of topics than found in the
+policy+practice documents.
 
@@
 We interpreted the most common bigrams from the policy+practice corpus
-(see Figure \ref{fig:policy-visual}), which includes all documents from
-municipalities, transportation consortia, and school boards, as the main
-ideas that STP stakeholder groups focus on and communicate to the public
-about AST. We then examined the context of these key ideas by extracting
+(see Figure \ref{fig:policy-visual}) as the main ideas that STP
+stakeholder groups focus on and communicate to the public about AST. We
+then examined the context of these key ideas by extracting
 words-in-context from the corpora. Table \ref{tab:policy-concordance}
@@
 \hypertarget{topic-modelling}{%
-\subsection{5.3. Topic modelling}\label{topic-modelling}}
+\subsection{Topic modelling}\label{topic-modelling}}
 
@@
 
-For the final part of our analysis, we conducted topic modelling to
-examine the different topics found in the policy and academic corpora.
-We focused on the policy/practice corpus, instead of assessing the
-municipal, school, and consortia documents separately, so that we could
-report on the various frames used across all documents put out by STP
-stakeholder groups in Ontario. We then estimated Latent Dirichlet
+We conducted topic modelling to examine the different topics found in
+the policy+practice and academic corpora. We estimated Latent Dirichlet
 Allocation (LDA) models for each corpus. Parameter tuning suggests that
@@
 corpus has between 17 and 25 topics. After running the LDA model for the
-academic corpus, we realized the difficulty of interpreting a minimum of
+academic corpus, we realized the difficulty of interpreting as many as
 17 topics based on the clusters of words that were identified. We
@@
 evaluating the output of terms in each topic. We found that there were 9
-distinct topics that could be interpreted in the policy corpus and 11
-topics in the academic corpus, after which there was too much overlap
-for the clusters to be meaningfully interpreted. Figures
+distinct topics that could be interpreted in the policy+practice corpus
+and 11 topics in the academic corpus, after which there was too much
+overlap for the clusters to be meaningfully interpreted. Figures
 \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main
@@
 and (11) public health and policies. This corpus reflects a broader
-range of topics than the policy/practice corpus.
+range of topics than the policy+practice corpus.
 
 \hypertarget{frames}{%
-\subsection{5.4. Frames}\label{frames}}
+\subsection{Frames}\label{frames}}
 
@@
 community through a reduction in traffic and vehicle emissions. Here, we
-present some examples from the policy documents that illustrate how the
-health and environmental frame is communicated:
-
-\begin{quote}
-\emph{If you live in a walk zone, the best way to get to school is by
-walking or biking. This promotes physical activity, helps the
-environment and minimizes traffic around schools during busy times.}
-(City of Barrie)
-\end{quote}
+present an example that illustrates how the health and environmental
+frame is communicated:
 
@@
 
-\begin{quote}
-\emph{The WCDSB supports active transportation as the preferred method
-of transportation to school because it is a healthy choice that has
-proven links to greater student achievement.} (Waterloo Catholic
-District School Board)
-\end{quote}
-
 Furthermore, we found that policy documents make claims about the
@@
 research and evaluation.
-
-\begin{quote}
-\emph{For their health, safety, environment and community: Kids learn
-healthy habits and concentrate better in class; One less car (yours)
-reduces traffic and parking problems in school zones; Teach your kids
-about traffic safety; Start a walking school bus; your kids make friends
-in every grade, and that can prevent bullying.} (City of Guelph)
-\end{quote}
 
@@
 \begin{quote}
-\emph{A way to make sure your child is safe while walking to school is
-with a `walking school bus.' Here are some tips for a walking school
-bus: Invite families who live nearby to walk; Pick a route and take a
-test walk; Take side streets and paths that are less busy with traffic;
-Decide how often the group will walk together; Talk with your boss to
-adjust your day; Have fun!} (City of Ottawa)
-\end{quote}
-
-\begin{quote}
 \emph{Help your students get started on the right foot - encourage them
@@
 awareness.} (Halton District School Board)
-\end{quote}
-
-\begin{quote}
-\emph{Want to boost your child's mental and physical health? Ottawa
-Public Health, City of Ottawa, and OSTA have produced a tipsheet for
-parents about ``active transportation'' to school -- fitting walking and
-wheeling into your daily routine.} (Ottawa-Carleton District School
-Board)
 \end{quote}
@@
 
-\begin{quote}
-\emph{Today, as more and more of our neighbourhoods are being
-retrofitted with new sidewalks and bike lanes, pedestrian crossovers,
-street lights, reduced speed limits and/or crossing guards, the walk or
-bike ride to and from school has never been easier, safer or healthier.}
-(Hamilton-Wentworth District Catholic School Board)
-\end{quote}
-
 \hypertarget{discussion}{%
-\section{6. Discussion}\label{discussion}}
+\section{Discussion}\label{discussion}}
 
 \hypertarget{current-ast-frames-in-ontario}{%
-\subsection{6.1. Current AST frames in
+\subsection{Current AST frames in
 Ontario}\label{current-ast-frames-in-ontario}}
 
-Using natural language processing techniques, we analyzed how AST is
-framed in 69 documents available to the public on the websites of STP
-stakeholder groups in Ontario. Two main frames in the policy+practice
-corpus were identified based on the most common bigrams and topics from
-the LDA model.
-
-We found that AST is primarily framed to parents as beneficial to the
-health and wellbeing of children and to environmental sustainability.
-The policy documents reflect the evidence that AST contributes
-positively to children's physical health (see Faulkner et al., 2009;
-Schoeppe et al., 2015), although the statements regarding the benefits
-of AST to children's school performance are less well-supported in the
-extant literature (Westman et al., 2020). STP stakeholder groups also
+Interpretation of the text assisted by natural language processing
+reveals that AST in Ontario is primarily framed to parents as beneficial
+to the health and wellbeing of children and to environmental
+sustainability. The policy documents reflect the evidence that AST
+contributes positively to children's physical health
+\citep[see][]{faulknerActiveSchoolTransport2009, schoeppeAssociationsChildrenActive2015},
+although the statements regarding the benefits of AST to children's
+school performance are less well-supported in the extant literature
+\citep{westmanTravelChildWellbeing2020}. STP stakeholder groups also
 communicate that increasing AST may reduce traffic near and around
 schools. This is conveyed presumably to alleviate parental concerns
-about traffic and safety (Evers et al., 2014; Mammen et al., 2012;
-Rothman et al., 2015; Wilson et al., 2018) or to reduce the frequency of
-risky behaviours from drivers around schools (Rothman et al., 2017).
+about traffic and safety
+\citep{eversParentSafetyPerceptions2014, mammenUnderstandingDriveEscort2012, rothmanAssociationsParentsPerception2015, wilsonUnderstandingChildParent2018}
+or to reduce the frequency of risky behaviours from drivers around
+schools \citep{rothmanSchoolEnvironmentStudent2017}.
 
@@
 identified different ways that parents could encourage or support their
-children to commute to school by using active modes. Some school boards
-and municipalities also shared resources such as walking tip sheets and
-guidance for starting a walking school bus. Other advice included
-dropping children off one or two blocks away from school so that they
-could walk or bike part of the trip. The general emphasis of this frame
+children to commute to school by using active modes (e.g., walking tip
+sheets, walking school buses, etc.). The general emphasis of this frame
 is communicating information that could change parental perceptions
 about the ease of their children using active modes to school, which may
-be seen by STP stakeholder groups as a ``modifiable'' factor (see Riazi
-et al., 2019). In turn, this could encourage parents to modify their
-routines and incorporate opportunities for their children to use active
-modes to school.
+be seen by STP stakeholder groups as a ``modifiable'' factor
+\citep[see][]{riaziCorrelatesChildrenIndependent2019}. In turn, this
+could encourage parents to modify their routines and incorporate
+opportunities for their children to use active modes to school.
 
@@
 school have reported concerns about traffic volume around schools
-(Mammen et al., 2012), but may not recognize that their own behaviour
-contributes to the problem that is perceived to prevent their child from
-safely walking or bicycling to school (Collins and Kearns, 2001).
-Reynard et al. (2021) similarly found in their analysis of Canadian
-municipal documents that one of the dominant frames presented the
-adoption of behaviours to help mitigate the climate crisis as a choice
-but not ``the expected norm.''
+\citep{mammenUnderstandingDriveEscort2012}, but may not recognize that
+their own behaviour contributes to the problem that is perceived to
+prevent their child from safely walking or bicycling to school
+\citep{collinsSafeJourneysEnterprising2001}. Reynard et al.
+\citeyearpar{reynardGrowthResilienceHow2021} similarly found in their
+analysis of Canadian municipal documents that one of the dominant frames
+presented the adoption of behaviours to help mitigate the climate crisis
+as a choice but not ``the expected norm''.
 
 We found that the proposed solutions in the secondary frame to increase
-AST align with different levels of the socioecological model: 1)
-behaviour change from individuals or households making different travel
-decisions; 2) policies like STP that create resources for AST; and 3)
-engineering solutions like bicycle lanes. This reflects findings from
-the AST literature that a range of solutions are needed to address
-different factors that influence AST (\emph{inter alia, see} Mitra,
-2013; Panter et al., 2010). The recognition of engineering changes may
-reflect the strong engagement of the ``policy stream'' (Kingdon, 1984)
-since engineering staff and municipal representatives are common STP
-stakeholders in Canada (Buttazzoni et al., 2018; Mammen et al., 2015),
+AST align with different levels of the SEM: 1) behaviour change from
+households making different travel decisions; 2) policies that create
+resources for AST; and 3) engineering solutions like bicycle lanes. This
+reflects findings from the AST literature that a range of solutions are
+needed to address different factors that influence AST
+\citep[\emph{inter alia,
+see}][]{mitraIndependentMobilityMode2013, panterAttitudesSocialSupport2010}.
+The recognition of engineering changes may reflect the strong engagement
+of engineering staff and municipal representatives in the Canadian STP
+process
+\citep{buttazzoniSupportingActiveSchool2018, mammenPuttingSchoolTravel2015},
 as well as the evidence that the built environment influences mode
@@
 \hypertarget{implications-for-school-travel-planning}{%
-\subsection{6.2. Implications for school travel
+\subsection{Implications for school travel
 planning}\label{implications-for-school-travel-planning}}
@@
 has occurred over recent decades in Canada and emphasize that this issue
-merits urgent behaviour change. A study investigating the influence of
-different valence framings of CO2 emissions on transport mode shift
-found that positive framing can be less effective than negative framing
-(Waygood and Avineri, 2018). A negative framing that challenges the
-social norm of driving could be more motivational to shift modes, which
-would be consistent with other findings (see Waygood and Avineri, 2018).
-Policy documents should make it clear that continued use of nonactive
-modes to school can deprive children of opportunities to increase
-physical activity and to gain health and social benefits.
+merits urgent behaviour change. A negative framing that challenges the
+social norm of driving could be more motivational to shift transport
+modes, which would be consistent with other findings
+\citep[see][]{waygoodCO2ValenceFraming2018}. Policy documents should
+make it clear that continued use of nonactive modes to school can
+deprive children of opportunities to increase physical activity and to
+gain health and social benefits.
 
@@
 of convenience and inclement weather in shaping household travel
-decisions (Buliung et al., 2011) and the complexity of travel
-arrangements that must be coordinated by households (see Buliung et al.,
-2021) were not found to be discussed. The desire to escort children to
-school, which has been noted by parents as a reason to continue driving
-(Westman et al., 2017a), is also not adequately addressed by STP
-stakeholders. Parental assessment of a child's ability to undertake the
-journey to school was likewise overlooked despite its role in decision
-making for mode choice to school (Faulkner et al., 2010). Framing AST as
-a developmental opportunity or a rite of passage that children have been
-denied could challenge the prevailing culture of risk avoidance which
-discourages parents from letting their children use active modes to
-school.
+decisions \citep{buliungSchoolTravelPlanning2011} and the complexity of
+travel arrangements that must be coordinated by households
+\citep[see][]{buliungLivingJourneySchool2021} were not found to be
+discussed. The desire to escort children to school, which has been noted
+by parents as a reason to continue driving
+\citep{westmanWhatDrivesThem2017}, is also not adequately addressed by
+STP stakeholders. Parental assessment of a child's ability to undertake
+the journey to school was likewise overlooked despite its role in
+decision making for mode choice to school
+\citep{faulknerWhatQuickestEasiest2010}. Framing AST as a developmental
+opportunity or a rite of passage that children have been denied could
+challenge the prevailing culture of risk avoidance which discourages
+parents from letting their children use active modes to school.
 
@@
 increase buy-in for their target audience. If Canadian STP stakeholders
-wish to involve more local residents in their efforts (Buttazzoni et
-al., 2018), it would also be worthwhile for them to produce different
-materials that communicate why this issue is important to the general
-public, regardless of whether they currently have children commuting
-to/from school.
+wish to involve more local residents in their efforts
+\citep{buttazzoniSupportingActiveSchool2018}, it would also be
+worthwhile for them to produce different materials that communicate why
+this issue is important to the general public, regardless of whether
+they currently have children commuting to/from school.
 
 \hypertarget{limitations}{%
-\subsection{6.3. Limitations}\label{limitations}}
+\subsection{Limitations}\label{limitations}}
 
@@
 \hypertarget{conclusion}{%
-\section{7. Conclusion}\label{conclusion}}
-
-We used natural language processing techniques to examine how different
-school travel planning (STP) stakeholders in Ontario frame the issue of
-AST. STP stakeholders frame AST as an accessible and feasible way to
-travel to school that is valuable to children's health and to the
+\section{Conclusion}\label{conclusion}}
+
+In this paper we examined how AST is framed in Ontario. Our analysis was
+supported by the use of natural language processing techniques, and
+reavealed that STP stakeholders frame AST as an accessible and feasible
+way to travel to school that is valuable to children's health and to the
 environment. STP stakeholders are communicating that this issue can be
@@
 
-\hypertarget{acknowledgments}{%
-\section{Acknowledgments}\label{acknowledgments}}
-
-This research was completed using open software, and the authors wish to
-acknowledge the developers of the following \texttt{R} packages:
-\texttt{dplyr} (Wickham et al., 2021b), \texttt{ggraph} (Pedersen,
-2021), \texttt{ggplot2} (Wickham et al., 2021a), \texttt{igraph} (file.,
-2022), \texttt{pdftools} (Ooms, 2021), \texttt{readr} (Wickham et al.,
-2021c), \texttt{reshape2} (Wickham, 2020), \texttt{stringr} (Wickham,
-2019), \texttt{text2vec} (Selivanov et al., 2020), \texttt{textdata}
-(Hvitfeldt, 2020), \texttt{tidyr} (Wickham, 2021), \texttt{tidytext}
-(Robinson and Silge, 2021), \texttt{tm} (Feinerer and Hornik, 2020),
-\texttt{tools} (\textbf{R-tools?}), \texttt{topicmodels} (Grün and
-Hornik, 2021), \texttt{widyr} (Robinson, 2021), \texttt{word2vec}
-(Wijffels, 2021), \texttt{wordcloud} (Fellows, 2018),
-\texttt{DiagrammeR} (\textbf{R-diagrammeR?}), and \texttt{kableextra}
-(\textbf{R-kableextra?}).
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-albalawiUsingTopicModeling2020}{}}%
-Albalawi, R., Yeap, T.H., Benyoucef, M., 2020. Using topic modeling
-methods for short-text data: A comparative analysis. Frontiers in
-Artificial Intelligence 3, 42.
-doi:\href{https://doi.org/10.3389/frai.2020.00042}{10.3389/frai.2020.00042}
-
-\leavevmode\vadjust pre{\hypertarget{ref-badlandDevelopmentSystemsModel2016}{}}%
-Badland, H., Kearns, R., Carroll, P., Oliver, M., Mavoa, S., Donovan,
-P., Parker, K., Chaudhury, M., Lin, E.-Y., Witten, K., 2016. Development
-of a systems model to visualise the complexity of children's independent
-mobility. Children's Geographies 14, 91--100.
-doi:\href{https://doi.org/10.1080/14733285.2015.1021240}{10.1080/14733285.2015.1021240}
-
-\leavevmode\vadjust pre{\hypertarget{ref-borrestadExperiencesRandomisedControlled2012}{}}%
-Børrestad, L.A.B., Østergaard, L., Andersen, L.B., Bere, E., 2012.
-Experiences from a randomised, controlled trial on cycling to school:
-Does cycling increase cardiorespiratory fitness? Scandinavian Journal of
-Public Health 40, 245--252.
-doi:\href{https://doi.org/10.1177/1403494812443606}{10.1177/1403494812443606}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brunsdon2020opening}{}}%
-Brunsdon, C., Comber, A., 2020. Opening practice: Supporting
-reproducibility and critical spatial data science. Journal of
-Geographical Systems.
-doi:\href{https://doi.org/10.1007/s10109-020-00334-2}{10.1007/s10109-020-00334-2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-buliungSchoolTravelPlanning2011}{}}%
-Buliung, R., Faulkner, G., Beesley, T., Kennedy, J., 2011. School travel
-planning: Mobilizing school and community resources to encourage active
-school transportation. Journal of School Health 81, 704--712.
-doi:\href{https://doi.org/10.1111/j.1746-1561.2011.00647.x}{10.1111/j.1746-1561.2011.00647.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-buliungLivingJourneySchool2021}{}}%
-Buliung, R., Hess, P., Flowers, L., Moola, F.J., Faulkner, G., 2021.
-Living the journey to school: Conceptual asymmetry between parents and
-planners on the journey to school. Social Science \& Medicine 284,
-114237.
-doi:\href{https://doi.org/10.1016/j.socscimed.2021.114237}{10.1016/j.socscimed.2021.114237}
-
-\leavevmode\vadjust pre{\hypertarget{ref-buttazzoniPromotingActiveSchool2019}{}}%
-Buttazzoni, A.N., Clark, A.F., Seabrook, J.A., Gilliland, J.A., 2019.
-Promoting active school travel in elementary schools: A regional case
-study of the school travel planning intervention. Journal of Transport
-\& Health 12, 206--219.
-doi:\href{https://doi.org/10.1016/j.jth.2019.01.007}{10.1016/j.jth.2019.01.007}
-
-\leavevmode\vadjust pre{\hypertarget{ref-buttazzoniSupportingActiveSchool2018}{}}%
-Buttazzoni, A.N., Coen, S.E., Gilliland, J.A., 2018. Supporting active
-school travel: A qualitative analysis of implementing a regional safe
-routes to school program. Social Science \& Medicine 212, 181--190.
-doi:\href{https://doi.org/10.1016/j.socscimed.2018.07.032}{10.1016/j.socscimed.2018.07.032}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GreenCommunities2016}{}}%
-Canada, G.C., 2020. Ontario active school travel {[}WWW Document{]}. URL
-\url{https://ontarioactiveschooltravel.ca/about-ontario-active-school-travel/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GreenCommunitiesProjects}{}}%
-Canada, G.C., 2021. Ontario active school travel fund {[}WWW
-Document{]}. URL
-\url{https://ontarioactiveschooltravel.ca/ontario-active-school-travel-fund/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-TACbikeinfra2020}{}}%
-Canada, T.A. of, 2020. Safety performance of bicycle infrastructure in
-canada {[}WWW Document{]}. URL
-\url{https://www.tac-atc.ca/en/publications/ptm-spbi-e}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chenPromotingActiveStudent2018}{}}%
-Chen, P., Jiao, J., Xu, M., Gao, X., Bischak, C., 2018. Promoting active
-student travel: A longitudinal study. Journal of Transport Geography 70,
-265--274.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2018.06.015}{10.1016/j.jtrangeo.2018.06.015}
-
-\leavevmode\vadjust pre{\hypertarget{ref-collinsSafeJourneysEnterprising2001}{}}%
-Collins, D.C.A., Kearns, R.A., 2001. The safe journeys of an
-enterprising school: Negotiating landscapes of opportunity and risk.
-Health \& Place 7, 293--306.
-doi:\href{https://doi.org/10.1016/S1353-8292(01)00021-1}{10.1016/S1353-8292(01)00021-1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-demeesterParentalPerceivedNeighborhood2014}{}}%
-De Meester, F., Van Dyck, D., De Bourdeaudhuij, I., Cardon, G., 2014.
-Parental perceived neighborhood attributes: Associations with active
-transport and physical activity among 10-12 year old children and the
-mediating role of independent mobility. BMC public health 14, 631.
-doi:\href{https://doi.org/10.1186/1471-2458-14-631}{10.1186/1471-2458-14-631}
-
-\leavevmode\vadjust pre{\hypertarget{ref-depouxCommunicatingClimateChange2017}{}}%
-Depoux, A., Hémono, M., Puig-Malet, S., Pédron, R., Flahault, A., 2017.
-Communicating climate change and health in the media. Public Health
-Reviews 38, 7.
-doi:\href{https://doi.org/10.1186/s40985-016-0044-1}{10.1186/s40985-016-0044-1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-eversParentSafetyPerceptions2014}{}}%
-Evers, C., Boles, S., Johnson-Shelton, D., Schlossberg, M., Richey, D.,
-2014. Parent safety perceptions of child walking routes. Journal of
-Transport \& Health 1, 108--115.
-doi:\href{https://doi.org/10.1016/j.jth.2014.03.003}{10.1016/j.jth.2014.03.003}
-
-\leavevmode\vadjust pre{\hypertarget{ref-farberRunning2011}{}}%
-Farber, S., Páez, A., 2011. Running to stay in place: The time-use
-implications of automobile oriented land-use and travel. Journal of
-Transport Geography 19, 782--793.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2010.09.008}{10.1016/j.jtrangeo.2010.09.008}
-
-\leavevmode\vadjust pre{\hypertarget{ref-faulknerActiveSchoolTransport2009}{}}%
-Faulkner, G.E.J., Buliung, R.N., Flora, P.K., Fusco, C., 2009. Active
-school transport, physical activity levels and body weight of children
-and youth: A systematic review. Preventive Medicine 48, 3--8.
-doi:\href{https://doi.org/10.1016/j.ypmed.2008.10.017}{10.1016/j.ypmed.2008.10.017}
-
-\leavevmode\vadjust pre{\hypertarget{ref-faulknerWhatQuickestEasiest2010}{}}%
-Faulkner, G.E., Richichi, V., Buliung, R.N., Fusco, C., Moola, F., 2010.
-What's "quickest and easiest?": Parental decision making about school
-trip mode. International Journal of Behavioral Nutrition and Physical
-Activity 7, 1--11.
-doi:\href{https://doi.org/10.1186/1479-5868-7-62}{10.1186/1479-5868-7-62}
-
-\leavevmode\vadjust pre{\hypertarget{ref-faulknerSchoolTravelChildren2013}{}}%
-Faulkner, G., Stone, M., Buliung, R., Wong, B., Mitra, R., 2013. School
-travel and children's physical activity: A cross-sectional study
-examining the influence of distance. BMC public health 13, 1166.
-doi:\href{https://doi.org/10.1186/1471-2458-13-1166}{10.1186/1471-2458-13-1166}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tm}{}}%
-Feinerer, I., Hornik, K., 2020. Tm: Text mining package.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-wordcloud}{}}%
-Fellows, I., 2018. Wordcloud: Word clouds.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-igraph}{}}%
-file., S.A., 2022. Igraph: Network analysis and visualization.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fuscoUnderstandingChildrenPerceptions2012}{}}%
-Fusco, C., Moola, F., Faulkner, G., Buliung, R., Richichi, V., 2012.
-Toward an understanding of children's perceptions of their transport
-geographies: (Non)active school travel and visual representations of the
-built environment. Journal of Transport Geography, Special {section On
-Child} \& {Youth Mobility} 20, 62--70.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2011.07.001}{10.1016/j.jtrangeo.2011.07.001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gamsonChangingCulture1987}{}}%
-Gamson, W.A., Modigliani, A., 1987. The changing culture of affirmative
-action, in: Waygood, E.O.D., Friman, M., Olsson, L.E., Mitra, R. (Eds.),
-Research in Political Sociology. {JAI Press}, pp. 137--177.
-
-\leavevmode\vadjust pre{\hypertarget{ref-goffmanFrameAnalysisEssay1974}{}}%
-Goffman, E., 1974. Frame analysis: An essay on the organization of
-experience, Frame analysis: {An} essay on the organization of
-experience. {Harvard University Press}, {Cambridge, MA, US}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-topicmodels}{}}%
-Grün, B., Hornik, K., 2021. Topicmodels: Topic models.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-textdata}{}}%
-Hvitfeldt, E., 2020. Textdata: Download and load various text datasets.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ikedaAssociationsChildrenActive2018}{}}%
-Ikeda, E., Hinckson, E., Witten, K., Smith, M., 2018. Associations of
-children's active school travel with perceptions of the physical
-environment and characteristics of the social environment: A systematic
-review. Health \& Place 54, 118--131.
-doi:\href{https://doi.org/10.1016/j.healthplace.2018.09.009}{10.1016/j.healthplace.2018.09.009}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jacobiQuantitativeAnalysisLarge2016}{}}%
-Jacobi, C., van Atteveldt, W., Welbers, K., 2016. Quantitative analysis
-of large amounts of journalistic texts using topic modelling. Digital
-Journalism 4, 89--106.
-doi:\href{https://doi.org/10.1080/21670811.2015.1093271}{10.1080/21670811.2015.1093271}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kingdonAgendasAlternativesPublic1984}{}}%
-Kingdon, J.W., 1984. Agendas, alternatives, and public policies. {Harper
-Collins}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-langUnderstandingModalChoice2011}{}}%
-Lang, D., Collins, D., Kearns, R., 2011. Understanding modal choice for
-the trip to school. Journal of Transport Geography 19, 509--514.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2010.05.005}{10.1016/j.jtrangeo.2010.05.005}
-
-\leavevmode\vadjust pre{\hypertarget{ref-laroucheRatherBikeSchool2016}{}}%
-Larouche, R., Stone, M., Buliung, R.N., Faulkner, G., 2016. ''I'd rather
-bike to school!'': Profiling children who would prefer to cycle to
-school. Journal of Transport \& Health 3, 377--385.
-doi:\href{https://doi.org/10.1016/j.jth.2016.06.010}{10.1016/j.jth.2016.06.010}
-
-\leavevmode\vadjust pre{\hypertarget{ref-larsenRouteBasedAnalysisCapture2012}{}}%
-Larsen, K., Gilliland, J., Hess, P.M., 2012. Route-based analysis to
-capture the environmental influences on a child's mode of travel between
-home and school. Annals of the Association of American Geographers 102,
-1348--1365.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mahFramecriticalPolicyAnalysis2014}{}}%
-Mah, C.L., Hamill, C., Rondeau, K., McIntyre, L., 2014. A frame-critical
-policy analysis of canada's response to the world food summit
-1998\textendash 2008. Archives of Public Health 72, 41.
-doi:\href{https://doi.org/10.1186/2049-3258-72-41}{10.1186/2049-3258-72-41}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mahDoesParentalSupport2017a}{}}%
-Mah, S.K., Nettlefold, L., Macdonald, H.M., Winters, M., Race, D., Voss,
-C., McKay, H.A., 2017. Does parental support influence children's active
-school travel? Preventive Medicine Reports 6, 346--351.
-doi:\href{https://doi.org/10.1016/j.pmedr.2017.04.008}{10.1016/j.pmedr.2017.04.008}
-
-\leavevmode\vadjust pre{\hypertarget{ref-maibachReframingClimateChange2010}{}}%
-Maibach, E.W., Nisbet, M., Baldwin, P., Akerlof, K., Diao, G., 2010.
-Reframing climate change as a public health issue: An exploratory study
-of public reactions. BMC Public Health 10, 1--11.
-doi:\href{https://doi.org/10.1186/1471-2458-10-299}{10.1186/1471-2458-10-299}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mammenUnderstandingDriveEscort2012}{}}%
-Mammen, G., Faulkner, G., Buliung, R., Lay, J., 2012. Understanding the
-drive to escort: A cross-sectional analysis examining parental attitudes
-towards children's school travel and independent mobility. BMC public
-health 12, 862.
-doi:\href{https://doi.org/10.1186/1471-2458-12-862}{10.1186/1471-2458-12-862}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mammenSchoolTravelPlanning2014}{}}%
-Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2014a. School travel
-planning in canada: Identifying child, family, and school-level
-characteristics associated with travel mode shift from driving to active
-school travel. Journal of Transport \& Health 1, 288--294.
-doi:\href{https://doi.org/10.1016/j.jth.2014.09.004}{10.1016/j.jth.2014.09.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mammenPuttingSchoolTravel2015}{}}%
-Mammen, G., Stone, M.R., Buliung, R., Faulkner, G., 2015. ''Putting
-school travel on the map'': Facilitators and barriers to implementing
-school travel planning in canada. Journal of Transport \& Health 2,
-318--326.
-doi:\href{https://doi.org/10.1016/j.jth.2015.05.003}{10.1016/j.jth.2015.05.003}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mammenActiveSchoolTravel2014}{}}%
-Mammen, G., Stone, M.R., Faulkner, G., Ramanathan, S., Buliung, R.,
-O'Brien, C., Kennedy, J., 2014b. Active school travel: An evaluation of
-the canadian school travel planning intervention. Preventive Medicine
-60, 55--59.
-doi:\href{https://doi.org/10.1016/j.ypmed.2013.12.008}{10.1016/j.ypmed.2013.12.008}
-
-\leavevmode\vadjust pre{\hypertarget{ref-michailChildrenExperiencesTheir2021}{}}%
-Michail, N., Ozbil, A., Parnell, R., Wilkie, S., 2021. Children's
-experiences of their journey to school: Integrating behaviour change
-frameworks to inform the role of the built environment in active school
-travel promotion. International Journal of Environmental Research and
-Public Health 18, 4992.
-doi:\href{https://doi.org/10.3390/ijerph18094992}{10.3390/ijerph18094992}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mitraIndependentMobilityMode2013}{}}%
-Mitra, R., 2013. Independent mobility and mode choice for school
-transportation: A review and framework for future research. Transport
-Reviews 33, 21--43.
-doi:\href{https://doi.org/10.1080/01441647.2012.743490}{10.1080/01441647.2012.743490}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-pdftools}{}}%
-Ooms, J., 2021. Pdftools: Text extraction, rendering and converting of
-PDF documents.
-
-\leavevmode\vadjust pre{\hypertarget{ref-paezEnjoymentCommuteComparison2010}{}}%
-Páez, A., Whalen, K., 2010. Enjoyment of commute: A comparison of
-different transportation modes. Transportation Research Part A: Policy
-and Practice 44, 537--549.
-doi:\href{https://doi.org/10.1016/j.tra.2010.04.003}{10.1016/j.tra.2010.04.003}
-
-\leavevmode\vadjust pre{\hypertarget{ref-panFramingAnalysisApproach1993}{}}%
-Pan, Z., Kosicki, G.M., 1993. Framing analysis: An approach to news
-discourse. Political Communication 10, 55--75.
-doi:\href{https://doi.org/10.1080/10584609.1993.9962963}{10.1080/10584609.1993.9962963}
-
-\leavevmode\vadjust pre{\hypertarget{ref-panterAttitudesSocialSupport2010}{}}%
-Panter, J.R., Jones, A.P., Sluijs, E.M.F. van, Griffin, S.J., 2010.
-Attitudes, social support and environmental perceptions as predictors of
-active commuting behaviour in school children. Journal of Epidemiology
-\& Community Health 64, 41--48.
-doi:\href{https://doi.org/10.1136/jech.2009.086918}{10.1136/jech.2009.086918}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggraph}{}}%
-Pedersen, T.L., 2021. Ggraph: An implementation of grammar of graphics
-for graphs and networks.
-
-\leavevmode\vadjust pre{\hypertarget{ref-pontEnvironmentalCorrelatesChildren2009}{}}%
-Pont, K., Ziviani, J., Wadley, D., Bennett, S., Abbott, R., 2009.
-Environmental correlates of children's active transportation: A
-systematic literature review. Health \& Place 15, 849--862.
-doi:\href{https://doi.org/10.1016/j.healthplace.2009.02.002}{10.1016/j.healthplace.2009.02.002}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ramanathanHappinessMotionEmotions2014a}{}}%
-Ramanathan, S., O'Brien, C., Faulkner, G., Stone, M., 2014. Happiness in
-motion: Emotions, well-being, and active school travel. Journal of
-School Health 84, 516--523.
-doi:\href{https://doi.org/10.1111/josh.12172}{10.1111/josh.12172}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reynardGrowthResilienceHow2021}{}}%
-Reynard, D., Collins, D., Shirgaokar, M., 2021. Growth over resilience:
-How canadian municipalities frame the challenge of reducing carbon
-emissions. Local Environment 0, 1--13.
-doi:\href{https://doi.org/10.1080/13549839.2021.1892046}{10.1080/13549839.2021.1892046}
-
-\leavevmode\vadjust pre{\hypertarget{ref-riaziCorrelatesChildrenIndependent2019}{}}%
-Riazi, N.A., Blanchette, S., Trudeau, F., Larouche, R., Tremblay, M.S.,
-Faulkner, G., 2019. Correlates of children's independent mobility in
-canada: A multi-site study. International Journal of Environmental
-Research and Public Health 16.
-doi:\href{https://doi.org/10.3390/ijerph16162862}{10.3390/ijerph16162862}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-widyr}{}}%
-Robinson, D., 2021. Widyr: Widen, process, then re-tidy data.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidytext}{}}%
-Robinson, D., Silge, J., 2021. Tidytext: Text mining using dplyr,
-ggplot2, and other tidy tools.
-
-\leavevmode\vadjust pre{\hypertarget{ref-romeroChildrenExperiencesEnjoyment2015}{}}%
-Romero, V., 2015. Children's experiences: Enjoyment and fun as
-additional encouragement for walking to school. Journal of Transport \&
-Health 2, 230--237.
-doi:\href{https://doi.org/10.1016/j.jth.2015.01.002}{10.1016/j.jth.2015.01.002}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rothmanSchoolEnvironmentStudent2017}{}}%
-Rothman, L., Buliung, R., Howard, A., Macarthur, C., Macpherson, A.,
-2017. The school environment and student car drop-off at elementary
-schools. Travel Behaviour and Society 9, 50--57.
-doi:\href{https://doi.org/10.1016/j.tbs.2017.03.001}{10.1016/j.tbs.2017.03.001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rothmanAssociationsParentsPerception2015}{}}%
-Rothman, L., Buliung, R., To, T., Macarthur, C., Macpherson, A., Howard,
-A., 2015. Associations between parents perception of traffic danger, the
-built environment and walking to school. Journal of Transport \& Health
-2, 327--335.
-doi:\href{https://doi.org/10.1016/j.jth.2015.05.004}{10.1016/j.jth.2015.05.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rothmanActiveSchoolTransportation2021}{}}%
-Rothman, L., Hagel, B., Howard, A., Cloutier, M.S., Macpherson, A.,
-Aguirre, A.N., McCormack, G.R., Fuselli, P., Buliung, R., HubkaRao, T.,
-Ling, R., Zanotto, M., Rancourt, M., Winters, M., 2021. Active school
-transportation and the built environment across canadian cities:
-Findings from the child active transportation safety and the environment
-(CHASE) study. Preventive Medicine 146, 106470.
-doi:\href{https://doi.org/10.1016/j.ypmed.2021.106470}{10.1016/j.ypmed.2021.106470}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rothmanDeclineActiveSchool2018}{}}%
-Rothman, L., Macpherson, A.K., Ross, T., Buliung, R.N., 2018. The
-decline in active school transportation (AST): A systematic review of
-the factors related to AST and changes in school transport over time in
-north america. Preventive Medicine 111, 314--322.
-doi:\href{https://doi.org/10.1016/j.ypmed.2017.11.018}{10.1016/j.ypmed.2017.11.018}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schoeppeAssociationsChildrenActive2015}{}}%
-Schoeppe, S., Duncan, M.J., Badland, H.M., Oliver, M., Browne, M., 2015.
-Associations between children's active travel and levels of physical
-activity and sedentary behavior. Journal of Transport \& Health 2,
-336--342.
-doi:\href{https://doi.org/10.1016/j.jth.2015.05.001}{10.1016/j.jth.2015.05.001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-text2vec}{}}%
-Selivanov, D., Bickel, M., Wang, Q., 2020. text2vec: Modern text mining
-framework for r.
-
-\leavevmode\vadjust pre{\hypertarget{ref-silgeTextMining2021}{}}%
-Silge, J., Robinson, D., 2022. Text mining with r: A tidy approach
-{[}WWW Document{]}. URL \url{https://www.tidytextmining.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-starkExploringIndependentActive2018}{}}%
-Stark, J., Frühwirth, J., Aschauer, F., 2018. Exploring independent and
-active mobility in primary school children in vienna. Journal of
-Transport Geography 68, 31--41.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2018.02.007}{10.1016/j.jtrangeo.2018.02.007}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vandenbergFactorsAffectingParental2020}{}}%
-van den Berg, P., Waygood, E.O.D., van de Craats, I., Kemperman, A.,
-2020. Factors affecting parental safety perception, satisfaction with
-school travel and mood in primary school children in the netherlands.
-Journal of Transport \& Health 16, 100837.
-doi:\href{https://doi.org/10.1016/j.jth.2020.100837}{10.1016/j.jth.2020.100837}
-
-\leavevmode\vadjust pre{\hypertarget{ref-waygoodCO2ValenceFraming2018}{}}%
-Waygood, E.O.D., Avineri, E., 2018. CO2 valence framing: Is it really
-any different from just giving the amounts? Transportation Research Part
-D: Transport and Environment 63, 718--732.
-doi:\href{https://doi.org/10.1016/j.trd.2018.07.011}{10.1016/j.trd.2018.07.011}
-
-\leavevmode\vadjust pre{\hypertarget{ref-waygoodChildrenTravelIncidental2015}{}}%
-Waygood, E.O.D., Friman, M., 2015. Children's travel and incidental
-community connections. Travel Behaviour and Society 2, 174--181.
-doi:\href{https://doi.org/10.1016/j.tbs.2015.03.003}{10.1016/j.tbs.2015.03.003}
-
-\leavevmode\vadjust pre{\hypertarget{ref-waygoodTransportChildrenWellbeing2020}{}}%
-Waygood, E.O.D., Friman, M., Olsson, L.E., Mitra, R. (Eds.), 2020.
-Transport and children's wellbeing. {Elsevier}, pp. i--ii.
-doi:\href{https://doi.org/10.1016/B978-0-12-814694-1.09993-0}{10.1016/B978-0-12-814694-1.09993-0}
-
-\leavevmode\vadjust pre{\hypertarget{ref-weathersDevelopmentsFramingClimate2016}{}}%
-Weathers, M.R., Kendall, B.E., 2016. Developments in the framing of
-climate change as a public health issue in US newspapers. Environmental
-Communication 10, 593--611.
-doi:\href{https://doi.org/10.1080/17524032.2015.1050436}{10.1080/17524032.2015.1050436}
-
-\leavevmode\vadjust pre{\hypertarget{ref-westmanWhatDrivesThem2017}{}}%
-Westman, J., Friman, M., Olsson, L.E., 2017a. What drives them to drive?
-\textemdash Parents' reasons for choosing the car to take their children
-to school. Frontiers in Psychology 8.
-doi:\href{https://doi.org/10.3389/fpsyg.2017.01970}{10.3389/fpsyg.2017.01970}
-
-\leavevmode\vadjust pre{\hypertarget{ref-westmanTravelChildWellbeing2020}{}}%
-Westman, J., Friman, M., Olsson, L.E., 2020. Travel and child wellbeing:
-The psychological and cognitive domains, in: Waygood, E.O.D., Friman,
-M., Olsson, L.E., Mitra, R. (Eds.), Transport and Children's Wellbeing.
-{Elsevier}, pp. 41--59.
-doi:\href{https://doi.org/10.1016/B978-0-12-814694-1.00003-8}{10.1016/B978-0-12-814694-1.00003-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-westmanChildrenTravelSchool2017}{}}%
-Westman, J., Olsson, L.E., Gärling, T., Friman, M., 2017b. Children's
-travel to school: Satisfaction, current mood, and cognitive performance.
-Transportation 44, 1365--1382.
-doi:\href{https://doi.org/10.1007/s11116-016-9705-7}{10.1007/s11116-016-9705-7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
-Wickham, H., 2019. Stringr: Simple, consistent wrappers for common
-string operations.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-reshape2}{}}%
-Wickham, H., 2020. reshape2: Flexibly reshape data: A reboot of the
-reshape package.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
-Wickham, H., 2021. Tidyr: Tidy messy data.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
-Wickham, H., Chang, W., Henry, L., Pedersen, T.L., Takahashi, K., Wilke,
-C., Woo, K., Yutani, H., Dunnington, D., 2021a. ggplot2: Create elegant
-data visualisations using the grammar of graphics.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
-Wickham, H., François, R., Henry, L., Müller, K., 2021b. Dplyr: A
-grammar of data manipulation.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
-Wickham, H., Hester, J., Bryan, J., 2021c. Readr: Read rectangular text
-data.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-word2vec}{}}%
-Wijffels, J., 2021. word2vec: Distributed representations of words.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wilsonUnderstandingChildParent2018}{}}%
-Wilson, K., Clark, A.F., Gilliland, J.A., 2018. Understanding child and
-parent perceptions of barriers influencing children's active school
-travel. BMC public health 18, 1053.
-doi:\href{https://doi.org/10.1186/s12889-018-5874-y}{10.1186/s12889-018-5874-y}
-
-\leavevmode\vadjust pre{\hypertarget{ref-zwertsHowChildrenView2010}{}}%
-Zwerts, E., Allaert, G., Janssens, D., Wets, G., Witlox, F., 2010. How
-children view their travel behaviour: A case study from flanders
-(belgium). Journal of Transport Geography, Special {section} on
-{Alternative Fuels} and {Vehicles} 18, 702--710.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2009.10.002}{10.1016/j.jtrangeo.2009.10.002}
-
-\end{CSLReferences}
+\renewcommand\refname{References}
+\bibliography{bibliography.bib}
 

### 2023-05-23 editorial-materials/YTRA-D-22-01243-response-to-reviewers.Rmd
Revisions after feedback from TR-A

---
title: "How is active school travel framed in Ontario, Canada?"
output: pdf_document
link-citations: yes
linkcolor: blue
bibliography: 
  - '`r system("kpsewhich ../AST-Framing-Ontario/bibliography.bib", intern=TRUE)`'
---

# Responses to reviewers

We wish to thank both reviewers for their constructive feedback. We feel that the paper has been much improved as a result of responding to their comments.

## Reviewer 1

### Comment 1 {#r1-comment-1}

> The authors have used topic modelling to study policy centred and academic writing about active transportation to school in Ontario, Canada. I was quite fascinated by the approach - the paper presents a new way of looking at a vast grey and peer reviewed literature on school travel that has developed over several decades.

Thank you for your kind comments and generous feedback.

### Comment 2 {#r1-comment-2}

> I think the authors should offer more detail on their search strategy beyond, in section 4.1.2, simply saying - we conducted a search using Web of Science. Digging into and report search method - and why/how such decisions are made is an important piece of work like this. Why did you limit your search to the fields indicated? How did you arrive at your search strings/keywords? Having some reporting here, similar to what one would find in a review paper (systematic, scoping, or narrative for that matter) would be useful.

Thank you for this comment. We were too terse with our reporting of the search protocol in the earlier version of the paper. This has been rectified in the current version, where we add relevant details, as follows.

The search was conducted using Web of Science's Core Collection. This was done in the Winter of 2021 and the parameters we used were {active OR walk* or cycl* or bicycl*} AND {"school travel"}. Initially, we found 322 papers, which we reduced to 250 after selecting only papers in the fields of transportation, planning, urban studies, geography, and public health. These fields were chosen because they had the greatest volume of documents and/or were of disciplinary interest to the authors. This list with 250 documents was then manually curated by the authors to ensure that all documents were relevant. This was done by checking the title and reading the abstract of the papers. For example, a paper with the title "Impact of automated photo enforcement of vehicle speed in school zones" [@quistberg2019impact] was excluded as being tangential to our research; the abstract of another paper revealed that it was mainly concerned with survey methods: "Common methods for measuring mode share include Hands Up surveys and family surveys, but these require teacher and parental involvement." [@sersli2019getting]. After this process, our academic corpus comprised 227 journal articles that were readied for analysis.

### Comment 3 {#r1-comment-3}

> I think section 5, and the paper overall, could be strengthened by writing a bit more on the relationship between this automated topic modelling approach, and traditional forms of qualitative thematic analysis - some reflection on the possibility of generating similar or different results, using either approach - would be quite fascinating and helpful. I couldn't help but wonder if the authors considered this approach to be a replace for .... or in addition too, traditional - less automated approaches. Certainly one advantage is just being able to handle the volume of data.

Thank you for this comment. We have added the following to the concluding section:

Finally, we would like to close with a brief note on the methodology. Natural language processing and analysis of frames are still not widely adopted in transportation research. Based on our experience, we tend to see computer-assisted text analysis as a complement rather than a substitute to expert reading of the documents. We would not recommend to proceed to interpretation without reading the documents, but the supervised automation helps to detect patterns that can be validated by an expert based on spot checks or more in-depth reading of the original sources. Like with any qualitative research, interpretation of the frames may differ by expert; in this research we aimed to develop a consensus interpretation by involving all authors in the discussion of the results. Furthermore, the research was conducted as an open, reproducible project: all code and data are available in a public repository^[\url{https://github.com/desjae/AST-Framing-Analysis-Ontario}], which means that all our assumptions are open to scrutiny. Moreover, other researchers can refer to the repository to expand or challenge our conclusions.

### Comment 4 {#r1-comment-4}

> This brings me to my primary concern - I couldn't help but wonder if this piece might be a better fit to TR-B or C - given the emphasis on demonstrating method/tools - and the production of conclusions that are rather unsurprising - the last sentence of the paper alone is something that has been the focus of much work, in practice, for decades.

Thank you for sharing this concern. The methods are not really new outside of their application to this research. Natural language processing is a field mature enough to have its own textbooks; framing analysis is also widespread, although its use in transportation research remains limited. We do not think of either method as emerging technologies or sufficiently innovative to make this a "methodologica" paper. Instead, what we think is new is the ability of these methods to reveal something interesting about the effectiveness of transportation policy.

The last sentence in the original paper reads "STP stakeholders should emphasize why AST rates should increase in local communities and how the negative effects of nonactive modes to school may impact children's health and wellbeing". It is true that there is abundant research about the negative effects of nonactive modes, and most experts would agree that those negative effects explain why active travel rates should increase. What is new is what you astutely note in the following comment: despite all this wealth of knowledge, we don't seem to be further along in terms of convincing the public of buying into active travel policies. Research into how active travel is framed can help us understand what needs to be done to craft more effective communications and shared meanings of the relevant issues.

### Comment 5 {#r1-comment-5}

> The same can be said of the first sentence of section 7.2 - i.e, the problem is the car, and so we need to make cars seem less helpful to the cause. At the same time, the wide ranging scope of the analysis somewhat interestingly tells us that despite all of this research and policy work - we are somehow no further along (overall) than perhaps we were at the very beginning.

This is a very shrewd comment that in our opinion bangs the nail right on the head: the problem is not so much that we don't know that the problem is the car. The problem is that we don't know how to effectively communicate that knowledge to a variety of stakeholders for the purpose of creating shared meanings that can support policy development and implementation. By examining the case of AST in Ontario we find that the framing of transportation in communities is reasonable but anodyne. It downloads responsibility for change to individuals and does not make an effective call for collective action. The tone is positive and does not convey urgency about some critical stakes (e.g., climate change). In essence, the framing can be likened to "eating spinach is good for you; if you decide to eat spinach we can tell you where to buy some". We cannot imagine anyone arguing that eating spinach is bad, but it is questionable how effective this message would be to persuade people to eat spinach.

We tried to capture these ideas in the rewritten abstract of the paper:

Active school travel (AST) is a relevant policy issue in Ontario, Canada, as reflected in provincial support for school travel planning (STP) efforts. Two pillars of school travel plans are education and encouragement. For these pillars to stand, all relevant stakeholders must be cognizant of and understand well the issues and stakes. For this reason, how AST is communicated to them is essential. In this research we adopt frame analysis to investigate the way various organizations communicate around AST to the public. A frame is a central organizing idea or story line that provides meaning to a particular phenomenon, and helps to set the parameters for conversations about policy. In the case of AST, framing can influence what policy alternatives are perceived as available by children, parents, and their wider communities. To investigate framing of AST in Ontario we use natural language processing techniques to analyze publicly available documents from Ontario stakeholders involved in school travel planning. We then compared the findings from these documents to a selection of academic studies on AST. We conclude that framing of AST in Ontario is mostly empirical-scientific and largely in agreement with academic research on AST. On the other hand, it it does not appeal to moral reasons for change, and is therefore oddly soothing and lacking in urgency. Furthermore, the frames used download responsibility for change to households, which limits the scope of policy alternatives by keeping collective action out of the frame.

\newpage

## Reviewer 2

### Comment 1 {#r2-comment-1}

> This paper is well written and the analysis is conducted rigorously and it is interesting.

We are grateful for your comments and feedback.

### Comment 2 {#r2-comment-2}

> However in my opinion is not within the scope of Transportation Research Part A. I did not understand the link with the policy and practice.

We wish to reiterate our response to [Reviewer 1](#r1-comment-4). We part from the working hypothesis that if the Editor, having perused the paper, decided to send it out for peer-review, they must have decided that the paper is within the scope of the journal.

Having said that, we made a renewed effort to clarify the link of our research to policy and practice. In particular, we think Reviewer 1 right on target with their [comment](#r1-comment-5): despite the mass of academic research in transportation, we do not seem to be further along in effectively communicating with the public the ever higher stakes of our ongoing love affair with the car. The problem does not seem to be the lack of policies, but awareness and buy-in by the public. Why is this the case when it comes to active school travel?

The paper has been reworked to (hopefully) improve the link between framing and policy. The argument goes as follows:

1. "Public policies are directly tied to the constant shaping of collective identities" [@beland2014developing, p. 551; also see beland2008nationalism; @akerlof2010identity]

2. Collective identities (and therefore policy) are shaped by frames: frames can activate or restrict particular responses in the intended audience [@panFramingAnalysisApproach1993]. They do this by position existing solutions as suitable to issues, which limits awareness of other policy approaches [@mahFramecriticalPolicyAnalysis2014] or, contrariwise, by revealing more diverse policy options than conventional wisdom would have [@bosomworth2015climate].

3. Content analysis of documents in the case of Ontario uncovers some reasons why AST, despite being a policy issue, has struggled to reverse motorization trends.

4. Active school travel is framed in Ontario in such a way that it downloads the responsibility for action to individuals; it does not make a convincing call for collective action. It is also fairly neutral at a time when some stakes (e.g., climate change) are extremely high. By adopting an empirical-scientific approach, it does not appeal to moral reasons for change. And it ends up being lukewarm and anodyne.

We tried to capture these ideas in the rewritten abstract of the paper:

Active school travel (AST) is a relevant policy issue in Ontario, Canada, as reflected in provincial support for school travel planning (STP) efforts. Two pillars of school travel plans are education and encouragement. For these pillars to stand, all relevant stakeholders must be cognizant of and understand well the issues and stakes. For this reason, how AST is communicated to them is essential. In this research we adopt frame analysis to investigate the way various organizations communicate around AST to the public. A frame is a central organizing idea or story line that provides meaning to a particular phenomenon, and helps to set the parameters for conversations about policy. In the case of AST, framing can influence what policy alternatives are perceived as available by children, parents, and their wider communities. To investigate framing of AST in Ontario we use natural language processing techniques to analyze publicly available documents from Ontario stakeholders involved in school travel planning. We then compared the findings from these documents to a selection of academic studies on AST. We conclude that framing of AST in Ontario is mostly empirical-scientific and largely in agreement with academic research on AST. On the other hand, it it does not appeal to moral reasons for change, and is therefore oddly soothing and lacking in urgency. Furthermore, the frames used download responsibility for change to households, which limits the scope of policy alternatives by keeping collective action out of the frame.

### Comment 3 {#r2-comment-3}

> The research finds that a specific policy is not working as intended and it seems to be very expensive. How can this result be generalised and used to say if any policy is "good value for money"? The authors need to convince me about the practical application of their method. Can you identify clear policy recommendations that can be used in practice?

Point 4 [above](#r2-comment-2) highlights some things that we learn from this research, and suggests some ways to change the way AST is framed to make them more efficient.

### Comment 4 {#r2-comment-4}

> Otherwise the paper, even if interesting, is only methodological and would fit better some journals that focuses on text analysis.

Thank you for your opinion. We will defer to the editor on the matter of scope of the journal.

\newpage

## References

### 2023-05-23 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Revisions after feedback from TR-A

@@
 ---
-title: How is active school travel framed in Ontario, Canada?
+title: "Framing active school travel in Ontario: , or how spinach is good for you"
 author:
@@
 abstract: |
-  Active school travel (AST) has been increasingly encouraged by various stakeholders in Ontario, Canada through efforts such as school travel planning.
-Education strategies like workshops or resources that promote AST are commonly implemented.
-The framing of AST through such strategies may influence how walking and bicycling to school are perceived by parents.
-It may also draw attention to AST as an issue affecting children's health which could motivate behaviour change.
-We used natural language processing, including topic modelling, to examine how AST is framed in publicly available documents from Ontario stakeholders involved in school travel planning.
-We then compared the findings from these documents to a selection of studies on AST and explored similarities between the two.
-We found that AST is framed in two ways: i) as a health and environmental issue; and ii) as an accessible and feasible transport option for children and parents.
-The frames encourage children and parents to adopt AST given its health and environmental benefits by providing resources to support behaviour change.
-The benefits of AST and strategies to support AST that are communicated by stakeholders are consistent with the evidence from academic research.
-While these frames present AST in a positive light, they may not encourage parents to view current household travel behaviours as unhealthy for their children or their community.
-Stakeholders promoting AST in Ontario should further problematize the decline of AST and challenge the norm of driving children to school.
+  Active school travel (AST) is a relevant policy issue in Ontario, Canada, as reflected in provincial support for school travel planning (STP) efforts.
+Two pillars of school travel plans are education and encouragement.
+For these pillars to stand, all relevant stakeholders must be cognizant of and understand well the issues and stakes.
+For this reason, how AST is communicated to them is essential.
+In this research we adopt frame analysis to investigate the way various organizations communicate around AST to the public.
+A frame is a central organizing idea or story line that provides meaning to a particular phenomenon, and helps to set the parameters for conversations about policy.
+In the case of AST, framing can influence what policy alternatives are perceived as available by children, parents, and their wider communities.
+To investigate framing of AST in Ontario we use natural language processing techniques to analyze publicly available documents from Ontario stakeholders involved in school travel planning.
+We then compared the findings from these documents to a selection of academic studies on AST.
+We conclude that framing of AST in Ontario is mostly empirical-scientific in style, and largely in agreement with academic research on AST.
+On the other hand, it it does not appeal to moral reasons for change, and is therefore oddly soothing and lacking in urgency.
+Furthermore, the frames used download responsibility for change to households, which limits the scope of policy alternatives by keeping collective action out of the frame.
+
 keywords: 
@@
 Another study in London, Ontario, reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012].
-From a public health perspective, increasing active travel to school represents a major opportunity to improve children's health and wellbeing.
+From a public policy perspective, increasing active travel to school represents a major opportunity to improve children's health and wellbeing [@faulknerActiveSchoolTransport2009], to mitigate traffic and improve perceptions of safety [@rothmanAssociationsParentsPerception2015], as well as to reduce carbon and other noxious emissions [@bearman2014modelling; @goodman2019scenarios].
 
 To promote this trend, in 2017 the Government of Ontario began to support communities develop AST initiatives through a program called _Ontario Active School Travel_ (OAST).
-By 2021, the program, run by Green Communities Canada had awarded over CAD 2 million and provided resources to over 25 projects across Ontario [@GreenCommunities2016].
+By 2021, the program, run by _Green Communities Canada_ had awarded over CAD 2 million and provided resources to over 25 projects across Ontario [@GreenCommunities2016].
 A popular intervention in many communities is school travel planning (STP) [see @GreenCommunitiesProjects].
@@
 
-Framing AST by STP stakeholders to a target audience (e.g., parents or the general public) can raise awareness of the relevant issues and influence how active travel to school is perceived.
+How AST is presented to a target audience (e.g., parents or the general public) is essential to define the parameters of what is possible policy-wise.
+Drawing from concepts in communication studies, the objective of this paper is to investigate how AST is framed in Ontario.
 Gamson and Modigliani [-@gamsonChangingCulture1987] define a frame as a “central organizing idea or story line that provides meaning” to a particular phenomenon.
 A frame can enable individuals "to locate, perceive, identify, and label" information pertaining to various dimensions of an issue [@goffmanFrameAnalysisEssay1974].
-Therefore, stakeholders involved in STP efforts can play a role in shaping public perception about AST to attract greater attention and recognition as a "problem" that needs to be addressed through behaviour change or new policies.
-
-After significant investment of human and financial resources to boost rates of AST in Ontario over the past few years, in this paper we ask this central question: How is AST framed to the public in Ontario?
-The following questions are subsidiary and help us address this main question: What benefits of AST are communicated to the public?
-What solutions are proposed to increase AST?
-
-We approach this question by means of natural language processing, and examine how three STP stakeholder groups in Ontario (municipalities, school boards, and transportation consortia) frame AST.
-We assemble a corpus of texts from public sources that present information for the general public or parents who are interested in AST.
-We examine word frequency, bigrams, and concordances in these selected documents, and also identify key topics presented by each stakeholder group.
+From this perspective, stakeholders involved in STP efforts play an important role in shaping public perception about AST by generating frames that  create meaning, thus influencing the degree of attention and recognition of a "problem" that needs to be addressed through behaviour change or new policies.
+
+Our research is supported by natural language processing techniques, applied to the analysis of documents produced by three STP stakeholder groups in Ontario (municipalities, school boards, and transportation consortia).
+We assemble a corpus of texts from public sources that present information for the general public or parents who are interested in AST and examine word frequency, bigrams, and concordances in these selected documents.
+Furthermore, we use topic analysis to identify themes presented by each stakeholder group.
 We then compare the findings from these documents to a selection of studies on AST and explore the extent to which there is concordance between the scholarly literature on AST and materials shared with the public.
+The results of this analysis, along with spot checks of the corpus by the authors, lead us to conclude that AST if framed as a matter of individual choices instead of collective action.
+The message is reasonable but anodyne, and it fails to communicate a sense of urgency about health and environmental issues, which may help to explain the limited success of policy.
+
+<!-- Compare the definition of "frame" to that of "narrative":
+
+FRAME
+A frame is a central organizing idea or story line that provides meaning to a particular phenomenon, and that enables individuals to locate, perceive, identify, and label information pertaining to various dimensions of an issue.
+
+NARRATIVE (See [@liu2023narrative]
+
+A narrative is defined as “a representation of connected events and characters that has an identifiable structure, is bounded in space and time, and contains implicit or explicit messages about the topic being
+addressed”)
+-->
 
@@
 
-Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behaviour is understood within the context of household, social, neighbourhood, and policy environments.
+<!--Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behaviour is understood within the context of household, social, neighbourhood, and policy environments.
 The SEM helps to identify multiple determinants that need to be addressed by school-based interventions to increase AST, with the consensus being that interventions should target multiple levels [@mitraIndependentMobilityMode2013].
-Rather than describing an extensive list of factors that influence AST and mode choice in Canada [e.g., @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], we discuss a few potentially modifiable determinants that may be targeted for change through STP.
-
-Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], as well as daily parental support [@mahDoesParentalSupport2017a].
-This indicates that shifting parental perceptions and habits is important.
-Convenience and inclement weather have been cited by parents as barriers to AST [@buliungSchoolTravelPlanning2011].
-Parental perceptions of the built or school environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and their children's skills [@mammenUnderstandingDriveEscort2012; @faulknerWhatQuickestEasiest2010] also influence mode choice to school.
-
-Distance between home and school is most negatively associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
+-->
+
+Rather than describing an extensive list of factors that influence AST and mode choice for travel to school in Canada [e.g., @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], we focus on two key aspects that may be targeted from a policy perspective: perceptions and behaviors by parents and built environmental factors.
+
+<!-- Influence of perceptions -->
+
+First, research has found that parents are key decision-makers with respect to children's form of travel to school [@rothmanAssociationsParentsPerception2015].
+Particularly, parental perceptions of the built or school environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010; @mandic2020differences] and their children's skills [@mammenUnderstandingDriveEscort2012; @faulknerWhatQuickestEasiest2010] tend to influence mode choice to school.
+Furthermore, children's mode choice to school is strongly influenced by their parents' travel behaviours, the complexity of their household's travel needs [@buliungLivingJourneySchool2021], as well as daily parental support [@mahDoesParentalSupport2017a].
+This suggests that shifting parental perceptions and habits is important.
+
+<!-- Physical factors -->
+
+With respect to the built environment, distance between home and school is most negatively associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
 Many studies have also found that the quality of the built environment along the route to school and around the school site [@ikedaAssociationsChildrenActive2018; @rothmanActiveSchoolTransportation2021] and provision of active travel infrastructure [@chenPromotingActiveStudent2018; @pontEnvironmentalCorrelatesChildren2009] facilitate AST.
 Canadian youth report that they feel most safe bicycling on streets in their neighbourhood or that have low volumes of traffic [@TACbikeinfra2020].
-Finally, concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012], which highlights that the volume and speed of cars can be a concern or deterrent for AST.
-
-School travel planning in Canada and relevance of framing analysis
+Finally, concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012]: ironically, concerns about traffic become a self-fulfilling prophecy.
+
+School travel planning in Canada and relevance of frames {#stp-frames}
 ======================
 
-School travel planning (STP) has been implemented in Canada since at least the late 2000s.
+AST has become a policy issue on the education and public health agendas in Ontario, supported, albeit in a modest way, by financial contributions from the provincial government.
+Still, the support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
+One of the main vehicles to promote AST is school travel planning (STP), which has been implemented in Canada since at least the late 2000s.
 Within the STP process, facilitators establish multi-sector committees which intervene at the participating school through a range of activities consisting of _[E]ducation_ strategies, _[E]ncouragement_ through in-person events or programs, _[E]ngineering_ improvements to or around the school site, and _[E]nforcement_ of traffic speeds around schools [or 4Es, @langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
@@
 
-By providing a "central organizing idea or story line" [@gamsonChangingCulture1987] framing of AST seems particularly important to shift parental attitudes and perceptions, given their reported influence on children's travel mode to school.
-Scholars in the field of political communications have proposed that communicators, such as the media or institutions, construct the narrative of a frame for policy positions or public issues in order to activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
-Organized groups of stakeholders can employ similar methods to attract attention to particular issues.
-Framing can be used to position existing solutions as suitable to address particular issues [@mahFramecriticalPolicyAnalysis2014], which may prevent the public from being aware of other policy approaches that challenge the status quo.
-The way policy issues are framed is ultimately important to understand because it plays a role in either altering or preserving the existing social perceptions.
-Finally, the ideas that are communicated by a particular frame can be either positive or negative [@waygoodCO2ValenceFraming2018].
-There is evidence that negative framing may be more effective at motivating individuals, for example, to change transport modes to reduce CO2 emissions [@waygoodCO2ValenceFraming2018].
-
-Framing of AST could also affect broader support in the community.
+The relevance of policy frames is highlighted by @beland2014developing, who remarks "framing processes as public relations are central to policy issues related to sustainable transportation".
+Seeing how highly influential parental perceptions are to AST, it is important to understand AST-related communications, since the construction of frames for policy positions or public issues can activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
+Besides parents and children, framing can also affect broader policy support for AST in the community.
 Municipal representatives are perceived to be instrumental but the involvement of other stakeholder groups (e.g., busing consortia representatives and local residents) can be lacking [@buttazzoniSupportingActiveSchool2018].
-In Ontario, it is reasonable to say that AST has become a policy issue on the education and public health agendas, supported, albeit in a modest way, by financial contributions from the provincial government.
-Still, the support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
-
-Since STP activities heavily focus on education or encouragement [@buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014; @buttazzoniSupportingActiveSchool2018], it is important that parents and communities are receptive to the goals of STP [@buttazzoniSupportingActiveSchool2018].
-Parents have been found to express different understandings, language, and perceptions than planners of how the built environment can influence school travel [@buliungLivingJourneySchool2021].
-This is also true when it comes to other factors like convenience of different modes to school [@langUnderstandingModalChoice2011].
-STP stakeholders must pay special attention to parents' understanding of the decline of AST as a problem, which may affect their receptivity to proposed solutions.
-
-The success of STP interventions would likely depend on parental judgments of factors that are related to school travel, as well as support from key policy makers.
-For example, parents have been found to view mixed land use as conducive for driving, despite transport planners viewing neighbourhoods with mixed uses as key for encouraging more active travel [@buliungLivingJourneySchool2021].
-Therefore, stakeholders involved in STP must make conscious choices about the proposed solutions and potential benefits of AST that are communicated to parents and the general public through publicly available content to convey its importance as a policy issue and to facilitate adoption of AST.
+In this sense, framing can be used to position existing solutions as suitable to address particular issues [@mahFramecriticalPolicyAnalysis2014], which may prevent the public from being aware of other policy approaches that challenge the status quo.
+Contrariwise, framing can be instrumental to revealing more diverse policy options than more diverse policy options than conventional wisdom would have [@bosomworth2015climate].
+Ultimately, it is important to understand framing of policy issues because creating meaning through frames contributes to the constant process of shaping of our collective identities, uncovering what we collectively find (un)acceptable and why [@beland2014developing].
+
+Given the heavy focus of STP activities on education or encouragement [@buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014; @buttazzoniSupportingActiveSchool2018], it is important for the issues to be effectively framed.
+In the past, parents have been found to express different understandings, language, and perceptions than planners of how the built environment can influence school travel: while parents tend to view mixed land use as conducive for driving, transport planners see mixed uses as a key for encouraging more active travel [@buliungLivingJourneySchool2021].
+Similarly mismatched understandings have been detected with respect to factors like the convenience of different modes to school [@langUnderstandingModalChoice2011].
+As a consequence, STP stakeholders must pay special attention to parents' and communities' understanding of the decline of AST as a problem, which may affect their receptivity to proposed solutions [@buttazzoniSupportingActiveSchool2018].
+
+So framing is important, but not all frames are equally effective.
+Frames can appeal to economic reasons, to science and logic, or to moral obligation.
+For example, @severson2015moral report that overall support for climate change policy is increased more when scientific frames, secular moral frames, and economic equity frames are used, compared to economic efficiency or religious moral frames.
+Frames can also be positive or negative, and there is evidence that negative framing may be more effective at motivating individuals, for example, to change transport modes to reduce CO2 emissions [@waygoodCO2ValenceFraming2018].
+As well, the effectiveness of the framing depends on the psychological distance to the relevant issues: how socially, temporally, geographically, or hypothetically close an individual perceives themselves to the issues can affect their support for various policies [@maiella2020psychological].
+For this reason, stakeholders involved in STP must make conscious choices about how issues surrounding AST are communicated if the goal is to increase support for and buy-in of AST policies.
 
@@
 We assembled a collection of publicly available documents that were sourced online from the main stakeholder groups involved in STP initiatives in Ontario: i) school boards (public or Catholic and English-speaking only); ii) municipal governments; and iii) transportation consortia.
-The latter involve a collaboration between municipal regions and school boards to deliver more efficient and timely transportation services to schools in each region.
+The latter involve collaborations between municipal regions and school boards to deliver more efficient and timely regional transportation services to schools.
 Non-profit organizations, police services, and advocacy groups are other stakeholders who often play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they do not consistently participate in STP initiatives in Ontario.
@@
 Webpages from STP stakeholder groups were included in our analysis if they were findable.
-This primary criterion was important since our analysis pertains to how such issues are framed to the general public.
+This primary criterion was important since our analysis pertains communication of issues to the general public.
 Thus, we included only webpages that were readily accessible, which we defined as requiring no more than four links from the initial Google search to reach.
@@
 
-We conducted a search on Web of Science for scholarly papers on the topic of school travel.
-We limited our search to the fields of public health, transportation, planning, urban studies, and geography.
-This initial corpus was curated by the authors to ensure that all documents were relevant.
-After this step, 227 journal articles were readied for analysis.
+We conducted a search on Web of Science for scholarly papers on the topic of school travel using Web of Science's Core Collection.
+The search was conducted in the Winter of 2021 and the parameters used were {active OR walk* or cycl* or bicycl*} AND {"school travel"}.
+Initially, we found 322 papers, which we reduced to 250 after selecting only papers in the fields of transportation, planning, urban studies, geography, and public health.
+These fields were chosen because they had the greatest volume of documents and/or were of disciplinary interest to the authors.
+This list with 250 documents was then manually curated by the authors to ensure that all documents were relevant.
+This was done by checking the title and reading the abstract of the papers.
+For example, a paper with the title "Impact of automated photo enforcement of vehicle speed in school zones" [@quistberg2019impact] was excluded as being tangential to our research; the abstract of another paper revealed that it was mainly concerned with survey methods: "Common methods for measuring mode share include Hands Up surveys and family surveys, but these require teacher and parental involvement." [@sersli2019getting].
+After this process, our academic corpus comprised 227 journal articles that were readied for analysis.
 
@@
 
-We use topic modelling to analyze the documents retrieved.
-Topic modelling is a natural language processing technique used to analyze text to identify the language and concepts being communicated.
-This method is practical for researchers working with large amounts of text because it replaces the manual coding of topics that would normally take place to analyze or summarize textual data [@jacobiQuantitativeAnalysisLarge2016].
-We primarily use the following software: `tidytext` [@R-tidytext], `topicmodels` [@R-topicmodels], `word2vec` [@R-word2vec], and `wordcloud` [@R-wordcloud].
+Topic modelling was used to analyze the documents retrieved.
+This is a natural language processing technique used to analyze text to identify the language and concepts being communicated.
+This method is practical for researchers working with large amounts of text because it can assist and complement the manual coding of topics that would normally take place to analyze or summarize textual data [@jacobiQuantitativeAnalysisLarge2016].
+We primarily use the following `R` packages: `tidytext` [@silge2016tidytext], `topicmodels` [@grun2011topic], `word2vec` [@wijffels2021word2vec], and `wordcloud` [@fellows2018wordloud].
 
@@
 This paper is an example of open and reproducible research that uses only open software.
-Following best practices in spatial data science [@brunsdon2020opening], the code and data needed to reproduce our research or conduct a similar analysis for other regions are available for download upon request.
+The source document is an R markdown document.
+Following best practices in spatial data science [@brunsdon2020opening], the code and data needed to reproduce our research or conduct a similar analysis for other regions are available in a publicly available repository^[\url{https://github.com/desjae/AST-Framing-Analysis-Ontario}].
 
@@
 Each corpus also has _safety_ and _traffic_ as common words which suggests that these are common concerns for parents.
-The word _physical_ is present in each corpus, but it's not clear what this refers to (e.g, _physical activity_, or the _physical environment_).
+The word _physical_ is present in each corpus, but this could refers to _physical activity_ or the _physical environment_.
 Furthermore, documents from STP stakeholder groups discuss _resources_, _information_, and _services_ about school travel.
-Unlike the academic papers, policy+practice documents include the words _route_ or _routes_ as frequent terms.
+Unlike the academic papers, policy+practice documents frequently include the words _route_ or _routes_.
 This could indicate the role of STP stakeholder groups in identifying safe routes to school to share with parents or families.
@@
 In addition, _time_, _factors_, _environment_, and _age_ are also identified in the academic papers.
-The prevalence of these terms is consistent with an academic focus on exploring the variables that influence mode choice.
+The prevalence of these terms is consistent with an academic focus on exploring the variables that influence travel to school.
 These words are absent from the list of common words in policy+practice documents.
@@
 Examination of document frequency reveals terms that are not present in all policy documents.
-This suggests that although documents pertain to the subject of school travel, not all stakeholders across Ontario disseminate information about AST.
+This suggests that although documents pertain to school travel, not all stakeholders across Ontario disseminate information about AST.
 We manually searched the policy+practice corpus and found that 48% of documents mention AST and 16% mention STP.
@@
 Bigrams refer to a pair of consecutive words.
-We combined all municipality, school board, and transportation consortia documents into the policy+practice.
-Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the policy+practice corpus.
+We combined all municipality, school board, and transportation consortia documents into the policy+practice corpus.
+Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in this corpus.
 This figure highlights the main ideas that are presented to the public in each of the policy corpora.
@@
 We also found _mental health_, _walk zone_, and _green communities_ as common pairs of consecutive words.
-_Green Communities Canada_ is a non-profit organization that has significantly supported AST initiatives through the Ontario Active School Travel program so the high frequency of this term in the policy+practice corpus is not surprising.
+Their presence makes sense given the involvment of  _Green Communities Canada_ in AST initiatives in Ontario.
 Overall, the policy documents from STP stakeholder groups seem to focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or barriers; and iv) supports for AST.
@@
 
-Next, we analyzed bigrams in the academic corpus separately to make comparisons with the policy+practice corpus.
-Figure \ref{fig:academic-visual} indicates that academic papers include several common bigrams that were also found in the policy documents including _physical activity_, which is the top bigram, _traffic safety_, and _safe routes_.
-However, many other factors are identified in the research literature that are not presented to the general public through policy documents.
+Next, we analyzed bigrams in the academic corpus separately to comparE with the policy+practice corpus.
+Figure \ref{fig:academic-visual} indicates that academic papers include several common bigrams that were also found in the policy documents including _physical activity_, which is the top bigram, as well as _traffic safety_ and _safe routes_.
+However, many other factors are identified in the academic corpus that are not presented to the general public through policy documents.
 Terms like _built environment_, _independent mobility_, and _urban form_ are other frequent pairs of consecutive words.
@@
 We experimented with the model by adjusting the number of topics and evaluating the output of terms in each topic.
-We found that there were 9 distinct topics that could be interpreted in the policy+practice corpus and 11 topics in the academic corpus, after which there was too much overlap for the clusters to be meaningfully interpreted.
-Figures \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main terms that are associated with the topics found in each corpus.
+We found that there were 9 distinct topics that could be interpreted in the policy+practice corpus and 11 topics in the academic corpus, after which there was too much overlap for the clusters to be meaningfully distinguished.
+Figures \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main terms associated with the topics found in each corpus.
 
@@
 
-Finally, both AST frames present solutions to encourage AST.
-STP stakeholder groups seem to be communicating that AST is a healthy and easy option as a result of policy changes (e.g., available resources for parents and children) and improvements to the built environment.
+Finally, both AST frames present the benefits of AST.
+STP stakeholder groups seem to be communicating that AST is a healthy and accessible option as a result of school travel plans and improvements to the built environment.
 This could include examples of various efforts that are underway to support AST including route planning.
@@
 
+Beyond supporting communities to develop STPs, these frames tend to place responsibility for change squarely on the members of the community:
+
+> __A way to make sure your child is safe while walking to school is with a ‘walking school bus.’ Here are some tips for a walking schoolbus...[tips]...Have fun!_ (City of Ottawa)
+
 Discussion
@@
 
-Interpretation of the text assisted by natural language processing reveals that AST in Ontario is primarily framed to parents as beneficial to the health and wellbeing of children and to environmental sustainability.
+Interpretation of the text assisted by natural language processing reveals that AST in Ontario is not always communicated to members of the public.
+As noted above, less than 50% of documents from municipalities, school boards, and transportation consortia discuss AST.
+In the rest of the documents, the primary way AST is framed tends to emphasize the benefits to the health and wellbeing of children and to the environment.
 The policy documents reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance are less well-supported in the extant literature [@westmanTravelChildWellbeing2020].
@@
 Neither frame appears to explain why declining rates of AST are a problem or convey any urgency to this issue so that it attracts the attention of parents, the general public, or policy makers.
-Communicating the potential outcomes of increased AST may be persuasive arguments to motivate behaviour change, but these frames do not seem to encourage parents or the general public to view their current behaviour as problematic or unhealthy for their children's development and their community.
-Thus, behaviour change is presented as an option for some but not an imperative for all.
 For example, parents who drive their children to school have reported concerns about traffic volume around schools [@mammenUnderstandingDriveEscort2012], but may not recognize that their own behaviour contributes to the problem that is perceived to prevent their child from safely walking or bicycling to school [@collinsSafeJourneysEnterprising2001].
-Reynard et al.
-[-@reynardGrowthResilienceHow2021] similarly found in their analysis of Canadian municipal documents that one of the dominant frames presented the adoption of behaviours to help mitigate the climate crisis as a choice but not "the expected norm".
-
-We found that the proposed solutions in the secondary frame to increase AST align with different levels of the SEM: 1) behaviour change from households making different travel decisions; 2) policies that create resources for AST; and 3) engineering solutions like bicycle lanes.
+Communicating the potential outcomes of increased AST present the issues in a positive light, but these frames do not seem to encourage parents or the general public to view their current behaviour as problematic or unhealthy for their children and the environment.
+Further, behaviour change is mainly presented as an option for some but not an imperative for all, which keeps collective action through government entities out of the frame.
+This echoes the findings of Reynard et al.
+[-@reynardGrowthResilienceHow2021], who found in their analysis of Canadian municipal documents that one of the dominant frames was to present behaviours that help mitigate the climate crisis as an individual choice but not "the expected norm".
+
+Overall, we find that the proposed solutions in the secondary frame reinforce some of the same ideas: 1) behaviour change from households making different travel decisions (individual responsibility); 2) policies that create resources for AST (mainly through education and plannning); and 3) engineering solutions like bicycle lanes.
 This reflects findings from the AST literature that a range of solutions are needed to address different factors that influence AST [_inter alia, see_ @mitraIndependentMobilityMode2013; @panterAttitudesSocialSupport2010].
 The recognition of engineering changes may reflect the strong engagement of engineering staff and municipal representatives in the Canadian STP process [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015], as well as the evidence that the built environment influences mode choice to school.
-However, it is beyond the scope of this paper to assess whether the proposed solutions are perceived to be sufficient by parents for increasing AST.
+
+As well as what is _in_ the frame, it is also interesting to look for what is _not_.
+As noted, a call for collective action tends to be missing, whereas the positive tone does not convey urgency about some critical stakes, including for instance climate change.
+By presenting the issues in an empirical-scientific way no moral imperative is mobilized to encourage change [@severson2015moral].
 
@@
 
-STP stakeholders should problematize the significant decline in AST that has occurred over recent decades in Canada and emphasize that this issue merits urgent behaviour change.
-A negative framing that challenges the social norm of driving could be more motivational to shift transport modes, which would be consistent with other findings [see @waygoodCO2ValenceFraming2018].
-Policy documents should make it clear that continued use of nonactive modes to school can deprive children of opportunities to increase physical activity and to gain health and social benefits.
-
-There is a noticeable lack of focus on certain household determinants of AST in the two frames that needs to be addressed.
-For example, the role of convenience and inclement weather in shaping household travel decisions [@buliungSchoolTravelPlanning2011] and the complexity of travel arrangements that must be coordinated by households [see @buliungLivingJourneySchool2021] were not found to be discussed.
+As we noted in Section \ref{stp-frames} above, STP in Ontario relies heavily on education and encouragement.
+From the get-go, these are two of the weakest tools in the arsenal of government actions [@ohare1989typology].
+For this reason, it is important that both are used effectively.
+Our analysis leads us to question the efficacy of the frames currently used for talking about AST in Ontario.
+If we had to paraphrase the way AST is framed, it would be like this: "eating spinach is good for you; here are some tips to help you choose spinach." The issues are presented as a matter of personal choice, purely optional, and without a sense of urgency.
+While emphasizing the risks may seem counterproductive, this approach has been found to be effective at motivating change [e.g., @lawlor2018risk; @waygoodCO2ValenceFraming2018].
+Accordingly, communications with the public could emphasize the risks associated with continued use of nonactive modes to school.
+
+In addition to privileging choice, the frames tend to leave out a number of household determinants of AST.
+For example, there was no discussion about the role of convenience and inclement weather in shaping household travel decisions [@buliungSchoolTravelPlanning2011] and the complexity of travel arrangements that must be coordinated by households [see @buliungLivingJourneySchool2021].
 The desire to escort children to school, which has been noted by parents as a reason to continue driving [@westmanWhatDrivesThem2017], is also not adequately addressed by STP stakeholders.
@@
 Framing AST as a developmental opportunity or a rite of passage that children have been denied could challenge the prevailing culture of risk avoidance which discourages parents from letting their children use active modes to school.
-
-Future research and evaluation by STP stakeholders should investigate how parents or the general public respond to messages or information that encourages the adoption of AST and evaluate which are most effective.
-It would be helpful to understand which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST.
-This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.
-If Canadian STP stakeholders wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different materials that communicate why this issue is important to the general public, regardless of whether they currently have children commuting to/from school.
 
@@
 
+In terms of future research, we suggest the need for further investigation into how parents or the general public respond to messages or information that encourages the adoption of AST and evaluate which are most effective.
+It would be helpful to understand which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST.
+This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.
+If Canadian STP stakeholders wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different materials that communicate why this issue is important to the general public, regardless of whether they currently have children commuting to/from school.
+
+Finally, we would like to close with a brief note on the methodology.
+Natural language processing and analysis of frames are still not widely adopted in transportation research.
+Based on our experience, we tend to see computer-assisted text analysis as a complement rather than a substitute to expert reading of the documents.
+We would not recommend to proceed to interpretation without reading the documents, but the supervised automation helps to detect patterns that can be validated by an expert based on spot checks or more in-depth reading of the original sources.
+Like with any qualitative research, interpretation of the frames may differ by expert; in this research we aimed to develop a consensus interpretation by involving all authors in the discussion of the results.
+Furthermore, since the research is an open, reproducible project, all our assumptions are open to scrutiny and use the data to check and/or expand the analysis presented here.
+
 References

### 2023-05-26 editorial-materials/YTRA-D-22-01243-response-to-reviewers.Rmd
Resubmission to TR-A after revisions by ED, DC, DR, EOW, and AP

@@
 ---
-title: "How is active school travel framed in Ontario, Canada?"
+title: "Response to reviewers"
 output: pdf_document
@@
 
-# Responses to reviewers
+We wish to thank both reviewers for their constructive feedback. We feel that the paper has been much improved as a result of responding to their comments.
 
-We wish to thank both reviewers for their constructive feedback. We feel that the paper has been much improved as a result of responding to their comments.
+In particular, we recognize that the methodology we chose is perhaps infrequently applied in transport research.
+That said, the purpose of the paper was to examine the way policy with respect to AST are communicated in Canada's most populous province.
+As the methodology is not common in transportation, we tried to explain more of it, which may be why the paper came off as methologically-focused.
+In this revision, we aimed to strike a balance between the focus (how is AST discussed in policy) and ensuring that readers understood the possibly unfamiliar methods.
 
@@
 Natural language processing is a field mature enough to have its own textbooks; framing analysis is also widespread, although its use in transportation research remains limited.
-We do not think of either method as emerging technologies or sufficiently innovative to make this a "methodologica" paper.
-Instead, what we think is new is the ability of these methods to reveal something interesting about the effectiveness of transportation policy.
+We do not think of either method as emerging technologies or sufficiently innovative to make this a "methodological" paper.
+Instead, what we think is new is the use of these methods to reveal something interesting about the effectiveness of transportation policy.
 
@@
 Having said that, we made a renewed effort to clarify the link of our research to policy and practice.
-In particular, we think Reviewer 1 right on target with their [comment](#r1-comment-5): despite the mass of academic research in transportation, we do not seem to be further along in effectively communicating with the public the ever higher stakes of our ongoing love affair with the car.
+In particular, we think Reviewer 1 is right on target with their [comment](#r1-comment-5): despite the mass of academic research in transportation, we do not seem to be further along in effectively communicating with the public the ever higher stakes of our ongoing love affair with the car.
 The problem does not seem to be the lack of policies, but awareness and buy-in by the public.
@@
 
-1. "Public policies are directly tied to the constant shaping of collective identities" [@beland2014developing, p. 551; also see beland2008nationalism; @akerlof2010identity]
+1. Public policies depend on what we collective believe is possible [@beland2014developing, p. 551; also see @beland2008nationalism; @akerlof2010identity]
 
 2.
-Collective identities (and therefore policy) are shaped by frames: frames can activate or restrict particular responses in the intended audience [@panFramingAnalysisApproach1993].
-They do this by position existing solutions as suitable to issues, which limits awareness of other policy approaches [@mahFramecriticalPolicyAnalysis2014] or, contrariwise, by revealing more diverse policy options than conventional wisdom would have [@bosomworth2015climate].
+Frames are essential for defining the parameters of our collective beliefs: frames can activate or restrict particular responses in the intended audience [@panFramingAnalysisApproach1993] by positioning existing solutions as suitable to issues.
+This can limit awareness of other policy approaches [@mahFramecriticalPolicyAnalysis2014].
+Contrariwise, they can expand the potential of policy by revealing more diverse options than conventional wisdom would have [@bosomworth2015climate].
 
@@
 By adopting an empirical-scientific approach, it does not appeal to moral reasons for change.
-And it ends up being lukewarm and anodyne.
-
-We tried to capture these ideas in the rewritten abstract of the paper:
-
-Active school travel (AST) is a relevant policy issue in Ontario, Canada, as reflected in provincial support for school travel planning (STP) efforts.
-Two pillars of school travel plans are education and encouragement.
-For these pillars to stand, all relevant stakeholders must be cognizant of and understand well the issues and stakes.
-For this reason, how AST is communicated to them is essential.
-In this research we adopt frame analysis to investigate the way various organizations communicate around AST to the public.
-A frame is a central organizing idea or story line that provides meaning to a particular phenomenon, and helps to set the parameters for conversations about policy.
-In the case of AST, framing can influence what policy alternatives are perceived as available by children, parents, and their wider communities.
-To investigate framing of AST in Ontario we use natural language processing techniques to analyze publicly available documents from Ontario stakeholders involved in school travel planning.
-We then compared the findings from these documents to a selection of academic studies on AST.
-We conclude that framing of AST in Ontario is mostly empirical-scientific and largely in agreement with academic research on AST.
-On the other hand, it it does not appeal to moral reasons for change, and is therefore oddly soothing and lacking in urgency.
-Furthermore, the frames used download responsibility for change to households, which limits the scope of policy alternatives by keeping collective action out of the frame.
+And it ends up being conservative and anodyne.
 
@@
 
-Point 4 [above](#r2-comment-2) highlights some things that we learn from this research, and suggests some ways to change the way AST is framed to make them more efficient.
+Point 4 [above](#r2-comment-2) highlights some things that we learn from this research, and suggests some ways in which frames around AST could be changed.
 
@@
 
-Thank you for your opinion. We will defer to the editor on the matter of scope of the journal.
+Thank you for your opinion. We will defer to the editor on the matter of scope.
 

### 2023-05-26 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Resubmission to TR-A after revisions by ED, DC, DR, EOW, and AP

@@
 ---
-title: "Framing active school travel in Ontario: , or how spinach is good for you"
+title: "Framing active school travel in Ontario, or how spinach is good for you"
 author:
@@
 abstract: |
-  Active school travel (AST) is a relevant policy issue in Ontario, Canada, as reflected in provincial support for school travel planning (STP) efforts.
-Two pillars of school travel plans are education and encouragement.
-For these pillars to stand, all relevant stakeholders must be cognizant of and understand well the issues and stakes.
-For this reason, how AST is communicated to them is essential.
-In this research we adopt frame analysis to investigate the way various organizations communicate around AST to the public.
-A frame is a central organizing idea or story line that provides meaning to a particular phenomenon, and helps to set the parameters for conversations about policy.
+  Active school travel (AST) is promoted in many jurisdictions, including Ontario, Canada, where there is provincial support for school travel planning (STP) efforts.
+Two pillars of school travel plans in the province are education and encouragement.
+For these pillars to stand, relevant stakeholders must be cognizant of and understand the issues and stakes.
+For this reason, we deem it important to understand how AST is communicated.
+In this research we adopt framing analysis to investigate the ways in which various organizations communicate to the public around AST.
+A frame is a central organizing idea or story line that provides meaning to a particular phenomenon, and thus helps to set the parameters for conversations about policy.
 In the case of AST, framing can influence what policy alternatives are perceived as available by children, parents, and their wider communities.
-To investigate framing of AST in Ontario we use natural language processing techniques to analyze publicly available documents from Ontario stakeholders involved in school travel planning.
-We then compared the findings from these documents to a selection of academic studies on AST.
+The research is supported by natural language processing techniques applied to publicly available documents from Ontario stakeholders involved in school travel planning.
+We then compare the findings from these documents to a selection of academic studies on AST.
 We conclude that framing of AST in Ontario is mostly empirical-scientific in style, and largely in agreement with academic research on AST.
-On the other hand, it it does not appeal to moral reasons for change, and is therefore oddly soothing and lacking in urgency.
-Furthermore, the frames used download responsibility for change to households, which limits the scope of policy alternatives by keeping collective action out of the frame.
+However, it is essentially conservative and does challenge to the status quo of motorized travel.
+Furthermore, the frames tend to download responsibility for change to households, which limits the scope of policy alternatives by keeping collective action out of the frame.
 
@@
 Another study in London, Ontario, reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012].
-From a public policy perspective, increasing active travel to school represents a major opportunity to improve children's health and wellbeing [@faulknerActiveSchoolTransport2009], to mitigate traffic and improve perceptions of safety [@rothmanAssociationsParentsPerception2015], as well as to reduce carbon and other noxious emissions [@bearman2014modelling; @goodman2019scenarios].
+From a public policy perspective, increasing active travel to school presents major opportunities to improve children's health and wellbeing [@faulknerActiveSchoolTransport2009], to mitigate traffic and improve perceptions of safety [@rothmanAssociationsParentsPerception2015], as well as to reduce emissions and other forms of pollution [@bearman2014modelling; @goodman2019scenarios].
 
@@
 In this context, STPs are "school-specific" interventions led by a facilitator who works with a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014].
-The five-step process involves identifying barriers to AST and implementing solutions or activities to make AST safer and more convenient: 1) setup of the program; 2) data collection and problem identification; 3) action planning; 4) implementation; 5) monitoring and evaluation [@buliungSchoolTravelPlanning2011; @langUnderstandingModalChoice2011].
+The five-step process involves identifying barriers to AST and implementing solutions or activities to make AST safer and more convenient: 1) setup of the program; 2) data collection and problem identification; 3) action planning; 4) implementation; 5) monitoring and evaluation [@hinckson2018school].
 
@@
 A frame can enable individuals "to locate, perceive, identify, and label" information pertaining to various dimensions of an issue [@goffmanFrameAnalysisEssay1974].
-From this perspective, stakeholders involved in STP efforts play an important role in shaping public perception about AST by generating frames that  create meaning, thus influencing the degree of attention and recognition of a "problem" that needs to be addressed through behaviour change or new policies.
+From this perspective, stakeholders involved in STP efforts play an important role in shaping public perceptions about AST by generating frames that create meaning, and thus influence the degree of attention and recognition of a "problem" that needs to be addressed through behavior change or new policies.
 
@@
 We then compare the findings from these documents to a selection of studies on AST and explore the extent to which there is concordance between the scholarly literature on AST and materials shared with the public.
-The results of this analysis, along with spot checks of the corpus by the authors, lead us to conclude that AST if framed as a matter of individual choices instead of collective action.
-The message is reasonable but anodyne, and it fails to communicate a sense of urgency about health and environmental issues, which may help to explain the limited success of policy.
+The results of this analysis, along with manual checks of the corpus by the authors, lead us to conclude that AST is framed as a matter of individual choices instead of collective action.
+The message is reasonable but inherently conservative and it fails to communicate a sense of urgency about health and environmental issues, which may help to explain the modest success of related policies [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014; @mammenActiveSchoolTravel2014]
 
@@
 
-<!--Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behaviour is understood within the context of household, social, neighbourhood, and policy environments.
+<!--
+ED:
+Factors that influence AST have been presented and organized using a socio-ecological model (SEM) [@mitraIndependentMobilityMode2013] or systems model [@badlandDevelopmentSystemsModel2016] whereby children's travel behavior is understood within the context of household, social, neighbourhood, and policy environments.
 The SEM helps to identify multiple determinants that need to be addressed by school-based interventions to increase AST, with the consensus being that interventions should target multiple levels [@mitraIndependentMobilityMode2013].
+
+AP:
+I removed the SEM from the paper because it was used mainly to appeal to the social science and medicine crowd, but does not seem to be essential for the presentation to the transportation research community
 -->
 
-Rather than describing an extensive list of factors that influence AST and mode choice for travel to school in Canada [e.g., @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], we focus on two key aspects that may be targeted from a policy perspective: perceptions and behaviors by parents and built environmental factors.
-
-<!-- Influence of perceptions -->
-
-First, research has found that parents are key decision-makers with respect to children's form of travel to school [@rothmanAssociationsParentsPerception2015].
-Particularly, parental perceptions of the built or school environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010; @mandic2020differences] and their children's skills [@mammenUnderstandingDriveEscort2012; @faulknerWhatQuickestEasiest2010] tend to influence mode choice to school.
-Furthermore, children's mode choice to school is strongly influenced by their parents' travel behaviours, the complexity of their household's travel needs [@buliungLivingJourneySchool2021], as well as daily parental support [@mahDoesParentalSupport2017a].
-This suggests that shifting parental perceptions and habits is important.
+Rather than describing an extensive list of factors that influence AST and mode choice for travel to school in Canada [e.g., @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], we focus on two key aspects that may be targeted from a policy perspective: built environmental factors and perceptions and behaviors of parents.
 
@@
 
-With respect to the built environment, distance between home and school is most negatively associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
+The built environment is a key factor for physical planning, and in this respect distance between home and school is the factor most negatively associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school.
 Many studies have also found that the quality of the built environment along the route to school and around the school site [@ikedaAssociationsChildrenActive2018; @rothmanActiveSchoolTransportation2021] and provision of active travel infrastructure [@chenPromotingActiveStudent2018; @pontEnvironmentalCorrelatesChildren2009] facilitate AST.
 Canadian youth report that they feel most safe bicycling on streets in their neighbourhood or that have low volumes of traffic [@TACbikeinfra2020].
-Finally, concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012]: ironically, concerns about traffic become a self-fulfilling prophecy.
+Finally, concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012]: ironically, concerns about the dangers of traffic become a vicious cycle [@rothmanSchoolEnvironmentStudent2017].
+
+<!-- Influence of perceptions -->
+
+Secondly, research has found that parents are key decision-makers with respect to children's mode of travel to school [@rothmanAssociationsParentsPerception2015].
+Particularly, after distance [@curtis2015built], parental perceptions of the built or school environment, as well as of their children's skills, have been found to be key in influencing mode choice to school [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010; @mandic2020differences; @mammenUnderstandingDriveEscort2012; @faulknerWhatQuickestEasiest2010].
+For example, @ramanathanHappinessMotionEmotions2014a found that parents and children who perceived active travel as beneficial for health and wellbeing benefits were more likely to use active modes to get to school.
+Furthermore, children's mode choice to school is strongly influenced by their parents' travel behaviors, the complexity of their household's travel needs [@buliungLivingJourneySchool2021], as well as daily parental support [@mahDoesParentalSupport2017a].
+This suggests that shifting parental perceptions and habits is important.
 
@@
 
-AST has become a policy issue on the education and public health agendas in Ontario, supported, albeit in a modest way, by financial contributions from the provincial government.
-Still, the support from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
+AST has become a policy issue on the education and public health agendas in Ontario, and is supported, albeit in a modest way, by financial contributions from the provincial government.
+Still, endorsement from a range of municipal representatives [see @buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015] demonstrates that the AST issue is on the political agenda.
 One of the main vehicles to promote AST is school travel planning (STP), which has been implemented in Canada since at least the late 2000s.
-Within the STP process, facilitators establish multi-sector committees which intervene at the participating school through a range of activities consisting of _[E]ducation_ strategies, _[E]ncouragement_ through in-person events or programs, _[E]ngineering_ improvements to or around the school site, and _[E]nforcement_ of traffic speeds around schools [or 4Es, @langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
-Following the first large-scale evaluation of STP as an intervention in Canada, AST rates increased and 14% of parents reported a perceived reduction in traffic outside the school [@buliungSchoolTravelPlanning2011].
-Assessments of the efficacy of STP [@buttazzoniPromotingActiveSchool2019; @mammenActiveSchoolTravel2014] indicate its potential to encourage behaviour change and adoption of AST.
-
-The relevance of policy frames is highlighted by @beland2014developing, who remarks "framing processes as public relations are central to policy issues related to sustainable transportation".
-Seeing how highly influential parental perceptions are to AST, it is important to understand AST-related communications, since the construction of frames for policy positions or public issues can activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
+Within the STP process, facilitators establish multi-sector committees which intervene at the participating school through four pillars consisting of _[E]ducation_ strategies, _[E]ncouragement_ through in-person events or programs, _[E]ngineering_ improvements to or around the school site, and _[E]nforcement_ of traffic speeds around schools [or 4Es, @langUnderstandingModalChoice2011; @mammenActiveSchoolTravel2014].
+Of the 4Es, [E]ngineering targets the first set of factors discussed in the preceding section (the built environment), whereas [E]ducation and [E]ncouragement target perceptions.
+
+The relevance of policy frames with respect to education and encouragement is highlighted by @beland2014developing, who remarks "framing processes as public relations are central to policy issues related to sustainable transportation".
+Seeing how influential parental perceptions are to AST, it is important to understand AST-related communications, since the construction of frames for policy positions or public issues can activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993].
 Besides parents and children, framing can also affect broader policy support for AST in the community.
@@
 In this sense, framing can be used to position existing solutions as suitable to address particular issues [@mahFramecriticalPolicyAnalysis2014], which may prevent the public from being aware of other policy approaches that challenge the status quo.
-Contrariwise, framing can be instrumental to revealing more diverse policy options than more diverse policy options than conventional wisdom would have [@bosomworth2015climate].
-Ultimately, it is important to understand framing of policy issues because creating meaning through frames contributes to the constant process of shaping of our collective identities, uncovering what we collectively find (un)acceptable and why [@beland2014developing].
-
-Given the heavy focus of STP activities on education or encouragement [@buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014; @buttazzoniSupportingActiveSchool2018], it is important for the issues to be effectively framed.
-In the past, parents have been found to express different understandings, language, and perceptions than planners of how the built environment can influence school travel: while parents tend to view mixed land use as conducive for driving, transport planners see mixed uses as a key for encouraging more active travel [@buliungLivingJourneySchool2021].
+Contrariwise, framing can be instrumental to revealing more diverse policy options than conventional wisdom would have [@bosomworth2015climate].
+Ultimately, it is important to understand framing of policy issues because creating meaning through frames contributes to the constant process of shaping of our collective understanding of issues, uncovering what we collectively find (un)acceptable and why [@beland2014developing].
+
+Given the role of education and encouragement in STP, it is important for the issues to be effectively framed.
+In the past, parents have been found to express understandings, language, and perceptions regarding the influence of the built environment on school travel that markedly differ from those of planners: while parents tend to view mixed land use as conducive for driving, transport planners see mixed uses as a key for encouraging more active travel [@buliungLivingJourneySchool2021].
 Similarly mismatched understandings have been detected with respect to factors like the convenience of different modes to school [@langUnderstandingModalChoice2011].
@@
 
-So framing is important, but not all frames are equally effective.
+Framing is important, but not all frames are equally effective.
 Frames can appeal to economic reasons, to science and logic, or to moral obligation.
-For example, @severson2015moral report that overall support for climate change policy is increased more when scientific frames, secular moral frames, and economic equity frames are used, compared to economic efficiency or religious moral frames.
+For example, @severson2015moral report that overall support for climate change policy increases more when scientific frames, secular moral frames, and economic equity frames are used, compared to economic efficiency or religious moral frames.
 Frames can also be positive or negative, and there is evidence that negative framing may be more effective at motivating individuals, for example, to change transport modes to reduce CO2 emissions [@waygoodCO2ValenceFraming2018].
@@
 Policy documents and academic papers reference _active_, _travel_, _walking_, _biking_ or _cycling_, and _students_ more than other terms.
-Each corpus also has _safety_ and _traffic_ as common words which suggests that these are common concerns for parents.
+Each corpus also has _safety_ and _traffic_ as common words, which suggests that these are common concerns.
 The word _physical_ is present in each corpus, but this could refers to _physical activity_ or the _physical environment_.
@@
 
-Bigrams refer to a pair of consecutive words.
+Bigrams refer to pairs of consecutive words.
 We combined all municipality, school board, and transportation consortia documents into the policy+practice corpus.
@@
 We also found _mental health_, _walk zone_, and _green communities_ as common pairs of consecutive words.
-Their presence makes sense given the involvment of  _Green Communities Canada_ in AST initiatives in Ontario.
+The latter makes sense given the involvment of  _Green Communities Canada_ in AST initiatives in Ontario.
 Overall, the policy documents from STP stakeholder groups seem to focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or barriers; and iv) supports for AST.
@@
 
-Next, we analyzed bigrams in the academic corpus separately to comparE with the policy+practice corpus.
+Next, we analyzed bigrams in the academic corpus separately to compare with the policy+practice corpus.
 Figure \ref{fig:academic-visual} indicates that academic papers include several common bigrams that were also found in the policy documents including _physical activity_, which is the top bigram, as well as _traffic safety_ and _safe routes_.
 However, many other factors are identified in the academic corpus that are not presented to the general public through policy documents.
-Terms like _built environment_, _independent mobility_, and _urban form_ are other frequent pairs of consecutive words.
+Terms like _built environment_, _independent mobility_, and _urban form_ are examples of these factors.
 Academic papers also often discuss _distance home_, _car ownership_, _household income_, and _population density_, which are factors that have been found to influence AST.
@@
 The academic corpus has a higher number of topics likely due to the volume of papers included.
-The following topics were identified based on the clusters of words: (1) physical activity; (2) safe routes to school for active travel; (3) behaviours and attitudes; (4) bicycling; (5) walking; (6) built environment; (7) trip choice; (8) active school travel interventions; (9) parents; (10) children's independent mobility; and (11) public health and policies.
+The following topics were identified based on the clusters of words: (1) physical activity; (2) safe routes to school for active travel; (3) behaviors and attitudes; (4) bicycling; (5) walking; (6) built environment; (7) trip choice; (8) active school travel interventions; (9) parents; (10) children's independent mobility; and (11) public health and policies.
 This corpus reflects a broader range of topics than the policy+practice corpus.
@@
 The secondary frame in policy documents is that AST is accessible and feasible for children and parents.
-Despite the emphasis on the logistics of busing in the topic modelling, the documents indicate that there is an opportunity for or prospect of behaviour change.
+Despite the emphasis on the logistics of busing in the topic modelling, the documents indicate that there is an opportunity for or prospect of behavior change.
 Some cities and schools explain how children and parents can leave the car at home and make the journey to school on foot or by bike.
@@
 
-Finally, both AST frames present the benefits of AST.
+Finally, both frames present the benefits of AST.
 STP stakeholder groups seem to be communicating that AST is a healthy and accessible option as a result of school travel plans and improvements to the built environment.
@@
 
-> __A way to make sure your child is safe while walking to school is with a ‘walking school bus.’ Here are some tips for a walking schoolbus...[tips]...Have fun!_ (City of Ottawa)
+> _A way to make sure your child is safe while walking to school is with a ‘walking school bus.’ Here are some tips for a walking schoolbus...[tips]...Have fun!_ (City of Ottawa)
 
@@
 
-Interpretation of the text assisted by natural language processing reveals that AST in Ontario is not always communicated to members of the public.
-As noted above, less than 50% of documents from municipalities, school boards, and transportation consortia discuss AST.
+In Ontario, municipalities, school boards and transportation consortia do not consistently include AST in their public communications.
+Indeed, as noted above, less than 50% of documents from these organizations discuss AST.
+Interpretation of the text assisted by natural language processing reveals that when AST is discussed, the primary frame emphasizes its benefits to the health and wellbeing of both children and the environment.
 In the rest of the documents, the primary way AST is framed tends to emphasize the benefits to the health and wellbeing of children and to the environment.
@@
 STP stakeholder groups also communicate that increasing AST may reduce traffic near and around schools.
-This is conveyed presumably to alleviate parental concerns about traffic and safety [@eversParentSafetyPerceptions2014; @mammenUnderstandingDriveEscort2012; @rothmanAssociationsParentsPerception2015; @wilsonUnderstandingChildParent2018] or to reduce the frequency of risky behaviours from drivers around schools [@rothmanSchoolEnvironmentStudent2017].
+This is conveyed presumably to alleviate parental concerns about traffic and safety [@eversParentSafetyPerceptions2014; @mammenUnderstandingDriveEscort2012; @rothmanAssociationsParentsPerception2015; @wilsonUnderstandingChildParent2018] or to reduce the frequency of risky behaviors from drivers around schools [@rothmanSchoolEnvironmentStudent2017].
 
 In the secondary frame, AST is presented as an accessible and feasible way for children to travel to and from school.
-Children and parents are encouraged to adopt new travel behaviours.
+Children and parents are encouraged to adopt new travel behaviors.
 STP stakeholder groups identified different ways that parents could encourage or support their children to commute to school by using active modes (e.g., walking tip sheets, walking school buses, etc.).
@@
 
-Both frames present the AST issue in a positive light.
-Neither frame appears to explain why declining rates of AST are a problem or convey any urgency to this issue so that it attracts the attention of parents, the general public, or policy makers.
-For example, parents who drive their children to school have reported concerns about traffic volume around schools [@mammenUnderstandingDriveEscort2012], but may not recognize that their own behaviour contributes to the problem that is perceived to prevent their child from safely walking or bicycling to school [@collinsSafeJourneysEnterprising2001].
-Communicating the potential outcomes of increased AST present the issues in a positive light, but these frames do not seem to encourage parents or the general public to view their current behaviour as problematic or unhealthy for their children and the environment.
-Further, behaviour change is mainly presented as an option for some but not an imperative for all, which keeps collective action through government entities out of the frame.
+Both frames present AST in a positive light, by highlighting the potential benefits.
+However, neither frame appears to explain why declining rates of AST are a problem or convey any urgency to this issue so that it attracts the attention of parents, the general public, or policy makers.
+For example, parents who drive their children to school have reported concerns about traffic volume around schools [@mammenUnderstandingDriveEscort2012], but may not recognize that their own behavior contributes to the problem that is perceived to prevent their child from safely walking or bicycling to school [@collinsSafeJourneysEnterprising2001; @rothmanSchoolEnvironmentStudent2017].
+There is evidence that negative framing is more effective at eliciting responses than positive framing (e.g., Kahneman and Tversky, 1979; Waygood and Avineri, 2018).
+In this case, the frames emphasize the positive side of active travel but leave the negative impacts of behaviors such driving children to school out of the frame.
+
+Further, behavior change is mainly presented as an option for some but not an imperative for all, which keeps collective action through government entities out of the frame.
 This echoes the findings of Reynard et al.
-[-@reynardGrowthResilienceHow2021], who found in their analysis of Canadian municipal documents that one of the dominant frames was to present behaviours that help mitigate the climate crisis as an individual choice but not "the expected norm".
-
-Overall, we find that the proposed solutions in the secondary frame reinforce some of the same ideas: 1) behaviour change from households making different travel decisions (individual responsibility); 2) policies that create resources for AST (mainly through education and plannning); and 3) engineering solutions like bicycle lanes.
+[-@reynardGrowthResilienceHow2021], who found in their analysis of Canadian municipal documents that one of the dominant frames was to present behaviors that help mitigate the climate crisis as an individual choice but not "the expected norm", or what society approves of, i.e., an injunctive norm [@lapinski2005explication].
+In this case, a stronger case of society's disapproval remains to be made.
+
+Overall, we find that the proposed solutions in the secondary frame reinforce some of the same ideas: 1) behavior change from households making different travel decisions (individual responsibility); 2) policies that create resources for AST (mainly through education and plannning); and 3) engineering solutions like bicycle lanes.
 This reflects findings from the AST literature that a range of solutions are needed to address different factors that influence AST [_inter alia, see_ @mitraIndependentMobilityMode2013; @panterAttitudesSocialSupport2010].
 The recognition of engineering changes may reflect the strong engagement of engineering staff and municipal representatives in the Canadian STP process [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015], as well as the evidence that the built environment influences mode choice to school.
-
-As well as what is _in_ the frame, it is also interesting to look for what is _not_.
-As noted, a call for collective action tends to be missing, whereas the positive tone does not convey urgency about some critical stakes, including for instance climate change.
-By presenting the issues in an empirical-scientific way no moral imperative is mobilized to encourage change [@severson2015moral].
+However, these measures tend to support the desired behavior without confronting the problem behavior with interventions such as forbidding drop-off within 100 m of the school, restricting vehicular traffic to only local traffic around schools at school-commute times, such as found in countries where nearly no children die while going to school [@waygood2020japan].
+
+As well as what is _in_ the frame, it is also interesting to look for what is _not_ there.
+The conservative orientation of the frames does not fundamentally challenge the status quo: not surprisingly, the frames advocate the option of active travel for those who are interested in realizing its benefits, but do not make a case for fundamental changes to the local environment, and also do not present a moral imperative for change  [@severson2015moral].
+The individualistic approach also means that a call for collective action tends to be missing.
 
@@
 As we noted in Section \ref{stp-frames} above, STP in Ontario relies heavily on education and encouragement.
-From the get-go, these are two of the weakest tools in the arsenal of government actions [@ohare1989typology].
-For this reason, it is important that both are used effectively.
-Our analysis leads us to question the efficacy of the frames currently used for talking about AST in Ontario.
-If we had to paraphrase the way AST is framed, it would be like this: "eating spinach is good for you; here are some tips to help you choose spinach." The issues are presented as a matter of personal choice, purely optional, and without a sense of urgency.
+From the get-go, these are not the strongest tools of government action [compared to, say, regulation and transfers; see @ohare1989typology].
+The conservative framing used further dilutes the force of STP interventions.
+If we had to paraphrase the way AST is framed across the province, it would be like this: "eating spinach is good for you; here are some tips to help you choose spinach." The issues are presented as a matter of personal choice, purely optional, and without a sense of urgency.
 While emphasizing the risks may seem counterproductive, this approach has been found to be effective at motivating change [e.g., @lawlor2018risk; @waygoodCO2ValenceFraming2018].
@@
 In addition to privileging choice, the frames tend to leave out a number of household determinants of AST.
-For example, there was no discussion about the role of convenience and inclement weather in shaping household travel decisions [@buliungSchoolTravelPlanning2011] and the complexity of travel arrangements that must be coordinated by households [see @buliungLivingJourneySchool2021].
+There was little discussion of socio-economic and demographic attributes associated with AST, such as age of children, parental education, income, and ethnicity [@rothmanDeclineActiveSchool2018].
+Similarly, there was no discussion about the role of convenience and inclement weather in shaping household travel decisions [@buliungSchoolTravelPlanning2011] and the complexity of travel arrangements that must be coordinated by households [see @buliungLivingJourneySchool2021].
 The desire to escort children to school, which has been noted by parents as a reason to continue driving [@westmanWhatDrivesThem2017], is also not adequately addressed by STP stakeholders.
@@
 
-## Limitations
-
-A limitation of this study is that we only analyzed English-language texts that were easily accessible to the general public on the websites of STP stakeholders in Ontario.
+Conclusion
+===============
+
+In this paper we examined how AST is framed in Ontario.
+Our analysis was supported by the use of natural language processing techniques, and reavealed that STP stakeholders frame AST as an accessible and feasible way to travel to school that is valuable to children's health and to the environment.
+STP stakeholders are communicating that this issue can be addressed through household behavior change and policy solutions.
+Policy documents reveal that STP stakeholders are focusing on "modifiable factors" such as parental perceptions or micro-scale elements in the built environment to increase rates of AST.
+However, AST may not be framed sufficiently as a "problem" that requires urgent intervention, which may impact how parents respond to behavior change initiatives and limit awareness in the general public.
+In their public materials about AST, STP stakeholders should emphasize why AST rates should increase in local communities and how the negative effects of nonactive modes to school may impact children's health and wellbeing.
+In summary, AST is presented in terms of potential benefits, but there is no real discussion whether they can be realized with only modest adjustments to the status quo.
+
+In terms of future research, we suggest the need for further investigation into how parents or the general public respond to messages or information that encourages the adoption of AST and evaluate which are most effective.
+It would be helpful to understand which frames would most encourage behavior change or increase political support for interventions that address barriers to AST.
+This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.
+If Canadian STP stakeholders wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different materials that communicate why this issue is important to the general public, regardless of whether they currently have children commuting to/from school.
+
+It is pertinent at this point to note that a limitation of this study is that we only analyzed English-language texts that were easily accessible to the general public on the websites of STP stakeholders in Ontario.
 We did not include French-language materials from Ontario's 12 French school boards (a mixture of public and Catholic schools).
@@
 
-Conclusion
-===============
-
-In this paper we examined how AST is framed in Ontario.
-Our analysis was supported by the use of natural language processing techniques, and reavealed that STP stakeholders frame AST as an accessible and feasible way to travel to school that is valuable to children's health and to the environment.
-STP stakeholders are communicating that this issue can be addressed through household behaviour change and policy solutions.
-Policy documents reveal that STP stakeholders are focusing on "modifiable factors" such as parental perceptions or micro-scale elements in the built environment to increase rates of AST.
-However, AST may not be framed sufficiently as a "problem" that requires urgent intervention, which may impact how parents respond to behaviour change initiatives and limit awareness in the general public.
-In their public materials about AST, STP stakeholders should emphasize why AST rates should increase in local communities and how the negative effects of nonactive modes to school may impact children's health and wellbeing.
-
-In terms of future research, we suggest the need for further investigation into how parents or the general public respond to messages or information that encourages the adoption of AST and evaluate which are most effective.
-It would be helpful to understand which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST.
-This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.
-If Canadian STP stakeholders wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different materials that communicate why this issue is important to the general public, regardless of whether they currently have children commuting to/from school.
-
 Finally, we would like to close with a brief note on the methodology.
 Natural language processing and analysis of frames are still not widely adopted in transportation research.
-Based on our experience, we tend to see computer-assisted text analysis as a complement rather than a substitute to expert reading of the documents.
+Based on our experience, we tend to see computer-assisted text analysis as a complement to rather than a substitute for expert reading of the documents.
 We would not recommend to proceed to interpretation without reading the documents, but the supervised automation helps to detect patterns that can be validated by an expert based on spot checks or more in-depth reading of the original sources.
 Like with any qualitative research, interpretation of the frames may differ by expert; in this research we aimed to develop a consensus interpretation by involving all authors in the discussion of the results.
-Furthermore, since the research is an open, reproducible project, all our assumptions are open to scrutiny and use the data to check and/or expand the analysis presented here.
+Furthermore, since the research is an open, reproducible project, all our assumptions are open to scrutiny and others use the data to check and/or expand the analysis presented here.
 

### 2023-05-26 AST-Framing-Ontario/AST-Framing-Ontario.tex
Resubmission to TR-A after revisions by ED, DC, DR, EOW, and AP

@@
 
-\usepackage{lineno} % add
-
 \usepackage{graphicx}
@@
 \usepackage{amssymb,amsmath}
+% TODO: Currently lineno needs to be loaded after amsmath because of conflict
+% https://github.com/latex-lineno/lineno/issues/5
+\usepackage{lineno} % add
 \usepackage{ifxetex,ifluatex}
@@
             pdfauthor={},
-            pdftitle={How is active school travel framed in Ontario, Canada?},
+            pdftitle={Framing active school travel in Ontario, or how spinach is good for you},
             colorlinks=false,
@@
 
-  \title{How is active school travel framed in Ontario, Canada?}
+  \title{Framing active school travel in Ontario, or how spinach is good
+for you}
     \author[McMaster University]{Elise Desjardins%
@@
   \begin{abstract}
-  Active school travel (AST) has been increasingly encouraged by various
-  stakeholders in Ontario, Canada through efforts such as school travel
-  planning. Education strategies like workshops or resources that
-  promote AST are commonly implemented. The framing of AST through such
-  strategies may influence how walking and bicycling to school are
-  perceived by parents. It may also draw attention to AST as an issue
-  affecting children's health which could motivate behaviour change. We
-  used natural language processing, including topic modelling, to
-  examine how AST is framed in publicly available documents from Ontario
-  stakeholders involved in school travel planning. We then compared the
-  findings from these documents to a selection of studies on AST and
-  explored similarities between the two. We found that AST is framed in
-  two ways: i) as a health and environmental issue; and ii) as an
-  accessible and feasible transport option for children and parents. The
-  frames encourage children and parents to adopt AST given its health
-  and environmental benefits by providing resources to support behaviour
-  change. The benefits of AST and strategies to support AST that are
-  communicated by stakeholders are consistent with the evidence from
-  academic research. While these frames present AST in a positive light,
-  they may not encourage parents to view current household travel
-  behaviours as unhealthy for their children or their community.
-  Stakeholders promoting AST in Ontario should further problematize the
-  decline of AST and challenge the norm of driving children to school.
+  Active school travel (AST) is promoted in many jurisdictions,
+  including Ontario, Canada, where there is provincial support for
+  school travel planning (STP) efforts. Two pillars of school travel
+  plans in the province are education and encouragement. For these
+  pillars to stand, relevant stakeholders must be cognizant of and
+  understand the issues and stakes. For this reason, we deem it
+  important to understand how AST is communicated. In this research we
+  adopt framing analysis to investigate the ways in which various
+  organizations communicate to the public around AST. A frame is a
+  central organizing idea or story line that provides meaning to a
+  particular phenomenon, and thus helps to set the parameters for
+  conversations about policy. In the case of AST, framing can influence
+  what policy alternatives are perceived as available by children,
+  parents, and their wider communities. The research is supported by
+  natural language processing techniques applied to publicly available
+  documents from Ontario stakeholders involved in school travel
+  planning. We then compare the findings from these documents to a
+  selection of academic studies on AST. We conclude that framing of AST
+  in Ontario is mostly empirical-scientific in style, and largely in
+  agreement with academic research on AST. However, it is essentially
+  conservative and does challenge to the status quo of motorized travel.
+  Furthermore, the frames tend to download responsibility for change to
+  households, which limits the scope of policy alternatives by keeping
+  collective action out of the frame.
   \end{abstract}
@@
 active travel \citep{larsenRouteBasedAnalysisCapture2012}. From a public
-health perspective, increasing active travel to school represents a
-major opportunity to improve children's health and wellbeing.
+policy perspective, increasing active travel to school presents major
+opportunities to improve children's health and wellbeing
+\citep{faulknerActiveSchoolTransport2009}, to mitigate traffic and
+improve perceptions of safety
+\citep{rothmanAssociationsParentsPerception2015}, as well as to reduce
+emissions and other forms of pollution
+\citep{bearman2014modelling, goodman2019scenarios}.
 
@@
 \emph{Ontario Active School Travel} (OAST). By 2021, the program, run by
-Green Communities Canada had awarded over CAD 2 million and provided
-resources to over 25 projects across Ontario
+\emph{Green Communities Canada} had awarded over CAD 2 million and
+provided resources to over 25 projects across Ontario
 \citep{GreenCommunities2016}. A popular intervention in many communities
@@
 identification; 3) action planning; 4) implementation; 5) monitoring and
-evaluation
-\citep{buliungSchoolTravelPlanning2011, langUnderstandingModalChoice2011}.
+evaluation \citep{hinckson2018school}.
 
-Framing AST by STP stakeholders to a target audience (e.g., parents or
-the general public) can raise awareness of the relevant issues and
-influence how active travel to school is perceived. Gamson and
-Modigliani \citeyearpar{gamsonChangingCulture1987} define a frame as a
-``central organizing idea or story line that provides meaning'' to a
-particular phenomenon. A frame can enable individuals ``to locate,
-perceive, identify, and label'' information pertaining to various
-dimensions of an issue \citep{goffmanFrameAnalysisEssay1974}. Therefore,
-stakeholders involved in STP efforts can play a role in shaping public
-perception about AST to attract greater attention and recognition as a
-``problem'' that needs to be addressed through behaviour change or new
-policies.
+How AST is presented to a target audience (e.g., parents or the general
+public) is essential to define the parameters of what is possible
+policy-wise. Drawing from concepts in communication studies, the
+objective of this paper is to investigate how AST is framed in Ontario.
+Gamson and Modigliani \citeyearpar{gamsonChangingCulture1987} define a
+frame as a ``central organizing idea or story line that provides
+meaning'' to a particular phenomenon. A frame can enable individuals
+``to locate, perceive, identify, and label'' information pertaining to
+various dimensions of an issue \citep{goffmanFrameAnalysisEssay1974}.
+From this perspective, stakeholders involved in STP efforts play an
+important role in shaping public perceptions about AST by generating
+frames that create meaning, and thus influence the degree of attention
+and recognition of a ``problem'' that needs to be addressed through
+behavior change or new policies.
 
-After significant investment of human and financial resources to boost
-rates of AST in Ontario over the past few years, in this paper we ask
-this central question: How is AST framed to the public in Ontario? The
-following questions are subsidiary and help us address this main
-question: What benefits of AST are communicated to the public? What
-solutions are proposed to increase AST?
-
-We approach this question by means of natural language processing, and
-examine how three STP stakeholder groups in Ontario (municipalities,
-school boards, and transportation consortia) frame AST. We assemble a
-corpus of texts from public sources that present information for the
-general public or parents who are interested in AST. We examine word
-frequency, bigrams, and concordances in these selected documents, and
-also identify key topics presented by each stakeholder group. We then
-compare the findings from these documents to a selection of studies on
-AST and explore the extent to which there is concordance between the
-scholarly literature on AST and materials shared with the public.
+Our research is supported by natural language processing techniques,
+applied to the analysis of documents produced by three STP stakeholder
+groups in Ontario (municipalities, school boards, and transportation
+consortia). We assemble a corpus of texts from public sources that
+present information for the general public or parents who are interested
+in AST and examine word frequency, bigrams, and concordances in these
+selected documents. Furthermore, we use topic analysis to identify
+themes presented by each stakeholder group. We then compare the findings
+from these documents to a selection of studies on AST and explore the
+extent to which there is concordance between the scholarly literature on
+AST and materials shared with the public. The results of this analysis,
+along with manual checks of the corpus by the authors, lead us to
+conclude that AST is framed as a matter of individual choices instead of
+collective action. The message is reasonable but inherently conservative
+and it fails to communicate a sense of urgency about health and
+environmental issues, which may help to explain the modest success of
+related policies
+\citep{buliungSchoolTravelPlanning2011, mammenSchoolTravelPlanning2014, mammenActiveSchoolTravel2014}
 
@@
 
-Factors that influence AST have been presented and organized using a
-socio-ecological model (SEM) \citep{mitraIndependentMobilityMode2013} or
-systems model \citep{badlandDevelopmentSystemsModel2016} whereby
-children's travel behaviour is understood within the context of
-household, social, neighbourhood, and policy environments. The SEM helps
-to identify multiple determinants that need to be addressed by
-school-based interventions to increase AST, with the consensus being
-that interventions should target multiple levels
-\citep{mitraIndependentMobilityMode2013}. Rather than describing an
-extensive list of factors that influence AST and mode choice in Canada
+Rather than describing an extensive list of factors that influence AST
+and mode choice for travel to school in Canada
 \citep[e.g.,][]{mammenUnderstandingDriveEscort2012, mitraIndependentMobilityMode2013, rothmanDeclineActiveSchool2018, wilsonUnderstandingChildParent2018},
-we discuss a few potentially modifiable determinants that may be
-targeted for change through STP.
+we focus on two key aspects that may be targeted from a policy
+perspective: built environmental factors and perceptions and behaviors
+of parents.
 
-Children's mode choice to school is strongly influenced by their
-parents' travel behaviours and the complexity of their household's
-travel needs \citep{buliungLivingJourneySchool2021}, as well as daily
-parental support \citep{mahDoesParentalSupport2017a}. This indicates
-that shifting parental perceptions and habits is important. Convenience
-and inclement weather have been cited by parents as barriers to AST
-\citep{buliungSchoolTravelPlanning2011}. Parental perceptions of the
-built or school environment
-\citep{demeesterParentalPerceivedNeighborhood2014, panterAttitudesSocialSupport2010}
-and their children's skills
-\citep{mammenUnderstandingDriveEscort2012, faulknerWhatQuickestEasiest2010}
-also influence mode choice to school.
-
-Distance between home and school is most negatively associated with AST
+The built environment is a key factor for physical planning, and in this
+respect distance between home and school is the factor most negatively
+associated with AST
 \citep{ikedaAssociationsChildrenActive2018, mammenUnderstandingDriveEscort2012, pontEnvironmentalCorrelatesChildren2009, rothmanDeclineActiveSchool2018}
@@
 have been reported by parents who drive their children to school
-\citep{mammenUnderstandingDriveEscort2012}, which highlights that the
-volume and speed of cars can be a concern or deterrent for AST.
+\citep{mammenUnderstandingDriveEscort2012}: ironically, concerns about
+the dangers of traffic become a vicious cycle
+\citep{rothmanSchoolEnvironmentStudent2017}.
 
-\hypertarget{school-travel-planning-in-canada-and-relevance-of-framing-analysis}{%
-\section{School travel planning in Canada and relevance of framing
-analysis}\label{school-travel-planning-in-canada-and-relevance-of-framing-analysis}}
+Secondly, research has found that parents are key decision-makers with
+respect to children's mode of travel to school
+\citep{rothmanAssociationsParentsPerception2015}. Particularly, after
+distance \citep{curtis2015built}, parental perceptions of the built or
+school environment, as well as of their children's skills, have been
+found to be key in influencing mode choice to school
+\citep{demeesterParentalPerceivedNeighborhood2014, panterAttitudesSocialSupport2010, mandic2020differences, mammenUnderstandingDriveEscort2012, faulknerWhatQuickestEasiest2010}.
+For example, \citet{ramanathanHappinessMotionEmotions2014a} found that
+parents and children who perceived active travel as beneficial for
+health and wellbeing benefits were more likely to use active modes to
+get to school. Furthermore, children's mode choice to school is strongly
+influenced by their parents' travel behaviors, the complexity of their
+household's travel needs \citep{buliungLivingJourneySchool2021}, as well
+as daily parental support \citep{mahDoesParentalSupport2017a}. This
+suggests that shifting parental perceptions and habits is important.
 
-School travel planning (STP) has been implemented in Canada since at
-least the late 2000s. Within the STP process, facilitators establish
-multi-sector committees which intervene at the participating school
-through a range of activities consisting of \emph{{[}E{]}ducation}
-strategies, \emph{{[}E{]}ncouragement} through in-person events or
-programs, \emph{{[}E{]}ngineering} improvements to or around the school
-site, and \emph{{[}E{]}nforcement} of traffic speeds around schools
-\citep[or
+\hypertarget{stp-frames}{%
+\section{School travel planning in Canada and relevance of
+frames}\label{stp-frames}}
+
+AST has become a policy issue on the education and public health agendas
+in Ontario, and is supported, albeit in a modest way, by financial
+contributions from the provincial government. Still, endorsement from a
+range of municipal representatives
+\citep[see][]{buttazzoniSupportingActiveSchool2018, mammenPuttingSchoolTravel2015}
+demonstrates that the AST issue is on the political agenda. One of the
+main vehicles to promote AST is school travel planning (STP), which has
+been implemented in Canada since at least the late 2000s. Within the STP
+process, facilitators establish multi-sector committees which intervene
+at the participating school through four pillars consisting of
+\emph{{[}E{]}ducation} strategies, \emph{{[}E{]}ncouragement} through
+in-person events or programs, \emph{{[}E{]}ngineering} improvements to
+or around the school site, and \emph{{[}E{]}nforcement} of traffic
+speeds around schools \citep[or
 4Es,][]{langUnderstandingModalChoice2011, mammenActiveSchoolTravel2014}.
-Following the first large-scale evaluation of STP as an intervention in
-Canada, AST rates increased and 14\% of parents reported a perceived
-reduction in traffic outside the school
-\citep{buliungSchoolTravelPlanning2011}. Assessments of the efficacy of
-STP
-\citep{buttazzoniPromotingActiveSchool2019, mammenActiveSchoolTravel2014}
-indicate its potential to encourage behaviour change and adoption of
-AST.
+Of the 4Es, {[}E{]}ngineering targets the first set of factors discussed
+in the preceding section (the built environment), whereas
+{[}E{]}ducation and {[}E{]}ncouragement target perceptions.
 
-By providing a ``central organizing idea or story line''
-\citep{gamsonChangingCulture1987} framing of AST seems particularly
-important to shift parental attitudes and perceptions, given their
-reported influence on children's travel mode to school. Scholars in the
-field of political communications have proposed that communicators, such
-as the media or institutions, construct the narrative of a frame for
-policy positions or public issues in order to activate or restrict a
-particular response in the intended audience
-\citep{panFramingAnalysisApproach1993}. Organized groups of stakeholders
-can employ similar methods to attract attention to particular issues.
-Framing can be used to position existing solutions as suitable to
-address particular issues \citep{mahFramecriticalPolicyAnalysis2014},
-which may prevent the public from being aware of other policy approaches
-that challenge the status quo. The way policy issues are framed is
-ultimately important to understand because it plays a role in either
-altering or preserving the existing social perceptions. Finally, the
-ideas that are communicated by a particular frame can be either positive
-or negative \citep{waygoodCO2ValenceFraming2018}. There is evidence that
-negative framing may be more effective at motivating individuals, for
-example, to change transport modes to reduce CO2 emissions
-\citep{waygoodCO2ValenceFraming2018}.
-
-Framing of AST could also affect broader support in the community.
+The relevance of policy frames with respect to education and
+encouragement is highlighted by \citet{beland2014developing}, who
+remarks ``framing processes as public relations are central to policy
+issues related to sustainable transportation''. Seeing how influential
+parental perceptions are to AST, it is important to understand
+AST-related communications, since the construction of frames for policy
+positions or public issues can activate or restrict a particular
+response in the intended audience
+\citep{panFramingAnalysisApproach1993}. Besides parents and children,
+framing can also affect broader policy support for AST in the community.
 Municipal representatives are perceived to be instrumental but the
@@
 representatives and local residents) can be lacking
-\citep{buttazzoniSupportingActiveSchool2018}. In Ontario, it is
-reasonable to say that AST has become a policy issue on the education
-and public health agendas, supported, albeit in a modest way, by
-financial contributions from the provincial government. Still, the
-support from a range of municipal representatives
-\citep[see][]{buttazzoniSupportingActiveSchool2018, mammenPuttingSchoolTravel2015}
-demonstrates that the AST issue is on the political agenda.
+\citep{buttazzoniSupportingActiveSchool2018}. In this sense, framing can
+be used to position existing solutions as suitable to address particular
+issues \citep{mahFramecriticalPolicyAnalysis2014}, which may prevent the
+public from being aware of other policy approaches that challenge the
+status quo. Contrariwise, framing can be instrumental to revealing more
+diverse policy options than conventional wisdom would have
+\citep{bosomworth2015climate}. Ultimately, it is important to understand
+framing of policy issues because creating meaning through frames
+contributes to the constant process of shaping of our collective
+understanding of issues, uncovering what we collectively find
+(un)acceptable and why \citep{beland2014developing}.
 
-Since STP activities heavily focus on education or encouragement
-\citep{buliungSchoolTravelPlanning2011, mammenActiveSchoolTravel2014, buttazzoniSupportingActiveSchool2018},
-it is important that parents and communities are receptive to the goals
-of STP \citep{buttazzoniSupportingActiveSchool2018}. Parents have been
-found to express different understandings, language, and perceptions
-than planners of how the built environment can influence school travel
-\citep{buliungLivingJourneySchool2021}. This is also true when it comes
-to other factors like convenience of different modes to school
-\citep{langUnderstandingModalChoice2011}. STP stakeholders must pay
-special attention to parents' understanding of the decline of AST as a
-problem, which may affect their receptivity to proposed solutions.
+Given the role of education and encouragement in STP, it is important
+for the issues to be effectively framed. In the past, parents have been
+found to express understandings, language, and perceptions regarding the
+influence of the built environment on school travel that markedly differ
+from those of planners: while parents tend to view mixed land use as
+conducive for driving, transport planners see mixed uses as a key for
+encouraging more active travel \citep{buliungLivingJourneySchool2021}.
+Similarly mismatched understandings have been detected with respect to
+factors like the convenience of different modes to school
+\citep{langUnderstandingModalChoice2011}. As a consequence, STP
+stakeholders must pay special attention to parents' and communities'
+understanding of the decline of AST as a problem, which may affect their
+receptivity to proposed solutions
+\citep{buttazzoniSupportingActiveSchool2018}.
 
-The success of STP interventions would likely depend on parental
-judgments of factors that are related to school travel, as well as
-support from key policy makers. For example, parents have been found to
-view mixed land use as conducive for driving, despite transport planners
-viewing neighbourhoods with mixed uses as key for encouraging more
-active travel \citep{buliungLivingJourneySchool2021}. Therefore,
-stakeholders involved in STP must make conscious choices about the
-proposed solutions and potential benefits of AST that are communicated
-to parents and the general public through publicly available content to
-convey its importance as a policy issue and to facilitate adoption of
-AST.
+Framing is important, but not all frames are equally effective. Frames
+can appeal to economic reasons, to science and logic, or to moral
+obligation. For example, \citet{severson2015moral} report that overall
+support for climate change policy increases more when scientific frames,
+secular moral frames, and economic equity frames are used, compared to
+economic efficiency or religious moral frames. Frames can also be
+positive or negative, and there is evidence that negative framing may be
+more effective at motivating individuals, for example, to change
+transport modes to reduce CO2 emissions
+\citep{waygoodCO2ValenceFraming2018}. As well, the effectiveness of the
+framing depends on the psychological distance to the relevant issues:
+how socially, temporally, geographically, or hypothetically close an
+individual perceives themselves to the issues can affect their support
+for various policies \citep{maiella2020psychological}. For this reason,
+stakeholders involved in STP must make conscious choices about how
+issues surrounding AST are communicated if the goal is to increase
+support for and buy-in of AST policies.
 
@@
 English-speaking only); ii) municipal governments; and iii)
-transportation consortia. The latter involve a collaboration between
+transportation consortia. The latter involve collaborations between
 municipal regions and school boards to deliver more efficient and timely
-transportation services to schools in each region. Non-profit
-organizations, police services, and advocacy groups are other
-stakeholders who often play a role in supporting AST and/or STP, but
-this study does not include any documents from these groups because they
-do not consistently participate in STP initiatives in Ontario.
+regional transportation services to schools. Non-profit organizations,
+police services, and advocacy groups are other stakeholders who often
+play a role in supporting AST and/or STP, but this study does not
+include any documents from these groups because they do not consistently
+participate in STP initiatives in Ontario.
 
@@
 they were findable. This primary criterion was important since our
-analysis pertains to how such issues are framed to the general public.
-Thus, we included only webpages that were readily accessible, which we
-defined as requiring no more than four links from the initial Google
-search to reach.
+analysis pertains communication of issues to the general public. Thus,
+we included only webpages that were readily accessible, which we defined
+as requiring no more than four links from the initial Google search to
+reach.
 
@@
 We conducted a search on Web of Science for scholarly papers on the
-topic of school travel. We limited our search to the fields of public
-health, transportation, planning, urban studies, and geography. This
-initial corpus was curated by the authors to ensure that all documents
-were relevant. After this step, 227 journal articles were readied for
-analysis.
+topic of school travel using Web of Science's Core Collection. The
+search was conducted in the Winter of 2021 and the parameters used were
+\{active OR walk* or cycl* or bicycl*\} AND \{``school travel''\}.
+Initially, we found 322 papers, which we reduced to 250 after selecting
+only papers in the fields of transportation, planning, urban studies,
+geography, and public health. These fields were chosen because they had
+the greatest volume of documents and/or were of disciplinary interest to
+the authors. This list with 250 documents was then manually curated by
+the authors to ensure that all documents were relevant. This was done by
+checking the title and reading the abstract of the papers. For example,
+a paper with the title ``Impact of automated photo enforcement of
+vehicle speed in school zones'' \citep{quistberg2019impact} was excluded
+as being tangential to our research; the abstract of another paper
+revealed that it was mainly concerned with survey methods: ``Common
+methods for measuring mode share include Hands Up surveys and family
+surveys, but these require teacher and parental involvement.''
+\citep{sersli2019getting}. After this process, our academic corpus
+comprised 227 journal articles that were readied for analysis.
 
@@
 
-We use topic modelling to analyze the documents retrieved. Topic
-modelling is a natural language processing technique used to analyze
-text to identify the language and concepts being communicated. This
-method is practical for researchers working with large amounts of text
-because it replaces the manual coding of topics that would normally take
+Topic modelling was used to analyze the documents retrieved. This is a
+natural language processing technique used to analyze text to identify
+the language and concepts being communicated. This method is practical
+for researchers working with large amounts of text because it can assist
+and complement the manual coding of topics that would normally take
 place to analyze or summarize textual data
 \citep{jacobiQuantitativeAnalysisLarge2016}. We primarily use the
-following software: \texttt{tidytext} \citep{R-tidytext},
-\texttt{topicmodels} \citep{R-topicmodels}, \texttt{word2vec}
-\citep{R-word2vec}, and \texttt{wordcloud} \citep{R-wordcloud}.
+following \texttt{R} packages: \texttt{tidytext}
+\citep{silge2016tidytext}, \texttt{topicmodels} \citep{grun2011topic},
+\texttt{word2vec} \citep{wijffels2021word2vec}, and \texttt{wordcloud}
+\citep{fellows2018wordloud}.
 
@@
 This paper is an example of open and reproducible research that uses
-only open software. Following best practices in spatial data science
+only open software. The source document is an R markdown document.
+Following best practices in spatial data science
 \citep{brunsdon2020opening}, the code and data needed to reproduce our
 research or conduct a similar analysis for other regions are available
-for download upon request.
+in a publicly available repository\footnote{\url{https://github.com/desjae/AST-Framing-Analysis-Ontario}}.
 
@@
 \emph{students} more than other terms. Each corpus also has
-\emph{safety} and \emph{traffic} as common words which suggests that
-these are common concerns for parents. The word \emph{physical} is
-present in each corpus, but it's not clear what this refers to (e.g,
-\emph{physical activity}, or the \emph{physical environment}).
-Furthermore, documents from STP stakeholder groups discuss
-\emph{resources}, \emph{information}, and \emph{services} about school
-travel. Unlike the academic papers, policy+practice documents include
-the words \emph{route} or \emph{routes} as frequent terms. This could
-indicate the role of STP stakeholder groups in identifying safe routes
-to school to share with parents or families. In the section below, the
-context in which these terms are used is explored further.
+\emph{safety} and \emph{traffic} as common words, which suggests that
+these are common concerns. The word \emph{physical} is present in each
+corpus, but this could refers to \emph{physical activity} or the
+\emph{physical environment}. Furthermore, documents from STP stakeholder
+groups discuss \emph{resources}, \emph{information}, and \emph{services}
+about school travel. Unlike the academic papers, policy+practice
+documents frequently include the words \emph{route} or \emph{routes}.
+This could indicate the role of STP stakeholder groups in identifying
+safe routes to school to share with parents or families. In the section
+below, the context in which these terms are used is explored further.
 
@@
 these terms is consistent with an academic focus on exploring the
-variables that influence mode choice. These words are absent from the
-list of common words in policy+practice documents. Table
+variables that influence travel to school. These words are absent from
+the list of common words in policy+practice documents. Table
 \ref{tab:word-table} indicates that the academic corpus discusses a
@@
 all policy documents. This suggests that although documents pertain to
-the subject of school travel, not all stakeholders across Ontario
-disseminate information about AST. We manually searched the
-policy+practice corpus and found that 48\% of documents mention AST and
-16\% mention STP. In contrast, inclement weather and its impacts on
-busing is a common topic addressed in school board and transportation
-consortia documents.
+school travel, not all stakeholders across Ontario disseminate
+information about AST. We manually searched the policy+practice corpus
+and found that 48\% of documents mention AST and 16\% mention STP. In
+contrast, inclement weather and its impacts on busing is a common topic
+addressed in school board and transportation consortia documents.
 
@@
 
-Bigrams refer to a pair of consecutive words. We combined all
+Bigrams refer to pairs of consecutive words. We combined all
 municipality, school board, and transportation consortia documents into
-the policy+practice. Figure \ref{fig:policy-visual} shows all of the
-bigrams that occur more than 10 times in the policy+practice corpus.
-This figure highlights the main ideas that are presented to the public
-in each of the policy corpora. The directional arrows indicate the
-arrangement of the words (e.g., active travel and not travel active) and
-the colour gradient of the arrows corresponds to the most frequently
-mentioned pairs (e.g., bigrams with darker arrows are found in the
-corpus more often).
+the policy+practice corpus. Figure \ref{fig:policy-visual} shows all of
+the bigrams that occur more than 10 times in this corpus. This figure
+highlights the main ideas that are presented to the public in each of
+the policy corpora. The directional arrows indicate the arrangement of
+the words (e.g., active travel and not travel active) and the colour
+gradient of the arrows corresponds to the most frequently mentioned
+pairs (e.g., bigrams with darker arrows are found in the corpus more
+often).
 
@@
 health}, \emph{walk zone}, and \emph{green communities} as common pairs
-of consecutive words. \emph{Green Communities Canada} is a non-profit
-organization that has significantly supported AST initiatives through
-the Ontario Active School Travel program so the high frequency of this
-term in the policy+practice corpus is not surprising. Overall, the
-policy documents from STP stakeholder groups seem to focus on four key
-areas: i) benefits or impacts of AST; ii) mechanisms of intervention;
-iii) concerns or barriers; and iv) supports for AST. This interpretation
-indicates that the general public accessing information about AST in
-Ontario is informed about a wide range of content related to this issue.
+of consecutive words. The latter makes sense given the involvment of
+\emph{Green Communities Canada} in AST initiatives in Ontario. Overall,
+the policy documents from STP stakeholder groups seem to focus on four
+key areas: i) benefits or impacts of AST; ii) mechanisms of
+intervention; iii) concerns or barriers; and iv) supports for AST. This
+interpretation indicates that the general public accessing information
+about AST in Ontario is informed about a wide range of content related
+to this issue.
 
-Next, we analyzed bigrams in the academic corpus separately to make
-comparisons with the policy+practice corpus. Figure
-\ref{fig:academic-visual} indicates that academic papers include several
-common bigrams that were also found in the policy documents including
-\emph{physical activity}, which is the top bigram, \emph{traffic
-safety}, and \emph{safe routes}. However, many other factors are
-identified in the research literature that are not presented to the
-general public through policy documents. Terms like \emph{built
-environment}, \emph{independent mobility}, and \emph{urban form} are
-other frequent pairs of consecutive words. Academic papers also often
-discuss \emph{distance home}, \emph{car ownership}, \emph{household
-income}, and \emph{population density}, which are factors that have been
-found to influence AST. Finally, the presence of \emph{statistically
-significant} among the top bigrams indicates that researchers often aim
-to identify associations using statistical measures. We found that the
-academic corpus focuses on a greater range of topics than found in the
-policy+practice documents.
+Next, we analyzed bigrams in the academic corpus separately to compare
+with the policy+practice corpus. Figure \ref{fig:academic-visual}
+indicates that academic papers include several common bigrams that were
+also found in the policy documents including \emph{physical activity},
+which is the top bigram, as well as \emph{traffic safety} and \emph{safe
+routes}. However, many other factors are identified in the academic
+corpus that are not presented to the general public through policy
+documents. Terms like \emph{built environment}, \emph{independent
+mobility}, and \emph{urban form} are examples of these factors. Academic
+papers also often discuss \emph{distance home}, \emph{car ownership},
+\emph{household income}, and \emph{population density}, which are
+factors that have been found to influence AST. Finally, the presence of
+\emph{statistically significant} among the top bigrams indicates that
+researchers often aim to identify associations using statistical
+measures. We found that the academic corpus focuses on a greater range
+of topics than found in the policy+practice documents.
 
@@
 and 11 topics in the academic corpus, after which there was too much
-overlap for the clusters to be meaningfully interpreted. Figures
+overlap for the clusters to be meaningfully distinguished. Figures
 \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main
-terms that are associated with the topics found in each corpus.
+terms associated with the topics found in each corpus.
 
@@
 the clusters of words: (1) physical activity; (2) safe routes to school
-for active travel; (3) behaviours and attitudes; (4) bicycling; (5)
+for active travel; (3) behaviors and attitudes; (4) bicycling; (5)
 walking; (6) built environment; (7) trip choice; (8) active school
@@
 of busing in the topic modelling, the documents indicate that there is
-an opportunity for or prospect of behaviour change. Some cities and
+an opportunity for or prospect of behavior change. Some cities and
 schools explain how children and parents can leave the car at home and
@@
 
-Finally, both AST frames present solutions to encourage AST. STP
-stakeholder groups seem to be communicating that AST is a healthy and
-easy option as a result of policy changes (e.g., available resources for
-parents and children) and improvements to the built environment. This
-could include examples of various efforts that are underway to support
-AST including route planning.
+Finally, both frames present the benefits of AST. STP stakeholder groups
+seem to be communicating that AST is a healthy and accessible option as
+a result of school travel plans and improvements to the built
+environment. This could include examples of various efforts that are
+underway to support AST including route planning.
 
@@
 
+Beyond supporting communities to develop STPs, these frames tend to
+place responsibility for change squarely on the members of the
+community:
+
+\begin{quote}
+\emph{A way to make sure your child is safe while walking to school is
+with a `walking school bus.' Here are some tips for a walking
+schoolbus\ldots{[}tips{]}\ldots Have fun!} (City of Ottawa)
+\end{quote}
+
 \hypertarget{discussion}{%
@@
 
-Interpretation of the text assisted by natural language processing
-reveals that AST in Ontario is primarily framed to parents as beneficial
-to the health and wellbeing of children and to environmental
-sustainability. The policy documents reflect the evidence that AST
-contributes positively to children's physical health
+In Ontario, municipalities, school boards and transportation consortia
+do not consistently include AST in their public communications. Indeed,
+as noted above, less than 50\% of documents from these organizations
+discuss AST. Interpretation of the text assisted by natural language
+processing reveals that when AST is discussed, the primary frame
+emphasizes its benefits to the health and wellbeing of both children and
+the environment. In the rest of the documents, the primary way AST is
+framed tends to emphasize the benefits to the health and wellbeing of
+children and to the environment. The policy documents reflect the
+evidence that AST contributes positively to children's physical health
 \citep[see][]{faulknerActiveSchoolTransport2009, schoeppeAssociationsChildrenActive2015},
@@
 \citep{eversParentSafetyPerceptions2014, mammenUnderstandingDriveEscort2012, rothmanAssociationsParentsPerception2015, wilsonUnderstandingChildParent2018}
-or to reduce the frequency of risky behaviours from drivers around
+or to reduce the frequency of risky behaviors from drivers around
 schools \citep{rothmanSchoolEnvironmentStudent2017}.
@@
 way for children to travel to and from school. Children and parents are
-encouraged to adopt new travel behaviours. STP stakeholder groups
+encouraged to adopt new travel behaviors. STP stakeholder groups
 identified different ways that parents could encourage or support their
@@
 
-Both frames present the AST issue in a positive light. Neither frame
-appears to explain why declining rates of AST are a problem or convey
-any urgency to this issue so that it attracts the attention of parents,
-the general public, or policy makers. Communicating the potential
-outcomes of increased AST may be persuasive arguments to motivate
-behaviour change, but these frames do not seem to encourage parents or
-the general public to view their current behaviour as problematic or
-unhealthy for their children's development and their community. Thus,
-behaviour change is presented as an option for some but not an
-imperative for all. For example, parents who drive their children to
-school have reported concerns about traffic volume around schools
+Both frames present AST in a positive light, by highlighting the
+potential benefits. However, neither frame appears to explain why
+declining rates of AST are a problem or convey any urgency to this issue
+so that it attracts the attention of parents, the general public, or
+policy makers. For example, parents who drive their children to school
+have reported concerns about traffic volume around schools
 \citep{mammenUnderstandingDriveEscort2012}, but may not recognize that
-their own behaviour contributes to the problem that is perceived to
+their own behavior contributes to the problem that is perceived to
 prevent their child from safely walking or bicycling to school
-\citep{collinsSafeJourneysEnterprising2001}. Reynard et al.
-\citeyearpar{reynardGrowthResilienceHow2021} similarly found in their
-analysis of Canadian municipal documents that one of the dominant frames
-presented the adoption of behaviours to help mitigate the climate crisis
-as a choice but not ``the expected norm''.
+\citep{collinsSafeJourneysEnterprising2001, rothmanSchoolEnvironmentStudent2017}.
+There is evidence that negative framing is more effective at eliciting
+responses than positive framing (e.g., Kahneman and Tversky, 1979;
+Waygood and Avineri, 2018). In this case, the frames emphasize the
+positive side of active travel but leave the negative impacts of
+behaviors such driving children to school out of the frame.
 
-We found that the proposed solutions in the secondary frame to increase
-AST align with different levels of the SEM: 1) behaviour change from
-households making different travel decisions; 2) policies that create
-resources for AST; and 3) engineering solutions like bicycle lanes. This
+Further, behavior change is mainly presented as an option for some but
+not an imperative for all, which keeps collective action through
+government entities out of the frame. This echoes the findings of
+Reynard et al. \citeyearpar{reynardGrowthResilienceHow2021}, who found
+in their analysis of Canadian municipal documents that one of the
+dominant frames was to present behaviors that help mitigate the climate
+crisis as an individual choice but not ``the expected norm'', or what
+society approves of, i.e., an injunctive norm
+\citep{lapinski2005explication}. In this case, a stronger case of
+society's disapproval remains to be made.
+
+Overall, we find that the proposed solutions in the secondary frame
+reinforce some of the same ideas: 1) behavior change from households
+making different travel decisions (individual responsibility); 2)
+policies that create resources for AST (mainly through education and
+plannning); and 3) engineering solutions like bicycle lanes. This
 reflects findings from the AST literature that a range of solutions are
@@
 as well as the evidence that the built environment influences mode
-choice to school. However, it is beyond the scope of this paper to
-assess whether the proposed solutions are perceived to be sufficient by
-parents for increasing AST.
+choice to school. However, these measures tend to support the desired
+behavior without confronting the problem behavior with interventions
+such as forbidding drop-off within 100 m of the school, restricting
+vehicular traffic to only local traffic around schools at school-commute
+times, such as found in countries where nearly no children die while
+going to school \citep{waygood2020japan}.
+
+As well as what is \emph{in} the frame, it is also interesting to look
+for what is \emph{not} there. The conservative orientation of the frames
+does not fundamentally challenge the status quo: not surprisingly, the
+frames advocate the option of active travel for those who are interested
+in realizing its benefits, but do not make a case for fundamental
+changes to the local environment, and also do not present a moral
+imperative for change \citep{severson2015moral}. The individualistic
+approach also means that a call for collective action tends to be
+missing.
 
@@
 
-STP stakeholders should problematize the significant decline in AST that
-has occurred over recent decades in Canada and emphasize that this issue
-merits urgent behaviour change. A negative framing that challenges the
-social norm of driving could be more motivational to shift transport
-modes, which would be consistent with other findings
-\citep[see][]{waygoodCO2ValenceFraming2018}. Policy documents should
-make it clear that continued use of nonactive modes to school can
-deprive children of opportunities to increase physical activity and to
-gain health and social benefits.
+As we noted in Section \ref{stp-frames} above, STP in Ontario relies
+heavily on education and encouragement. From the get-go, these are not
+the strongest tools of government action {[}compared to, say, regulation
+and transfers; see \citet{ohare1989typology}{]}. The conservative
+framing used further dilutes the force of STP interventions. If we had
+to paraphrase the way AST is framed across the province, it would be
+like this: ``eating spinach is good for you; here are some tips to help
+you choose spinach.'' The issues are presented as a matter of personal
+choice, purely optional, and without a sense of urgency. While
+emphasizing the risks may seem counterproductive, this approach has been
+found to be effective at motivating change
+\citep[e.g.,][]{lawlor2018risk, waygoodCO2ValenceFraming2018}.
+Accordingly, communications with the public could emphasize the risks
+associated with continued use of nonactive modes to school.
 
-There is a noticeable lack of focus on certain household determinants of
-AST in the two frames that needs to be addressed. For example, the role
-of convenience and inclement weather in shaping household travel
-decisions \citep{buliungSchoolTravelPlanning2011} and the complexity of
-travel arrangements that must be coordinated by households
-\citep[see][]{buliungLivingJourneySchool2021} were not found to be
-discussed. The desire to escort children to school, which has been noted
-by parents as a reason to continue driving
-\citep{westmanWhatDrivesThem2017}, is also not adequately addressed by
-STP stakeholders. Parental assessment of a child's ability to undertake
-the journey to school was likewise overlooked despite its role in
-decision making for mode choice to school
+In addition to privileging choice, the frames tend to leave out a number
+of household determinants of AST. There was little discussion of
+socio-economic and demographic attributes associated with AST, such as
+age of children, parental education, income, and ethnicity
+\citep{rothmanDeclineActiveSchool2018}. Similarly, there was no
+discussion about the role of convenience and inclement weather in
+shaping household travel decisions
+\citep{buliungSchoolTravelPlanning2011} and the complexity of travel
+arrangements that must be coordinated by households
+\citep[see][]{buliungLivingJourneySchool2021}. The desire to escort
+children to school, which has been noted by parents as a reason to
+continue driving \citep{westmanWhatDrivesThem2017}, is also not
+adequately addressed by STP stakeholders. Parental assessment of a
+child's ability to undertake the journey to school was likewise
+overlooked despite its role in decision making for mode choice to school
 \citep{faulknerWhatQuickestEasiest2010}. Framing AST as a developmental
@@
 
-Future research and evaluation by STP stakeholders should investigate
-how parents or the general public respond to messages or information
-that encourages the adoption of AST and evaluate which are most
-effective. It would be helpful to understand which frames would most
-encourage behaviour change or increase political support for
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+In this paper we examined how AST is framed in Ontario. Our analysis was
+supported by the use of natural language processing techniques, and
+reavealed that STP stakeholders frame AST as an accessible and feasible
+way to travel to school that is valuable to children's health and to the
+environment. STP stakeholders are communicating that this issue can be
+addressed through household behavior change and policy solutions. Policy
+documents reveal that STP stakeholders are focusing on ``modifiable
+factors'' such as parental perceptions or micro-scale elements in the
+built environment to increase rates of AST. However, AST may not be
+framed sufficiently as a ``problem'' that requires urgent intervention,
+which may impact how parents respond to behavior change initiatives and
+limit awareness in the general public. In their public materials about
+AST, STP stakeholders should emphasize why AST rates should increase in
+local communities and how the negative effects of nonactive modes to
+school may impact children's health and wellbeing. In summary, AST is
+presented in terms of potential benefits, but there is no real
+discussion whether they can be realized with only modest adjustments to
+the status quo.
+
+In terms of future research, we suggest the need for further
+investigation into how parents or the general public respond to messages
+or information that encourages the adoption of AST and evaluate which
+are most effective. It would be helpful to understand which frames would
+most encourage behavior change or increase political support for
 interventions that address barriers to AST. This type of information
@@
 
-\hypertarget{limitations}{%
-\subsection{Limitations}\label{limitations}}
+It is pertinent at this point to note that a limitation of this study is
+that we only analyzed English-language texts that were easily accessible
+to the general public on the websites of STP stakeholders in Ontario. We
+did not include French-language materials from Ontario's 12 French
+school boards (a mixture of public and Catholic schools). Parents likely
+receive information about AST directly from schools, which may contain
+more content that reflects the local barriers to AST, but these
+materials were not used in our analysis.
 
-A limitation of this study is that we only analyzed English-language
-texts that were easily accessible to the general public on the websites
-of STP stakeholders in Ontario. We did not include French-language
-materials from Ontario's 12 French school boards (a mixture of public
-and Catholic schools). Parents likely receive information about AST
-directly from schools, which may contain more content that reflects the
-local barriers to AST, but these materials were not used in our
-analysis.
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-In this paper we examined how AST is framed in Ontario. Our analysis was
-supported by the use of natural language processing techniques, and
-reavealed that STP stakeholders frame AST as an accessible and feasible
-way to travel to school that is valuable to children's health and to the
-environment. STP stakeholders are communicating that this issue can be
-addressed through household behaviour change and policy solutions.
-Policy documents reveal that STP stakeholders are focusing on
-``modifiable factors'' such as parental perceptions or micro-scale
-elements in the built environment to increase rates of AST. However, AST
-may not be framed sufficiently as a ``problem'' that requires urgent
-intervention, which may impact how parents respond to behaviour change
-initiatives and limit awareness in the general public. In their public
-materials about AST, STP stakeholders should emphasize why AST rates
-should increase in local communities and how the negative effects of
-nonactive modes to school may impact children's health and wellbeing.
+Finally, we would like to close with a brief note on the methodology.
+Natural language processing and analysis of frames are still not widely
+adopted in transportation research. Based on our experience, we tend to
+see computer-assisted text analysis as a complement to rather than a
+substitute for expert reading of the documents. We would not recommend
+to proceed to interpretation without reading the documents, but the
+supervised automation helps to detect patterns that can be validated by
+an expert based on spot checks or more in-depth reading of the original
+sources. Like with any qualitative research, interpretation of the
+frames may differ by expert; in this research we aimed to develop a
+consensus interpretation by involving all authors in the discussion of
+the results. Furthermore, since the research is an open, reproducible
+project, all our assumptions are open to scrutiny and others use the
+data to check and/or expand the analysis presented here.
 

### 2023-12-11 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
More revisions requested by Elisabetta Cherchi that feel like make-work

@@
 We conclude that framing of AST in Ontario is mostly empirical-scientific in style, and largely in agreement with academic research on AST.
-However, it is essentially conservative and does challenge to the status quo of motorized travel.
+However, it is essentially conservative and does not challenge the status quo of motorized travel.
 Furthermore, the frames tend to download responsibility for change to households, which limits the scope of policy alternatives by keeping collective action out of the frame.
@@
 The results of this analysis, along with manual checks of the corpus by the authors, lead us to conclude that AST is framed as a matter of individual choices instead of collective action.
-The message is reasonable but inherently conservative and it fails to communicate a sense of urgency about health and environmental issues, which may help to explain the modest success of related policies [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014; @mammenActiveSchoolTravel2014]
+The message is reasonable but inherently conservative and it fails to communicate a sense of urgency about health and environmental issues, which may help to explain the modest success of related policies [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014; @mammenActiveSchoolTravel2014].
 
@@
 Contrariwise, framing can be instrumental to revealing more diverse policy options than conventional wisdom would have [@bosomworth2015climate].
-Ultimately, it is important to understand framing of policy issues because creating meaning through frames contributes to the constant process of shaping of our collective understanding of issues, uncovering what we collectively find (un)acceptable and why [@beland2014developing].
+Ultimately, it is important to understand framing of policy issues because creating meaning through frames contributes to the constant process of shaping our collective understanding of issues, uncovering what we collectively find (un)acceptable and why [@beland2014developing].
 
@@
 For example, parents who drive their children to school have reported concerns about traffic volume around schools [@mammenUnderstandingDriveEscort2012], but may not recognize that their own behavior contributes to the problem that is perceived to prevent their child from safely walking or bicycling to school [@collinsSafeJourneysEnterprising2001; @rothmanSchoolEnvironmentStudent2017].
-There is evidence that negative framing is more effective at eliciting responses than positive framing (e.g., Kahneman and Tversky, 1979; Waygood and Avineri, 2018).
+There is evidence that negative framing is more effective at eliciting responses than positive framing [e.g., @kahneman1979interpretation; @waygoodCO2ValenceFraming2018].
 In this case, the frames emphasize the positive side of active travel but leave the negative impacts of behaviors such driving children to school out of the frame.
@@
 
-Overall, we find that the proposed solutions in the secondary frame reinforce some of the same ideas: 1) behavior change from households making different travel decisions (individual responsibility); 2) policies that create resources for AST (mainly through education and plannning); and 3) engineering solutions like bicycle lanes.
+Overall, we find that the proposed solutions in the secondary frame reinforce some of the same ideas: 1) behavior change from households making different travel decisions (individual responsibility); 2) policies that create resources for AST (mainly through education and planning); and 3) engineering solutions like bicycle lanes.
 This reflects findings from the AST literature that a range of solutions are needed to address different factors that influence AST [_inter alia, see_ @mitraIndependentMobilityMode2013; @panterAttitudesSocialSupport2010].
@@
 
-## Implications for school travel planning
-
-As we noted in Section \ref{stp-frames} above, STP in Ontario relies heavily on education and encouragement.
-From the get-go, these are not the strongest tools of government action [compared to, say, regulation and transfers; see @ohare1989typology].
-The conservative framing used further dilutes the force of STP interventions.
-If we had to paraphrase the way AST is framed across the province, it would be like this: "eating spinach is good for you; here are some tips to help you choose spinach." The issues are presented as a matter of personal choice, purely optional, and without a sense of urgency.
-While emphasizing the risks may seem counterproductive, this approach has been found to be effective at motivating change [e.g., @lawlor2018risk; @waygoodCO2ValenceFraming2018].
-Accordingly, communications with the public could emphasize the risks associated with continued use of nonactive modes to school.
+## Policy implications
+
+Starting in 2017, the province of Ontario has had a policy of supporting communities develop Active School Travel initiatives.
+By 2021, this initiative had awarded millions of dollars to over 25 projects across the province, including for School Travel Plans (STP).
+As we noted in Section \ref{stp-frames}, STP in Ontario rely heavily on education and encouragement.
+From the get-go, these are not the strongest policy tools, compared to, say, construction of infrastructure, regulation, or transfers [see @ohare1989typology].
+
+Given the weight that education and encouragement are expected to carry in the process, it is important to understand how the relevant issues are communicated to the public.
+The results of the research indicate that various authorities in Ontario frame AST in a conservative way that dilutes the force of STP interventions.
+If we had to paraphrase the way AST is framed across the province, it would be like this: "eating spinach is good for you; here are some tips to help you choose spinach." The issues are presented as a matter of personal choice, where action is purely optional, and lacking a sense of urgency.
+While emphasizing the risks may seem counterproductive, generating awareness of consequences of a lack of action has been found to be effective at motivating change [e.g., @lawlor2018risk; @waygoodCO2ValenceFraming2018].
+Accordingly, communications with the public would do well to emphasize the risks associated with continued use of nonactive modes to school.
 
@@
 Framing AST as a developmental opportunity or a rite of passage that children have been denied could challenge the prevailing culture of risk avoidance which discourages parents from letting their children use active modes to school.
+
+Assuming that School Travel Plans will continue to be emphasized as one of the key policies to increase Active School Travel in Ontario, we suggest that the way the issues are framed by authorities and communities be revised as follows:
+
+1.
+Active School Travel is already presented in a positive light ("it is good for you"), but the risks of inaction are not sufficiently communicated ("continued used of fossil fuels threatens our natural environment").
+1.
+Individual choices are important ("here are tips to choose spinach"), but collective action is more effective ("we all need to eat some spinach").
+Accordingly, AST should be presented as a choice that not only some individuals make, but importantly, that communities make _sometimes through their authorities_.
+1. Recognize variations in capabilities in STP; framing AST as a war on some mobility styles confounds the need for certain mobility styles by people with various financial and physical capabilities.
+1. Recognize the agency of children, as their voices do not seem to be properly reflected in any of the frames.
 

### 2023-12-11 AST-Framing-Ontario/AST-Framing-Ontario.tex
More revisions requested by Elisabetta Cherchi that feel like make-work

@@
   agreement with academic research on AST. However, it is essentially
-  conservative and does challenge to the status quo of motorized travel.
-  Furthermore, the frames tend to download responsibility for change to
-  households, which limits the scope of policy alternatives by keeping
-  collective action out of the frame.
+  conservative and does not challenge the status quo of motorized
+  travel. Furthermore, the frames tend to download responsibility for
+  change to households, which limits the scope of policy alternatives by
+  keeping collective action out of the frame.
   \end{abstract}
@@
 related policies
-\citep{buliungSchoolTravelPlanning2011, mammenSchoolTravelPlanning2014, mammenActiveSchoolTravel2014}
+\citep{buliungSchoolTravelPlanning2011, mammenSchoolTravelPlanning2014, mammenActiveSchoolTravel2014}.
 
@@
 framing of policy issues because creating meaning through frames
-contributes to the constant process of shaping of our collective
+contributes to the constant process of shaping our collective
 understanding of issues, uncovering what we collectively find
@@
 There is evidence that negative framing is more effective at eliciting
-responses than positive framing (e.g., Kahneman and Tversky, 1979;
-Waygood and Avineri, 2018). In this case, the frames emphasize the
-positive side of active travel but leave the negative impacts of
-behaviors such driving children to school out of the frame.
+responses than positive framing
+\citep[e.g.,][]{kahneman1979interpretation, waygoodCO2ValenceFraming2018}.
+In this case, the frames emphasize the positive side of active travel
+but leave the negative impacts of behaviors such driving children to
+school out of the frame.
 
@@
 policies that create resources for AST (mainly through education and
-plannning); and 3) engineering solutions like bicycle lanes. This
+planning); and 3) engineering solutions like bicycle lanes. This
 reflects findings from the AST literature that a range of solutions are
@@
 
-\hypertarget{implications-for-school-travel-planning}{%
-\subsection{Implications for school travel
-planning}\label{implications-for-school-travel-planning}}
-
-As we noted in Section \ref{stp-frames} above, STP in Ontario relies
-heavily on education and encouragement. From the get-go, these are not
-the strongest tools of government action {[}compared to, say, regulation
-and transfers; see \citet{ohare1989typology}{]}. The conservative
-framing used further dilutes the force of STP interventions. If we had
-to paraphrase the way AST is framed across the province, it would be
-like this: ``eating spinach is good for you; here are some tips to help
-you choose spinach.'' The issues are presented as a matter of personal
-choice, purely optional, and without a sense of urgency. While
-emphasizing the risks may seem counterproductive, this approach has been
-found to be effective at motivating change
+\hypertarget{policy-implications}{%
+\subsection{Policy implications}\label{policy-implications}}
+
+Starting in 2017, the province of Ontario has had a policy of supporting
+communities develop Active School Travel initiatives. By 2021, this
+initiative had awarded millions of dollars to over 25 projects across
+the province, including for School Travel Plans (STP). As we noted in
+Section \ref{stp-frames}, STP in Ontario rely heavily on education and
+encouragement. From the get-go, these are not the strongest policy
+tools, compared to, say, construction of infrastructure, regulation, or
+transfers \citep[see][]{ohare1989typology}.
+
+Given the weight that education and encouragement are expected to carry
+in the process, it is important to understand how the relevant issues
+are communicated to the public. The results of the research indicate
+that various authorities in Ontario frame AST in a conservative way that
+dilutes the force of STP interventions. If we had to paraphrase the way
+AST is framed across the province, it would be like this: ``eating
+spinach is good for you; here are some tips to help you choose
+spinach.'' The issues are presented as a matter of personal choice,
+where action is purely optional, and lacking a sense of urgency. While
+emphasizing the risks may seem counterproductive, generating awareness
+of consequences of a lack of action has been found to be effective at
+motivating change
 \citep[e.g.,][]{lawlor2018risk, waygoodCO2ValenceFraming2018}.
-Accordingly, communications with the public could emphasize the risks
-associated with continued use of nonactive modes to school.
+Accordingly, communications with the public would do well to emphasize
+the risks associated with continued use of nonactive modes to school.
 
@@
 
+Assuming that School Travel Plans will continue to be emphasized as one
+of the key policies to increase Active School Travel in Ontario, we
+suggest that the way the issues are framed by authorities and
+communities be revised as follows:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Active School Travel is already presented in a positive light (``it is
+  good for you''), but the risks of inaction are not sufficiently
+  communicated (``continued used of fossil fuels threatens our natural
+  environment'').
+\item
+  Individual choices are important (``here are tips to choose
+  spinach''), but collective action is more effective (``we all need to
+  eat some spinach''). Accordingly, AST should be presented as a choice
+  that not only some individuals make, but importantly, that communities
+  make \emph{sometimes through their authorities}.
+\item
+  Recognize variations in capabilities in STP; framing AST as a war on
+  some mobility styles confounds the need for certain mobility styles by
+  people with various financial and physical capabilities.
+\item
+  Recognize the agency of children, as their voices do not seem to be
+  properly reflected in any of the frames.
+\end{enumerate}
+
 \hypertarget{conclusion}{%

### 2023-12-14 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Elisabetta requested one more edit.

@@
 
+> "Half the money I spend on advertising is wasted; the trouble is I don't know which half."  
+> --- John Wanamaker
+
 In this paper we examined how AST is framed in Ontario.
@@
 If Canadian STP stakeholders wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different materials that communicate why this issue is important to the general public, regardless of whether they currently have children commuting to/from school.
+A difficulty when thinking about effective frames is, as an anonymous peer-reviewer insisted, demonstrating that a given strategy for communicating policy is "good value for money".
+It is perhaps the case that half of all the money spent in communications is wasted but, as Wanamaker quiped, it is seldom clear which half.
+We are not aware of any studies that try to assess the cost-effectiveness of different frames, and we suggest that this might be a fruitful area for future research in controlled settings, for example using stated preference experiments.
 

### 2023-12-14 AST-Framing-Ontario/AST-Framing-Ontario.tex
Elisabetta requested one more edit.

@@
 
+\begin{quote}
+``Half the money I spend on advertising is wasted; the trouble is I
+don't know which half.''\\
+--- John Wanamaker
+\end{quote}
+
 In this paper we examined how AST is framed in Ontario. Our analysis was
@@
 this issue is important to the general public, regardless of whether
-they currently have children commuting to/from school.
+they currently have children commuting to/from school. A difficulty when
+thinking about effective frames is, as an anonymous peer-reviewer
+insisted, demonstrating that a given strategy for communicating policy
+is ``good value for money''. It is perhaps the case that half of all the
+money spent in communications is wasted but, as Wanamaker quiped, it is
+seldom clear which half. We are not aware of any studies that try to
+assess the cost-effectiveness of different frames, and we suggest that
+this might be a fruitful area for future research in controlled
+settings, for example using stated preference experiments.
 

### 2024-01-10 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Minor fixes to bibliography and text

@@
 Interpretation of the text assisted by natural language processing reveals that when AST is discussed, the primary frame emphasizes its benefits to the health and wellbeing of both children and the environment.
-In the rest of the documents, the primary way AST is framed tends to emphasize the benefits to the health and wellbeing of children and to the environment.
 The policy documents reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance are less well-supported in the extant literature [@westmanTravelChildWellbeing2020].
@@
 It would be helpful to understand which frames would most encourage behavior change or increase political support for interventions that address barriers to AST.
-This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.
+This type of information could ensure that educational strategies and promotional materials increase buy-in from their target audience.
 If Canadian STP stakeholders wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different materials that communicate why this issue is important to the general public, regardless of whether they currently have children commuting to/from school.

### 2024-01-10 AST-Framing-Ontario/AST-Framing-Ontario.tex
Minor fixes to bibliography and text

@@
 emphasizes its benefits to the health and wellbeing of both children and
-the environment. In the rest of the documents, the primary way AST is
-framed tends to emphasize the benefits to the health and wellbeing of
-children and to the environment. The policy documents reflect the
-evidence that AST contributes positively to children's physical health
+the environment. The policy documents reflect the evidence that AST
+contributes positively to children's physical health
 \citep[see][]{faulknerActiveSchoolTransport2009, schoeppeAssociationsChildrenActive2015},
@@
 could ensure that educational strategies and promotional materials
-increase buy-in for their target audience. If Canadian STP stakeholders
+increase buy-in from their target audience. If Canadian STP stakeholders
 wish to involve more local residents in their efforts

### 2024-05-07 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Added package with files for Elisabetta

--- 2023-12-11 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
@@
 We conclude that framing of AST in Ontario is mostly empirical-scientific in style, and largely in agreement with academic research on AST.
-However, it is essentially conservative and does not challenge the status quo of motorized travel.
+However, it is essentially conservative and does challenge to the status quo of motorized travel.
 Furthermore, the frames tend to download responsibility for change to households, which limits the scope of policy alternatives by keeping collective action out of the frame.
@@
 ```{r load-packages, include=FALSE}
-library(DiagrammeR)
-library(dplyr)
-library(ggraph)
-library(ggplot2)
-library(igraph)
-library(kableExtra)
-library(pdftools)
-library(readr)
-library(reshape2)
-library(stringr)
-library(text2vec)
-library(textdata)
-library(tidyr)
-library(tidytext)
-library(tm) 
-library(tools)
-library(topicmodels)
-library(widyr)
-library(word2vec)
-library(wordcloud)
-library(ldatuning)
-library(quanteda)
+library(DiagrammeR) # Graph/Network Visualization
+library(dplyr) # A Grammar of Data Manipulation
+library(ggraph) # An Implementation of Grammar of Graphics for Graphs and Networks
+library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
+library(igraph) # Network Analysis and Visualization
+library(kableExtra) # Construct Complex Table with 'kable' and Pipe Syntax
+library(pdftools) # Text Extraction, Rendering and Converting of PDF Documents
+library(readr) # Read Rectangular Text Data
+library(reshape2) # Flexibly Reshape Data: A Reboot of the Reshape Package
+library(stringr) # Simple, Consistent Wrappers for Common String Operations
+library(text2vec) # Modern Text Mining Framework for R
+library(textdata) # Download and Load Various Text Datasets
+library(tidyr) # Tidy Messy Data
+library(tidytext) # Text Mining using 'dplyr', 'ggplot2', and Other Tidy Tools
+library(tm) # Text Mining Package 
+library(tools) # Tools for Package Development
+library(topicmodels) # Topic Models
+library(widyr) # Widen, Process, then Re-Tidy Data
+library(word2vec) # Distributed Representations of Words
+library(wordcloud) # Word Clouds
+library(ldatuning) # Tuning of the Latent Dirichlet Allocation Models Parameters
+library(quanteda) # Quantitative Analysis of Textual Data
 ```
@@
 The results of this analysis, along with manual checks of the corpus by the authors, lead us to conclude that AST is framed as a matter of individual choices instead of collective action.
-The message is reasonable but inherently conservative and it fails to communicate a sense of urgency about health and environmental issues, which may help to explain the modest success of related policies [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014; @mammenActiveSchoolTravel2014].
+The message is reasonable but inherently conservative and it fails to communicate a sense of urgency about health and environmental issues, which may help to explain the modest success of related policies [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014; @mammenActiveSchoolTravel2014]
 
@@
 Contrariwise, framing can be instrumental to revealing more diverse policy options than conventional wisdom would have [@bosomworth2015climate].
-Ultimately, it is important to understand framing of policy issues because creating meaning through frames contributes to the constant process of shaping our collective understanding of issues, uncovering what we collectively find (un)acceptable and why [@beland2014developing].
+Ultimately, it is important to understand framing of policy issues because creating meaning through frames contributes to the constant process of shaping of our collective understanding of issues, uncovering what we collectively find (un)acceptable and why [@beland2014developing].
 
@@
 For example, parents who drive their children to school have reported concerns about traffic volume around schools [@mammenUnderstandingDriveEscort2012], but may not recognize that their own behavior contributes to the problem that is perceived to prevent their child from safely walking or bicycling to school [@collinsSafeJourneysEnterprising2001; @rothmanSchoolEnvironmentStudent2017].
-There is evidence that negative framing is more effective at eliciting responses than positive framing [e.g., @kahneman1979interpretation; @waygoodCO2ValenceFraming2018].
+There is evidence that negative framing is more effective at eliciting responses than positive framing (e.g., Kahneman and Tversky, 1979; Waygood and Avineri, 2018).
 In this case, the frames emphasize the positive side of active travel but leave the negative impacts of behaviors such driving children to school out of the frame.
@@
 
-Overall, we find that the proposed solutions in the secondary frame reinforce some of the same ideas: 1) behavior change from households making different travel decisions (individual responsibility); 2) policies that create resources for AST (mainly through education and planning); and 3) engineering solutions like bicycle lanes.
+Overall, we find that the proposed solutions in the secondary frame reinforce some of the same ideas: 1) behavior change from households making different travel decisions (individual responsibility); 2) policies that create resources for AST (mainly through education and plannning); and 3) engineering solutions like bicycle lanes.
 This reflects findings from the AST literature that a range of solutions are needed to address different factors that influence AST [_inter alia, see_ @mitraIndependentMobilityMode2013; @panterAttitudesSocialSupport2010].
@@
 
-## Policy implications
-
-Starting in 2017, the province of Ontario has had a policy of supporting communities develop Active School Travel initiatives.
-By 2021, this initiative had awarded millions of dollars to over 25 projects across the province, including for School Travel Plans (STP).
-As we noted in Section \ref{stp-frames}, STP in Ontario rely heavily on education and encouragement.
-From the get-go, these are not the strongest policy tools, compared to, say, construction of infrastructure, regulation, or transfers [see @ohare1989typology].
-
-Given the weight that education and encouragement are expected to carry in the process, it is important to understand how the relevant issues are communicated to the public.
-The results of the research indicate that various authorities in Ontario frame AST in a conservative way that dilutes the force of STP interventions.
-If we had to paraphrase the way AST is framed across the province, it would be like this: "eating spinach is good for you; here are some tips to help you choose spinach." The issues are presented as a matter of personal choice, where action is purely optional, and lacking a sense of urgency.
-While emphasizing the risks may seem counterproductive, generating awareness of consequences of a lack of action has been found to be effective at motivating change [e.g., @lawlor2018risk; @waygoodCO2ValenceFraming2018].
-Accordingly, communications with the public would do well to emphasize the risks associated with continued use of nonactive modes to school.
+## Implications for school travel planning
+
+As we noted in Section \ref{stp-frames} above, STP in Ontario relies heavily on education and encouragement.
+From the get-go, these are not the strongest tools of government action [compared to, say, regulation and transfers; see @ohare1989typology].
+The conservative framing used further dilutes the force of STP interventions.
+If we had to paraphrase the way AST is framed across the province, it would be like this: "eating spinach is good for you; here are some tips to help you choose spinach." The issues are presented as a matter of personal choice, purely optional, and without a sense of urgency.
+While emphasizing the risks may seem counterproductive, this approach has been found to be effective at motivating change [e.g., @lawlor2018risk; @waygoodCO2ValenceFraming2018].
+Accordingly, communications with the public could emphasize the risks associated with continued use of nonactive modes to school.
 
@@
 Framing AST as a developmental opportunity or a rite of passage that children have been denied could challenge the prevailing culture of risk avoidance which discourages parents from letting their children use active modes to school.
-
-Assuming that School Travel Plans will continue to be emphasized as one of the key policies to increase Active School Travel in Ontario, we suggest that the way the issues are framed by authorities and communities be revised as follows:
-
-1.
-Active School Travel is already presented in a positive light ("it is good for you"), but the risks of inaction are not sufficiently communicated ("continued used of fossil fuels threatens our natural environment").
-1.
-Individual choices are important ("here are tips to choose spinach"), but collective action is more effective ("we all need to eat some spinach").
-Accordingly, AST should be presented as a choice that not only some individuals make, but importantly, that communities make _sometimes through their authorities_.
-1. Recognize variations in capabilities in STP; framing AST as a war on some mobility styles confounds the need for certain mobility styles by people with various financial and physical capabilities.
-1. Recognize the agency of children, as their voices do not seem to be properly reflected in any of the frames.
 
